### 2025-01-25 paper/main.tex
add paper

\documentclass[fleqn]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{siunitx}
\usepackage{physics}
\usepackage{stmaryrd} % double brackets for jump operator
\usepackage{nameref}
\usepackage{booktabs}
\usepackage{makecell} % for table cells with line breaks
\usepackage{bm}
\usepackage{amsopn}
\usepackage[skip=10pt]{caption}
\usepackage{color}
\usepackage{xcolor,colortbl}
%\usepackage{soul}
\usepackage[nameinlink, capitalise]{cleveref}
\usepackage{graphicx}
\usepackage{graphbox} % for center-aligning figures vertically
\usepackage{tkz-euclide} % draw tikz pictures
\usepackage{subcaption}
\usepackage{tablefootnote} % for table footnotes
\usepackage{float} % figure placement

% Bibliography tools
\usepackage{csquotes}

% Set some cref options
\newcommand{\crefrangeconjunction}{--} % Change crefrange from "to" to dashed
\crefname{figure}{Figure}{Figure}

%% Some new commands
% Partial derivatives
\newcommand{\pdifft}[1]{\frac{\partial  #1}{\partial t}}
\newcommand{\pdiffx}[1]{\frac{\partial #1}{\partial x}}
\newcommand{\pdiffy}[1]{\frac{\partial #1}{\partial y}}
\newcommand{\pdiffxi}[1]{\frac{\partial #1}{\partial x_i}}
\newcommand{\pdiffxj}[1]{\frac{\partial #1}{\partial x_j}}
\newcommand{\secpdiffx}[1]{\frac{\partial^2 #1}{\partial x^2}}
\newcommand{\secpdiffxi}[1]{\frac{\partial^2 #1}{\partial x_i \partial x_i}}
\newcommand{\secpdiffxj}[1]{\frac{\partial^2 #1}{\partial x_j \partial x_j}}

% Norms
\newcommand{\normltwo}[1]{{ \vert\vert#1\vert\vert}_{L^2}}
\newcommand{\normltwovec}[1]{{ \vert\vert#1\vert\vert}_{\mathbf{L}^2}}
\newcommand{\normlinf}[1]{{\vert\vert#1\vert\vert}_{L^{\infty}}}
\newcommand{\Hnorm}[1]{\norm{#1}_{\mathbf{H}^1}}
\newcommand{\Hdivnorm}[1]{\norm{#1}_{\mathbf{H}(\mathrm{div};\Omega)}}

% Integrals
\newcommand{\dx}{\, \mathrm d\bm{x}}
\newcommand{\intO}[1]{\int_{\Omega}#1 \, \mathrm d\bm{x}}
\newcommand{\intG}[1]{\int_{\Gamma}#1 \, \mathrm ds}
\newcommand{\intF}[1]{\int_{\mathcal{F}_k}#1 \, \mathrm dS}
\newcommand{\intGnf}[1]{\int_{\Gamma_{\mathrm{nf}}}#1 \, \mathrm ds}
\newcommand{\intGinj}[1]{\int_{\Gamma_{\mathrm{inj}}}#1 \, \mathrm ds}
\newcommand{\intGin}[1]{\int_{\Gamma_{\mathrm{in}}}#1 \, \mathrm ds}
\newcommand{\intGout}[1]{\int_{\Gamma_{\mathrm{out}}}#1 \, \mathrm ds}
\newcommand{\intGinjout}[1]{\int_{\Gamma_{\mathrm{inj}}\cup\Gamma_{\mathrm{out}}}#1 \, \mathrm ds}
\newcommand{\intGs}[1]{\int_{\Gamma_s}#1 \, \mathrm ds}
\newcommand{\intGc}[1]{\int_{\Gamma_c}#1 \, \mathrm ds}
\newcommand{\intGp}[1]{\int_{\Gamma_p}#1 \, \mathrm ds}

% Domain and boundaries
\newcommand{\Gs}{\Gamma_{s}}
\newcommand{\Gc}{\Gamma_{c}}
\newcommand{\Gp}{\Gamma_{p}}
\newcommand{\Ginj}{\Gamma_{\mathrm{inj}}}
\newcommand{\Gnf}{\Gamma_{\mathrm{nf}}}
\newcommand{\Gin}{\Gamma_{\mathrm{in}}}
\newcommand{\Gout}{\Gamma_{\mathrm{out}}}

% Discontinuity operators
\newcommand{\avg}[1]{\{#1\}}
\newcommand{\jump}[1]{\llbracket#1\rrbracket}

% Bold faced math characters
\newcommand{\ff}{\mathbf{f}}
\newcommand{\nn}{\mathbf{n}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\uuref}{\mathbf{u}_{\mathrm{ref}}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\ww}{\mathbf{w}}
\newcommand{\xx}{\bm{x}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\VV}{\mathbf{V}}
\newcommand{\bsig}{\bm{\sigma}}
\newcommand{\bsigpar}{\hat{\bsig}_{\parallel}}
\newcommand{\bsigperp}{\hat{\bsig}_{\perp}}
\newcommand{\beps}{\bm{\varepsilon}}
\newcommand{\btau}{\bm{\tau}}

% Comments
\newcommand{\lyng}[1]{\textcolor{blue}{#1}}
\newcommand{\rt}[1]{\textcolor{red}{#1}}
\newcommand{\mer}[1]{\textcolor{magenta}{#1}}
\newcommand{\mk}[1]{\textcolor{olive}{MK: #1}}

% Title
\title{Cilia-mediated flow and transport in zebrafish brain ventricles in vivo and in silico}
\author[1,*]{Halvor Herlyng}
\author[1]{Ada J.~Ellingsrud}
\author[1]{Miroslav Kuchta} 
\author[X]{Inyoung Jeong} % OK?
\author[1,3,+]{Marie E.~Rognes} % OK order?
\author[2,+]{Nathalie Jurisch-Yaksi}
\affil[1]{Department for Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway}
\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}}
\affil[+]{these authors contributed equally to this work}
% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={cilia-csf},
  pdfauthor={H.~Herlyng \textit{et al.}}
}
\fi

\begin{abstract}
    This paper presents ...
    %Flow of cerebrospinal fluid in zebrafish brain ventricles is studied in this work. Motivated by experimental observations, we consider motile cilia and cardiac beating as the driving flow mechanisms. A mathematical model of the flow is developed and coupled with a transport model to study the transport of molecules inside the brain ventricles. The Stokes equations are used to model the flow, with the motile cilia acting as a force on the fluid through a stress boundary condition that allows slip at the wall. Transport is modeled with an advection-diffusion equation coupled to the velocity field obtained from solving the Stokes equations. The flow and transport models are discretized with finite element methods. For the Stokes equations we employ a non-conforming discretization based on elements of the Brezzi-Douglas-Marini family. The advection-diffusion equation is discretized with discontinuous Galerkin elements. We implement and solve the discretized equations numerically to simulate flow and transport in a zebrafish brain ventricles geometry obtained with medical imaging.
\end{abstract}
\begin{document}
\maketitle
% Introduction:
% 1. What are cilia and why are they important?
% 2. Previous studies of cilia flow
% 3. What problem do we want to solve
% 4. The model and work done in this paper
\section*{Introduction}
Development of brains and sustaining healthy functioning of the brain relies on a myriad of regulatory processes. One of these processes is the flow of cerebrospinal fluid (CSF) in the brain ventricles. The brain ventricles are hollow structures inside the skull where CSF is produced and flows around, transporting nutrients, neurotransmitters and other molecules important for neural development.

The inner walls of the brain ventricles are lined with an epithelial cell layer. In some regions of the ventricles, motile cilia protrude the epithelial cell layer. Motile cilia are hair-like structures that beat in a metachronal wave pattern such as to generate a complicated flow pattern in the brain ventricles. Motile cilia are also found in other parts of the body where fluids are transport, such as the airways, liver and intestines. Regarding the function of motile cilia in the brain, it has previously been pointed out that further studies are needed for investigating their role~\cite{Eichele2020Cilia-drivenVentricle}, as well as the role of spatially organized CSF flow~\cite{Olstad2019CiliaryDevelopment}, in the development of the brain and its ventricular system.

Experiments~\cite{Olstad2019CiliaryDevelopment} have demonstrated that cilia induce a directional flow in the brain ventricles. In addition to the directional flow induced by motile cilia, a pulsatile component in the CSF flow in zebrafish ventricles has been observed~\cite{Olstad2019CiliaryDevelopment}. Cilia are also found to serve crucial roles in other organs than the brain. Motile cilia are essential for olfactory computations~\cite{Reiten2017Motile-Cilia-MediatedComputations}, and they are also fundamental to mucous transport in the trachea~\cite{Sleigh1988TheCilia}.

Early computational studies modeled ciliary transport of mucous in lungs with mathematics~\cite{Fulford1986Muco-ciliaryLung}. Propulsion of ciliated organisms has for some time been studied with mathematics~\cite{BLAKE1974MechanicsMotion}. According to Brennen~\emph{et al.}~\cite{Brennen1977FluidFlagella}, the study of cilia locomotion and fluid systems utilizing cilia sparked interest after a review on locomotion of protozoa microorganisms performed by Jahn~\emph{et al.}~\cite{Jahn1972LocomotionProtozoa}. Fine-scale interaction between single or several cilia and surrounding fluids has previously been analyzed with mathematics and numerics~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids, Cui2019NumericalMethod, Cui2022AFlow}, also specifically for cilia in brain ventricles of zebrafish embryos~\cite{Salman2022ComputationalEmbryo}. Quantification of bulk flow and effects on bulk transport by cilia arrays (or sheets) have not been studied as much, though by some~\cite{Ramirez-SanJuan2020Multi-scaleArrays}. Two-dimensional modeling of flow and transport mediated by motile cilia in zebrafish brain central canal has previously been carried out~\cite{Thouvenin2020OriginCanal}. There is, however, very limited research on three-dimensional modeling of cilia-mediated flow and transport in brain ventricles. There are a couple of studies indicating that the effect of cilia on CSF flow is local in the human brain~\cite{Siyahhan2014FlowVentricles, Yoshida2022EffectVentricles}. Zebrafish ventricles are much smaller than human ventricles, meaning cilia play a larger role in establishing a CSF flow pattern. We wish to investigate the mechanisms of ciliary and cardiac-beating flow components, and how they each contribute to transport of molecules inside the brain ventricles.

In this paper, we present protein photoconversion experiments in zebrafish embryo brain ventricles, as well as a computational model of cerebrospinal fluid flow and protein transport.

\section*{Methods}\label{sec:methods}
\subsection*{Zebrafish maintenance and strains in photoconversion experiments}
The animal facilities of zebrafish~(\emph{danio rerio}) we used are approved by the Norwegian Food Safety Authority (NFSA, Mattilsynet). Furthermore, the zebrafish were maintained in accordance with the guidelines set by the NFSA and the European Communities Council Directive.

The larval and adult zebrafish were raised under standard husbandry conditions at 28.5°C in a Techniplast Zebtech Multilinking system. The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a 14/10 hr light/dark cycle. From fertilization to 3 dpf, larvae were maintained in egg water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water) and subsequently transferred to artificial fish water (AFW) (1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were \emph{ccdc103(dnaaf19)\textsuperscript{tn222a}} (\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}(received from Drummond lab, MGH) and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures}, \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}. Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.

Wholemount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at the 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described in D’Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}. Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+}) or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding. The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.

\subsection*{Genotyping}
Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA, tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C. To stop the lysis reaction, the samples were heated to 95°C for 10 minutes and then centrifuged at 13000 rpm for 2 minutes. The supernatant containing gDNA was utilized for KASP assays-based analysis. The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™). For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14 $\mu$L of assay mix; 1.86 $\mu$L of RO water.

\subsection*{Generation of \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}} line}
The open reading frame (ORF) of the neuropeptide y (npy) signal peptide (\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal of zebrafish codon optimized Dendra2 DNA sequence. Then the conjugated DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and 3’ ends (GenScript Biotech), and the synthesized signal-Dendra2 DNA was inserted into the pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish} through restriction enzyme cloning (GenScript Biotech).

To generate the transgenic line, the 5xuas:Signal-Dendra2 plasmid DNA was used. A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg) was microinjected into one-cell stage embryos, as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected embryos were raised to adulthood (F0). Germline-transmitted founder zebrafish were identified by breeding with multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven Dendra2 signals were screened and raised to adult zebrafish.

\subsection*{Wholemount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
To image 2 dpf larval zebrafish, the fish were anesthetized in 0.013\% MS222 in AFW and mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100), to obtain a lateral view of the brain ventricles. After the fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify. After solidification, AFW containing 0.013\% MS222 was added, and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss) and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat) at room temperature.

The time-lapse images were acquired in a single plane, covering the telencephalic, diencephalic and rhombencephalic ventricles simultaneously, with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish. The first 10 images were scanned without photoconversion to obtain a baseline value of fluorescence intensity, and the next 290 images were scanned while performing photoconversion.

For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software were used. A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel) of the dorsoposterior diencephalic ventricle with 100\% laser power. The laser was illuminated in the area repeatedly between each scanning. After imaging, the fish health was checked and only data from healthy fish were analyzed.
Data were collected and analyzed from three separate experiments, with a total of 8 controls and 6 mutants.

\subsection*{Photoconversion data analysis}
All data analysis was performed in MATLAB and the codes are available in the repository of this article: \url{repo-link}.

Following import of the image data, the photoconverted channel was aligned to correct for drift in $x,y$ directions using previously developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}. Only stable recordings were further analyzed. 
To increase the signal to noise ratio, the images were downsampled by a block average using a resampling factor of 6 (using the MATLAB function blockproc). The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as $\Delta F$$)$ was calculated for each pixel at each time point of the data. Here, the value $F_0$ is the average fluorescence intensity for the baseline (the first 10 time-lapse images) acquired before photoconversion.

To identify the time needed to pass a certain threshold value, $\Delta F$ values were first smoothened. The first timepoint when values surpassed the threshold was reported per pixel (in the downsampled images). A mask for the image was generated using the green (not photoconverted) channel and calculated on the block-averaged data based on the intensity being higher than 1.5x median intensity of all the frames.

In order to obtain $\Delta F$ values for a region of interest (ROI), ROIs were first drawn on the aligned and block-averaged time series. Six ROIs were drawn manually: ROI 1 at the location of photoconversion, and ROIs 2--6 in different regions of the ventricular system. The pixel values of the fluorescence intensity within one ROI are averaged for each time point, and the relative change $\Delta F$ is then calculated with this averaged value. To normalize the data with respect to photoconversion efficiency, the $\Delta F$ curves for all ROIs were divided by the $\Delta F$ values obtained for ROI 1 at the end of the experiment, so that $\Delta F$ values for the photoconverted site ROI 1 ranged from zero to one. Finally, we average the $\Delta F$ data from controls over the number of controls, and the data from mutants over the number of mutants. We report these mean values together with a one-standard deviation error band.

\subsection*{Intraventricular injection of microbeads and particle tracking}
In addition to photoconversion experiments, we carried out particle tracking inside the brain ventricles of a larval zebrafish, to demonstrate the motile-cilia and cardiac-cycle related flow features observed and described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}. A schematical illustration of the flow features in the brain ventricles is shown in~\cref{fig:figure1}, panel \textbf{a}. The experimental setup is identical (\lyng{HH: Is this true?}) to the ones considered there, and we refer to that paper for further details than the ones provided here in the following.

Anesthetized 2 dpf control zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads (SPHERO Fluorescent Yellow Particles 1\% w/v, $F = 0.16$ mm) diluted in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITC-dextran; Sigma-Aldrich, R9379) dissolved in artificial cerebrospinal fluid. Artificial cerebrospinal fluid composition was as follows: 124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O, 1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3}, 2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O. The needles used for the injections were pulled with a Sutter Instrument Co. Model P-2000 from thin-walled glass capillaries (1.00 mm; VWR) and cut open with a forceps. A volume of 1 nl of the solution was injected with a pressure injector (Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle. The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.

Following injection, the zebrafish was directly placed under the confocal microscope and 1200 images were acquired at a frequency of 13.1 Hz. A single optical section was obtained. Particle tracking was done using TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis} and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}. The parameters for TrackMate were as follows. The DoG detector was used with the settings: threshold: 2.0, with median filtering; radius: 2.0, with subpixel localization. Next, the Simple LAP tracker was used with settings: max frame gap: 2; alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0; splitting max distance: 15.0; allow gap closing: true; allow track splitting: false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9. Only the particle tracks with at least 30 data points, while simultaneously covering a distance of at least 8.8 $\mu$m, were plotted in~\cref{fig:figure1} (panels \textbf{b} and \textbf{c}).

\subsection*{Image-based computational geometry of zebrafish brain ventricles}
We generated a 3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. From the imaging data, we constructed a computational mesh of the ventricles (\cref{fig:figure1}, panel \textbf{d}). The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. The standard mesh consisted of 132 134 tetrahedral cells associated with a total of 943 820 degrees of freedom, and the mesh had a maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic  (anterior), the di-/mesencephalic  (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts.

Motile cilia were shown to line certain parts of the ventricular surface~\cite{Olstad2019CiliaryDevelopment}, as marked with pink in~\cref{fig:figure1} (panel \textbf{d}). Beating motion of the cilia generates cerebrospinal fluid (CSF) flow with rotational structures in the brain ventricles, resulting in a compartmentalized flow~(\cref{fig:figure1}, panels \textbf{a}--\textbf{c}). Meanwhile, the beating heart of the zebrafish embryo induces a pulsatile CSF flow component.
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=\linewidth]{graphics/figure1.png}
    \caption{\lyng{Experimenting with velocity colorbars, thoughts on the two options? Or have two separate as it is now?}}
    \label{fig:figure1}
\end{figure}

\subsection*{Computational model of cerebrospinal fluid dynamics}
We model the flow of cerebrospinal fluid (CSF) in the brain ventricles by the time-dependent, incompressible Stokes equations: find the fluid velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$ and the fluid pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
\begin{subequations}
    \begin{align}
  \rho\pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}\mbox{ in }\Omega,\label{eq:stokes_eq_mom}\\
  \nabla \cdot \uu &= 0\mbox{ in }\Omega,
  \end{align}
  \label{eq:stokes_eqs}% 
\end{subequations}%
where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions. Furthermore, $\rho$ is the CSF density and $\mu$ is the dynamic viscosity of the CSF. We introduce the tangential traction $\bsigpar$ as the tangential component of the traction $\hat{\bsig}=\bsig\nn$:
\begin{equation*}
    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
\end{equation*}
where $\nn$ is the outer unit normal of the surface $\Gamma = \partial\Omega$, and $P_{\nn}(\rr)$ is the tangential  projection of a vector $\rr$ onto $\Gamma$. We consider three types of boundary conditions:  (i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$), (ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$), and (iii) \emph{free slip} (no flow normal to the boundary $\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$). Unless noted otherwise, the free-slip condition is applied on the boundary. We use the initial conditions $\uu(\xx, 0)=\mathbf{0}$ and $p(\xx, t) = 0$ for all $\xx\in\Omega$.

\subsection*{Cilia-driven flow}
On the boundary $\Gc$ of the ciliated regions of the ventricle walls~(pink-colored facets in~\cref{fig:figure1}, panel \textbf{d}), we impose the tangential traction $\bsigpar=\btau$ to represent the forces from the cilia acting on the cerebrospinal fluid. We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where $\lambda(\xx)$ is a function that is chosen differently for the cilia regions considered~(see~\cref{subsec:appendixA1}). The sign of the vector $\rr=\pm(1, 0, 1)$ also depends on the cilia region. Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by comparing simulations with experimental data~\cite{Olstad2019CiliaryDevelopment}.

\subsection*{Flow induced by cardiac pulsations}\label{subsec:pressure_bcs}
To induce a pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and $\Tilde{p}(t)=-A\sin{\omega t}$ on two separate parts of the boundary $\Gp$, located anterior and posterior, respectively, on the brain ventricles geometry~(blue-colored facets in~\cref{fig:figure1}, panel \textbf{d}). The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow, and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}. The angular cardiac frequency $\omega=2\pi f=6.97$ rad/s was determined by measurements of the cardiac frequency $f=2.22$ Hz.

\iffalse
\subsection*{Computational cerebrospinal fluid dynamics in a moving reference frame}
 An Arbitrary Lagrangian Eulerian (ALE) formulation~\cite{san2009convergence} is used as an alternative to the normal pressure boundary conditions to model back-and-forth flow induced by cardiac pulsations. In a reference frame moving with a velocity $\uuref=(A_{\mathrm{ref}}\sin{\omega t}, 0, 0)$, we reformulate the Stokes equations~\eqref{eq:stokes_eqs} using an ALE formulation:
\begin{subequations}
    \begin{alignat}{2}
        \rho\bigg(\pdifft{\uu} + (\uu_{\mathrm{ref}}\cdot\nabla)\uu\bigg) &= \nabla\cdot\bm{\sigma}(\uu, p), \label{eq:mom_eq_ALE}\\
        \nabla\cdot\uu &= 0.
    \end{alignat}
    \label{eq:stokes_eqs_ALE}%
\end{subequations}%
We then solve for the velocity $\mathbf{w} = \uu - \uuref$ in the moving reference frame, where $\uu$ is the velocity in the fixed reference frame. The amplitude $A_{\mathrm{ref}}=919$ $\mu$m/s, calibrated based on experimental data, determines the magnitude of the pulsatile flow, and $\omega=2\pi f$ is the angular cardiac frequency. In the ALE formulation, we consider the impermeability boundary condition $\mathbf{w}\cdot\nn=0$ in the normal direction and the free-slip boundary condition $\bsigpar(\mathbf{w}, p) = \mathbf{0}$ in the tangential direction.
\fi

\subsection*{Solute transport}
We simulate transport of photoconverted proteins in the brain ventricles by modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and time $t > 0$ by the advection-diffusion equation
\begin{equation}
    \pdifft{c} + \nabla\cdot\JJ = 0\mbox{  in }\Omega,
    \label{eq:adv_diff_strong}
\end{equation}
where $\mathbf{J}$ is the total concentration flux. The total concentration flux is assumed to consist of an advective flux and a diffusive flux:
\begin{equation*}
    \JJ = c\uu - D\nabla c\mbox{ in }\Omega.
\end{equation*}
Here, $\uu$ is the cerebrospinal fluid velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs}, and $D$ is the molecular diffusion coefficient of the solute. The diffusion coefficient was estimated through extrapolation of previous measurements~\cite{GuraSadovsky2017MeasurementExpansion, Mahmood2023ExosomeTemperature, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} via the Stokes-Einstein relation. We elaborate on the extrapolation in a later section.

We set the initial condition $c(\xx, 0)=0$ for all $\xx\in\Omega$. The ventricular walls are assumed to be impermeable, except for at the pressure boundary $\Gamma_p$. We consider three different boundary conditions: (i) \emph{no flux} ($\JJ\cdot\nn=0$), (ii) \emph{influx} (time-periodic condition on the total flux $(\JJ\cdot\nn)|_{\mathrm{in}}^{n+1}=(\JJ\cdot\nn)|_{\mathrm{out}}^{n}$) and (iii) \emph{outflux} (zero diffusive flux $D\nabla c\cdot\nn=0$). Unless stated otherwise, the no-flux condition $\JJ\cdot\nn=0$ was applied on the boundary.
%(ii) \emph{injection site} (imposing the Dirichlet boundary condition $c=\Tilde{c}$),
\subsection*{Modeling protein photoconversion in the brain ventricles}
To represent protein photoconversion in a region $\Omega_{\mathrm{pc}}\subset\Omega$, we prescribe a time-dependent value to the solute concentration in $\Omega_{\mathrm{pc}}$, such that $c(\xx, t)$ for all $\xx\in\Omega_{\mathrm{pc}}$ and $t>0$. The subdomain $\Omega_{\mathrm{pc}}$ is a region in the dorsal part of the diencephalic ventricle that corresponds to the region where photoconversion was performed in experiments. Specifically, for all $\xx\in\Omega_{\mathrm{pc}}$, we set the concentration to 
\begin{equation}
c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}}.
\label{eq:injection_curve}
\end{equation}
The value $a=65$ was chosen so that~\eqref{eq:injection_curve} is similar to the fluorescence intensity curve observed in the physical photoconversion experiments.

Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for. We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$; $\Gout$ denotes the part where $\uu\cdot\nn > 0$. On $\Gin$, a total flux boundary condition was set: the inflow flux at a given timestep was set equal to the outflow boundary flux at the previous timestep. This was done to approximate a periodic boundary condition. On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.

%To represent the solute injection at $\Ginj$ (cf.~\cref{fig:injection_sites}), we impose a constant Dirichlet boundary condition $c=\Tilde{c}$. Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for. We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$; $\Gout$ denotes the part where $\uu\cdot\nn > 0$. On $\Gin$, a total flux boundary condition was set: the inflow flux at a given timestep was set equal to the outflow boundary flux at the previous timestep. This was done to approximate a periodic boundary condition. On $\Gout$, we considered the diffusive flux normal to the boundary to be zero. 
%\lyng{MOVE? Following previous works~\cite{papanastasiou1992new, griffiths1997no, lynch2020numerical}, the advective flux $c\uu$ on $\Gout$ was left as an unknown in the variational form.}

\subsection*{Physical parameters and dimensionless numbers \lyng{HH: Change this to "quantities of interest" and add mean concentration and time to threshold?}}\label{subsec:parameters}
The cerebrospinal fluid density $\rho$ and dynamic viscosity $\mu$ were set following the work of Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}). We considered a range of small, medium and large molecules with three different diffusion coefficients $D_1, D_2$ and $D_3$ (cf. the following section for details on determining their values). Experimental data~\cite{Olstad2019CiliaryDevelopment} indicate velocities proximate to the ventricular walls of $27.4 \pm 5.4 \ \mu$m/s and $2.6 \pm 0.6 \ \mu$m/s in the dorsal and ventral regions of the diencephalic ventricle, respectively. In the telencephalic ventricle, the velocities were estimated at $4.7 \pm 1.3 \ \mu$m/s. We calibrated $\tau$ and $A$ heuristically by comparing these experimental velocity values with the simulated, maximum velocity magnitude. In addition, particle tracking data of pulsatile motion~(\cref{sec:appC_particle_transport}) was used in the calibration process to determine the relative contributions of the cardiac pulsations, as compared to the cilia-driven flow, to the velocity magnitude.
\begin{table}[h!]
    \centering
    \caption{Physical parameters of the flow and transport models. (*) Calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}. (\textdagger) Estimated based on experimental data~\cite{GuraSadovsky2017MeasurementExpansion, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}.}
    \label{tab:parameter_table}
    \begin{tabular}{lcccc}
    \toprule
        Parameter & Symbol & Value & Unit & Reference \\
        \midrule
        Fluid density & $\rho$ & $1000$ & $\mathrm{kg/m^3}$ & \cite{Bloomfield1998EffectsFluid} \\
        Dynamic viscosity & $\mu$ & $\num{6.97e-04}$ & $\mathrm{Pa\cdot s}$ & \cite{Bloomfield1998EffectsFluid} \\
        Cardiac frequency & $f$ & 2.22 & Hz &  \cite{Olstad2019CiliaryDevelopment}\\
        Angular cardiac frequency & $\omega = 2\pi f$ & 6.97 & rad/s & \cite{Olstad2019CiliaryDevelopment}\\
        Cilia tangential traction & $\tau$ & \num{6.5e-04} & Pa & * \\
        Pressure amplitude & $A$ & \num{1.5e-03} & Pa & * \\
        %Ref. frame motion amplitude & $A_{\mathrm{ref}}$ & \num{9.19e-04} & m/s & *\\
        Exosome diffusion coefficient & $D_1$ & $\num{1.63e-12}$ & $\mathrm{m^2/s}$ & \textdagger\\
        STM+GFP diffusion coefficient  & $D_2$ & $\num{5.75e-11}$ & $\mathrm{m^2/s}$ & \textdagger\\
        Dendra2 diffusion coefficient  & $D_3$ & $\num{1.15e-10}$ & $\mathrm{m^2/s}$ & \textdagger\\
    \bottomrule
    \end{tabular}
\end{table}

To evaluate the relative importance of advection and diffusion as transport mechanisms, we consider the Péclet number
\begin{equation*}
    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
\end{equation*}
Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, whereas $D$ is the solute diffusion coefficient as previously. To assess the assumption that the CSF flow is governed by the Stokes equations, we also compute the Reynolds number
\begin{equation*}
    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
\end{equation*}
with $L_r$ and $U_r$ as the length and velocity scales characteristic of the flow.

\subsection*{Estimation of diffusion coefficients with the Stokes-Einstein relation}\label{subsec:diff_coeffs}
Motivated by an interest in molecules that are significant in neural development, we study the transport of molecules resembling Dendra2 Fluorescent Protein (Dendra2), Starmaker+Green Fluorescent Protein (STM+GFP) and Exosomes. In simulations, we use the diffusion coefficients $D_1$, $D_2$ and $D_3$ (\cref{tab:parameter_table}) for these three molecules, respectively. The molecular diffusion coefficients were estimated in part based on values reported in the literature, and in part via extrapolation with the Stokes--Einstein relation (\cref{tab:diff_coeff_table}). The Stokes-Einstein relation
\begin{equation}
    D = \frac{k_B T}{6\pi \mu R}
    \label{eq:D_stokes_einstein}
\end{equation}
is an expression for the diffusion coefficient of a spherical molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}. In~\eqref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant, $T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the solvent (in this case the cerebrospinal fluid), and $R$ is the radius of the molecule. For the exosomes, we calculate $D$ using~\eqref{eq:D_stokes_einstein} with $R=200$ nm. We chose this radius to cover the slowest diffusing exosomes, since the smaller exosomes would have diffusion coefficients similar to the other molecules. For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ should scale roughly with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}. Implicit in this approach is the assumption that the proteins all have the same density.
\begin{table}[h!]
    \centering
    \caption{Estimated diffusion coefficients and diffusion coefficients reported in the literature. STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.  (*) The value was extrapolated based on the value of $D$ for GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that $D$ scales with the cube root of the molecule mass. (\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
    \label{tab:diff_coeff_table}
    \begin{tabular}{l|ccc}
        \toprule
        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
        \midrule 
        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight} & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
        STM+GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{5.75e-11}$ & * \\
        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection*{Model versions and physiological scenarios}\label{subsec:model_versions}
We have introduced boundary conditions to model two separate driving forces of cerebrospinal fluid flow, namely motile cilia and cardiac pulsations. To distinguish the impact of each component, three different setups for the flow model were considered: 
\begin{itemize}
    \item Model 0: The baseline model representing a wild-type zebrafish. Both cilia forces and cardiac pulsations are included in the model.

    \item Model I: Only cilia forces are modeled, no cardiac pulsations.

    \item Model II: Only cardiac pulsations are modeled, no cilia forces.

    %\item Model IIb: Only cardiac pulsations are modeled, using the domain movement approach. No cilia forces.
\end{itemize}
When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments. In region 1, we use the function~\eqref{eq:injection_curve} to enforce the concentration such that it represents the experimental data of photoconversion of proteins. We consider the three different diffusion coefficients introduced in previous sections to simulate and compare results for transport of molecules of varying sizes.

\lyng{Add information on removing cilia and modifying geometries simulation studies in this section?}
\begin{table}[h!]
    \centering
    \caption{A summary of the flow model versions. For all model versions, we consider a free slip boundary condition on $\Gs=\Gamma\setminus\left(\Gc\cup\Gp\right)$.}
    \label{tab:model_versions}
    \begin{tabular}{c|c@{\hskip 0.4in}c}
       \toprule
       Model & Driving force & Flow BCs \\ %& Domain motion \\
       \midrule
       Baseline (0)   & Cilia and cardiac & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$, \\ normal pressure $\Tilde{p}(t)$ on $\Gp$} \\[0.3in] %& No\\[0.3in]
       No cardiac (I) & Cilia   & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$} \\[0.3in]%& No\\[0.3in]
       No cilia (II) & Cardiac & \makecell[c]{Normal pressure $\Tilde{p}(t)$ on $\Gp$} \\% & No\\[0.3in]
       %No cilia (IIb) & Cardiac & \makecell[l]{Impermeability $\mathbf{w}\cdot\nn=0$ and \\ free slip $\bsigpar(\mathbf{w}, p)=\mathbf{0}$ on $\Gamma$}  & Yes \\
       \bottomrule
    \end{tabular}
\end{table}

%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
\subsection*{Numerical approximation of the flow equations}
The Stokes equations~\eqref{eq:stokes_eqs} were discretized with a finite element method. In time, we employ a first-order implicit Euler discretization. We chose the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle. For the spatial discretization, we used piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity. The BDM elements have degrees of freedom associated with integral moments of the velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems}, thus we enforced the impermeability condition $\uu\cdot\nn=0$ strongly. We imposed the boundary conditions for both the tangential traction $\bsigpar$ and the normal pressure $\Tilde{p}(t)$ weakly. For the pressure, we used piecewise constant elements, referred to as zeroth order discontinuous Galerkin (DG) elements. The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a stable discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}. Since the divergence of the velocity is a subspace of the pressure space for this scheme, the divergence-free condition of the velocity is satisfied exactly on each element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation. The BDM discretization includes a penalty parameter $\gamma$ which needs to be chosen large enough to ensure stability of the finite element method. We set $\gamma=10.$

In the absence of pressure boundary conditions, the pressure in the Stokes equations is only determined up to an additive constant. Thus, with the boundary conditions used in model version I, the pressure is not uniquely defined and discretization of the Stokes equations leads to a singular linear equation system. \lyng{To make the discrete problem well-posed for this setup, the right-hand side vector of the linear system assembled after discretization of the Stokes equations equations is orthogonalized with respect to the basis of the nullspace of the pressure to ensure existence of solutions. This nullspace is the set of (real) scalar constants. Furthermore, information of the pressure nullspace is provided to the linear solver, such that a unique solution is determined.}

\subsection*{Numerical approximation of the transport equations}
The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized with a first-order implicit Euler method in time, and a first-order, symmetric interior penalty discontinuous Galerkin (DG) method in space~\cite{Arnold1982AnElements}. Like for the flow equations, we use a timestep size of $\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles, meaning the final time of simulation $T = 856$ s. The DG penalty parameter $\alpha = 25$ was chosen large enough to ensure stability of the finite element method. To accurately approximate the solute concentrations even in the presence of strong advection (high Péclet numbers), we use an upwind scheme for the velocity when calculating the advective flux~\cite{Patankar2018NumericalFlow}.

\subsection*{Solution strategy and software implementation}
Because of the one-way coupling between the velocity field $\uu$ and the concentration $c$, the governing equations for the cerebrospinal fluid flow and the concentration can be solved sequentially when modeling solute transport. For model version I, the flow field is a steady-state solution. In this case, we first solve the Stokes equations~\eqref{eq:stokes_eqs} for $\uu$ and $p$ until we reach the steady-state solution, and then use the velocity field $\uu$ as input when solving the advection-diffusion equation~\eqref{eq:adv_diff_strong}. For the baseline model 0 and model II, the Stokes equations are solved for one period of the pulsatile cardiac motion. The solution of this one period is then used periodically as input when solving the advection-diffusion equation.

The finite element methods derived for the Stokes equations and the advection-diffusion equation were implemented and solved numerically with DOLFINx, the Python interface of the finite element software FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend. For solving the linear systems, a direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the discretized Stokes equations. For the discretized advection-diffusion equation, we used an iterative solver based on the GMRES routine~\cite{Saad1986GMRES:Systems} with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen}. Numerical experiments verified the accuracy of the model implementation (\cref{sec:appB_verification}). The implementation of the model presented in this work is available at~\url{insert-repo-link-here}.

%%--------------RESULTS--------------%%
\section*{Results}\label{sec:results}
\subsection*{Cerebrospinal fluid flow in the brain ventricles is compartmentalized}
With cilia forces and cardiac forces represented in the flow model (model version 0), we observe a vortex-structured flow pattern in the anterior and middle ventricles~(\cref{fig:figure1}, panel \textbf{g} \lyng{Need to reorder panels in figure 1, since results for model 0 are introduced first.}). This rotational motion shows that cilia-mediated flow is dominating in these regions, as the vortex structures are a consequence of the applied tangential stresses on the ciliated boundaries combined with the assumption of fluid incompressibility. In the posterior ventricle, we observe directional flow as the pressure-driven flow is dominating in this region. The cardiac pressure forces induce a pulsatile motion of the cerebrospinal fluid synchronized with the cardiac cycle, with velocity magnitudes of the pulsatile motion being approximately an order of magnitude smaller than the velocities related to the cilia-driven motion. Over a cardiac cycle, the maximum velocity magnitude in the ventricles was 27.7 $\mu$m/s, located dorsally in the posterior part of the middle ventricle. This maximum velocity was attained at the time instant coinciding with the peak of the cardiac pulsatile flow flowing caudally, as a result of both the tangential stress boundary condition and the pulsatile pressure-driven flow being aligned with the rostrocaudal axis (the $x$ axis). A calculation using the observed maximum velocity of 27.7 $\mu$m/s, and choosing the approximate height of the middle ventricle $110 \ \mu$m as a characteristic length scale, yields a Reynolds number $\mathrm{Re} \approx 0.004$, justifying the assumption of Stokes flow.

\subsection*{Vortex structures vanish in the absence of cilia}
Excluding the cilia tangential traction from the model (model II), vortex-structured compartmentalization of the ventricular flow does not occur, and the flow is directional and pulsatile as a result of the pressure boundary conditions imposed~(\cref{fig:figure1}, panel \textbf{d}). The pulsatile motion is absent when disregarding cardiac motion~(model I, see \cref{fig:figure1}, panel \textbf{d}). For model I, the boundary conditions are not time-dependent, rendering the solution to the Stokes equations~\eqref{eq:stokes_eqs} a steady-state flow field. Streamlines demonstrate the compartmentalization of the cerebrospinal fluid flow driven by cilia, and we observe highest vorticity in the vicinity of cilia.

\subsection*{Ventricular solute transport is advection-dominated for small molecules}
To qualitatively analyze protein transport, we compare the solute concentration fields from simulation of photoconversion in a dorsal region of the middle ventricle. We simulate transport using the three diffusion coefficients $D_1$, $D_2$ and $D_3$, and present concentration fields in a slice of the ventricles geometry for each diffusion coefficient at three time instants~(\cref{fig:figure2_compare_diffusion_coefficients}, panel~\textbf{a}). The slices are taken in the $xz$-plane, which aligns with the rostrocaudal axis, at $y=140$ $\mu$m, the center of the geometry. Note that the colorbars colored by the value of the concentration $c$ are different for each column (corresponding to the choice of $D$). Upper limits of the colorbars are the maximum value of $c$ in the respective slice at $t=450.5$ s, for the respective $D$.

Overall, transport occurs more rapidly with increasing diffusion coefficient. For the smallest diffusion coefficient $D_1$ (representing exosomes), advective transport by the cilia-driven cerebrospinal fluid flow dominates diffusion in the distribution of solute concentration~(\cref{fig:figure2_compare_diffusion_coefficients}, panel~\textbf{a}, left column). The rotational flow structures of the velocity field are apparent in the concentration field, indicating that transport along the streamlines of the flow field is more rapid than the diffusion across the streamlines. Diffusive transport becomes more rapid with increasing diffusion coefficient, and the flow structures of the cerebrospinal fluid flow become more obfuscated. This is evident in the concentration fields calculated with the medium ($D_2$, representing STM+GFP) and high ($D_3$, representing Dendra2) diffusion coefficients (\cref{fig:figure2_compare_diffusion_coefficients}, panel \textbf{a}, middle and right column). Compared to the $D_1$ case, for $D_2$ and $D_3$ solute spreads more uniformly throughout the ventricular geometry. Also, for $D_2$ and $D_3$, the solute spreads more quickly to regions distal to the photoconversion site. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}
    \caption{\textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm, the center of the geometry) showing the concentration field simulated with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s. Note that the colorbars indicating the magnitude of $c$ have different limits for each column. \textbf{b--d.} Mean concentration $\overline{c}$ in each region of interest (ROI) as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively. \textbf{e.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs. \textbf{f.} The time $\hat{t}$ before the mean concentration $\overline{c}$ exceeds a threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup. Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}
    \label{fig:figure2_compare_diffusion_coefficients}
\end{figure}

We quantify the transport of solute by showing the profile of the mean concentrations
\begin{equation}
    \overline{c}_i = \frac{1}{|\Omega_i|}\int_{\Omega_i} c\dx,
    \label{eq:c_mean_i}
\end{equation}
in the regions of interest (ROIs) $\Omega_i$ as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$. The $\overline{c}_i$ profiles and an illustration of the ROIs are presented in panels~\textbf{b--e} of~\cref{fig:figure2_compare_diffusion_coefficients}. The dynamics of ROI 1 follows from imposing~\cref{eq:injection_curve}. Note that the total mass added to the system is not exactly the same for all three diffusion coefficients, since the total mass added depends on how fast the mass added in ROI 1 is transported away from that region.

For ROIs 2--6, we observe more rapid concentration increases when the diffusion coefficient increases.  For all three diffusion coefficients, the dynamics of ROI 6 is the slowest. Region 5 exhibits a more rapid increase in mean concentration, and an even faster increase is observed for ROIs 2--4. The profiles of the latter three regions are similar, displaying only small differences in all of the three plots.

As another way of quantifying transport, we report the times $\hat{t}$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}$~(\cref{fig:figure2_compare_diffusion_coefficients}, panel \textbf{f}). We use $\hat{c}=0.25$ for regions 1--4 and $\hat{c}=0.10$ for regions 5 and 6. The choice of different threshold values is because of the slower dynamics in ROIs 5 and 6. In region 6, the threshold is never exceeded for $D_1$, with the mean concentration close to zero at the end of the simulation.

Finally, we calculate Péclet numbers for the entire ventricular geometry using estimates of the diffusion and advection timescales $t_d=L_p^2/D$ and $t_a=L_p/U_p$. Recall that
\begin{equation*}
    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a},
\end{equation*}
so that if $\mathrm{Pe} > 1$, transport is dominated by advection, and if $\mathrm{Pe} < 1$ transport is dominated by diffusion. For the length scale $L_p$ we choose the approximate length of the ventricles geometry in the $x$-direction, $L_p=600 \ \mu$m. We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$. The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
\begin{equation*}
    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
\end{equation*}
and then averaging $\overline{u}$ in time over one cardiac cycle to obtain $\overline{U}=1.41 \ \mu$m/s. This yields the three Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.

\subsection*{Comparing experimental and computational results}
Transport of photoconverted proteins was quantified by the relative change in fluorescence intensity $\Delta F=(F(t)-F_0)/F_0$ over time~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}). The solid lines are the mean values of $\Delta F$ for the fish cohort, with shaded regions covering one standard deviation. The first region of interest (ROI 1) is the laser-targeted region. We remind the reader that the fluorescence intensity change $\Delta F$ is scaled by the maximum fluorescence intensity $F_0$ in ROI 1 to ease comparison of the profiles.

Qualitatively, the fluorescence intensity change in region one resembles intensity dynamics observed in previous experiments studying the photoconversion properties of Dendra2 fluorescent proteins~\cite{Makarov2014Steady-stateDendra2}. The transport to the other regions can be separated into two groups: the fluorescence intensity change $\Delta F$ for ROIs 2--4 in the middle ventricle are all similar, whereas the more distal regions ROI 5 and 6 (anterior and posterior ventricle, respectively) exhibit a slower increase in $F$. In ROIs 2--4, the $\Delta F$ curves are concave, similar to ROI 1, while in ROIs 5 and 6 the curves are convex. Although the fluorescence intensity increases throughout all of the experiments, the maximum $\Delta F$ is not necessarily attained at the final time of the experiments, mostly due to signal noise. At the final time, the mean fluoresence intensities in regions 2--4 all exceed 60\% (63\%, 71\%, 67\%, respectively) of the final value $F_0$ in ROI 1, wheras ROIs 5 and 6 reach mean values of 29\% and 18\%, respectively.

% Final Delta F values
%0.6322650156762044 ROI 2
%0.7059449124175479 ROI 3
%0.6694500367160006 ROI 4
%0.28986700094045437 ROI 5
%0.18155055624229066 ROI 6

The experimental photoconversion procedure was simulated by solving the advection-diffusion equation with the diffusion coefficient of Dendra2 ($D_3$). We quantify the transport with the time evolution of the mean concentration $\overline{c}$ in transport simulations~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}). Imposing the concentration in ROI 1 mimics the fluorescence intensity change $\Delta F$ in ROI 1. Since the initial condition of the simulation is a mean concentration of zero, the mean concentration $\overline{c}$ can be interpreted as the change in mean concentration and is thus a similar metric to $\Delta F$.

Comparing the simulation results with experimental results, transport dynamics of regions 2--6 are faster in the simulation. We observe higher final values of $\overline{c}$ compared to the final values of $\Delta F$ in the experiments. In simulations, the three $\overline{c}$ profiles of ROIs 2--4 behave similar as the $\Delta F$ profiles in these regions, although the orders of ROI 3 and 4 are opposite in the simulations as compared to the experiments. For all regions, the maximum mean concentration is attained at the final time of the simulations. The final value of $\overline{c}$ in regions 2--4 were 0.76, 0.72 and 0.82, respectively. As in the experiments, the transport to regions 5 and 6 is slower than the transport to the middle ventricle sites, even though the final values of $\overline{c}$ are higher than those of $\Delta F$. The anterior ventricle (region 5) has a final $\overline{c}$ value of 0.56, while in the posterior ventricle (region 6) the final value is 0.35. Qualitatively, the $\overline{c}$ profile in the posterior ventricle compares with $\Delta F$ in this region, displaying a convex curve that has an approximately linear increase after an initial nonlinear increase. The anterior ventricle (region 5), on other hand, has an S-shaped $\overline{c}$ curve in the simulations, which differs from the linear $\Delta F$ curve in the experiments. 
% Final mean c values ROIs 2-6: 0.7637806  0.72025859 0.81903216 0.56204164 0.34926411
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time in each region of interest (ROI) observed during experiments of photoconversion of Dendra2 proteins in ROI 1. \textbf{b.} Mean concentration $\overline{c}$ as function of time in each ROI in a simulation of Dendra2 protein transport with the diffusion coefficient $D_3$. \textbf{c.} Time to $\Delta F$ reaches a threshold value of 0.25 in one of the animals of the dataset presented in panel \textbf{a}. \textbf{d.} Time to $\overline{c}$ reaches a threshold value of 0.25 for a transport simulation with diffusion coefficient $D_3$.}
    \label{fig:figure3_compare_exp_and_sim_control}
\end{figure}

To further quantify the spatial differences of changes in fluorescence intensity and concentration, we determined the time $\hat{t}$ to exceed a threshold value of 0.25~(\cref{fig:figure3_compare_exp_and_sim_control}, panels \textbf{c} and \textbf{d}). For the fluorescence intensity change $\Delta F$, we determined this time-to-threshold for the same downsampled dataset that was used to calculate $\Delta F$. In the simulations, we determined the time to reach the threshold value in each degree of freedom of the concentration finite element function. In~\cref{fig:figure3_compare_exp_and_sim_control}, we have excluded the posterior-most regions of the geometries, as the values of $\Delta F$ and $c$ never reached the threshold value of 0.25 in these regions.

\subsection*{Absence of ciliary motion affects local protein distribution}
We compare the time evolution of fluorescence intensity in control and \emph{schmalhans}~(\emph{smh}) mutant zebrafish, plotting the means of $\Delta F$ across the cohorts, shaded with one standard deviation regions~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{a}). Additionally, we determined the time needed to reach a threshold fluorescent intensity change in each region of interest (ROI) for each fish~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{b}). It is important to note that this threshold was set differently for two groups of regions: the threshold value was set to 0.25 for ROIs 1--4, whereas for ROIs 5 and 6 the threshold value was 0.10. This choice was made because of the slower dynamics of ROIs 5 and 6. The individual data points of the times to threshold are presented together with the distributions and the means. Based on the times to reach a threshold value of $\Delta F$, we test the null hypothesis that the control and mutant photoconversion data are from the same population (or equivalently, have equal distributions). We report the $p$-value for this hypothesis calculated with a two-sided Mann-Whitney U test that included a continuity correction, with a confidence level of 95\%.

In ROI 2, there is a statistically significant slower fluorescence intensity increase in the \emph{smh} mutant fish compared to controls~(\cref{fig:figure4_compare_control_mutant}). Compared to the control dataset, the mean time-to-threshold in ROI 2 is 45\% higher for the mutant dataset. In the other ROIs, the differences in the experimental results for the controls and the mutants are not significantly different. We note that, both within the control and within the mutant dataset, there are considerable individual differences in the times to reach the threshold.

To simulate protein transport in mutant fish, we used flow model II (only cardiac motion as flow mechanism, no cilia) to model the ciliary dysfunction of the \emph{smh} mutants. We visualize the time evolution of the mean concentration in each ROI for both model II and the baseline model (model 0), in addition to a similar time-to-threshold as computed for the experimental data~(\cref{fig:figure4_compare_control_mutant}, panel~\textbf{c}). As for the experiments, we use a threshold value of $0.25$ in regions 2-4 and a value of $0.10$ for regions 5 and 6. For ROI 2, we observe the same dynamics in simulations as in experiments: there is a slower increase in mean concentration in ROI 2 compared to the baseline model. The difference is even greater for the simulations, with the time-to-threshold in ROI 2 for model II 90\% higher than for model 0. Additionally, ROIs 4 and 5 exhibit very different $\overline{c}$ profiles. The difference is less significant for ROI 3, and for the posterior ventricle (region 6) the profiles are very similar. 
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
    \caption{\textbf{a.} Relative change in fluorescence intensity $F$ over time in each region of interest (ROI) for control (black lines) and \emph{smh} mutant (red lines) fish. 
    \textbf{b.} Times when $\Delta F$ first exceeds a threshold value, equal to 0.25 (ROIs 2-4) or 0.10 (ROIs 5, 6), for control (gray dots) and \emph{smh} mutant (red dots) fish. The thick black lines denote mean values of the datasets, and $p$-values were calculated using a Mann-Whitney U test with a confidence level of 95\%.
    \textbf{c.} Mean concentration $\overline{c}$ as function of time in each ROI, simulated using the baseline model (black lines) and the cardiac-only model (red lines). The horizontal gray lines mark the threshold value $\hat{c}$, and the time $\hat{t}$ when the threshold is first exceeded is reported in the plot legends. Note that in both panels \textbf{a} and \textbf{c}, the vertical axes have different limits in each plot.}
    \label{fig:figure4_compare_control_mutant}
\end{figure}

\subsection*{Loss of cilia can slow down transport}
To simulate the pathology of region-specific cilia absence, we consider three scenarios where we modify the boundary conditions of the cerebrospinal fluid (CSF) flow model. The cilia tangential stress boundary condition for the boundary where we remove cilia is changed to a free-slip boundary condition, which prescribes zero tangential forces representing cilia motion in the region considered. We consider removal of cilia in the three separate cilia-covered regions of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle, and the ventral part of the diencephalic ventricle~(\cref{fig:figure5_compare_cilia_modifications}, panel \textbf{a}). For the three scenarios, we simulate CSF flow modeled by the Stokes equations with the modified boundary conditions, and use the resulting velocity field in transport simulations of Dendra2. The maximum velocity observed in the simulations when removing telencephalic, ventral diencephalic and dorsal diencephalic cilia were, respectively, 27.7 $\mu$m/s, 27.2 $\mu$m/s, and 8.0 $\mu$m/s. We remind the reader that the maximum velocity observed for the baseline model was 27.7 $\mu$m/s.

Upon removal of telencephalic cilia, the evolution of the mean concentration $\overline{c}$ with time is essentially unaltered~(\cref{fig:figure5_compare_cilia_modifications}, panel \textbf{b}). Without ventral cilia in the diencephalic ventricle, $\overline{c}$ increases slightly slower in region of interest (ROI) 3 compared to the baseline model. Furthermore, there is a higher mean concentration in the anterior ventricle (ROI 5) and a lower mean concentration in the posterior ventricle (ROI 6) in the absence of ventral cilia when comparing to the baseline model, meaning more solute has spread towards the anterior ventricle and less solute has spread towards the posterior ventricle.

Changes in the transport dynamics are most prominent when removing the dorsal cilia in the diencephalic ventricle. For this setup, all ROIs (except ROI 1, for which we impose the concentration dynamics) exhibit significant changes in the dynamics of $\overline{c}$. Compared to the baseline model results, there is a slower increase in, and lower final values of, the mean concentration in middle and anterior ventricles (ROIs 2--5). In contrast, the transport to the posterior ventricle (ROI 6) is more rapid upon removal of the dorsal diencephalic ventricle cilia. It is evident from the final values of $\overline{c}$ that there is less total mass added to the system in the absence of dorsal cilia. This is due to the lower velocities in the vicinity of ROI 1, resulting in less ability to carry away mass from the volume where the concentration is imposed.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{Caption}
    \label{fig:figure5_compare_cilia_modifications}
\end{figure}

\subsection*{Modification of ventricles geometry impacts protein distribution}
The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals. Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh. Specifically, we consider four alternative meshes: one where the connection between the anterior and middle ventricles is constricted; one where the connection between the middle and posterior ventricles is constricted; one where the middle ventricle is shrunk in the lateral direction; the combination of the above three modifications~(\cref{fig:figure6_sim_results_compare_geometries}, panel \textbf{a}). We simulate CSF flow in the modified geometries with the baseline model and use the resulting velocity field to simulate transport of Dendra2.

\lyng{Quantify in terms of percentage changes in the final mean concentration values.} Constricting the connection between the anterior and middle ventricle leads to slower transport to region of interest (ROI) 5 located in the anterior ventricle, and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry. On the other hand, constricting the connection between the middle and the posterior ventricle leads to less transport into the posterior ventricle (ROI 6), and slightly more transport towards the anterior ventricle (ROI 5). Faster transport to ROI 5 and slower transport to ROI 6 is also the case for the geometry with a shrunk middle ventricle. Additionally, for this configuration the transport towards the anterior region of the middle ventricle (ROI 3) is slowed down. For the mesh where all three ventricles are modified, we observe higher retention of solute in the middle ventricles (ROIs 2--4). Both the anterior and the posterior ventricles (ROIs 5 and 6) have a lower mean concentration, compared to the results for the original geometry.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
    \caption{Caption. \mk{MK: How do the different geoemtries compare in terms of volume, areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
    \label{fig:figure6_sim_results_compare_geometries}
\end{figure}

\cleardoublepage

%%--------------------------------------%%
%%--------------------------------------%%
%%--------------DISCUSSION--------------%%
%%--------------------------------------%%
%%--------------------------------------%%

\section*{Discussion}
We have presented a computational model of cerebrospinal fluid (CSF) flow in brain ventricles of 2 days post-fertilization (2dpf) zebrafish embryo. By imposing tangential stresses and normal traction on the CSF flow, the simulated flow fields had similar features to the flow fields observed experimentally, consisting of vortex-structured flow and pulsatile flow. The CSF flow was used to model transport of a solute by an advection-diffusion equation. Qualitatively, simulations compared well to experiments of Dendra2 fluorescent protein photoconversion. Transport in cilia-mutant fish (\emph{schmalhans} mutants) and a CSF model without cilia, was compared to control experiments and the baseline CSF model, indicating a local effect of cilia motion on protein transport. Using the computational model of flow and transport, we further studied region-specific removal of cilia and ventricles geometry modification, and how these changes affected transport.

\subsection*{The roles of diffusion and advection in transport of photoconverted proteins}
We quantify transport in terms of fluorescence intensity change $\Delta F$ (experiments) and mean concentration $\overline{c}$ (simulations) as functions of time. For both measures, we observed concave curves in some regions and convex curves in some regions, due to differing transport regimes. In experiments, regions distal to the photoconversion site showed a linear increase in $F$, probably because advection is absent in the distal regions where cilia are absent, such that diffusion is the sole mode of transport. In regions proximal to photoconversion, advection and diffusion occur simultaneously due to the presence of cilia, leading to concave profiles for $\Delta F$. The convex diffusion-only behavior was observed for transport to the posterior ventricle in the simulations, but $\overline{c}$ was concave for the anterior ventricle, opposed to the experimental results \lyng{Include some referencing to textbook solutions of the diffusion and advection equations? E.g. semi-infinite slab or boundary layer solutions.}. Based on the geometry modification study, the reason for this difference in behavior might be that the duct between the anterior and middle ventricle is inflated in our computational mesh, as a result of the dye-injection performed before imaging\lyng{Cite this?}.

In general, the mean concentration dynamics of the simulations was more rapid than the fluorescence intensity dynamics of the photoconversion experiments. This is strongly related to our definition of the photoconversion site (region of interest 1) in the simulations, and whether this corresponds well to the region used in experiments, since the volume of the region used in the simulations determines the total amount of solute. In addition to this alignment of the computational and experimental region of interest definition being hard to quantify, another reason for discrepancy in the results could be the fact that the brain ventricles are permeable, such that some Dendra2 diffuses out of the brain ventricles in the experiments. An assay has shown that the neuroepithelium lining the walls of brain ventricles in embryonic zebrafish 24 hours post-fertilization is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}. Dendra2 are almost 26 kDa in size~\cite{Gurskaya2006EngineeringLight}, and are thus under this reported limit. If this permeability is also the case for 2 days post-fertilization zebrafish embryo ventricles, this could explain why the dynamics appear to be slower in the experiments.

Transport of Dendra2 fluorescent protein appears to be a balance of advection and diffusion. Advection is the strongest transport mechanism on a global scale (global Péclet number 7.4), but for shorter distances diffusion is balancing out advection. Simulating transport of larger molecules (thus with smaller diffusion coefficients) showed an increased importance of the role of advection. For the smallest diffusion coefficient used ($D_1$), which represented 200 nm exosomes, there was essentially zero solute in the posterior ventricle at the final simulation time (around 850 s). This is consistent with the statement above that transport to the posterior ventricle from the middle ventricle is driven by diffusion, based on estimated transport times of diffusion and advection: For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance of $L=200$ $\mu$m is approximately 24500 s. Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen on a timescale of the order of $t_a=L/\overline{U}=141$ s. Comparing this with the minuscule values of $\overline{c}$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection played a role in transporting solute from the photoconversion site in the middle ventricle to the posterior ventricle, values of $\overline{c}$ in the posterior ventricle would be higher than those observed.

The changes in the times to threshold when changing $D$ are greatest for regions of interest (ROIs) 4--6, further indicating that, relative to advection, diffusion has a greater impact in these regions than compared to regions 1--3. In region of interest 2 (anterior, dorsal region of the middle ventricle), the time to threshold is lower for $D_2$ than $D_3$. This is probably a result of less solute diffusing away from ROI 1 for $D_2$ than for $D_3$, meaning that more solute can be transported by advection along the ciliated walls of the ventricles towards ROI 2. We also note that, for regions of interest 3 and 4, the order of the $\Delta F$ and $\overline{c}$ profiles are opposite. This can be related to the difference in the exact location of ROIs 3 and 4 in simulations and experiments.

\subsection*{Simulation studies: modifying cilia and geometry}
We studied the impacts of removing cilia in specific regions of our model. Removing the dorsal cilia has a strong impact on the resulting CSF flow field and the solute transport quantified by the mean concentration of solute. We observed that the maximum velocity in the ventricles decreased roughly by a factor of three from 27.7 $\mu$m/s to 8.0 $\mu$m/s. The impactful changes to the flow field is because the total force applied on the dorsal cilia boundary is great in magnitude, providing important contribution to establishing the CSF flow structures. With weaker flow in the dorsal region of the middle ventricle, there is less advective transport. Also, the weaker dorsal flow leads to less total mass added to the system, since there is less spreading out of the concentration imposed in region of interest number one. \lyng{Quantify this?}

Absence of ventral cilia in the middle ventricle did not greatly impact flow dynamics and transport, but lead to slightly less transport towards the posterior ventricle, and slightly more transport towards the anterior ventricle. This is because the ventral cilia help establish flow towards the posterior ventricles. Removing the cilia in the anterior ventricle leaves the transport results virtually unaltered, although the CSF flow vortex structure in the anterior ventricle vanishes. This would then probably have a greater impact for smaller diffusion coefficients, as it is evident in~\cref{fig:figure2_compare_diffusion_coefficients} that transport with $D_1$ is mainly advective.
\lyng{Compare numerical results with transport results in Figure 7 in Olstad et al.}

Modifying the ventricular geometry had varying impact. Both when (separately) shrinking the connection between the fore- and mid-brain and the mid- and hind-brain, we observe a slight increase in the mean concentration $\overline{c}$ of regions of interests 2--4. In regions 5 and 6, we observe a decrease in $\overline{c}$ in the region that we shrink the connection from the middle ventricle to. Meanwhile, the other region has an increase in $\overline{c}$, a result of mass conservation.

When shrinking the middle ventricle, the mean concentration decreases in regions 2--4 of the middle ventricle. The effect on $\overline{c}$ in regions 5 and 6 is similar to when the mid-hind connection is shrunk: less solute is transported towards the hind-brain and more solute is transported towards the fore-brain. Combining all three geometry modifications, we see an increase in $\overline{c}$ in regions 2--4. Now, there is an decrease in both region 5 and 6, which is more similar to the experimental $\Delta F$ curves (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}) in these regions compared to the simulated $\overline{c}$ on the standard geometry (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}). This is in line with the expectation that shrinking the geometry is closer to replicating the geometries of the fish used in experiments, because the ventricular geometry is inflated by the injection procedure performed during image segmentation.

\lyng{Discuss cilia serving as an "enhanced mixing factor" on small scales, refer to Kurtcuoglu et al. and other paper that studied this in human brain ventricles.}
\lyng{Include a discussion of what happened when Kurtcuoglu et al. and the other paper removed cilia.}

\subsection*{Computational model assumptions and boundary conditions}
To model flow of cerebrospinal fluid, we employed slip boundary conditions at the ventricular walls, contrasting the classical choice of a noslip boundary condition. The use of slip boundary conditions is motivated by experimental observations of the flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}. It has been observed that the fluid velocity increases towards the wall. Using slip boundary conditions allows for this behavior while avoiding the need to resolve a boundary layer near the ventricle walls, which would arise with a noslip boundary condition. \lyng{HH: Remove noslip comment?} A couple of previous continuum model simulation studies~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal} have modeled cilia as body forces. We chose to model the cilia as a force exerted tangentially on the boundary as this fits well in the slip boundary condition framework, while at the same time being a good representation of the real nature of cilia, since they are in reality microscale structures confined to the ventricular walls that generate flow through collective motion.

In our CSF flow model, the ciliated boundaries are homogeneous, whereas in reality, cilia populate the ventricle walls in a heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneous spatial arrangement of cilia, both in location and beating direction, has been shown to enhance particle clearance in airway cilia arrays in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}. Incorporating spatial arrangement heterogeneity in our model could possibly result in different transport timescales, but we would not expect notable changes to the general trends of the macroscopic transport that we study here, since the effects of introducing heterogeneous spacing of cilia would alter the magnitude of cilia forces, but not their direction. On the other hand, introducing more heterogeneous beating directionality could alter both the transport timescales and directionality. Our model has all of the cilia tangential traction aligned, and more heterogeneity in this alignment as a result of heterogeneity in the beating directionality would presumably affect both magnitude and directionality of advective transport. Previous studies have demonstrated that changes to beating directionality affects transport, and that specific coordination of the ciliary beating is e.g. crucial to maintain healthy functioning of mucous transport in airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction, Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet}, and important in nodal flow~\cite{}. Although these studies were mostly on spatial scales resolving individual cilia, we could envision the same effects in our continuum model, similar to the results of previous numerical studies~\cite{Ramirez-SanJuan2020Multi-scaleArrays, Thouvenin2020OriginCanal}.

The handling of the influx and the outflux in the advection-diffusion equation merits discussion. We handle the outflux by leaving the advective flux term as an unknown in the weak formulation of the advection-diffusion equation. This has been referred to with different names in previous works, names such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition}, the ``no boundary condition"~\cite{Griffiths1997TheCondition}, and the ``consistent flux boundary condition"~\cite{Lynch2020NumericalHemodynamics}. In leaving the advective flux term in the weak form we are lacking a boundary condition, so the approach seems problematic in the continuous sense of the problem. However, the discrete problem is well-posed, because the approach represents constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}. Attempting to conserve the total solute mass inside the ventricles, we applied an approximate periodic boundary condition to the inflow boundary, by setting the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous timestep $n-1$. This is expected to be of low-order accuracy, and for high Péclet numbers, the boundary condition affects the concentration field in the vicinity of the in- and outflow boundaries due to large advective fluxes. For the simulation scenarios we considered, both in terms of model parameters and time span, the photoconversion region where solute is added to the system is far enough away from the in- and outflow boundaries that the flux boundary condition we impose does not significantly impact the results. Nevertheless, we deliberately excluded the space proximal to in- and outflow boundaries in the anterior and posterior regions of interest (5 and 6) to limit adverse effects.

A possible improvement to the in- and outflow boundary conditions we employed would be to consider a 3D-0D coupling of the in- and outflow boundaries using ordinary differential equations, similar to what has been done in cardiac modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}. However, if the ventricular system in reality is a closed system, one should rather seek out a way of modeling the CSF flow without open boundaries to avoid handling in- and outflow boundary conditions. A more appropriate way of handling the beating cardiac motion could be to impose a ventricular wall deformation, which in turn would induce CSF flow whilst enforcing the impermeability condition $\uu\cdot\nn=0$ on all of the ventricular walls. Such wall-motion induced CSF flow has been modeled and simulated in the human brain ventricular system~\cite{Causemann2022HumanFramework, Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.

\subsection*{Estimation of computational model parameters}
We estimated the values of the diffusion coefficients used in this study. The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$ is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the values $D_2$ and $D_1$ were extrapolated based on experimental data~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells, Mahmood2023ExosomeTemperature} using the Stokes-Einstein relation~\cite{Einstein1905UberTeilchen}~(\cref{eq:D_stokes_einstein}). This extrapolation assumes the diffusing substance is of spherical shape, which proteins are not, and the relation does not necessarily hold in CSF. Consequently, there is uncertainty in the values used. We note that Sadovsky~\emph{et al.}~\cite{GuraSadovsky2017MeasurementExpansion} reported that Dendra2 satisfies the Stokes-Einstein in the solution they used, a solution which had similar viscosity to water. We used CSF density and viscosity values measured in humans~\cite{Bloomfield1998EffectsFluid}, and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances, the CSF in which photoconverted Dendra2 are transport in our experiments may be more viscous than what we consider. This would reduce the diffusion coefficient~(cf.~\cref{eq:D_stokes_einstein}), but based on reports of protein concentration having a limited impact on the viscosity of CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}, this reduction is presumably limited. Merely the presence of other proteins and nutrients may also reduce the diffusion coefficient by reduction of the mean-free path lengths. Considering the diffusion coefficients $D_1$ and $D_2$ both smaller than $D_3$ in our transport analysis provides information about how the simulation results of Dendra2 transport would be altered if the diffusion coefficient $D_3$ is overestimated.

We heuristically determined the parameter $\tau = \num{6.5e-4}$ Pa, which determines the magnitude of the cilia tangential traction boundary conditions. The maximum force applied was in the dorsal region of the middle ventricle, where the posterior region had a tangential traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = \num{2.5e-3}$ Pa applied to the boundary. A couple of previous simulation studies of cilia-mediated flow in brain ventricles have used a volumetric force density to represent the cilia. Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles} used a force expression that increased linearly from the wall to a maximum force density of $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 $\mu$m away from the wall, which represented cilium length. If we assumed our cilia array to have the same thickness of $l = 15$ $\mu$m, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$ would correspond to a maximum force density of 
\begin{equation*}
    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{l} = \frac{\num{2.5e-3} \ \mathrm{Pa}}{15 \ \mu\mathrm{m}} = 169 \ \mathrm{N/m^3},
\end{equation*}
which smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude. The length 15 $\mu m$ is the typical length of cilia in human brain ventricles~\cite{Afzelius2004Cilia-relatedDiseases}, while in zebrafish they are closer to 5 $\mu$m~\cite{Salman2022ComputationalEmbryo}. With $l=5$ $\mu$m, our traction parameter corresponds to a maximum force density of $f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ used by Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}. We note that they based $f_{\mathrm{max}}$ on reconstructions of flow velocities in murine brain ventricles.

Another study that used a force density to model ciliary motion is Thouvenin~\emph{et al.}~\cite{Thouvenin2020OriginCanal}, where two-dimensional flow in the central canal of zebrafish embryos was modeled using a cilia force density of 4000 N/$\mathrm{m^2}$. The resulting numerical velocity fields matched well with \emph{in vivo} measurements, where the maximum velocity was around 5 $\mu$m/s (recall that we observed a maximum of 27.7 $\mu$m/s in the present study). The geometry they studied resembles a pipe, probably offering more flow resistance than the open geometry considered in our work, which may be why they needed a larger force density to accurately represent experimental results. In any case, it is interesting to note that our and these two previous studies have estimated cilia force densities that only differ by one order of magnitude.

\subsection*{Numerical approximation and convergence rates}
The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employ for the Stokes equations is computationally more expensive than a more conventional approach based on e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem} ($\mathbb{P}_2-\mathbb{P}_1$ elements) or lower-order enriched elements~\cite{Brezzi2011MixedMethods}, such as the mini-element ($\mathbb{P}_1-\mathbb{P}_1$ with a velocity stabilization). Here, $\mathbb{P}_k$ is the set of continuous Lagrange polynomials of order $k$. We opted for the BDM-DG scheme because of its exactly-mass-conserving property, since numerical experiments proved that a divergence-free velocity field was  paramount to attain a stable discretization of the advection-diffusion equation in advection-dominated regions. Preliminary attempts using Taylor-Hood elements proved hard to achieve stable transport results with a reasonable computational mesh size. Stability either required excessive mesh refinement and/or problem-specific tuning of hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization method~\cite{Franca1992StabilizedModel}. Probing numerical values of the divergence of the velocity when using Taylor-Hood elements revealed that, on the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was in the order of $10^{-6}$, while the maximum value of the divergence of the velocity was of order unity. This is a result of the fact that incompressibility is only achieved in a distributional sense when employing Taylor-Hood elements. On a refined mesh with roughly six times as many computational cells as the standard mesh, the numerical values of $\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still of the same orders as reported for the standard mesh. This may lead to the hyperbolic advective term in the advection-diffusion equation accumulating errors that grow unstable.

In addition to its favorable mass-conserving property, the BDM-DG scheme lets us impose the impermeability condition strongly, and the tangential traction boundary condition weakly, without any tailored approach, since these boundary conditions appear naturally in the weak form of the Stokes equations~(\cref{subsec:appendixA1}). If instead e.g. Taylor-Hood elements were to be used, the impermeability boundary condition must be handled with for example a Nitsche method~\cite{Nitsche1971UberSind} or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers, Bertoluzza2017BoundaryHemodynamics}.

%The error norms used to calculate the convergence rates that we report are not the ones naturally appearing in \emph{a priori} error estimates of a $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ discretization. Therefore, we cannot say anything explicit about expected convergence rates. However, the polynomial order $k$ of the elements provide an upper bound on the convergence rate, with the expectation that the $L^2$ error norm convergence rates should not exceed $k+1$. We observe convergence rates approaching $k+1$ and $k$ for the $\uu$ and $p$ error norms in $L^2$, when using polynomial orders $k$ and $k-1$, respectively.

\emph{A priori} error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
derived in a mesh-dependent broken $H^1$-norm for $\uu$ and the $L^2$-norm for the pressure. The respective 
errors are expected to decay with order $k$, see for example Cockburn~\emph{et al.}~\cite{Cockburn2005AEquations}. For the sake of simplicity,~\Cref{tab:cylinder_error_rates} reports the velocity errors in the standard $H^1$ norm. Using polynomial degree  
$k=1$, we observe linear convergence in both the velocity and the pressure.   
\mk{MK: I see 1.5 in the table for $\uu$ in $L^2$?} \lyng{HH: Yes, while the $H^1$ error decays linearly, isn't this in line with expectations? Could be more specific: "Using polynomial degree 
$k=1$, we observe linear convergence in both the velocity $H^1$ error and the pressure $L^2$ error."}

\lyng{HH: Add a paragraph discussing the advection-diffusion equation discretization with DG elements?}

\subsection*{The role of cilia in the brain ventricles}
Based on the observations made by Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}, it is clear that cilia are paramount for establishing healthy CSF flow patterns in embryonic zebrafish ventricles. However, our results indicate that when it comes to transport of small proteins, diffusion alone can do a lot of the work. This is because the embryonic zebrafish brain ventricles are very small. The same conclusion could not be drawn for larger animals, e.g. mice, rats, humans. \lyng{Refer to and discuss some previous works there, e.g. Faubel, Eichele etc.}

%Whether the zebrafish brain ventricles are a closed or open system at the embryonic developmental stage of two days post-fertilization is still an open question. According to Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}, despite the directional CSF flow generated by the motile cilia and the pulsatile displacement by the heartbeat, they did not observe any net CSF flow across the brain ventricles. Considering our results of modeling pulsatile flow with the brain ventricles as open (with normal pressure boundary conditions, model version IIa) or closed (domain movement, model version IIb), does it seem more likely that the ventricles are closed or open?

The observation that hydrocephalus is more prevalent in mouse mutants than humans with primary ciliary dyskinesia suggests that the size of the ventricular system or the genetic disparity between species may account for the sensitivity of each species to hydrocephalus~\cite{Olstad2019CiliaryDevelopment}. Previous modeling work of CSF flow in human brain ventricles suggests that motile ciliary beating contributes specifically to the near-wall flow, while blood vessel pulsations, respiration and CSF secretion combine to generate a pulsatile bulk flow~\cite{Siyahhan2014FlowVentricles}. Cilia thus probably play an important role in regulating the amount of substances close to the ventricular wall, similar to coral reefs, where it has been observed that cilia are primary regulators of oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}. But for zebrafish embryos, the ventricles are so small that the flow generated by ciliary motion is of the scale of the geometry, and thus not only contributes to near-wall flow dynamics, but the whole ventricular system.

\lyng{HH: Refer to Eichele et al. article discussion about role of cilia.}

%Yet, according to Olstad~\emph{et al.}, the distribution of CSF is strongly influenced by bodily movement that eliminates the stringent boundaries of the ventricular cavities. Accounting for such bodily movement could be a next step.

%Olstad \textit{et al.}\cite{Olstad2019CiliaryDevelopment} observed that bodily movement influenced ventricular flow. We do not account for body movement in this work.

\subsection*{Limitations and further work}
The model presented has certain limitations. Future work could consider spatial heterogeneity of the cilia, and how this affects flow and transport. Results from modeling pulsatile flow indicate that deformation of the ventricles due to cardiac motion might be the underlying mechanism of the pulsatile flow observed in experiments. Modeling deformation of the ventricles and investigating how the arising flow compares with pulsatile flow observed in experiments could be an interesting next step.

\section*{Conclusion}
We have presented a numerical model of flow and transport in zebrafish brain ventricles based on finite element methods. A realistic brain ventricles geometry from medical imaging was used to perform a computational study with the presented model. The flow model reproduces qualitatively the experimentally observed flow features of cilia-mediated cerebrospinal fluid (CSF) flow in zebrafish brain ventricles. With the transport model coupled to the flow equations, we estimated how slowly or rapidly different molecules are transported in the ventricles. In line with experimental observations, the transport times to the posterior ventricles are significant because of the absence of cilia in this region. In the anterior and middle ventricles the transport is advection-dominated due to the CSF flow generated by the cilia, resulting in rapid transport of molecules.

%%--------------ACKNOWLEDGMENTS--------------%%
\section*{Acknowledgments}
Halvor Herlyng acknowledges support from the national infrastructure for computational science in Norway, Sigma2, via grant \#NN8049K. Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
\newpage

%%--------------APPENDIX--------------%%
\appendix
\section{Supplementary Theory}
\subsection{Weak Formulation of the Stokes Equations}\label{subsec:appendixA1}
We consider the time-dependent Stokes equations
\begin{subequations}
\begin{alignat}{2}
   \rho\pdifft{\uu} - \nabla \cdot \bsig(\uu, p) &= \mathbf{0} \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_mom}\\
  \nabla \cdot \uu &= 0 \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_div} 
\end{alignat}
\label{eq:appendix_stokes_eqs}% 
\end{subequations}%
in the domain $\Omega$ with boundary $\Gamma$, where $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ is the viscous stress tensor, in which $\beps(\uu) = \frac{1}{2}(\nabla\uu + (\nabla\uu)^T)$ is the symmetric gradient. Furthermore, $\uu\in\VV$ is the fluid velocity and $p\in Q$ is the fluid pressure, and $\rho$ and $\mu$ are the fluid density and dynamic viscosity, respectively. Unless otherwise stated, we let $\bsig = \bsig(\uu, p)$.

We will consider the function spaces $\VV$ and $Q$ based on the Sobolev spaces $\mathbf{H}^1(\mathrm{div}; \Omega)$ and $L^2(\Omega)$, respectively, defined as 
\begin{align*}
    L^2(\Omega) &= \bigg\{p \ : \ \intO{p^2} < \infty\bigg\} \\
    \mathbf{H}^1(\mathrm{div}; \Omega) &= \bigg\{\uu \ : \ \uu\in\mathbf{L}^2(\Omega), \nabla\cdot\uu\in L^2(\Omega)\bigg\}.
\end{align*}
Bold-faced characters for a space denotes a $d$--dimensional vector space, where $d$ is the spatial dimension of $\Omega$. For example, $\mathbf{H}^1(\Omega) = [H^1(\Omega)]^3$ if $\Omega$ is three-dimensional. We will consider $p\in Q=L^2_0(\Omega)$, with subscript 0 meaning that $\intO{p} = 0$, and $\uu\in\VV$ with
\begin{equation*}
    \VV =  \bigg\{\vv \ : \ \vv\in\mathbf{H}^1(\mathrm{div}; \Omega), \vv\cdot\nn=0 \ \mathrm{on} \ \Gamma\setminus\Gamma_{\mathrm{io}}\bigg\}.
\end{equation*}
Here $\Gamma_{\mathrm{io}}$ denotes an in- or outflow boundary.

\mk{
You should be careful here. The H(div) functions do not have a well defined gradient (and in turn $\varepsilon$). However, for the derivations of the continuous problem you don't need H(div). I would derive all the weak forms in $V = \left\{ v\in H^1, v\cdot n = \text{on} \Gamma\right\}$. Then in A.2 you say we chose spaces $V_h$ which are are not conforming, i.e. it does not hold that $V_h\subset V$. Instead you have $V_h\subset H(div)$. Reasons is better mass csrv and as a bonus the bcs can be enforced strongly. Note that H(div) functions can have jumps in tangential components on surfaces in $\Omega$. Then introduce the discrete weak form.  
}
To derive a weak formulation of the Stokes equations~\eqref{eq:appendix_stokes_eqs}, we begin by multiplying~\eqref{eq:BDM_stokes_mom} with a test function $\vv\in\VV$ and integrating over the domain:
\begin{equation*}
    \intO{\rho\pdifft{\uu}\cdot\vv} - \intO{(\nabla\cdot\bsig)\cdot\vv} = \mathbf{0}.
\end{equation*}
Performing integration by parts of the stress term and applying Green's first identity, we get
\begin{equation}
    \intO{\rho\pdifft{\uu}\cdot\vv} - \intG{\bsig\nn\cdot\vv} + \intO{2\mu\beps(\uu) : \beps(\vv)} - \intO{p\nabla\cdot\vv} = \mathbf{0}, \label{eq:modelA_weak_form1}
\end{equation}
where the symbol : signifies the matrix inner product, $A:B=\text{trace}{(A^TB)}$ for matrices $A, B\in\mathbb{R}^{d\times d}$.

Further steps depend on the boundary conditions applied, which is different for the three model versions we consider. Before going through the different model versions, let us introduce some notation used in defining slip boundary conditions. We make use of a decomposition
of any vector $\vv$ on the boundary $\Gamma$ into its normal and tangential components,
$\vv = \vv_{\perp} + \vv_{\parallel}$, where $\vv_{\perp}=(\vv\cdot\nn)\nn$ and
$\vv_{\parallel}=P_{\nn}(\vv)$. The tangential projection is defined as
\begin{equation}
    P_{\nn}(\vv) = (\mathbf{I} - \nn\otimes\nn)\vv,
    \label{eq:projection_operator_appendix}
\end{equation}
where $\nn$ is the outer unit normal of the surface. Introducing $\hat{\bsig} = \bsig\nn$ for the traction (vector), the forcing due to cilia is represented by constraining $\bsigpar$ on the part of the boundary populated by cilia. In particular, we let $\bsigpar = \btau(\xx, \rr) = \tau\lambda(\xx) P_{\nn}(\rr)$, where the parameter $\tau=\num{6.5e-4}$ Pa was used to control the magnitude of the tangential stresses, and chosen by calibrating simulated velocity fields with experimental data~\cite{Olstad2019CiliaryDevelopment}. The details of the function $\lambda(\xx)$ follow subsequent to deriving the weak form.

We choose $\mathbf{r} = \rr^+ = (1, 0, 1)$ or $\mathbf{r} = \rr^- = -(1, 0, 1)$ to impose forces perpendicular to the $y$-axis. The reason for this is that all of the experimental images we compare with are taken in the $xz$-plane, rendering flow features in the $y$-direction unobservable. Next, we consider the way of handling the stress boundary integral for each model version.

%Note, however, that $\tau$ is not equivalent to the magnitude of $\btau$, since the projection operator~\eqref{eq:projection_operator_appendix} does not necessarily yield a unit vector for an arbitrary vector $\vv$.

\textbf{Model Version I.} This model version has cilia forces as the only mechanism driving flow. We consider the Stokes equations~\eqref{eq:appendix_stokes_eqs} with the slip boundary conditions
\begin{subequations}
    \begin{alignat}{2}
        \uu\cdot\nn &= 0 \quad &&\mathrm{on} \ \Gamma=\Gc\cup\Gs, \label{eq:modelA_slip_BC_impermeability} \\
        %\hat{\sigma} - (\hat{\sigma}\cdot\nn)\nn &= \tau P_{\nn}(\rr) \quad &&\mathrm{on} \ \Gamma_s,
        \bsigpar &= \btau \quad &&\mathrm{on} \ \Gc,
        \label{eq:modelA_slip_BC_shear} \\
        \bsigpar &= \mathbf{0} \quad &&\mathrm{on} \ \Gs,\label{eq:modelA_full_slip_BC}
    \end{alignat}\label{eq:modelA_slip_BC}%
\end{subequations}%
on the boundary $\Gamma=\Gamma_c\cup\Gamma_s$. The boundary $\Gamma_s$ is a free-slip boundary, where we impose the free-slip condition~\eqref{eq:modelA_full_slip_BC}. The first condition~\eqref{eq:modelA_slip_BC_impermeability} is the impermeability condition, enforcing no flow normal to the boundary, whereas~\eqref{eq:modelA_slip_BC_shear} imposes a stress tangential to the boundary. These tangential stresses are applied to represent the forces that the collective cilia motion exerts on the cerebrospinal fluid.

The boundary conditions~\eqref{eq:modelA_slip_BC} are set weakly through the stress boundary integral 
\begin{equation}
    \intG{\bsig\nn\cdot\vv} =  \intG{\hat{\bsig}\cdot\vv}
    \label{eq:boundary_integral_BC1}
\end{equation}
in the weak form~\eqref{eq:modelA_weak_form1} of the Stokes equations. We decompose the traction vector $\hat{\bsig}$ into a normal and tangential component:
\begin{equation*}
    \hat{\bsig} = \bsigperp + \bsigpar
\end{equation*}
Inserting the above into~\eqref{eq:boundary_integral_BC1}, combined with application of the tangential traction condition~\eqref{eq:modelA_slip_BC_shear} and the free-slip condition~\eqref{eq:modelA_full_slip_BC}, yields
\begin{equation}
    \intG{\hat{\bsig}\cdot\vv} = \int_{\Gc\cup\Gs}{(\bsigperp + \bsigpar)\cdot\vv}\, ds = 
    \int_{\Gc\cup\Gs}{\bsigperp\cdot\vv}\, ds + \intGc{\btau\cdot\vv} = \intG{\bsigperp\cdot\vv} + \intGc{\btau\cdot\vv}.
    \label{eq:boundary_integral_BC2}
\end{equation}
The second term on the right-hand side of~\eqref{eq:boundary_integral_BC2} is moved to the right-hand side of the weak form, since $\btau$ is known. Using $\hat{\bsig}_{\perp} = (\hat{\bsig}\cdot\nn)\nn$, we can write the first term on the right-hand side of~\eqref{eq:boundary_integral_BC2} as
\begin{equation}
    \intG{\bsigperp\cdot\vv} = \intG{(\hat{\bsig}\cdot\nn)\nn\cdot\vv} = \intG{(\hat{\bsig}\cdot\nn)(\vv\cdot\nn)}.
    \label{eq:boundary_integral_BC_normal}
\end{equation}
In a later section, we will discretize the weak formulation of the Stokes equations with Brezzi-Douglas-Marini finite elements~\cite{Brezzi1985TwoProblems}. These elements are defined through integral moments of the normal component of a variable on the facets of an element, we can strongly enforce the value of $\uu\cdot\nn$ and thus the boundary condition~\eqref{eq:modelA_slip_BC_impermeability}. Consequently, the test function counterpart $\vv\cdot\nn$ vanishes on the boundary, and the term~\eqref{eq:boundary_integral_BC_normal} is therefore dropped from the weak form. As a result, for model verison I, the weak form of the momentum equation takes the following form:
\begin{equation*}
    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} - \intO{p\nabla\cdot\vv} = \intGc{\btau\cdot\vv}, \quad\forall\vv\in\VV.
\end{equation*}
Next, multiplying the continuity equation~\eqref{eq:BDM_stokes_div} with a test function $q\in Q$, we require that
\begin{equation}
    -\intO{q\nabla\cdot\uu} = 0,\quad\forall q\in Q
    \label{eq:pressure_weak_form}
\end{equation}
The full weak form of the Stokes equations for model version I is then: find $(\uu, \, p) \in \VV\times Q$, such that
\begin{subequations}
    \begin{alignat}{5}
        &\intO{\rho\pdifft{\uu}\cdot\vv} + &\intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} - &\intO{p\nabla\cdot\vv} &&= \intGc{\btau\cdot\vv}, &&\quad\forall\vv\in\VV, \label{eq:stokes_weak_mom_modelA}\\ 
        &{} &{}  -&\intO{q\nabla\cdot\uu} &&= 0, &&\quad\forall q\in Q. \label{eq:stokes_weak_cont_modelA}
    \end{alignat}%
    \label{eq:stokes_weak_modelA}%
\end{subequations}%
We observe that, in this case with slip boundary conditions on the entirety of the boundary $\Gamma$, the
vector $(\uu, p)=(\mathbf{0}, C)$ for any real constant $C$ satisfies the equations. The system~\eqref{eq:stokes_weak_modelA} is thus singular with a one-dimensional nullspace of constant pressures. \lyng{Consequently, assembly of our discretization of the  equations~\eqref{eq:stokes_weak_modelA} into a linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$. To ensure existence of solutions, we orthogonalize the right-hand side vector $\mathbf{b}$ with respect to the pressure nullspace basis (the set of all constants), before solving the linear system. To obtain a unique solution, which together with existence renders the problem well-posed, information of the pressure nullspace is passed to the linear solver.} Let us remark that the singularity is a consequence of the fact that the impermeability condition is assumed to hold on the \emph{entire} domain boundary for this model version, which leaves the pressure under-determined as a result of no boundary condition specifying the pressure.

The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia motion differ for the cilia regions. We heuristically determined $\tau$ and $\lambda(\xx)$. As noted previously, $\tau=\num{6.5e-4}$ Pa. We set $\rr = \rr^+$ and $\rr = \rr^-$ in the ventral and dorsal regions of the diencephalic ventricle, respectively. In the ventral region, we set the linear profile $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$, where $[x_{0, v}, x_{e, v}]$ is the $x$-range of the cilia region, so the stresses decrease linearly towards the posterior part of the geometry. We impose a linearly increasing profile over the $x$-range $[x_{0, d}, x_{e, d}]$ in the dorsal region: $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$. \lyng{Put all of this information on $\lambda$ choice in a table.}

In the telencephalic ventricle, we set $\rr=\rr^-$ and $\lambda=\frac{2}{5}$ in the anterior most part of the cilia region, and $\rr=\rr^+$ and $\lambda(\xx)=1$ in the posterior part.

\textbf{Model Version II.} For this model version, the only physical mechanism inducing fluid flow is the cardiac cycle. We model the influence of the cardiac cycle with a normal pressure boundary condition:
\begin{subequations}
    \begin{alignat}{2}
      \uu\cdot\nn = 0, \ \hat{\bsig}_{\parallel} &= \mathbf{0} \quad &&\mathrm{on} \ \Gs, \label{eq:modelB_slip_BC} \\
      (\mu\nabla\uu - p\mathbf{I})\nn &= \Tilde{p}(t)\nn \quad &&\mathrm{on} \ \Gp, \label{eq:modelB_pressure_BC}
    \end{alignat}%
\end{subequations}%
where the boundary $\Gamma = \Gs\cup\Gp$ consists of a free-slip boundary $\Gs$, and a part $\Gp$ where a normal traction type of boundary condition is imposed. Note, however, that the transpose velocity gradient term must be included inside the parentheses on the left-hand side of~\eqref{eq:modelB_pressure_BC} for it to be the traction $\bsig$. Since this is not the case, we rather refer to this boundary condition as a normal pressure boundary condition. The boundary $\Gs$ is handled as discussed in the previous section, such that the stress boundary integral~\eqref{eq:boundary_integral_BC1} vanishes over $\Gs$. Therefore, we now have
\begin{align}
    \intG{\hat{\bsig}\cdot\vv} = \intGp{\hat{\bsig}\cdot\vv} &= \intGp{(\mu(\nabla\uu + (\nabla\uu)^T) - p\mathbf{I})\nn\cdot\vv}\notag \\
    &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{(\mu\nabla\uu - p\mathbf{I})\nn\cdot\vv}\notag\\
    &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}
    \label{eq:modelB_boundary_integral1}
\end{align}
We leave the first term on the left-hand side of~\eqref{eq:modelB_boundary_integral1} in the weak form of the momentum equation. The second term is determined by the boundary condition~\eqref{eq:modelB_pressure_BC}, and is therefore moved to the right-hand side of the weak form. The weak form of the momentum equation for model version IIa is then
\begin{equation}
    \begin{aligned}
    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} - \intO{p\nabla\cdot\vv} &-\intGp{\mu(\nabla\uu)^T\nn\cdot\vv} \\ &=\intGp{\Tilde{p}(t)(\vv\cdot\nn)}, \quad\forall\vv\in\VV.
    \end{aligned}
    \label{eq:weak_form_mom_eq_modelB}
\end{equation}
Also considering the weak form of the continuity equation, the weak formulation for model version II then reads: find $(\uu,\, p)\in\VV\times Q$ such that~\eqref{eq:weak_form_mom_eq_modelB} and~\eqref{eq:pressure_weak_form} hold for all $(\vv, \, q)\in\VV\times Q$.
To simulate the back-and-forth motion induced by the cardiac cycle observed in previous work~\cite{Olstad2019CiliaryDevelopment}, we apply sinusoidal forcing. The boundary $\Gamma_p$ has two separate regions: one located on the anterior ventricle and one on the posterior ventricle~(\cref{fig:figure1}, panel \textbf{b}). For the normal pressure boundary condition, we set $\Tilde{p}(t) = 0$ on the anterior part and
$\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The amplitude $A$ was tuned and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.

\iffalse
\textbf{Model Version IIb.} A second approach to modeling the pulsatile flow generated by the cardiac cycle was applying a rigid motion to the geometry, and then solving for the velocity defined in the reference frame attached to the geometry. We consider an approach similar to San Mart{\'\i}n \emph{et al.}~\cite{san2009convergence}, based on the framework commonly referred to as an Arbitrary Lagrangian Eulerian formulation of the governing equations. Consider the Stokes equations 
\begin{subequations}
    \begin{alignat}{2}
        \rho\pdifft{\uu} - \nabla\cdot\bm{\sigma}(\uu, p) &= \mathbf{0}, \\
        \nabla\cdot\uu &= 0,
    \end{alignat}
    \label{eq:stokes_eqs_moving_ref}%
\end{subequations}%
in a time-dependent, moving domain $\Omega_t$, and define the coordinates $\hat{\xx} = (\hat{x}, \hat{y}, \hat{z})$ as the reference frame attached to $\Omega_t$. In $\Omega_t$, we consider the variables $\psi(\hat{\xx}, t)$, so that we have $\uu(\hat{\xx}, t)$ and $p(\hat{\xx}, t)$ in~\eqref{eq:stokes_eqs_moving_ref}. As before, we denote $\Omega$ the domain in the absolute, fixed reference frame with coordinates $\xx = (x, y, z)$ and variables $\psi(\xx, t)$. To determine the velocity inside the brain ventricles without moving the computational mesh, we can solve the Stokes equations for the velocity $\ww$ defined in the moving reference frame. This is done by first solving for $\uu$ in the fixed reference frame, whilst accounting for the mesh motion $\uuref$. Then, with $\uu$ and $\ww$ defined in separate coordinate systems that move with a velocity $\uuref$ relative to each other, the velocities are related by $\uu = \ww + \uuref$~\cite{meriam2012engineering}. After solving for $\uu$, we thus calculate $\ww = \uu - \uuref$.  To rewrite the variables in~\eqref{eq:stokes_eqs_moving_ref} into variables of $\xx$ instead of $\hat{\xx}$, nothing has to be done with the divergence operators since we consider a rigid motion, rendering spatial differentiation unchanged. The temporal derivative is not the same in the two coordinate systems, however. Differentiation with respect to time and application of the chain rule yields
\begin{equation*}
    \begin{aligned}
        \pdifft{\psi}(\hat{\xx}, t) &= \pdifft{\psi}(\xx, t) + \frac{\partial \psi}{\partial\hat{\xx}}\pdifft{\hat{\xx}} \\
        &= \pdifft{\psi}(\xx, t) + \frac{\partial \psi}{\partial\xx}\frac{\partial\xx}{\partial\hat{\xx}}\pdifft{\hat{\xx}} \\
        &= \pdifft{\psi}(\xx, t) + \frac{\partial \psi}{\partial\xx}\pdifft{\hat{\xx}}.
    \end{aligned}
\end{equation*}
The last equality follows from the fact that the motion of the moving reference frame is rigid, such that the differences in $\hat{\xx}$ and $\xx$ are only due to translation, and not dilatation, of the coordinate systems. We can recognize $\partial\hat{\xx}/\partial t = \uu_{\mathrm{ref}}$ as the velocity of the domain $\Omega_t$. Since $\partial\psi/\partial\xx = \nabla\psi$, we get
\begin{equation}
    \pdifft{\psi}(\hat{\xx}, t) = \pdifft{\psi}(\xx, t) + \uu_{\mathrm{ref}}\cdot\nabla\psi,
    \label{eq:temporal_derivative_relation}
\end{equation}
where the second term leads to the interpretation that the variable $\psi(\xx, t)$ in the fixed reference frame is advected with the velocity $\uu_{\mathrm{ref}}$ of the moving reference frame. Using the relation~\eqref{eq:temporal_derivative_relation}, we can rewrite~\eqref{eq:stokes_eqs_moving_ref} in the fixed reference frame:
\begin{subequations}
    \begin{alignat}{2}
        \rho\bigg(\pdifft{\uu} + (\uu_{\mathrm{ref}}\cdot\nabla)\uu\bigg) &= \nabla\cdot\bm{\sigma}(\uu, p), \label{eq:mom_eq_fixed}\\
        \nabla\cdot\uu &= 0,
    \end{alignat}
    \label{eq:stokes_eqs_fixed}%
\end{subequations}%
where the variables in~\eqref{eq:stokes_eqs_fixed} are variables of $\xx$ and $t$. The boundary conditions also change slightly for this formulation. Since the impermeability condition $\ww\cdot\nn=0$ is now supposed to hold in the moving reference frame, we get the boundary condition $\uu\cdot\nn = \uuref\cdot\nn$. To simulate the oscillatory motion arising from the cardiac cycle, we applied the motion $\uuref = (A_{\mathrm{ref}}\sin{\omega t}, 0, 0)$, where the amplitude $A_{\mathrm{ref}}$ was calibrated with experimental data and $\omega = 2\pi f$ was determined by the cardiac frequency $f$~\cite{Olstad2019CiliaryDevelopment}. Since the domain movement is rigid, we have $\beps(\uuref) = \mathbf{0}$, such that the stress boundary condition $P_{\nn}(\bsig(\ww, p)) = \mathbf{0}$ directly translates to $P_{\nn}(\bsig(\uu, p)) = \mathbf{0}$. Solving~\eqref{eq:stokes_eqs_fixed} with the boundary conditions $\uu\cdot\nn = \uuref\cdot\nn$ and $P_{\nn}(\bsig(\uu, p)) = \mathbf{0}$, we obtain the velocity in the moving reference frame by calculating $\ww = \uu - \uuref$.
\fi

\textbf{Model Version 0.} This model version, regarded as the baseline model, considers both cilia and cardiac beating as driving mechanisms of fluid flow. We therefore consider the boundary conditions
\begin{subequations}
    \begin{alignat}{2}
      \uu\cdot\nn = 0, \ \bsigpar &= \btau  \quad &&\mathrm{on} \ \Gc, \label{eq:slip_BC_modelC} \\
      \uu\cdot\nn = 0, \ \bsigpar &= \mathbf{0}  \quad &&\mathrm{on} \ \Gs, \label{eq:freeslip_BC_modelC} \\
      (\mu\nabla\uu - p\mathbf{I})\nn &= \Tilde{p}(t)\nn \quad &&\mathrm{on} \ \Gp, \label{eq:pressure_BC_modelC}
    \end{alignat}
\end{subequations}%
where $\Gamma = \Gc\cup\Gs\cup\Gp$ is the boundary of $\Omega$. The quantities $\btau$ and $\Tilde{p}(t)$ are as introduced in the sections on model versions I and IIa. We handle the boundary conditions~\eqref{eq:slip_BC_modelC} and~\eqref{eq:freeslip_BC_modelC} as introduced for model version I, and the boundary condition~\eqref{eq:pressure_BC_modelC} is applied as discussed in the section on model IIa. The abstract weak formulation for model version 0 is then: find $(\uu,\, p)\in\VV\times Q$ such that
\begin{subequations}
    \begin{alignat}{2}
        \mathcal{A}(\uu, \vv) + \mathcal{B}(\vv, p) &= \mathcal{L}(\vv), &&\quad\forall\vv\in\VV, \\
        \mathcal{B}(\uu, q) &= 0, &&\quad\forall q\in Q,
    \end{alignat}%
    \label{eq:abstract_weak_form_modelC}
\end{subequations}%
with the definitions
\begin{align}
    \mathcal{A}(\uu, \vv) &= \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} -\intGp{\mu(\nabla\uu)^T\nn\cdot\vv}, \label{eq:stokes_bilinear_form}\\
    \mathcal{B}(\uu, q) &= -\intO{q\nabla\cdot\uu}, \label{eq:stokes_skew_form}\\
    \mathcal{L}(\vv) &= \intGc{\btau\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}. \label{eq:stokes_linear_form}
\end{align}

\subsection{Discretization of the Stokes Equations}
We will outline the discretization of the weak formulation~\cref{eq:abstract_weak_form_modelC,eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form} of the Stokes equations for model version 0. A similar approach can be used to discretize the weak formulation for the other model versions. First, we consider the spatial discretization of the weak formulation. We rewrite the weak form in terms of the discretized variables, denoted with the subscript $h$:
\begin{subequations}
    \begin{alignat}{2}
        \mathcal{A}(\uu_h, \vv_h) + \mathcal{B}(\vv_h, p_h) &= \mathcal{L}(\vv_h), &&\quad\forall\vv_h\in\VV_h, \\
        \mathcal{B}(\uu_h, q_h) &= 0, &&\quad\forall q_h\in Q_h.
    \end{alignat}%
    \label{eq:no_stabilization_abstract_discrete_weak_form_modelC}%
\end{subequations}%
Our choice for the discrete spaces $\VV_h$ and $Q_h$ are finite elements of the Brezzi-Douglas-Marini family~\cite{Brezzi1985TwoProblems} and discontinuous Galerkin elements, respectively. Application of this scheme requires a stabilization of the bilinear form $\mathcal{A}(\uu_h, \vv_h)$. We apply the stabilization outlined in Hong~\emph{et al.}~\cite{Hong2016AEquations}. First, we define the average and jump operators, respectively, as
\begin{equation*}
    \avg{\uu} = \frac{\uu^+\cdot\nn^+ - \uu^-\cdot\nn^-}{2} \qquad\mathrm{and}\qquad \jump{\uu} = \uu^+ - \uu^-,
\end{equation*}
where $\nn$ is the normal vector on a facet separating two cells, where the plus and minus signs denote variables in each of the two cells. The normal vector is chosen such that it points towards the exterior of its corresponding cell. On the boundary, the operators are defined as $\avg{\uu} = \uu\cdot\nn$ and $\jump{\uu} = \uu$,
with $\nn$ pointing to the exterior of the domain. We now define and add the bilinear form
\begin{align*}
    \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) &= \sum_{k\in K}\intF{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}\cdot \jump{P_{\nn}(\vv_h)}}\\
    &-\sum_{k\in K}\intF{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}-\sum_{k\in K}\intF{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}
\end{align*}
to the discrete weak  formulation~\eqref{eq:no_stabilization_abstract_discrete_weak_form_modelC}, where $\mathcal{F} = \{\mathcal{F}_k : k\in K\}$ is the set of all interior facets $\mathcal{F}_k$ of the computational mesh. The parameter $\gamma>0$ is introduced to penalize jumps in the tangential components of the velocity across facets, wheras $h$ is the cell diameter of a mesh cell, defined as the maximal distance between two points in a cell. The semi-discrete weak formulation of the Stokes equations reads: find ($\uu_h, p_h$)$\in$($\VV_h, Q_h$) such that
\begin{subequations}
    \begin{alignat}{2}
        \mathcal{A}(\uu_h, \vv_h) + \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) + \mathcal{B}(\vv_h, p_h) &= \mathcal{L}(\vv_h), &&\quad\forall\vv_h\in\VV_h, \\
        \mathcal{B}(\uu_h, q_h) &= 0, &&\quad\forall q_h\in Q_h.
    \end{alignat}%
    \label{eq:abstract_semi_discrete_weak_form_modelC}%
\end{subequations}%
We solved~\eqref{eq:abstract_semi_discrete_weak_form_modelC} numerically with the penalty parameter $\gamma=10$.

In time, we discretize the weak formulation~\eqref{eq:abstract_semi_discrete_weak_form_modelC} with the implicit Euler scheme.

\subsection{Weak Formulation of the Advection-Diffusion Equation}
Recall the strong form of the advection-diffusion equation:
\begin{equation}
    \pdifft{c} + \nabla\cdot\JJ = 0 \quad\mathrm{in} \ \Omega,
    \label{eq:adv_diff_strong_DG}
\end{equation}
where $\Omega$ is the domain with boundary $\Gamma$, and the total solute flux
\begin{equation*}
    \JJ(c) = c\uu - D\nabla c.
\end{equation*}
We consider $\JJ = \JJ(c)$, unless otherwise indicated. The concentration $c\in W$ and the cerebrospinal fluid velocity $\uu\in\VV$. The weak form of~\eqref{eq:adv_diff_strong_DG} is derived by multiplying the equation with a test function $\phi \in W$ and integrating over the domain: 
\begin{equation*}
    \intO{\pdifft{c}\phi} + \intO{(\nabla\cdot\JJ)\phi} = 0.
    %\label{eq:adv_diff_weak_DG_1}
\end{equation*}
Integrating the second term by parts and applying Green's first identity yields
\begin{equation}
    \intO{\pdifft{c}\phi} + \intG{(\JJ\cdot\nn)\phi} - \intO{\JJ\cdot\nabla\phi} = 0.\label{eq:adv_diff_weak_formA1}
\end{equation}
The boundary integral of the total flux is handled differently for the three different model versions, depending on the boundary conditions considered.

\textbf{Model Version I.} We consider $\Omega$ to be closed and with impermeable walls, setting $\JJ\cdot\nn=0$ on $\Gamma$. The weak form is then reduced to
\begin{equation*}
    \intO{\pdifft{c}\phi} - \intO{\JJ\cdot\nabla\phi} = 0, \quad\forall\phi\in W.
\end{equation*}
Defining the left-hand side as the bilinear form
\begin{equation*}
    a(c, \phi) = \intO{\pdifft{c}\phi} - \intO{\JJ\cdot\nabla\phi}, 
\end{equation*}
we have the following abstract weak formulation for model version I: find $c\in W$ such that
\begin{equation*}
    a(c, \phi) = 0, \quad\forall\phi\in W. %\label{eq:adv_diff_weak_formA2}
\end{equation*}

\textbf{Model Version II.} When using the normal pressure boundary condition~\eqref{eq:modelB_pressure_BC} to model pulsatile flow, we have in- and outflow of cerebrospinal fluid and thus advection of $c$ on the pressure boundary $\Gp$. Let $\Gp=\Gin\cup\Gout$ and $\Gamma = \Gnf\cup\Gin\cup\Gout$, with 
\begin{align*}
    \Gin  &= \bigg\{\xx\in\Gamma : \uu(\xx, t)\cdot\nn(\xx) < 0 \bigg\}, \\
    \Gout &= \bigg\{\xx\in\Gamma : \uu(\xx, t)\cdot\nn(\xx) > 0 \bigg\},
\end{align*}
as in- and outflow boundaries, respectively, where we have emphasized that both $\uu$ and $\nn$ are spatially dependent variables. With $\JJ\cdot\nn=0$ on the no-flux boundary $\Gnf$, we have
\begin{equation*}
    \intG{(\JJ\cdot\nn)\phi} = \intGin{(\JJ\cdot\nn)\phi} + \intGout{(\JJ\cdot\nn)\phi}. 
\end{equation*}
For the outflow boundary integral over $\Gout$, we impose zero diffusive flux $D\nabla c\cdot\nn=0$, with the advection term $c(\uu\cdot\nn)$ simply left in the variational form as an unknown. For the continuous problem this is problematic, since we are lacking a boundary condition to close the problem. In the discrete setting, however, this method of leaving the boundary term has been shown to yield consistent results~\cite{Papanastasiou1992ACondition, Lynch2020NumericalHemodynamics, Griffiths1997TheCondition}. Intuitively, one can think of this outflow boundary condition as setting the advective flux to being the one consistent with the weak form, for which there is a unique $c$ satisfying the equations, with $\uu$ determined by the Stokes equations.

The flux integral over the inflow boundary $\Gin$ cannot be handled in the same way as the method used for $\Gout$, as this would not preserve coercivity of the weak form. Lacking experimental data both for the magnitude and origin of an inflow boundary flux, we deal with the inflow boundary in an explicit way that resembles an approximation of a periodic boundary condition. At a timestep $n$, when solving the linear system for the concentration $c^{n+1}$ at the next timestep $n+1$, we set the inflow flux $h_{\mathrm{in}}^{n+1} = h_{\mathrm{out}}^{n}$, where the latter is the outflow flux
\begin{equation*}
    h_{\mathrm{out}}^{n} = \JJ^n\cdot\nn = (c^n\uu^n - D\nabla c^n)\cdot\nn
\end{equation*}
at the previous timestep. In the limit that the timestep $\Delta t\to 0$, we would be imposing
\begin{equation*}
    \intGin{(\JJ\cdot\nn)} = \intGout{(\JJ\cdot\nn)},
\end{equation*}
which means no mass would be added to the system except for at the injection site, which is desired as we endeavor to model the ventricles as a closed system.

Using the introduced approaches of handling the in- and outflow boundaries, the resulting abstract weak formulation for model version II is: find $c\in W$ such that
\begin{equation}
    a(c, \phi) + \Tilde{b}(c, \phi) = \Tilde{L}(\phi), \quad\forall\phi\in W, \label{eq:adv_diff_weak_formB}
\end{equation}
with the definitions
\begin{align}
    a(c, \phi) &= \intO{\pdifft{c}\phi} - \intO{\JJ\cdot\nabla\phi}, \label{eq:adv_diff_bilinear_form}\\
    \Tilde{b}(c, \phi) &= \intGout{c(\uu\cdot\nn)\phi}, \label{eq:adv_diff_skew_form} \\
    \Tilde{L}(\phi) &= \intGin{h_{\mathrm{in}}\phi}.\label{eq:adv_diff_linear_form}
\end{align}

\textbf{Model Version 0.} Since both free-slip and cilia tangential traction boundaries have the same no-flux boundary condition in the advection-diffusion equation, the weak formulation of the advection-diffusion equation for model version 0 is identical to that of model version II, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.

\subsection{Discretization of the Advection-Diffusion Equation}
We outline the discretization of the advection-diffusion weak formulation for model version 0, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}. The weak formulation is discretized with a symmetric interior-penalty method using discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}. Let the subscript $h$ denote discrete variables. Exchanging the variables in~\eqref{eq:adv_diff_weak_formB} with their discrete counterparts yields the discrete weak form: find $c_h\in W_h$ such that
\begin{equation*}
    a(c_h, \phi_h) + \Tilde{b}(c_h, \phi_h) = \Tilde{L}(\phi_h), \quad\forall\phi_h\in W_h.
\end{equation*}
The space $W_h$ is constructed with  finite elements with discontinuous linear Lagrange polynomial basis functions, allowing for discontinuities in the discrete solution across element edges.  To achieve a stable discretization with these elements, we add the stabilization
\begin{equation}
    \begin{aligned}
        a_{\mathrm{stab}}(c_h, \phi_h) = &\sum_{k\in K}\intF{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}} +\sum_{k\in K}\intF{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
         -&\sum_{k\in K}\intF{D\avg{\nabla\phi_h}\cdot\jump{c_h}} -\sum_{k\in K}\intF{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
    \end{aligned}\label{eq:SIP_stabilization}
\end{equation}
\mk{
Above and also in weak form of BDM Stokes there should not be the sum over elements.
The sum is over facets. The way it is written you would include each interior facet twice.
}
to the discrete weak formulation, where
\begin{equation*}
    \hat{u}_h = \frac{1}{2}\left(\uu_h\cdot\nn + \vert\uu_h\cdot\nn\vert\right)
\end{equation*}
is used to upwind the velocity $\uu_h$, with the velocity upwinded with respect to a facet $\mathcal{F}_k$. The stabilization parameter $\alpha>0$ must be chosen large enough to achieve stability. The average and jump operators used in~\eqref{eq:SIP_stabilization} are defined, respectively, as
\begin{equation*}
    \avg{c} = \frac{c^+ + c^-}{2} \qquad\mathrm{and}\qquad \jump{c} = c^+\nn^+ + c^-\nn^-.
\end{equation*}
The final discrete weak formulation of the advection-diffusion equation is: find $c_h\in W_h$, such that
\begin{equation}
    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + \Tilde{b}(c_h, \phi_h) = \Tilde{L}(\phi_h), \quad\forall\phi_h\in W_h.
    \label{eq:discrete_weak_form_adv_diff}
\end{equation}
In this work, we solved~\eqref{eq:discrete_weak_form_adv_diff} numerically with the penalty parameter value $\alpha=25$.

In time, we discretized~\eqref{eq:discrete_weak_form_adv_diff} with the implicit Euler scheme.

%--------------VERIFICATION--------------%
\section{Verification}\label{sec:appB_verification}
\subsection{Method of Manufactured Solutions}\label{subsec:mms}
Let $\hat{\xx} = (\hat{x}, \hat{y}, \hat{z}) = \frac{1}{L}(x, y, z)$ be the spatial coordinates scaled by the length $L$, which is the length of the computational domain $\Omega$ in the $x$-direction. Letting $\bm{\phi}$ be the vector-valued function
\begin{equation*}
    \bm{\phi} = \left(\sin{(\pi(\hat{x} - \hat{y}))}, \sin{(\pi(\hat{y} + \hat{z}))}, \sin{(\pi(\hat{x} - \hat{z}))}\right)
    %\label{eq:velocity_potential_mms}
\end{equation*}
and defining the velocity as 
\begin{equation}
    \uu_{\mathrm{mms}} = \nabla\times\bm{\phi},
    \label{eq:velocity_mms}
\end{equation}
we have by construction that the velocity is divergence-free, owing to the identity $\nabla\cdot(\nabla\times\mathbf{F}) = 0$ for an arbitrary vector field $\mathbf{F}$. The pressure was defined as
\begin{equation}
    p_{\mathrm{mms}} = \cos{(\pi(\hat{x} + \hat{y} + \hat{z}))}.
    \label{eq:pressure_mms}
\end{equation}
Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions}, we construct a Stokes problem where~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms} are the solutions. To this end, we consider the general form of the steady Stokes equations
\begin{subequations}
    \begin{align}
        -\nabla\cdot\bsig &= \ff \qquad\mathrm{in \ }\Omega,\\
        \nabla\cdot\uu &= g \qquad\mathrm{in \ }\Omega,
    \end{align}
    \label{eq:stokes_mms}%
\end{subequations}%
with $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and $\beps(\uu) = \frac{1}{2}\left(\nabla\uu + (\nabla\uu)^T\right)$, and the boundary conditions
\begin{alignat}{2}
    \uu &= \uu_{\mathrm{mms}} \qquad&&\mathrm{on \ }\Gamma, \\
    p   &= p_{\mathrm{mms}} \qquad&&\mathrm{on \ }\Gamma,
\end{alignat}
\mk{You cannot have both conditions on the same piece of boundary. If you prescribed 
velocity everywhere then the discrete solution should be normalized such that 
$\int_{\Omega}(p_h - p_{\mathrm{mms}})=0$.
}
where $\Gamma=\partial\Omega$ is the boundary of the domain. Since the velocity field~\eqref{eq:velocity_mms} is divergence free by construction, $g = 0$. Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$  using~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}, the solutions $\uu$ and $p$ to~\eqref{eq:stokes_mms} will be the ones defined by~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}. Convergence rates can thus readily be calculated by comparing the numerical approximations of $\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$.

\subsection{Norms and Convergence Order}\label{subsec:norms_and_eoc}
Errors of the velocity $\uu_h$ and pressure $p_h$ approximated with finite elements were measured in the $\mathbf{H}^1$ and $L^2$ error norms, respectively. With the exact velocity field $\uu_{\mathrm{ex}}$, the $\mathbf{H}^1$ error norm was calculated as
\begin{equation*}
    \Hnorm{\uu_h - \uu_{\mathrm{ex}}}^2 = \intO{\nabla(\uu_h - \uu_{\mathrm{ex}}) : \nabla(\uu_h - \uu_{\mathrm{ex}})}.
\end{equation*}
The $L^2$ error norms for the pressure were calculated as
\begin{equation*}
    \normltwo{p_h - p_{\mathrm{ex}}}^2 = \intO{(p_h - p_{\mathrm{ex}})^2}.
\end{equation*}
The approximated functions were interpolated onto elements in a space of piecewise-continuous Lagrange polynomials of three polynomial degrees higher than the elements used to approximate the functions, meaning that polynomial degrees 5 and 4 were used for the velocity and pressure errors, respectively. Numerical integration was performed with a Gauss quadrature rule, with the quadrature rule degree equal to the polynomial degree of the integrated finite element functions.

Convergence rates reported in~\cref{subsec:numerical_verification} were approximated in the following way. Define the error $e_k$ for a given mesh resolution $h_k$. Based on the assumption that the error scales as $e_k \approx C{h_k}^l$, where $C$ is a constant independent of $h_k$, the convergence order $l$ was approximated as
\begin{equation}
    l = \frac{\log{(e_k/e_{k+1}})}{\log{(h_k/h_{k+1}})}.
    \label{eq:convergence_order_estimate}
\end{equation}
Consider a finite element function 
\begin{equation*}
    \phi = \phi_i\psi_i(\xx)
\end{equation*}
with basis functions $\psi_i$, where $i$ are the degrees of freedom and Einstein summation is employed. The infinity norm of $\phi$ was approximated from the vector
of coefficients $\left\{\phi_i\right\}$, which represent point evaluations of $\phi$ as
\begin{equation*}
    \normlinf{\phi} = \max_i{\vert \phi_i\vert}.
\end{equation*}

\subsection{Numerical Verification of Model Implementation}\label{subsec:numerical_verification}
A cylinder geometry meshed with varying degrees of refinement was used to perform convergence analysis of the numerical methods used to solve the Stokes equations. The cylinder had unit length and a diameter of one half length unit. For the analysis, we used tangential traction boundary conditions on all of the cylinder surface. Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions} with the velocity and pressure expressions defined in~\cref{subsec:mms} for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{H}(\mathrm{div};\Omega)$ and $\mathbf{H}^1$ error norms for $\uu_h$, and the $L^2$ error norm for $p_h$~(\cref{tab:cylinder_error_rates}). Based on the error norm calculations, we also calculated the experimental order of convergence~(\cref{subsec:norms_and_eoc}). We observe convergence in all of the reported error norms. Furthermore, we report the error in calculation of the maximum velocities, and observe convergence in this error as well. Lastly, we calculated the $L^2$ norm of the divergence $\nabla\cdot\uu_h$ to verify the property of mass conservation.
\begin{table}[!htbp]
    \small
    \centering
    \caption{Error norms of the velocity $\uu_h$ in the $\mathbf{L}^2$ and $\mathbf{H}^1$ norms, the pressure $p_h$ in the $L^2$ norm, and the error in the maximum velocity magnitude $\uu_{h, {\mathrm{mag}}}$ for mesh refinement on a cylinder mesh with model version I. Additionally, we report the $L^2$ norm of the divergence of the velocity. For all error norms, convergence rates calculated with~\eqref{eq:convergence_order_estimate} are given in parentheses.}\label{tab:cylinder_error_rates}
    \begin{tabular}{cc|ccccc}
        \toprule
        $h/h_0$ & \# dofs & $\normltwovec{\uu_h - \uu_{\mathrm{ex}}}$ & $\Hnorm{\uu_h - \uu_{\mathrm{ex}}}$ & $\normltwo{p_h - p_{\mathrm{ex}}}$ & $\normlinf{u_h} -\normlinf{u_{\mathrm{ex}}}$ & $\normltwo{\nabla\cdot\uu_h}$\\ 
        \midrule 
        1    & 8652 & \num{2.3e-02} (---) & \num{4.3e-01} (---) & \num{5.4e-01} (---) & \num{2.4e-02} (---) & \num{1.4e-07} \\  
        1/2  & 41190 & \num{9.3e-03} (1.30) & \num{2.8e-01} (0.61) & \num{3.7e-01} (0.53) & \num{5.0e-03} (2.25) & \num{2.8e-08} \\  
        1/4  & 255016 & \num{3.5e-03} (1.42)    & \num{1.4e-01} (1.00) & \num{2.1e-01} (0.79) & \num{1.4e-03} (1.83) & \num{7.3e-11} \\         
        1/8  & 1855337 & \num{1.3e-03} (1.46) & \num{6.9e-02}  (1.03) & \num{1.1e-01} (0.94)  & \num{6.7e-04} (1.08) & \num{1.4e-10} \\   
        \bottomrule
    \end{tabular}
\end{table}

To verify the model implementation with the zebrafish brain ventricles mesh, we compared velocity norms for varying degrees of refinement of the brain ventricles mesh~(\cref{tab:ventricles_norms_BDM}). For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$. For a velocity vector $\uu=(u_x, u_y, u_z)$, the velocity magnitude is $u = \sqrt{u_x^2 + u_y^2 + u_z^2}$. We also report the maximum value $\normlinf{u_h}$ scaled by the area $|\Gc|=\intGc{}$ over which tangential traction $\btau$ was applied. We chose this measure using $|\Gc|$ as a scale because the regions of the mesh marked as cilia-populated changes slightly with every mesh refinement, owing to the unstructured organization of the mesh cells. This change in the surface area over which the tangential traction was applied directly affected the maximum velocity magnitude, since the maximum velocity magnitude is a result of the total amount of force $\intGc{\btau\cdot P_{\nn}(\rr)}$ applied on the ciliated boundary, where the cilia vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ as introduced in~\cref{subsec:appendixA1}. In the numerical experiments, we set a constant $\tau = 6.5\times 10^{-4}$ Pa, with $\rr = (1, 0, 1)$ in the ventral diencephalic ventricle cilia region and $\rr = -(1, 0, 1)$ in the telencephalic and dorsal diencephalic ventricle cilia regions. We used $\gamma=10$ for the BDM penalty parameter.

To account for the fact that the volume $|\Omega|=\intO{}$ also changes slightly with mesh refinement, we report the $\mathbf{L}^2$ norm of $\uu_h$ scaled by $|\Omega|$.
Finally, we provide verification of mass conservation by reporting the $\mathbf{L}^2$ norms of the divergence $\nabla\cdot\uu_h$. We remark that the units used in the model implementation was millimeters, which is why~\cref{tab:ventricles_norms_BDM} reports units in millimeters, instead of micrometers which has been used elsewhere in the paper. 
\begin{table}[!htbp]
    \centering
    \caption{Velocity norms under mesh refinement on the brain ventricles mesh using model version I with $\btau = \tau P_{\nn}(\rr)$, using $\tau = 6.5\times 10^{-4}$ Pa and $\rr = (1, 0, 1)$.}\label{tab:ventricles_norms_BDM}
    \begin{tabular}{cc|cccc}
        \toprule
        \# cells & \# dofs & $\normlinf{u_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$ & $\frac{1}{|\Gc|}\normlinf{u_h}$ $\left[\frac{1}{\mathrm{mm\cdot s}}\right]$ & $\frac{1}{\vert\Omega\vert}\normltwovec{\uu_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$ & $\normltwo{\nabla\cdot\uu_h}$ $\left[\frac{\mathrm{mm^3}}{\mathrm{s^2}}\right]$\\
        \midrule 
        132134  & 943820  & 0.0276 & 0.97 & \num{3.6e-03} & \num{6.3e-16}\\
        180901  & 1289881 & 0.0284 & 0.98 & \num{3.7e-03} & \num{1.5e-13}\\
        262598  & 1870703 & 0.0292 & 0.98 & \num{3.8e-03} & \num{6.2e-16}\\
        395339  & 2811668 & 0.0292 & 0.96 & \num{3.8e-03} & \num{1.9e-14}\\
        627439  & 4448761 & 0.0286 & 0.92 & \num{3.7e-03} & \num{4.6e-14}\\
        \bottomrule
    \end{tabular}
\end{table}
\iffalse
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{graphics/cylinder_mesh.png}
    \caption{The cylinder geometry used for convergence analysis. The cylinder had unit length and a diameter of half a unit length. Illustrated here is the mesh of highest resolution, with $h/h_0 = 1/8$ and a total of 1 855 337 degrees of freedom.}
    \label{fig:cylinder_mesh}
\end{figure}
\fi

\section{Quantification of Particle Transport}\label{sec:appC_particle_transport}
Particle tracking data~\cite{Olstad2019CiliaryDevelopment} was analyzed. For four zebrafish, five recordings with a few particles for each fish were carried out. The particles tracked were in the duct between the rhombencephalic ventricle and the diencephalic ventricle. Frequency of image acquisition was 20.22 Hz. The collected data constituted $x$ and $y$ positions of the particles at every time instant of image acquisition. The velocities $\uu_x$ and $\uu_y$ were determined by calculating the change in positions $\Delta x$ and $\Delta y$ relative to the change in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the frequency of acquisition. Mean velocities $\overline{u}_x$~(\cref{fig:meanx}) and $\overline{u}_y$~(\cref{fig:meany}), which serve as a quantification of particle drift, were calculated by taking the difference between the last and first positions of a particle.

Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was 0.26 $\mu$m/s and the mean of $\overline{u}_y$ was 0.08 $\mu$m/s. The maximum mean velocities in absolute values were 10.2 $\mu$m/s and 2.4 $\mu$m/s for $\overline{u}_x$ and $\overline{u}_y$, respectively. We used flow model II (only cardiac forces) to tune the pressure boundary condition amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude of 4.8 $\mu$m/s, which is close to the maximum observed in the particle tracking data when rejecting the outlier at around 10 $\mu$m/s; (ii) it yields a time-averaged mean velocity of 0.89 $\mu$m/s, which is close to the mean observed in the particle tracking data.
\begin{figure}[H]
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
        \subcaption{Mean velocities in the $x$ direction of the particles tracked.}\label{fig:meanx}
    \end{minipage}
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
        \subcaption{Mean velocities in the $y$ direction of the particles tracked.}\label{fig:meany}
    \end{minipage} 
    \caption{Particle tracking data. The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
\end{figure}
\clearpage
\bibliography{ref}{}
\end{document}

### 2025-01-25 scripts/BDM_flow_zfish.py

@@ -12,9 +12,9 @@ from petsc4py  import PETSc
 from basix.ufl import element, mixed_element
 from dolfinx.fem.petsc import assemble_matrix, _assemble_vector_vec, set_bc, apply_lifting, create_vector
 
-from imports.mesh                 import recal_mark_boundaries_flow, recal_anterior_cilia_volume, recal_middle_ventral_cilia_volume
-from imports.forcing_expressions  import OscillatoryPressure
-from imports.normals_and_tangents import facet_vector_approximation
+from utilities.mesh                 import recal_mark_boundaries_flow, recal_anterior_cilia_volume, recal_middle_ventral_cilia_volume
+from utilities.forcing_expressions  import OscillatoryPressure
+from utilities.normals_and_tangents import facet_vector_approximation
 
 print = PETSc.Sys.Print
 

### 2025-01-25 scripts/DG_transport.py

@@ -1,5 +1,5 @@
-from imports.local_imports import *
-from imports.mesh          import mark_boundaries_flow_and_transport, create_ventricle_volumes_meshtags
+from utilities.local_imports import *
+from utilities.mesh          import mark_boundaries_flow_and_transport, create_ventricle_volumes_meshtags
 
 import os
 import time

### 2025-01-25 scripts/TH_flow_zfish.py

@@ -1,481 +1,0 @@
-import multiphenicsx.fem
-import multiphenicsx.fem.petsc
-from imports.mesh                import mark_boundaries_flow
-from imports.local_imports       import *
-from imports.utilities           import tangential_projection
-from imports.forcing_expressions import OscillatoryPressure
-
-import adios2
-import adios4dolfinx as a4d
-
-print = PETSc.Sys.Print
-
-# Mesh tags for flow
-ANTERIOR_PRESSURE    = 2
-POSTERIOR_PRESSURE   = 3
-VOLUME               = 4
-MIDDLE_VENTRAL_CILIA = 5
-MIDDLE_DORSAL_CILIA  = 6
-ANTERIOR_CILIA       = 7
-SLIP                 = 9
-
-class FlowSolver:
-    """ Solver for the Stokes equations using a Lagrange multiplier for the normal stresses.
-
-    """
-
-    f = 2.22 # Cardiac frequency [Hz]
-
-    def __init__(self, mesh: dfx.mesh.Mesh,
-                       model_version: str,
-                       write_output: bool = False,
-                       pp: bool = False) -> None:
-        """ Constructor.
-
-        Parameters
-        ----------
-        mesh : dfx.mesh.Mesh
-            Computational mesh.
-
-        """
-
-        self.mesh = mesh
-
-        io_boundaries = False if model_version == 'A' else True
-        self.ft   = mark_boundaries_flow(mesh=mesh, inflow_outflow=io_boundaries)
-        self.model_version = model_version
-        self.write_output = write_output
-        self.pp  = pp
-        
-
-    def SetBilinearForm(self, u    : ufl.TrialFunction, v   : ufl.TestFunction,
-                              p    : ufl.TrialFunction, q   : ufl.TestFunction,
-                              zeta : ufl.TrialFunction, eta : ufl.TestFunction):
-        """ Create and set the bilinear form for the Stokes equations variational problem. """
-        eps   = lambda u: ufl.sym(grad(u)) # Symmetric gradient
-        dx = self.dx
-        ds = self.ds
-        n  = self.n
-
-        # Initialize form blocks
-        a00 = a01 = a02 = 0
-        a10 = 0
-        a20 = 0
-
-        if self.model_version == 'A':
-            # whole boundary is slip BC
[…]

### 2025-01-25 scripts/annotate_subplots.py

@@ -1,0 +1,91 @@
+import vtk # Needed for pyvista
+
+import numpy   as np
+import pyvista as pv
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py    import MPI
+from basix.ufl import element
+
+# Set latex text properties
+
+plt.rcParams.update({
+    "text.usetex": True,
+    "font.family": "serif"
+})
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+input_filename = "../output/checkpoints/transport/DG1/pressure/model_C/D1/concentration_inj=anterior_dorsal"
+mesh = a4d.read_mesh(comm=comm, file=input_filename, engine="BP4", ghost_mode=gm)
+
+# Get mesh properties
+x_geo = mesh.geometry.x
+
+x_min = x_geo[:, 0].min()
+x_max = x_geo[:, 0].max()
+x_mid = (x_min + x_max) / 2
+
+y_max = x_geo[:, 1].max()
+
+z_min = x_geo[:, 2].min()
+z_max = x_geo[:, 2].max()
+z_mid = (z_min + z_max) / 2
+
+# Set up unstructured grids with data
+k = 1 # element degree
+W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), k)) # DG1 function space
+cells, types, x = dfx.plot.vtk_mesh(W)
+timesteps = [100, 500, 1000] # the timesteps to visualize
+grids = [pv.UnstructuredGrid(cells, types, x) for _ in range(3*len(timesteps))]
+
+m = 0 # grid index
+for j in range(len(timesteps)):
+    for i in [1, 2, 3]:    
+        c_in = dfx.fem.Function(W)
+        a4d.read_function(u=c_in, filename=input_filename, engine="BP4", time=timesteps[j])
+        grids[m].point_data["c"] = c_in.x.array.real
+        grids[m].set_active_scalars("c")
+        m += 1 # increment
+
+# Create plot object
+plot_shape = (len(timesteps), 3)
+plotter = pv.Plotter(shape=plot_shape, window_size=[3200, 1400], border=False)
+# cmap = "CET_D1A" # Cold-warm colormap
+cmap = "speed"
+
+# Colorbar arguments
+sargs = dict(
+    title_font_size=50,
+    label_font_size=40,
+    shadow=True,
+    n_labels=3,
[…]

### 2025-01-25 scripts/cellwise_time_to_threshold.py

@@ -1,0 +1,43 @@
+import numpy as np
+import dolfinx as dfx
+import adios4dolfinx as a4d
+
+from mpi4py import MPI
+from basix.ufl import element
+
+
+k = 1 # Finite element degree of concentration data
+comm = MPI.COMM_WORLD # MPI communicator
+gm = dfx.mesh.GhostMode.shared_facet # Mesh MPI ghost mode
+
+# Model version and filename
+model_version = 'C'
+input_filename = f"/Users/hherlyng/zebrafish-cilia-csf/src/output/transport/model_{model_version}_D3_DG1_pressureBC/injection_site_middle_dorsal_posterior/checkpoints/concentration/"
+
+# Load mesh
+mesh = a4d.read_mesh(comm=comm, filename=input_filename, engine="BP4", ghost_mode=gm)
+
+# Create finite element function in DG_k space
+el_k = element("DG", mesh.basix_cell(), k)
+DG_k = dfx.fem.functionspace(mesh, el_k)
+
+f_k = dfx.fem.Function(DG_k) # Finite element function for reading in the concentration
+t_hat = dfx.fem.Function(DG_k) # Finite element function for storing the times to threshold
+t_hat.x.array[:] = -1 # Initialize all t_hats as -1
+
+# Load DGk file
+times = np.arange(1, 38001) # The timesteps considered
+threshold = 0.25 # The threshold for assigning times as t_hat
+
+# Loop over all timesteps
+for time in times:
+    print(f"Time = {time}", flush=True)
+    a4d.read_function(filename=input_filename, u=f_k, engine="BP4", time=time) # Read concentration field
+    idx_set = np.where(f_k.x.array > threshold)[0] # Index to dofs of f_k that are above the threshold
+    below = np.where(t_hat.x.array == -1)[0] # Index to dofs of t_hat that have not yet been assigned a time
+    above_idx = np.intersect1d(idx_set, below) # The intersection of the above two, which are the dofs where t_hat should be assigned as current timestep
+    t_hat.x.array[above_idx] = time
+    
+# Write output
+with dfx.io.VTXWriter(comm, f"t_hat_model_{model_version}.bp", [t_hat], "BP4") as vtx: vtx.write(0) # VTX file (for visualization)
+a4d.write_function_on_input_mesh(filename=f"t_hat_model_{model_version}", u=t_hat) # Checkpoint file (can be reloaded later)

### 2025-01-25 scripts/compare_concentrations.py

@@ -1,0 +1,36 @@
+import dolfinx as dfx
+import adios4dolfinx as a4d
+from mpi4py.MPI import COMM_WORLD as comm
+from basix.ufl import element
+
+ghost_mode = dfx.mesh.GhostMode.shared_facet
+file_A = '../output/checkpoints/transport/model_A/D1/concentration_inj=anterior_dorsal/'
+file_C = '../output/checkpoints/transport/model_C/D1/concentration_inj=anterior_dorsal/'
+mesh = a4d.read_mesh(comm, file_A, "BP4", ghost_mode)
+el_dg = element("DG", mesh.basix_cell(), 1)
+el_cg = element("Lagrange", mesh.basix_cell(), 1)
+DG1 = dfx.fem.functionspace(mesh, el_dg)
+P1  = dfx.fem.functionspace(mesh, el_cg)
+c_A = dfx.fem.Function(DG1)
+c_C = dfx.fem.Function(DG1)
+c_diff = dfx.fem.Function(DG1)
+c_out = dfx.fem.Function(P1)
+
+read_time = 0
+a4d.read_function(c_A, file_A, time=read_time)
+a4d.read_function(c_C, file_C, time=read_time)
+c_diff.x.array[:] = c_A.x.array.copy() - c_C.x.array.copy()
+c_out.interpolate(c_diff)
+xdmf_c_diff = dfx.io.XDMFFile(comm, 'c_diff.xdmf', 'w')
+xdmf_c_diff.write_mesh(mesh)
+xdmf_c_diff.write_function(c_out, read_time)
+for _ in range(199):
+    read_time += 1
+    print(f"Time = {read_time}")
+    a4d.read_function(c_A, file_A, time=read_time)
+    a4d.read_function(c_C, file_C, time=read_time)
+    c_diff.x.array[:] = c_A.x.array.copy() - c_C.x.array.copy()
+    print(f"Maximum concentration difference: {c_diff.x.array.max()}")
+    c_out.interpolate(c_diff)
+    xdmf_c_diff.write_function(c_out, read_time)
+xdmf_c_diff.close()

### 2025-01-25 scripts/create_colormap.py

@@ -1,0 +1,102 @@
+def register_colormaps() -> None:
+    import matplotlib
+    import matplotlib.colors
+
+    colors_greens = [[1, 0.984314, 0.901961],
+            [0.960784, 0.94902, 0.670588],
+            [0.886275, 0.921569, 0.533333],
+            [0.784314, 0.878431, 0.396078],
+            [0.666667, 0.839216, 0.294118],
+            [0.556863, 0.8, 0.239216],
+            [0.431373, 0.760784, 0.160784],
+            [0.317647, 0.721569, 0.113725],
+            [0.211765, 0.678431, 0.082353],
+            [0.109804, 0.631373, 0.05098],
+            [0.082353, 0.588235, 0.082353],
+            [0.109804, 0.54902, 0.152941],
+            [0.113725, 0.521569, 0.203922],
+            [0.117647, 0.490196, 0.243137],
+            [0.117647, 0.45098, 0.270588],
+            [0.113725, 0.4, 0.278431],
+            [0.109804, 0.34902, 0.278431]
+    ]
+
+    colors_wgk = [[1, 1, 1],
+              [0.901961, 0.941176, 0.796078],
+              [0.8, 0.878431, 0.580392],
+              [0.701961, 0.815686, 0.364706],
+              [0.6, 0.752941, 0.145098],
+              [0.498039, 0.690196, 0],
+              [0.396078, 0.627451, 0],
+              [0.294118, 0.564706, 0],
+              [0.196078, 0.501961, 0],
+              [0.094118, 0.439216, 0],
+              [0, 0.376471, 0],
+              [0, 0.313725, 0],
+              [0, 0.25098, 0],
+              [0, 0.188235, 0],
+              [0, 0.12549, 0],
+              [0, 0.062745, 0],
+              [0, 0, 0]
+    ]
+    # Refine color data
+    import numpy as np
+    import scipy.interpolate
+    arr = np.array(colors_wgk)
+    x = np.linspace(0, 1, len(arr[:, 0]))
+    interp_R = scipy.interpolate.interp1d(x, arr[:, 0])
+    interp_G = scipy.interpolate.interp1d(x, arr[:, 1])
+    interp_B = scipy.interpolate.interp1d(x, arr[:, 2])
+    x_fine = np.linspace(0, 1, 101)
+
+    refined_colors = np.zeros(shape=(len(x_fine), 3))
[…]

### 2025-01-25 scripts/gifs_compare_diff_coeffs.py

@@ -1,0 +1,98 @@
+import vtk # Needed for pyvista
+
+import pyvista as pv
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+
+from mpi4py    import MPI
+from basix.ufl import element
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+k = 1 # finite element degree
+read_file1 = f"../output/checkpoints/transport/DG{k}/pressure/model_C/D1/concentration_inj=middle_dorsal_posterior"
+read_file2 = f"../output/checkpoints/transport/DG{k}/pressure/model_C/D2/concentration_inj=middle_dorsal_posterior"
+read_file3 = f"../output/checkpoints/transport/DG{k}/pressure/model_C/D3/concentration_inj=middle_dorsal_posterior"
+mesh = a4d.read_mesh(comm=comm, file=read_file1, engine="BP4", ghost_mode=gm)
+plotter = pv.Plotter(shape=(1, 3), window_size=[3200, 1400])
+# Get mesh properties
+x_geo = mesh.geometry.x
+
+x_min = x_geo[:, 0].min()
+x_max = x_geo[:, 0].max()
+x_mid = (x_min + x_max) / 2
+
+y_max = x_geo[:, 1].max()
+
+z_min = x_geo[:, 2].min()
+z_max = x_geo[:, 2].max()
+z_mid = (z_min + z_max) / 2
+plotter.camera.position    = (x_mid, 0, z_mid*1.1)
+plotter.camera.focal_point = (x_mid, y_max, z_mid)
+plotter.camera.zoom(0.2)
+
+
+skip = 50
+dt = 0.02252
+fps = 40
+plotter.open_gif(f"../output/illustrations/DG{k}_compare_diff_coeffs_fps={fps}.gif", fps=fps)#int(1/dt)//skip)
+f = 2.22 # Cardiac frequency [Hz]
+period = 1 / f
+T  = 1000*period
+dt = period / 20
+num_steps = int(T / dt)
+
+W_scalar = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), k)) # DG function space
+c1 = dfx.fem.Function(W_scalar)
+c2 = dfx.fem.Function(W_scalar)
+c3 = dfx.fem.Function(W_scalar)
+cells, types, x = dfx.plot.vtk_mesh(mesh) if k==0 else dfx.plot.vtk_mesh(W_scalar) 
[…]

### 2025-01-25 scripts/meshing/mesh_ventricles.py

@@ -1,12 +1,0 @@
-import dolfinx as dfx
-
-from imports.mesh import read_msh_parallel
-from mpi4py import MPI
-
-# for i in range(9):
-i=10
-filename = './geometries/ventricles_' + str(i) + '.msh'
-mesh = read_msh_parallel(filename=filename, comm=MPI.COMM_WORLD)
-
-with dfx.io.XDMFFile(MPI.COMM_WORLD, filename.removesuffix('.msh') + '.xdmf', 'w') as xdmf:
-    xdmf.write_mesh(mesh=mesh)

### 2025-01-25 scripts/meshing/refine_mesh_boundary.py

@@ -1,25 +1,0 @@
-import dolfinx as dfx
-from mpi4py import MPI
-
-with dfx.io.XDMFFile(MPI.COMM_WORLD, "./geometries/ventricles_0.xdmf", "r") as xdmf:
-    mesh = xdmf.read_mesh()
-print(f"Number of mesh cells: {mesh.topology.index_map(3).size_global}")
-topo = mesh.topology
-tdim = mesh.topology.dim
-topo.create_connectivity(tdim, tdim-1)
-topo.create_connectivity(tdim, tdim-2)
-topo.create_connectivity(tdim-1, tdim)
-topo.create_connectivity(tdim-1, tdim-2)
-topo.create_connectivity(tdim-2, tdim-1)
-topo.create_connectivity(tdim-2, tdim)
-topo.create_connectivity(tdim-2, tdim-1)
-
-
-bdry_facets = dfx.mesh.exterior_facet_indices(topo)
-bdry_vertices = dfx.mesh.compute_incident_entities(topo, bdry_facets, tdim-1, tdim-2)
-
-mesh = dfx.mesh.refine(mesh=mesh, edges=bdry_vertices)
-
-with dfx.io.XDMFFile(MPI.COMM_WORLD, "./BL_refinement.xdmf", "w") as xdmf:
-    xdmf.write_mesh(mesh)
-print(f"Number of mesh cells in refined mesh: {mesh.topology.index_map(3).size_global}")

### 2025-01-25 scripts/plot_compare_cilia_regions.py

@@ -1,0 +1,118 @@
+import vtk # Needed for pyvista
+import ufl
+
+import numpy   as np
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py       import MPI
+from imports.mesh import create_ventricle_volumes_meshtags
+
+# Set matplotlib properties
+plt.rcParams.update({
+    "text.usetex" : True,
+    "font.family" : "sans-serif",
+    "axes.spines.top" : False,
+    "axes.spines.right" : False
+})
+plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+k = 1 # element degree
+model_version = 'C'
+original_mesh_input_filename = f"output/flow/checkpoints/variable_tau/pressure+original/model_{model_version}/velocity_data_dt=0.02252"
+mesh = a4d.read_mesh(comm=comm, filename=original_mesh_input_filename, engine="BP4", ghost_mode=gm)
+ct, ROI_tags = create_ventricle_volumes_meshtags(mesh)
+dx = ufl.Measure('dx', domain=mesh, subdomain_data=ct)
+volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=MPI.SUM) for tag in ROI_tags]
+volumes[3] += volumes[2]+volumes[1]+volumes[0]
+
+# Load data c_hat, the total concenctration in each ROI
+with open(f"output/transport/results/variable_tau/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_original    = np.load(file)
+with open(f"output/transport/results/variable_tau+rm_dorsal/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_dorsal  = np.load(file)
+with open(f"output/transport/results/variable_tau+rm_ventral/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_ventral = np.load(file)
[…]

### 2025-01-25 scripts/plot_compare_geometry.py

@@ -1,0 +1,152 @@
+import ufl
+
+import numpy   as np
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py       import MPI
+from imports.mesh import create_ventricle_volumes_meshtags
+
+"""
+Plot and compare results for the original ventricles mesh and the (more) shrunk ventricles mesh. The original ventricles mesh
+is based on the initial surface geometry retrieved from the Jurisch-Yaksi lab, the shrunk versions are the original mesh
+modified using the "shrink" mesh modifier in Blender. 
+
+Three different regions of the mesh were modified, and four modified meshes are considered:
+    - fore-shrunk: a mesh with shrinkage of the connection between the telencephalic ventricle and the diencephalic ventricle 
+    - middle-shrunk: a mesh with shrinkage of the diencephalic ventricle in the lateral direction (shrinkage along y-axis of mesh)
+    - fore-shrunk: a mesh with shrinkage of the connection between the diencephalic ventricle and the rhombencephalic ventricle
+    - fore+middle+hind shrunk: a mesh with all the three modifications outlined above performed
+
+Everything in this script with a subscript 1 is an attribute/variable of the original mesh.
+Everything in this script with a subscript 2 is an attribute/variable of the fore-shrunk mesh.
+Everything in this script with a subscript 3 is an attribute/variable of the middle-shrunk mesh.
+Everything in this script with a subscript 4 is an attribute/variable of the hind-shrunk mesh.
+Everything in this script with a subscript 5 is an attribute/variable of the fore+middle+hind-shrunk mesh.
+
+Author: Halvor Herlyng, 2024.
+"""
+
+# Set matplotlib properties
+plt.rcParams.update({
+    "text.usetex" : True,
+    "font.family" : "sans-serif",
+    "axes.spines.top" : False,
+    "axes.spines.right" : False
+})
[…]

### 2025-01-25 scripts/plot_compare_models.py

@@ -1,0 +1,146 @@
+import ufl
+
+import numpy   as np
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py       import MPI
+from imports.mesh import create_ventricle_volumes_meshtags
+
+# Set matplotlib properties
+plt.rcParams.update({
+    "text.usetex" : True,
+    "font.family" : "sans-serif",
+    "axes.spines.top" : False,
+    "axes.spines.right" : False
+})
+plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+k = 1 # element degree
+molecule = 'D3'
+tau_version  = 'original_tau'
+tau_version  = 'variable_tau'
+mesh_version = 'original'
+mesh_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+{mesh_version}/model_C/velocity_data_dt=0.02252"
+mesh = a4d.read_mesh(comm=comm, filename=mesh_input_filename, engine="BP4", ghost_mode=gm)
+
+# Create meshtags and calculate ROI volumes
+mt, ROI_tags = create_ventricle_volumes_meshtags(mesh)
+dx = ufl.Measure('dx', domain=mesh, subdomain_data=mt)
+volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=MPI.SUM) for tag in ROI_tags]
+volumes[3] += volumes[2]+volumes[1]+volumes[0] # Add ROI 1, 2, 3 volumes to ROI 4 volume
+
+# Load data c_bar, the total concenctration in each ROI
+with open(f"./output/transport/results/original_tau/{mesh_version}/log_model_B_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
+    c_bar_B = np.load(file)
+with open(f"./output/transport/results/{tau_version}/{mesh_version}/log_model_C_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
+    c_bar_C = np.load(file)
+
+# Scale the total concentrations in the ROIs by the volume of the respective ROI
+for i in ROI_tags: 
[…]

### 2025-01-25 scripts/plot_experiments_separate.py

@@ -1,0 +1,63 @@
+import numpy   as np
+import matplotlib.pyplot as plt
+
+from scipy.io import loadmat
+
+# Set matplotlib properties
+plt.rcParams.update({
+    "text.usetex" : True,
+    "font.family" : "sans-serif",
+    "axes.spines.top" : False,
+    "axes.spines.right" : False
+})
+plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
+
+# Set data directory and load .mat files
+data_dir = "./data_photoconversion/aggregated_data/"
+metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
+colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
+control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data
+mutant  = loadmat(data_dir+"mutant_data")['mut'] # The mutant fish cohort photoconversion data
+tt_control = loadmat(data_dir+"tt_control")['tt_control'][0][0] # Time-to-threshold data for the control cohort
+tt_mutant  = loadmat(data_dir+"tt_mutant")['tt_mutant'][0][0] # Time-to-threshold data for the mutant cohort 
+fps = metadata['metadata'][0][0][2][0][0] # Extract fps from metadata
+
+# Get the number of timesteps
+num_timesteps = control.shape[2]
+times = 1/fps*np.arange(num_timesteps)
+ROI_idx = range(6)
+
+# Plot the figures
+fig1, ax1 = plt.subplots(num=1, figsize=([18, 14])) # Plot for the control data
+fig2, ax2 = plt.subplots(num=2, figsize=([18, 14])) # Plot for the mutant data
+
+lw = 4.5 # linewidth
+
+for i in ROI_idx:
+    # Plot control data
+    y = np.mean(control[:, i, :], axis=0)
+    err = np.std(control[:, i, :], axis=0)/np.sqrt(control.shape[0])
+    ax1.plot(times, y, label=f'ROI {i+1}', color=colors[i], linewidth=lw)
+    ax1.fill_between(times, y-err, y+err, color=colors[i], alpha=0.25)
+
+    # Plot mutant data
+    y = np.mean(mutant[:, i, :], axis=0)
[…]

### 2025-01-25 scripts/plot_mean_concentrations.py

@@ -1,0 +1,202 @@
+import vtk # Needed for pyvista
+import ufl
+import time
+
+import numpy   as np
+import pyvista as pv
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py    import MPI
+from basix.ufl import element
+
+# Set latex text properties
+plt.rcParams.update({
+    "text.usetex": False,
+    "font.family": "serif"
+})
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+k = 1 # element degree
+mesh_input_filename = "output/checkpoints/pressure/model_C/velocity_data_dt=0.02252"#f"./output/checkpoints/transport/DG{k}/pressure/model_C/D3/concentration_inj=middle_dorsal_posterior"
+mesh = a4d.read_mesh(comm=comm, file=mesh_input_filename, engine="BP4", ghost_mode=gm)
+
+DEFAULT   = 2
+MIDDLE    = 3
+ANTERIOR  = 4
+POSTERIOR = 5
+
+def create_ventricle_volumes_meshtags(mesh: dfx.mesh.Mesh):
+    z_min = mesh.geometry.x[:, 2].min()
+    z_max = mesh.geometry.x[:, 2].max()
+    z_mid = (z_min + z_max) / 2
+    a1 = [0.165, 0.0, z_mid]
+    b1 = [0.125, 0.0, z_max*0.78]
+
+    a2 = [0.33, 0.0, z_mid*0.8]
+    b2 = [0.345, 0.0, z_max*0.75]
+
+    line1 = lambda t: a1[2] + (b1[2] - a1[2])/(b1[0] - a1[0])*(t - a1[0])
+    line2 = lambda t: a2[2] + (b2[2] - a2[2])/(b2[0] - a2[0])*(t - a2[0])
+
+    def middle_ventricle(x):
+        return np.logical_and(x[2] >= line1(x[0]), x[2] >= line2(x[0]))
+
+    def anterior_ventricle(x):
+        return x[2] < line1(x[0])
+
+    def posterior_ventricle(x):
+        return x[2] < line2(x[0])
+
+    tdim = mesh.topology.dim
+    ## TODO: update to using midpoint coordinate of cells located
+    middle_cells = dfx.mesh.locate_entities(mesh, tdim, middle_ventricle)
[…]

### 2025-01-25 scripts/refine_mesh_boundary.py

@@ -1,0 +1,25 @@
+import dolfinx as dfx
+from mpi4py import MPI
+
+with dfx.io.XDMFFile(MPI.COMM_WORLD, "./geometries/ventricles_0.xdmf", "r") as xdmf:
+    mesh = xdmf.read_mesh()
+print(f"Number of mesh cells: {mesh.topology.index_map(3).size_global}")
+topo = mesh.topology
+tdim = mesh.topology.dim
+topo.create_connectivity(tdim, tdim-1)
+topo.create_connectivity(tdim, tdim-2)
+topo.create_connectivity(tdim-1, tdim)
+topo.create_connectivity(tdim-1, tdim-2)
+topo.create_connectivity(tdim-2, tdim-1)
+topo.create_connectivity(tdim-2, tdim)
+topo.create_connectivity(tdim-2, tdim-1)
+
+
+bdry_facets = dfx.mesh.exterior_facet_indices(topo)
+bdry_vertices = dfx.mesh.compute_incident_entities(topo, bdry_facets, tdim-1, tdim-2)
+
+mesh = dfx.mesh.refine(mesh=mesh, edges=bdry_vertices)
+
+with dfx.io.XDMFFile(MPI.COMM_WORLD, "./BL_refinement.xdmf", "w") as xdmf:
+    xdmf.write_mesh(mesh)
+print(f"Number of mesh cells in refined mesh: {mesh.topology.index_map(3).size_global}")

### 2025-01-25 scripts/slices_concentration.py

@@ -1,0 +1,128 @@
+import vtk # Needed for pyvista
+
+import numpy   as np
+import pyvista as pv
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py    import MPI
+from basix.ufl import element
+
+""" Visualize concentration slices in a 3x3 figure. """
+
+
+# Set latex text properties
+plt.rcParams.update({
+    "text.usetex": True,
+    "font.family": "serif"
+})
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+k = 1 # element degree
+model_version = 'C'
+tau_version = 'variable_tau'
+input_filename1 = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_D1_DG1_pressureBC/checkpoints/concentration_snapshots/"
+input_filename2 = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_D2_DG1_pressureBC/checkpoints/concentration_snapshots/"
+input_filename3 = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_D3_DG1_pressureBC/checkpoints/concentration_snapshots/"
+mesh1 = a4d.read_mesh(comm=comm, filename=input_filename1, engine="BP4", ghost_mode=gm)
+mesh2 = a4d.read_mesh(comm=comm, filename=input_filename2, engine="BP4", ghost_mode=gm)
+mesh3 = a4d.read_mesh(comm=comm, filename=input_filename3, engine="BP4", ghost_mode=gm)
+
+# Get mesh properties
+x_geo = mesh1.geometry.x
+
+x_min = x_geo[:, 0].min()
+x_max = x_geo[:, 0].max()
+x_mid = (x_min + x_max) / 2
+
+y_max = x_geo[:, 1].max()
+
+z_min = x_geo[:, 2].min()
+z_max = x_geo[:, 2].max()
+z_mid = (z_min + z_max) / 2
+
+# Set up unstructured grids with data
+W1 = dfx.fem.functionspace(mesh=mesh1, element=element("DG", mesh1.basix_cell(), k)) # DG1 function space
+W2 = dfx.fem.functionspace(mesh=mesh2, element=element("DG", mesh1.basix_cell(), k)) # DG1 function space
[…]

### 2025-01-25 scripts/slices_concentration_varying_inj_site.py

@@ -1,0 +1,119 @@
+import vtk # Needed for pyvista
+
+import numpy   as np
+import pyvista as pv
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from mpi4py    import MPI
+from basix.ufl import element
+
+import matplotlib as mpl
+import matplotlib.colors
+colors = [[14, 28, 31], [14, 29, 32], [15, 30, 33], [15, 32, 34], [16, 33, 36], [16, 34, 37], [16, 35, 38], [17, 37, 39], [17, 38, 40], [18, 39, 42], [18, 40, 43], [18, 42, 44], [19, 43, 45], [19, 44, 46], [19, 45, 47], [20, 47, 48], [20, 48, 49], [20, 49, 49], [20, 50, 50], [21, 51, 51], [21, 52, 52], [21, 54, 52], [21, 55, 53], [21, 56, 54], [22, 57, 55], [22, 58, 56], [22, 59, 56], [22, 60, 57], [22, 61, 58], [23, 62, 58], [23, 63, 59], [23, 64, 59], [23, 65, 60], [23, 66, 61], [23, 67, 61], [24, 68, 62], [24, 69, 63], [24, 70, 63], [24, 71, 64], [24, 72, 64], [25, 73, 65], [25, 75, 66], [25, 76, 66], [26, 78, 67], [26, 79, 67], [26, 80, 68], [27, 82, 68], [27, 83, 69], [27, 85, 69], [27, 86, 70], [28, 88, 70], [28, 89, 71], [28, 90, 71], [28, 91, 71], [28, 92, 71], [28, 93, 71], [29, 94, 71], [29, 95, 71], [29, 96, 71], [29, 97, 71], [29, 98, 71], [29, 99, 71], [29, 100, 71], [29, 101, 71], [29, 102, 71], [29, 103, 71], [29, 104, 71], [29, 105, 71], [30, 106, 70], [30, 107, 70], [30, 108, 70], [30, 109, 70], [30, 110, 70], [30, 111, 70], [30, 112, 69], [30, 113, 69], [30, 114, 69], [30, 115, 69], [30, 116, 68], [30, 117, 68], [30, 118, 67], [30, 119, 67], [30, 119, 66], [30, 120, 66], [30, 121, 65], [30, 122, 64], [30, 122, 64], [30, 123, 63], [30, 124, 63], [30, 125, 62], [30, 125, 61
[…]

### 2025-01-25 scripts/tag_ventricles.py

@@ -1,0 +1,13 @@
+import dolfinx as dfx
+from mpi4py import MPI
+from imports.mesh import mark_boundaries_flow, create_ventricle_volumes_meshtags
+
+with dfx.io.XDMFFile(MPI.COMM_WORLD, "geometries/fore_middle_hind_shrunk.xdmf", "r") as xdmf:
+    mesh = xdmf.read_mesh()
+
+# ft = mark_boundaries_flow(mesh, True, modify=3)
+ct, _ = create_ventricle_volumes_meshtags(mesh)
+
+with dfx.io.XDMFFile(MPI.COMM_WORLD, "new_mesh.xdmf", "w") as xdmf:
+    xdmf.write_mesh(mesh)
+    xdmf.write_meshtags(ct, mesh.geometry)

### 2025-01-25 scripts/utilities/create_removed_sphere_cube_mesh.py

@@ -1,0 +1,119 @@
+import gmsh
+
+import numpy   as np
+
+from   mpi4py  import MPI
+
+gmsh.initialize()
+
+# Mesh and domain parameters
+L = 1 # Length of domain [m]
+H = 1 # Height of domain [m]
+D = 1 # Depth of domain [m]
+r = 0.2 # Radius of sphere [m]
+
+c_x = 0.5 # x coordinate of sphere center [m]
+c_y = 0.5 # y coordinate of sphere center [m]
+c_z = 0.5 # z coordinate of sphere center [m]
+
+gmsh_dim = 3
+mesh_comm = MPI.COMM_WORLD
+model_rank = 0
+if mesh_comm.rank == model_rank:
+    box_domain = gmsh.model.occ.addBox(0, 0, 0, L, H, D, tag = 1)
+    ball       = gmsh.model.occ.addSphere(c_x, c_y, c_z, r)
+
+# Remove the cylinder from the box domain
+if mesh_comm.rank == model_rank:
+    fluid_domain = gmsh.model.occ.cut([(gmsh_dim, box_domain)], [(gmsh_dim, ball)])
+    gmsh.model.occ.synchronize()
+
+# Add physical volume marker for the fluid mesh
+fluid_marker = 10
+if mesh_comm.rank == model_rank:
+    volumes = gmsh.model.getEntities(dim = gmsh_dim)
+    assert(len(volumes) == 1)
+    gmsh.model.addPhysicalGroup(volumes[0][0], [volumes[0][1]], fluid_marker)
+    gmsh.model.setPhysicalName(volumes[0][0], fluid_marker, "Fluid")
+    
+# Tag the boundaries of the mesh by computing the centers of mass of the boundaries
+LEFT    = 1
+RIGHT   = 2
+FRONT   = 3
+BACK    = 4
+BOTTOM  = 5
+TOP     = 6
+SPHERE  = 8
+left, right, front, back, bottom, top, sphere = [], [], [], [], [], [], []
+
+#INLET, OUTLET, WALL, CYLINDER = 2, 3, 4, 5 # Marker values
+#inflow, outflow, walls, cyl = [], [], [], []
+
+if mesh_comm.rank == model_rank:
+    # Get boundaries and loop over all
+    boundaries = gmsh.model.getBoundary(volumes, oriented = False)
+    for boundary in boundaries:
+        com = gmsh.model.occ.getCenterOfMass(boundary[0], boundary[1])
+        if np.allclose(com, [0, H/2, D/2]):
[…]

### 2025-01-25 scripts/utilities/local_imports.py

@@ -1,0 +1,10 @@
+import ufl
+import typing
+import numpy.typing
+
+import numpy     as np
+import dolfinx   as dfx
+
+from ufl      import inner, grad, div, dot, dx
+from mpi4py   import MPI
+from petsc4py import PETSc

### 2025-01-25 scripts/utilities/normals_and_tangents.py

@@ -1,0 +1,248 @@
+# Copyright (C) 2023 Jørgen S. Dokken and Halvor Herlyng
+#
+# SPDX-License-Identifier:    MIT
+
+import ufl
+import meshio
+
+import numpy   as np
+import dolfinx as dfx
+
+from mpi4py   import MPI
+from petsc4py import PETSc
+
+from dolfinx.fem.petsc     import assemble_matrix, assemble_vector, apply_lifting, set_bc
+from dolfinx.cpp.fem.petsc import insert_diagonal
+
+def tangential_projection(u: ufl.Coefficient, n: ufl.FacetNormal) -> ufl.Coefficient:
+    """
+    See for instance:
+    https://link.springer.com/content/pdf/10.1023/A:1022235512626.pdf
+    """
+    return (ufl.Identity(u.ufl_shape[0]) - ufl.outer(n, n)) * u
+
+def facet_vector_approximation(V: dfx.fem.FunctionSpace,
+                               mt: dfx.mesh.MeshTags | None = None,
+                               mt_id: int | tuple[int] | None = None,
+                               tangent: bool = False,
+                               interior: bool = False,
+                               jit_options: dict | None = None,
+                               form_compiler_options: dict | None = None) -> dfx.fem.Function:
+    """
+    Approximate the facet normal or tangent on a surface by projecting it into the function space for a set of facets.
+
+    Args:
+        V: The function space to project into. Needs to be defined on discontinuous elements.
+
+        mt: The `dolfinx.mesh.MeshTags` containing facet markers.
+
+        mt_id: The id for the facets in `mt` we want to represent the normal or tangent on.
+
+        tangent: To approximate the tangent of the facets set this flag to `True`.
+
+        jit_options: Parameters used in CFFI JIT compilation of C code generated by FFCx.
+            See https://github.com/FEniCS/dolfinx/blob/main/python/dolfinx/jit.py#L22-L37
+            for all available parameters. Takes priority over all other parameter values.
+
+        form_compiler_options: Parameters used in FFCx compilation of this form. Run `ffcx - -help` at
+            the commandline to see all available options. Takes priority over all
+            other parameter values, except for `scalar_type` which is determined by
[…]

### 2025-01-25 scripts/velocity_profiles.py

@@ -1,0 +1,84 @@
+import vtk # Needed for pyvista
+
+import numpy   as np
+import pyvista as pv
+import dolfinx as dfx
+import adios4dolfinx     as a4d
+import matplotlib.pyplot as plt
+
+from scipy.interpolate import interp1d
+from mpi4py    import MPI
+from basix.ufl import element
+
+# Set latex text properties
+plt.rcParams.update({
+    "text.usetex": True,
+    "font.family": "serif"
+})
+
+comm = MPI.COMM_WORLD # MPI Communicator
+gm   = dfx.mesh.GhostMode.shared_facet
+
+# Read velocity data
+filename = "../output/checkpoints/pressure/model_A/velocity_data_dt=0.02252"
+mesh = a4d.read_mesh(comm=comm, file=filename, engine="BP4", ghost_mode=gm)
+W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), 1, shape=(3,))) # DG1 vector function space
+u = dfx.fem.Function(W)
+a4d.read_function(u=u, filename=filename, engine="BP4")
+
+# Interpolate velocity into continuous P2 space
+V = dfx.fem.functionspace(mesh=mesh, element=element("Lagrange", mesh.basix_cell(), 2, shape=(3,)))
+v = dfx.fem.Function(V)
+v.interpolate(u)
+
+u_x = v.sub(0).collapse().x.array
+u_x *= 1000 # scale to micrometers/s
+cells, types, x = dfx.plot.vtk_mesh(V)
+grid = pv.UnstructuredGrid(cells, types, x)
+grid.point_data["u_x"] = u_x
+grid.set_active_scalars("u_x")
+a = [0.166102, 0.140979, 0.138141]
+b = [0.16292, 0.149926, 0.23489]
+data = grid.sample_over_line(pointa=a, pointb=b)
+z_start = data.bounds[4]
+z_end = data.bounds[5]
+z_coords = np.linspace(z_start, z_end, len(data.active_scalars))
+z_coords *= 1000 # scale to micrometers
+interp = interp1d(z_coords, data.active_scalars, kind='cubic')
+
+# Plot
+fig, ax = plt.subplots(figsize=([12, 8]))
+ax.plot(interp(z_coords), z_coords, color='b', linewidth=3, label='Line 1')
+ax.plot(np.zeros_like(z_coords), z_coords, 'k--')
[…]

### 2025-01-25 scripts/visualization/compare_concentrations.py

@@ -1,36 +1,0 @@
-import dolfinx as dfx
-import adios4dolfinx as a4d
-from mpi4py.MPI import COMM_WORLD as comm
-from basix.ufl import element
-
-ghost_mode = dfx.mesh.GhostMode.shared_facet
-file_A = '../output/checkpoints/transport/model_A/D1/concentration_inj=anterior_dorsal/'
-file_C = '../output/checkpoints/transport/model_C/D1/concentration_inj=anterior_dorsal/'
-mesh = a4d.read_mesh(comm, file_A, "BP4", ghost_mode)
-el_dg = element("DG", mesh.basix_cell(), 1)
-el_cg = element("Lagrange", mesh.basix_cell(), 1)
-DG1 = dfx.fem.functionspace(mesh, el_dg)
-P1  = dfx.fem.functionspace(mesh, el_cg)
-c_A = dfx.fem.Function(DG1)
-c_C = dfx.fem.Function(DG1)
-c_diff = dfx.fem.Function(DG1)
-c_out = dfx.fem.Function(P1)
-
-read_time = 0
-a4d.read_function(c_A, file_A, time=read_time)
-a4d.read_function(c_C, file_C, time=read_time)
-c_diff.x.array[:] = c_A.x.array.copy() - c_C.x.array.copy()
-c_out.interpolate(c_diff)
-xdmf_c_diff = dfx.io.XDMFFile(comm, 'c_diff.xdmf', 'w')
-xdmf_c_diff.write_mesh(mesh)
-xdmf_c_diff.write_function(c_out, read_time)
-for _ in range(199):
-    read_time += 1
-    print(f"Time = {read_time}")
-    a4d.read_function(c_A, file_A, time=read_time)
-    a4d.read_function(c_C, file_C, time=read_time)
-    c_diff.x.array[:] = c_A.x.array.copy() - c_C.x.array.copy()
-    print(f"Maximum concentration difference: {c_diff.x.array.max()}")
-    c_out.interpolate(c_diff)
-    xdmf_c_diff.write_function(c_out, read_time)
-xdmf_c_diff.close()

### 2025-01-25 scripts/visualization/concentration_profiles.py

@@ -1,150 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from scipy.interpolate import interp1d
-from mpi4py    import MPI
-from basix.ufl import element
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": True,
-    "font.family": "serif"
-})
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-
-# Read velocity data
-filename = "../output/checkpoints/transport/DG1/pressure/model_C/D1/concentration_inj=middle_dorsal_posterior"
-mesh = a4d.read_mesh(comm=comm, file=filename, engine="BP4", ghost_mode=gm)
-W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), 1)) # DG1 function space
-u = dfx.fem.Function(W)
-a4d.read_function(u=u, filename=filename, engine="BP4", time=10000)
-
-# Interpolate velocity into continuous P2 space
-V = dfx.fem.functionspace(mesh=mesh, element=element("Lagrange", mesh.basix_cell(), 2))
-c = dfx.fem.Function(V)
-c.interpolate(u)
-
-a = [0.135448, 0.140393, 0.176273]
-b = [0.329539, 0.140393, 0.176273]
-cells, types, x = dfx.plot.vtk_mesh(V)
-grid = pv.UnstructuredGrid(cells, types, x)
-grid.point_data["c"] = c.x.array
-grid.set_active_scalars("c")
-data = grid.sample_over_line(pointa=a, pointb=b)
-x_start = data.bounds[0]
-x_end = data.bounds[1]
-x_coords = np.linspace(x_start, x_end, len(data.active_scalars))
-x_coords *= 1000 # scale to micrometers
-interp = interp1d(x_coords, data.active_scalars, kind='cubic')
-fig, ax = plt.subplots(figsize=([12, 8]))
-ax.plot(x_coords, interp(x_coords), color='r', linewidth=3, label=r'$D_1$')
-
-
-# New timestep
-filename = "../output/checkpoints/transport/DG1/pressure/model_C/D2/concentration_inj=middle_dorsal_posterior"
[…]

### 2025-01-25 scripts/visualization/create_colormap.py

@@ -1,102 +1,0 @@
-def register_colormaps() -> None:
-    import matplotlib
-    import matplotlib.colors
-
-    colors_greens = [[1, 0.984314, 0.901961],
-            [0.960784, 0.94902, 0.670588],
-            [0.886275, 0.921569, 0.533333],
-            [0.784314, 0.878431, 0.396078],
-            [0.666667, 0.839216, 0.294118],
-            [0.556863, 0.8, 0.239216],
-            [0.431373, 0.760784, 0.160784],
-            [0.317647, 0.721569, 0.113725],
-            [0.211765, 0.678431, 0.082353],
-            [0.109804, 0.631373, 0.05098],
-            [0.082353, 0.588235, 0.082353],
-            [0.109804, 0.54902, 0.152941],
-            [0.113725, 0.521569, 0.203922],
-            [0.117647, 0.490196, 0.243137],
-            [0.117647, 0.45098, 0.270588],
-            [0.113725, 0.4, 0.278431],
-            [0.109804, 0.34902, 0.278431]
-    ]
-
-    colors_wgk = [[1, 1, 1],
-              [0.901961, 0.941176, 0.796078],
-              [0.8, 0.878431, 0.580392],
-              [0.701961, 0.815686, 0.364706],
-              [0.6, 0.752941, 0.145098],
-              [0.498039, 0.690196, 0],
-              [0.396078, 0.627451, 0],
-              [0.294118, 0.564706, 0],
-              [0.196078, 0.501961, 0],
-              [0.094118, 0.439216, 0],
-              [0, 0.376471, 0],
-              [0, 0.313725, 0],
-              [0, 0.25098, 0],
-              [0, 0.188235, 0],
-              [0, 0.12549, 0],
-              [0, 0.062745, 0],
-              [0, 0, 0]
-    ]
-    # Refine color data
-    import numpy as np
-    import scipy.interpolate
-    arr = np.array(colors_wgk)
-    x = np.linspace(0, 1, len(arr[:, 0]))
-    interp_R = scipy.interpolate.interp1d(x, arr[:, 0])
-    interp_G = scipy.interpolate.interp1d(x, arr[:, 1])
-    interp_B = scipy.interpolate.interp1d(x, arr[:, 2])
-    x_fine = np.linspace(0, 1, 101)
-
-    refined_colors = np.zeros(shape=(len(x_fine), 3))
[…]

### 2025-01-25 scripts/visualization/gifs_concentration.py

@@ -1,67 +1,0 @@
-import vtk # Needed for pyvista
-
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-
-from mpi4py    import MPI
-from basix.ufl import element
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # finite element degree
-D_num = 2
-inj_site = 'posterior_dorsal'
-read_file = f"../output/checkpoints/transport/DG{k}/pressure/model_C/D{D_num}/concentration_inj={inj_site}"
-mesh = a4d.read_mesh(comm=comm, file=read_file, engine="BP4", ghost_mode=gm)
-plotter = pv.Plotter(window_size=([1280, 720]))
-# Get mesh properties
-x_geo = mesh.geometry.x
-
-x_min = x_geo[:, 0].min()
-x_max = x_geo[:, 0].max()
-x_mid = (x_min + x_max) / 2
-
-y_max = x_geo[:, 1].max()
-
-z_min = x_geo[:, 2].min()
-z_max = x_geo[:, 2].max()
-z_mid = (z_min + z_max) / 2
-plotter.camera.position    = (x_mid, 0, z_mid*1.1)
-plotter.camera.focal_point = (x_mid, y_max, z_mid)
-plotter.camera.zoom(0.267)
-
-
-skip = 50
-dt = 0.02252
-fps = 40
-plotter.open_gif(f"../output/illustrations/DG{k}_Diff{D_num}_concentration_inj={inj_site}gi_fps={fps}.gif", fps=fps)#int(1/dt)//skip)
-f = 2.22 # Cardiac frequency [Hz]
-period = 1 / f
-T  = 1000*period
-dt = period / 20
-num_steps = int(T / dt)
-
-W_scalar = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), k)) # DG function space
-c = dfx.fem.Function(W_scalar)
-cells, types, x = dfx.plot.vtk_mesh(mesh) if k==0 else dfx.plot.vtk_mesh(W_scalar) 
-function_grid = pv.UnstructuredGrid(cells, types, x)
-# Set colormap
-from create_colormap import register_colormaps
-register_colormaps()
-cmap = "wgk"
-for i in range(0, num_steps, skip):
-    a4d.read_function(u=c, filename=read_file, engine="BP4", time=i)
-    if k==0:
[…]

### 2025-01-25 scripts/visualization/import_image.py

@@ -1,38 +1,0 @@
-import matplotlib.pyplot as plt
-from mpl_toolkits.axes_grid1 import ImageGrid
-import typer
-from typing import List
-
-def compare_models(modela:str, modelb:str, times:List[int]):
-
-    fig = plt.figure(figsize=(5., 9.), frameon=True)
-    grid = ImageGrid(fig, 111, nrows_ncols=(len(times), 3), axes_pad=0.0)
-    for i, t in enumerate(times):
-        for j,m in enumerate([modela, modelb, "diff"]):
-            fn = f"plots/{m}/{m}_{t}.png"
-            if m=="diff":
-                fn = f"plots/comparisons/{modela}_{modelb}/{modela}_{modelb}_diff_{t}.png"
-            img = plt.imread(fn)
-            ax = grid.axes_row[i][j]
-            ax.axis('off')
-            if i + 1==len(times):
-                ax.imshow(img[100:-10,140:-140])
-            else:
-                ax.imshow(img[100:-100,140:-140])
-
-        ax = grid.axes_row[i][0]
-        ax.text(-0.08, 0.5, f"{time_str(t)} h", rotation=90, va="center",
-                    transform=ax.transAxes, fontsize=6)
-        
-    descr = [read_config(f"configfiles/{m}.yml")["description"] for m in [modela, modelb]]
-        
-    for j,m in enumerate(descr +  ["difference"]):
-        ax = grid.axes_row[0][j]
-        ax.text(0.5, 1.05, m, ha="center", transform=ax.transAxes, fontsize=6)
-
-
-    plt.savefig(f"plots/comparisons/{modela}_{modelb}/{modela}_{modelb}.png",
-                 dpi=300, bbox_inches="tight",)
-
-if __name__ == "__main__":
-    typer.run(compare_models)

### 2025-01-25 scripts/visualization/plot_ROI_time_to_threshold.py

@@ -1,117 +1,0 @@
-import vtk # Needed for pyvista
-import ufl
-
-import numpy   as np
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py       import MPI
-from basix.ufl    import element
-from imports.mesh import create_ventricle_volumes_meshtags
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": False,
-    "font.family": "serif"
-})
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-model_version = 'C'
-molecule = 'D3'
-mesh_input_filename = "output/flow/checkpoints/pressure+original/model_C/velocity_data_dt=0.02252"
-mesh = a4d.read_mesh(comm=comm, filename=mesh_input_filename, engine="BP4", ghost_mode=gm)
-
-# Get mesh properties
-x_geo = mesh.geometry.x
-
-x_min = x_geo[:, 0].min()
-x_max = x_geo[:, 0].max()
-x_mid = (x_min + x_max) / 2
-
-y_max = x_geo[:, 1].max()
-
-z_min = x_geo[:, 2].min()
-z_max = x_geo[:, 2].max()
-z_mid = (z_min + z_max) / 2
-
-# Set up unstructured grids with data
-W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), k)) # DG1 function space
-c_in = dfx.fem.Function(W) # Concentration finite element function
-cells, types, x = dfx.plot.vtk_mesh(W)
-
-# Create meshtags and calculate ROI volumes
-mt, ROI_tags = create_ventricle_volumes_meshtags(mesh, mod=True)
-dx = ufl.Measure('dx', domain=mesh, subdomain_data=mt)
-volumes_mod = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=MPI.SUM) for tag in ROI_tags]
-mt, ROI_tags = create_ventricle_volumes_meshtags(mesh, mod=False)
-dx = ufl.Measure('dx', domain=mesh, subdomain_data=mt)
-volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=MPI.SUM) for tag in ROI_tags]
-
[…]

### 2025-01-25 scripts/visualization/plot_compare_cilia_regions.py

@@ -1,118 +1,0 @@
-import vtk # Needed for pyvista
-import ufl
-
-import numpy   as np
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py       import MPI
-from imports.mesh import create_ventricle_volumes_meshtags
-
-# Set matplotlib properties
-plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
-    "axes.spines.top" : False,
-    "axes.spines.right" : False
-})
-plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-model_version = 'C'
-original_mesh_input_filename = f"output/flow/checkpoints/variable_tau/pressure+original/model_{model_version}/velocity_data_dt=0.02252"
-mesh = a4d.read_mesh(comm=comm, filename=original_mesh_input_filename, engine="BP4", ghost_mode=gm)
-ct, ROI_tags = create_ventricle_volumes_meshtags(mesh)
-dx = ufl.Measure('dx', domain=mesh, subdomain_data=ct)
-volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=MPI.SUM) for tag in ROI_tags]
-volumes[3] += volumes[2]+volumes[1]+volumes[0]
-
-# Load data c_hat, the total concenctration in each ROI
-with open(f"output/transport/results/variable_tau/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_original    = np.load(file)
-with open(f"output/transport/results/variable_tau+rm_dorsal/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_dorsal  = np.load(file)
-with open(f"output/transport/results/variable_tau+rm_ventral/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_ventral = np.load(file)
[…]

### 2025-01-25 scripts/visualization/plot_compare_geometry.py

@@ -1,152 +1,0 @@
-import ufl
-
-import numpy   as np
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py       import MPI
-from imports.mesh import create_ventricle_volumes_meshtags
-
-"""
-Plot and compare results for the original ventricles mesh and the (more) shrunk ventricles mesh. The original ventricles mesh
-is based on the initial surface geometry retrieved from the Jurisch-Yaksi lab, the shrunk versions are the original mesh
-modified using the "shrink" mesh modifier in Blender. 
-
-Three different regions of the mesh were modified, and four modified meshes are considered:
-    - fore-shrunk: a mesh with shrinkage of the connection between the telencephalic ventricle and the diencephalic ventricle 
-    - middle-shrunk: a mesh with shrinkage of the diencephalic ventricle in the lateral direction (shrinkage along y-axis of mesh)
-    - fore-shrunk: a mesh with shrinkage of the connection between the diencephalic ventricle and the rhombencephalic ventricle
-    - fore+middle+hind shrunk: a mesh with all the three modifications outlined above performed
-
-Everything in this script with a subscript 1 is an attribute/variable of the original mesh.
-Everything in this script with a subscript 2 is an attribute/variable of the fore-shrunk mesh.
-Everything in this script with a subscript 3 is an attribute/variable of the middle-shrunk mesh.
-Everything in this script with a subscript 4 is an attribute/variable of the hind-shrunk mesh.
-Everything in this script with a subscript 5 is an attribute/variable of the fore+middle+hind-shrunk mesh.
-
-Author: Halvor Herlyng, 2024.
-"""
-
-# Set matplotlib properties
-plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
-    "axes.spines.top" : False,
-    "axes.spines.right" : False
-})
[…]

### 2025-01-25 scripts/visualization/plot_compare_models.py

@@ -1,146 +1,0 @@
-import ufl
-
-import numpy   as np
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py       import MPI
-from imports.mesh import create_ventricle_volumes_meshtags
-
-# Set matplotlib properties
-plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
-    "axes.spines.top" : False,
-    "axes.spines.right" : False
-})
-plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-molecule = 'D3'
-tau_version  = 'original_tau'
-tau_version  = 'variable_tau'
-mesh_version = 'original'
-mesh_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+{mesh_version}/model_C/velocity_data_dt=0.02252"
-mesh = a4d.read_mesh(comm=comm, filename=mesh_input_filename, engine="BP4", ghost_mode=gm)
-
-# Create meshtags and calculate ROI volumes
-mt, ROI_tags = create_ventricle_volumes_meshtags(mesh)
-dx = ufl.Measure('dx', domain=mesh, subdomain_data=mt)
-volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=MPI.SUM) for tag in ROI_tags]
-volumes[3] += volumes[2]+volumes[1]+volumes[0] # Add ROI 1, 2, 3 volumes to ROI 4 volume
-
-# Load data c_bar, the total concenctration in each ROI
-with open(f"./output/transport/results/original_tau/{mesh_version}/log_model_B_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
-    c_bar_B = np.load(file)
-with open(f"./output/transport/results/{tau_version}/{mesh_version}/log_model_C_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
-    c_bar_C = np.load(file)
-
-# Scale the total concentrations in the ROIs by the volume of the respective ROI
-for i in ROI_tags: 
[…]

### 2025-01-25 scripts/visualization/plot_experiments_compare_control_mutant.py

@@ -1,122 +1,0 @@
-import numpy   as np
-import pandas  as pd
-import seaborn as sns
-import matplotlib.pyplot as plt
-
-from scipy.io import loadmat
-from scipy.stats import ranksums, mannwhitneyu
-
-# Set matplotlib properties
-plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
-    "axes.spines.top" : False,
-    "axes.spines.right" : False
-})
-plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
-
-# Set data directory and load .mat files
-data_dir = "./data_photoconversion/aggregated_data/"
-metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
-colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
-control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data
-mutant  = loadmat(data_dir+"mutant_data")['mut'] # The mutant fish cohort photoconversion data
-ttt_control = loadmat(data_dir+"tt_control")['tt_control'][0][0] # Time-to-threshold data for the control cohort
-ttt_mutant  = loadmat(data_dir+"tt_mutant")['tt_mutant'][0][0] # Time-to-threshold data for the mutant cohort 
-fps = metadata['metadata'][0][0][2][0][0] # Extract fps from metadata
-ROI_tags = [1, 2, 3, 4, 5, 6]
-
-# Clean ttt data and store it in dataframes
-df_control = pd.DataFrame({tag: np.array(arr, dtype=np.float64).flatten() for tag, arr in zip(ROI_tags, ttt_control)})
-df_mutant  = pd.DataFrame({tag: np.array(arr, dtype=np.float64).flatten() for tag, arr in zip(ROI_tags, ttt_mutant )})
-
-# Get the number of timesteps
-num_timesteps = control.shape[2]
-c_threshold1 = 0.25 # threshold value used to calculate "time to threshold" in ROIs 1-4
-c_threshold2 = 0.10 # threshold value used to calculate "time to threshold" in ROIs 5-6
-times = 1/fps*np.arange(num_timesteps)
-
-#-------- Plot the figures --------#
[…]

### 2025-01-25 scripts/visualization/plot_experiments_separate.py

@@ -1,63 +1,0 @@
-import numpy   as np
-import matplotlib.pyplot as plt
-
-from scipy.io import loadmat
-
-# Set matplotlib properties
-plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
-    "axes.spines.top" : False,
-    "axes.spines.right" : False
-})
-plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
-
-# Set data directory and load .mat files
-data_dir = "./data_photoconversion/aggregated_data/"
-metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
-colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
-control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data
-mutant  = loadmat(data_dir+"mutant_data")['mut'] # The mutant fish cohort photoconversion data
-tt_control = loadmat(data_dir+"tt_control")['tt_control'][0][0] # Time-to-threshold data for the control cohort
-tt_mutant  = loadmat(data_dir+"tt_mutant")['tt_mutant'][0][0] # Time-to-threshold data for the mutant cohort 
-fps = metadata['metadata'][0][0][2][0][0] # Extract fps from metadata
-
-# Get the number of timesteps
-num_timesteps = control.shape[2]
-times = 1/fps*np.arange(num_timesteps)
-ROI_idx = range(6)
-
-# Plot the figures
-fig1, ax1 = plt.subplots(num=1, figsize=([18, 14])) # Plot for the control data
-fig2, ax2 = plt.subplots(num=2, figsize=([18, 14])) # Plot for the mutant data
-
-lw = 4.5 # linewidth
-
-for i in ROI_idx:
-    # Plot control data
-    y = np.mean(control[:, i, :], axis=0)
-    err = np.std(control[:, i, :], axis=0)/np.sqrt(control.shape[0])
-    ax1.plot(times, y, label=f'ROI {i+1}', color=colors[i], linewidth=lw)
-    ax1.fill_between(times, y-err, y+err, color=colors[i], alpha=0.25)
-
-    # Plot mutant data
-    y = np.mean(mutant[:, i, :], axis=0)
[…]

### 2025-01-25 scripts/visualization/plot_mean_concentrations.py

@@ -1,202 +1,0 @@
-import vtk # Needed for pyvista
-import ufl
-import time
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py    import MPI
-from basix.ufl import element
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": False,
-    "font.family": "serif"
-})
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-mesh_input_filename = "output/checkpoints/pressure/model_C/velocity_data_dt=0.02252"#f"./output/checkpoints/transport/DG{k}/pressure/model_C/D3/concentration_inj=middle_dorsal_posterior"
-mesh = a4d.read_mesh(comm=comm, file=mesh_input_filename, engine="BP4", ghost_mode=gm)
-
-DEFAULT   = 2
-MIDDLE    = 3
-ANTERIOR  = 4
-POSTERIOR = 5
-
-def create_ventricle_volumes_meshtags(mesh: dfx.mesh.Mesh):
-    z_min = mesh.geometry.x[:, 2].min()
-    z_max = mesh.geometry.x[:, 2].max()
-    z_mid = (z_min + z_max) / 2
-    a1 = [0.165, 0.0, z_mid]
-    b1 = [0.125, 0.0, z_max*0.78]
-
-    a2 = [0.33, 0.0, z_mid*0.8]
-    b2 = [0.345, 0.0, z_max*0.75]
-
-    line1 = lambda t: a1[2] + (b1[2] - a1[2])/(b1[0] - a1[0])*(t - a1[0])
-    line2 = lambda t: a2[2] + (b2[2] - a2[2])/(b2[0] - a2[0])*(t - a2[0])
-
-    def middle_ventricle(x):
-        return np.logical_and(x[2] >= line1(x[0]), x[2] >= line2(x[0]))
-
-    def anterior_ventricle(x):
-        return x[2] < line1(x[0])
-
-    def posterior_ventricle(x):
-        return x[2] < line2(x[0])
-
-    tdim = mesh.topology.dim
-    ## TODO: update to using midpoint coordinate of cells located
-    middle_cells = dfx.mesh.locate_entities(mesh, tdim, middle_ventricle)
[…]

### 2025-01-25 scripts/visualization/single_slice.py

@@ -1,88 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py    import MPI
-from basix.ufl import element
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": True,
-    "font.family": "serif"
-})
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-input_filename = f"../output/checkpoints/transport/DG{k}/pressure/model_C/D1/concentration_inj=middle_dorsal_posterior"
-mesh = a4d.read_mesh(comm=comm, file=input_filename, engine="BP4", ghost_mode=gm)
-
-# Get mesh properties
-x_geo = mesh.geometry.x
-
-x_min = x_geo[:, 0].min()
-x_max = x_geo[:, 0].max()
-x_mid = (x_min + x_max) / 2
-
-y_max = x_geo[:, 1].max()
-
-z_min = x_geo[:, 2].min()
-z_max = x_geo[:, 2].max()
-z_mid = (z_min + z_max) / 2
-
-a1 = [0.165, 0.0, z_mid]
-b1 = [0.125, 0.0, z_max*0.78]
-
-a2 = [0.33, 0.0, z_mid*0.8]
-b2 = [0.345, 0.0, z_max*0.75]
-
-# Set up unstructured grids with data
-W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), k)) # DG1 function space
-cells, types, x = dfx.plot.vtk_mesh(W)
-grid = pv.UnstructuredGrid(cells, types, x)
-
-c_in = dfx.fem.Function(W)
-a4d.read_function(u=c_in, filename=input_filename, engine="BP4", time=0)
-grid.point_data["c"] = c_in.x.array.real
-grid.set_active_scalars("c")
-
-
-# Create plot object
-plotter = pv.Plotter(window_size=[3200, 1400], border=False)
-
-# Set colormap
-from create_colormap import register_colormaps
-register_colormaps()
-cmap = "wgk"
-
-# Colorbar arguments
-sargs = dict(
-    title_font_size=100,
-    label_font_size=150,
-    shadow=True,
-    n_labels=2,
-    italic=True,
-    fmt="%.1g",
-    font_family="times",
[…]

### 2025-01-25 scripts/visualization/slice_time_to_threshold.py

@@ -1,80 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py    import MPI
-from basix.ufl import element
-
-""" Visualize concentration slices in a 3x3 figure. """
-
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": True,
-    "font.family": "serif"
-})
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-model_version = 'C'
-molecule = 'D3'
-tau_version = 'variable_tau'
-input_filename = f"../output/flow/checkpoints/{tau_version}/pressure+original/model_C/velocity_data_dt=0.02252/"
-mesh = a4d.read_mesh(comm=comm, filename=input_filename, engine="BP4", ghost_mode=gm)
-
-# Get mesh properties
-x_geo = mesh.geometry.x
-
-x_min = x_geo[:, 0].min()
-x_max = x_geo[:, 0].max()
-x_mid = (x_min + x_max) / 2
-
-y_max = x_geo[:, 1].max()
-
-z_min = x_geo[:, 2].min()
-z_max = x_geo[:, 2].max()
-z_mid = (z_min + z_max) / 2
-
-# Set up unstructured grids with data
-W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), k)) # DGk function space
-cells, types, x = dfx.plot.vtk_mesh(W)
-grid = pv.UnstructuredGrid(cells, types, x)
-
-# Load time to threshold function values
-c_in = dfx.fem.Function(W)
-input_filename = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_{molecule}_DG1_pressureBC/t_hat/"
-a4d.read_function(u=c_in, filename=input_filename, engine="BP4", time=0)
-grid.point_data["c"] = c_in.x.array.real
-grid.set_active_scalars("c")
-grid = grid.threshold(0.0) # Remove all points with values below zero (points that never reached the threshold)
-grid = grid.threshold(840, invert=True) # Clip off posterior edge providing spurious coloring of cells
-
-# Create plot object
-plotter = pv.Plotter(window_size=[1600, 900], border=False)
-
-# Set colormap
[…]

### 2025-01-25 scripts/visualization/slices_concentration.py

@@ -1,128 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py    import MPI
-from basix.ufl import element
-
-""" Visualize concentration slices in a 3x3 figure. """
-
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": True,
-    "font.family": "serif"
-})
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-k = 1 # element degree
-model_version = 'C'
-tau_version = 'variable_tau'
-input_filename1 = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_D1_DG1_pressureBC/checkpoints/concentration_snapshots/"
-input_filename2 = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_D2_DG1_pressureBC/checkpoints/concentration_snapshots/"
-input_filename3 = f"../output/transport/results/{tau_version}/original/log_model_{model_version}_D3_DG1_pressureBC/checkpoints/concentration_snapshots/"
-mesh1 = a4d.read_mesh(comm=comm, filename=input_filename1, engine="BP4", ghost_mode=gm)
-mesh2 = a4d.read_mesh(comm=comm, filename=input_filename2, engine="BP4", ghost_mode=gm)
-mesh3 = a4d.read_mesh(comm=comm, filename=input_filename3, engine="BP4", ghost_mode=gm)
-
-# Get mesh properties
-x_geo = mesh1.geometry.x
-
-x_min = x_geo[:, 0].min()
-x_max = x_geo[:, 0].max()
-x_mid = (x_min + x_max) / 2
-
-y_max = x_geo[:, 1].max()
-
-z_min = x_geo[:, 2].min()
-z_max = x_geo[:, 2].max()
-z_mid = (z_min + z_max) / 2
-
-# Set up unstructured grids with data
-W1 = dfx.fem.functionspace(mesh=mesh1, element=element("DG", mesh1.basix_cell(), k)) # DG1 function space
-W2 = dfx.fem.functionspace(mesh=mesh2, element=element("DG", mesh1.basix_cell(), k)) # DG1 function space
[…]

### 2025-01-25 scripts/visualization/slices_concentration_varying_inj_site.py

@@ -1,119 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from mpi4py    import MPI
-from basix.ufl import element
-
-import matplotlib as mpl
-import matplotlib.colors
-colors = [[14, 28, 31], [14, 29, 32], [15, 30, 33], [15, 32, 34], [16, 33, 36], [16, 34, 37], [16, 35, 38], [17, 37, 39], [17, 38, 40], [18, 39, 42], [18, 40, 43], [18, 42, 44], [19, 43, 45], [19, 44, 46], [19, 45, 47], [20, 47, 48], [20, 48, 49], [20, 49, 49], [20, 50, 50], [21, 51, 51], [21, 52, 52], [21, 54, 52], [21, 55, 53], [21, 56, 54], [22, 57, 55], [22, 58, 56], [22, 59, 56], [22, 60, 57], [22, 61, 58], [23, 62, 58], [23, 63, 59], [23, 64, 59], [23, 65, 60], [23, 66, 61], [23, 67, 61], [24, 68, 62], [24, 69, 63], [24, 70, 63], [24, 71, 64], [24, 72, 64], [25, 73, 65], [25, 75, 66], [25, 76, 66], [26, 78, 67], [26, 79, 67], [26, 80, 68], [27, 82, 68], [27, 83, 69], [27, 85, 69], [27, 86, 70], [28, 88, 70], [28, 89, 71], [28, 90, 71], [28, 91, 71], [28, 92, 71], [28, 93, 71], [29, 94, 71], [29, 95, 71], [29, 96, 71], [29, 97, 71], [29, 98, 71], [29, 99, 71], [29, 100, 71], [29, 101, 71], [29, 102, 71], [29, 103, 71], [29, 104, 71], [29, 105, 71], [30, 106, 70], [30, 107, 70], [30, 108, 70], [30, 109, 70], [30, 110, 70], [30, 111, 70], [30, 112, 69], [30, 113, 69], [30, 114, 69], [30, 115, 69], [30, 116, 68], [30, 117, 68], [30, 118, 67], [30, 119, 67], [30, 119, 66], [30, 120, 66], [30, 121, 65], [30, 122, 64], [30, 122, 64], [30, 123, 63], [30, 124, 63], [30, 125, 62], [30, 125, 61
[…]

### 2025-01-25 scripts/visualization/velocity_profiles.py

@@ -1,84 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-import matplotlib.pyplot as plt
-
-from scipy.interpolate import interp1d
-from mpi4py    import MPI
-from basix.ufl import element
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": True,
-    "font.family": "serif"
-})
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-
-# Read velocity data
-filename = "../output/checkpoints/pressure/model_A/velocity_data_dt=0.02252"
-mesh = a4d.read_mesh(comm=comm, file=filename, engine="BP4", ghost_mode=gm)
-W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), 1, shape=(3,))) # DG1 vector function space
-u = dfx.fem.Function(W)
-a4d.read_function(u=u, filename=filename, engine="BP4")
-
-# Interpolate velocity into continuous P2 space
-V = dfx.fem.functionspace(mesh=mesh, element=element("Lagrange", mesh.basix_cell(), 2, shape=(3,)))
-v = dfx.fem.Function(V)
-v.interpolate(u)
-
-u_x = v.sub(0).collapse().x.array
-u_x *= 1000 # scale to micrometers/s
-cells, types, x = dfx.plot.vtk_mesh(V)
-grid = pv.UnstructuredGrid(cells, types, x)
-grid.point_data["u_x"] = u_x
-grid.set_active_scalars("u_x")
-a = [0.166102, 0.140979, 0.138141]
-b = [0.16292, 0.149926, 0.23489]
-data = grid.sample_over_line(pointa=a, pointb=b)
-z_start = data.bounds[4]
-z_end = data.bounds[5]
-z_coords = np.linspace(z_start, z_end, len(data.active_scalars))
-z_coords *= 1000 # scale to micrometers
-interp = interp1d(z_coords, data.active_scalars, kind='cubic')
-
-# Plot
-fig, ax = plt.subplots(figsize=([12, 8]))
-ax.plot(interp(z_coords), z_coords, color='b', linewidth=3, label='Line 1')
-ax.plot(np.zeros_like(z_coords), z_coords, 'k--')
[…]

### 2025-01-25 scripts/visualization/visualize.py

@@ -1,84 +1,0 @@
-import vtk # Needed for pyvista
-
-import numpy   as np
-import pyvista as pv
-import dolfinx as dfx
-import adios4dolfinx     as a4d
-
-from basix.ufl import element
-
-from mpi4py            import MPI
-
-comm = MPI.COMM_WORLD # MPI Communicator
-gm   = dfx.mesh.GhostMode.shared_facet
-filename = "../output/checkpoints/transport/model_C/D1/concentration_inj=posterior_dorsal"
-mesh = a4d.read_mesh(comm=comm, file=filename, engine="BP4", ghost_mode=gm)
-
-def visualize_concentration_slices(mesh: dfx.mesh.Mesh, input_filename: str, output_filename: str):
-    # Get mesh properties
-    x_geo = mesh.geometry.x
-
-    x_min = x_geo[:, 0].min()
-    x_max = x_geo[:, 0].max()
-    x_mid = (x_min + x_max) / 2
-
-    y_max = x_geo[:, 1].max()
-
-    z_min = x_geo[:, 2].min()
-    z_max = x_geo[:, 2].max()
-    z_mid = (z_min + z_max) / 2
-
-    # Set up unstructured grids with data
-    W = dfx.fem.functionspace(mesh=mesh, element=element("DG", mesh.basix_cell(), 1)) # DG1 function space
-    cells, types, x = dfx.plot.vtk_mesh(W)
-    timesteps = [0, 1000, 2000, 3000, 4000, 5000] # the timesteps to visualize
-    grids = [pv.UnstructuredGrid(cells, types, x) for _ in range(len(timesteps))]
-    for i in range(len(timesteps)):
-        c_in = dfx.fem.Function(W)
-        a4d.read_function(u=c_in, filename=input_filename, engine="BP4", time=timesteps[i])
-        c_in.x.array[np.where(c_in.x.array[:] <= 0)] = 0.0
-        grids[i].point_data["c"] = c_in.x.array.real
-        grids[i].set_active_scalars("c")
-
-    # Create plot object
-    plot_shape = (2, 3)
-    plotter = pv.Plotter(shape=plot_shape, window_size=[3000, 1400], border=False)
-    # cmap = "CET_D1A" # Cold-warm colormap
-    cmap = "speed"
-    
-    # Colorbar arguments
-    sargs = dict(
-        title_font_size=50,
-        label_font_size=40,
-        shadow=True,
-        n_labels=3,
-        italic=True,
[…]

### 2025-01-25 utilities/forcing_expressions.py

@@ -1,277 +1,0 @@
-import numpy as np
-import numpy.typing
-
-class PressureExpression:
-    """ A class used to generate expressions for pressure as a function of time.
-    """
-    def __init__(self, A: float) -> None:
-        self.t = 0.0 # Initial time
-        self.A = A   # Amplitude
-
-    def __call__(self, x):
-        return np.ones(x.shape[1]) * (-self.A * np.sin(2 * np.pi * self.t))
-
-class fExpressionSteady:
-
-    def __init__(self, mu: float, dim: int = 2):
-        self.mu = mu
-        self.dim = dim
-    
-    def __call__(self, x):
-        if self.dim == 2:
-            lapl_term_x = -self.mu * 2*np.pi**2 * np.sin(np.pi*x[0]) * np.sin(np.pi*x[1])
-            pres_term_x = 2*np.pi * np.cos(2*np.pi*x[0]) * np.sin(2*np.pi*x[1])
-            f_x         = -lapl_term_x + pres_term_x
-
-            lapl_term_y = self.mu * 2 * np.pi**2 * np.cos(np.pi*x[0]) * np.sin(np.pi*x[1])
-            pres_term_y = 2*np.pi * np.sin(2*np.pi*x[0]) * np.cos(2*np.pi*x[1])
-            f_y         = -lapl_term_y + pres_term_y
-
-            return np.stack((f_x, f_y))
-        elif self.dim == 3:
-            raise NotImplementedError("3D not implemented yet.")
-
-class gExpressionSteady:
-
-    def __init__(self, dim: int = 2):
-        self.dim = dim
-
-    def __call__(self, x):
-        if self.dim == 2:
-            return np.pi * np.cos(np.pi*x[1]) * (np.sin(np.pi*x[0]) - np.cos(np.pi*x[0]))
-
-        elif self.dim == 3:
-            raise NotImplementedError("3D not implemented yet.")
-
-# class tauExpressionSteady:
-
-
-class VelocityExpressionSteady:
-    def __init__(self, dim: int = 2):
-        self.dim = dim
-
-    def __call__(self, x):
-        if self.dim == 2:
-            return np.stack((np.sin(np.pi*x[0]) * np.sin(np.pi*x[1]),
-                            -np.cos(np.pi*x[0]) * np.sin(np.pi*x[1]),
-                            ))
-        else:
-            raise NotImplementedError("3D not implemented yet.")
-
[…]

### 2025-01-25 utilities/local_imports.py

@@ -1,10 +1,0 @@
-import ufl
-import typing
-import numpy.typing
-
-import numpy     as np
-import dolfinx   as dfx
-
-from ufl      import inner, grad, div, dot, dx
-from mpi4py   import MPI
-from petsc4py import PETSc

### 2025-01-25 utilities/mesh.py

@@ -1,1062 +1,0 @@
-import ufl
-import gmsh
-import meshio
-import numpy.typing
-
-import numpy     as np
-import dolfinx   as dfx
-
-from mpi4py   import MPI
-from pathlib  import Path
-
-# Mesh tags
-NOSLIP    = 1
-INLET     = 2
-OUTLET    = 3
-VOLUME    = 4
-LOWER     = 5
-UPPER     = 6
-ANTERIOR  = 7
-ANTERIOR2 = 8
-SLIP      = 9
-
-
-# Mesh tags for flow
-ANTERIOR_PRESSURE    = 2
-POSTERIOR_PRESSURE   = 3
-VOLUME               = 4
-MIDDLE_VENTRAL_CILIA = 5
-MIDDLE_DORSAL_CILIA  = 6
-ANTERIOR_CILIA       = 7
-ANTERIOR_CILIA2      = 8
-SLIP                 = 9
-
-# Mesh tags for transport
-ANTERIOR_DORSAL         = 11
-POSTERIOR_DORSAL        = 12
-MIDDLE_DORSAL_POSTERIOR = 13
-MIDDLE_DORSAL_ANTERIOR  = 14
-POSTERIOR_VENTRAL       = 15
-ANTERIOR_VENTRAL        = 16
-MIDDLE_VENTRAL          = 17
-
-def old_create_ventricle_volumes_meshtags(mesh: dfx.mesh.Mesh) -> tuple((dfx.mesh.MeshTags, list[int])):
-    """ Create cell meshtags for the different regions of interest (ROI)
-        used in the analysis and comparison with experimental data.
-
-    Parameters
-    ----------
-    mesh : dfx.mesh.Mesh
-        The brain ventricles mesh.
-
-    Returns
-    -------
-    tuple(dfx.mesh.MeshTags, list[int])
-        The celltags and a list of the integer tag values for each ROI.
-    """
-    
-    # Define the planes that separate the anterior, middle and posterior ventricles
-    z_min = mesh.comm.allreduce(mesh.geometry.x[:, 2].min(), op=MPI.MIN)
-    z_max = mesh.comm.allreduce(mesh.geometry.x[:, 2].max(), op=MPI.MAX)
-    z_mid = (z_min + z_max) / 2
-    a1 = [0.165, 0.0, z_mid]
-    b1 = [0.125, 0.0, z_max*0.78]
-
[…]

### 2025-01-25 utilities/mesh_cylinders.py

@@ -1,223 +1,0 @@
-import numpy as np
-import gmsh
-
-# --------------------------------------------------------------------
-def cylinder_gmsh(model: gmsh.model, length: float, radius: float):
-    #         B
-    #      C  0  A
-    #         D
-    fac = model.occ
-    
-    origin = fac.addPoint(-length/2, 0, 0)
-    A = fac.addPoint(-length/2, radius, 0)
-    B = fac.addPoint(-length/2, 0, radius)
-    C = fac.addPoint(-length/2, -radius, 0)
-    D = fac.addPoint(-length/2, 0, -radius)    
-
-    OA = fac.addLine(origin, A)
-    OB = fac.addLine(origin, B)
-    OC = fac.addLine(origin, C)
-    OD = fac.addLine(origin, D)
-
-    AOB = fac.addCircleArc(A, origin, B)
-    BOC = fac.addCircleArc(B, origin, C)
-    COD = fac.addCircleArc(C, origin, D)
-    DOA = fac.addCircleArc(D, origin, A)
-
-    ur = fac.addPlaneSurface([fac.addCurveLoop([AOB, -OB, OA])])
-    ul = fac.addPlaneSurface([fac.addCurveLoop([BOC, -OC, OB])])
-    ll = fac.addPlaneSurface([fac.addCurveLoop([COD, -OD, OC])])
-    lr = fac.addPlaneSurface([fac.addCurveLoop([DOA, -OA, OD])])
-
-    [fac.extrude([(2, s)], length, 0, 0) for s in (ur, ul, ll, lr)]
-    fac.synchronize()
-
-    fac.removeAllDuplicates()
-    fac.synchronize()
-    
-    vol = model.getEntities(3)
-    bdry = model.getBoundary(vol)
-
-    tol = 1E-10
-    normals = {}
-    left, right, wall = [], [], []
-    for dim, tag in bdry:
-        tag = abs(tag)
-        x = fac.getCenterOfMass(dim, tag)
-        # p = model.getParametrization(dim, tag, x)
-        # normal = model.getNormal(tag, p)
-        
-        if abs(x[0]+length/2) < tol:
-            left.append(tag)
-        elif abs(x[0]-length/2) < tol:
-            right.append(tag)
-        else:
-            wall.append(tag)
-
-    fac.synchronize()            
-    model.addPhysicalGroup(2, left, 1)
-    model.addPhysicalGroup(2, right, 2)
[…]

### 2025-01-25 utilities/mesh_gmsh.py

@@ -1,188 +1,0 @@
-import gmsh
-
-import numpy   as np
-import dolfinx as dfx
-
-from mpi4py import MPI
-
-# Mesh tags
-LEFT    = 1
-RIGHT   = 2
-FRONT   = 3
-BACK    = 4
-BOTTOM  = 5
-TOP     = 6
-
-# Rotated meshes
-def create_rectangle_mesh_gmsh(L: int=1, H: int=1, res: float=0.1, theta: float=np.pi/4) \
-                            -> tuple((dfx.mesh.Mesh, dfx.mesh.MeshTags)):
-    """
-    Create a rectangle of length L and height H, rotated theta degrees
-    around origin.
-
-
-    Parameters
-    ----------
-    L
-        Length of the box
-    H
-        Height of the box
-    res
-        Mesh resolution (uniform)
-    theta
-        Rotation angle
-    """
-    gmsh.initialize()
-
-    if MPI.COMM_WORLD.rank == 0:
-        gmsh.model.add("Rectangle")
-
-        # Create square
-        rectangle = gmsh.model.occ.addRectangle(0, 0, 0,
-                                                L, H)
-        gmsh.model.occ.synchronize()
-
-        # Find entity markers before rotation
-        surfaces = gmsh.model.occ.getEntities(dim=1)
-
-        left_wall   = []
-        right_wall  = []
-        bottom_wall = []
-        top_wall    = []
-
-        for surface in surfaces:
-            com = gmsh.model.occ.getCenterOfMass(surface[0], surface[1])
-            if np.allclose(com, [0, H/2, 0]):
-                left_wall.append(surface[1])
-            elif np.allclose(com, [L, H/2, 0]):
-                right_wall.append(surface[1])
-            elif np.isclose(com[1], 0):
-                bottom_wall.append(surface[1])
-            elif np.isclose(com[1], H):
-                top_wall.append(surface[1])
-        # Rotate channel theta degrees in the xy-plane
-        gmsh.model.occ.rotate([(2, rectangle)], 0, 0, 0,
-                              0, 0, 1, theta)
-        gmsh.model.occ.synchronize()
-
-        # Add physical markers
-        gmsh.model.addPhysicalGroup(2, [rectangle], 1)
-        gmsh.model.setPhysicalName(2, 1, "Fluid volume")
[…]

### 2025-01-25 utilities/normals_and_tangents.py

@@ -1,248 +1,0 @@
-# Copyright (C) 2023 Jørgen S. Dokken and Halvor Herlyng
-#
-# SPDX-License-Identifier:    MIT
-
-import ufl
-import meshio
-
-import numpy   as np
-import dolfinx as dfx
-
-from mpi4py   import MPI
-from petsc4py import PETSc
-
-from dolfinx.fem.petsc     import assemble_matrix, assemble_vector, apply_lifting, set_bc
-from dolfinx.cpp.fem.petsc import insert_diagonal
-
-def tangential_projection(u: ufl.Coefficient, n: ufl.FacetNormal) -> ufl.Coefficient:
-    """
-    See for instance:
-    https://link.springer.com/content/pdf/10.1023/A:1022235512626.pdf
-    """
-    return (ufl.Identity(u.ufl_shape[0]) - ufl.outer(n, n)) * u
-
-def facet_vector_approximation(V: dfx.fem.FunctionSpace,
-                               mt: dfx.mesh.MeshTags | None = None,
-                               mt_id: int | tuple[int] | None = None,
-                               tangent: bool = False,
-                               interior: bool = False,
-                               jit_options: dict | None = None,
-                               form_compiler_options: dict | None = None) -> dfx.fem.Function:
-    """
-    Approximate the facet normal or tangent on a surface by projecting it into the function space for a set of facets.
-
-    Args:
-        V: The function space to project into. Needs to be defined on discontinuous elements.
-
-        mt: The `dolfinx.mesh.MeshTags` containing facet markers.
-
-        mt_id: The id for the facets in `mt` we want to represent the normal or tangent on.
-
-        tangent: To approximate the tangent of the facets set this flag to `True`.
-
-        jit_options: Parameters used in CFFI JIT compilation of C code generated by FFCx.
-            See https://github.com/FEniCS/dolfinx/blob/main/python/dolfinx/jit.py#L22-L37
-            for all available parameters. Takes priority over all other parameter values.
-
-        form_compiler_options: Parameters used in FFCx compilation of this form. Run `ffcx - -help` at
-            the commandline to see all available options. Takes priority over all
-            other parameter values, except for `scalar_type` which is determined by
[…]

### 2025-01-25 utilities/utilities.py

@@ -1,474 +1,0 @@
-import ufl
-
-import numpy     as np
-import dolfinx   as dfx
-
-from mpi4py    import MPI
-from petsc4py  import PETSc
-from basix.ufl import element
-
-def nonmatching_mesh_interpolation(mesh0: dfx.mesh.Mesh,
-                                   mesh1: dfx.mesh.Mesh, 
-                                   u: dfx.fem.Function, 
-                                   vector: bool=False, 
-                                   write_output: bool=False,
-                                   xtype=np.float64):
-    """ Interpolate the function u onto a rectangular slice that lies in the yz-plane.
-
-    Parameters
-    ----------
-    mesh0 : dfx.mesh.Mesh
-        Brain ventricles mesh.
-    mesh1 : dfx.mesh.Mesh
-        Rectangle mesh.
-    u : dfx.fem.Function
-        Finite element function to be interpolated.
-    vector : bool, optional
-        Use vector finite elements if True, by default False.
-    write_output : bool, optional
-        Write the function u and the rectangle interpolation of u to files if True, by default False.
-    xtype : numpy dtype, optional
-        Numpy datatype, by default np.float64.
-
-    Returns
-    -------
-    dfx.fem.Function
-        interpolation of function u onto the rectangle slice.
-    """
-    el0 = element("DG", mesh0.basix_cell(), 1, shape=(3,), dtype=xtype) if vector else element("DG", mesh0.basix_cell(), 1, dtype=xtype)
-    V0 = dfx.fem.functionspace(mesh0, el0)
-    el1 = element("DG", mesh1.basix_cell(), 1, shape=(3,), dtype=xtype) if vector else element("DG", mesh1.basix_cell(), 1, dtype=xtype)
-    V1 = dfx.fem.functionspace(mesh1, el1)
-    padding = 1e-14
-
-    # Check that both interfaces of create nonmatching meshes interpolation data returns the same
-    mesh1_cell_map = mesh1.topology.index_map(mesh1.topology.dim)
-    num_cells_on_proc = mesh1_cell_map.size_local + mesh1_cell_map.num_ghosts
-    cells = np.arange(num_cells_on_proc, dtype=np.int32)
-    interpolation_data = dfx.fem.create_interpolation_data(V1, V0, cells, padding=padding)
-
-    # Interpolate 3D->2D
-    u1 = dfx.fem.Function(V1, dtype=xtype)
[…]

### 2025-01-27 paper/main.tex
update paper, clean utilities

@@
 % Title
-\title{Cilia-mediated flow and transport in zebrafish brain ventricles in vivo and in silico}
+\title{The role of cilia-mediated cerebrospinal fluid flow in intraventricular transport in zebrafish embryos}
 \author[1,*]{Halvor Herlyng}
@@
 \hypersetup{
-  pdftitle={cilia-csf},
+  pdftitle={zebrafish-cilia-csf},
   pdfauthor={H.~Herlyng \textit{et al.}}
@@
 \section*{Introduction}
+\lyng{HH: This needs work, have just jotted down some stuff to have references ready.}
+
 Development of brains and sustaining healthy functioning of the brain relies on a myriad of regulatory processes.
@@
 A schematical illustration of the flow features in the brain ventricles is shown in~\cref{fig:figure1}, panel \textbf{a}.
-The experimental setup is identical (\lyng{HH: Is this true?}) to the ones considered there, and we refer to that paper for further details than the ones provided here in the following.
+Our experimental setup for the particle tracking is identical to the ones considered there (\lyng{HH: Is this true?}), and we refer to that paper for further details than the ones provided here in the following.
 
@@
 
-\subsection*{Solute transport}
+\subsection*{Computational model of solute transport}
 We simulate transport of photoconverted proteins in the brain ventricles by modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and time $t > 0$ by the advection-diffusion equation
@@
 
-\subsection*{Physical parameters and dimensionless numbers \lyng{HH: Change this to "quantities of interest" and add mean concentration and time to threshold?}}\label{subsec:parameters}
+\subsection*{Physical parameters}\label{subsec:parameters}
 The cerebrospinal fluid density $\rho$ and dynamic viscosity $\mu$ were set following the work of Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
@@
 
-To evaluate the relative importance of advection and diffusion as transport mechanisms, we consider the Péclet number
-\begin{equation*}
-    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
-\end{equation*}
-Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, whereas $D$ is the solute diffusion coefficient as previously.
-To assess the assumption that the CSF flow is governed by the Stokes equations, we also compute the Reynolds number
-\begin{equation*}
-    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
-\end{equation*}
-with $L_r$ and $U_r$ as the length and velocity scales characteristic of the flow.
-
 \subsection*{Estimation of diffusion coefficients with the Stokes-Einstein relation}\label{subsec:diff_coeffs}
@@
 \subsection*{Model versions and physiological scenarios}\label{subsec:model_versions}
-We have introduced boundary conditions to model two separate driving forces of cerebrospinal fluid flow, namely motile cilia and cardiac pulsations.
-To distinguish the impact of each component, three different setups for the flow model were considered:
+We have introduced boundary conditions to model two separate driving forces of cerebrospinal fluid (CSF) flow, namely motile cilia and cardiac pulsations.
+To distinguish the impact of each component, three different setups for the flow model were considered~(\cref{tab:flow_model_versions}):
 \begin{itemize}
@@
 \end{itemize}
-When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
-In region 1, we use the function~\eqref{eq:injection_curve} to enforce the concentration such that it represents the experimental data of photoconversion of proteins.
-We consider the three different diffusion coefficients introduced in previous sections to simulate and compare results for transport of molecules of varying sizes.
-
-\lyng{Add information on removing cilia and modifying geometries simulation studies in this section?}
 \begin{table}[h!]
@@
     \caption{A summary of the flow model versions. For all model versions, we consider a free slip boundary condition on $\Gs=\Gamma\setminus\left(\Gc\cup\Gp\right)$.}
-    \label{tab:model_versions}
+    \label{tab:flow_model_versions}
     \begin{tabular}{c|c@{\hskip 0.4in}c}
@@
 \end{table}
+
+When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
+In region number one (the photoconversion region), we use the function~\eqref{eq:injection_curve} to enforce the concentration such that it represents the experimental data of photoconversion of proteins.
+We consider the three different diffusion coefficients introduced in previous sections to simulate and compare results for transport of molecules of varying sizes.
+
+To simulate transport in the pathological case of region-specific cilia absence, we consider three scenarios where we modify the boundary conditions of the CSF flow model.
+The cilia tangential stress boundary condition for the boundary where we remove cilia is changed to a free-slip boundary condition, prescribing zero tangential forces to represent absence of cilia motion in the region where we consider cilia removal.
+We consider removal of cilia in the three separate cilia-covered regions of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle, and the ventral part of the diencephalic ventricle~(\cref{fig:figure1}, panel~\textbf{d}).
+For the three scenarios, we simulate CSF flow modeled by the Stokes equations~\eqref{eq:stokes_eqs} with the modified boundary conditions, and use the resulting velocity field in transport simulations.
+
+The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
+Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
+Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaenously.
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+
+\subsection*{Quantities of interest}
+We quantify the transport of solute by calculating the mean concentrations
+\begin{equation}
+    \overline{c}_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
+    \label{eq:c_mean_i}
+\end{equation}
+in the regions of interest (ROIs) $\Omega_i$ as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$.
+The dynamics of ROI 1 follows from imposing~\cref{eq:injection_curve}.
+As another way of quantifying transport, we report the times $\hat{t}_i$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}_i$.
+We use $\hat{c}_i=0.25$ for regions of interest 1--4 and $\hat{c}_i=0.10$ for regions 5 and 6.
+
+To evaluate the relative importance of advection and diffusion as transport mechanisms, we consider the Péclet number
+\begin{equation*}
+    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
+\end{equation*}
+Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, whereas $D$ is the solute diffusion coefficient as previously.
+To assess the assumption that the CSF flow is governed by the Stokes equations, we also compute the Reynolds number
+\begin{equation*}
+    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
+\end{equation*}
+with $L_r$ and $U_r$ as the length and velocity scales characteristic of the flow.
 
@@
 Thus, with the boundary conditions used in model version I, the pressure is not uniquely defined and discretization of the Stokes equations leads to a singular linear equation system.
-\lyng{To make the discrete problem well-posed for this setup, the right-hand side vector of the linear system assembled after discretization of the Stokes equations equations is orthogonalized with respect to the basis of the nullspace of the pressure to ensure existence of solutions.
+To make the discrete problem well-posed for this setup, the right-hand side vector of the linear system assembled after discretization of the Stokes equations equations is orthogonalized with respect to the basis of the nullspace of the pressure to ensure existence of solutions.
 This nullspace is the set of (real) scalar constants.
-Furthermore, information of the pressure nullspace is provided to the linear solver, such that a unique solution is determined.}
+Furthermore, information of the pressure nullspace is provided to the linear solver, such that a unique solution is determined.
 
@@
 \subsection*{Cerebrospinal fluid flow in the brain ventricles is compartmentalized}
-With cilia forces and cardiac forces represented in the flow model (model version 0), we observe a vortex-structured flow pattern in the anterior and middle ventricles~(\cref{fig:figure1}, panel \textbf{g} \lyng{Need to reorder panels in figure 1, since results for model 0 are introduced first.}).
+With cilia forces and cardiac forces represented in the flow model (model version 0), we observe a vortex-structured flow pattern in the anterior and middle ventricles~(\cref{fig:figure1}, panel \textbf{e}).
 This rotational motion shows that cilia-mediated flow is dominating in these regions, as the vortex structures are a consequence of the applied tangential stresses on the ciliated boundaries combined with the assumption of fluid incompressibility.
@@
 \subsection*{Vortex structures vanish in the absence of cilia}
-Excluding the cilia tangential traction from the model (model II), vortex-structured compartmentalization of the ventricular flow does not occur, and the flow is directional and pulsatile as a result of the pressure boundary conditions imposed~(\cref{fig:figure1}, panel \textbf{d}).
-The pulsatile motion is absent when disregarding cardiac motion~(model I, see \cref{fig:figure1}, panel \textbf{d}).
+The pulsatile motion is absent when disregarding cardiac motion~(model I, \cref{fig:figure1}, panel~\textbf{f}).
 For model I, the boundary conditions are not time-dependent, rendering the solution to the Stokes equations~\eqref{eq:stokes_eqs} a steady-state flow field.
 Streamlines demonstrate the compartmentalization of the cerebrospinal fluid flow driven by cilia, and we observe highest vorticity in the vicinity of cilia.
+Excluding the cilia tangential traction from the model (model II), vortex-structured compartmentalization of the ventricular flow does not occur, and the flow is directional and pulsatile as a result of the pressure boundary conditions imposed~(\cref{fig:figure1}, panel \textbf{g}).
 
@@
 
-We quantify the transport of solute by showing the profile of the mean concentrations
-\begin{equation}
-    \overline{c}_i = \frac{1}{|\Omega_i|}\int_{\Omega_i} c\dx,
-    \label{eq:c_mean_i}
-\end{equation}
-in the regions of interest (ROIs) $\Omega_i$ as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$.
-The $\overline{c}_i$ profiles and an illustration of the ROIs are presented in panels~\textbf{b--e} of~\cref{fig:figure2_compare_diffusion_coefficients}.
-The dynamics of ROI 1 follows from imposing~\cref{eq:injection_curve}.
-Note that the total mass added to the system is not exactly the same for all three diffusion coefficients, since the total mass added depends on how fast the mass added in ROI 1 is transported away from that region.
-
+Transport of solute is quantified by the profile of the mean concentrations $\overline{c}_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\cref{fig:figure2_compare_diffusion_coefficients}, panels \textbf{b--d}).
+An illustration of the ROIs is provided in \cref{fig:figure2_compare_diffusion_coefficients}, panel~\textbf{e}.
+The dynamics of ROI 1 follow from imposing~\cref{eq:injection_curve}.
 For ROIs 2--6, we observe more rapid concentration increases when the diffusion coefficient increases.
@@
 The profiles of the latter three regions are similar, displaying only small differences in all of the three plots.
-
-As another way of quantifying transport, we report the times $\hat{t}$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}$~(\cref{fig:figure2_compare_diffusion_coefficients}, panel \textbf{f}).
-We use $\hat{c}=0.25$ for regions 1--4 and $\hat{c}=0.10$ for regions 5 and 6.
+\lyng{HH: Add some quantification in terms of percentages, e.g.
+final values of $\overline{c}_i$ for the different $D_i$?}
+%\lyng{HH: is this really true?: Note that the total mass added to the system is not exactly the same for all three diffusion coefficients, since the total mass added depends on how fast the mass added in ROI 1 is transported away from that region.}
+
+We report the times $\hat{t}$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}$~(\cref{fig:figure2_compare_diffusion_coefficients}, panel \textbf{f}).
+Recall that $\hat{c}=0.25$ for regions of interest 1--4 and $\hat{c}=0.10$ for regions 5 and 6.
 The choice of different threshold values is because of the slower dynamics in ROIs 5 and 6.
@@
 This yields the three Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
+\lyng{HH: move choice of length scale/calculation of velocity scale to Methods?
+Same question for Reynolds number calculation.}
 
 \subsection*{Comparing experimental and computational results}
-Transport of photoconverted proteins was quantified by the relative change in fluorescence intensity $\Delta F=(F(t)-F_0)/F_0$ over time~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}).
+Transport of photoconverted proteins is quantified by the change in fluorescence intensity $\Delta F=(F(t)-F_0)/F_0$ over time~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}).
 The solid lines are the mean values of $\Delta F$ for the fish cohort, with shaded regions covering one standard deviation.
 The first region of interest (ROI 1) is the laser-targeted region.
-We remind the reader that the fluorescence intensity change $\Delta F$ is scaled by the maximum fluorescence intensity $F_0$ in ROI 1 to ease comparison of the profiles.
-
-Qualitatively, the fluorescence intensity change in region one resembles intensity dynamics observed in previous experiments studying the photoconversion properties of Dendra2 fluorescent proteins~\cite{Makarov2014Steady-stateDendra2}.
-The transport to the other regions can be separated into two groups: the fluorescence intensity change $\Delta F$ for ROIs 2--4 in the middle ventricle are all similar, whereas the more distal regions ROI 5 and 6 (anterior and posterior ventricle, respectively) exhibit a slower increase in $F$.
+Qualitatively, the fluorescence intensity change in this region resembles intensity dynamics observed in experiments that studied the photoconversion properties of Dendra2 fluorescent proteins~\cite{Makarov2014Steady-stateDendra2}.
+The transport to the other regions can be separated into two groups: the fluorescence intensity change $\Delta F$ for ROIs 2--4 in the middle ventricle are all similar, whereas the more distal regions ROI 5 and 6 (anterior and posterior ventricle, respectively) exhibit a slower increase in $\Delta F$.
 In ROIs 2--4, the $\Delta F$ curves are concave, similar to ROI 1, while in ROIs 5 and 6 the curves are convex.
-Although the fluorescence intensity increases throughout all of the experiments, the maximum $\Delta F$ is not necessarily attained at the final time of the experiments, mostly due to signal noise.
-At the final time, the mean fluoresence intensities in regions 2--4 all exceed 60\% (63\%, 71\%, 67\%, respectively) of the final value $F_0$ in ROI 1, wheras ROIs 5 and 6 reach mean values of 29\% and 18\%, respectively.
+Although the fluorescence intensity increases throughout all of the experiments, the maximum $\Delta F$ is not necessarily attained at the final time of the experiments.
+At the final time, the mean fluoresence intensities in regions 2--4 all exceed 0.60 (0.63, 0.71, 0.67, respectively) of the final value $F_0$ in ROI 1, wheras ROIs 5 and 6 reach mean values of 0.29 and 0.18, respectively.
 
@@
 
-The experimental photoconversion procedure was simulated by solving the advection-diffusion equation with the diffusion coefficient of Dendra2 ($D_3$).
-We quantify the transport with the time evolution of the mean concentration $\overline{c}$ in transport simulations~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
+The experiment of photoconverting Dendra2 was simulated by solving the advection-diffusion equation with the diffusion coefficient $D_3$.
+We quantify the simulated transport with the time evolution of mean concentrations $\overline{c}$~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
 Imposing the concentration in ROI 1 mimics the fluorescence intensity change $\Delta F$ in ROI 1.
@@
 For all regions, the maximum mean concentration is attained at the final time of the simulations.
-The final value of $\overline{c}$ in regions 2--4 were 0.76, 0.72 and 0.82, respectively.
-As in the experiments, the transport to regions 5 and 6 is slower than the transport to the middle ventricle sites, even though the final values of $\overline{c}$ are higher than those of $\Delta F$.
-The anterior ventricle (region 5) has a final $\overline{c}$ value of 0.56, while in the posterior ventricle (region 6) the final value is 0.35.
+The final value of $\overline{c}$ in regions 2--4 were 0.76, 0.72 and 0.82, respectively, compared to 0.63, 0.71 and 0.67 for $\Delta F$.
+As in the experiments, the transport to regions 5 and 6 is slower than the transport to the middle ventricle sites, though the final values of $\overline{c}$ are higher than those of $\Delta F$.
+The anterior ventricle (region 5) has a final $\overline{c}$ value of 0.56 (final $\Delta F= 0.29$), while in the posterior ventricle (region 6) the final value is 0.35 (final $\Delta F= 0.18$).
 Qualitatively, the $\overline{c}$ profile in the posterior ventricle compares with $\Delta F$ in this region, displaying a convex curve that has an approximately linear increase after an initial nonlinear increase.
@@
 
-To further quantify the spatial differences of changes in fluorescence intensity and concentration, we determined the time $\hat{t}$ to exceed a threshold value of 0.25~(\cref{fig:figure3_compare_exp_and_sim_control}, panels \textbf{c} and \textbf{d}).
-For the fluorescence intensity change $\Delta F$, we determined this time-to-threshold for the same downsampled dataset that was used to calculate $\Delta F$.
-In the simulations, we determined the time to reach the threshold value in each degree of freedom of the concentration finite element function.
-In~\cref{fig:figure3_compare_exp_and_sim_control}, we have excluded the posterior-most regions of the geometries, as the values of $\Delta F$ and $c$ never reached the threshold value of 0.25 in these regions.
+We qualitatively compared fluorescence intensities and mean concentrations with the time $\hat{t}$ to exceed a threshold value of 0.25~(\cref{fig:figure3_compare_exp_and_sim_control}, panels \textbf{c} and \textbf{d}).
+For $\Delta F$, we determined this time-to-threshold for the same downsampled dataset that was used to calculate $\Delta F$.
+In the simulations, we determined the time for $\overline{c}$ to reach the threshold value in each degree of freedom of the concentration finite element function.
+We have excluded the posterior-most regions of the geometries in~\cref{fig:figure3_compare_exp_and_sim_control}, because the values of $\Delta F$ and $c$ never exceeded the threshold value of 0.25 in these regions.
 
@@
 We compare the time evolution of fluorescence intensity in control and \emph{schmalhans}~(\emph{smh}) mutant zebrafish, plotting the means of $\Delta F$ across the cohorts, shaded with one standard deviation regions~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{a}).
-Additionally, we determined the time needed to reach a threshold fluorescent intensity change in each region of interest (ROI) for each fish~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{b}).
-It is important to note that this threshold was set differently for two groups of regions: the threshold value was set to 0.25 for ROIs 1--4, whereas for ROIs 5 and 6 the threshold value was 0.10.
+Additionally, we determine the time needed to reach a threshold fluorescent intensity change in each region of interest (ROI) for each fish~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{b}).
+It is important to note that this threshold was set differently for two groups of regions: the $\Delta F$ threshold value was set to 0.25 for ROIs 1--4, whereas for ROIs 5 and 6 the threshold value was 0.10.
 This choice was made because of the slower dynamics of ROIs 5 and 6.
-The individual data points of the times to threshold are presented together with the distributions and the means.
+For each region of interest, the individual data points of the times to threshold are presented together with the distributions and the means of the data points.
 Based on the times to reach a threshold value of $\Delta F$, we test the null hypothesis that the control and mutant photoconversion data are from the same population (or equivalently, have equal distributions).
-We report the $p$-value for this hypothesis calculated with a two-sided Mann-Whitney U test that included a continuity correction, with a confidence level of 95\%.
-
-In ROI 2, there is a statistically significant slower fluorescence intensity increase in the \emph{smh} mutant fish compared to controls~(\cref{fig:figure4_compare_control_mutant}).
+We report the $p$-value for this hypothesis calculated using a two-sided Mann-Whitney U test that included a continuity correction, with a confidence level of 95\%.
+
+In ROI 2, there is a statistically significant slower fluorescence intensity increase in the \emph{smh} mutant fish compared to controls~(\cref{fig:figure4_compare_control_mutant}, panel~\textbf{b}).
 Compared to the control dataset, the mean time-to-threshold in ROI 2 is 45\% higher for the mutant dataset.
-In the other ROIs, the differences in the experimental results for the controls and the mutants are not significantly different.
-We note that, both within the control and within the mutant dataset, there are considerable individual differences in the times to reach the threshold.
+In the other ROIs, the differences in the experimental results for controls and mutants are not significantly different.
+We observe that, both within the control and within the mutant dataset, there are considerable individual differences in the times to reach the threshold.
 
 To simulate protein transport in mutant fish, we used flow model II (only cardiac motion as flow mechanism, no cilia) to model the ciliary dysfunction of the \emph{smh} mutants.
-We visualize the time evolution of the mean concentration in each ROI for both model II and the baseline model (model 0), in addition to a similar time-to-threshold as computed for the experimental data~(\cref{fig:figure4_compare_control_mutant}, panel~\textbf{c}).
-As for the experiments, we use a threshold value of $0.25$ in regions 2-4 and a value of $0.10$ for regions 5 and 6.
+We visualize the time evolution of the mean concentration $\overline{c}$ in each ROI for both model II and the baseline model (model 0), in addition to a similar time-to-threshold $\hat{t}$ as computed for the experimental data~(\cref{fig:figure4_compare_control_mutant}, panel~\textbf{c}).
+As for the experiments, we use a threshold value of $0.25$ in regions 2--4 and a value of $0.10$ for regions 5 and 6 to calculate $\hat{t}$.
 For ROI 2, we observe the same dynamics in simulations as in experiments: there is a slower increase in mean concentration in ROI 2 compared to the baseline model.
 The difference is even greater for the simulations, with the time-to-threshold in ROI 2 for model II 90\% higher than for model 0.
-Additionally, ROIs 4 and 5 exhibit very different $\overline{c}$ profiles.
+Additionally, ROIs 4 and 5 exhibit very different $\overline{c}$ profiles for the two different flow models.
 The difference is less significant for ROI 3, and for the posterior ventricle (region 6) the profiles are very similar.
@@
 \subsection*{Loss of cilia can slow down transport}
-To simulate the pathology of region-specific cilia absence, we consider three scenarios where we modify the boundary conditions of the cerebrospinal fluid (CSF) flow model.
-The cilia tangential stress boundary condition for the boundary where we remove cilia is changed to a free-slip boundary condition, which prescribes zero tangential forces representing cilia motion in the region considered.
-We consider removal of cilia in the three separate cilia-covered regions of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle, and the ventral part of the diencephalic ventricle~(\cref{fig:figure5_compare_cilia_modifications}, panel \textbf{a}).
-For the three scenarios, we simulate CSF flow modeled by the Stokes equations with the modified boundary conditions, and use the resulting velocity field in transport simulations of Dendra2.
+Considering removal of cilia in three different regions through modified flow boundary conditions, we simulate CSF flow modeled by the Stokes equations and use the resulting velocity field in transport simulations of Dendra2.
 The maximum velocity observed in the simulations when removing telencephalic, ventral diencephalic and dorsal diencephalic cilia were, respectively, 27.7 $\mu$m/s, 27.2 $\mu$m/s, and 8.0 $\mu$m/s.
@@
 It is evident from the final values of $\overline{c}$ that there is less total mass added to the system in the absence of dorsal cilia.
-This is due to the lower velocities in the vicinity of ROI 1, resulting in less ability to carry away mass from the volume where the concentration is imposed.
+\lyng{HH:This is due to the lower velocities in the vicinity of ROI 1, resulting in less ability to carry away mass from the volume where the concentration is imposed.
+\emph{Is this correct?}}
 \begin{figure}[H]
@@
 \subsection*{Modification of ventricles geometry impacts protein distribution}
-The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
-Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh.
-Specifically, we consider four alternative meshes: one where the connection between the anterior and middle ventricles is constricted; one where the connection between the middle and posterior ventricles is constricted; one where the middle ventricle is shrunk in the lateral direction; the combination of the above three modifications~(\cref{fig:figure6_sim_results_compare_geometries}, panel \textbf{a}).
-We simulate CSF flow in the modified geometries with the baseline model and use the resulting velocity field to simulate transport of Dendra2.
-
-\lyng{Quantify in terms of percentage changes in the final mean concentration values.} Constricting the connection between the anterior and middle ventricle leads to slower transport to region of interest (ROI) 5 located in the anterior ventricle, and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
+We simulate flow and transport in four alternative brain ventricles meshes: one where the connection between the anterior and middle ventricles is constricted; one where the connection between the middle and posterior ventricles is constricted; one where the middle ventricle is shrunk in the lateral direction; the combination of the above three modifications~(\cref{fig:figure6_sim_results_compare_geometries}, panel \textbf{a}).
+We simulate CSF flow in the modified geometries with the baseline flow model and use the resulting velocity field to simulate transport of Dendra2.
+
+Constricting the connection between the anterior and middle ventricle leads to slower transport to region of interest (ROI) 5 located in the anterior ventricle, and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
 On the other hand, constricting the connection between the middle and the posterior ventricle leads to less transport into the posterior ventricle (ROI 6), and slightly more transport towards the anterior ventricle (ROI 5).
@@
 Both the anterior and the posterior ventricles (ROIs 5 and 6) have a lower mean concentration, compared to the results for the original geometry.
+
+\lyng{HH: Quantify differences in terms of percentage changes in the final mean concentration values, maybe with a bar plot?}
 \begin{figure}[H]
@@
 \subsection*{The roles of diffusion and advection in transport of photoconverted proteins}
-We quantify transport in terms of fluorescence intensity change $\Delta F$ (experiments) and mean concentration $\overline{c}$ (simulations) as functions of time.
-For both measures, we observed concave curves in some regions and convex curves in some regions, due to differing transport regimes.
-In experiments, regions distal to the photoconversion site showed a linear increase in $F$, probably because advection is absent in the distal regions where cilia are absent, such that diffusion is the sole mode of transport.
+We quantified transport in terms of fluorescence intensity change $\Delta F$ (experiments) and mean concentration $\overline{c}$ (simulations) as functions of time.
+For both measures, we observed that transport dynamics in the middle ventricle where Dendra2 fluorescent protein was photoconverted contrasted with the dynamics of the more distal regions of the anterior and posterior ventricles.
+In experiments, regions distal to the photoconversion site showed an approximately linear increase in $\Delta F$, probably because advection is absent in the transport to the distal regions, such that diffusion is the sole mode of transport.
 In regions proximal to photoconversion, advection and diffusion occur simultaneously due to the presence of cilia, leading to concave profiles for $\Delta F$.
-The convex diffusion-only behavior was observed for transport to the posterior ventricle in the simulations, but $\overline{c}$ was concave for the anterior ventricle, opposed to the experimental results \lyng{Include some referencing to textbook solutions of the diffusion and advection equations?
+The convex diffusion-only behavior was observed in the mean concentration $\overline{c}_6$ profile of the posterior ventricle in the simulations, but $\overline{c}_5$ was concave for the anterior ventricle, opposed to the experimental results \lyng{HH: \emph{Is this the correct interpretation of convex vs.
+concave curves?} Include some referencing to textbook solutions of the diffusion and advection equations to explain this convex vs.
+concave?
 E.g.
-semi-infinite slab or boundary layer solutions.}.
-Based on the geometry modification study, the reason for this difference in behavior might be that the duct between the anterior and middle ventricle is inflated in our computational mesh, as a result of the dye-injection performed before imaging\lyng{Cite this?}.
+semi-infinite slab or boundary layer solutions to inflow/outflow problem.}.
+Based on the geometry modification study, the reason for this difference in behavior might be that the duct between the anterior and middle ventricle is inflated in our computational mesh, as a result of the dye-injection performed before imaging~\lyng{Cite this?}.
+This inflation allows for effective cilia-mediated advection from the middle ventricle to the anterior ventricle.
 
 In general, the mean concentration dynamics of the simulations was more rapid than the fluorescence intensity dynamics of the photoconversion experiments.
-This is strongly related to our definition of the photoconversion site (region of interest 1) in the simulations, and whether this corresponds well to the region used in experiments, since the volume of the region used in the simulations determines the total amount of solute.
-In addition to this alignment of the computational and experimental region of interest definition being hard to quantify, another reason for discrepancy in the results could be the fact that the brain ventricles are permeable, such that some Dendra2 diffuses out of the brain ventricles in the experiments.
+This is strongly related to our definition of the photoconversion site (region of interest 1) in the simulations, and whether this corresponds well to the region used in experiments, because the volume of the photoconversion region used in the simulations determines the total amount of solute, and thus impacts the rate of transport.
+The alignment of the computational and experimental region of interest definition is hard to quantify.
+Additionally, a source of discrepancy in the results is the fact that the brain ventricles might be permeable, such that some Dendra2 diffuses out of the brain ventricles in the experiments.
 An assay has shown that the neuroepithelium lining the walls of brain ventricles in embryonic zebrafish 24 hours post-fertilization is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
 Dendra2 are almost 26 kDa in size~\cite{Gurskaya2006EngineeringLight}, and are thus under this reported limit.
-If this permeability is also the case for 2 days post-fertilization zebrafish embryo ventricles, this could explain why the dynamics appear to be slower in the experiments.
+If such permeability also is the case for 2 days post-fertilization zebrafish embryo ventricles, this would lead to Dendra2 leaking out of the brain ventricles in the experiments, making the dynamics appear slower.
 
@@
 Advection is the strongest transport mechanism on a global scale (global Péclet number 7.4), but for shorter distances diffusion is balancing out advection.
-Simulating transport of larger molecules (thus with smaller diffusion coefficients) showed an increased importance of the role of advection.
-For the smallest diffusion coefficient used ($D_1$), which represented 200 nm exosomes, there was essentially zero solute in the posterior ventricle at the final simulation time (around 850 s).
-This is consistent with the statement above that transport to the posterior ventricle from the middle ventricle is driven by diffusion, based on estimated transport times of diffusion and advection: For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance of $L=200$ $\mu$m is approximately 24500 s.
+Simulating transport of larger molecules (thus with smaller diffusion coefficients) proved advection to be increasingly important as molecule size increased.
+For the smallest diffusion coefficient used, $D_1$, which represented 200 nm exosomes, there was essentially zero solute in the posterior ventricle at the final simulation time (around 850 s).
+This is consistent with the statement above that transport to the posterior ventricle from the middle ventricle is driven by diffusion, based on estimated transport times of diffusion and advection: For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance $L=200$ $\mu$m from the middle to the posterior ventricle is approximately 24500 s.
 Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen on a timescale of the order of $t_a=L/\overline{U}=141$ s.
-Comparing this with the minuscule values of $\overline{c}$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection played a role in transporting solute from the photoconversion site in the middle ventricle to the posterior ventricle, values of $\overline{c}$ in the posterior ventricle would be higher than those observed.
-
-The changes in the times to threshold when changing $D$ are greatest for regions of interest (ROIs) 4--6, further indicating that, relative to advection, diffusion has a greater impact in these regions than compared to regions 1--3.
+Comparing this with the minuscule values of $\overline{c}_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection played a role in transporting solute from the photoconversion site in the middle ventricle to the posterior ventricle, values of $\overline{c}_6$ would be higher than those observed.
+
+The changes in the times to threshold when changing the diffusion coefficient are greatest for regions of interest (ROIs) 4--6, further indicating that, relative to advection, diffusion has a greater impact in these regions than compared to regions 1--3.
 In region of interest 2 (anterior, dorsal region of the middle ventricle), the time to threshold is lower for $D_2$ than $D_3$.
@@
 We also note that, for regions of interest 3 and 4, the order of the $\Delta F$ and $\overline{c}$ profiles are opposite.
-This can be related to the difference in the exact location of ROIs 3 and 4 in simulations and experiments.
+This could be related to the difference in the exact location of ROIs 3 and 4 in simulations and experiments, or due to cilia-advection being more prominent in the simulations (cf.
+the discussion on differences in transport to the anterior ventricle).
 
 \subsection*{Simulation studies: modifying cilia and geometry}
-We studied the impacts of removing cilia in specific regions of our model.
-Removing the dorsal cilia has a strong impact on the resulting CSF flow field and the solute transport quantified by the mean concentration of solute.
-We observed that the maximum velocity in the ventricles decreased roughly by a factor of three from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
-The impactful changes to the flow field is because the total force applied on the dorsal cilia boundary is great in magnitude, providing important contribution to establishing the CSF flow structures.
+We studied the impacts of removing cilia in specific regions of our model~(\cref{fig:figure5_compare_cilia_modifications}).
+Removing the dorsal cilia has a strong impact on the resulting CSF flow field and the mean solute concentration.
+Removing the dorsal cilia decreased the maximum velocity in the ventricles roughly by a factor of three from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
+The impactful changes to the flow field is because the total force applied on the dorsal cilia boundary is great in magnitude in our model, and the dorsal cilia are thus important to establishing the CSF flow structures.
 With weaker flow in the dorsal region of the middle ventricle, there is less advective transport.
-Also, the weaker dorsal flow leads to less total mass added to the system, since there is less spreading out of the concentration imposed in region of interest number one.
-\lyng{Quantify this?}
+\lyng{HH: Quantify the difference in force applied in the dorsal region: $\int_{c, dorsal}\btau\cdot\mathbf{t}\,\mathrm ds$.}
 
 Absence of ventral cilia in the middle ventricle did not greatly impact flow dynamics and transport, but lead to slightly less transport towards the posterior ventricle, and slightly more transport towards the anterior ventricle.
-This is because the ventral cilia help establish flow towards the posterior ventricles.
+This is because the ventral cilia help induce flow towards the posterior ventricles.
 Removing the cilia in the anterior ventricle leaves the transport results virtually unaltered, although the CSF flow vortex structure in the anterior ventricle vanishes.
 This would then probably have a greater impact for smaller diffusion coefficients, as it is evident in~\cref{fig:figure2_compare_diffusion_coefficients} that transport with $D_1$ is mainly advective.
-\lyng{Compare numerical results with transport results in Figure 7 in Olstad et al.}
-
-Modifying the ventricular geometry had varying impact.
+
+\lyng{HH: Compare numerical results with transport results in Figure 7 in \cite{Olstad2019CiliaryDevelopment}.}
+
+\lyng{HH: Discuss cilia serving as an "enhanced mixing factor" on small scales, refer to this~\cite{Siyahhan2014FlowVentricles} and this~\cite{Yoshida2022EffectVentricles} paper that studied this in human brain ventricles.
+Include a discussion of what happened when these papers removed cilia.}
+
+Modifying the ventricular geometry had varying impact on transport~(\cref{fig:figure6_sim_results_compare_geometries}).
 Both when (separately) shrinking the connection between the fore- and mid-brain and the mid- and hind-brain, we observe a slight increase in the mean concentration $\overline{c}$ of regions of interests 2--4.
@@
 Meanwhile, the other region has an increase in $\overline{c}$, a result of mass conservation.
-
-When shrinking the middle ventricle, the mean concentration decreases in regions 2--4 of the middle ventricle.
+When shrinking the middle ventricle, the mean concentration decreases in regions 2--4.
 The effect on $\overline{c}$ in regions 5 and 6 is similar to when the mid-hind connection is shrunk: less solute is transported towards the hind-brain and more solute is transported towards the fore-brain.
+
 Combining all three geometry modifications, we see an increase in $\overline{c}$ in regions 2--4.
-Now, there is an decrease in both region 5 and 6, which is more similar to the experimental $\Delta F$ curves (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}) in these regions compared to the simulated $\overline{c}$ on the standard geometry (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
+Now, there is a decrease in both region 5 and 6, which is more similar to the experimental $\Delta F$ curves (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}) in these regions compared to the simulated $\overline{c}$ on the standard geometry (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
 This is in line with the expectation that shrinking the geometry is closer to replicating the geometries of the fish used in experiments, because the ventricular geometry is inflated by the injection procedure performed during image segmentation.
-
-\lyng{Discuss cilia serving as an "enhanced mixing factor" on small scales, refer to Kurtcuoglu et al. and other paper that studied this in human brain ventricles.}
-\lyng{Include a discussion of what happened when Kurtcuoglu et al. and the other paper removed cilia.}
 
@@
 The use of slip boundary conditions is motivated by experimental observations of the flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
-It has been observed that the fluid velocity increases towards the wall.
-Using slip boundary conditions allows for this behavior while avoiding the need to resolve a boundary layer near the ventricle walls, which would arise with a noslip boundary condition.
-\lyng{HH: Remove noslip comment?} A couple of previous continuum model simulation studies~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal} have modeled cilia as body forces.
-We chose to model the cilia as a force exerted tangentially on the boundary as this fits well in the slip boundary condition framework, while at the same time being a good representation of the real nature of cilia, since they are in reality microscale structures confined to the ventricular walls that generate flow through collective motion.
+It has been observed that the fluid velocity increases towards the wall~(this is also evident in~\cref{fig:figure1}, panel~\textbf{c}).
+Using slip boundary conditions allows for this behavior.
+A couple of previous continuum model simulation studies of cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal} have modeled cilia as body forces.
+We chose to model the cilia as a force exerted tangentially on the boundary.
+First, we deem this a good representation of the real nature of cilia, since they are in reality microscale structures confined to the ventricular walls that generate flow through collective motion.
+Second, it avoids the need of excessive mesh refinement near the ciliated boundaries in the case that a body force were to be applied in a $\sim$ 5 $\mu$m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.
 
@@
 Incorporating spatial arrangement heterogeneity in our model could possibly result in different transport timescales, but we would not expect notable changes to the general trends of the macroscopic transport that we study here, since the effects of introducing heterogeneous spacing of cilia would alter the magnitude of cilia forces, but not their direction.
-On the other hand, introducing more heterogeneous beating directionality could alter both the transport timescales and directionality.
-Our model has all of the cilia tangential traction aligned, and more heterogeneity in this alignment as a result of heterogeneity in the beating directionality would presumably affect both magnitude and directionality of advective transport.
-Previous studies have demonstrated that changes to beating directionality affects transport, and that specific coordination of the ciliary beating is e.g.
-crucial to maintain healthy functioning of mucous transport in airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction, Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet}, and important in nodal flow~\cite{}.
-Although these studies were mostly on spatial scales resolving individual cilia, we could envision the same effects in our continuum model, similar to the results of previous numerical studies~\cite{Ramirez-SanJuan2020Multi-scaleArrays, Thouvenin2020OriginCanal}.
-
-The handling of the influx and the outflux in the advection-diffusion equation merits discussion.
+On the other hand, introducing more heterogeneous beating directionality could alter the transport timescales as well as the directionality.
+In our model, all of the applied cilia tangential traction is aligned with the rostrocaudal axis, and more heterogeneity in this alignment to reflect heterogeneity in the beating directionality of cilia would presumably affect both magnitude and directionality of advective transport.
+Previous studies have demonstrated that changes to beating directionality affects transport, and that specific coordination of the ciliary beating is important in the brain ventricles for flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004Cilia-relatedDiseases}, but also in other phenomena such as maintaining healthy functioning of mucous transport in airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction, Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet} and in nodal flow which establishes left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry, Sawamoto2006NewBrain}.
+Although these studies were mostly on spatial scales resolving individual cilia, we could envision the same effects in our continuum model, similar to the results of previous numerical studies~\cite{Ramirez-SanJuan2020Multi-scaleArrays, Thouvenin2020OriginCanal, Yoshida2022EffectVentricles}.
+
+We used an advection-diffusion equation to simulate protein transport in the brain ventricles.
+Except for where we imposed a normal pressure boundary condition on the CSF flow, we imposed a no-flux condition on the concentration.
+Imposing a pressure-driven cardiac-related flow on certain parts of the CSF flow boundary leads to in- and outflow, and the advective transport then requires handling of in- and outflux boundary conditions.
+Reflecting our assumption that the ventricular system is closed, we set boundary conditions such that the total mass is conserved in the limit that the timestep size is zero.
 We handle the outflux by leaving the advective flux term as an unknown in the weak formulation of the advection-diffusion equation.
@@
 However, the discrete problem is well-posed, because the approach represents constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}.
-Attempting to conserve the total solute mass inside the ventricles, we applied an approximate periodic boundary condition to the inflow boundary, by setting the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous timestep $n-1$.
+
+On the inflow boundary, we applied an approximate periodic boundary condition by setting the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous timestep $n-1$.
 This is expected to be of low-order accuracy, and for high Péclet numbers, the boundary condition affects the concentration field in the vicinity of the in- and outflow boundaries due to large advective fluxes.
-For the simulation scenarios we considered, both in terms of model parameters and time span, the photoconversion region where solute is added to the system is far enough away from the in- and outflow boundaries that the flux boundary condition we impose does not significantly impact the results.
+For the simulation scenarios we considered, both in terms of model parameters and time span, the photoconversion region where solute originates is far enough away from the in- and outflow boundaries for the flux boundary condition to not significantly impact the results.
 Nevertheless, we deliberately excluded the space proximal to in- and outflow boundaries in the anterior and posterior regions of interest (5 and 6) to limit adverse effects.
@@
 However, if the ventricular system in reality is a closed system, one should rather seek out a way of modeling the CSF flow without open boundaries to avoid handling in- and outflow boundary conditions.
-A more appropriate way of handling the beating cardiac motion could be to impose a ventricular wall deformation, which in turn would induce CSF flow whilst enforcing the impermeability condition $\uu\cdot\nn=0$ on all of the ventricular walls.
-Such wall-motion induced CSF flow has been modeled and simulated in the human brain ventricular system~\cite{Causemann2022HumanFramework, Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
+A more appropriate way of handling the beating cardiac motion could be to impose a ventricular wall deformation, assumed to result from pulsatile motion of the heart and/or cardiac vessels surrounding the ventricles.
+This wall deformation would induce CSF flow while simultaneously permitting enforcement of the impermeability condition $\uu\cdot\nn=0$ on the ventricular walls.
+Such wall-motion induced CSF flow has been modeled and simulated successfully in the human brain ventricular system~\cite{Causemann2022HumanFramework, Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
 
 \subsection*{Estimation of computational model parameters}
-We estimated the values of the diffusion coefficients used in this study.
+The diffusion coefficients used in this study were partially based on values from experiments and partially estimated.
 The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$ is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the values $D_2$ and $D_1$ were extrapolated based on experimental data~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells, Mahmood2023ExosomeTemperature} using the Stokes-Einstein relation~\cite{Einstein1905UberTeilchen}~(\cref{eq:D_stokes_einstein}).
@@
 This would reduce the diffusion coefficient~(cf.~\cref{eq:D_stokes_einstein}), but based on reports of protein concentration having a limited impact on the viscosity of CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}, this reduction is presumably limited.
-Merely the presence of other proteins and nutrients may also reduce the diffusion coefficient by reduction of the mean-free path lengths.
+Merely the presence of other proteins and nutrients may also reduce the diffusion coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
 Considering the diffusion coefficients $D_1$ and $D_2$ both smaller than $D_3$ in our transport analysis provides information about how the simulation results of Dendra2 transport would be altered if the diffusion coefficient $D_3$ is overestimated.
+In the case that $D_3$ is underestimated, we assume the results would follow the same trend as the differences between results for $D_2$ and $D_3$: diffusion becomes more important, and is almost balancing advective transport for $D_3$.
+Thus for a higher diffusion coefficient, we would see transport that is mostly explained by diffusive behavior.
 
@@
 Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles} used a force expression that increased linearly from the wall to a maximum force density of $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 $\mu$m away from the wall, which represented cilium length.
-If we assumed our cilia array to have the same thickness of $l = 15$ $\mu$m, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$ would correspond to a maximum force density of
+If we assumed a cilia array of the same thickness $l = 15$ $\mu$m in our model, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$ would correspond to a maximum force density of
 \begin{equation*}
@@
 which smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 $\mu m$ is the typical length of cilia in human brain ventricles~\cite{Afzelius2004Cilia-relatedDiseases}, while in zebrafish they are closer to 5 $\mu$m~\cite{Salman2022ComputationalEmbryo}.
+The length 15 $\mu m$ is the a typical length of cilia in human brain ventricles (in general the length is between 10--15 $\mu$m~\cite{Afzelius2004Cilia-relatedDiseases}), while in zebrafish they are closer to 5 $\mu$m~\cite{Salman2022ComputationalEmbryo}.
 With $l=5$ $\mu$m, our traction parameter corresponds to a maximum force density of $f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ used by Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}.
@@
 mice, rats, humans.
-\lyng{Refer to and discuss some previous works there, e.g.
+\lyng{HH: Refer to and discuss some previous works there, e.g.
 Faubel, Eichele etc.}
@@
 \subsection*{Limitations and further work}
-The model presented has certain limitations.
-Future work could consider spatial heterogeneity of the cilia, and how this affects flow and transport.
-Results from modeling pulsatile flow indicate that deformation of the ventricles due to cardiac motion might be the underlying mechanism of the pulsatile flow observed in experiments.
-Modeling deformation of the ventricles and investigating how the arising flow compares with pulsatile flow observed in experiments could be an interesting next step.
+The model presented has certain limitations. Future work could consider:
+\begin{itemize}
+    \item spatial heterogeneity of the cilia, how this affects flow and transport
+    \item time-varying cilia?
+    \item improved advection-diffusion equation BCs
+    \item Modeling deformation of the ventricles and investigating how the arising flow compares with pulsatile flow observed in experiments
+\end{itemize}
 
 \section*{Conclusion}
-We have presented a numerical model of flow and transport in zebrafish brain ventricles based on finite element methods.
+We have presented experimental data from imaging photoconversion of a fluorescent protein in zebrafish brain ventricles, both for healthy animals and mutant animals with ciliary dysfunction.
+Experimental results indicate that cilia only affect the local distribution of proteins, while most of the transport is by diffusion.
+We also presented a numerical model of flow and transport in zebrafish brain ventricles based on finite element methods.
 A realistic brain ventricles geometry from medical imaging was used to perform a computational study with the presented model.
-The flow model reproduces qualitatively the experimentally observed flow features of cilia-mediated cerebrospinal fluid (CSF) flow in zebrafish brain ventricles.
-With the transport model coupled to the flow equations, we estimated how slowly or rapidly different molecules are transported in the ventricles.
-In line with experimental observations, the transport times to the posterior ventricles are significant because of the absence of cilia in this region.
-In the anterior and middle ventricles the transport is advection-dominated due to the CSF flow generated by the cilia, resulting in rapid transport of molecules.
+The flow model reproduces qualitatively the experimentally observed flow features of cilia-mediated cerebrospinal fluid flow in zebrafish brain ventricles.
+Coupling the flow to the transport model, we estimated how slowly or rapidly molecules of varying size are transported in the ventricles.
+Simulations indicate that cilia-driven advection is important for transport of larger molecules.
 
@@
 The system~\eqref{eq:stokes_weak_modelA} is thus singular with a one-dimensional nullspace of constant pressures.
-\lyng{Consequently, assembly of our discretization of the  equations~\eqref{eq:stokes_weak_modelA} into a linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
+Consequently, assembly of our discretization of the  equations~\eqref{eq:stokes_weak_modelA} into a linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
 To ensure existence of solutions, we orthogonalize the right-hand side vector $\mathbf{b}$ with respect to the pressure nullspace basis (the set of all constants), before solving the linear system.
-To obtain a unique solution, which together with existence renders the problem well-posed, information of the pressure nullspace is passed to the linear solver.} Let us remark that the singularity is a consequence of the fact that the impermeability condition is assumed to hold on the \emph{entire} domain boundary for this model version, which leaves the pressure under-determined as a result of no boundary condition specifying the pressure.
+To obtain a unique solution, which together with existence renders the problem well-posed, information of the pressure nullspace is passed to the linear solver.
+Let us remark that the singularity is a consequence of the fact that the impermeability condition is assumed to hold on the \emph{entire} domain boundary for this model version, which leaves the pressure under-determined as a result of no boundary condition specifying the pressure.
 
@@
 For the normal pressure boundary condition, we set $\Tilde{p}(t) = 0$ on the anterior part and
-$\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The amplitude $A$ was tuned and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.
+$\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The value of the amplitude $A$ was based on heuristics and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.
 
@@
 
-In time, we discretize the weak formulation~\eqref{eq:abstract_semi_discrete_weak_form_modelC} with the implicit Euler scheme.
+In time, we discretize the weak formulation~\eqref{eq:abstract_semi_discrete_weak_form_modelC} with the implicit Euler method.
 
@@
 \begin{equation}
-    a(c, \phi) + \Tilde{b}(c, \phi) = \Tilde{L}(\phi), \quad\forall\phi\in W, \label{eq:adv_diff_weak_formB}
+    a(c, \phi) + b(c, \phi) = L(\phi), \quad\forall\phi\in W, \label{eq:adv_diff_weak_formB}
 \end{equation}
@@
     a(c, \phi) &= \intO{\pdifft{c}\phi} - \intO{\JJ\cdot\nabla\phi}, \label{eq:adv_diff_bilinear_form}\\
-    \Tilde{b}(c, \phi) &= \intGout{c(\uu\cdot\nn)\phi}, \label{eq:adv_diff_skew_form} \\
-    \Tilde{L}(\phi) &= \intGin{h_{\mathrm{in}}\phi}.\label{eq:adv_diff_linear_form}
+    b(c, \phi) &= \intGout{c(\uu\cdot\nn)\phi}, \label{eq:adv_diff_skew_form} \\
+    L(\phi) &= \intGin{h_{\mathrm{in}}\phi}.\label{eq:adv_diff_linear_form}
 \end{align}
@@
 \begin{equation*}
-    a(c_h, \phi_h) + \Tilde{b}(c_h, \phi_h) = \Tilde{L}(\phi_h), \quad\forall\phi_h\in W_h.
+    a(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h), \quad\forall\phi_h\in W_h.
 \end{equation*}
@@
 \begin{equation}
-    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + \Tilde{b}(c_h, \phi_h) = \Tilde{L}(\phi_h), \quad\forall\phi_h\in W_h.
+    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h), \quad\forall\phi_h\in W_h.
     \label{eq:discrete_weak_form_adv_diff}
@@
 
-In time, we discretized~\eqref{eq:discrete_weak_form_adv_diff} with the implicit Euler scheme.
+In time, we discretized~\eqref{eq:discrete_weak_form_adv_diff} with the implicit Euler method.
 
@@
 \end{subequations}%
-with $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and $\beps(\uu) = \frac{1}{2}\left(\nabla\uu + (\nabla\uu)^T\right)$, and the boundary conditions
+with $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and $\beps(\uu) = \frac{1}{2}\left(\nabla\uu + (\nabla\uu)^T\right)$, and the boundary condition
 \begin{alignat}{2}
-    \uu &= \uu_{\mathrm{mms}} \qquad&&\mathrm{on \ }\Gamma, \\
-    p   &= p_{\mathrm{mms}} \qquad&&\mathrm{on \ }\Gamma,
+    \uu &= \uu_{\mathrm{mms}} \qquad&&\mathrm{on \ }\Gamma,
 \end{alignat}
-\mk{You cannot have both conditions on the same piece of boundary. If you prescribed 
-velocity everywhere then the discrete solution should be normalized such that 
-$\int_{\Omega}(p_h - p_{\mathrm{mms}})=0$.
-}
 where $\Gamma=\partial\Omega$ is the boundary of the domain.
 Since the velocity field~\eqref{eq:velocity_mms} is divergence free by construction, $g = 0$.
-Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$  using~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}, the solutions $\uu$ and $p$ to~\eqref{eq:stokes_mms} will be the ones defined by~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}.
-Convergence rates can thus readily be calculated by comparing the numerical approximations of $\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$.
+Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$  using~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}, the solutions $\uu$ and $p$ to~\eqref{eq:stokes_mms} will be the ones defined by~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}, as long as we enforce equality in the mean pressures, i.e.
+$\intO{(p_h - p_{\mathrm{mms}})}=0$.
+Convergence rates are then readily calculated by comparing the numerical approximations of $\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$ on meshes of varying grid resolution.
 
@@
 This change in the surface area over which the tangential traction was applied directly affected the maximum velocity magnitude, since the maximum velocity magnitude is a result of the total amount of force $\intGc{\btau\cdot P_{\nn}(\rr)}$ applied on the ciliated boundary, where the cilia vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ as introduced in~\cref{subsec:appendixA1}.
-In the numerical experiments, we set a constant $\tau = 6.5\times 10^{-4}$ Pa, with $\rr = (1, 0, 1)$ in the ventral diencephalic ventricle cilia region and $\rr = -(1, 0, 1)$ in the telencephalic and dorsal diencephalic ventricle cilia regions.
+In the numerical experiments, we set a constant $\tau = 6.5\times 10^{-4}$ Pa and $\lambda(\xx)=1$.
+We set $\rr = (1, 0, 1)$ in the ventral middle ventricle cilia region and $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle cilia regions.
 We used $\gamma=10$ for the BDM penalty parameter.
@@
     \centering
-    \caption{Velocity norms under mesh refinement on the brain ventricles mesh using model version I with $\btau = \tau P_{\nn}(\rr)$, using $\tau = 6.5\times 10^{-4}$ Pa and $\rr = (1, 0, 1)$.}\label{tab:ventricles_norms_BDM}
+    \caption{Velocity norms under mesh refinement on the brain ventricles mesh using model version I with $\btau = \tau P_{\nn}(\rr)$, using $\tau = 6.5\times 10^{-4}$ Pa, $\rr = (1, 0, 1)$ in the ventral middle ventricle and, $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle.}\label{tab:ventricles_norms_BDM}
     \begin{tabular}{cc|cccc}

### 2025-01-27 scripts/mesh_ventricles.py

@@ -1,6 +1,6 @@
 import dolfinx as dfx
 
-from imports.mesh import read_msh_parallel
+from utilities.mesh import read_msh_parallel
 from mpi4py import MPI
 
 # for i in range(9):

### 2025-01-27 scripts/plot_compare_simulations_geometry.py

@@ -6,7 +6,7 @@ import adios4dolfinx     as a4d
 import matplotlib.pyplot as plt
 
 from mpi4py       import MPI
-from imports.mesh import create_ventricle_volumes_meshtags
+from utilities.mesh import create_ventricle_volumes_meshtags
 
 """
 Plot and compare results for the original ventricles mesh and the (more) shrunk ventricles mesh. The original ventricles mesh
@@ -43,12 +43,12 @@ k = 1 # element degree
 model_version = 'C'
 molecule = 'D3'
 tau_version = 'variable_tau'
-transport_dir = f"./output/transport/results/{tau_version}/"
-mesh1_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+original/model_{model_version}/velocity_data_dt=0.02252"
-mesh2_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+shrunk/model_{model_version}/velocity_data_dt=0.02252"
-mesh3_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+middle_shrunk/model_{model_version}/velocity_data_dt=0.02252"
-mesh4_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+hind_shrunk/model_{model_version}/velocity_data_dt=0.02252"
-mesh5_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+fore_middle_hind_shrunk/model_{model_version}/velocity_data_dt=0.02252"
+transport_dir = f"../output/transport/results/{tau_version}/"
+mesh1_input_filename = f"../output/flow/checkpoints/{tau_version}/pressure+original/model_{model_version}/velocity_data_dt=0.02252"
+mesh2_input_filename = f"../output/flow/checkpoints/{tau_version}/pressure+shrunk/model_{model_version}/velocity_data_dt=0.02252"
+mesh3_input_filename = f"../output/flow/checkpoints/{tau_version}/pressure+middle_shrunk/model_{model_version}/velocity_data_dt=0.02252"
+mesh4_input_filename = f"../output/flow/checkpoints/{tau_version}/pressure+hind_shrunk/model_{model_version}/velocity_data_dt=0.02252"
[…]

### 2025-01-27 scripts/simulate_flow.py

@@ -667,7 +667,7 @@ if __name__ == '__main__':
 
     # Input parameters
     direct = True # Use direct solver if True, else use iterative solver
-    model = 'B' # Model version A (only cilia), B (only cardiac) or C (cilia+cardiac)
+    model = 'C' # Model version A (only cilia), B (only cardiac) or C (cilia+cardiac)
     f = 2.22 # Cardiac frequency [Hz]
     period = 1 / f # The cardiac period [s]
     T  = 1*period # Simulation end time [s]

### 2025-01-27 scripts/simulate_mms_verification.py

@@ -157,7 +157,7 @@ SLIP                 = 8
 
 def get_system(msh: dfx.mesh.Mesh, penalty_val: float, mu_val: float, direct: bool):
 
-    from imports.mesh import mark_boundaries_flow
+    from utilities.mesh import mark_boundaries_flow
     bdry_facets = mark_boundaries_flow(mesh=msh, inflow_outflow=False)
     k  = 1
     cell = msh.basix_cell()
@@ -336,11 +336,11 @@ if __name__ == '__main__':
         eu_div_prev = 0
         ep_L2_prev  = 0
 
-        for i in [0, 1, 2]:#, 3, 4, 5]:
+        for i in [0, 1, 2, 3, 4, 5]:
 
             with dfx.io.XDMFFile(MPI.COMM_WORLD, f'./geometries/cylinder_{i}.xdmf', "r") as xdmf:
                 mesh = xdmf.read_mesh()
-            mesh.geometry.x[:] *= 1000
+            mesh.geometry.x[:] *= 1000 # Scale mesh
             
             A, b, W, B, u0, p0 = get_system_mms(mesh, penalty_value, mu_value, direct)
             uh, ph, uh_out, niters, rnorm = solve(A, B, b, W, direct)
@@ -371,7 +371,7 @@ if __name__ == '__main__':
             u0_mag_max = u0_mag.max()
             u0_Linf = mesh.comm.allreduce(u0_mag_max, op=MPI.MAX)
 
-            from imports.utilities import calc_error_H1, calc_error_L2, calc_error_Hdiv
+            from utilities.helpers import calc_error_H1, calc_error_L2, calc_error_Hdiv
             eu_H1  = calc_error_H1(u_approx=uh, u_exact=u0, dX=dx)
             eu_L2  = calc_error_L2(u_approx=uh, u_exact=u0, dX=dx)
             ep_L2  = calc_error_L2(u_approx=ph, u_exact=p0, dX=dx)
@@ -427,7 +427,7 @@ if __name__ == '__main__':
             uh, ph, uh_out, niters, rnorm = solve(A, B, b, W, direct)
 
             # Calculate mean pressure and subtract it from the calculated pressure
-            from imports.mesh import mark_boundaries_flow
+            from utilities.mesh import mark_boundaries_flow
             ft = mark_boundaries_flow(mesh, inflow_outflow=False)
             dx = ufl.Measure('dx', domain=mesh)
[…]

### 2025-01-27 scripts/utilities/create_removed_circle_square_mesh.py

@@ -1,113 +1,0 @@
-import gmsh
-
-import numpy   as np
-
-from   mpi4py  import MPI
-
-gmsh.initialize()
-
-# Mesh and domain parameters
-L = 1 # Length of domain [m]
-H = 1 # Height of domain [m]
-r = 0.1 # Radius of cylinder [m]
-x_c = 0.5 # Distance from inlet boundary to cylinder tip in x direction [m]
-y_c = 0.5 # Distance from lower boundary to cylinder bottom in y direction [m]
-
-c_x = 0.5 # x coordinate of cylinder center [m]
-c_y = 0.5 # y coordinate of cylinder center [m]
-
-gmsh_dim = 2
-mesh_comm = MPI.COMM_WORLD
-model_rank = 0
-if mesh_comm.rank == model_rank:
-    box_domain = gmsh.model.occ.addRectangle(0, 0, 0, L, H, tag = 1)
-    cylinder   = gmsh.model.occ.addDisk(c_x, c_y, 0, r, r)
-
-# Remove the cylinder from the box domain
-if mesh_comm.rank == model_rank:
-    fluid_domain = gmsh.model.occ.cut([(gmsh_dim, box_domain)], [(gmsh_dim, cylinder)])
-    gmsh.model.occ.synchronize()
-
-# Add physical volume marker for the fluid mesh
-fluid_marker = 1
-if mesh_comm.rank == model_rank:
-    volumes = gmsh.model.getEntities(dim = gmsh_dim)
-    assert(len(volumes) == 1)
-    gmsh.model.addPhysicalGroup(volumes[0][0], [volumes[0][1]], fluid_marker)
-    gmsh.model.setPhysicalName(volumes[0][0], fluid_marker, "Fluid")
-
-# Tag the boundaries of the mesh by computing the centers of mass of the boundaries
-LEFT    = 1
-RIGHT   = 2
-FRONT   = 3
-BACK    = 4
-BOTTOM  = 5
-TOP     = 6
-CYLINDER = 7
-left, right, bottom, top, cyl = [], [], [], [], []
-
-#INLET, OUTLET, WALL, CYLINDER = 2, 3, 4, 5 # Marker values
-#inflow, outflow, walls, cyl = [], [], [], []
-
-if mesh_comm.rank == model_rank:
-    # Get boundaries and loop over all
-    boundaries = gmsh.model.getBoundary(volumes, oriented = False)
-    for boundary in boundaries:
-        com = gmsh.model.occ.getCenterOfMass(boundary[0], boundary[1])
[…]

### 2025-01-27 scripts/utilities/create_removed_sphere_cube_mesh.py

@@ -1,119 +1,0 @@
-import gmsh
-
-import numpy   as np
-
-from   mpi4py  import MPI
-
-gmsh.initialize()
-
-# Mesh and domain parameters
-L = 1 # Length of domain [m]
-H = 1 # Height of domain [m]
-D = 1 # Depth of domain [m]
-r = 0.2 # Radius of sphere [m]
-
-c_x = 0.5 # x coordinate of sphere center [m]
-c_y = 0.5 # y coordinate of sphere center [m]
-c_z = 0.5 # z coordinate of sphere center [m]
-
-gmsh_dim = 3
-mesh_comm = MPI.COMM_WORLD
-model_rank = 0
-if mesh_comm.rank == model_rank:
-    box_domain = gmsh.model.occ.addBox(0, 0, 0, L, H, D, tag = 1)
-    ball       = gmsh.model.occ.addSphere(c_x, c_y, c_z, r)
-
-# Remove the cylinder from the box domain
-if mesh_comm.rank == model_rank:
-    fluid_domain = gmsh.model.occ.cut([(gmsh_dim, box_domain)], [(gmsh_dim, ball)])
-    gmsh.model.occ.synchronize()
-
-# Add physical volume marker for the fluid mesh
-fluid_marker = 10
-if mesh_comm.rank == model_rank:
-    volumes = gmsh.model.getEntities(dim = gmsh_dim)
-    assert(len(volumes) == 1)
-    gmsh.model.addPhysicalGroup(volumes[0][0], [volumes[0][1]], fluid_marker)
-    gmsh.model.setPhysicalName(volumes[0][0], fluid_marker, "Fluid")
-    
-# Tag the boundaries of the mesh by computing the centers of mass of the boundaries
-LEFT    = 1
-RIGHT   = 2
-FRONT   = 3
-BACK    = 4
-BOTTOM  = 5
-TOP     = 6
-SPHERE  = 8
-left, right, front, back, bottom, top, sphere = [], [], [], [], [], [], []
-
-#INLET, OUTLET, WALL, CYLINDER = 2, 3, 4, 5 # Marker values
-#inflow, outflow, walls, cyl = [], [], [], []
-
-if mesh_comm.rank == model_rank:
-    # Get boundaries and loop over all
-    boundaries = gmsh.model.getBoundary(volumes, oriented = False)
-    for boundary in boundaries:
-        com = gmsh.model.occ.getCenterOfMass(boundary[0], boundary[1])
-        if np.allclose(com, [0, H/2, D/2]):
[…]

### 2025-01-27 scripts/utilities/hF_measures.py

@@ -1,117 +1,0 @@
-import ufl
-
-import dolfinx as dfx
-
-from ufl import dot, avg, sym, grad, jump, sqrt, inner, dx, ds, dS
-from petsc4py import PETSc
-
-# NOTE: these are the jump operators from Krauss, Zikatonov paper.
-# Jump is just a difference and it preserves the rank 
-Jump = lambda arg: arg('+') - arg('-')
-# Average uses dot with normal and AGAIN MINUS; it reduces the rank
-Avg = lambda arg, n: 0.5*(dot(arg('+'), n('+')) - dot(arg('-'), n('-')))
-# Action of (1 - n x n)
-Tangent = lambda v, n: v - n*dot(v, n)    
-
-Normal = lambda u, n: n*dot(u, n)
-
-
-def Stabilization(u, v, mu, stab_h, stab_gamma):
-    '''Displacement/Flux Stabilization from Krauss et al paper'''
-    mesh = u.ufl_domain().ufl_cargo()
-
-    get_nom, get_den = get_penalty(stab_h, stab_gamma)
-    penalty = get_nom(u)
-
-    hA = avg(get_den(mesh))
-
-    n = ufl.FacetNormal(mesh)
-
-    D = lambda v: sym(grad(v))
-
-    return (-inner(Avg(2*mu*D(u), n), Jump(Tangent(v, n)))*dS
-            -inner(Avg(2*mu*D(v), n), Jump(Tangent(u, n)))*dS
-            + 2*mu*(penalty/hA)*inner(Jump(Tangent(u, n)), Jump(Tangent(v, n)))*dS), penalty/hA
-
-
-def get_penalty(stab_h, stab_gamma):
-    '''Nom/Denominator of the penalty formula'''
-    nitsche_conformity_penalty = lambda u, stab_gamma=stab_gamma: stab_gamma
-
-    hA = {'diameter': CellDiameter2,
-          'edge': EdgeLength,
-          'centroid': CentroidDistance,
-          }[stab_h]
-
-    return nitsche_conformity_penalty, hA
-
-
-def CellDiameter2(mesh):
-    '''Length of edge as P0 edge function'''
-    Q = dfx.fem.FunctionSpace(mesh, 'Discontinuous Lagrange Trace', 0)
-    q = ufl.TestFunction(Q)
-
-    fh = dfx.fem.Function(Q)
-    hA = ufl.FacetArea(mesh)
[…]

### 2025-01-27 scripts/utilities/mesh.py

@@ -1,5 +1,4 @@
 import ufl
-import gmsh
 import meshio
 import numpy.typing
 
@@ -204,104 +203,6 @@ def create_ventricle_volumes_meshtags(mesh: dfx.mesh.Mesh) -> tuple((dfx.mesh.Me
     for i in reversed(ROI_tags): volume_marker[ROI_cells[i]] = ROI_tags[i-1] # Mark the cells in each ROI with the corresponding ROI tag
 
     return (dfx.mesh.meshtags(mesh, tdim, np.arange(num_volumes, dtype=np.int32), volume_marker), ROI_tags)
-
-def mesh_rectangle(mesh0: dfx.mesh.Mesh, ghost_mode: dfx.mesh.GhostMode):
-    """ Mesh a rectangle slice that lies in the yz-plane of the ventricles.
-
-    Parameters
-    ----------
-    mesh0 : dfx.mesh.Mesh
-        The brain ventricles mesh.
-
-    Returns
-    -------
-    dfx.mesh.Mesh
-        Rectangle slice mesh.
-    """
-    comm = mesh0.comm # MPI communicator
-    rank = comm.rank  # MPI process rank
-    gmsh.initialize()
-    
-    x_min = comm.allreduce(mesh0.geometry.x[:, 0].min(), op=MPI.MIN)
-    x_max = comm.allreduce(mesh0.geometry.x[:, 0].max(), op=MPI.MAX)
-    x_mid = .5*(x_min+x_max)
-    y_min = comm.allreduce(mesh0.geometry.x[:, 1].min(), op=MPI.MIN)
-    y_max = comm.allreduce(mesh0.geometry.x[:, 1].max(), op=MPI.MAX)
-    z_min = comm.allreduce(mesh0.geometry.x[:, 2].min(), op=MPI.MIN)
-    z_max = comm.allreduce(mesh0.geometry.x[:, 2].max(), op=MPI.MAX)
-        
-    if rank==0:
-        gmsh.model.occ.addRectangle(x=z_min, y=y_max/4, z=0, dx=z_max-z_min, dy=.5*(y_max-y_min), tag=1)
-        gmsh.model.occ.rotate(dimTags=[(2, 1)], x=x_mid, y=0, z=0, ax=0, ay=1, az=0, angle=np.pi/2)
-        gmsh.model.occ.synchronize()
-        surfaces = gmsh.model.getEntities(dim=2)
[…]

### 2025-02-03 paper/main.tex
Edits in Methods - Part I

@@
 
+\newcommand{\fixme}[1]{\textcolor{red}{#1}}
+
 % Title
@@
 
-\section*{Methods}\label{sec:methods}
+\section*{Methods}
+\label{sec:methods}
+
+\mer{@HH: I suggest you write \cref{fig:figure1}\textbf{a}, rather than \cref{fig:figure1} panel \textbf{a}, throughout. Increases signal-to-noise ratio.}
+
 \subsection*{Zebrafish maintenance and strains in photoconversion experiments}
-The animal facilities of zebrafish~(\emph{danio rerio}) we used are approved by the Norwegian Food Safety Authority (NFSA, Mattilsynet).
+The zebrafish~(\emph{danio rerio}) animal facilities used are approved by the Norwegian Food Safety Authority (NFSA, Mattilsynet).
 Furthermore, the zebrafish were maintained in accordance with the guidelines set by the NFSA and the European Communities Council Directive.
-
 The larval and adult zebrafish were raised under standard husbandry conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
@@
 
-Wholemount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at the 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described in D’Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Wholemount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at the 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described by D’Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
 Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+}) or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
@@
 \subsection*{Generation of \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}} line}
+\mer{MER: Could this heading be made understandable by non-experts?}
 The open reading frame (ORF) of the neuropeptide y (npy) signal peptide (\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal of zebrafish codon optimized Dendra2 DNA sequence.
-Then the conjugated DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and 3’ ends (GenScript Biotech), and the synthesized signal-Dendra2 DNA was inserted into the pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish} through restriction enzyme cloning (GenScript Biotech).
-
+Next the conjugated DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and 3’ ends (GenScript Biotech), and the synthesized signal-Dendra2 DNA was inserted into the pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish} through restriction enzyme cloning (GenScript Biotech).
 To generate the transgenic line, the 5xuas:Signal-Dendra2 plasmid DNA was used.
-A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg) was microinjected into one-cell stage embryos, as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}.
+A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg) was microinjected into one-cell stage embryos, as described by Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}.
 The injected embryos were raised to adulthood (F0).
@@
 The first 10 images were scanned without photoconversion to obtain a baseline value of fluorescence intensity, and the next 290 images were scanned while performing photoconversion.
-
 For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software were used.
@@
 \subsection*{Photoconversion data analysis}
-All data analysis was performed in MATLAB and the codes are available in the repository of this article: \url{repo-link}.
-
+
+Photoconversion data analysis was performed in MATLAB and the codes are \fixme{openly available\cite{zenodo-archive-for-repo-link-fixme}}.
 Following import of the image data, the photoconverted channel was aligned to correct for drift in $x,y$ directions using previously developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
 Only stable recordings were further analyzed.
-To increase the signal to noise ratio, the images were downsampled by a block average using a resampling factor of 6 (using the MATLAB function blockproc).
+To increase the signal-to-noise ratio, the images were downsampled by a block average using a resampling factor of 6 (using the MATLAB function blockproc).
 The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as $\Delta F$$)$ was calculated for each pixel at each time point of the data.
@@
 
-Anesthetized 2 dpf control zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads (SPHERO Fluorescent Yellow Particles 1\% w/v, $F = 0.16$ mm) diluted in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITC-dextran; Sigma-Aldrich, R9379) dissolved in artificial cerebrospinal fluid.
-Artificial cerebrospinal fluid composition was as follows: 124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O, 1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3}, 2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
+Anesthetized 2 dpf control zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads (SPHERO Fluorescent Yellow Particles 1\% w/v, $F = 0.16$ mm) diluted in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITC-dextran; Sigma-Aldrich, R9379) dissolved in artificial CSF.
+Artificial CSF composition was as follows: 124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O, 1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3}, 2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
 The needles used for the injections were pulled with a Sutter Instrument Co.
@@
 A single optical section was obtained.
-Particle tracking was done using TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis} and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
+Particle tracking was done using TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis} and plotted using MATLAB, as described by Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
 The parameters for TrackMate were as follows.
@@
 Next, the Simple LAP tracker was used with settings: max frame gap: 2; alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0; splitting max distance: 15.0; allow gap closing: true; allow track splitting: false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
-Only the particle tracks with at least 30 data points, while simultaneously covering a distance of at least 8.8 $\mu$m, were plotted in~\cref{fig:figure1} (panels \textbf{b} and \textbf{c}).
+Only the particle tracks with at least 30 data points, while simultaneously covering a distance of at least 8.8 $\mu$m, were shown (\cref{fig:figure1}, panels \textbf{b} and \textbf{c}).
 
@@
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}.
-The standard mesh consisted of 132 134 tetrahedral cells associated with a total of 943 820 degrees of freedom, and the mesh had a maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m).
+The standard mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) \mer{edge length} of 14.9 $\mu$m (4.68 $\mu$m).
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic  (anterior), the di-/mesencephalic  (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts.
-
-Motile cilia were shown to line certain parts of the ventricular surface~\cite{Olstad2019CiliaryDevelopment}, as marked with pink in~\cref{fig:figure1} (panel \textbf{d}).
-Beating motion of the cilia generates cerebrospinal fluid (CSF) flow with rotational structures in the brain ventricles, resulting in a compartmentalized flow~(\cref{fig:figure1}, panels \textbf{a}--\textbf{c}).
-Meanwhile, the beating heart of the zebrafish embryo induces a pulsatile CSF flow component.
-\begin{figure}[hbt!]
+Parts of the ventricular surfaces were marked to be lined with motile cilia~\cite{Olstad2019CiliaryDevelopment} (\cref{fig:figure1}\textbf{d}, pink markers).
+\mer{MER: @HH: Check if you mean edge length or mesh cell size here.}
+\begin{figure}%[hbt!]
     \centering
@@
 
-\subsection*{Computational model of cerebrospinal fluid dynamics}
-We model the flow of cerebrospinal fluid (CSF) in the brain ventricles by the time-dependent, incompressible Stokes equations: find the fluid velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$ and the fluid pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
+\subsection*{Computational CSF dynamics}
+
+The beating motion of the cilia generates CSF flow with steady rotational structures~\cite{Olstad2019CiliaryDevelopment} within the brain ventricles (\cref{fig:figure1}, panels \textbf{a}--\textbf{c}).
+In addition, cardiac pulsations induces pulsatile CSF flow.
+We model this flow of CSF in the brain ventricles by the time-dependent, incompressible Stokes equations which read as follows.
+Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$ and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
 \begin{subequations}
@@
 \end{equation*}
-where $\nn$ is the outer unit normal of the surface $\Gamma = \partial\Omega$, and $P_{\nn}(\rr)$ is the tangential  projection of a vector $\rr$ onto $\Gamma$.
+where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$, and $P_{\nn}(\rr)$ is the tangential  projection of a vector $\rr$ onto $\Gamma$.
 We consider three types of boundary conditions:  (i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$), (ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$), and (iii) \emph{free slip} (no flow normal to the boundary $\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
 Unless noted otherwise, the free-slip condition is applied on the boundary.
-We use the initial conditions $\uu(\xx, 0)=\mathbf{0}$ and $p(\xx, t) = 0$ for all $\xx\in\Omega$.
+We use the initial condition\mer{s} $\uu(\xx, 0)=\mathbf{0}$ \mer{and $p(\xx, t) = 0$} for all $\xx\in\Omega$.
+\mer{MER: I don't think you use an initial condition on the pressure.
+Please check and remove if so.
+You can also just write: ``We assume that the system starts at rest ($\uu(t = 0) = \mathbf{0}$)''.}
 
 \subsection*{Cilia-driven flow}
-On the boundary $\Gc$ of the ciliated regions of the ventricle walls~(pink-colored facets in~\cref{fig:figure1}, panel \textbf{d}), we impose the tangential traction $\bsigpar=\btau$ to represent the forces from the cilia acting on the cerebrospinal fluid.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where $\lambda(\xx)$ is a function that is chosen differently for the cilia regions considered~(see~\cref{subsec:appendixA1}).
-The sign of the vector $\rr=\pm(1, 0, 1)$ also depends on the cilia region.
-Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by comparing simulations with experimental data~\cite{Olstad2019CiliaryDevelopment}.
+On the ciliated regions of the ventricle walls $\Gc$ (\cref{fig:figure1}, panel \textbf{d}), we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces of the cilia acting on the CSF.
+We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$ and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the cilia region (see~\cref{subsec:appendixA1}).
+Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by model calibration against the experimental data~\cite{Olstad2019CiliaryDevelopment}.
 
 \subsection*{Flow induced by cardiac pulsations}\label{subsec:pressure_bcs}
-To induce a pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and $\Tilde{p}(t)=-A\sin{\omega t}$ on two separate parts of the boundary $\Gp$, located anterior and posterior, respectively, on the brain ventricles geometry~(blue-colored facets in~\cref{fig:figure1}, panel \textbf{d}).
+To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts of the boundary $\Gp$~(\cref{fig:figure1}, panel \textbf{d}, blue markers).
 The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow, and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-The angular cardiac frequency $\omega=2\pi f=6.97$ rad/s was determined by measurements of the cardiac frequency $f=2.22$ Hz.
-
-\iffalse
-\subsection*{Computational cerebrospinal fluid dynamics in a moving reference frame}
- An Arbitrary Lagrangian Eulerian (ALE) formulation~\cite{san2009convergence} is used as an alternative to the normal pressure boundary conditions to model back-and-forth flow induced by cardiac pulsations.
+The angular cardiac frequency $\omega=2\pi f=6.97$ rad/s was set based on a measured cardiac frequency of $f=2.22$ Hz.
+
+%% \iffalse
+%% \subsection*{Computational cerebrospinal fluid dynamics in a moving reference frame}
+%%  An Arbitrary Lagrangian Eulerian (ALE) formulation~\cite{san2009convergence} is used as an alternative to the normal pressure boundary conditions to model back-and-forth flow induced by cardiac pulsations.
 In a reference frame moving with a velocity $\uuref=(A_{\mathrm{ref}}\sin{\omega t}, 0, 0)$, we reformulate the Stokes equations~\eqref{eq:stokes_eqs} using an ALE formulation:
-\begin{subequations}
-    \begin{alignat}{2}
-        \rho\bigg(\pdifft{\uu} + (\uu_{\mathrm{ref}}\cdot\nabla)\uu\bigg) &= \nabla\cdot\bm{\sigma}(\uu, p), \label{eq:mom_eq_ALE}\\
-        \nabla\cdot\uu &= 0.
-    \end{alignat}
-    \label{eq:stokes_eqs_ALE}%
-\end{subequations}%
-We then solve for the velocity $\mathbf{w} = \uu - \uuref$ in the moving reference frame, where $\uu$ is the velocity in the fixed reference frame.
+%% \begin{subequations}
+%%     \begin{alignat}{2}
+%%         \rho\bigg(\pdifft{\uu} + (\uu_{\mathrm{ref}}\cdot\nabla)\uu\bigg) &= \nabla\cdot\bm{\sigma}(\uu, p), \label{eq:mom_eq_ALE}\\
+%%         \nabla\cdot\uu &= 0.
+%%     \end{alignat}
+%%     \label{eq:stokes_eqs_ALE}%
+%% \end{subequations}%
+%% We then solve for the velocity $\mathbf{w} = \uu - \uuref$ in the moving reference frame, where $\uu$ is the velocity in the fixed reference frame.
 The amplitude $A_{\mathrm{ref}}=919$ $\mu$m/s, calibrated based on experimental data, determines the magnitude of the pulsatile flow, and $\omega=2\pi f$ is the angular cardiac frequency.
 In the ALE formulation, we consider the impermeability boundary condition $\mathbf{w}\cdot\nn=0$ in the normal direction and the free-slip boundary condition $\bsigpar(\mathbf{w}, p) = \mathbf{0}$ in the tangential direction.
-\fi
+%% \fi
 
@@
 \subsection*{Numerical approximation of the flow equations}
+
+\mer{associated with a total of 943 820 degrees of freedom}
+
 The Stokes equations~\eqref{eq:stokes_eqs} were discretized with a finite element method.

### 2025-02-03 paper/main.tex
Edit in Methods - Part II. Some items to discuss.

@@
 
-\subsection*{Image-based computational geometry of zebrafish brain ventricles}
+\subsection*{Image-based computational geometries of zebrafish brain ventricles}
 We generated a 3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}.
@@
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}.
-The standard mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) \mer{edge length} of 14.9 $\mu$m (4.68 $\mu$m).
+The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) \mer{edge length} of 14.9 $\mu$m (4.68 $\mu$m).
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic  (anterior), the di-/mesencephalic  (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts.
@@
 
+%\subsection*{Computational geometry variations}
+The morphology and geometry of the brain ventricles vary across zebrafish individuals, and under physiological and pathological conditions.
+Motivated by an interest in how geometry impacts solute distribution, we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, the middle ventricle, the mid-hind brain connection, and all three simultaneously.
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+\mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}
+
+%% The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
+Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
+Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaenously.
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+
 \subsection*{Computational CSF dynamics}
@@
     \begin{align}
-  \rho\pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}\mbox{ in }\Omega,\label{eq:stokes_eq_mom}\\
-  \nabla \cdot \uu &= 0\mbox{ in }\Omega,
+      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
+      \quad \text{in } \Omega,
+      \label{eq:stokes_eq_mom}\\
+      \nabla \cdot \uu &= 0
+      \quad  \text{in } \Omega,
   \end{align}
@@
 
-\subsection*{Computational model of solute transport}
-We simulate transport of photoconverted proteins in the brain ventricles by modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and time $t > 0$ by the advection-diffusion equation
-\begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0\mbox{  in }\Omega,
+\subsection*{Computational model of solute transport after photoconversion}
+We simulate transport of photoconverted proteins within the brain ventricles by modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and time $t > 0$ by the advection-diffusion equation
+\begin{equation}
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
     \label{eq:adv_diff_strong}
 \end{equation}
-where $\mathbf{J}$ is the total concentration flux. The total concentration flux is assumed to consist of an advective flux and a diffusive flux:
-\begin{equation*}
-    \JJ = c\uu - D\nabla c\mbox{ in }\Omega.
+where the total concentration flux $\mathbf{J}$ is assumed to consist of an advective and a diffusive flux:
+\begin{equation*}
+    \JJ = c\uu - D\nabla c .
 \end{equation*}
 Here, $\uu$ is the cerebrospinal fluid velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs}, and $D$ is the molecular diffusion coefficient of the solute.
-The diffusion coefficient was estimated through extrapolation of previous measurements~\cite{GuraSadovsky2017MeasurementExpansion, Mahmood2023ExosomeTemperature, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} via the Stokes-Einstein relation.
-We elaborate on the extrapolation in a later section.
-
-We set the initial condition $c(\xx, 0)=0$ for all $\xx\in\Omega$.
-The ventricular walls are assumed to be impermeable, except for at the pressure boundary $\Gamma_p$.
-We consider three different boundary conditions: (i) \emph{no flux} ($\JJ\cdot\nn=0$), (ii) \emph{influx} (time-periodic condition on the total flux $(\JJ\cdot\nn)|_{\mathrm{in}}^{n+1}=(\JJ\cdot\nn)|_{\mathrm{out}}^{n}$) and (iii) \emph{outflux} (zero diffusive flux $D\nabla c\cdot\nn=0$).
-Unless stated otherwise, the no-flux condition $\JJ\cdot\nn=0$ was applied on the boundary.
-%(ii) \emph{injection site} (imposing the Dirichlet boundary condition $c=\Tilde{c}$),
-\subsection*{Modeling protein photoconversion in the brain ventricles}
-To represent protein photoconversion in a region $\Omega_{\mathrm{pc}}\subset\Omega$, we prescribe a time-dependent value to the solute concentration in $\Omega_{\mathrm{pc}}$, such that $c(\xx, t)$ for all $\xx\in\Omega_{\mathrm{pc}}$ and $t>0$.
-The subdomain $\Omega_{\mathrm{pc}}$ is a region in the dorsal part of the diencephalic ventricle that corresponds to the region where photoconversion was performed in experiments.
-Specifically, for all $\xx\in\Omega_{\mathrm{pc}}$, we set the concentration to
-\begin{equation}
-c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}}.
-\label{eq:injection_curve}
-\end{equation}
-The value $a=65$ was chosen so that~\eqref{eq:injection_curve} is similar to the fluorescence intensity curve observed in the physical photoconversion experiments.
-
-Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for.
+Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
+The ventricular walls are assumed to be impermeable (admitting \emph{no flux} i.e.~$\JJ\cdot\nn=0$), except at the anterior/posterior boundary $\Gamma_p$.
+\fixme{There, we consider either prescribed \emph{influx} in the form of a time-periodic condition on the total flux $(\JJ\cdot\nn)|_{\mathrm{in}}^{n+1}=(\JJ\cdot\nn)|_{\mathrm{out}}^{n}$ and/or \emph{outflux} with zero diffusive flux $D\nabla c\cdot\nn=0$.}
+\mer{MER: Could we make this section about the boundary conditions easier to read? I've had a go at it, please check.}
+
+\fixme{Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for.
 We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$; $\Gout$ denotes the part where $\uu\cdot\nn > 0$.
@@
 This was done to approximate a periodic boundary condition.
-On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.
+On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.}
+\mer{MER: I moved this paragraph from the section below, because it seemed to belong here. But needs edits.}
+
+%Unless stated otherwise, the no-flux condition $\JJ\cdot\nn=0$ was applied on the boundary.
+%(ii) \emph{injection site} (imposing the Dirichlet boundary condition $c=\Tilde{c}$),
+
+%\subsection*{Modeling protein photoconversion}
+
+To computationally represent protein photoconversion in a region $\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1), we prescribe a given time-dependent value to the solute concentration in this region.
+% in $\Omega_{\mathrm{pc}}$.
+%, such that $c(\xx, t)$ for all $\xx\in\Omega_{\mathrm{pc}}$ and $t>0$.
+Mimicking the experimental protocol, we consider the dorsal part of the diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
+\begin{equation}
+  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}}
+  \qquad \xx \in \Omega_{\mathrm{pc}}, \quad \fixme{t > 0}.
+\label{eq:injection_curve}
+\end{equation}
+The value $a=65$ was chosen to fit the fluorescence intensity curve observed in the physical photoconversion experiments.
 
@@
 
-\subsection*{Physical parameters}\label{subsec:parameters}
-The cerebrospinal fluid density $\rho$ and dynamic viscosity $\mu$ were set following the work of Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
-We considered a range of small, medium and large molecules with three different diffusion coefficients $D_1, D_2$ and $D_3$ (cf.
-the following section for details on determining their values).
-Experimental data~\cite{Olstad2019CiliaryDevelopment} indicate velocities proximate to the ventricular walls of $27.4 \pm 5.4 \ \mu$m/s and $2.6 \pm 0.6 \ \mu$m/s in the dorsal and ventral regions of the diencephalic ventricle, respectively.
-In the telencephalic ventricle, the velocities were estimated at $4.7 \pm 1.3 \ \mu$m/s.
+\subsection*{Estimation of diffusion coefficients via the Stokes-Einstein relation}
+%\label{subsec:diff_coeffs}
+
+Motivated by an interest in molecules that are significant in neural development, we study the transport of molecules resembling Dendra2 Fluorescent Protein (Dendra2), Starmaker+Green Fluorescent Protein (STM+GFP) and Exosomes.
+To estimate the diffusion coefficients of these, when and if not available in the literature, we use the Stokes--Einstein relation:
+\begin{equation}
+    D = \frac{k_B T}{6\pi \mu R} ,
+    \label{eq:D_stokes_einstein}
+\end{equation}
+which is an expression for the diffusion coefficient of a spherical molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
+In~\eqref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant, $T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the solvent (in this case the CSF), and $R$ is the radius of the molecule.
+For the exosomes, we calculate $D$ using~\eqref{eq:D_stokes_einstein} with $R=200$ nm.
+This radius covers the slowest diffusing exosomes, since the smaller exosomes would have diffusion coefficients similar to the other molecules.
+For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
+The resulting diffusion coefficients used in the simulations are summarized in \cref{tab:parameter_table}.
+
+%% In summary, in the simulations, we use the diffusion coefficients $D_1$, $D_2$ and $D_3$ (\cref{tab:parameter_table}) for these three molecules
+
+%Implicit in this approach is the assumption that the proteins all have the same density.
+
+%% The molecular diffusion coefficients were estimated in part based on values reported in the literature, and in part via extrapolation with the Stokes--Einstein relation (\cref{tab:diff_coeff_table}).
+The Stokes-Einstein relation
+\begin{table}[h!]
+    \centering
+    \label{tab:diff_coeff_table}
+    \begin{tabular}{l|ccc}
+        \toprule
+        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
+        \midrule 
+        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight} & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
+        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
+        STM+GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{5.75e-11}$ & * \\
+        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
+        \bottomrule
+    \end{tabular}
+    \caption{Molecular mass and diffusion coefficients of simulated solutes.
+STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+(*) The value was extrapolated based on the value of $D$ for GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that $D$ scales with the cube root of the molecule mass.
+(\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
+\end{table}
+
+%% The diffusion coefficient was estimated through extrapolation of previous measurements~\cite{GuraSadovsky2017MeasurementExpansion, Mahmood2023ExosomeTemperature, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} via the Stokes-Einstein relation
+
+\subsection*{Physical parameters}
+%\label{subsec:parameters}
+The cerebrospinal fluid density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
+We considered small, medium and large-sized molecules by three different diffusion coefficients $D_1, D_2$ and $D_3$ (\Cref{tab:parameter_table}).
+Experimental data~\cite{Olstad2019CiliaryDevelopment} indicate \fixme{velocities} proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and $2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the diencephalic ventricle, respectively.
+In the telencephalic ventricle, the velocities were estimated at $4.7 \pm 1.3$ \textmu m/s.
 We calibrated $\tau$ and $A$ heuristically by comparing these experimental velocity values with the simulated, maximum velocity magnitude.
 In addition, particle tracking data of pulsatile motion~(\cref{sec:appC_particle_transport}) was used in the calibration process to determine the relative contributions of the cardiac pulsations, as compared to the cilia-driven flow, to the velocity magnitude.
+\mer{MER: What velocities?
+Net velocities?
+Velocity magnitude aka speed?
+Also, haven't you said this part about the experimental data already?
+Either place the details there, or all here.
+I suggest there.}
+\mer{MER: I suggest you move the parts relevant for cilia/cardiac flow to where you mentioned it first, and then merge this section with the Estimation of diffusion ....
+Just refer to \cref{tab:parameter_table}.
+Actually, unsure if you need it.
+You say everything in the text or in the other Table right?}
 \begin{table}[h!]
     \centering
-    \caption{Physical parameters of the flow and transport models.
-(*) Calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-(\textdagger) Estimated based on experimental data~\cite{GuraSadovsky2017MeasurementExpansion, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}.}
-    \label{tab:parameter_table}
     \begin{tabular}{lcccc}
@@
     \end{tabular}
+    \caption{Physical parameters of the flow and transport models.
+(*) Calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
+(\textdagger) Estimated based on experimental data~\cite{GuraSadovsky2017MeasurementExpansion, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}.}
+    \label{tab:parameter_table}
 \end{table}
 
-\subsection*{Estimation of diffusion coefficients with the Stokes-Einstein relation}\label{subsec:diff_coeffs}
-Motivated by an interest in molecules that are significant in neural development, we study the transport of molecules resembling Dendra2 Fluorescent Protein (Dendra2), Starmaker+Green Fluorescent Protein (STM+GFP) and Exosomes.
-In simulations, we use the diffusion coefficients $D_1$, $D_2$ and $D_3$ (\cref{tab:parameter_table}) for these three molecules, respectively.
-The molecular diffusion coefficients were estimated in part based on values reported in the literature, and in part via extrapolation with the Stokes--Einstein relation (\cref{tab:diff_coeff_table}).
-The Stokes-Einstein relation
-\begin{equation}
-    D = \frac{k_B T}{6\pi \mu R}
-    \label{eq:D_stokes_einstein}
-\end{equation}
-is an expression for the diffusion coefficient of a spherical molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
-In~\eqref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant, $T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the solvent (in this case the cerebrospinal fluid), and $R$ is the radius of the molecule.
-For the exosomes, we calculate $D$ using~\eqref{eq:D_stokes_einstein} with $R=200$ nm.
-We chose this radius to cover the slowest diffusing exosomes, since the smaller exosomes would have diffusion coefficients similar to the other molecules.
-For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ should scale roughly with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-Implicit in this approach is the assumption that the proteins all have the same density.
-\begin{table}[h!]
-    \centering
-    \caption{Estimated diffusion coefficients and diffusion coefficients reported in the literature.
-STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-(*) The value was extrapolated based on the value of $D$ for GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that $D$ scales with the cube root of the molecule mass.
-(\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
-    \label{tab:diff_coeff_table}
-    \begin{tabular}{l|ccc}
-        \toprule
-        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
-        \midrule 
-        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight} & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
-        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM+GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{5.75e-11}$ & * \\
-        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\subsection*{Model versions and physiological scenarios}\label{subsec:model_versions}
-We have introduced boundary conditions to model two separate driving forces of cerebrospinal fluid (CSF) flow, namely motile cilia and cardiac pulsations.
-To distinguish the impact of each component, three different setups for the flow model were considered~(\cref{tab:flow_model_versions}):
+\subsection*{Computational flow scenarios}
+%\label{subsec:model_versions}
+To study the impact of the motile cilia and the cardiac pulsations on the CSF flow, we consider the following computational flow scenarios, each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
 \begin{itemize}
-    \item Model 0: The baseline model representing a wild-type zebrafish. Both cilia forces and cardiac pulsations are included in the model.
-
-    \item Model I: Only cilia forces are modeled, no cardiac pulsations.
-
-    \item Model II: Only cardiac pulsations are modeled, no cilia forces.
+    \item A \emph{baseline} flow model representing a wild-type zebrafish including contributions both from the cilia forces and the cardiac pulsations.
+In this scenario, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.
+% Model 0
+
+    \item A \emph{no-cardiac/cilia-only} flow model including contributions from the cilia forces but no cardiac pulsations.
+Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$, and \mer{XXX on the anterior/posterior boundary $\Gp$.} % Model I
+
+    \item A \emph{no-cilia/cardiac-only} flow model including contributions from the cardiac pulstaions but no cilia forces.
+Here, we set the tangential traction to zero on the cilia boundary $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.
+% Model II
+    %\item Model II: Only cardiac pulsations are modeled, no cilia forces.
 
@@
 \end{itemize}
-\begin{table}[h!]
-    \centering
-    \caption{A summary of the flow model versions. For all model versions, we consider a free slip boundary condition on $\Gs=\Gamma\setminus\left(\Gc\cup\Gp\right)$.}
-    \label{tab:flow_model_versions}
-    \begin{tabular}{c|c@{\hskip 0.4in}c}
-       \toprule
-       Model & Driving force & Flow BCs \\ %& Domain motion \\
-       \midrule
-       Baseline (0)   & Cilia and cardiac & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$, \\ normal pressure $\Tilde{p}(t)$ on $\Gp$} \\[0.3in] %& No\\[0.3in]
-       No cardiac (I) & Cilia   & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$} \\[0.3in]%& No\\[0.3in]
-       No cilia (II) & Cardiac & \makecell[c]{Normal pressure $\Tilde{p}(t)$ on $\Gp$} \\% & No\\[0.3in]
-       %No cilia (IIb) & Cardiac & \makecell[l]{Impermeability $\mathbf{w}\cdot\nn=0$ and \\ free slip $\bsigpar(\mathbf{w}, p)=\mathbf{0}$ on $\Gamma$}  & Yes \\
-       \bottomrule
-    \end{tabular}
-\end{table}
-
+
+%% \begin{table}[h!]
+%%     \centering
+%%     \caption{A summary of the flow model versions. For all model versions, we consider a free slip boundary condition on $\Gs=\Gamma\setminus\left(\Gc\cup\Gp\right)$.}
+%%     \label{tab:flow_model_versions}
+%%     \begin{tabular}{c|c@{\hskip 0.4in}c}
+%%        \toprule
+%%        Model & Driving force & Flow BCs \\ %& Domain motion \\
+%%        \midrule
+%%        Baseline (0)   & Cilia and cardiac & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$, \\ normal pressure $\Tilde{p}(t)$ on $\Gp$} \\[0.3in] %& No\\[0.3in]
+%%        No cardiac (I) & Cilia   & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$} \\[0.3in]%& No\\[0.3in]
+%%        No cilia (II) & Cardiac & \makecell[c]{Normal pressure $\Tilde{p}(t)$ on $\Gp$} \\% & No\\[0.3in]
+%%        %No cilia (IIb) & Cardiac & \makecell[l]{Impermeability $\mathbf{w}\cdot\nn=0$ and \\ free slip $\bsigpar(\mathbf{w}, p)=\mathbf{0}$ on $\Gamma$}  & Yes \\
+%%        \bottomrule
+%%     \end{tabular}
+%% \end{table}
+
+\mer{MER: Let's discuss the paragraphs below and see where they fit best.}
 When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
@@
 For the three scenarios, we simulate CSF flow modeled by the Stokes equations~\eqref{eq:stokes_eqs} with the modified boundary conditions, and use the resulting velocity field in transport simulations.
-
-The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
-Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
-Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaenously.
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
 
@@
 \subsection*{Modification of ventricles geometry impacts protein distribution}
+
+The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
+Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
+Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaenously.
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+
 We simulate flow and transport in four alternative brain ventricles meshes: one where the connection between the anterior and middle ventricles is constricted; one where the connection between the middle and posterior ventricles is constricted; one where the middle ventricle is shrunk in the lateral direction; the combination of the above three modifications~(\cref{fig:figure6_sim_results_compare_geometries}, panel \textbf{a}).

### 2025-02-03 paper/main.tex
Edit in Methods - Part III

@@
 \end{equation*}
-Here, $\uu$ is the cerebrospinal fluid velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs}, and $D$ is the molecular diffusion coefficient of the solute.
+Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs}, and $D$ is the molecular diffusion coefficient of the solute.
 Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
@@
 %\label{subsec:parameters}
-The cerebrospinal fluid density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
+The CSF density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
 We considered small, medium and large-sized molecules by three different diffusion coefficients $D_1, D_2$ and $D_3$ (\Cref{tab:parameter_table}).
@@
 
-\mer{MER: Let's discuss the paragraphs below and see where they fit best.}
+\mer{MER: Let's discuss the paragraphs below and see where they fit best.
+I think we can drop the first paragraph (you said this already).
+I find the second paragraph to be somewhat confusing (low signal-to-noise ratio).}
 When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
@@
 \subsection*{Quantities of interest}
-We quantify the transport of solute by calculating the mean concentrations
+We calculate the mean solute concentrations
 \begin{equation}
@@
 \end{equation}
-in the regions of interest (ROIs) $\Omega_i$ as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$.
-The dynamics of ROI 1 follows from imposing~\cref{eq:injection_curve}.
-As another way of quantifying transport, we report the times $\hat{t}_i$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}_i$.
-We use $\hat{c}_i=0.25$ for regions of interest 1--4 and $\hat{c}_i=0.10$ for regions 5 and 6.
+in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$) as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$.
+The dynamics of ROI 1 follows directly from~\eqref{eq:injection_curve}.
+In addition, we report time-to-threshold: the time $\hat{t}_i$ when the mean concentration $\overline{c}_i$ first exceed a threshold value $\hat{c}_i$.
+We use $\hat{c}_i=0.25$ for ROI 1--4 and $\hat{c}_i=0.10$ for ROI 5--6.
 
@@
 \end{equation*}
-Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, whereas $D$ is the solute diffusion coefficient as previously.
+Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, and $D$ is the solute diffusion coefficient.
 To assess the assumption that the CSF flow is governed by the Stokes equations, we also compute the Reynolds number
@@
 \end{equation*}
-with $L_r$ and $U_r$ as the length and velocity scales characteristic of the flow.
+with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
 
 %-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
-\subsection*{Numerical approximation of the flow equations}
-
-\mer{associated with a total of 943 820 degrees of freedom}
-
-The Stokes equations~\eqref{eq:stokes_eqs} were discretized with a finite element method.
-In time, we employ a first-order implicit Euler discretization.
-We chose the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
-For the spatial discretization, we used piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
-The BDM elements have degrees of freedom associated with integral moments of the velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems}, thus we enforced the impermeability condition $\uu\cdot\nn=0$ strongly.
-We imposed the boundary conditions for both the tangential traction $\bsigpar$ and the normal pressure $\Tilde{p}(t)$ weakly.
-For the pressure, we used piecewise constant elements, referred to as zeroth order discontinuous Galerkin (DG) elements.
-The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a stable discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-Since the divergence of the velocity is a subspace of the pressure space for this scheme, the divergence-free condition of the velocity is satisfied exactly on each element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
-The BDM discretization includes a penalty parameter $\gamma$ which needs to be chosen large enough to ensure stability of the finite element method.
-We set $\gamma=10.$
-
+\subsection*{Numerical approximation of the Stokes equations}
+
+The Stokes equations~\eqref{eq:stokes_eqs} are discretized with a finite element method in space, while in time, we employ a first-order implicit Euler discretization.
+We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
+For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
+The BDM elements have degrees of freedom associated with integral moments of the velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems}, thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
+We impose the boundary conditions for both the tangential traction $\bsigpar$ and the normal pressure $\Tilde{p}(t)$ weakly.
+For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
+The resulting total number of degrees of freedom at each time step is 943 820.
+\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming but stable discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
+The discretization includes a penalty parameter $\gamma$ which needs to be chosen large enough to ensure stability of the finite element method.
+We set $\gamma=10$.} Since the divergence of the velocity is a subspace of the pressure space for this scheme, the divergence-free condition of the velocity is satisfied exactly on each element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
+
+\mer{MER: I think this is too much detail. One sentence suffices, or it goes in the Supplementary.}
 In the absence of pressure boundary conditions, the pressure in the Stokes equations is only determined up to an additive constant.
@@
 The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized with a first-order implicit Euler method in time, and a first-order, symmetric interior penalty discontinuous Galerkin (DG) method in space~\cite{Arnold1982AnElements}.
-Like for the flow equations, we use a timestep size of $\Delta t = 0.02252$ s.
-We simulate transport for 1900 cardiac cycles, meaning the final time of simulation $T = 856$ s.
-The DG penalty parameter $\alpha = 25$ was chosen large enough to ensure stability of the finite element method.
 To accurately approximate the solute concentrations even in the presence of strong advection (high Péclet numbers), we use an upwind scheme for the velocity when calculating the advective flux~\cite{Patankar2018NumericalFlow}.
+As for the flow equations, we use a timestep size of $\Delta t = 0.02252$ s.
+We simulate transport for 1900 cardiac cycles, with a final time of simulation $T = 856$ s.
+A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
 
 \subsection*{Solution strategy and software implementation}
-Because of the one-way coupling between the velocity field $\uu$ and the concentration $c$, the governing equations for the cerebrospinal fluid flow and the concentration can be solved sequentially when modeling solute transport.
-For model version I, the flow field is a steady-state solution.
-In this case, we first solve the Stokes equations~\eqref{eq:stokes_eqs} for $\uu$ and $p$ until we reach the steady-state solution, and then use the velocity field $\uu$ as input when solving the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
-For the baseline model 0 and model II, the Stokes equations are solved for one period of the pulsatile cardiac motion.
-The solution of this one period is then used periodically as input when solving the advection-diffusion equation.
-
-The finite element methods derived for the Stokes equations and the advection-diffusion equation were implemented and solved numerically with DOLFINx, the Python interface of the finite element software FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
-For solving the linear systems, a direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the discretized Stokes equations.
-For the discretized advection-diffusion equation, we used an iterative solver based on the GMRES routine~\cite{Saad1986GMRES:Systems} with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen}.
+Because of the one-way coupling between the velocity field $\uu$ and the concentration $c$, the governing equations for the CSF flow and the concentration can be solved sequentially when modeling solute transport.
+\fixme{For the no-cardiac/cilia-only flow scenario, the velocity quickly reaches steady-state.} In this case, we first solve the \fixme{steady-state} Stokes equations~\eqref{eq:stokes_eqs} for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
+For the other flow scenarios, the Stokes equations are solved for one period of the pulsatile cardiac motion.
+The solution of this one period is then used periodically as input for the advection-diffusion equation.
+
+The numerical solution schemes for the Stokes equations and the advection-diffusion equation were implemented and solved numerically with DOLFINx, the Python interface of the finite element software FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
+A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the linear systems resulting from the discretized Stokes equations.
+For the discretized advection-diffusion equation, we used an iterative linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen}.
 Numerical experiments verified the accuracy of the model implementation (\cref{sec:appB_verification}).
-The implementation of the model presented in this work is available at~\url{insert-repo-link-here}.
+This simulation software is openly available~\cite{zenodo-link-to-all-code}.
 

### 2025-02-03 paper/main.tex
Begin working on Results...

@@
 
-Wholemount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at the 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described by D’Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Whole-mount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at the 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described by D’Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
 Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+}) or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
@@
 
-\subsection*{Wholemount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
+\subsection*{Whole-mount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
 To image 2 dpf larval zebrafish, the fish were anesthetized in 0.013\% MS222 in AFW and mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100), to obtain a lateral view of the brain ventricles.
@@
 
-    \item A \emph{no-cilia/cardiac-only} flow model including contributions from the cardiac pulstaions but no cilia forces.
+    \item A \emph{no-cilia/cardiac-only} flow model including contributions from the cardiac pulsations but no cilia forces.
 Here, we set the tangential traction to zero on the cilia boundary $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.
@@
 \section*{Results}\label{sec:results}
+
 \subsection*{Cerebrospinal fluid flow in the brain ventricles is compartmentalized}
-With cilia forces and cardiac forces represented in the flow model (model version 0), we observe a vortex-structured flow pattern in the anterior and middle ventricles~(\cref{fig:figure1}, panel \textbf{e}).
-This rotational motion shows that cilia-mediated flow is dominating in these regions, as the vortex structures are a consequence of the applied tangential stresses on the ciliated boundaries combined with the assumption of fluid incompressibility.
-In the posterior ventricle, we observe directional flow as the pressure-driven flow is dominating in this region.
-The cardiac pressure forces induce a pulsatile motion of the cerebrospinal fluid synchronized with the cardiac cycle, with velocity magnitudes of the pulsatile motion being approximately an order of magnitude smaller than the velocities related to the cilia-driven motion.
-Over a cardiac cycle, the maximum velocity magnitude in the ventricles was 27.7 $\mu$m/s, located dorsally in the posterior part of the middle ventricle.
-This maximum velocity was attained at the time instant coinciding with the peak of the cardiac pulsatile flow flowing caudally, as a result of both the tangential stress boundary condition and the pulsatile pressure-driven flow being aligned with the rostrocaudal axis (the $x$ axis).
-A calculation using the observed maximum velocity of 27.7 $\mu$m/s, and choosing the approximate height of the middle ventricle $110 \ \mu$m as a characteristic length scale, yields a Reynolds number $\mathrm{Re} \approx 0.004$, justifying the assumption of Stokes flow.
+
+\mer{Why?} To characterize CSF flow patterns predicted by
+computational fluid dynamics within the brain ventricles, we consider
+the simulated CSF velocity and pressure when driven by both cilia and
+cardiac pulsations. \mer{MER: Stopped here...} With cilia forces and
+cardiac forces represented in the flow model (model version 0), we
+observe a vortex-structured flow pattern in the anterior and middle
+ventricles~(\cref{fig:figure1}, panel \textbf{e}). This rotational
+motion shows that cilia-mediated flow is dominating in these regions,
+as the vortex structures are a consequence of the applied tangential
+stresses on the ciliated boundaries combined with the assumption of
+fluid incompressibility. In the posterior ventricle, we observe
+directional flow as the pressure-driven flow is dominating in this
+region. The cardiac pressure forces induce a pulsatile motion of the
+cerebrospinal fluid synchronized with the cardiac cycle, with velocity
+magnitudes of the pulsatile motion being approximately an order of
+magnitude smaller than the velocities related to the cilia-driven
+motion. Over a cardiac cycle, the maximum velocity magnitude in the
+ventricles was 27.7 $\mu$m/s, located dorsally in the posterior part
+of the middle ventricle. This maximum velocity was attained at the
+time instant coinciding with the peak of the cardiac pulsatile flow
+flowing caudally, as a result of both the tangential stress boundary
+condition and the pulsatile pressure-driven flow being aligned with
+the rostrocaudal axis (the $x$ axis). A calculation using the observed
+maximum velocity of 27.7 $\mu$m/s, and choosing the approximate height
+of the middle ventricle $110 \ \mu$m as a characteristic length scale,
+yields a Reynolds number $\mathrm{Re} \approx 0.004$, justifying the
+assumption of Stokes flow.
 
@@
 Although the fluorescence intensity increases throughout all of the experiments, the maximum $\Delta F$ is not necessarily attained at the final time of the experiments.
-At the final time, the mean fluoresence intensities in regions 2--4 all exceed 0.60 (0.63, 0.71, 0.67, respectively) of the final value $F_0$ in ROI 1, wheras ROIs 5 and 6 reach mean values of 0.29 and 0.18, respectively.
+At the final time, the mean fluorescence intensities in regions 2--4 all exceed 0.60 (0.63, 0.71, 0.67, respectively) of the final value $F_0$ in ROI 1, whereas ROIs 5 and 6 reach mean values of 0.29 and 0.18, respectively.
 
@@
 Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
-Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaenously.
+Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaneously.
 We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
@@
     \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
-    \caption{Caption. \mk{MK: How do the different geoemtries compare in terms of volume, areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
+    \caption{Caption. \mk{MK: How do the different geometries compare in terms of volume, areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
     \label{fig:figure6_sim_results_compare_geometries}

### 2025-02-03 paper/main.tex
Edits in Results 1

@@
 
-\mer{@HH: I suggest you write \cref{fig:figure1}\textbf{a}, rather than \cref{fig:figure1} panel \textbf{a}, throughout. Increases signal-to-noise ratio.}
+\mer{@HH: I suggest you write \cref{fig:figure1}a, rather than \cref{fig:figure1} panel \textbf{a}, throughout. Increases signal-to-noise ratio.}
 
@@
 
-\subsection*{Computational flow scenarios}
+\subsection*{Computational modelling scenarios}
 %\label{subsec:model_versions}
@@
 
-\subsection*{Cerebrospinal fluid flow in the brain ventricles is compartmentalized}
-
-\mer{Why?} To characterize CSF flow patterns predicted by
-computational fluid dynamics within the brain ventricles, we consider
-the simulated CSF velocity and pressure when driven by both cilia and
-cardiac pulsations. \mer{MER: Stopped here...} With cilia forces and
-cardiac forces represented in the flow model (model version 0), we
-observe a vortex-structured flow pattern in the anterior and middle
-ventricles~(\cref{fig:figure1}, panel \textbf{e}). This rotational
-motion shows that cilia-mediated flow is dominating in these regions,
-as the vortex structures are a consequence of the applied tangential
-stresses on the ciliated boundaries combined with the assumption of
-fluid incompressibility. In the posterior ventricle, we observe
-directional flow as the pressure-driven flow is dominating in this
-region. The cardiac pressure forces induce a pulsatile motion of the
-cerebrospinal fluid synchronized with the cardiac cycle, with velocity
-magnitudes of the pulsatile motion being approximately an order of
-magnitude smaller than the velocities related to the cilia-driven
-motion. Over a cardiac cycle, the maximum velocity magnitude in the
-ventricles was 27.7 $\mu$m/s, located dorsally in the posterior part
-of the middle ventricle. This maximum velocity was attained at the
-time instant coinciding with the peak of the cardiac pulsatile flow
-flowing caudally, as a result of both the tangential stress boundary
-condition and the pulsatile pressure-driven flow being aligned with
-the rostrocaudal axis (the $x$ axis). A calculation using the observed
-maximum velocity of 27.7 $\mu$m/s, and choosing the approximate height
-of the middle ventricle $110 \ \mu$m as a characteristic length scale,
-yields a Reynolds number $\mathrm{Re} \approx 0.004$, justifying the
-assumption of Stokes flow.
-
-\subsection*{Vortex structures vanish in the absence of cilia}
-The pulsatile motion is absent when disregarding cardiac motion~(model I, \cref{fig:figure1}, panel~\textbf{f}).
+\subsection*{Cilia induces flow compartmentalization within the brain ventricles}
+
+\mer{One sentence on why? - what do we not know - what do we try to
+  find out?} To characterize CSF flow patterns predicted by
+computational fluid dynamics within the brain ventricles, we begin by
+considering the simulated CSF velocity and pressure when driven by
+both cilia motion and cardiac pressure pulsations. These forces induce
+\fixme{persistent} flow features, with vortex-structures in the
+anterior and middle ventricles and \fixme{unidirectional} flow in the
+posterior ventricle (\Cref{fig:figure1}\textbf{e},
+\fixme{Supplementary video 1}). These characteristic patterns suggest
+that the flow in the anterior and middle ventricles are dominated by
+the cilia contribution, while the cardiac pressure pulsations dominate
+within the posterior ventricle. Over one cardiac cycle, the CSF flow
+speed reaches up to 27.7 \textmu m/s, dorsally in the posterior part
+of the middle ventricle. This peak is attained at the time instant
+coinciding with the time of peak caudal cardiac pulsatile flow, as a
+result of both the traction induced by the cilia and the pulsatile
+pressure-driven flow being aligned with the rostrocaudal ($x-$)
+axis. Using this maximum velocity magnitude and choosing the height of
+the middle ventricle ($110$ \textmu m) as a characteristic length
+scale, yields a Reynolds number $\mathrm{Re} \approx 0.004$,
+justifying the assumption of Stokes flow. To further examine the
+effect of the cilia, we next consider a no-cilia model variation. In
+this scenario, the simulated CSF flow is pulsatile and
+\fixme{unidirectional} (\cref{fig:figure1}g), with a peak velocity
+magnitude of \fixme{$4.8$ \textmu m/s}. On the other hand, the
+vortices (re)appear when considering a variation with cilia but no
+cardiac contribution (\cref{fig:figure1}h), in which case the highest
+velocities ($26.5$ \textmu m/s) also occur in the vicinity of the
+cilia. Thus, the bidirectional traction induced by motile cilia
+inherently leads to a partial compartmentalization of the ventricular
+system.
+
+%% %\subsection*{Vortex structures vanish in the absence of cilia}
+%% The pulsatile motion is absent when disregarding cardiac motion~(model I, \cref{fig:figure1}, panel~\textbf{f}).
 For model I, the boundary conditions are not time-dependent, rendering the solution to the Stokes equations~\eqref{eq:stokes_eqs} a steady-state flow field.
 Streamlines demonstrate the compartmentalization of the cerebrospinal fluid flow driven by cilia, and we observe highest vorticity in the vicinity of cilia.
-Excluding the cilia tangential traction from the model (model II), vortex-structured compartmentalization of the ventricular flow does not occur, and the flow is directional and pulsatile as a result of the pressure boundary conditions imposed~(\cref{fig:figure1}, panel \textbf{g}).
+
+%% Excluding the cilia tangential traction from the model (model II), vortex-structured compartmentalization of the ventricular flow does not occur, and the flow is directional and pulsatile as a result of the pressure boundary conditions imposed~(\cref{fig:figure1}, panel \textbf{g}).
+
+%% The cardiac pressure forces induce a pulsatile motion of the
+%% cerebrospinal fluid synchronized with the cardiac cycle, with velocity
+%% magnitudes of the pulsatile motion being approximately an order of
+%% magnitude smaller than the velocities related to the cilia-driven
+%% motion.
 

### 2025-02-03 paper/main.tex
Edits in Results 2

@@
 The CSF density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
-We considered small, medium and large-sized molecules by three different diffusion coefficients $D_1, D_2$ and $D_3$ (\Cref{tab:parameter_table}).
+We considered large, medium and small-sized molecules by three different diffusion coefficients $D_1, D_2$ and $D_3$ (\Cref{tab:parameter_table}).
 Experimental data~\cite{Olstad2019CiliaryDevelopment} indicate \fixme{velocities} proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and $2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the diencephalic ventricle, respectively.
@@
 Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, and $D$ is the solute diffusion coefficient.
+\fixme{Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection, and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
+As a length scale $L_p$, we choose the approximate length of the ventricles geometry in the $x$-direction, $L_p=600$ \textmu m.
+We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
+The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
+\begin{equation*}
+    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
+\end{equation*}
+and then averaging $\overline{u}$ in time over one cardiac cycle.}
+
 To assess the assumption that the CSF flow is governed by the Stokes equations, we also compute the Reynolds number
@@
 Numerical experiments verified the accuracy of the model implementation (\cref{sec:appB_verification}).
-This simulation software is openly available~\cite{zenodo-link-to-all-code}.
+The simulation code is openly available~\cite{zenodo-link-to-all-code}.
 
@@
 
-\subsection*{Cilia induces flow compartmentalization within the brain ventricles}
+\subsection*{Motile cilia induce flow compartmentalization within the brain ventricles}
 
@@
 \subsection*{Ventricular solute transport is advection-dominated for small molecules}
-To qualitatively analyze protein transport, we compare the solute concentration fields from simulation of photoconversion in a dorsal region of the middle ventricle.
-We simulate transport using the three diffusion coefficients $D_1$, $D_2$ and $D_3$, and present concentration fields in a slice of the ventricles geometry for each diffusion coefficient at three time instants~(\cref{fig:figure2_compare_diffusion_coefficients}, panel~\textbf{a}).
-The slices are taken in the $xz$-plane, which aligns with the rostrocaudal axis, at $y=140$ $\mu$m, the center of the geometry.
-Note that the colorbars colored by the value of the concentration $c$ are different for each column (corresponding to the choice of $D$).
-Upper limits of the colorbars are the maximum value of $c$ in the respective slice at $t=450.5$ s, for the respective $D$.
-
-Overall, transport occurs more rapidly with increasing diffusion coefficient.
-For the smallest diffusion coefficient $D_1$ (representing exosomes), advective transport by the cilia-driven cerebrospinal fluid flow dominates diffusion in the distribution of solute concentration~(\cref{fig:figure2_compare_diffusion_coefficients}, panel~\textbf{a}, left column).
-The rotational flow structures of the velocity field are apparent in the concentration field, indicating that transport along the streamlines of the flow field is more rapid than the diffusion across the streamlines.
-Diffusive transport becomes more rapid with increasing diffusion coefficient, and the flow structures of the cerebrospinal fluid flow become more obfuscated.
-This is evident in the concentration fields calculated with the medium ($D_2$, representing STM+GFP) and high ($D_3$, representing Dendra2) diffusion coefficients (\cref{fig:figure2_compare_diffusion_coefficients}, panel \textbf{a}, middle and right column).
-Compared to the $D_1$ case, for $D_2$ and $D_3$ solute spreads more uniformly throughout the ventricular geometry.
-Also, for $D_2$ and $D_3$, the solute spreads more quickly to regions distal to the photoconversion site.
-\begin{figure}[H]
+We next ask what is the impact of these CSF flow patterns and
+magnitudes on solute transport generally within the brain ventricles?
+To address this question, we simulate the distribution and evolution
+of different solutes subject to photoconversion within a region of
+interest in the dorsal region of the middle ventricle (ROI 1)
+(\Cref{fig:fig2}\fixme{e/x}). In particular, we consider the spread of
+a solute concentration with a given molecular diffusion coefficient,
+corresponding to Exosomes ($D_1 = 1.63 \times 10^{-12}$ m$^2$/s),
+STM+GFP ($D_2 = 5.75 \times 10^{-11}$ m$^2$/s), and Dendra2 ($D_3 =
+1.15 \times 10^{-10}$ m$^2$/s). As expected, transport occurs more
+rapidly with increasing diffusion coefficient. Interestingly, the
+distribution patterns differ between the different-characteristics
+solutes. For the smallest diffusion coefficient, representing
+Exosomes, the advection induced by the CSF flow dominates diffusion
+(\Cref{fig:fig2}a). The vortex structures of the velocity field
+carries over into the concentration field, indicating that transport
+along the streamlines is more rapid than the diffusion across the
+streamlines. The balance between diffusion and advection shifts with
+increasing diffusion coefficients, the CSF flow structures become more
+obfuscated, and the solute spreads more uniformly throughout the
+ventricular geometry (\Cref{fig:fig2}\fixme{x-y}). Interestingly, the
+smaller solutes with higher diffusion coefficients spread more quickly
+to regions distal to the photoconversion site (\Cref{fig:fig2}\fixme{z}).
+\begin{figure}%[H]
     \centering
     \includegraphics[width=0.95\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}
-    \caption{\textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm, the center of the geometry) showing the concentration field simulated with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s.
+    \caption{Simulated distribution and evolution after photoconversion of Dendra ($D_1$), STM+GFP ($D_2$) and Exosomes ($D_3$).
+\mer{MER: I think you should show on the same color scale here in a) (the range of values lets you and then it is possible to compare).
+Split a into a, b, c.
+Show e) first (so that e) becomes a)}.
+\textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm, the center of the geometry) showing the concentration field simulated with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s.
 Note that the colorbars indicating the magnitude of $c$ have different limits for each column.
@@
 Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}
-    \label{fig:figure2_compare_diffusion_coefficients}
+    \label{fig:fig2}
 \end{figure}
 
-Transport of solute is quantified by the profile of the mean concentrations $\overline{c}_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\cref{fig:figure2_compare_diffusion_coefficients}, panels \textbf{b--d}).
-An illustration of the ROIs is provided in \cref{fig:figure2_compare_diffusion_coefficients}, panel~\textbf{e}.
+\mer{MER: Stopped here with the editing (except commenting out), assuming that Nathalie had something to say about the next paragraph.}
+
+Transport of solute is quantified by the profile of the mean concentrations $\overline{c}_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\cref{fig:fig2}, panels \textbf{b--d}).
+An illustration of the ROIs is provided in \cref{fig:fig2}, panel~\textbf{e}.
 The dynamics of ROI 1 follow from imposing~\cref{eq:injection_curve}.
@@
 %\lyng{HH: is this really true?: Note that the total mass added to the system is not exactly the same for all three diffusion coefficients, since the total mass added depends on how fast the mass added in ROI 1 is transported away from that region.}
-
-We report the times $\hat{t}$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}$~(\cref{fig:figure2_compare_diffusion_coefficients}, panel \textbf{f}).
+%
+%
+%\mer{MER: This belongs in Methods (and is written there) or does not need to be stated.}
+%% We report the times $\hat{t}$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}$~(\cref{fig:fig2}, panel \textbf{f}).
 Recall that $\hat{c}=0.25$ for regions of interest 1--4 and $\hat{c}=0.10$ for regions 5 and 6.
@@
 
-Finally, we calculate Péclet numbers for the entire ventricular geometry using estimates of the diffusion and advection timescales $t_d=L_p^2/D$ and $t_a=L_p/U_p$. Recall that
-\begin{equation*}
-    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a},
-\end{equation*}
-so that if $\mathrm{Pe} > 1$, transport is dominated by advection, and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
+%% \mer{Moved this to Methods.}
+%% Finally, we calculate Péclet numbers for the entire ventricular geometry using estimates of the diffusion and advection timescales $t_d=L_p^2/D$ and $t_a=L_p/U_p$.
+%% Recall that
+%% \begin{equation*}
+%%     \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a},
+%% \end{equation*}
+%% so that if $\mathrm{Pe} > 1$, transport is dominated by advection, and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
 For the length scale $L_p$ we choose the approximate length of the ventricles geometry in the $x$-direction, $L_p=600 \ \mu$m.
@@
 The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
-\begin{equation*}
-    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
-\end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle to obtain $\overline{U}=1.41 \ \mu$m/s.
+%% \begin{equation*}
+%%     \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
+%% \end{equation*}
+%% and then averaging $\overline{u}$ in time over one cardiac cycle to obtain $\overline{U}=1.41 \ \mu$m/s.
 This yields the three Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
 \lyng{HH: move choice of length scale/calculation of velocity scale to Methods?
-Same question for Reynolds number calculation.}
+Same question for Reynolds number calculation.} \mer{MER: Yes, definitely.}
 
@@
 Removing the cilia in the anterior ventricle leaves the transport results virtually unaltered, although the CSF flow vortex structure in the anterior ventricle vanishes.
-This would then probably have a greater impact for smaller diffusion coefficients, as it is evident in~\cref{fig:figure2_compare_diffusion_coefficients} that transport with $D_1$ is mainly advective.
+This would then probably have a greater impact for smaller diffusion coefficients, as it is evident in~\cref{fig:fig2} that transport with $D_1$ is mainly advective.
 

### 2025-02-03 paper/main.tex
Isn't it larger?

@@
 
-\subsection*{Ventricular solute transport is advection-dominated for small molecules}
+\subsection*{Ventricular solute transport is advection-dominated for \fixme{larger} molecules}
 We next ask what is the impact of these CSF flow patterns and

### 2025-02-03 paper/main.tex
Updates from discussion just now.

@@
 % Title
-\title{The role of cilia-mediated cerebrospinal fluid flow in intraventricular transport in zebrafish embryos}
+\title{The role of advection versus diffusion in intraventricular transport}
 \author[1,*]{Halvor Herlyng}
@@
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}.
-The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) \mer{edge length} of 14.9 $\mu$m (4.68 $\mu$m).
+The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m).
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic  (anterior), the di-/mesencephalic  (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts.
-Parts of the ventricular surfaces were marked to be lined with motile cilia~\cite{Olstad2019CiliaryDevelopment} (\cref{fig:figure1}\textbf{d}, pink markers).
-\mer{MER: @HH: Check if you mean edge length or mesh cell size here.}
+Parts of the ventricular surfaces were marked to be lined with motile cilia~\cite{Olstad2019CiliaryDevelopment} (\cref{fig:figure1}d, pink markers).
 \begin{figure}%[hbt!]
@@
 Unless noted otherwise, the free-slip condition is applied on the boundary.
-We use the initial condition\mer{s} $\uu(\xx, 0)=\mathbf{0}$ \mer{and $p(\xx, t) = 0$} for all $\xx\in\Omega$.
-\mer{MER: I don't think you use an initial condition on the pressure.
-Please check and remove if so.
-You can also just write: ``We assume that the system starts at rest ($\uu(t = 0) = \mathbf{0}$)''.}
+We assume that the system starts at rest ($\uu(t = 0) = \mathbf{0}$).
 
@@
 The ventricular walls are assumed to be impermeable (admitting \emph{no flux} i.e.~$\JJ\cdot\nn=0$), except at the anterior/posterior boundary $\Gamma_p$.
+\fixme{At the anterior/posterior boundary we allow the solute concentration to be advected into and out of the domain in a manner that ensures conservation of mass (see \Cref{sec:appendix:X} for details).}
+\mer{MER: @Halvor: could you have a go at moving the precise description to the Appendix?}
 \fixme{There, we consider either prescribed \emph{influx} in the form of a time-periodic condition on the total flux $(\JJ\cdot\nn)|_{\mathrm{in}}^{n+1}=(\JJ\cdot\nn)|_{\mathrm{out}}^{n}$ and/or \emph{outflux} with zero diffusive flux $D\nabla c\cdot\nn=0$.}
-\mer{MER: Could we make this section about the boundary conditions easier to read? I've had a go at it, please check.}
-
 \fixme{Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for.
@@
 On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.}
-\mer{MER: I moved this paragraph from the section below, because it seemed to belong here. But needs edits.}
+%\mer{MER: I moved this paragraph from the section below, because it seemed to belong here. But needs edits.}
 
@@
 For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations are summarized in \cref{tab:parameter_table}.
+The resulting diffusion coefficients used in the simulations are summarized in \cref{tab:diff_coeff_table}.
 
@@
     \centering
-    \label{tab:diff_coeff_table}
     \begin{tabular}{l|ccc}
@@
 (\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
+    \label{tab:diff_coeff_table}
 \end{table}
@@
 I suggest there.}
-\mer{MER: I suggest you move the parts relevant for cilia/cardiac flow to where you mentioned it first, and then merge this section with the Estimation of diffusion ....
-Just refer to \cref{tab:parameter_table}.
-Actually, unsure if you need it.
-You say everything in the text or in the other Table right?}
+\mer{MER: I suggest you introduce parameter values when introduced, and move the parts relevant for cilia/cardiac flow to where you mentioned it first, and then merge this section with the Estimation of diffusion ....
+Then remove this section and \Cref{tab:parameter_table}.}
 \begin{table}[h!]
@@
 
-\subsection*{Computational modelling scenarios}
+\subsection*{Computational flow modelling scenarios}
 %\label{subsec:model_versions}
@@
 
-\mer{MER: Let's discuss the paragraphs below and see where they fit best.
-I think we can drop the first paragraph (you said this already).
-I find the second paragraph to be somewhat confusing (low signal-to-noise ratio).}
+\mer{MER: @Halvor I suggest you move these two paragraphs into their respective Results sections (Results 2 and 5). Putting the bullet points above at the end of the Stokes equations is a great idea!}
 When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
@@
 \mer{One sentence on why? - what do we not know - what do we try to
-  find out?} To characterize CSF flow patterns predicted by
+  find out?} \mer{@Halvor: If you want, try to revamp this paragraph
+  as suggested by Nathalie. First cilia. Then pulsatile. Then
+  combined.} To characterize CSF flow patterns predicted by
 computational fluid dynamics within the brain ventricles, we begin by

### 2025-02-03 paper/main.tex
Methods updates

@@
 \newcommand{\crefrangeconjunction}{--} % Change crefrange from "to" to dashed
-\crefname{figure}{Figure}{Figure}
 
@@
 In addition to photoconversion experiments, we carried out particle tracking inside the brain ventricles of a larval zebrafish, to demonstrate the motile-cilia and cardiac-cycle related flow features observed and described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}.
-A schematical illustration of the flow features in the brain ventricles is shown in~\cref{fig:figure1}, panel \textbf{a}.
+A schematical illustration of the flow features in the brain ventricles is shown in~\Cref{fig:figure1}a.
 Our experimental setup for the particle tracking is identical to the ones considered there (\lyng{HH: Is this true?}), and we refer to that paper for further details than the ones provided here in the following.
@@
 We generated a 3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}.
-From the imaging data, we constructed a computational mesh of the ventricles (\cref{fig:figure1}, panel \textbf{d}).
-The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}.
+From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:figure1}d). The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
 The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). 
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic  (anterior), the di-/mesencephalic  (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts.
-Parts of the ventricular surfaces were marked to be lined with motile cilia~\cite{Olstad2019CiliaryDevelopment} (\cref{fig:figure1}d, pink markers).
+Parts of the ventricular surfaces were marked to be lined with motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:figure1}d, pink markers).
 \begin{figure}%[hbt!]
@@
 
-%\subsection*{Computational geometry variations}
 The morphology and geometry of the brain ventricles vary across zebrafish individuals, and under physiological and pathological conditions. 
-Motivated by an interest in how geometry impacts solute distribution, we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, the middle ventricle, the mid-hind brain connection, and all three simultaneously.
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
-\mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}
-
-%% The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
-Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
-Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaenously.
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+Motivated by an interest in how geometry impacts solute distribution, we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, 
+the middle ventricle, the mid-hind brain connection, and all three simultaneously. 
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry. \mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}
 
 \subsection*{Computational CSF dynamics}
-
-The beating motion of the cilia generates CSF flow with steady rotational structures~\cite{Olstad2019CiliaryDevelopment} within the brain ventricles (\cref{fig:figure1}, panels \textbf{a}--\textbf{c}).
-In addition, cardiac pulsations induces pulsatile CSF flow.
-We model this flow of CSF in the brain ventricles by the time-dependent, incompressible Stokes equations which read as follows.
+The beating motion of the cilia generates CSF flow with steady rotational structures~\cite{Olstad2019CiliaryDevelopment} within the brain ventricles (\Cref{fig:figure1}a--c).
+In addition, cardiac pulsations induces pulsatile CSF flow. We model this flow of CSF in the brain ventricles by the time-dependent, incompressible Stokes equations which read as follows.
 Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$ and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
@@
 Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
-Furthermore, $\rho$ is the CSF density and $\mu$ is the dynamic viscosity of the CSF.
+Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density and $\mu=6.97\times 10^{-4}$ Pa is the dynamic viscosity of the CSF.
 We introduce the tangential traction $\bsigpar$ as the tangential component of the traction $\hat{\bsig}=\bsig\nn$:
@@
 where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$, and $P_{\nn}(\rr)$ is the tangential  projection of a vector $\rr$ onto $\Gamma$.
-We consider three types of boundary conditions:  (i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$), (ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$), and (iii) \emph{free slip} (no flow normal to the boundary $\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the boundary.
-We assume that the system starts at rest ($\uu(t = 0) = \mathbf{0}$).
+We consider three types of boundary conditions:  (i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
+and (iii) \emph{free slip} (no flow normal to the boundary $\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
+Unless noted otherwise, the free-slip condition is applied on the boundary. We assume that the system starts at rest ($\uu(\xx, t=0) = \mathbf{0}$).
 
 \subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\cref{fig:figure1}, panel \textbf{d}), we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces of the cilia acting on the CSF.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$ and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the cilia region (see~\cref{subsec:appendixA1}).
+On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:figure1}d), we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces of the cilia acting on the CSF.
+We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$ and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the cilia region (see~\Cref{subsec:appendixA1}).
 Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by model calibration against the experimental data~\cite{Olstad2019CiliaryDevelopment}.
@@
 \subsection*{Flow induced by cardiac pulsations}\label{subsec:pressure_bcs}
-To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts of the boundary $\Gp$~(\cref{fig:figure1}, panel \textbf{d}, blue markers).
+To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts of the boundary $\Gp$~(\Cref{fig:figure1}d, blue markers).
 The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow, and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
 The angular cardiac frequency $\omega=2\pi f=6.97$ rad/s was set based on a measured cardiac frequency of $f=2.22$ Hz.
-
-%% \iffalse
-%% \subsection*{Computational cerebrospinal fluid dynamics in a moving reference frame}
-%%  An Arbitrary Lagrangian Eulerian (ALE) formulation~\cite{san2009convergence} is used as an alternative to the normal pressure boundary conditions to model back-and-forth flow induced by cardiac pulsations.
-In a reference frame moving with a velocity $\uuref=(A_{\mathrm{ref}}\sin{\omega t}, 0, 0)$, we reformulate the Stokes equations~\eqref{eq:stokes_eqs} using an ALE formulation:
-%% \begin{subequations}
-%%     \begin{alignat}{2}
-%%         \rho\bigg(\pdifft{\uu} + (\uu_{\mathrm{ref}}\cdot\nabla)\uu\bigg) &= \nabla\cdot\bm{\sigma}(\uu, p), \label{eq:mom_eq_ALE}\\
-%%         \nabla\cdot\uu &= 0.
-%%     \end{alignat}
-%%     \label{eq:stokes_eqs_ALE}%
-%% \end{subequations}%
-%% We then solve for the velocity $\mathbf{w} = \uu - \uuref$ in the moving reference frame, where $\uu$ is the velocity in the fixed reference frame.
-The amplitude $A_{\mathrm{ref}}=919$ $\mu$m/s, calibrated based on experimental data, determines the magnitude of the pulsatile flow, and $\omega=2\pi f$ is the angular cardiac frequency.
-In the ALE formulation, we consider the impermeability boundary condition $\mathbf{w}\cdot\nn=0$ in the normal direction and the free-slip boundary condition $\bsigpar(\mathbf{w}, p) = \mathbf{0}$ in the tangential direction.
-%% \fi
 
@@
 The ventricular walls are assumed to be impermeable (admitting \emph{no flux} i.e.~$\JJ\cdot\nn=0$), except at the anterior/posterior boundary $\Gamma_p$.
-\fixme{At the anterior/posterior boundary we allow the solute concentration to be advected into and out of the domain in a manner that ensures conservation of mass (see \Cref{sec:appendix:X} for details).}
+\fixme{At the anterior/posterior boundary we allow the solute concentration to be advected into and out of the domain in a manner that ensures conservation of mass (see~\Cref{sec:appendix:X} for details).}
 \mer{MER: @Halvor: could you have a go at moving the precise description to the Appendix?}
@@
 \fixme{Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for.
-We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$; $\Gout$ denotes the part where $\uu\cdot\nn > 0$.
+We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$;
+$\Gout$ denotes the part where $\uu\cdot\nn > 0$.
 On $\Gin$, a total flux boundary condition was set: the inflow flux at a given timestep was set equal to the outflow boundary flux at the previous timestep.
-This was done to approximate a periodic boundary condition.
-On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.}
-%\mer{MER: I moved this paragraph from the section below, because it seemed to belong here. But needs edits.}
-
-%Unless stated otherwise, the no-flux condition $\JJ\cdot\nn=0$ was applied on the boundary.
-%(ii) \emph{injection site} (imposing the Dirichlet boundary condition $c=\Tilde{c}$),
-
-%\subsection*{Modeling protein photoconversion}
+This was done to approximate a periodic boundary condition. On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.}
 
@@
 
-%To represent the solute injection at $\Ginj$ (cf.~\cref{fig:injection_sites}), we impose a constant Dirichlet boundary condition $c=\Tilde{c}$.
-Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for.
-We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$; $\Gout$ denotes the part where $\uu\cdot\nn > 0$.
-On $\Gin$, a total flux boundary condition was set: the inflow flux at a given timestep was set equal to the outflow boundary flux at the previous timestep.
-This was done to approximate a periodic boundary condition.
-On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.
-%\lyng{MOVE? Following previous works~\cite{papanastasiou1992new, griffiths1997no, lynch2020numerical}, the advective flux $c\uu$ on $\Gout$ was left as an unknown in the variational form.}
-
 \subsection*{Estimation of diffusion coefficients via the Stokes-Einstein relation}
-%\label{subsec:diff_coeffs}
-
 Motivated by an interest in molecules that are significant in neural development, we study the transport of molecules resembling Dendra2 Fluorescent Protein (Dendra2), Starmaker+Green Fluorescent Protein (STM+GFP) and Exosomes.
@@
 \begin{equation}
-    D = \frac{k_B T}{6\pi \mu R} ,
+    D = \frac{k_B T}{6\pi \mu R},
     \label{eq:D_stokes_einstein}
@@
 This radius covers the slowest diffusing exosomes, since the smaller exosomes would have diffusion coefficients similar to the other molecules.
-For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations are summarized in \cref{tab:diff_coeff_table}.
-
-%% In summary, in the simulations, we use the diffusion coefficients $D_1$, $D_2$ and $D_3$ (\cref{tab:parameter_table}) for these three molecules
+For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
+The resulting diffusion coefficients used in the simulations are summarized in \Cref{tab:diff_coeff_table}.
 
@@
 
-%% The molecular diffusion coefficients were estimated in part based on values reported in the literature, and in part via extrapolation with the Stokes--Einstein relation (\cref{tab:diff_coeff_table}).
-The Stokes-Einstein relation
 \begin{table}[h!]
@@
     \end{tabular}
-    \caption{Molecular mass and diffusion coefficients of simulated solutes.
-STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-(*) The value was extrapolated based on the value of $D$ for GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}, assuming that $D$ scales with the cube root of the molecule mass.
-(\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
+    \caption{Molecular mass and diffusion coefficients of simulated solutes. STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+    (*) The value was extrapolated based on the value of $D$ for GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+    assuming that $D$ scales with the cube root of the molecule mass. (\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
     \label{tab:diff_coeff_table}
@@
 
-%% The diffusion coefficient was estimated through extrapolation of previous measurements~\cite{GuraSadovsky2017MeasurementExpansion, Mahmood2023ExosomeTemperature, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} via the Stokes-Einstein relation
-
 \subsection*{Physical parameters}
-%\label{subsec:parameters}
-The CSF density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\cref{tab:parameter_table}).
+The CSF density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\Cref{tab:parameter_table}).
 We considered large, medium and small-sized molecules by three different diffusion coefficients $D_1, D_2$ and $D_3$ (\Cref{tab:parameter_table}).
@@
 We calibrated $\tau$ and $A$ heuristically by comparing these experimental velocity values with the simulated, maximum velocity magnitude.
-In addition, particle tracking data of pulsatile motion~(\cref{sec:appC_particle_transport}) was used in the calibration process to determine the relative contributions of the cardiac pulsations, as compared to the cilia-driven flow, to the velocity magnitude.
+In addition, particle tracking data of pulsatile motion was used in the calibration process to determine the relative contributions of the cardiac pulsations, as compared to the cilia-driven flow, to the velocity magnitude.
 \mer{MER: What velocities?
@@
 \subsection*{Computational flow modelling scenarios}
-%\label{subsec:model_versions}
 To study the impact of the motile cilia and the cardiac pulsations on the CSF flow, we consider the following computational flow scenarios, each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
@@
     \item A \emph{baseline} flow model representing a wild-type zebrafish including contributions both from the cilia forces and the cardiac pulsations.
-In this scenario, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.
-% Model 0
-
-    \item A \emph{no-cardiac/cilia-only} flow model including contributions from the cilia forces but no cardiac pulsations.
+    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0
+
+    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the cilia forces but no cardiac pulsations.
     Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$, and \mer{XXX on the anterior/posterior boundary $\Gp$.} % Model I
 
-    \item A \emph{no-cilia/cardiac-only} flow model including contributions from the cardiac pulsations but no cilia forces.
-Here, we set the tangential traction to zero on the cilia boundary $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.
-% Model II
-    %\item Model II: Only cardiac pulsations are modeled, no cilia forces.
-
-    %\item Model IIb: Only cardiac pulsations are modeled, using the domain movement approach. No cilia forces.
+    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the cardiac pulsations but no cilia forces.
+    Here, we set the tangential traction to zero on the cilia boundary $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.  % Model II
 \end{itemize}
-
-%% \begin{table}[h!]
-%%     \centering
-%%     \caption{A summary of the flow model versions. For all model versions, we consider a free slip boundary condition on $\Gs=\Gamma\setminus\left(\Gc\cup\Gp\right)$.}
-%%     \label{tab:flow_model_versions}
-%%     \begin{tabular}{c|c@{\hskip 0.4in}c}
-%%        \toprule
-%%        Model & Driving force & Flow BCs \\ %& Domain motion \\
-%%        \midrule
-%%        Baseline (0)   & Cilia and cardiac & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$, \\ normal pressure $\Tilde{p}(t)$ on $\Gp$} \\[0.3in] %& No\\[0.3in]
-%%        No cardiac (I) & Cilia   & \makecell[l]{Impermeability $\uu\cdot\nn=0$ and tangential traction $\bsigpar=\btau$ on $\Gc$} \\[0.3in]%& No\\[0.3in]
-%%        No cilia (II) & Cardiac & \makecell[c]{Normal pressure $\Tilde{p}(t)$ on $\Gp$} \\% & No\\[0.3in]
-%%        %No cilia (IIb) & Cardiac & \makecell[l]{Impermeability $\mathbf{w}\cdot\nn=0$ and \\ free slip $\bsigpar(\mathbf{w}, p)=\mathbf{0}$ on $\Gamma$}  & Yes \\
-%%        \bottomrule
-%%     \end{tabular}
-%% \end{table}
 
@@
 To simulate transport in the pathological case of region-specific cilia absence, we consider three scenarios where we modify the boundary conditions of the CSF flow model.
-The cilia tangential stress boundary condition for the boundary where we remove cilia is changed to a free-slip boundary condition, prescribing zero tangential forces to represent absence of cilia motion in the region where we consider cilia removal.
-We consider removal of cilia in the three separate cilia-covered regions of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle, and the ventral part of the diencephalic ventricle~(\cref{fig:figure1}, panel~\textbf{d}).
-For the three scenarios, we simulate CSF flow modeled by the Stokes equations~\eqref{eq:stokes_eqs} with the modified boundary conditions, and use the resulting velocity field in transport simulations.
+The cilia tangential stress boundary condition for the boundary where we remove cilia is changed to a free-slip boundary condition,
+prescribing zero tangential forces to represent absence of cilia motion in the region where we consider cilia removal.
+We consider removal of cilia in the three separate cilia-covered regions of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle,
+and the ventral part of the diencephalic ventricle~(\Cref{fig:figure1}d).
+For the three scenarios, we simulate CSF flow modeled by the Stokes equations~\eqref{eq:stokes_eqs} with the modified boundary conditions,
+and use the resulting velocity field in transport simulations.
 
@@
 \fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming but stable discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-The discretization includes a penalty parameter $\gamma$ which needs to be chosen large enough to ensure stability of the finite element method.
-We set $\gamma=10$.} Since the divergence of the velocity is a subspace of the pressure space for this scheme, the divergence-free condition of the velocity is satisfied exactly on each element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
-
-\mer{MER: I think this is too much detail. One sentence suffices, or it goes in the Supplementary.}
-In the absence of pressure boundary conditions, the pressure in the Stokes equations is only determined up to an additive constant.
-Thus, with the boundary conditions used in model version I, the pressure is not uniquely defined and discretization of the Stokes equations leads to a singular linear equation system.
-To make the discrete problem well-posed for this setup, the right-hand side vector of the linear system assembled after discretization of the Stokes equations equations is orthogonalized with respect to the basis of the nullspace of the pressure to ensure existence of solutions.
-This nullspace is the set of (real) scalar constants.
-Furthermore, information of the pressure nullspace is provided to the linear solver, such that a unique solution is determined.
-
-\subsection*{Numerical approximation of the transport equations}
-The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized with a first-order implicit Euler method in time, and a first-order, symmetric interior penalty discontinuous Galerkin (DG) method in space~\cite{Arnold1982AnElements}.
+The discretization includes a penalty parameter $\gamma$ which needs to be chosen large enough to ensure stability of the finite element method. We set $\gamma=10$.}
+Since the divergence of the velocity is a subspace of the pressure space for this scheme, the divergence-free condition of the velocity is satisfied exactly on each element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
+
+\subsection*{Numerical approximation of the advection-diffusion equation}
+The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized with a first-order implicit Euler method in time, and a first-order,
+symmetric interior penalty discontinuous Galerkin (DG) method in space~\cite{Arnold1982AnElements}.
 To accurately approximate the solute concentrations even in the presence of strong advection (high Péclet numbers), we use an upwind scheme for the velocity when calculating the advective flux~\cite{Patankar2018NumericalFlow}.
-As for the flow equations, we use a timestep size of $\Delta t = 0.02252$ s.
-We simulate transport for 1900 cardiac cycles, with a final time of simulation $T = 856$ s.
+As for the flow equations, we use a timestep size of $\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles, with a final time of simulation $T = 856$ s.
 A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
@@
 Because of the one-way coupling between the velocity field $\uu$ and the concentration $c$, the governing equations for the CSF flow and the concentration can be solved sequentially when modeling solute transport.
-\fixme{For the no-cardiac/cilia-only flow scenario, the velocity quickly reaches steady-state.} In this case, we first solve the \fixme{steady-state} Stokes equations~\eqref{eq:stokes_eqs} for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
+\fixme{For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state.} In this case, we first solve the \fixme{steady-state} Stokes equations~\eqref{eq:stokes_eqs} for $\uu$ and $p$,
+and then use the velocity field $\uu$ as input when solving the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
 For the other flow scenarios, the Stokes equations are solved for one period of the pulsatile cardiac motion.
@@
 
-The numerical solution schemes for the Stokes equations and the advection-diffusion equation were implemented and solved numerically with DOLFINx, the Python interface of the finite element software FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
+The numerical solution schemes for the Stokes equations and the advection-diffusion equation were implemented and solved numerically with DOLFINx,
+the Python interface of the finite element software FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
 A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the linear systems resulting from the discretized Stokes equations.
 For the discretized advection-diffusion equation, we used an iterative linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen}.
-Numerical experiments verified the accuracy of the model implementation (\cref{sec:appB_verification}).
-The simulation code is openly available~\cite{zenodo-link-to-all-code}.
+Numerical experiments verified the accuracy of the model implementation (\Cref{sec:appB_verification}). The simulation code is openly available~\cite{zenodo-link-to-all-code}.
 
@@
 anterior and middle ventricles and \fixme{unidirectional} flow in the
-posterior ventricle (\Cref{fig:figure1}\textbf{e},
+posterior ventricle (\Cref{fig:figure1}e,
 \fixme{Supplementary video 1}). These characteristic patterns suggest
@@
 this scenario, the simulated CSF flow is pulsatile and
-\fixme{unidirectional} (\cref{fig:figure1}g), with a peak velocity
+\fixme{unidirectional} (\Cref{fig:figure1}g), with a peak velocity
 magnitude of \fixme{$4.8$ \textmu m/s}. On the other hand, the
 vortices (re)appear when considering a variation with cilia but no
-cardiac contribution (\cref{fig:figure1}h), in which case the highest
+cardiac contribution (\Cref{fig:figure1}h), in which case the highest
 velocities ($26.5$ \textmu m/s) also occur in the vicinity of the
@@
 
-\subsection*{Ventricular solute transport is advection-dominated for \fixme{larger} molecules}
+\subsection*{Ventricular solute transport is advection-dominated for larger molecules}
 We next ask what is the impact of these CSF flow patterns and
@@
 (\Cref{fig:fig2}a). The vortex structures of the velocity field
-carries over into the concentration field, indicating that transport
+carry over into the concentration field, indicating that transport
 along the streamlines is more rapid than the diffusion across the
@@
     \caption{Simulated distribution and evolution after photoconversion of Dendra ($D_1$), STM+GFP ($D_2$) and Exosomes ($D_3$).
-\mer{MER: I think you should show on the same color scale here in a) (the range of values lets you and then it is possible to compare).
-Split a into a, b, c.
-Show e) first (so that e) becomes a)}.
+    \mer{MER: I think you should show on the same color scale here in a) (the range of values lets you and then it is possible to compare). Split a into a, b, c. Show e) first (so that e) becomes a)}.
     \textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm, the center of the geometry) showing the concentration field simulated with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s.
@@
 
-Transport of solute is quantified by the profile of the mean concentrations $\overline{c}_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\cref{fig:fig2}, panels \textbf{b--d}).
-An illustration of the ROIs is provided in \cref{fig:fig2}, panel~\textbf{e}.
-The dynamics of ROI 1 follow from imposing~\cref{eq:injection_curve}.
+Transport of solute is quantified by the profile of the mean concentrations $\overline{c}_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\Cref{fig:fig2}b--d).
+An illustration of the ROIs is provided in \Cref{fig:fig2}e. The dynamics of ROI 1 follow from imposing~\Cref{eq:injection_curve}.
 For ROIs 2--6, we observe more rapid concentration increases when the diffusion coefficient increases. 
@@
 The profiles of the latter three regions are similar, displaying only small differences in all of the three plots.
-\lyng{HH: Add some quantification in terms of percentages, e.g.
-final values of $\overline{c}_i$ for the different $D_i$?}
-%\lyng{HH: is this really true?: Note that the total mass added to the system is not exactly the same for all three diffusion coefficients, since the total mass added depends on how fast the mass added in ROI 1 is transported away from that region.}
-%
-%
-%\mer{MER: This belongs in Methods (and is written there) or does not need to be stated.}
-%% We report the times $\hat{t}$ when the mean concentrations $\overline{c}_i$ first exceed a threshold value $\hat{c}$~(\cref{fig:fig2}, panel \textbf{f}).
-Recall that $\hat{c}=0.25$ for regions of interest 1--4 and $\hat{c}=0.10$ for regions 5 and 6.
-The choice of different threshold values is because of the slower dynamics in ROIs 5 and 6.
+\lyng{HH: Add some quantification in terms of percentages, e.g. final values of $\overline{c}_i$ for the different $D_i$?}
 In region 6, the threshold is never exceeded for $D_1$, with the mean concentration close to zero at the end of the simulation. 
-
-%% \mer{Moved this to Methods.}
-%% Finally, we calculate Péclet numbers for the entire ventricular geometry using estimates of the diffusion and advection timescales $t_d=L_p^2/D$ and $t_a=L_p/U_p$.
-%% Recall that
-%% \begin{equation*}
-%%     \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a},
-%% \end{equation*}
-%% so that if $\mathrm{Pe} > 1$, transport is dominated by advection, and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
-For the length scale $L_p$ we choose the approximate length of the ventricles geometry in the $x$-direction, $L_p=600 \ \mu$m.
-We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
-The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
-%% \begin{equation*}
-%%     \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
-%% \end{equation*}
-%% and then averaging $\overline{u}$ in time over one cardiac cycle to obtain $\overline{U}=1.41 \ \mu$m/s.
-This yields the three Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
-\lyng{HH: move choice of length scale/calculation of velocity scale to Methods?
-Same question for Reynolds number calculation.} \mer{MER: Yes, definitely.}
+To quantify the balance of advection versus diffusion as transport mehcanisms on a global scale, we calculate the Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
+Since $\mathrm{Pe}>1$, this indicates that advection is the dominant transport mechanism for the molecules considered.
 
 \subsection*{Comparing experimental and computational results}
-Transport of photoconverted proteins is quantified by the change in fluorescence intensity $\Delta F=(F(t)-F_0)/F_0$ over time~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}).
+Transport of photoconverted proteins is quantified by the change in fluorescence intensity $\Delta F=(F(t)-F_0)/F_0$ over time~(\Cref{fig:figure3_compare_exp_and_sim_control}a).
 The solid lines are the mean values of $\Delta F$ for the fish cohort, with shaded regions covering one standard deviation.

### 2025-02-03 paper/main.tex
add Introduction

@@
 \usepackage{xcolor,colortbl}
-%\usepackage{soul}
 \usepackage[nameinlink, capitalise]{cleveref}
@@
 \newcommand{\uu}{\mathbf{u}}
-\newcommand{\uuref}{\mathbf{u}_{\mathrm{ref}}}
 \newcommand{\vv}{\mathbf{v}}
@@
 \section*{Introduction}
-\lyng{HH: This needs work, have just jotted down some stuff to have references ready.}
-
-Development of brains and sustaining healthy functioning of the brain relies on a myriad of regulatory processes.
-One of these processes is the flow of cerebrospinal fluid (CSF) in the brain ventricles.
-The brain ventricles are hollow structures inside the skull where CSF is produced and flows around, transporting nutrients, neurotransmitters and other molecules important for neural development.
-
-The inner walls of the brain ventricles are lined with an epithelial cell layer.
-In some regions of the ventricles, motile cilia protrude the epithelial cell layer.
-Motile cilia are hair-like structures that beat in a metachronal wave pattern such as to generate a complicated flow pattern in the brain ventricles.
-Motile cilia are also found in other parts of the body where fluids are transport, such as the airways, liver and intestines.
-Regarding the function of motile cilia in the brain, it has previously been pointed out that further studies are needed for investigating their role~\cite{Eichele2020Cilia-drivenVentricle}, as well as the role of spatially organized CSF flow~\cite{Olstad2019CiliaryDevelopment}, in the development of the brain and its ventricular system.
-
-Experiments~\cite{Olstad2019CiliaryDevelopment} have demonstrated that cilia induce a directional flow in the brain ventricles.
-In addition to the directional flow induced by motile cilia, a pulsatile component in the CSF flow in zebrafish ventricles has been observed~\cite{Olstad2019CiliaryDevelopment}.
-Cilia are also found to serve crucial roles in other organs than the brain.
-Motile cilia are essential for olfactory computations~\cite{Reiten2017Motile-Cilia-MediatedComputations}, and they are also fundamental to mucous transport in the trachea~\cite{Sleigh1988TheCilia}.
-
-Early computational studies modeled ciliary transport of mucous in lungs with mathematics~\cite{Fulford1986Muco-ciliaryLung}.
-Propulsion of ciliated organisms has for some time been studied with mathematics~\cite{BLAKE1974MechanicsMotion}.
-According to Brennen~\emph{et al.}~\cite{Brennen1977FluidFlagella}, the study of cilia locomotion and fluid systems utilizing cilia sparked interest after a review on locomotion of protozoa microorganisms performed by Jahn~\emph{et al.}~\cite{Jahn1972LocomotionProtozoa}.
-Fine-scale interaction between single or several cilia and surrounding fluids has previously been analyzed with mathematics and numerics~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids, Cui2019NumericalMethod, Cui2022AFlow}, also specifically for cilia in brain ventricles of zebrafish embryos~\cite{Salman2022ComputationalEmbryo}.
-Quantification of bulk flow and effects on bulk transport by cilia arrays (or sheets) have not been studied as much, though by some~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
-Two-dimensional modeling of flow and transport mediated by motile cilia in zebrafish brain central canal has previously been carried out~\cite{Thouvenin2020OriginCanal}.
-There is, however, very limited research on three-dimensional modeling of cilia-mediated flow and transport in brain ventricles.
-There are a couple of studies indicating that the effect of cilia on CSF flow is local in the human brain~\cite{Siyahhan2014FlowVentricles, Yoshida2022EffectVentricles}.
-Zebrafish ventricles are much smaller than human ventricles, meaning cilia play a larger role in establishing a CSF flow pattern.
-We wish to investigate the mechanisms of ciliary and cardiac-beating flow components, and how they each contribute to transport of molecules inside the brain ventricles.
-
-In this paper, we present protein photoconversion experiments in zebrafish embryo brain ventricles, as well as a computational model of cerebrospinal fluid flow and protein transport.
+Brain development and function depend on numerous regulatory processes, including interactions with cerebrospinal fluid (CSF).
+CSF is a clear liquid produced by the choroid plexus, which is a secretory epithelium located within the brain ventricles.
+Following production, CSF flows through the ventricular system and subarachnoid space, where it regulates brain development and
+homeostasis by transporting growth factors, nutrients, neurotransmitters, waste products and other molecules and metabolites.
+
+To achieve its function, CSF needs to circulate throughout the brain. In fact, CSF disturbances can univocally lead to brain disorders,
+such as hydrocephalus where accumulation of CSF requires emergency surgical treatment.
+CSF movement occurs through multiple physiological processes, including the action of motile cilia on the ventricular wall,
+CSF secretion by the choroid plexus and pressure gradients generated by the cardiac cycle, respiration, and bodily movement.
+Motile cilia are microscopic hair-like structures that beat in a metachronal wave pattern to generate flow pattern. Due to their microscopic size, ranging from 6 to 15 microns,
+they contribute to fluid flow primarily at the surface of the brain ventricles.
+In contrast, pressure gradients generate fluid flow further from the ventricular walls and along the perivascular space surrounding the major blood vessels.
+
+To date, it remains poorly understood how cilia contribute to the overall fluid flow and solute transport in the brain.
+These questions have been especially challenging to tackle due to technical limitations.
+Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz, while other fluid dynamic processes in the brain are slower and span larger three-dimensional volumes.
+Most studies until now have analyzed one process at a time, especially in mammals.
+For instance, multiple studies have convincingly shown that cilia generate complex flow patterns at the surface of the brain ventricles.
+However, since all these studies have been performed on brain explants, they failed to identify the role of pressure gradients associated with respiration and heart pulsations in CSF transport.
+Similarly, while MRI technology can measure CSF movement in humans, it cannot detect the fast movements of cilia or understand their impact in the large human brain.
+Consequently, we lack a comprehensive understanding of how cilia contribute to CSF movement and solute transport, and whether cilia dysfunction will alter CSF distribution and lead to brain disorders.
+This is particularly important since ventricular enlargement or hydrocephalus is commonly observed in animal models with motile cilia deficiency, potentially affecting brain activity and behavior.
+
+The technical limitations of studying cilia-mediated flow and transport opens the possibility of computational investigations. Cilia have been studied previously with mathematical modeling,
+with numerous studies on the interaction between single or several cilia and surrounding fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids, Cui2019NumericalMethod, Cui2022AFlow}.
+Others consider applications such as ciliary transport of mucous in airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
+propulsion and locomotion of ciliated organisms~\cite{BLAKE1974MechanicsMotion, Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella},
+coral reefs~\cite{Pacherres2022CiliaryProduction}, and the brain~\cite{Siyahhan2014FlowVentricles, Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
+
+In this study, we combined computational and experimental approaches to investigate the role of motile cilia in CSF flow generation and solute transport.
+First, we computed flow patterns and intraventricular transport in silico. To this end, we used the geometry of the zebrafish larval brain ventricles,
+for which we have detailed knowledge of cilia properties and CSF movement velocities and frequencies.
+Notably, this early developmental stage allows us to simplify our model by omitting CSF secretion, which starts at later stages, while still being well conserved with mammals.
+Next, we validated our computation model with experimental data by monitoring the dynamics of a photoconvertible fluorescent protein expressed within the brain ventricles.
+Our results identified that diffusion plays a major role in the transport of small solutes, whereas cilia majorly contribute to the movement of larger particles.
+We also found that the location of cilia and the ventricular geometry greatly impact solute distribution.
+Altogether, our work presents a computational framework and new concepts of how cilia collaborate with other factors to distribute molecules and particles within the brain ventricles.
 
 \section*{Methods}
-\label{sec:methods}
 

### 2025-02-03 paper/main.tex
methods: update experimental, switch order experimental-computational

@@
 \newcommand{\lyng}[1]{\textcolor{blue}{#1}}
-\newcommand{\rt}[1]{\textcolor{red}{#1}}
 \newcommand{\mer}[1]{\textcolor{magenta}{#1}}
@@
 \author[1,3,+]{Marie E.~Rognes} % OK order?
-\author[2,+]{Nathalie Jurisch-Yaksi}
+\author[2,+, *]{Nathalie Jurisch-Yaksi}
 \affil[1]{Department for Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
@@
 \affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
-\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}}
+\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no} \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
 \affil[+]{these authors contributed equally to this work}
@@
   pdftitle={zebrafish-cilia-csf},
-  pdfauthor={H.~Herlyng \textit{et al.}}
+  pdfauthor={H.~Herlyng~\emph{et al.}}
 }
@@
 Motivated by experimental observations, we consider motile cilia and cardiac beating as the driving flow mechanisms.
-A mathematical model of the flow is developed and coupled with a transport model to study the transport of molecules inside the brain ventricles.
-The Stokes equations are used to model the flow, with the motile cilia acting as a force on the fluid through a stress boundary condition that allows slip at the wall.
-Transport is modeled with an advection-diffusion equation coupled to the velocity field obtained from solving the Stokes equations.
-The flow and transport models are discretized with finite element methods.
+    %A mathematical model of the flow is developed and coupled with a transport model to study the transport of molecules inside the brain ventricles. 
+    %The Stokes equations are used to model the flow, with the motile cilia acting as a force on the fluid through a stress boundary condition that allows slip at the wall. 
+    %Transport is modeled with an advection-diffusion equation coupled to the velocity field obtained from solving the Stokes equations.
+    %The flow and transport models are discretized with finite element methods.
 For the Stokes equations we employ a non-conforming discretization based on elements of the Brezzi-Douglas-Marini family.
-The advection-diffusion equation is discretized with discontinuous Galerkin elements.
-We implement and solve the discretized equations numerically to simulate flow and transport in a zebrafish brain ventricles geometry obtained with medical imaging.
+    %The advection-diffusion equation is discretized with discontinuous Galerkin elements. 
+    %We implement and solve the discretized equations numerically to simulate flow and transport in a zebrafish brain ventricles geometry obtained with medical imaging.
 \end{abstract}
@@
 
-The technical limitations of studying cilia-mediated flow and transport opens the possibility of computational investigations. Cilia have been studied previously with mathematical modeling,
+The technical limitations of studying cilia-mediated flow and transport opens the possibility of mathematical modeling and computational investigations. Cilia have been studied previously,
 with numerous studies on the interaction between single or several cilia and surrounding fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids, Cui2019NumericalMethod, Cui2022AFlow}.
-Others consider applications such as ciliary transport of mucous in airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
+Others considered applications such as ciliary transport of mucous in airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
 propulsion and locomotion of ciliated organisms~\cite{BLAKE1974MechanicsMotion, Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella},
 coral reefs~\cite{Pacherres2022CiliaryProduction}, and the brain~\cite{Siyahhan2014FlowVentricles, Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
+These studies have provided valuable insights, showing that cilia lend themselves to simulation studies.
 
@@
 \mer{@HH: I suggest you write \cref{fig:figure1}a, rather than \cref{fig:figure1} panel \textbf{a}, throughout. Increases signal-to-noise ratio.}
-
-\subsection*{Zebrafish maintenance and strains in photoconversion experiments}
-The zebrafish~(\emph{danio rerio}) animal facilities used are approved by the Norwegian Food Safety Authority (NFSA, Mattilsynet).
-Furthermore, the zebrafish were maintained in accordance with the guidelines set by the NFSA and the European Communities Council Directive.
-The larval and adult zebrafish were raised under standard husbandry conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
-The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a 14/10 hr light/dark cycle.
-From fertilization to 3 dpf, larvae were maintained in egg water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water) and subsequently transferred to artificial fish water (AFW) (1.2 g marine salt in 20 L RO water).
-The zebrafish lines used in the experiments were \emph{ccdc103(dnaaf19)\textsuperscript{tn222a}} (\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}(received from Drummond lab, MGH) and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures}, \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
-Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
-
-Whole-mount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at the 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described by D’Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
-Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+}) or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
-The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
-
-\subsection*{Genotyping}
-Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA, tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
-To stop the lysis reaction, the samples were heated to 95°C for 10 minutes and then centrifuged at 13000 rpm for 2 minutes.
-The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14 $\mu$L of assay mix; 1.86 $\mu$L of RO water.
-
-\subsection*{Generation of \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}} line}
-\mer{MER: Could this heading be made understandable by non-experts?}
-The open reading frame (ORF) of the neuropeptide y (npy) signal peptide (\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal of zebrafish codon optimized Dendra2 DNA sequence.
-Next the conjugated DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and 3’ ends (GenScript Biotech), and the synthesized signal-Dendra2 DNA was inserted into the pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish} through restriction enzyme cloning (GenScript Biotech).
-To generate the transgenic line, the 5xuas:Signal-Dendra2 plasmid DNA was used.
-A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg) was microinjected into one-cell stage embryos, as described by Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}.
-The injected embryos were raised to adulthood (F0).
-Germline-transmitted founder zebrafish were identified by breeding with multiple Gal4 transgenic lines.
-Stable F1 embryos expressing the Gal4-driven Dendra2 signals were screened and raised to adult zebrafish.
-
-\subsection*{Whole-mount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
-To image 2 dpf larval zebrafish, the fish were anesthetized in 0.013\% MS222 in AFW and mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100), to obtain a lateral view of the brain ventricles.
-After the fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
-After solidification, AFW containing 0.013\% MS222 was added, and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss) and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat) at room temperature.
-
-The time-lapse images were acquired in a single plane, covering the telencephalic, diencephalic and rhombencephalic ventricles simultaneously, with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame).
-The size of the images was $1024\times400$ pixels.
-In total, 300 images were acquired per fish.
-The first 10 images were scanned without photoconversion to obtain a baseline value of fluorescence intensity, and the next 290 images were scanned while performing photoconversion.
-For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software were used.
-A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel) of the dorsoposterior diencephalic ventricle with 100\% laser power.
-The laser was illuminated in the area repeatedly between each scanning.
-After imaging, the fish health was checked and only data from healthy fish were analyzed.
-Data were collected and analyzed from three separate experiments, with a total of 8 controls and 6 mutants.
-
-\subsection*{Photoconversion data analysis}
-
-Photoconversion data analysis was performed in MATLAB and the codes are \fixme{openly available\cite{zenodo-archive-for-repo-link-fixme}}.
-Following import of the image data, the photoconverted channel was aligned to correct for drift in $x,y$ directions using previously developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
-Only stable recordings were further analyzed.
-To increase the signal-to-noise ratio, the images were downsampled by a block average using a resampling factor of 6 (using the MATLAB function blockproc).
-The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as $\Delta F$$)$ was calculated for each pixel at each time point of the data.
-Here, the value $F_0$ is the average fluorescence intensity for the baseline (the first 10 time-lapse images) acquired before photoconversion.
-
-To identify the time needed to pass a certain threshold value, $\Delta F$ values were first smoothened.
-The first timepoint when values surpassed the threshold was reported per pixel (in the downsampled images).
-A mask for the image was generated using the green (not photoconverted) channel and calculated on the block-averaged data based on the intensity being higher than 1.5x median intensity of all the frames.
-
-In order to obtain $\Delta F$ values for a region of interest (ROI), ROIs were first drawn on the aligned and block-averaged time series.
-Six ROIs were drawn manually: ROI 1 at the location of photoconversion, and ROIs 2--6 in different regions of the ventricular system.
-The pixel values of the fluorescence intensity within one ROI are averaged for each time point, and the relative change $\Delta F$ is then calculated with this averaged value.
-To normalize the data with respect to photoconversion efficiency, the $\Delta F$ curves for all ROIs were divided by the $\Delta F$ values obtained for ROI 1 at the end of the experiment, so that $\Delta F$ values for the photoconverted site ROI 1 ranged from zero to one.
-Finally, we average the $\Delta F$ data from controls over the number of controls, and the data from mutants over the number of mutants.
-We report these mean values together with a one-standard deviation error band.
-
-\subsection*{Intraventricular injection of microbeads and particle tracking}
-In addition to photoconversion experiments, we carried out particle tracking inside the brain ventricles of a larval zebrafish, to demonstrate the motile-cilia and cardiac-cycle related flow features observed and described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}.
-A schematical illustration of the flow features in the brain ventricles is shown in~\Cref{fig:figure1}a.
-Our experimental setup for the particle tracking is identical to the ones considered there (\lyng{HH: Is this true?}), and we refer to that paper for further details than the ones provided here in the following.
-
-Anesthetized 2 dpf control zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads (SPHERO Fluorescent Yellow Particles 1\% w/v, $F = 0.16$ mm) diluted in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITC-dextran; Sigma-Aldrich, R9379) dissolved in artificial CSF.
-Artificial CSF composition was as follows: 124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O, 1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3}, 2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
-The needles used for the injections were pulled with a Sutter Instrument Co.
-Model P-2000 from thin-walled glass capillaries (1.00 mm; VWR) and cut open with a forceps.
-A volume of 1 nl of the solution was injected with a pressure injector (Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
-The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
-
-Following injection, the zebrafish was directly placed under the confocal microscope and 1200 images were acquired at a frequency of 13.1 Hz.
-A single optical section was obtained.
-Particle tracking was done using TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis} and plotted using MATLAB, as described by Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
-The parameters for TrackMate were as follows.
-The DoG detector was used with the settings: threshold: 2.0, with median filtering; radius: 2.0, with subpixel localization.
-Next, the Simple LAP tracker was used with settings: max frame gap: 2; alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0; splitting max distance: 15.0; allow gap closing: true; allow track splitting: false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
-Only the particle tracks with at least 30 data points, while simultaneously covering a distance of at least 8.8 $\mu$m, were shown (\cref{fig:figure1}, panels \textbf{b} and \textbf{c}).
 
@@
 To computationally represent protein photoconversion in a region $\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1), we prescribe a given time-dependent value to the solute concentration in this region.
-% in $\Omega_{\mathrm{pc}}$.
-%, such that $c(\xx, t)$ for all $\xx\in\Omega_{\mathrm{pc}}$ and $t>0$.
 Mimicking the experimental protocol, we consider the dorsal part of the diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
@@
 
+%%------PHYSICAL EXPERIMENTS------%%
+\subsection*{Zebrafish maintenance and strains in photoconversion experiments}
+The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the Norwegian Food Safety Authority (NFSA, Mattilsynet).
+The zebrafish were maintained in accordance with the guidelines set by the NFSA and the European Communities Council Directive.
+
+The larval and adult zebrafish were raised under standard husbandry conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
+The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a 14/10 hr light/dark cycle.
+From fertilization to 3 dpf, larvae were maintained in egg water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
+and subsequently transferred to artificial fish water (AFW) (1.2 g marine salt in 20 L RO water).
+The zebrafish lines used in the experiments were \emph{ccdc103(dnaaf19)\textsuperscript{tn222a}} (\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
+and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures}, \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
+Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
+
+Wholemount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
+\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+}) or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
+The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
+
+\subsection*{Genotyping of adult zebrafish}
+Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA, tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
+To stop the lysis reaction, the samples were heated to 95°C for 10 minutes and then centrifuged at 13000 rpm for 2 minutes.
+The supernatant containing gDNA was utilized for KASP assays-based analysis.
+The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
+For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14 $\mu$L of assay mix; 1.86 $\mu$L of RO water.
+
+\subsection*{Generation of \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}} line}
+\lyng{Needs a more understandable title.}
+The open reading frame (ORF) of the neuropeptide y (npy) signal peptide (\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal of zebrafish codon optimized Dendra2 DNA sequence.
+The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and 3’ ends (GenScript Biotech),
+and inserted into the pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish} through restriction enzyme cloning (GenScript Biotech).
+
+To generate the transgenic line, the 5xuas:Signal-Dendra2 plasmid DNA was used.
+A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg) was microinjected into one-cell stage embryos,
+as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected embryos were raised to adulthood (F0).
+Germline-transmitted founder zebrafish were identified by breeding with multiple Gal4 transgenic lines.
+Stable F1 embryos expressing the Gal4-driven Dendra2 signals were screened and raised to adult zebrafish.
+
+\subsection*{Wholemount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
+Two dpf larval zebrafish were anesthetized in 0.013\% MS222 (Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
+to obtain a lateral view of the brain ventricles. After the fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
+After solidification, AFW containing 0.013\% MS222 was added, and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
+and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat) at room temperature.
+
+The time-lapse images were acquired in a single plane, covering the telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
+with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
+The first 10 images were scanned without photoconversion to obtain a baseline value of fluorescence intensity, and the next 290 images were scanned while performing photoconversion.
+
+For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software were used. A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel)
+of the dorsoposterior diencephalic ventricle with 100\% laser power. The laser was illuminated in the area repeatedly between each scanning.
+After imaging, the fish health was checked and only data from healthy fish were analyzed.
+Data were collected and analyzed from three separate experiments, with a total of 8 controls and 6 mutants.
+
+\subsection*{Photoconversion data analysis}
+All data analysis was performed in MATLAB and the codes are available in the repository of this article: \url{repo-link}.
+
+Following import of the image data, the photoconverted channel was aligned to correct for drift
+in $x,y$ directions using previously developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}. Only stable recordings were further analyzed. 
+To increase the signal to noise ratio, the images were downsampled by a block average using a resampling factor of 6 (using the MATLAB function blockproc).
+The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as $\Delta F$$)$ was calculated for each pixel at each time point of the data.
+Here, the value $F_0$ is the average fluorescence intensity for the baseline (the first 10 time-lapse images) acquired before photoconversion.
+
+To identify the time needed to pass a certain threshold value, $\Delta F$ values were first smoothened.
+The first timepoint when values surpassed the threshold was reported per pixel (in the downsampled images).
+A mask for the image was generated using the green (not photoconverted) channel and calculated on the block-averaged data based on the intensity being higher than 1.5x median intensity of all the frames.
+
+To obtain $\Delta F$ values for a region of interest (ROI), ROIs were first drawn on the aligned and block-averaged time series.
+Six ROIs were drawn manually: ROI 1 around the location of photoconversion, and ROIs 2--6 in different regions of the ventricular system.
+The pixel values of the fluorescence intensity within one ROI were averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
+To normalize the data with respect to photoconversion efficiency, the $\Delta F$ curves for all ROIs were divided by the $\Delta F$ values obtained for ROI 1 at the end of the experiment,
+so that $\Delta F$ values for the photoconverted site ROI 1 ranged from zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
+We report these mean values together with a one-standard deviation error band.
+
+\subsection*{Intraventricular injection of microbeads and particle tracking}
+To recover the flow fields shown in~\Cref{fig:figure1}b, c, we carried out particle tracking in a larval zebrafish injected with fluorescent beads.
+As described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}, anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
+(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
+dissolved in artificial CSF. Artificial CSF composition was as follows: 124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
+1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3}, 2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
+The needles used for the injections were pulled with a Sutter Instrument Co. Model P-2000 from thin-walled glass capillaries (1.00 mm; VWR) and cut open with a forceps.
+A volume of 1 nl of the solution was injected with a pressure injector (Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
+The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
+
+Following injection, the zebrafish was directly placed under the confocal microscope and 1200 images were acquired at a frequency of 13.1 Hz.
+A single optical section was obtained. Particle tracking was done using TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
+and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}. The parameters for TrackMate were as follows.
+The DoG detector was used with the settings: threshold: 2.0, with median filtering; radius: 2.0, with subpixel localization.
+Next, the Simple LAP tracker was used with settings: max frame gap: 2; alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
+splitting max distance: 15.0; allow gap closing: true; allow track splitting: false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
+Only the particle tracks with at least 30 data points, while simultaneously covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:figure1}b, c.
+
 %%--------------RESULTS--------------%%

### 2025-02-03 paper/main.tex
Results: modify sections 2-5, add a reference

@@
 %% Some new commands
+% Math
+\newcommand{\cbar}{\overline{c}}
+
 % Partial derivatives
@@
 \begin{equation}
-    \overline{c}_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
+    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
     \label{eq:c_mean_i}
@@
 The dynamics of ROI 1 follows directly from~\eqref{eq:injection_curve}.
-In addition, we report time-to-threshold: the time $\hat{t}_i$ when the mean concentration $\overline{c}_i$ first exceed a threshold value $\hat{c}_i$.
+In addition, we report time-to-threshold: the time $\hat{t}_i$ when the mean concentration $\cbar_i$ first exceed a threshold value $\hat{c}_i$.
 We use $\hat{c}_i=0.25$ for ROI 1--4 and $\hat{c}_i=0.10$ for ROI 5--6.
@@
     Note that the colorbars indicating the magnitude of $c$ have different limits for each column.
-    \textbf{b--d.} Mean concentration $\overline{c}$ in each region of interest (ROI) as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively.
+    \textbf{b--d.} Mean concentration $\cbar$ in each region of interest (ROI) as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively.
     \textbf{e.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
-    \textbf{f.} The time $\hat{t}$ before the mean concentration $\overline{c}$ exceeds a threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.
+    \textbf{f.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.
     Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}
@@
 
-Transport of solute is quantified by the profile of the mean concentrations $\overline{c}_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\Cref{fig:fig2}b--d).
+Transport of solute is quantified by the profile of the mean concentrations $\cbar_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\Cref{fig:fig2}b--d).
 An illustration of the ROIs is provided in \Cref{fig:fig2}e. The dynamics of ROI 1 follow from imposing~\Cref{eq:injection_curve}.
@@
 The profiles of the latter three regions are similar, displaying only small differences in all of the three plots.
-\lyng{HH: Add some quantification in terms of percentages, e.g. final values of $\overline{c}_i$ for the different $D_i$?}
+\lyng{HH: Add some quantification in terms of percentages, e.g. final values of $\cbar_i$ for the different $D_i$?}
 In region 6, the threshold is never exceeded for $D_1$, with the mean concentration close to zero at the end of the simulation. 
@@
 
-\subsection*{Comparing experimental and computational results}
-Transport of photoconverted proteins is quantified by the change in fluorescence intensity $\Delta F=(F(t)-F_0)/F_0$ over time~(\Cref{fig:figure3_compare_exp_and_sim_control}a).
-The solid lines are the mean values of $\Delta F$ for the fish cohort, with shaded regions covering one standard deviation.
-The first region of interest (ROI 1) is the laser-targeted region.
-Qualitatively, the fluorescence intensity change in this region resembles intensity dynamics observed in experiments that studied the photoconversion properties of Dendra2 fluorescent proteins~\cite{Makarov2014Steady-stateDendra2}.
-The transport to the other regions can be separated into two groups: the fluorescence intensity change $\Delta F$ for ROIs 2--4 in the middle ventricle are all similar, whereas the more distal regions ROI 5 and 6 (anterior and posterior ventricle, respectively) exhibit a slower increase in $\Delta F$.
-In ROIs 2--4, the $\Delta F$ curves are concave, similar to ROI 1, while in ROIs 5 and 6 the curves are convex.
-Although the fluorescence intensity increases throughout all of the experiments, the maximum $\Delta F$ is not necessarily attained at the final time of the experiments.
-At the final time, the mean fluorescence intensities in regions 2--4 all exceed 0.60 (0.63, 0.71, 0.67, respectively) of the final value $F_0$ in ROI 1, whereas ROIs 5 and 6 reach mean values of 0.29 and 0.18, respectively.
-
+\subsection*{Validation of the simulations with experimental data}
+To validate our computational model, we performed photoconversion experiments in transgenic zebrafish larvae expressing a secreted Dendra2 in their brain ventricles.
+Our photoconversion protocol consisted of the acquisition of a baseline, before localized exposure to a UV laser (at the ROI 1 location)
+that converts Dendra2 from a green to a red emitting fluorescent protein. 
+To quantify the transport of photoconverted proteins, we measured and calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
+over time (\Cref{fig:figure3_compare_exp_and_sim_control}a, $F_0$ being the average fluorescence at baseline).
+
+We obtained very similar kinetics curves (\Cref{fig:figure3_compare_exp_and_sim_control}a, b)
+and time-to-threshold values (\Cref{fig:figure3_compare_exp_and_sim_control}c, d) when comparing our
+experiments (\Cref{fig:figure3_compare_exp_and_sim_control}a, c) with
+simulation (\Cref{fig:figure3_compare_exp_and_sim_control}b, d).
+Importantly, since the initial condition of the simulation is a mean concentration of zero,
+the mean concentration $\cbar$ can be interpreted as the change in mean concentration and is thus a similar metric to $\Delta F$.
+The final values of $\cbar$ were 0.76, 0.72, 0.82, 0.56 and 0.35 respectively,
+compared to 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
+Notwithstanding similarities, we observed small differences between the experiments and simulation.
+For instance, transport dynamics in ROIs 2--6 were faster in the simulation and reached higher final values.
+Moreover, the $\cbar$ profiles of ROIs 3--4 were opposite order in the simulations as compared to the experiments.
+Despite observing small differences, the \emph{in vivo} experiments and
+simulations were similar enough to convincingly validate the model.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
+    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time in each region of interest (ROI)
+    observed during experiments of photoconversion of Dendra2 proteins in ROI 1.
+    \textbf{b.} Mean concentration $\cbar$ as function of time in each ROI in a simulation of Dendra2 protein transport with
+    the diffusion coefficient $D_3$.
+    \textbf{c.} Time to $\Delta F$ reaches a threshold value of 0.25 in one representative zebrafish larva.
+    Time to $\cbar$ reaches a threshold value of 0.25 for a transport simulation with diffusion coefficient $D_3$.
+    We have excluded the posterior-most regions of the geometries,
+    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold value of 0.25 in these regions.}
+    \label{fig:figure3_compare_exp_and_sim_control}
+\end{figure}
 % Final Delta F values
@@
 %0.18155055624229066 ROI 6
-
-The experiment of photoconverting Dendra2 was simulated by solving the advection-diffusion equation with the diffusion coefficient $D_3$.
-We quantify the simulated transport with the time evolution of mean concentrations $\overline{c}$~(\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
-Imposing the concentration in ROI 1 mimics the fluorescence intensity change $\Delta F$ in ROI 1.
-Since the initial condition of the simulation is a mean concentration of zero, the mean concentration $\overline{c}$ can be interpreted as the change in mean concentration and is thus a similar metric to $\Delta F$.
-
-Comparing the simulation results with experimental results, transport dynamics of regions 2--6 are faster in the simulation.
-We observe higher final values of $\overline{c}$ compared to the final values of $\Delta F$ in the experiments.
-In simulations, the three $\overline{c}$ profiles of ROIs 2--4 behave similar as the $\Delta F$ profiles in these regions, although the orders of ROI 3 and 4 are opposite in the simulations as compared to the experiments.
-For all regions, the maximum mean concentration is attained at the final time of the simulations.
-The final value of $\overline{c}$ in regions 2--4 were 0.76, 0.72 and 0.82, respectively, compared to 0.63, 0.71 and 0.67 for $\Delta F$.
-As in the experiments, the transport to regions 5 and 6 is slower than the transport to the middle ventricle sites, though the final values of $\overline{c}$ are higher than those of $\Delta F$.
-The anterior ventricle (region 5) has a final $\overline{c}$ value of 0.56 (final $\Delta F= 0.29$), while in the posterior ventricle (region 6) the final value is 0.35 (final $\Delta F= 0.18$).
-Qualitatively, the $\overline{c}$ profile in the posterior ventricle compares with $\Delta F$ in this region, displaying a convex curve that has an approximately linear increase after an initial nonlinear increase.
-The anterior ventricle (region 5), on other hand, has an S-shaped $\overline{c}$ curve in the simulations, which differs from the linear $\Delta F$ curve in the experiments.
 % Final mean c values ROIs 2-6: 0.7637806  0.72025859 0.81903216 0.56204164 0.34926411
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
-    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time in each region of interest (ROI) observed during experiments of photoconversion of Dendra2 proteins in ROI 1.
-\textbf{b.} Mean concentration $\overline{c}$ as function of time in each ROI in a simulation of Dendra2 protein transport with the diffusion coefficient $D_3$.
-\textbf{c.} Time to $\Delta F$ reaches a threshold value of 0.25 in one of the animals of the dataset presented in panel \textbf{a}.
-\textbf{d.} Time to $\overline{c}$ reaches a threshold value of 0.25 for a transport simulation with diffusion coefficient $D_3$.}
-    \label{fig:figure3_compare_exp_and_sim_control}
-\end{figure}
-
-We qualitatively compared fluorescence intensities and mean concentrations with the time $\hat{t}$ to exceed a threshold value of 0.25~(\cref{fig:figure3_compare_exp_and_sim_control}, panels \textbf{c} and \textbf{d}).
-For $\Delta F$, we determined this time-to-threshold for the same downsampled dataset that was used to calculate $\Delta F$.
-In the simulations, we determined the time for $\overline{c}$ to reach the threshold value in each degree of freedom of the concentration finite element function.
-We have excluded the posterior-most regions of the geometries in~\cref{fig:figure3_compare_exp_and_sim_control}, because the values of $\Delta F$ and $c$ never exceeded the threshold value of 0.25 in these regions.
 
 \subsection*{Absence of ciliary motion affects local protein distribution}
-We compare the time evolution of fluorescence intensity in control and \emph{schmalhans}~(\emph{smh}) mutant zebrafish, plotting the means of $\Delta F$ across the cohorts, shaded with one standard deviation regions~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{a}).
-Additionally, we determine the time needed to reach a threshold fluorescent intensity change in each region of interest (ROI) for each fish~(\cref{fig:figure4_compare_control_mutant}, panel \textbf{b}).
-It is important to note that this threshold was set differently for two groups of regions: the $\Delta F$ threshold value was set to 0.25 for ROIs 1--4, whereas for ROIs 5 and 6 the threshold value was 0.10.
-This choice was made because of the slower dynamics of ROIs 5 and 6.
-For each region of interest, the individual data points of the times to threshold are presented together with the distributions and the means of the data points.
-Based on the times to reach a threshold value of $\Delta F$, we test the null hypothesis that the control and mutant photoconversion data are from the same population (or equivalently, have equal distributions).
-We report the $p$-value for this hypothesis calculated using a two-sided Mann-Whitney U test that included a continuity correction, with a confidence level of 95\%.
-
-In ROI 2, there is a statistically significant slower fluorescence intensity increase in the \emph{smh} mutant fish compared to controls~(\cref{fig:figure4_compare_control_mutant}, panel~\textbf{b}).
-Compared to the control dataset, the mean time-to-threshold in ROI 2 is 45\% higher for the mutant dataset.
-In the other ROIs, the differences in the experimental results for controls and mutants are not significantly different.
-We observe that, both within the control and within the mutant dataset, there are considerable individual differences in the times to reach the threshold.
-
-To simulate protein transport in mutant fish, we used flow model II (only cardiac motion as flow mechanism, no cilia) to model the ciliary dysfunction of the \emph{smh} mutants.
-We visualize the time evolution of the mean concentration $\overline{c}$ in each ROI for both model II and the baseline model (model 0), in addition to a similar time-to-threshold $\hat{t}$ as computed for the experimental data~(\cref{fig:figure4_compare_control_mutant}, panel~\textbf{c}).
-As for the experiments, we use a threshold value of $0.25$ in regions 2--4 and a value of $0.10$ for regions 5 and 6 to calculate $\hat{t}$.
-For ROI 2, we observe the same dynamics in simulations as in experiments: there is a slower increase in mean concentration in ROI 2 compared to the baseline model.
-The difference is even greater for the simulations, with the time-to-threshold in ROI 2 for model II 90\% higher than for model 0.
-Additionally, ROIs 4 and 5 exhibit very different $\overline{c}$ profiles for the two different flow models.
-The difference is less significant for ROI 3, and for the posterior ventricle (region 6) the profiles are very similar.
+To assess the impact of cilia motion on solute distribution, we measured the movement of photoconverted Dendra2 signal
+in control and motile-cilia mutant zebrafish (\emph{schmalhans} (\emph{smh})).
+By plotting the means of $\Delta F$ (\Cref{fig:figure4_compare_control_mutant}a) and the time to threshold
+across the control and mutant cohorts (\Cref{fig:figure4_compare_control_mutant}b), we identified a significant
+difference in Dendra2 distribution in ROIs 2 and 4, but not in ROIs 3, 5, and 6. In ROIs 2 and 4,
+which measure Dendra2 distribution downstream of the photoconversion site,
+we observed a slower increase of fluorescence intensity,
+resulting in a $\sim 45\%$ higher mean time-to-threshold in the \emph{smh}
+mutant compared to controls (\Cref{fig:figure4_compare_control_mutant}b).
+
+Next, to identify whether our model would recapitulate these findings,
+we simulated protein transport by using the only-cardiac/no-cilia flow model 
+and compared it with the baseline model (both cilia and cardiac motion) (\Cref{fig:figure4_compare_control_mutant}c).
+Similar to our experiments, we observed slower dynamics in simulations for ROIs 2 and 4.
+Interestingly, the difference was even greater for the simulations,
+with the time-to-threshold in ROI 2 being 90\% higher in absence of cilia-mediated flow.
+Moreover, ROI 5 exhibits very different $\cbar$ profiles for the two configurations in our computational model,
+but not in our experimental data.
+Altogether, our findings identify that diffusion plays an important role for solute movement to regions upstream in the cilia flow fields or to distant ventricles.
 \begin{figure}[H]
@@
     The thick black lines denote mean values of the datasets, and $p$-values were calculated using a Mann-Whitney U test with a confidence level of 95\%.
-    \textbf{c.} Mean concentration $\overline{c}$ as function of time in each ROI, simulated using the baseline model (black lines) and the cardiac-only model (red lines).
+    \textbf{c.} Mean concentration $\cbar$ as function of time in each ROI, simulated using the baseline model (black lines) and the cardiac-only/no-cilia model (red lines).
     The horizontal gray lines mark the threshold value $\hat{c}$, and the time $\hat{t}$ when the threshold is first exceeded is reported in the plot legends.
@@
 
-\subsection*{Loss of cilia can slow down transport}
-Considering removal of cilia in three different regions through modified flow boundary conditions, we simulate CSF flow modeled by the Stokes equations and use the resulting velocity field in transport simulations of Dendra2.
-The maximum velocity observed in the simulations when removing telencephalic, ventral diencephalic and dorsal diencephalic cilia were, respectively, 27.7 $\mu$m/s, 27.2 $\mu$m/s, and 8.0 $\mu$m/s.
-We remind the reader that the maximum velocity observed for the baseline model was 27.7 $\mu$m/s.
-
-Upon removal of telencephalic cilia, the evolution of the mean concentration $\overline{c}$ with time is essentially unaltered~(\cref{fig:figure5_compare_cilia_modifications}, panel \textbf{b}).
-Without ventral cilia in the diencephalic ventricle, $\overline{c}$ increases slightly slower in region of interest (ROI) 3 compared to the baseline model.
-Furthermore, there is a higher mean concentration in the anterior ventricle (ROI 5) and a lower mean concentration in the posterior ventricle (ROI 6) in the absence of ventral cilia when comparing to the baseline model, meaning more solute has spread towards the anterior ventricle and less solute has spread towards the posterior ventricle.
-
-Changes in the transport dynamics are most prominent when removing the dorsal cilia in the diencephalic ventricle.
-For this setup, all ROIs (except ROI 1, for which we impose the concentration dynamics) exhibit significant changes in the dynamics of $\overline{c}$.
-Compared to the baseline model results, there is a slower increase in, and lower final values of, the mean concentration in middle and anterior ventricles (ROIs 2--5).
-In contrast, the transport to the posterior ventricle (ROI 6) is more rapid upon removal of the dorsal diencephalic ventricle cilia.
-It is evident from the final values of $\overline{c}$ that there is less total mass added to the system in the absence of dorsal cilia.
-\lyng{HH:This is due to the lower velocities in the vicinity of ROI 1, resulting in less ability to carry away mass from the volume where the concentration is imposed.
-\emph{Is this correct?}}
+\subsection*{Loss of cilia motility in specific subpopulation slows down transport}
+We previously identified three distinct ciliated cell lineages in the
+zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain}.
+To identify the role of these lineages on CSF transport, we modified flow boundary conditions
+in the three different ciliated regions (\Cref{fig:figure5_compare_cilia_modifications}a) and simulated
+CSF flow using the Stokes equations. We identified that the velocities were most strongly
+affected when removing cilia in the dorsal diencephalic cilia,
+as the maximum velocity dropped from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
+In contrast, removing telencephalic and ventral diencephalic had minimalno to little impact and resulted in maximum velocities of 27.7 $\mu$m/s or 27.2 $\mu$m/s, respectively.
+
+With the resulting velocity fields, we simulated transport of Dendra2.
+Changes in the transport dynamics were most prominent when removing the dorsal cilia
+in the diencephalic ventricle, which produces the strongest flow at this developmental stage.
+All ROIs (except ROI 1, where we locally released solutes) exhibit significant changes
+in the dynamics of $\cbar$ (\Cref{fig:figure5_compare_cilia_modifications}b).
+Compared to the baseline model results, we observed a slower increase and lower final concentration
+in the middle and anterior ventricles (ROIs 2--5),
+and a faster transport to the posterior ventricle (ROI 6).
+In contrast, removal of telencephalic cilia did not alter the evolution of the
+mean concentration $\cbar$ with time (\Cref{fig:figure5_compare_cilia_modifications}b).
+Finally, without ventral cilia in the diencephalic ventricle,
+more solute has spread towards the anterior ventricle (ROI 5) and
+less solute has spread towards the posterior ventricle (ROI 6).
+
 \begin{figure}[H]
@@
 \subsection*{Modification of ventricles geometry impacts protein distribution}
-
-The brain ventricular geometry varies significantly across zebrafish individuals, both healthy and sick animals.
-Motivated by an interest in how these variations can impact solute transport in the brain ventricles, we study the impact on simulation results when modifying the computational geometry and mesh in four different scenarios.
-Because our computational mesh is inflated by the dye-injection performed before image segmentation, we study four different mesh versions where we shrink: the fore-mid brain connection; the middle ventricle; the mid-hind brain connection; and all of the three above simultaneously.
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
-
-We simulate flow and transport in four alternative brain ventricles meshes: one where the connection between the anterior and middle ventricles is constricted; one where the connection between the middle and posterior ventricles is constricted; one where the middle ventricle is shrunk in the lateral direction; the combination of the above three modifications~(\cref{fig:figure6_sim_results_compare_geometries}, panel \textbf{a}).
-We simulate CSF flow in the modified geometries with the baseline flow model and use the resulting velocity field to simulate transport of Dendra2.
-
-Constricting the connection between the anterior and middle ventricle leads to slower transport to region of interest (ROI) 5 located in the anterior ventricle, and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
-On the other hand, constricting the connection between the middle and the posterior ventricle leads to less transport into the posterior ventricle (ROI 6), and slightly more transport towards the anterior ventricle (ROI 5).
-Faster transport to ROI 5 and slower transport to ROI 6 is also the case for the geometry with a shrunk middle ventricle.
-Additionally, for this configuration the transport towards the anterior region of the middle ventricle (ROI 3) is slowed down.
-For the mesh where all three ventricles are modified, we observe higher retention of solute in the middle ventricles (ROIs 2--4).
-Both the anterior and the posterior ventricles (ROIs 5 and 6) have a lower mean concentration, compared to the results for the original geometry.
+We simulate flow and transport in four alternative brain ventricles meshes:
+one where the connection between the anterior and middle ventricles is constricted;
+one where the connection between the middle and posterior ventricles is constricted;
+one where the middle ventricle is shrunk in the lateral direction;
+the combination of the above three modifications~(\Cref{fig:figure6_sim_results_compare_geometries}a).
+We simulate CSF flow in the modified geometries with the baseline flow model and use
+the resulting velocity field to simulate transport of Dendra2.
+
+Constricting the connection between the anterior and middle ventricle leads to
+slower transport to region of interest (ROI) 5 located in the anterior ventricle,
+and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
+On the other hand, constricting the connection between the middle and the posterior ventricle
+leads to less transport into the posterior ventricle (ROI 6),
+and slightly more transport towards the anterior ventricle (ROI 5).
+Faster transport to ROI 5 and slower transport to ROI 6 is also
+the case for the geometry with a shrunk middle ventricle.
+Additionally, for this configuration the transport towards the anterior region of
+the middle ventricle (ROI 3) is slowed down.
+For the mesh where all three ventricles are modified,
+we observe higher retention of solute in the middle ventricles (ROIs 2--4).
+Both the anterior and the posterior ventricles (ROIs 5 and 6) have a lower mean concentration,
+compared to the results for the original geometry.
 
@@
     \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
-    \caption{Caption. \mk{MK: How do the different geometries compare in terms of volume, areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
+    \caption{Caption. \mk{MK: How do the different geoemtries compare in terms of volume, areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
     \label{fig:figure6_sim_results_compare_geometries}
 \end{figure}
-
-\cleardoublepage
 
@@
 \subsection*{The roles of diffusion and advection in transport of photoconverted proteins}
-We quantified transport in terms of fluorescence intensity change $\Delta F$ (experiments) and mean concentration $\overline{c}$ (simulations) as functions of time.
+We quantified transport in terms of fluorescence intensity change $\Delta F$ (experiments) and mean concentration $\cbar$ (simulations) as functions of time.
 For both measures, we observed that transport dynamics in the middle ventricle where Dendra2 fluorescent protein was photoconverted contrasted with the dynamics of the more distal regions of the anterior and posterior ventricles.
@@
 In regions proximal to photoconversion, advection and diffusion occur simultaneously due to the presence of cilia, leading to concave profiles for $\Delta F$.
-The convex diffusion-only behavior was observed in the mean concentration $\overline{c}_6$ profile of the posterior ventricle in the simulations, but $\overline{c}_5$ was concave for the anterior ventricle, opposed to the experimental results \lyng{HH: \emph{Is this the correct interpretation of convex vs.
+The convex diffusion-only behavior was observed in the mean concentration $\cbar_6$ profile of the posterior ventricle in the simulations, but $\cbar_5$ was concave for the anterior ventricle, opposed to the experimental results \lyng{HH: \emph{Is this the correct interpretation of convex vs.
 concave curves?} Include some referencing to textbook solutions of the diffusion and advection equations to explain this convex vs.
@@
 Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen on a timescale of the order of $t_a=L/\overline{U}=141$ s.
-Comparing this with the minuscule values of $\overline{c}_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection played a role in transporting solute from the photoconversion site in the middle ventricle to the posterior ventricle, values of $\overline{c}_6$ would be higher than those observed.
+Comparing this with the minuscule values of $\cbar_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection played a role in transporting solute from the photoconversion site in the middle ventricle to the posterior ventricle, values of $\cbar_6$ would be higher than those observed.
 
@@
 This is probably a result of less solute diffusing away from ROI 1 for $D_2$ than for $D_3$, meaning that more solute can be transported by advection along the ciliated walls of the ventricles towards ROI 2.
-We also note that, for regions of interest 3 and 4, the order of the $\Delta F$ and $\overline{c}$ profiles are opposite.
+We also note that, for regions of interest 3 and 4, the order of the $\Delta F$ and $\cbar$ profiles are opposite.
 This could be related to the difference in the exact location of ROIs 3 and 4 in simulations and experiments, or due to cilia-advection being more prominent in the simulations (cf.
@@
 Modifying the ventricular geometry had varying impact on transport~(\cref{fig:figure6_sim_results_compare_geometries}).
-Both when (separately) shrinking the connection between the fore- and mid-brain and the mid- and hind-brain, we observe a slight increase in the mean concentration $\overline{c}$ of regions of interests 2--4.
-In regions 5 and 6, we observe a decrease in $\overline{c}$ in the region that we shrink the connection from the middle ventricle to.
-Meanwhile, the other region has an increase in $\overline{c}$, a result of mass conservation.
+Both when (separately) shrinking the connection between the fore- and mid-brain and the mid- and hind-brain, we observe a slight increase in the mean concentration $\cbar$ of regions of interests 2--4.
+In regions 5 and 6, we observe a decrease in $\cbar$ in the region that we shrink the connection from the middle ventricle to.
+Meanwhile, the other region has an increase in $\cbar$, a result of mass conservation.
 When shrinking the middle ventricle, the mean concentration decreases in regions 2--4.
-The effect on $\overline{c}$ in regions 5 and 6 is similar to when the mid-hind connection is shrunk: less solute is transported towards the hind-brain and more solute is transported towards the fore-brain.
-
-Combining all three geometry modifications, we see an increase in $\overline{c}$ in regions 2--4.
-Now, there is a decrease in both region 5 and 6, which is more similar to the experimental $\Delta F$ curves (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}) in these regions compared to the simulated $\overline{c}$ on the standard geometry (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
+The effect on $\cbar$ in regions 5 and 6 is similar to when the mid-hind connection is shrunk: less solute is transported towards the hind-brain and more solute is transported towards the fore-brain.
+
+Combining all three geometry modifications, we see an increase in $\cbar$ in regions 2--4.
+Now, there is a decrease in both region 5 and 6, which is more similar to the experimental $\Delta F$ curves (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}) in these regions compared to the simulated $\cbar$ on the standard geometry (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
 This is in line with the expectation that shrinking the geometry is closer to replicating the geometries of the fish used in experiments, because the ventricular geometry is inflated by the injection procedure performed during image segmentation.

### 2025-02-03 paper/main.tex
Results 6

@@
 \subsection*{Modification of ventricles geometry impacts protein distribution}
-We simulate flow and transport in four alternative brain ventricles meshes:
+To assess the impact of ventricular morphologies on solute distribution,
+we used four alternative brain ventricles meshes:
 one where the connection between the anterior and middle ventricles is constricted;
@@
 one where the middle ventricle is shrunk in the lateral direction;
-the combination of the above three modifications~(\Cref{fig:figure6_sim_results_compare_geometries}a).
-We simulate CSF flow in the modified geometries with the baseline flow model and use
-the resulting velocity field to simulate transport of Dendra2.
+and the combination of the above three modifications (\Cref{fig:figure6_sim_results_compare_geometries}a).
+We simulate CSF flow in the modified geometries with the baseline flow model
+and use the resulting velocity field to simulate transport of Dendra2 (\Cref{fig:figure6_sim_results_compare_geometries}b).
 
 Constricting the connection between the anterior and middle ventricle leads to
-slower transport to region of interest (ROI) 5 located in the anterior ventricle,
+slower transport to the anterior ventricle (ROI 5),
 and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
@@
 and slightly more transport towards the anterior ventricle (ROI 5).
-Faster transport to ROI 5 and slower transport to ROI 6 is also
-the case for the geometry with a shrunk middle ventricle.
-Additionally, for this configuration the transport towards the anterior region of
-the middle ventricle (ROI 3) is slowed down.
+Faster transport to the anterior ventricle (ROI 5) and slower transport to the
+posterior ventricle (ROI 6) is also the case for the geometry with a shrunk middle ventricle.
+Additionally, for this configuration the transport upstream the flow fields towards the
+ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
 For the mesh where all three ventricles are modified,
-we observe higher retention of solute in the middle ventricles (ROIs 2--4).
-Both the anterior and the posterior ventricles (ROIs 5 and 6) have a lower mean concentration,
-compared to the results for the original geometry.
+we observe higher retention of solute in the middle ventricle (ROIs 2--4),
+while both the anterior and the posterior ventricles (ROIs 5 and 6) have lower concentration.
+Altogether our results identify that the geometry and width of the ventricular ducts matter
+for solute transport and may explain why we observed larger differences
+in the cilia-deficient model than in the experimental data in
+\Cref{fig:figure4_compare_control_mutant}, which have different duct diameters.
 
@@
 We have presented a computational model of cerebrospinal fluid (CSF) flow in brain ventricles of 2 days post-fertilization (2dpf) zebrafish embryo.
-By imposing tangential stresses and normal traction on the CSF flow, the simulated flow fields had similar features to the flow fields observed experimentally, consisting of vortex-structured flow and pulsatile flow.
+By imposing tangential traction and normal pressure on the CSF flow, the simulated flow fields had similar features to the flow fields observed experimentally, consisting of vortex-structured flow and pulsatile flow.
 The CSF flow was used to model transport of a solute by an advection-diffusion equation.

### 2025-02-03 paper/main.tex
Discussion 1-3, some Appendix updates

@@
 \section*{Discussion}
-We have presented a computational model of cerebrospinal fluid (CSF) flow in brain ventricles of 2 days post-fertilization (2dpf) zebrafish embryo.
-By imposing tangential traction and normal pressure on the CSF flow, the simulated flow fields had similar features to the flow fields observed experimentally, consisting of vortex-structured flow and pulsatile flow.
-The CSF flow was used to model transport of a solute by an advection-diffusion equation.
-Qualitatively, simulations compared well to experiments of Dendra2 fluorescent protein photoconversion.
-Transport in cilia-mutant fish (\emph{schmalhans} mutants) and a CSF model without cilia, was compared to control experiments and the baseline CSF model, indicating a local effect of cilia motion on protein transport.
-Using the computational model of flow and transport, we further studied region-specific removal of cilia and ventricles geometry modification, and how these changes affected transport.
-
-\subsection*{The roles of diffusion and advection in transport of photoconverted proteins}
-We quantified transport in terms of fluorescence intensity change $\Delta F$ (experiments) and mean concentration $\cbar$ (simulations) as functions of time.
-For both measures, we observed that transport dynamics in the middle ventricle where Dendra2 fluorescent protein was photoconverted contrasted with the dynamics of the more distal regions of the anterior and posterior ventricles.
-In experiments, regions distal to the photoconversion site showed an approximately linear increase in $\Delta F$, probably because advection is absent in the transport to the distal regions, such that diffusion is the sole mode of transport.
-In regions proximal to photoconversion, advection and diffusion occur simultaneously due to the presence of cilia, leading to concave profiles for $\Delta F$.
-The convex diffusion-only behavior was observed in the mean concentration $\cbar_6$ profile of the posterior ventricle in the simulations, but $\cbar_5$ was concave for the anterior ventricle, opposed to the experimental results \lyng{HH: \emph{Is this the correct interpretation of convex vs.
-concave curves?} Include some referencing to textbook solutions of the diffusion and advection equations to explain this convex vs.
-concave?
-E.g.
-semi-infinite slab or boundary layer solutions to inflow/outflow problem.}.
-Based on the geometry modification study, the reason for this difference in behavior might be that the duct between the anterior and middle ventricle is inflated in our computational mesh, as a result of the dye-injection performed before imaging~\lyng{Cite this?}.
-This inflation allows for effective cilia-mediated advection from the middle ventricle to the anterior ventricle.
-
-In general, the mean concentration dynamics of the simulations was more rapid than the fluorescence intensity dynamics of the photoconversion experiments.
-This is strongly related to our definition of the photoconversion site (region of interest 1) in the simulations, and whether this corresponds well to the region used in experiments, because the volume of the photoconversion region used in the simulations determines the total amount of solute, and thus impacts the rate of transport.
-The alignment of the computational and experimental region of interest definition is hard to quantify.
-Additionally, a source of discrepancy in the results is the fact that the brain ventricles might be permeable, such that some Dendra2 diffuses out of the brain ventricles in the experiments.
-An assay has shown that the neuroepithelium lining the walls of brain ventricles in embryonic zebrafish 24 hours post-fertilization is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
-Dendra2 are almost 26 kDa in size~\cite{Gurskaya2006EngineeringLight}, and are thus under this reported limit.
-If such permeability also is the case for 2 days post-fertilization zebrafish embryo ventricles, this would lead to Dendra2 leaking out of the brain ventricles in the experiments, making the dynamics appear slower.
-
-Transport of Dendra2 fluorescent protein appears to be a balance of advection and diffusion.
-Advection is the strongest transport mechanism on a global scale (global Péclet number 7.4), but for shorter distances diffusion is balancing out advection.
-Simulating transport of larger molecules (thus with smaller diffusion coefficients) proved advection to be increasingly important as molecule size increased.
-For the smallest diffusion coefficient used, $D_1$, which represented 200 nm exosomes, there was essentially zero solute in the posterior ventricle at the final simulation time (around 850 s).
-This is consistent with the statement above that transport to the posterior ventricle from the middle ventricle is driven by diffusion, based on estimated transport times of diffusion and advection: For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance $L=200$ $\mu$m from the middle to the posterior ventricle is approximately 24500 s.
-Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen on a timescale of the order of $t_a=L/\overline{U}=141$ s.
-Comparing this with the minuscule values of $\cbar_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection played a role in transporting solute from the photoconversion site in the middle ventricle to the posterior ventricle, values of $\cbar_6$ would be higher than those observed.
-
-The changes in the times to threshold when changing the diffusion coefficient are greatest for regions of interest (ROIs) 4--6, further indicating that, relative to advection, diffusion has a greater impact in these regions than compared to regions 1--3.
-In region of interest 2 (anterior, dorsal region of the middle ventricle), the time to threshold is lower for $D_2$ than $D_3$.
-This is probably a result of less solute diffusing away from ROI 1 for $D_2$ than for $D_3$, meaning that more solute can be transported by advection along the ciliated walls of the ventricles towards ROI 2.
-We also note that, for regions of interest 3 and 4, the order of the $\Delta F$ and $\cbar$ profiles are opposite.
-This could be related to the difference in the exact location of ROIs 3 and 4 in simulations and experiments, or due to cilia-advection being more prominent in the simulations (cf.
-the discussion on differences in transport to the anterior ventricle).
-
-\subsection*{Simulation studies: modifying cilia and geometry}
-We studied the impacts of removing cilia in specific regions of our model~(\cref{fig:figure5_compare_cilia_modifications}).
-Removing the dorsal cilia has a strong impact on the resulting CSF flow field and the mean solute concentration.
-Removing the dorsal cilia decreased the maximum velocity in the ventricles roughly by a factor of three from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
-The impactful changes to the flow field is because the total force applied on the dorsal cilia boundary is great in magnitude in our model, and the dorsal cilia are thus important to establishing the CSF flow structures.
-With weaker flow in the dorsal region of the middle ventricle, there is less advective transport.
-\lyng{HH: Quantify the difference in force applied in the dorsal region: $\int_{c, dorsal}\btau\cdot\mathbf{t}\,\mathrm ds$.}
-
-Absence of ventral cilia in the middle ventricle did not greatly impact flow dynamics and transport, but lead to slightly less transport towards the posterior ventricle, and slightly more transport towards the anterior ventricle.
-This is because the ventral cilia help induce flow towards the posterior ventricles.
-Removing the cilia in the anterior ventricle leaves the transport results virtually unaltered, although the CSF flow vortex structure in the anterior ventricle vanishes.
-This would then probably have a greater impact for smaller diffusion coefficients, as it is evident in~\cref{fig:fig2} that transport with $D_1$ is mainly advective.
+We have presented a computational model of CSF flow and solute transport within the brain ventricles.
+In this study, we used the larval zebrafish brain ventricles since its geometry,
+flow components and kinetics are well described, thereby allowing us to validate
+our simulation experimentally. Nevertheless, our simulations can be implemented in
+other systems in the future when their flow parameters are comprehensively resolved.  
+By imposing tangential traction and normal pressure on the CSF flow, we achieved to reproduce
+flow fields with similar features as observed experimentally, consisting of vortex-structured flow,
+mediated by cilia, and pulsatile flow, mediated by the cardiac cycle.
+
+Using the simulated CSF flow, we modeled solute transport by an advection-diffusion equation.
+These results compared well with experimental data performed \emph{in vivo} in zebrafish.
+Next, by using both a model and zebrafish mutants with paralyzed cilia,
+we identified that even though advection by cilia is dominant,
+diffusion plays a significant role  in protein transport. Finally, we report how local
+flow patterns and ventricular geometries affect solute distribution.
+Altogether our results provide not only new findings on the role of
+diffusion and advection but also offer a new framework to study CSF transport in complex geometries.
+
+\subsection*{The roles of advection and diffusion in intraventricular solute transport}
+To determine the roles of advection and diffusion in solute transport, we quantified transport
+based on changes in fluorescence intensity $\Delta F$ (experiments) and
+mean concentration $\cbar$ (simulations) as functions of time.
+Even though we identified very similar dynamics in simulations and
+\emph{in vivo} experiments, the dynamics of the simulations were generally
+more rapid and resulted in higher total amounts.
+Differences between experiments and simulations may relate to
+ventricular size, as we showed that modifying the duct volumes impacts
+solute distribution and the geometry used for the model was larger than in experiments.
+Alternatively, it may relate to the way we defined the photoconversion site (region of interest 1)
+in the simulations, since the volume of the photoconversion region determines
+the total amount of solute, and thereby the rate of transport. Another source
+of discrepancy may relate to the permeability of the ventricular wall,
+which we have ignored in our simulation. Reports have shown that the
+neuroepithelium lining the walls of brain ventricles in 24h old zebrafish
+is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
+Since Dendra2 is around 26 kDa in size~\cite{Gurskaya2006EngineeringLight},
+and thus under this reported limit, one could assume that if Dendra2
+leaks out of the brain ventricles, the dynamics become slower.
+
+In general, the mean concentration dynamics of the simulations was 
+more rapid than the fluorescence intensity dynamics of the photoconversion experiments.
+This is strongly related to our definition of the photoconversion site
+(ROI 1) in the simulations, and whether this corresponds well to the
+region used in experiments, because the volume of the photoconversion
+region used in the simulations determines the total amount of solute,
+and thus impacts the rate of transport. The alignment of the computational
+and experimental region of interest definition is hard to quantify.
+Additionally, a source of discrepancy in the results is the fact that the
+brain ventricles might be permeable, such that some Dendra2 diffuses out
+of the brain ventricles in the experiments. An assay has shown that the neuroepithelium
+lining the walls of brain ventricles in embryonic zebrafish 24 hours post-fertilization
+is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
+Dendra2 are almost 26 kDa in size~\cite{Gurskaya2006EngineeringLight},
+and are thus under this reported limit. If such permeability also is the case for 2 days
+post-fertilization zebrafish embryo ventricles, this would lead to Dendra2 leaking
+out of the brain ventricles in the experiments, making the dynamics appear slower.
+
+Nevertheless, our results convincingly show that intraventricular transport of proteins
+depends on a balance of advection and diffusion. While advection is the strongest transport
+mechanism on a global scale for Dendra2 (global Péclet number 7.4), diffusion is balancing out
+advection especially for shorter distances and for regions devoid of motile cilia activity.
+Indeed, we identified that the diffusion coefficient had a greater impact on transport to
+regions located upstream in the CSF flow field (ROI 4\lyng{ actually 3?}) or in different ventricles (ROIs 5--6),
+than the regions located downstream of cilia-mediated flow (ROI 2).
+
+In contrast, we identified that transport of larger molecules
+(thus with smaller diffusion coefficients),
+such as 200 nm exosomes, are almost entirely dependent on advection.
+Indeed, there was essentially zero solute in the posterior ventricle at the
+final simulation time (around 850 s), where transport is largely driven by diffusion.
+For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance
+$L=200$ $\mu$m from the middle to the posterior ventricle is approximately 24500 s.
+Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen
+on a timescale of the order of $t_a=L/\overline{U}=141$ s. Comparing this with the minuscule values of
+$\cbar_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection
+played a role in transporting solute from the photoconversion site in the middle ventricle
+to the posterior ventricle, values of $\cbar_6$ would be higher than those observed.
+
+\subsection*{Impact of cilia properties and ventricular geometry}
+To gain further insights into how CSF distribution depends on cilia properties and geometries,
+we manipulated certain parameters in our models. First, we removed cilia in specific regions of
+our model (\Cref{fig:figure5_compare_cilia_modifications}). We identified that the cilia in the
+dorsal middle ventricle contribute the most to solute distribution, which aligns well with the fact
+that these cilia generate the strongest flow field \emph{in vivo} and in our model.
+In contrast, removing the ventral cilia in the middle ventricle did not greatly impact flow dynamics.
+However, it lead to reduced transport towards the posterior ventricle,
+and increased transport towards the anterior ventricle, as the ventral cilia help induce
+flow towards the posterior ventricles. Removing the cilia in the anterior ventricle did not affect the transport.
+
+Next, we modified the ventricular geometry and identified varying impact on transport.
+Notably, shrinking ducts reduced movement between the ventricles, while shrinking the middle ventricle
+reduced diffusive transport upstream of the flow field (ROI 4).
+We previously identified large inter-individual variation in ventricular size and
+CSF velocities between larva at given developmental stages and throughout development~\fixme{Add some citation here? Olstad/D'Gama}.
+Our results suggest that these two parameters may well co-vary and explain the variation.
+
+Altogether, our model is flexible and thereby allows \emph{in silico} testing of
+further hypotheses on the contribution of ciliated lineages and geometries.
+We trust that it will be useful as a basis for future analysis of CSF dynamics in more complex geometries.
 
@@
 
-Modifying the ventricular geometry had varying impact on transport~(\cref{fig:figure6_sim_results_compare_geometries}).
-Both when (separately) shrinking the connection between the fore- and mid-brain and the mid- and hind-brain, we observe a slight increase in the mean concentration $\cbar$ of regions of interests 2--4.
-In regions 5 and 6, we observe a decrease in $\cbar$ in the region that we shrink the connection from the middle ventricle to.
-Meanwhile, the other region has an increase in $\cbar$, a result of mass conservation.
-When shrinking the middle ventricle, the mean concentration decreases in regions 2--4.
-The effect on $\cbar$ in regions 5 and 6 is similar to when the mid-hind connection is shrunk: less solute is transported towards the hind-brain and more solute is transported towards the fore-brain.
-
-Combining all three geometry modifications, we see an increase in $\cbar$ in regions 2--4.
-Now, there is a decrease in both region 5 and 6, which is more similar to the experimental $\Delta F$ curves (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{a}) in these regions compared to the simulated $\cbar$ on the standard geometry (\cref{fig:figure3_compare_exp_and_sim_control}, panel \textbf{b}).
-This is in line with the expectation that shrinking the geometry is closer to replicating the geometries of the fish used in experiments, because the ventricular geometry is inflated by the injection procedure performed during image segmentation.
-
 \subsection*{Computational model assumptions and boundary conditions}
-To model flow of cerebrospinal fluid, we employed slip boundary conditions at the ventricular walls, contrasting the classical choice of a noslip boundary condition.
-The use of slip boundary conditions is motivated by experimental observations of the flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
-It has been observed that the fluid velocity increases towards the wall~(this is also evident in~\cref{fig:figure1}, panel~\textbf{c}).
+To model CSF, we employed slip boundary conditions at the ventricular walls,
+contrasting the classical choice of a noslip boundary condition.
+The use of slip boundary conditions is motivated by experimental observations of the
+flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
+It has been observed, both previously and in this work, that the fluid velocity increases towards the wall~(\Cref{fig:figure1}c).
 Using slip boundary conditions allows for this behavior.
-A couple of previous continuum model simulation studies of cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal} have modeled cilia as body forces.
-We chose to model the cilia as a force exerted tangentially on the boundary.
-First, we deem this a good representation of the real nature of cilia, since they are in reality microscale structures confined to the ventricular walls that generate flow through collective motion.
-Second, it avoids the need of excessive mesh refinement near the ciliated boundaries in the case that a body force were to be applied in a $\sim$ 5 $\mu$m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.
-
-In our CSF flow model, the ciliated boundaries are homogeneous, whereas in reality, cilia populate the ventricle walls in a heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}.
-Heterogeneous spatial arrangement of cilia, both in location and beating direction, has been shown to enhance particle clearance in airway cilia arrays in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
-Incorporating spatial arrangement heterogeneity in our model could possibly result in different transport timescales, but we would not expect notable changes to the general trends of the macroscopic transport that we study here, since the effects of introducing heterogeneous spacing of cilia would alter the magnitude of cilia forces, but not their direction.
-On the other hand, introducing more heterogeneous beating directionality could alter the transport timescales as well as the directionality.
-In our model, all of the applied cilia tangential traction is aligned with the rostrocaudal axis, and more heterogeneity in this alignment to reflect heterogeneity in the beating directionality of cilia would presumably affect both magnitude and directionality of advective transport.
-Previous studies have demonstrated that changes to beating directionality affects transport, and that specific coordination of the ciliary beating is important in the brain ventricles for flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004Cilia-relatedDiseases}, but also in other phenomena such as maintaining healthy functioning of mucous transport in airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction, Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet} and in nodal flow which establishes left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry, Sawamoto2006NewBrain}.
-Although these studies were mostly on spatial scales resolving individual cilia, we could envision the same effects in our continuum model, similar to the results of previous numerical studies~\cite{Ramirez-SanJuan2020Multi-scaleArrays, Thouvenin2020OriginCanal, Yoshida2022EffectVentricles}.
+A couple of previous continuum model simulation studies of cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
+have modeled cilia as body forces. We chose to model the cilia as a force exerted tangentially on the boundary.
+First, we deem this a good representation of the real nature of cilia,
+since they are in reality microscale structures confined to the ventricular walls that
+generate flow through collective motion. Second, it avoids the need of excessive mesh
+refinement near the ciliated boundaries in the case that a
+body force were to be applied in a $\sim$ 5 $\mu$m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.
+
+In our CSF flow model, the ciliated boundaries are homogeneous,
+whereas in reality, cilia populate the ventricle walls in a
+heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneous spatial
+arrangement of cilia, both in location and beating direction,
+has been shown to enhance particle clearance in airway cilia arrays
+in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}. Incorporating spatial arrangement heterogeneity
+in our model could possibly result in different transport timescales,
+but we would not expect notable changes to the general trends of the macroscopic
+transport that we study here, since the effects of introducing heterogeneous spacing
+of cilia would alter the magnitude of cilia forces, but not their direction.
+On the other hand, introducing more heterogeneous beating directionality could
+alter the transport timescales as well as the directionality. In our model, all of the applied cilia
+tangential traction is aligned with the rostrocaudal axis, and more heterogeneity
+in this alignment to reflect heterogeneity in the beating directionality of
+cilia would presumably affect both magnitude and directionality of advective transport.
+Previous studies have demonstrated that changes to beating directionality affects transport,
+and that specific coordination of the ciliary beating is important in the brain ventricles for
+flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
+Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004Cilia-relatedDiseases},
+but also in other phenomena such as maintaining healthy functioning of mucous transport in
+airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction,
+Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet} and in nodal flow which establishes
+left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry,
+Sawamoto2006NewBrain}. Although these studies were mostly on spatial scales resolving individual cilia,
+we could envision the same effects in our continuum model,
+similar to the results of previous numerical studies~\cite{Ramirez-SanJuan2020Multi-scaleArrays,
+Thouvenin2020OriginCanal, Yoshida2022EffectVentricles}.
 
 We used an advection-diffusion equation to simulate protein transport in the brain ventricles.
-Except for where we imposed a normal pressure boundary condition on the CSF flow, we imposed a no-flux condition on the concentration.
-Imposing a pressure-driven cardiac-related flow on certain parts of the CSF flow boundary leads to in- and outflow, and the advective transport then requires handling of in- and outflux boundary conditions.
-Reflecting our assumption that the ventricular system is closed, we set boundary conditions such that the total mass is conserved in the limit that the timestep size is zero.
-We handle the outflux by leaving the advective flux term as an unknown in the weak formulation of the advection-diffusion equation.
-This has been referred to with different names in previous works, names such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition}, the ``no boundary condition"~\cite{Griffiths1997TheCondition}, and the ``consistent flux boundary condition"~\cite{Lynch2020NumericalHemodynamics}.
-In leaving the advective flux term in the weak form we are lacking a boundary condition, so the approach seems problematic in the continuous sense of the problem.
-However, the discrete problem is well-posed, because the approach represents constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}.
-
-On the inflow boundary, we applied an approximate periodic boundary condition by setting the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous timestep $n-1$.
-This is expected to be of low-order accuracy, and for high Péclet numbers, the boundary condition affects the concentration field in the vicinity of the in- and outflow boundaries due to large advective fluxes.
-For the simulation scenarios we considered, both in terms of model parameters and time span, the photoconversion region where solute originates is far enough away from the in- and outflow boundaries for the flux boundary condition to not significantly impact the results.
-Nevertheless, we deliberately excluded the space proximal to in- and outflow boundaries in the anterior and posterior regions of interest (5 and 6) to limit adverse effects.
-
-A possible improvement to the in- and outflow boundary conditions we employed would be to consider a 3D-0D coupling of the in- and outflow boundaries using ordinary differential equations, similar to what has been done in cardiac modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
-However, if the ventricular system in reality is a closed system, one should rather seek out a way of modeling the CSF flow without open boundaries to avoid handling in- and outflow boundary conditions.
-A more appropriate way of handling the beating cardiac motion could be to impose a ventricular wall deformation, assumed to result from pulsatile motion of the heart and/or cardiac vessels surrounding the ventricles.
-This wall deformation would induce CSF flow while simultaneously permitting enforcement of the impermeability condition $\uu\cdot\nn=0$ on the ventricular walls.
-Such wall-motion induced CSF flow has been modeled and simulated successfully in the human brain ventricular system~\cite{Causemann2022HumanFramework, Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
+Except for where we imposed a normal pressure boundary condition on the CSF flow,
+we imposed a no-flux condition on the concentration. Imposing a pressure-driven
+cardiac-related flow on certain parts of the CSF flow boundary leads to in- and outflow,
+and the advective transport then requires handling of in- and outflux boundary conditions.
+Reflecting our assumption that the ventricular system is closed, we set boundary conditions such
+that the total mass is conserved in the limit that the timestep size is zero.
+We handle the outflux by leaving the advective flux term as an unknown in the weak formulation
+of the advection-diffusion equation. This has been referred to with different names in previous works,
+names such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition},
+the ``no boundary condition"~\cite{Griffiths1997TheCondition}, and the 
+``consistent flux boundary condition"~\cite{Lynch2020NumericalHemodynamics}. 
+In leaving the advective flux term in the weak form we are lacking a boundary condition,
+so the approach seems problematic in the continuous sense of the problem.
+However, the discrete problem is well-posed, because the approach represents
+constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}.
+
+On the inflow boundary, we applied an approximate periodic boundary condition by setting
+the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous
+timestep $n-1$. This is expected to be of low-order accuracy, and for high Péclet numbers,
+the boundary condition affects the concentration field in the vicinity of the in- and outflow boundaries
+due to large advective fluxes. For the simulation scenarios we considered, both in terms of model parameters
+and time span, the photoconversion region where solute originates is far enough away from the in- and outflow
+boundaries for the flux boundary condition to not significantly impact the results. Nevertheless,
+we deliberately excluded the space proximal to in- and outflow boundaries in
+the anterior and posterior regions of interest (5 and 6) to limit adverse effects.
+
+A possible improvement to the in- and outflow boundary conditions we employed would be
+to consider a 3D-0D coupling of the in- and outflow boundaries using ordinary differential equations,
+similar to what has been done in cardiac modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
+However, if the ventricular system in reality is a closed system,
+one should rather seek out a way of modeling the CSF flow without open boundaries to avoid
+handling in- and outflow boundary conditions. A more appropriate way of handling the beating
+cardiac motion could be to impose a ventricular wall deformation, assumed to result from pulsatile
+motion of the heart and/or cardiac vessels surrounding the ventricles. This wall deformation would
+induce CSF flow while simultaneously permitting enforcement of the impermeability condition
+$\uu\cdot\nn=0$ on the ventricular walls. Such wall-motion induced CSF flow has been modeled and
+simulated successfully in the human brain ventricular system~\cite{Causemann2022HumanFramework,
+Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
 
@@
 \section{Supplementary Theory}
-\subsection{Weak Formulation of the Stokes Equations}\label{subsec:appendixA1}
+\subsection{Weak formulation of the Stokes equations}\label{subsec:appendixA1}
 We consider the time-dependent Stokes equations
@@
 $\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The value of the amplitude $A$ was based on heuristics and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.
-
-\iffalse
-\textbf{Model Version IIb.} A second approach to modeling the pulsatile flow generated by the cardiac cycle was applying a rigid motion to the geometry, and then solving for the velocity defined in the reference frame attached to the geometry.
-We consider an approach similar to San Mart{\'\i}n \emph{et al.}~\cite{san2009convergence}, based on the framework commonly referred to as an Arbitrary Lagrangian Eulerian formulation of the governing equations.
-Consider the Stokes equations
-\begin{subequations}
-    \begin{alignat}{2}
-        \rho\pdifft{\uu} - \nabla\cdot\bm{\sigma}(\uu, p) &= \mathbf{0}, \\
-        \nabla\cdot\uu &= 0,
-    \end{alignat}
-    \label{eq:stokes_eqs_moving_ref}%
-\end{subequations}%
-in a time-dependent, moving domain $\Omega_t$, and define the coordinates $\hat{\xx} = (\hat{x}, \hat{y}, \hat{z})$ as the reference frame attached to $\Omega_t$.
-In $\Omega_t$, we consider the variables $\psi(\hat{\xx}, t)$, so that we have $\uu(\hat{\xx}, t)$ and $p(\hat{\xx}, t)$ in~\eqref{eq:stokes_eqs_moving_ref}.
-As before, we denote $\Omega$ the domain in the absolute, fixed reference frame with coordinates $\xx = (x, y, z)$ and variables $\psi(\xx, t)$.
-To determine the velocity inside the brain ventricles without moving the computational mesh, we can solve the Stokes equations for the velocity $\ww$ defined in the moving reference frame.
-This is done by first solving for $\uu$ in the fixed reference frame, whilst accounting for the mesh motion $\uuref$.
-Then, with $\uu$ and $\ww$ defined in separate coordinate systems that move with a velocity $\uuref$ relative to each other, the velocities are related by $\uu = \ww + \uuref$~\cite{meriam2012engineering}.
-After solving for $\uu$, we thus calculate $\ww = \uu - \uuref$.
-To rewrite the variables in~\eqref{eq:stokes_eqs_moving_ref} into variables of $\xx$ instead of $\hat{\xx}$, nothing has to be done with the divergence operators since we consider a rigid motion, rendering spatial differentiation unchanged.
-The temporal derivative is not the same in the two coordinate systems, however.
-Differentiation with respect to time and application of the chain rule yields
-\begin{equation*}
-    \begin{aligned}
-        \pdifft{\psi}(\hat{\xx}, t) &= \pdifft{\psi}(\xx, t) + \frac{\partial \psi}{\partial\hat{\xx}}\pdifft{\hat{\xx}} \\
-        &= \pdifft{\psi}(\xx, t) + \frac{\partial \psi}{\partial\xx}\frac{\partial\xx}{\partial\hat{\xx}}\pdifft{\hat{\xx}} \\
-        &= \pdifft{\psi}(\xx, t) + \frac{\partial \psi}{\partial\xx}\pdifft{\hat{\xx}}.
-    \end{aligned}
-\end{equation*}
-The last equality follows from the fact that the motion of the moving reference frame is rigid, such that the differences in $\hat{\xx}$ and $\xx$ are only due to translation, and not dilatation, of the coordinate systems.
-We can recognize $\partial\hat{\xx}/\partial t = \uu_{\mathrm{ref}}$ as the velocity of the domain $\Omega_t$.
-Since $\partial\psi/\partial\xx = \nabla\psi$, we get
-\begin{equation}
-    \pdifft{\psi}(\hat{\xx}, t) = \pdifft{\psi}(\xx, t) + \uu_{\mathrm{ref}}\cdot\nabla\psi,
-    \label{eq:temporal_derivative_relation}
-\end{equation}
-where the second term leads to the interpretation that the variable $\psi(\xx, t)$ in the fixed reference frame is advected with the velocity $\uu_{\mathrm{ref}}$ of the moving reference frame.
-Using the relation~\eqref{eq:temporal_derivative_relation}, we can rewrite~\eqref{eq:stokes_eqs_moving_ref} in the fixed reference frame:
-\begin{subequations}
-    \begin{alignat}{2}
-        \rho\bigg(\pdifft{\uu} + (\uu_{\mathrm{ref}}\cdot\nabla)\uu\bigg) &= \nabla\cdot\bm{\sigma}(\uu, p), \label{eq:mom_eq_fixed}\\
-        \nabla\cdot\uu &= 0,
-    \end{alignat}
-    \label{eq:stokes_eqs_fixed}%
-\end{subequations}%
-where the variables in~\eqref{eq:stokes_eqs_fixed} are variables of $\xx$ and $t$.
-The boundary conditions also change slightly for this formulation.
-Since the impermeability condition $\ww\cdot\nn=0$ is now supposed to hold in the moving reference frame, we get the boundary condition $\uu\cdot\nn = \uuref\cdot\nn$.
-To simulate the oscillatory motion arising from the cardiac cycle, we applied the motion $\uuref = (A_{\mathrm{ref}}\sin{\omega t}, 0, 0)$, where the amplitude $A_{\mathrm{ref}}$ was calibrated with experimental data and $\omega = 2\pi f$ was determined by the cardiac frequency $f$~\cite{Olstad2019CiliaryDevelopment}.
-Since the domain movement is rigid, we have $\beps(\uuref) = \mathbf{0}$, such that the stress boundary condition $P_{\nn}(\bsig(\ww, p)) = \mathbf{0}$ directly translates to $P_{\nn}(\bsig(\uu, p)) = \mathbf{0}$.
-Solving~\eqref{eq:stokes_eqs_fixed} with the boundary conditions $\uu\cdot\nn = \uuref\cdot\nn$ and $P_{\nn}(\bsig(\uu, p)) = \mathbf{0}$, we obtain the velocity in the moving reference frame by calculating $\ww = \uu - \uuref$.
-\fi
 
@@
 
-\subsection{Discretization of the Stokes Equations}
+\subsection{Discretization of the Stokes equations}
 We will outline the discretization of the weak formulation~\cref{eq:abstract_weak_form_modelC,eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form} of the Stokes equations for model version 0.
@@
 
-\subsection{Weak Formulation of the Advection-Diffusion Equation}
+\subsection{Weak formulation of the advection-diffusion equation}
 Recall the strong form of the advection-diffusion equation:
@@
 
-\subsection{Discretization of the Advection-Diffusion Equation}
+\subsection{Discretization of the advection-diffusion equation}
 We outline the discretization of the advection-diffusion weak formulation for model version 0, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
@@
 \subsection{Method of Manufactured Solutions}\label{subsec:mms}
-Let $\hat{\xx} = (\hat{x}, \hat{y}, \hat{z}) = \frac{1}{L}(x, y, z)$ be the spatial coordinates scaled by the length $L$, which is the length of the computational domain $\Omega$ in the $x$-direction.
-Letting $\bm{\phi}$ be the vector-valued function
+Let $\hat{\xx} = (\hat{x}, \hat{y}, \hat{z}) = \frac{1}{L}(x, y, z)$
+be the spatial coordinates scaled by the length $L$, which is the length of
+the computational domain $\Omega$ in the $x$-direction. Letting $\bm{\phi}$ be the vector-valued function
 \begin{equation*}
     \bm{\phi} = \left(\sin{(\pi(\hat{x} - \hat{y}))}, \sin{(\pi(\hat{y} + \hat{z}))}, \sin{(\pi(\hat{x} - \hat{z}))}\right)
-    %\label{eq:velocity_potential_mms}
 \end{equation*}
@@
 \end{equation}
-we have by construction that the velocity is divergence-free, owing to the identity $\nabla\cdot(\nabla\times\mathbf{F}) = 0$ for an arbitrary vector field $\mathbf{F}$. The pressure was defined as
+we have by construction that the velocity is divergence-free,
+owing to the identity $\nabla\cdot(\nabla\times\mathbf{F}) = 0$ for
+an arbitrary vector field $\mathbf{F}$. The pressure was defined as
 \begin{equation}
@@
 \end{equation}
-Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions}, we construct a Stokes problem where~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms} are the solutions.
+Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions},
+we construct a problem with the Stokes equations where~\eqref{eq:velocity_mms}
+and~\eqref{eq:pressure_mms} are the solutions.
 To this end, we consider the general form of the steady Stokes equations
@@
 \end{subequations}%
-with $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and $\beps(\uu) = \frac{1}{2}\left(\nabla\uu + (\nabla\uu)^T\right)$, and the boundary condition
+with $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and
+$\beps(\uu) = \frac{1}{2}\left(\nabla\uu + (\nabla\uu)^T\right)$, and the boundary condition
 \begin{alignat}{2}
@@
 where $\Gamma=\partial\Omega$ is the boundary of the domain.
-Since the velocity field~\eqref{eq:velocity_mms} is divergence free by construction, $g = 0$.
-Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$  using~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}, the solutions $\uu$ and $p$ to~\eqref{eq:stokes_mms} will be the ones defined by~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms}, as long as we enforce equality in the mean pressures, i.e.
-$\intO{(p_h - p_{\mathrm{mms}})}=0$.
-Convergence rates are then readily calculated by comparing the numerical approximations of $\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$ on meshes of varying grid resolution.
-
-\subsection{Norms and Convergence Order}\label{subsec:norms_and_eoc}
-Errors of the velocity $\uu_h$ and pressure $p_h$ approximated with finite elements were measured in the $\mathbf{H}^1$ and $L^2$ error norms, respectively.
+Since the velocity field~\eqref{eq:velocity_mms} is divergence free by construction,
+$g = 0$. Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$
+using~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms},
+the solutions $\uu$ and $p$ to~\eqref{eq:stokes_mms} will be the ones
+defined by~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms},
+as long as we enforce equality in the mean pressures, i.e. $\intO{(p_h - p_{\mathrm{mms}})}=0$.
+Convergence rates are then readily calculated by comparing the numerical approximations of
+$\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$ on meshes of varying grid resolution.
+
+\subsection{Norms and convergence order}\label{subsec:norms_and_eoc}
+Errors of the velocity $\uu_h$ and pressure $p_h$ approximated with finite elements
+were measured in the $\mathbf{H}^1$ and $L^2$ error norms, respectively.
 With the exact velocity field $\uu_{\mathrm{ex}}$, the $\mathbf{H}^1$ error norm was calculated as
@@
 \end{equation*}
-The approximated functions were interpolated onto elements in a space of piecewise-continuous Lagrange polynomials of three polynomial degrees higher than the elements used to approximate the functions, meaning that polynomial degrees 5 and 4 were used for the velocity and pressure errors, respectively.
-Numerical integration was performed with a Gauss quadrature rule, with the quadrature rule degree equal to the polynomial degree of the integrated finite element functions.
-
-Convergence rates reported in~\cref{subsec:numerical_verification} were approximated in the following way.
-Define the error $e_k$ for a given mesh resolution $h_k$.
-Based on the assumption that the error scales as $e_k \approx C{h_k}^l$, where $C$ is a constant independent of $h_k$, the convergence order $l$ was approximated as
+The approximated functions were interpolated onto elements in a space of piecewise-continuous
+Lagrange polynomials of three polynomial degrees higher than the elements used to approximate
+the functions, meaning that polynomial degrees 5 and 4 were used for the velocity and pressure
+errors, respectively. Numerical integration was performed with a Gauss quadrature rule,
+with the quadrature rule degree equal to the polynomial degree of the integrated finite element functions.
+
+Convergence rates reported in~\Cref{subsec:numerical_verification} were
+approximated in the following way. Define the error $e_k$ for a given mesh
+resolution $h_k$. Based on the assumption that the error scales as
+$e_k \approx C{h_k}^l$, where $C$ is a constant independent of $h_k$,
+the convergence order $l$ was approximated as
 \begin{equation}
@@
 \end{equation*}
-with basis functions $\psi_i$, where $i$ are the degrees of freedom and Einstein summation is employed. The infinity norm of $\phi$ was approximated from the vector
+with basis functions $\psi_i$, where $i$ are the degrees of freedom and Einstein summation is employed.
+The infinity norm of $\phi$ was approximated from the vector
 of coefficients $\left\{\phi_i\right\}$, which represent point evaluations of $\phi$ as
@@
 
-\subsection{Numerical Verification of Model Implementation}\label{subsec:numerical_verification}
-A cylinder geometry meshed with varying degrees of refinement was used to perform convergence analysis of the numerical methods used to solve the Stokes equations.
+\subsection{Numerical verification of model implementation}\label{subsec:numerical_verification}
+A cylinder geometry meshed with varying degrees of refinement was used to
+perform convergence analysis of the numerical methods used to solve the Stokes equations.
 The cylinder had unit length and a diameter of one half length unit.
-For the analysis, we used tangential traction boundary conditions on all of the cylinder surface.
-Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions} with the velocity and pressure expressions defined in~\cref{subsec:mms} for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{H}(\mathrm{div};\Omega)$ and $\mathbf{H}^1$ error norms for $\uu_h$, and the $L^2$ error norm for $p_h$~(\cref{tab:cylinder_error_rates}).
-Based on the error norm calculations, we also calculated the experimental order of convergence~(\cref{subsec:norms_and_eoc}).
-We observe convergence in all of the reported error norms.
-Furthermore, we report the error in calculation of the maximum velocities, and observe convergence in this error as well.
-Lastly, we calculated the $L^2$ norm of the divergence $\nabla\cdot\uu_h$ to verify the property of mass conservation.
+For the analysis, we used tangential traction boundary conditions on all
+of the cylinder surface. Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions}
+with the velocity and pressure expressions defined in~\Cref{subsec:mms}
+for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{H}(\mathrm{div};\Omega)$
+and $\mathbf{H}^1$ error norms for $\uu_h$, and the $L^2$ error norm for
+$p_h$~(\cref{tab:cylinder_error_rates}). Based on the error norm calculations,
+we also calculated the experimental order of convergence~(\Cref{subsec:norms_and_eoc}).
+We observe convergence in all of the reported error norms. Furthermore,
+we report the error in calculation of the maximum velocities, and observe
+convergence in this error as well. Lastly, we calculated the $L^2$ norm of
+the divergence $\nabla\cdot\uu_h$ to verify the property of mass conservation.
 \begin{table}[!htbp]
@@
 
-To verify the model implementation with the zebrafish brain ventricles mesh, we compared velocity norms for varying degrees of refinement of the brain ventricles mesh~(\cref{tab:ventricles_norms_BDM}).
+To verify the model implementation with the zebrafish brain ventricles mesh,
+we compared velocity norms for varying degrees of refinement of the brain ventricles mesh~(\Cref{tab:ventricles_norms_BDM}).
 For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$.
-For a velocity vector $\uu=(u_x, u_y, u_z)$, the velocity magnitude is $u = \sqrt{u_x^2 + u_y^2 + u_z^2}$.
-We also report the maximum value $\normlinf{u_h}$ scaled by the area $|\Gc|=\intGc{}$ over which tangential traction $\btau$ was applied.
-We chose this measure using $|\Gc|$ as a scale because the regions of the mesh marked as cilia-populated changes slightly with every mesh refinement, owing to the unstructured organization of the mesh cells.
-This change in the surface area over which the tangential traction was applied directly affected the maximum velocity magnitude, since the maximum velocity magnitude is a result of the total amount of force $\intGc{\btau\cdot P_{\nn}(\rr)}$ applied on the ciliated boundary, where the cilia vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ as introduced in~\cref{subsec:appendixA1}.
-In the numerical experiments, we set a constant $\tau = 6.5\times 10^{-4}$ Pa and $\lambda(\xx)=1$.
-We set $\rr = (1, 0, 1)$ in the ventral middle ventricle cilia region and $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle cilia regions.
-We used $\gamma=10$ for the BDM penalty parameter.
-
-To account for the fact that the volume $|\Omega|=\intO{}$ also changes slightly with mesh refinement, we report the $\mathbf{L}^2$ norm of $\uu_h$ scaled by $|\Omega|$.
-Finally, we provide verification of mass conservation by reporting the $\mathbf{L}^2$ norms of the divergence $\nabla\cdot\uu_h$.
-We remark that the units used in the model implementation was millimeters, which is why~\cref{tab:ventricles_norms_BDM} reports units in millimeters, instead of micrometers which has been used elsewhere in the paper.
+For a velocity vector $\uu=(u_x, u_y, u_z)$, the velocity magnitude is
+$u = \sqrt{u_x^2 + u_y^2 + u_z^2}$. We also report the maximum value
+$\normlinf{u_h}$ scaled by the area $|\Gc|=\intGc{}$ over which tangential traction
+$\btau$ was applied. We chose this measure using $|\Gc|$ as a scale because the regions
+of the mesh marked as cilia-populated changes slightly with every mesh refinement,
+owing to the unstructured organization of the mesh cells. This change in the surface
+area over which the tangential traction was applied directly affected the maximum velocity magnitude,
+since the maximum velocity magnitude is a result of the total amount of force
+$\intGc{\btau\cdot P_{\nn}(\rr)}$ applied on the ciliated boundary, where the cilia
+vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ as introduced in~\Cref{subsec:appendixA1}.
+In the numerical experiments, we set a constant $\tau = 6.5\times 10^{-4}$ Pa and
+$\lambda(\xx)=1$. We set $\rr = (1, 0, 1)$ in the ventral middle ventricle cilia region
+and $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle cilia
+regions. We used $\gamma=10$ for the BDM penalty parameter.
+
+To account for the fact that the volume $|\Omega|=\intO{}$ also changes
+slightly with mesh refinement, we report the $\mathbf{L}^2$ norm of $\uu_h$ scaled by $|\Omega|$.
+Finally, we provide verification of mass conservation by reporting the $\mathbf{L}^2$ norms of
+the divergence $\nabla\cdot\uu_h$. We remark that the units used in the model
+implementation was millimeters, which is why~\Cref{tab:ventricles_norms_BDM}
+reports units in millimeters, instead of micrometers which has been used elsewhere in the paper. 
 \begin{table}[!htbp]
@@
 \end{table}
-\iffalse
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{graphics/cylinder_mesh.png}
-    \caption{The cylinder geometry used for convergence analysis.
-The cylinder had unit length and a diameter of half a unit length.
-Illustrated here is the mesh of highest resolution, with $h/h_0 = 1/8$ and a total of 1 855 337 degrees of freedom.}
-    \label{fig:cylinder_mesh}
-\end{figure}
-\fi
-
-\section{Quantification of Particle Transport}\label{sec:appC_particle_transport}
+
+\section{Quantification of particle transport}\label{sec:appC_particle_transport}
 Particle tracking data~\cite{Olstad2019CiliaryDevelopment} was analyzed.
 For four zebrafish, five recordings with a few particles for each fish were carried out.
-The particles tracked were in the duct between the rhombencephalic ventricle and the diencephalic ventricle.
-Frequency of image acquisition was 20.22 Hz.
-The collected data constituted $x$ and $y$ positions of the particles at every time instant of image acquisition.
-The velocities $\uu_x$ and $\uu_y$ were determined by calculating the change in positions $\Delta x$ and $\Delta y$ relative to the change in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the frequency of acquisition.
-Mean velocities $\overline{u}_x$~(\cref{fig:meanx}) and $\overline{u}_y$~(\cref{fig:meany}), which serve as a quantification of particle drift, were calculated by taking the difference between the last and first positions of a particle.
-
-Particle movement varied over the different measurements.
-The mean of $\overline{u}_x$ was 0.26 $\mu$m/s and the mean of $\overline{u}_y$ was 0.08 $\mu$m/s.
-The maximum mean velocities in absolute values were 10.2 $\mu$m/s and 2.4 $\mu$m/s for $\overline{u}_x$ and $\overline{u}_y$, respectively.
-We used flow model II (only cardiac forces) to tune the pressure boundary condition amplitude $A$.
-The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude of 4.8 $\mu$m/s, which is close to the maximum observed in the particle tracking data when rejecting the outlier at around 10 $\mu$m/s; (ii) it yields a time-averaged mean velocity of 0.89 $\mu$m/s, which is close to the mean observed in the particle tracking data.
+The particles tracked were in the duct between the rhombencephalic ventricle and the
+diencephalic ventricle. Frequency of image acquisition was 20.22 Hz.
+The collected data constituted $x$ and $y$ positions of the particles at every time
+instant of image acquisition. The velocities $\uu_x$ and $\uu_y$ were determined by
+calculating the change in positions $\Delta x$ and $\Delta y$ relative to the change
+in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the frequency of acquisition.
+Mean velocities $\overline{u}_x$~(\Cref{fig:meanx}) and $\overline{u}_y$~(\Cref{fig:meany}),
+which serve as a quantification of particle drift, were calculated
+by taking the difference between the last and first positions of a particle.
+
+Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
+0.26 $\mu$m/s and the mean of $\overline{u}_y$ was 0.08 $\mu$m/s. The maximum mean velocities
+in absolute values were 10.2 $\mu$m/s and 2.4 $\mu$m/s for $\overline{u}_x$ and $\overline{u}_y$,
+respectively. We used flow model II (only cardiac forces) to tune the pressure boundary condition
+amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude
+of 4.8 $\mu$m/s, which is close to the maximum observed in the particle tracking data when
+rejecting the outlier at around 10 $\mu$m/s; (ii) it yields a time-averaged mean velocity
+of 0.89 $\mu$m/s, which is close to the mean observed in the particle tracking data.
 \begin{figure}[H]

### 2025-02-04 paper/main.tex
appendix edits, discussion on role of cilia

@@
 \usepackage{booktabs}
-\usepackage{makecell} % for table cells with line breaks
 \usepackage{bm}
@@
 \usepackage{graphicx}
-\usepackage{graphbox} % for center-aligning figures vertically
 \usepackage{tkz-euclide} % draw tikz pictures
@@
 
-In this study, we combined computational and experimental approaches to investigate the role of motile cilia in CSF flow generation and solute transport.
-First, we computed flow patterns and intraventricular transport in silico. To this end, we used the geometry of the zebrafish larval brain ventricles,
+In this study, we combined computational and experimental approaches to investigate the role of motile cilia in CSF flow and solute transport.
+First, we computed flow patterns and intraventricular transport \emph{in silico}. To this end, we used the geometry of the zebrafish larval brain ventricles,
 for which we have detailed knowledge of cilia properties and CSF movement velocities and frequencies.
-Notably, this early developmental stage allows us to simplify our model by omitting CSF secretion, which starts at later stages, while still being well conserved with mammals.
+Notably, this early developmental stage allows us to simplify our model by omitting CSF secretion, which starts at later stages, while still being well-conserved with mammals.
 Next, we validated our computation model with experimental data by monitoring the dynamics of a photoconvertible fluorescent protein expressed within the brain ventricles.
-Our results identified that diffusion plays a major role in the transport of small solutes, whereas cilia majorly contribute to the movement of larger particles.
-We also found that the location of cilia and the ventricular geometry greatly impact solute distribution.
-Altogether, our work presents a computational framework and new concepts of how cilia collaborate with other factors to distribute molecules and particles within the brain ventricles.
+Our results show that diffusion plays a major role in the transport of small solutes, whereas cilia majorly contribute to the movement of larger particles.
+We also found that the location of cilia, as well as the ventricular geometry, greatly impact solute distribution.
+Altogether, our work presents a computational framework together with new concepts of how cilia
+collaborate with other factors to distribute molecules and particles within the brain ventricles.
 
 \section*{Methods}
-
-\mer{@HH: I suggest you write \cref{fig:figure1}a, rather than \cref{fig:figure1} panel \textbf{a}, throughout. Increases signal-to-noise ratio.}
-
 \subsection*{Image-based computational geometries of zebrafish brain ventricles}
-We generated a 3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}.
-From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:figure1}d). The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
+To model flow and transport in zebrafish larval brain ventricles, we generated a 3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
+injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
+From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:figure1}d).
+The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
 The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). 
-At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic  (anterior), the di-/mesencephalic  (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts.
-Parts of the ventricular surfaces were marked to be lined with motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:figure1}d, pink markers).
+At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
+the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
+Parts of the ventricular surfaces were marked to be lined with
+motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:figure1}d, pink markers).
 \begin{figure}%[hbt!]
@@
 the middle ventricle, the mid-hind brain connection, and all three simultaneously. 
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry. \mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+\mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}
 
 \subsection*{Computational CSF dynamics}
-The beating motion of the cilia generates CSF flow with steady rotational structures~\cite{Olstad2019CiliaryDevelopment} within the brain ventricles (\Cref{fig:figure1}a--c).
-In addition, cardiac pulsations induces pulsatile CSF flow. We model this flow of CSF in the brain ventricles by the time-dependent, incompressible Stokes equations which read as follows.
-Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$ and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
+The beating motion of the cilia generates CSF flow with steady rotational structures~\cite{Olstad2019CiliaryDevelopment}
+within the brain ventricles (\Cref{fig:figure1}a--c).
+In addition, cardiac pulsations induces pulsatile CSF flow.
+We model this flow of CSF in the brain ventricles by the time-dependent,
+incompressible Stokes equations which read as follows.
+Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
+and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
 \begin{subequations}
@@
       \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
-      \quad \text{in } \Omega,
-      \label{eq:stokes_eq_mom}\\
+      \quad \text{in } \Omega,\\
       \nabla \cdot \uu &= 0
@@
 \end{subequations}%
-where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
+where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
+and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
 Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
-Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density and $\mu=6.97\times 10^{-4}$ Pa is the dynamic viscosity of the CSF.
-We introduce the tangential traction $\bsigpar$ as the tangential component of the traction $\hat{\bsig}=\bsig\nn$:
+Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
+and $\mu=6.97\times 10^{-4}$ Pa is the dynamic viscosity of the CSF.
+We introduce the tangential traction $\bsigpar$ as the
+tangential component of the traction $\hat{\bsig}=\bsig\nn$:
 \begin{equation*}
@@
 \end{equation*}
-where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$, and $P_{\nn}(\rr)$ is the tangential  projection of a vector $\rr$ onto $\Gamma$.
-We consider three types of boundary conditions:  (i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
+and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
+We consider three types of boundary conditions:
+(i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
 (ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
 and (iii) \emph{free slip} (no flow normal to the boundary $\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the boundary. We assume that the system starts at rest ($\uu(\xx, t=0) = \mathbf{0}$).
+Unless noted otherwise, the free-slip condition is applied on the boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
 
 \subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:figure1}d), we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces of the cilia acting on the CSF.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$ and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by model calibration against the experimental data~\cite{Olstad2019CiliaryDevelopment}.
+On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:figure1}d),
+we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces of the cilia acting on the CSF.
+We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
+and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the cilia region (see~\Cref{subsec:appendixA1}).
+Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by heuristic
+model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
 
 \subsection*{Flow induced by cardiac pulsations}\label{subsec:pressure_bcs}
-To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts of the boundary $\Gp$~(\Cref{fig:figure1}d, blue markers).
-The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow, and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
+To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
+$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the boundary $\Gp$~(\Cref{fig:figure1}d, blue markers).
+The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow,
+and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
 The angular cardiac frequency $\omega=2\pi f=6.97$ rad/s was set based on a measured cardiac frequency of $f=2.22$ Hz.
@@
 \subsection*{Computational model of solute transport after photoconversion}
-We simulate transport of photoconverted proteins within the brain ventricles by modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and time $t > 0$ by the advection-diffusion equation
+We simulate transport of photoconverted proteins within the brain ventricles by
+modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
+time $t > 0$ by the advection-diffusion equation
 \begin{equation}
@@
 \end{equation*}
-Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs}, and $D$ is the molecular diffusion coefficient of the solute.
+Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs},
+and $D$ is the molecular diffusion coefficient of the solute.
 Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
-The ventricular walls are assumed to be impermeable (admitting \emph{no flux} i.e.~$\JJ\cdot\nn=0$), except at the anterior/posterior boundary $\Gamma_p$.
-\fixme{At the anterior/posterior boundary we allow the solute concentration to be advected into and out of the domain in a manner that ensures conservation of mass (see~\Cref{sec:appendix:X} for details).}
-\mer{MER: @Halvor: could you have a go at moving the precise description to the Appendix?}
-\fixme{There, we consider either prescribed \emph{influx} in the form of a time-periodic condition on the total flux $(\JJ\cdot\nn)|_{\mathrm{in}}^{n+1}=(\JJ\cdot\nn)|_{\mathrm{out}}^{n}$ and/or \emph{outflux} with zero diffusive flux $D\nabla c\cdot\nn=0$.}
-\fixme{Additionally, when considering pulsatile motion, the in- and outflow on the pressure boundary $\Gp$ must be accounted for.
-We split $\Gp$ in two parts; $\Gin$ denotes the part of $\Gp$ where $\uu\cdot\nn < 0$;
-$\Gout$ denotes the part where $\uu\cdot\nn > 0$.
-On $\Gin$, a total flux boundary condition was set: the inflow flux at a given timestep was set equal to the outflow boundary flux at the previous timestep.
-This was done to approximate a periodic boundary condition. On $\Gout$, we considered the diffusive flux normal to the boundary to be zero.}
+The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
+except at the anterior/posterior boundary $\Gamma_p$.
+At the anterior/posterior boundary, we permit the solute concentration to be advected into
+and out of the domain in a manner that ensures conservation of mass (see~\Cref{subsec:adv_diff_eq_weak_form} for details).
 
@@
   \qquad \xx \in \Omega_{\mathrm{pc}}, \quad \fixme{t > 0}.
-\label{eq:injection_curve}
+\label{eq:photoconversion_curve}
 \end{equation}
@@
         Pressure amplitude & $A$ & \num{1.5e-03} & Pa & * \\
-        %Ref. frame motion amplitude & $A_{\mathrm{ref}}$ & \num{9.19e-04} & m/s & *\\
         Exosome diffusion coefficient & $D_1$ & $\num{1.63e-12}$ & $\mathrm{m^2/s}$ & \textdagger\\
@@
     (*) Calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-(\textdagger) Estimated based on experimental data~\cite{GuraSadovsky2017MeasurementExpansion, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}.}
+    (\textdagger) Estimated based on experimental
+    data~\cite{GuraSadovsky2017MeasurementExpansion, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}.}
     \label{tab:parameter_table}
@@
 When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
-In region number one (the photoconversion region), we use the function~\eqref{eq:injection_curve} to enforce the concentration such that it represents the experimental data of photoconversion of proteins.
+In region number one (the photoconversion region), we use the function~\eqref{eq:photoconversion_curve} to enforce the concentration such that it represents the experimental data of photoconversion of proteins.
 We consider the three different diffusion coefficients introduced in previous sections to simulate and compare results for transport of molecules of varying sizes.
@@
 in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$) as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$.
-The dynamics of ROI 1 follows directly from~\eqref{eq:injection_curve}.
+The dynamics of ROI 1 follows directly from~\eqref{eq:photoconversion_curve}.
 In addition, we report time-to-threshold: the time $\hat{t}_i$ when the mean concentration $\cbar_i$ first exceed a threshold value $\hat{c}_i$.
@@
 Transport of solute is quantified by the profile of the mean concentrations $\cbar_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\Cref{fig:fig2}b--d).
-An illustration of the ROIs is provided in \Cref{fig:fig2}e. The dynamics of ROI 1 follow from imposing~\Cref{eq:injection_curve}.
+An illustration of the ROIs is provided in \Cref{fig:fig2}e. The dynamics of ROI 1 follow from imposing~\Cref{eq:photoconversion_curve}.
 For ROIs 2--6, we observe more rapid concentration increases when the diffusion coefficient increases. 
@@
 In region 6, the threshold is never exceeded for $D_1$, with the mean concentration close to zero at the end of the simulation. 
-To quantify the balance of advection versus diffusion as transport mehcanisms on a global scale, we calculate the Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
+To quantify the balance of advection versus diffusion as transport mehcanisms on a global scale,
+we calculate the Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
 Since $\mathrm{Pe}>1$, this indicates that advection is the dominant transport mechanism for the molecules considered.
@@
 as the maximum velocity dropped from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
-In contrast, removing telencephalic and ventral diencephalic had minimalno to little impact and resulted in maximum velocities of 27.7 $\mu$m/s or 27.2 $\mu$m/s, respectively.
+In contrast, removing telencephalic and ventral diencephalic had minimal
+impact and resulted in maximum velocities of 27.7 $\mu$m/s or 27.2 $\mu$m/s, respectively.
 
@@
 
-\lyng{HH: Quantify differences in terms of percentage changes in the final mean concentration values, maybe with a bar plot?}
+\lyng{HH: Quantify differences in terms of percentage changes in the
+final mean concentration values, maybe with a bar plot?}
 \begin{figure}[H]
@@
     \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
-    \caption{Caption. \mk{MK: How do the different geoemtries compare in terms of volume, areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
+    \caption{Caption. \mk{MK: How do the different geoemtries compare in terms of volume,
+    areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
     \label{fig:figure6_sim_results_compare_geometries}
@@
 \subsection*{The roles of advection and diffusion in intraventricular solute transport}
-To determine the roles of advection and diffusion in solute transport, we quantified transport
+To investigate the roles of advection and diffusion in solute transport, we quantified transport
 based on changes in fluorescence intensity $\Delta F$ (experiments) and
@@
 Indeed, we identified that the diffusion coefficient had a greater impact on transport to
-regions located upstream in the CSF flow field (ROI 4\lyng{ actually 3?}) or in different ventricles (ROIs 5--6),
+regions located upstream in the CSF flow field (ROI 4 \fixme{@Nathalie: should this have been 3 instead of 4?}) or in different ventricles (ROIs 5--6),
 than the regions located downstream of cilia-mediated flow (ROI 2).
@@
 We previously identified large inter-individual variation in ventricular size and
-CSF velocities between larva at given developmental stages and throughout development~\fixme{Add some citation here? Olstad/D'Gama}.
+CSF velocities between larva at given developmental stages and throughout development~\fixme{@Nathalie: Add some citation here? Olstad/D'Gama}.
 Our results suggest that these two parameters may well co-vary and explain the variation.
@@
 
-\lyng{HH: Discuss cilia serving as an "enhanced mixing factor" on small scales, refer to this~\cite{Siyahhan2014FlowVentricles} and this~\cite{Yoshida2022EffectVentricles} paper that studied this in human brain ventricles.
-Include a discussion of what happened when these papers removed cilia.}
+\lyng{HH: Discuss cilia serving as an "enhanced mixing factor" on small scales,
+refer to this~\cite{Siyahhan2014FlowVentricles} and this~\cite{Yoshida2022EffectVentricles}
+paper that studied this in human brain ventricles. Include a discussion of what happened when these papers removed cilia.}
 
@@
 \subsection*{Estimation of computational model parameters}
-The diffusion coefficients used in this study were partially based on values from experiments and partially estimated.
-The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$ is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the values $D_2$ and $D_1$ were extrapolated based on experimental data~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells, Mahmood2023ExosomeTemperature} using the Stokes-Einstein relation~\cite{Einstein1905UberTeilchen}~(\cref{eq:D_stokes_einstein}).
-This extrapolation assumes the diffusing substance is of spherical shape, which proteins are not, and the relation does not necessarily hold in CSF.
-Consequently, there is uncertainty in the values used.
-We note that Sadovsky~\emph{et al.}~\cite{GuraSadovsky2017MeasurementExpansion} reported that Dendra2 satisfies the Stokes-Einstein in the solution they used, a solution which had similar viscosity to water.
-We used CSF density and viscosity values measured in humans~\cite{Bloomfield1998EffectsFluid}, and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances, the CSF in which photoconverted Dendra2 are transport in our experiments may be more viscous than what we consider.
-This would reduce the diffusion coefficient~(cf.~\cref{eq:D_stokes_einstein}), but based on reports of protein concentration having a limited impact on the viscosity of CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}, this reduction is presumably limited.
-Merely the presence of other proteins and nutrients may also reduce the diffusion coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
-Considering the diffusion coefficients $D_1$ and $D_2$ both smaller than $D_3$ in our transport analysis provides information about how the simulation results of Dendra2 transport would be altered if the diffusion coefficient $D_3$ is overestimated.
-In the case that $D_3$ is underestimated, we assume the results would follow the same trend as the differences between results for $D_2$ and $D_3$: diffusion becomes more important, and is almost balancing advective transport for $D_3$.
-Thus for a higher diffusion coefficient, we would see transport that is mostly explained by diffusive behavior.
-
-We heuristically determined the parameter $\tau = \num{6.5e-4}$ Pa, which determines the magnitude of the cilia tangential traction boundary conditions.
-The maximum force applied was in the dorsal region of the middle ventricle, where the posterior region had a tangential traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = \num{2.5e-3}$ Pa applied to the boundary.
-A couple of previous simulation studies of cilia-mediated flow in brain ventricles have used a volumetric force density to represent the cilia.
-Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles} used a force expression that increased linearly from the wall to a maximum force density of $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 $\mu$m away from the wall, which represented cilium length.
-If we assumed a cilia array of the same thickness $l = 15$ $\mu$m in our model, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$ would correspond to a maximum force density of
+The diffusion coefficients used in this study were partially based on values
+from experiments and partially estimated. The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$
+is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an
+experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the values $D_2$ and
+$D_1$ were extrapolated based on experimental data~\cite{Swaminathan1997PhotobleachingDiffusion,
+Potma2001ReducedCells, Mahmood2023ExosomeTemperature} using the Stokes-Einstein
+relation~\cite{Einstein1905UberTeilchen}~(\Cref{eq:D_stokes_einstein}).
+This extrapolation assumes the diffusing substance is of spherical shape, which proteins are not,
+and the relation does not necessarily hold in CSF. Consequently, there is uncertainty in the values used.
+We note that Sadovsky~\emph{et al.}~\cite{GuraSadovsky2017MeasurementExpansion} reported that
+Dendra2 satisfies the Stokes-Einstein in the solution they used, a solution which had similar viscosity
+to water. We used CSF density and viscosity values measured in humans~\cite{Bloomfield1998EffectsFluid},
+and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances,
+the CSF in which photoconverted Dendra2 are transport in our experiments may be more viscous
+than what we consider. This would reduce the diffusion coefficient~(cf.~\Cref{eq:D_stokes_einstein}),
+but based on reports of protein concentration having a limited impact on the viscosity of
+CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}, this reduction is presumably
+limited. Merely the presence of other proteins and nutrients may also reduce the diffusion
+coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
+Considering the diffusion coefficients $D_1$ and $D_2$ both smaller than $D_3$ in our transport analysis
+provides information about how the simulation results of Dendra2 transport would be altered if the
+diffusion coefficient $D_3$ is overestimated. In the case that $D_3$ is underestimated, we assume the
+results would follow the same trend as the differences between results for $D_2$ and $D_3$: diffusion becomes
+more important, and is almost balancing advective transport for $D_3$. Thus for a higher diffusion coefficient,
+we would see transport that is mostly explained by diffusive behavior.
+
+We heuristically determined the parameter $\tau = \num{6.5e-4}$ Pa, which determines
+the magnitude of the cilia tangential traction boundary conditions. The maximum force applied
+was in the dorsal region of the middle ventricle, where the posterior region had a tangential
+traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = \num{2.5e-3}$ Pa applied to the
+boundary. A couple of previous simulation studies of cilia-mediated flow in brain ventricles have
+used a volumetric force density to represent the cilia. Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}
+used a force expression that increased linearly from the wall to a maximum force density of
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 $\mu$m away from the wall,
+which represented cilium length. If we assumed a cilia array of the same thickness
+$l = 15$ $\mu$m in our model, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$
+would correspond to a maximum force density of 
 \begin{equation*}
@@
 which smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 $\mu m$ is the a typical length of cilia in human brain ventricles (in general the length is between 10--15 $\mu$m~\cite{Afzelius2004Cilia-relatedDiseases}), while in zebrafish they are closer to 5 $\mu$m~\cite{Salman2022ComputationalEmbryo}.
-With $l=5$ $\mu$m, our traction parameter corresponds to a maximum force density of $f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ used by Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}.
+The length 15 $\mu m$ is the a typical length of cilia in human brain ventricles
+(in general the length is between 10--15 $\mu$m~\cite{Afzelius2004Cilia-relatedDiseases}),
+while in zebrafish they are closer to 5 $\mu$m~\cite{Salman2022ComputationalEmbryo}.
+With $l=5$ $\mu$m, our traction parameter corresponds to a maximum force density of
+$f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$
+used by Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}.
 We note that they based $f_{\mathrm{max}}$ on reconstructions of flow velocities in murine brain ventricles.
 
-Another study that used a force density to model ciliary motion is Thouvenin~\emph{et al.}~\cite{Thouvenin2020OriginCanal}, where two-dimensional flow in the central canal of zebrafish embryos was modeled using a cilia force density of 4000 N/$\mathrm{m^2}$.
-The resulting numerical velocity fields matched well with \emph{in vivo} measurements, where the maximum velocity was around 5 $\mu$m/s (recall that we observed a maximum of 27.7 $\mu$m/s in the present study).
-The geometry they studied resembles a pipe, probably offering more flow resistance than the open geometry considered in our work, which may be why they needed a larger force density to accurately represent experimental results.
-In any case, it is interesting to note that our and these two previous studies have estimated cilia force densities that only differ by one order of magnitude.
+Another study that used a force density to model ciliary motion is
+Thouvenin~\emph{et al.}~\cite{Thouvenin2020OriginCanal}, where two-dimensional flow
+in the central canal of zebrafish embryos was modeled using a cilia force density of
+4000 N/$\mathrm{m^2}$. The resulting numerical velocity fields matched well with
+\emph{in vivo} measurements, where the maximum velocity magnitude was around 5 $\mu$m/s
+(recall that our model exhibits a maximum of 27.7 $\mu$m/s).
+The geometry they studied resembles a pipe, probably offering more flow resistance
+than the open geometry considered in our work, which may be why they needed a larger
+force density to accurately represent experimental results. In any case, it is
+interesting to note that our and these two previous studies have estimated
+cilia force densities that only differ by one order of magnitude.
 
 \subsection*{Numerical approximation and convergence rates}
-The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employ for the Stokes equations is computationally more expensive than a more conventional approach based on e.g.
-Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem} ($\mathbb{P}_2-\mathbb{P}_1$ elements) or lower-order enriched elements~\cite{Brezzi2011MixedMethods}, such as the mini-element ($\mathbb{P}_1-\mathbb{P}_1$ with a velocity stabilization).
+The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme
+($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employ for the Stokes equations
+is computationally more expensive than a more conventional approach based on
+e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
+($\mathbb{P}_2-\mathbb{P}_1$ elements) or lower-order enriched elements~\cite{Brezzi2011MixedMethods},
+such as the mini-element ($\mathbb{P}_1-\mathbb{P}_1$ with a velocity stabilization).
 Here, $\mathbb{P}_k$ is the set of continuous Lagrange polynomials of order $k$.
-We opted for the BDM-DG scheme because of its exactly-mass-conserving property, since numerical experiments proved that a divergence-free velocity field was  paramount to attain a stable discretization of the advection-diffusion equation in advection-dominated regions.
-Preliminary attempts using Taylor-Hood elements proved hard to achieve stable transport results with a reasonable computational mesh size.
-Stability either required excessive mesh refinement and/or problem-specific tuning of hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization method~\cite{Franca1992StabilizedModel}.
-Probing numerical values of the divergence of the velocity when using Taylor-Hood elements revealed that, on the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was in the order of $10^{-6}$, while the maximum value of the divergence of the velocity was of order unity.
-This is a result of the fact that incompressibility is only achieved in a distributional sense when employing Taylor-Hood elements.
-On a refined mesh with roughly six times as many computational cells as the standard mesh, the numerical values of $\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still of the same orders as reported for the standard mesh.
-This may lead to the hyperbolic advective term in the advection-diffusion equation accumulating errors that grow unstable.
-
-In addition to its favorable mass-conserving property, the BDM-DG scheme lets us impose the impermeability condition strongly, and the tangential traction boundary condition weakly, without any tailored approach, since these boundary conditions appear naturally in the weak form of the Stokes equations~(\cref{subsec:appendixA1}).
-If instead e.g.
-Taylor-Hood elements were to be used, the impermeability boundary condition must be handled with for example a Nitsche method~\cite{Nitsche1971UberSind} or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers, Bertoluzza2017BoundaryHemodynamics}.
-
-%The error norms used to calculate the convergence rates that we report are not the ones naturally appearing in \emph{a priori} error estimates of a $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ discretization.
-Therefore, we cannot say anything explicit about expected convergence rates.
-However, the polynomial order $k$ of the elements provide an upper bound on the convergence rate, with the expectation that the $L^2$ error norm convergence rates should not exceed $k+1$.
-We observe convergence rates approaching $k+1$ and $k$ for the $\uu$ and $p$ error norms in $L^2$, when using polynomial orders $k$ and $k-1$, respectively.
+We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
+since numerical experiments proved that a divergence-free velocity field was
+paramount to attain a stable discretization of the advection-diffusion equation
+in advection-dominated regions. Preliminary attempts using Taylor-Hood elements
+proved hard to achieve stable transport results with a reasonable computational mesh size.
+Stability either required excessive mesh refinement and/or problem-specific tuning of
+hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization
+method~\cite{Franca1992StabilizedModel}. Probing numerical values of the divergence of
+the velocity when using Taylor-Hood elements revealed that, on the standard computational
+mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was in the order of $10^{-6}$, while the
+maximum value of the divergence of the velocity was of order unity. This is a result
+of the fact that incompressibility is only achieved in a distributional sense when
+employing Taylor-Hood elements. On a refined mesh with roughly six times as many
+computational cells as the standard mesh, the numerical values of
+$\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still
+of the same orders as reported for the standard mesh. This may lead to the
+hyperbolic advective term in the advection-diffusion equation accumulating errors
+that grow unstable over time.
+
+In addition to its favorable mass-conserving property, the BDM-DG scheme
+lets us impose the impermeability condition strongly, and the tangential
+traction boundary condition weakly, without any tailored approach,
+since these boundary conditions appear naturally in the weak form of the
+Stokes equations~(\cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
+elements were to be used, the impermeability boundary condition must
+be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
+or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers, Bertoluzza2017BoundaryHemodynamics}.
 
@@
 
-\subsection*{The role of cilia in the brain ventricles}
-Based on the observations made by Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}, it is clear that cilia are paramount for establishing healthy CSF flow patterns in embryonic zebrafish ventricles.
-However, our results indicate that when it comes to transport of small proteins, diffusion alone can do a lot of the work.
-This is because the embryonic zebrafish brain ventricles are very small.
-The same conclusion could not be drawn for larger animals, e.g.
-mice, rats, humans.
-\lyng{HH: Refer to and discuss some previous works there, e.g.
-Faubel, Eichele etc.}
-
-%Whether the zebrafish brain ventricles are a closed or open system at the embryonic developmental stage of two days post-fertilization is still an open question.
-According to Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}, despite the directional CSF flow generated by the motile cilia and the pulsatile displacement by the heartbeat, they did not observe any net CSF flow across the brain ventricles.
-Considering our results of modeling pulsatile flow with the brain ventricles as open (with normal pressure boundary conditions, model version IIa) or closed (domain movement, model version IIb), does it seem more likely that the ventricles are closed or open?
-
-The observation that hydrocephalus is more prevalent in mouse mutants than humans with primary ciliary dyskinesia suggests that the size of the ventricular system or the genetic disparity between species may account for the sensitivity of each species to hydrocephalus~\cite{Olstad2019CiliaryDevelopment}.
-Previous modeling work of CSF flow in human brain ventricles suggests that motile ciliary beating contributes specifically to the near-wall flow, while blood vessel pulsations, respiration and CSF secretion combine to generate a pulsatile bulk flow~\cite{Siyahhan2014FlowVentricles}.
-Cilia thus probably play an important role in regulating the amount of substances close to the ventricular wall, similar to coral reefs, where it has been observed that cilia are primary regulators of oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}.
-But for zebrafish embryos, the ventricles are so small that the flow generated by ciliary motion is of the scale of the geometry, and thus not only contributes to near-wall flow dynamics, but the whole ventricular system.
+\subsection*{The role of motile cilia in intraventricular flow and transport}
+Our work has studied CSF flow and solute distribution
+in a relatively small and simple model, which is devoid of
+active CSF secretion and CSF absorption. Even though there is
+a clear conservation of the ventricular system across vertebrates,
+there are also important considerations to take, which include
+ventricular size and geometries, properties of ciliated cells,
+animal posture, and magnitude of velocities. For instance, a large
+volume would require an extensive amount of time for solutes to distribute
+if based solely on diffusion. Besides, the presence of multiple cilia
+instead of a single cilium per cell, as described in mammalian ependymal cells,
+will generate much stronger velocities. Hence advection may be more
+dominant in those situations. However, in large brains, cilia beating will
+only contribute to a restricted flow at the very close proximity of the ventricular walls,
+while blood vessel pulsations, respiration and CSF secretion will generate a
+pulsatile bulk flow in the central regions of the ventricles~\cite{Siyahhan2014FlowVentricles}.
+Based on this, cilia probably play an important role in regulating the
+amount of substances close to the ventricular walls, similar to coral
+reefs, where it has been observed that cilia are primary regulators of
+oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}.
+But for zebrafish embryos, the ventricles are so small that the flow
+generated by ciliary motion is of the scale of the geometry, and thus not
+only contributes to near-wall flow dynamics, but the whole ventricular system.
+As of now, motile cilia deficiency has been associated with altered brain function
+in the zebrafish and ventricular enlargement in zebrafish, rodents and humans.
+Yet the molecular mechanisms leading to these alterations are poorly understood.
+We trust that our model sets the basis for future work addressing these open questions.
+We are also confident that our model can be adjusted and implemented to fit
+microscopic and macroscopic parameters once acquired for larger brains.
 
 \lyng{HH: Refer to Eichele et al. article discussion about role of cilia.}
-
-%Yet, according to Olstad~\emph{et al.}, the distribution of CSF is strongly influenced by bodily movement that eliminates the stringent boundaries of the ventricular cavities.
-Accounting for such bodily movement could be a next step.
-
-%Olstad \textit{et al.}\cite{Olstad2019CiliaryDevelopment} observed that bodily movement influenced ventricular flow. We do not account for body movement in this work.
 
@@
 \section*{Acknowledgments}
-Halvor Herlyng acknowledges support from the national infrastructure for computational science in Norway, Sigma2, via grant \#NN8049K.
-Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
+Halvor Herlyng acknowledges support from the national infrastructure for computational
+science in Norway, Sigma2, via grant \#NN8049K. Thanks are extended to J\o rgen Dokken
+for valuable model implementation discussions.
+This work was funded by the Research Council of Norway (NJY FRIPRO grants 314189 and 353348).
 \newpage
@@
 \end{subequations}%
-in the domain $\Omega$ with boundary $\Gamma$, where $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ is the viscous stress tensor, in which $\beps(\uu) = \frac{1}{2}(\nabla\uu + (\nabla\uu)^T)$ is the symmetric gradient.
-Furthermore, $\uu\in\VV$ is the fluid velocity and $p\in Q$ is the fluid pressure, and $\rho$ and $\mu$ are the fluid density and dynamic viscosity, respectively.
-Unless otherwise stated, we let $\bsig = \bsig(\uu, p)$.
-
-We will consider the function spaces $\VV$ and $Q$ based on the Sobolev spaces $\mathbf{H}^1(\mathrm{div}; \Omega)$ and $L^2(\Omega)$, respectively, defined as 
+in the domain $\Omega$ with boundary $\Gamma$, where
+$\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$ is the viscous
+stress tensor, in which $\beps(\uu) = \frac{1}{2}(\nabla\uu + (\nabla\uu)^T)$
+is the symmetric gradient. Furthermore, $\uu\in\VV$ is the fluid velocity
+and $p\in Q$ is the fluid pressure, and $\rho$ and $\mu$ are the fluid density
+and dynamic viscosity, respectively. Unless otherwise stated, we let $\bsig = \bsig(\uu, p)$.
+
+We will consider the function spaces $\VV$ and $Q$ based on the
+Sobolev spaces $\mathbf{H}^1(\mathrm{div}; \Omega)$ and $L^2(\Omega)$,
+respectively, defined as 
 \begin{align*}
@@
 \end{align*}
-Bold-faced characters for a space denotes a $d$--dimensional vector space, where $d$ is the spatial dimension of $\Omega$.
-For example, $\mathbf{H}^1(\Omega) = [H^1(\Omega)]^3$ if $\Omega$ is three-dimensional.
-We will consider $p\in Q=L^2_0(\Omega)$, with subscript 0 meaning that $\intO{p} = 0$, and $\uu\in\VV$ with
+Bold-faced characters for a space denotes a $d$--dimensional vector space,
+where $d$ is the spatial dimension of $\Omega$. For example,
+$\mathbf{H}^1(\Omega) = [H^1(\Omega)]^3$ if $\Omega$ is three-dimensional.
+We will consider $p\in Q=L^2_0(\Omega)$, with subscript 0 meaning
+that $\intO{p} = 0$, and $\uu\in\VV$ with
 \begin{equation*}
@@
 \mk{
-You should be careful here.
-The H(div) functions do not have a well defined gradient (and in turn $\varepsilon$).
-However, for the derivations of the continuous problem you don't need H(div).
-I would derive all the weak forms in $V = \left\{ v\in H^1, v\cdot n = \text{on} \Gamma\right\}$.
-Then in A.2 you say we chose spaces $V_h$ which are are not conforming, i.e.
-it does not hold that $V_h\subset V$.
-Instead you have $V_h\subset H(div)$.
-Reasons is better mass csrv and as a bonus the bcs can be enforced strongly.
-Note that H(div) functions can have jumps in tangential components on surfaces in $\Omega$.
-Then introduce the discrete weak form.
+You should be careful here. The H(div) functions do not have a
+well defined gradient (and in turn $\varepsilon$). However, for the derivations of
+the continuous problem you don't need H(div). I would derive all the weak forms
+in $V = \left\{ v\in H^1, v\cdot n = \text{on} \Gamma\right\}$. Then in A.2 you say we
+chose spaces $V_h$ which are are not conforming, i.e. it does not hold that $V_h\subset V$.
+Instead you have $V_h\subset H(div)$. Reasons is better mass csrv and as a
+bonus the bcs can be enforced strongly. Note that H(div) functions can have
+jumps in tangential components on surfaces in $\Omega$. Then introduce the discrete weak form.  
 }
-To derive a weak formulation of the Stokes equations~\eqref{eq:appendix_stokes_eqs}, we begin by multiplying~\eqref{eq:BDM_stokes_mom} with a test function $\vv\in\VV$ and integrating over the domain:
+To derive a weak formulation of the Stokes equations~\eqref{eq:appendix_stokes_eqs},
+we begin by multiplying~\eqref{eq:BDM_stokes_mom} with a
+test function $\vv\in\VV$ and integrating over the domain:
 \begin{equation*}
@@
 \end{equation}
-where the symbol : signifies the matrix inner product, $A:B=\text{trace}{(A^TB)}$ for matrices $A, B\in\mathbb{R}^{d\times d}$.
-
-Further steps depend on the boundary conditions applied, which is different for the three model versions we consider.
-Before going through the different model versions, let us introduce some notation used in defining slip boundary conditions.
-We make use of a decomposition
+where the symbol : signifies the matrix inner product,
+$A:B=\text{trace}{(A^TB)}$ for matrices $A, B\in\mathbb{R}^{d\times d}$.
+
+Further steps depend on the boundary conditions applied,
+which is different for the three model versions we consider.
+Before going through the different model versions, let us introduce
+some notation used in defining slip boundary conditions. We make use of a decomposition
 of any vector $\vv$ on the boundary $\Gamma$ into its normal and tangential components,
@@
 \end{equation}
-where $\nn$ is the outer unit normal of the surface.
-Introducing $\hat{\bsig} = \bsig\nn$ for the traction (vector), the forcing due to cilia is represented by constraining $\bsigpar$ on the part of the boundary populated by cilia.
-In particular, we let $\bsigpar = \btau(\xx, \rr) = \tau\lambda(\xx) P_{\nn}(\rr)$, where the parameter $\tau=\num{6.5e-4}$ Pa was used to control the magnitude of the tangential stresses, and chosen by calibrating simulated velocity fields with experimental data~\cite{Olstad2019CiliaryDevelopment}.
+where $\nn$ is the outer unit normal of the surface. Introducing
+$\hat{\bsig} = \bsig\nn$ for the traction (vector), the forcing due
+to cilia is represented by constraining $\bsigpar$ on the part of the
+boundary populated by cilia. In particular, we let
+$\bsigpar = \btau(\xx, \rr) = \tau\lambda(\xx) P_{\nn}(\rr)$,
+where the parameter $\tau=\num{6.5e-4}$ Pa was used to control the magnitude
+of the tangential stresses, and chosen by calibrating simulated velocity
+fields with experimental data~\cite{Olstad2019CiliaryDevelopment}.
 The details of the function $\lambda(\xx)$ follow subsequent to deriving the weak form.
@@
 We choose $\mathbf{r} = \rr^+ = (1, 0, 1)$ or $\mathbf{r} = \rr^- = -(1, 0, 1)$ to impose forces perpendicular to the $y$-axis.
-The reason for this is that all of the experimental images we compare with are taken in the $xz$-plane, rendering flow features in the $y$-direction unobservable.
+The reason for this is that all of the experimental images we compare with are taken in the $xz$-plane,
+rendering flow features in the $y$-direction unobservable.
 Next, we consider the way of handling the stress boundary integral for each model version.
 
-%Note, however, that $\tau$ is not equivalent to the magnitude of $\btau$, since the projection operator~\eqref{eq:projection_operator_appendix} does not necessarily yield a unit vector for an arbitrary vector $\vv$.
-
-\textbf{Model Version I.} This model version has cilia forces as the only mechanism driving flow. We consider the Stokes equations~\eqref{eq:appendix_stokes_eqs} with the slip boundary conditions
+\textbf{Only-cilia/no-cardiac model.} This model version has cilia forces
+as the only mechanism driving flow. We consider the
+Stokes equations~\eqref{eq:appendix_stokes_eqs} with the slip boundary conditions
 \begin{subequations}
@@
 The system~\eqref{eq:stokes_weak_modelA} is thus singular with a one-dimensional nullspace of constant pressures.
-Consequently, assembly of our discretization of the  equations~\eqref{eq:stokes_weak_modelA} into a linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
-To ensure existence of solutions, we orthogonalize the right-hand side vector $\mathbf{b}$ with respect to the pressure nullspace basis (the set of all constants), before solving the linear system.
-To obtain a unique solution, which together with existence renders the problem well-posed, information of the pressure nullspace is passed to the linear solver.
-Let us remark that the singularity is a consequence of the fact that the impermeability condition is assumed to hold on the \emph{entire} domain boundary for this model version, which leaves the pressure under-determined as a result of no boundary condition specifying the pressure.
-
-The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia motion differ for the cilia regions.
-We heuristically determined $\tau$ and $\lambda(\xx)$.
-As noted previously, $\tau=\num{6.5e-4}$ Pa.
-We set $\rr = \rr^+$ and $\rr = \rr^-$ in the ventral and dorsal regions of the diencephalic ventricle, respectively.
-In the ventral region, we set the linear profile $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$, where $[x_{0, v}, x_{e, v}]$ is the $x$-range of the cilia region, so the stresses decrease linearly towards the posterior part of the geometry.
-We impose a linearly increasing profile over the $x$-range $[x_{0, d}, x_{e, d}]$ in the dorsal region: $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$.
+Consequently, assembly of our discretization of the  equations~\eqref{eq:stokes_weak_modelA} into a
+linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
+To ensure existence of solutions, we orthogonalize the right-hand side vector $\mathbf{b}$ with
+respect to the pressure nullspace basis (the set of all constants), before solving the linear system.
+To obtain a unique solution, which together with existence renders the problem well-posed,
+information of the pressure nullspace is passed to the linear solver. Let us remark that
+the singularity is a consequence of the fact that the impermeability condition is assumed
+to hold on the \emph{entire} domain boundary for this model version, which leaves the
+pressure under-determined as a result of no boundary condition specifying the pressure.
+
+The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia
+motion differ for the cilia regions. We heuristically determined $\tau$ and $\lambda(\xx)$.
+As noted previously, $\tau=\num{6.5e-4}$ Pa. We set $\rr = \rr^+$ and $\rr = \rr^-$ in
+the ventral and dorsal regions of the diencephalic ventricle, respectively. In the ventral region,
+we set the linear profile $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$,
+where $[x_{0, v}, x_{e, v}]$ is the $x$-range of the cilia region, so the stresses decrease
+linearly towards the posterior part of the geometry. We impose a linearly increasing profile
+over the $x$-range $[x_{0, d}, x_{e, d}]$ in the dorsal region:
+$\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$.
 \lyng{Put all of this information on $\lambda$ choice in a table.}
 
-In the telencephalic ventricle, we set $\rr=\rr^-$ and $\lambda=\frac{2}{5}$ in the anterior most part of the cilia region, and $\rr=\rr^+$ and $\lambda(\xx)=1$ in the posterior part.
-
-\textbf{Model Version II.} For this model version, the only physical mechanism inducing fluid flow is the cardiac cycle.
+In the telencephalic ventricle, we set $\rr=\rr^-$ and $\lambda=\frac{2}{5}$
+in the anterior most part of the cilia region,
+and $\rr=\rr^+$ and $\lambda(\xx)=1$ in the posterior part.
+
+\textbf{Only-cardiac/no-cilia model.} For this model version,
+the only physical mechanism inducing fluid flow is the cardiac cycle.
 We model the influence of the cardiac cycle with a normal pressure boundary condition:
@@
 
-\textbf{Model Version 0.} This model version, regarded as the baseline model, considers both cilia and cardiac beating as driving mechanisms of fluid flow.
-We therefore consider the boundary conditions
+\textbf{Baseline model.} This model version, regarded as the baseline model, considers both cilia and cardiac beating as driving mechanisms of fluid flow. We therefore consider the boundary conditions
 \begin{subequations}
@@
 
-\subsection{Weak formulation of the advection-diffusion equation}
+\subsection{Weak formulation of the advection-diffusion equation}\label{subsec:adv_diff_eq_weak_form}
 Recall the strong form of the advection-diffusion equation:
@@
 The concentration $c\in W$ and the cerebrospinal fluid velocity $\uu\in\VV$.
-The weak form of~\eqref{eq:adv_diff_strong_DG} is derived by multiplying the equation with a test function $\phi \in W$ and integrating over the domain:
+The weak form of~\eqref{eq:adv_diff_strong_DG} is derived by
+multiplying the equation with a test function $\phi \in W$ and integrating over the domain: 
 \begin{equation*}
     \intO{\pdifft{c}\phi} + \intO{(\nabla\cdot\JJ)\phi} = 0.
-    %\label{eq:adv_diff_weak_DG_1}
 \end{equation*}
@@
 
-\textbf{Model Version I.} We consider $\Omega$ to be closed and with impermeable walls, setting $\JJ\cdot\nn=0$ on $\Gamma$. The weak form is then reduced to
+\textbf{Only-cilia/no-cardiac model.} We consider $\Omega$ to be closed and with impermeable walls, setting $\JJ\cdot\nn=0$ on $\Gamma$. The weak form is then reduced to
 \begin{equation*}
@@
 \begin{equation*}
-    a(c, \phi) = 0, \quad\forall\phi\in W. %\label{eq:adv_diff_weak_formA2}
-\end{equation*}
-
-\textbf{Model Version II.} When using the normal pressure boundary condition~\eqref{eq:modelB_pressure_BC} to model pulsatile flow, we have in- and outflow of cerebrospinal fluid and thus advection of $c$ on the pressure boundary $\Gp$.
+    a(c, \phi) = 0, \quad\forall\phi\in W.
+\end{equation*}
+
+\textbf{Only-cardiac/no-cilia model.} When using the normal pressure boundary condition~\eqref{eq:modelB_pressure_BC} to model pulsatile flow,
+we have in- and outflow of cerebrospinal fluid and thus advection of $c$ on the pressure boundary $\Gp$.
 Let $\Gp=\Gin\cup\Gout$ and $\Gamma = \Gnf\cup\Gin\cup\Gout$, with 
@@
 \end{align*}
-as in- and outflow boundaries, respectively, where we have emphasized that both $\uu$ and $\nn$ are spatially dependent variables. With $\JJ\cdot\nn=0$ on the no-flux boundary $\Gnf$, we have
+as in- and outflow boundaries, respectively, where we have emphasized that
+both $\uu$ and $\nn$ are spatially dependent variables.
+With $\JJ\cdot\nn=0$ on the no-flux boundary $\Gnf$, we have
 \begin{equation*}
@@
 \end{equation*}
-For the outflow boundary integral over $\Gout$, we impose zero diffusive flux $D\nabla c\cdot\nn=0$, with the advection term $c(\uu\cdot\nn)$ simply left in the variational form as an unknown.
+For the outflow boundary integral over $\Gout$, we impose zero diffusive flux $D\nabla c\cdot\nn=0$,
+with the advection term $c(\uu\cdot\nn)$ simply left in the variational form as an unknown.
 For the continuous problem this is problematic, since we are lacking a boundary condition to close the problem. 
-In the discrete setting, however, this method of leaving the boundary term has been shown to yield consistent results~\cite{Papanastasiou1992ACondition, Lynch2020NumericalHemodynamics, Griffiths1997TheCondition}.
-Intuitively, one can think of this outflow boundary condition as setting the advective flux to being the one consistent with the weak form, for which there is a unique $c$ satisfying the equations, with $\uu$ determined by the Stokes equations.
-
-The flux integral over the inflow boundary $\Gin$ cannot be handled in the same way as the method used for $\Gout$, as this would not preserve coercivity of the weak form.
-Lacking experimental data both for the magnitude and origin of an inflow boundary flux, we deal with the inflow boundary in an explicit way that resembles an approximation of a periodic boundary condition.
-At a timestep $n$, when solving the linear system for the concentration $c^{n+1}$ at the next timestep $n+1$, we set the inflow flux $h_{\mathrm{in}}^{n+1} = h_{\mathrm{out}}^{n}$, where the latter is the outflow flux
+In the discrete setting, however, this method of leaving the boundary term has been shown
+to yield consistent results~\cite{Papanastasiou1992ACondition, Lynch2020NumericalHemodynamics,
+Griffiths1997TheCondition}. Intuitively, one can think of this outflow boundary condition as
+setting the advective flux to being the one consistent with the weak form,
+for which there is a unique $c$ satisfying the equations, with $\uu$ determined by the Stokes equations.
+
+The flux integral over the inflow boundary $\Gin$ cannot be handled
+in the same way as the method used for $\Gout$, as this would not preserve
+coercivity of the weak form. Lacking experimental data both for the magnitude and
+origin of an inflow boundary flux, we deal with the inflow boundary in an explicit
+way that resembles an approximation of a periodic boundary condition. At a timestep $n$,
+when solving the linear system for the concentration $c^{n+1}$ at the next timestep $n+1$,
+we set the inflow flux $h_{\mathrm{in}}^{n+1} = h_{\mathrm{out}}^{n}$, where the latter is the outflow flux
 \begin{equation*}
@@
 \end{equation*}
-which means no mass would be added to the system except for at the injection site, which is desired as we endeavor to model the ventricles as a closed system.
-
-Using the introduced approaches of handling the in- and outflow boundaries, the resulting abstract weak formulation for model version II is: find $c\in W$ such that
+which means no mass would be added to the system except for at the injection site,
+which is desired as we endeavor to model the ventricles as a closed system.
+
+Using the introduced approaches of handling the in- and outflow boundaries,
+the resulting abstract weak formulation for model version II is: find $c\in W$ such that
 \begin{equation}
@@
 
-\textbf{Model Version 0.} Since both free-slip and cilia tangential traction boundaries have the same no-flux boundary condition in the advection-diffusion equation, the weak formulation of the advection-diffusion equation for model version 0 is identical to that of model version II, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
+\textbf{Baseline model.} Since both free-slip and cilia tangential traction boundaries have the same no-flux boundary condition in the advection-diffusion equation, the weak formulation of the advection-diffusion equation for model version 0 is identical to that of model version II, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
 

### 2025-02-04 paper/main.tex
redistribute/remove 'Physical parameters' section

@@
 \section*{Introduction}
-Brain development and function depend on numerous regulatory processes, including interactions with cerebrospinal fluid (CSF).
-CSF is a clear liquid produced by the choroid plexus, which is a secretory epithelium located within the brain ventricles.
-Following production, CSF flows through the ventricular system and subarachnoid space, where it regulates brain development and
-homeostasis by transporting growth factors, nutrients, neurotransmitters, waste products and other molecules and metabolites.
-
-To achieve its function, CSF needs to circulate throughout the brain. In fact, CSF disturbances can univocally lead to brain disorders,
+Brain development and function depend on numerous regulatory processes,
+including interactions with cerebrospinal fluid (CSF).
+CSF is a clear liquid produced by the choroid plexus, which is a secretory
+epithelium located within the brain ventricles.
+Following production, CSF flows through the ventricular system and
+subarachnoid space, where it regulates brain development and
+homeostasis by transporting growth factors, nutrients, neurotransmitters,
+waste products and other molecules and metabolites.
+
+To achieve its function, CSF needs to circulate throughout the brain.
+In fact, CSF disturbances can univocally lead to brain disorders,
 such as hydrocephalus where accumulation of CSF requires emergency surgical treatment.
-CSF movement occurs through multiple physiological processes, including the action of motile cilia on the ventricular wall,
-CSF secretion by the choroid plexus and pressure gradients generated by the cardiac cycle, respiration, and bodily movement.
-Motile cilia are microscopic hair-like structures that beat in a metachronal wave pattern to generate flow pattern. Due to their microscopic size, ranging from 6 to 15 microns,
+CSF movement occurs through multiple physiological processes, including the action of
+motile cilia on the ventricular wall,
+CSF secretion by the choroid plexus and pressure gradients generated by the
+cardiac cycle, respiration, and bodily movement.
+Motile cilia are microscopic hair-like structures that beat in a metachronal
+wave pattern to generate flow pattern. Due to their microscopic size, ranging from 6 to 15 microns,
 they contribute to fluid flow primarily at the surface of the brain ventricles.
-In contrast, pressure gradients generate fluid flow further from the ventricular walls and along the perivascular space surrounding the major blood vessels.
-
-To date, it remains poorly understood how cilia contribute to the overall fluid flow and solute transport in the brain.
+In contrast, pressure gradients generate fluid flow further from the ventricular
+walls and along the perivascular space surrounding the major blood vessels.
+
+To date, it remains poorly understood how cilia contribute to the overall fluid
+flow and solute transport in the brain.
 These questions have been especially challenging to tackle due to technical limitations.
-Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz, while other fluid dynamic processes in the brain are slower and span larger three-dimensional volumes.
+Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz,
+while other fluid dynamic processes in the brain are slower and span larger three-dimensional volumes.
 Most studies until now have analyzed one process at a time, especially in mammals.
-For instance, multiple studies have convincingly shown that cilia generate complex flow patterns at the surface of the brain ventricles.
-However, since all these studies have been performed on brain explants, they failed to identify the role of pressure gradients associated with respiration and heart pulsations in CSF transport.
-Similarly, while MRI technology can measure CSF movement in humans, it cannot detect the fast movements of cilia or understand their impact in the large human brain.
-Consequently, we lack a comprehensive understanding of how cilia contribute to CSF movement and solute transport, and whether cilia dysfunction will alter CSF distribution and lead to brain disorders.
-This is particularly important since ventricular enlargement or hydrocephalus is commonly observed in animal models with motile cilia deficiency, potentially affecting brain activity and behavior.
-
-The technical limitations of studying cilia-mediated flow and transport opens the possibility of mathematical modeling and computational investigations. Cilia have been studied previously,
-with numerous studies on the interaction between single or several cilia and surrounding fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids, Cui2019NumericalMethod, Cui2022AFlow}.
-Others considered applications such as ciliary transport of mucous in airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
-propulsion and locomotion of ciliated organisms~\cite{BLAKE1974MechanicsMotion, Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella},
-coral reefs~\cite{Pacherres2022CiliaryProduction}, and the brain~\cite{Siyahhan2014FlowVentricles, Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
+For instance, multiple studies have convincingly shown that cilia generate complex
+flow patterns at the surface of the brain ventricles.
+However, since all these studies have been performed on brain explants, they failed
+to identify the role of pressure gradients associated with respiration and heart pulsations in CSF transport.
+Similarly, while MRI technology can measure CSF movement in humans, it cannot detect
+the fast movements of cilia or understand their impact in the large human brain.
+Consequently, we lack a comprehensive understanding of how cilia contribute to CSF
+movement and solute transport, and whether cilia dysfunction will alter CSF distribution
+and lead to brain disorders.
+This is particularly important since ventricular enlargement or hydrocephalus is
+commonly observed in animal models with motile cilia deficiency, potentially affecting
+brain activity and behavior.
+
+The technical limitations of studying cilia-mediated flow and transport opens the
+possibility of mathematical modeling and computational investigations. Cilia have been studied previously,
+with numerous studies on the interaction between single or several cilia and surrounding
+fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids,
+Cui2019NumericalMethod, Cui2022AFlow}.
+Others considered applications such as ciliary transport of mucous in
+airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
+propulsion and locomotion of ciliated organisms~\cite{BLAKE1974MechanicsMotion,
+Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella},
+coral reefs~\cite{Pacherres2022CiliaryProduction}, and the brain~\cite{Siyahhan2014FlowVentricles,
+Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
 These studies have provided valuable insights, showing that cilia lend themselves to simulation studies.
 
-In this study, we combined computational and experimental approaches to investigate the role of motile cilia in CSF flow and solute transport.
-First, we computed flow patterns and intraventricular transport \emph{in silico}. To this end, we used the geometry of the zebrafish larval brain ventricles,
-for which we have detailed knowledge of cilia properties and CSF movement velocities and frequencies.
-Notably, this early developmental stage allows us to simplify our model by omitting CSF secretion, which starts at later stages, while still being well-conserved with mammals.
-Next, we validated our computation model with experimental data by monitoring the dynamics of a photoconvertible fluorescent protein expressed within the brain ventricles.
-Our results show that diffusion plays a major role in the transport of small solutes, whereas cilia majorly contribute to the movement of larger particles.
-We also found that the location of cilia, as well as the ventricular geometry, greatly impact solute distribution.
-Altogether, our work presents a computational framework together with new concepts of how cilia
-collaborate with other factors to distribute molecules and particles within the brain ventricles.
+In this study, we combined computational and experimental approaches to investigate
+the role of motile cilia in CSF flow and solute transport.
+First, we computed flow patterns and intraventricular transport \emph{in silico}. To
+this end, we used the geometry of the zebrafish larval brain ventricles,
+for which we have detailed knowledge of cilia properties and CSF movement velocities
+and frequencies. Notably, this early developmental stage allows us to simplify our model
+by omitting CSF secretion, which starts at later stages, while still being well-conserved with mammals.
+Next, we validated our computation model with experimental data by monitoring
+the dynamics of a photoconvertible fluorescent protein expressed within the brain ventricles.
+Our results show that diffusion plays a major role in the transport of small solutes,
+whereas cilia majorly contribute to the movement of larger particles.
+We also found that the location of cilia, as well as the ventricular geometry, greatly
+impact solute distribution. Altogether, our work presents a computational
+framework together with new concepts of how cilia
+collaborate with other factors to distribute molecules and
+particles within the brain ventricles.
 
@@
 \subsection*{Image-based computational geometries of zebrafish brain ventricles}
-To model flow and transport in zebrafish larval brain ventricles, we generated a 3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
+To model flow and transport in zebrafish larval brain ventricles, we generated a
+3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
 injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
@@
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
-The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). 
+The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
+maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). 
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
@@
 Parts of the ventricular surfaces were marked to be lined with
-motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:figure1}d, pink markers).
+motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:figure1}d, magenta markers).
 \begin{figure}%[hbt!]
@@
     \includegraphics[width=\linewidth]{graphics/figure1.png}
-    \caption{\lyng{Experimenting with velocity colorbars, thoughts on the two options? Or have two separate as it is now?}}
+    \caption{\lyng{Experimenting with velocity colorbars, thoughts on the
+    two options? Or have two separate as it is now?}}
     \label{fig:figure1}
@@
 
-The morphology and geometry of the brain ventricles vary across zebrafish individuals, and under physiological and pathological conditions. 
-Motivated by an interest in how geometry impacts solute distribution, we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, 
+The morphology and geometry of the brain ventricles vary across zebrafish
+individuals, and under physiological and pathological conditions. 
+Motivated by an interest in how geometry impacts solute distribution,
+we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, 
 the middle ventricle, the mid-hind brain connection, and all three simultaneously. 
@@
 \subsection*{Computational CSF dynamics}
-The beating motion of the cilia generates CSF flow with steady rotational structures~\cite{Olstad2019CiliaryDevelopment}
+The beating motion of the cilia generates CSF flow with steady rotational
+structures~\cite{Olstad2019CiliaryDevelopment}
 within the brain ventricles (\Cref{fig:figure1}a--c).
@@
 Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
-and $\mu=6.97\times 10^{-4}$ Pa is the dynamic viscosity of the CSF.
+and $\mu=6.97\times 10^{-4} \ \mathrm{Pa\cdot s}$ is the dynamic viscosity
+of the CSF~\cite{Bloomfield1998EffectsFluid}.
 We introduce the tangential traction $\bsigpar$ as the
@@
 We consider three types of boundary conditions:
-(i) \emph{tangential traction} (no flow normal to the boundary $\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
-(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
-and (iii) \emph{free slip} (no flow normal to the boundary $\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
+(i) \emph{tangential traction} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
+the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
+and (iii) \emph{free slip} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
+Unless noted otherwise, the free-slip condition is applied on the
+boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
+
+To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
+we consider the following computational flow scenarios,
+each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
+\begin{itemize}
+    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
+    contributions both from the cilia forces and the cardiac pulsations.
+    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
+    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0
+
+    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
+    cilia forces but no cardiac pulsations.
+    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
+    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I
+
+    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
+    cardiac pulsations but no cilia forces.
+    Here, we set the tangential traction to zero on the cilia boundary
+    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
+    anterior/posterior boundary $\Gp$.  % Model II
+\end{itemize}
 
 \subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:figure1}d),
-we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces of the cilia acting on the CSF.
+On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:figure1}d, magenta markers),
+we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
+of the cilia acting on the CSF.
 We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
-and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by heuristic
+and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
+cilia region (see~\Cref{subsec:appendixA1}).
+Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by 
 model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
+The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
+$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
+In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
+We calibrated $\tau$ heuristically by comparing these experimental velocity values
+with the simulated, maximum velocity magnitude.
 
@@
 To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
-$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the boundary $\Gp$~(\Cref{fig:figure1}d, blue markers).
+$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
+boundary $\Gp$~(\Cref{fig:figure1}d, blue markers).
+Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
+the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
 The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow,
 and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-The angular cardiac frequency $\omega=2\pi f=6.97$ rad/s was set based on a measured cardiac frequency of $f=2.22$ Hz.
+Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
+Particle tracking data of pulsatile motion was used to determine the contributions of the
+cardiac pulsations to the velocity magnitude,
+as compared to the effect of cilia motion on the flow (see~\Cref{sec:appC_particle_transport}).
 
@@
 At the anterior/posterior boundary, we permit the solute concentration to be advected into
-and out of the domain in a manner that ensures conservation of mass (see~\Cref{subsec:adv_diff_eq_weak_form} for details).
-
-To computationally represent protein photoconversion in a region $\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1), we prescribe a given time-dependent value to the solute concentration in this region.
-Mimicking the experimental protocol, we consider the dorsal part of the diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
-\begin{equation}
-  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}}
-  \qquad \xx \in \Omega_{\mathrm{pc}}, \quad \fixme{t > 0}.
+and out of the domain in a manner that ensures conservation of mass
+(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
+
+To computationally represent protein photoconversion in a region
+$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
+we prescribe a given time-dependent value to the solute concentration in this region. 
+Mimicking the experimental protocol, we consider the dorsal part of the
+diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
+\begin{equation}
+  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
+  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
 \label{eq:photoconversion_curve}
 \end{equation}
-The value $a=65$ was chosen to fit the fluorescence intensity curve observed in the physical photoconversion experiments.
+The value $a=65$ was chosen to fit the fluorescence intensity curve
+observed in the physical photoconversion experiments.
 
 \subsection*{Estimation of diffusion coefficients via the Stokes-Einstein relation}
-Motivated by an interest in molecules that are significant in neural development, we study the transport of molecules resembling Dendra2 Fluorescent Protein (Dendra2), Starmaker+Green Fluorescent Protein (STM+GFP) and Exosomes.
-To estimate the diffusion coefficients of these, when and if not available in the literature, we use the Stokes--Einstein relation:
+Motivated by an interest in molecules that are significant in neural development,
+we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
+used in this study, the Starmaker+Green Fluorescent Protein (STM+GFP) reported in
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and Exosomes.
+To estimate the diffusion coefficients of these, when and if not
+available in the literature, we use the Stokes--Einstein relation:
 \begin{equation}
@@
 \end{equation}
-which is an expression for the diffusion coefficient of a spherical molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
-In~\eqref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant, $T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the solvent (in this case the CSF), and $R$ is the radius of the molecule.
-For the exosomes, we calculate $D$ using~\eqref{eq:D_stokes_einstein} with $R=200$ nm.
-This radius covers the slowest diffusing exosomes, since the smaller exosomes would have diffusion coefficients similar to the other molecules.
-For STM+GFP, we estimated the diffusion coefficient by extrapolating the experimentally observed diffusion coefficient of GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein}, $D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations are summarized in \Cref{tab:diff_coeff_table}.
+which is an expression for the diffusion coefficient of a spherical
+molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
+In~\eqref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
+$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
+solvent (in this case the CSF), and $R$ is the radius of the molecule.
+For the exosomes, we calculate $D$ using~\eqref{eq:D_stokes_einstein}
+with $R=200$ nm. This radius covers the slowest diffusing exosomes,
+since the smaller exosomes would have diffusion coefficients similar to the other molecules.
+For STM+GFP, we estimated the diffusion coefficient by extrapolating
+the experimentally observed diffusion coefficient of
+GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein},
+$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
+The resulting diffusion coefficients used in the simulations
+are $D_1$ (Exosomes), $D_2$ (STM+GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
 
@@
         \midrule 
-        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight} & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
-        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM+GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{5.75e-11}$ & * \\
+        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
+        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
+        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
+        STM+GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{5.75e-11}$ & * \\
         Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
@@
     \end{tabular}
-    \caption{Molecular mass and diffusion coefficients of simulated solutes. STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-    (*) The value was extrapolated based on the value of $D$ for GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-    assuming that $D$ scales with the cube root of the molecule mass. (\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
+    \caption{Molecular mass and diffusion coefficients of simulated solutes.
+    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+    (*) The value was extrapolated based on the value of $D$ for
+    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+    assuming that $D$ scales with the cube root of the molecule mass.
+    (\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
     \label{tab:diff_coeff_table}
@@
 
-\subsection*{Physical parameters}
-The CSF density $\rho$ and dynamic viscosity $\mu$ were set following Bloomfield \textit{et al.}~\cite{Bloomfield1998EffectsFluid}~(\Cref{tab:parameter_table}).
-We considered large, medium and small-sized molecules by three different diffusion coefficients $D_1, D_2$ and $D_3$ (\Cref{tab:parameter_table}).
-Experimental data~\cite{Olstad2019CiliaryDevelopment} indicate \fixme{velocities} proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and $2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the diencephalic ventricle, respectively.
-In the telencephalic ventricle, the velocities were estimated at $4.7 \pm 1.3$ \textmu m/s.
-We calibrated $\tau$ and $A$ heuristically by comparing these experimental velocity values with the simulated, maximum velocity magnitude.
-In addition, particle tracking data of pulsatile motion was used in the calibration process to determine the relative contributions of the cardiac pulsations, as compared to the cilia-driven flow, to the velocity magnitude.
-\mer{MER: What velocities?
-Net velocities?
-Velocity magnitude aka speed?
-Also, haven't you said this part about the experimental data already?
-Either place the details there, or all here.
-I suggest there.}
-\mer{MER: I suggest you introduce parameter values when introduced, and move the parts relevant for cilia/cardiac flow to where you mentioned it first, and then merge this section with the Estimation of diffusion ....
-Then remove this section and \Cref{tab:parameter_table}.}
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{lcccc}
-    \toprule
-        Parameter & Symbol & Value & Unit & Reference \\
-        \midrule
-        Fluid density & $\rho$ & $1000$ & $\mathrm{kg/m^3}$ & \cite{Bloomfield1998EffectsFluid} \\
-        Dynamic viscosity & $\mu$ & $\num{6.97e-04}$ & $\mathrm{Pa\cdot s}$ & \cite{Bloomfield1998EffectsFluid} \\
-        Cardiac frequency & $f$ & 2.22 & Hz &  \cite{Olstad2019CiliaryDevelopment}\\
-        Angular cardiac frequency & $\omega = 2\pi f$ & 6.97 & rad/s & \cite{Olstad2019CiliaryDevelopment}\\
-        Cilia tangential traction & $\tau$ & \num{6.5e-04} & Pa & * \\
-        Pressure amplitude & $A$ & \num{1.5e-03} & Pa & * \\
-        Exosome diffusion coefficient & $D_1$ & $\num{1.63e-12}$ & $\mathrm{m^2/s}$ & \textdagger\\
-        STM+GFP diffusion coefficient  & $D_2$ & $\num{5.75e-11}$ & $\mathrm{m^2/s}$ & \textdagger\\
-        Dendra2 diffusion coefficient  & $D_3$ & $\num{1.15e-10}$ & $\mathrm{m^2/s}$ & \textdagger\\
-    \bottomrule
-    \end{tabular}
-    \caption{Physical parameters of the flow and transport models.
-    (*) Calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-    (\textdagger) Estimated based on experimental
-    data~\cite{GuraSadovsky2017MeasurementExpansion, Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells}.}
-    \label{tab:parameter_table}
-\end{table}
-
 \subsection*{Computational flow modelling scenarios}
-To study the impact of the motile cilia and the cardiac pulsations on the CSF flow, we consider the following computational flow scenarios, each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
-\begin{itemize}
-    \item A \emph{baseline} flow model representing a wild-type zebrafish including contributions both from the cilia forces and the cardiac pulsations.
-    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0
-
-    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the cilia forces but no cardiac pulsations.
-    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$, and \mer{XXX on the anterior/posterior boundary $\Gp$.} % Model I
-
-    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the cardiac pulsations but no cilia forces.
-    Here, we set the tangential traction to zero on the cilia boundary $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$.  % Model II
-\end{itemize}
 

### 2025-02-04 paper/main.tex
Results 1

@@
 
-\mer{MER: @Halvor I suggest you move these two paragraphs into their respective Results sections (Results 2 and 5). Putting the bullet points above at the end of the Stokes equations is a great idea!}
-When simulating transport of solute in the ventricles, we consider the same six different regions of interest that were considered in the photoconversion experiments.
-In region number one (the photoconversion region), we use the function~\eqref{eq:photoconversion_curve} to enforce the concentration such that it represents the experimental data of photoconversion of proteins.
-We consider the three different diffusion coefficients introduced in previous sections to simulate and compare results for transport of molecules of varying sizes.
-
-To simulate transport in the pathological case of region-specific cilia absence, we consider three scenarios where we modify the boundary conditions of the CSF flow model.
-The cilia tangential stress boundary condition for the boundary where we remove cilia is changed to a free-slip boundary condition,
-prescribing zero tangential forces to represent absence of cilia motion in the region where we consider cilia removal.
-We consider removal of cilia in the three separate cilia-covered regions of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle,
+\mer{MER: @Halvor I suggest you move these two paragraphs into their respective
+Results sections (Results 2 and 5).}
+When simulating transport of solute in the ventricles,
+we consider the same six different regions of interest that were
+considered in the photoconversion experiments.
+In region number one (the photoconversion region),
+we use the function~\eqref{eq:photoconversion_curve} to enforce
+the concentration such that it represents the experimental data
+of photoconversion of proteins. We consider the three different diffusion
+coefficients introduced in previous sections to simulate and compare results
+for transport of molecules of varying sizes.
+
+To simulate transport in the pathological case of region-specific cilia absence,
+we consider three scenarios where we modify the boundary conditions of the CSF flow model.
+The cilia tangential stress boundary condition for the boundary where we
+remove cilia is changed to a free-slip boundary condition,
+prescribing zero tangential forces to represent absence of cilia motion
+in the region where we consider cilia removal.
+We consider removal of cilia in the three separate cilia-covered regions
+of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle,
 and the ventral part of the diencephalic ventricle~(\Cref{fig:figure1}d).
-For the three scenarios, we simulate CSF flow modeled by the Stokes equations~\eqref{eq:stokes_eqs} with the modified boundary conditions,
+For the three scenarios, we simulate CSF flow modeled by the Stokes
+equations~\eqref{eq:stokes_eqs} with the modified boundary conditions,
 and use the resulting velocity field in transport simulations.
@@
 \end{equation}
-in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$) as functions of time, where $|\Omega_i|$ is the volume of the domain $\Omega_i$.
-The dynamics of ROI 1 follows directly from~\eqref{eq:photoconversion_curve}.
-In addition, we report time-to-threshold: the time $\hat{t}_i$ when the mean concentration $\cbar_i$ first exceed a threshold value $\hat{c}_i$.
-We use $\hat{c}_i=0.25$ for ROI 1--4 and $\hat{c}_i=0.10$ for ROI 5--6.
-
-To evaluate the relative importance of advection and diffusion as transport mechanisms, we consider the Péclet number
-\begin{equation*}
-    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}} = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
-\end{equation*}
-Here, $L_p$ and $U_p$ are characteristic length and velocity scales, respectively, and $D$ is the solute diffusion coefficient.
-\fixme{Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection, and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
-As a length scale $L_p$, we choose the approximate length of the ventricles geometry in the $x$-direction, $L_p=600$ \textmu m.
+in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
+as functions of time, where $|\Omega_i|$ is the volume of
+the domain $\Omega_i$. The dynamics of ROI 1 follows directly
+from~\eqref{eq:photoconversion_curve}. In addition,
+we report time-to-threshold: the time $\hat{t}_i$ when
+the mean concentration $\cbar_i$ first exceed a threshold
+value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
+$\hat{c}_i=0.10$ for ROI 5--6.
+
+To evaluate the relative importance of advection and
+diffusion as transport mechanisms, we consider the Péclet number
+\begin{equation*}
+    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
+    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
+\end{equation*}
+Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
+and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
+Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
+respectively, and $D$ is the solute diffusion coefficient.
+In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
+ventricles geometry along the rostrocaudal ($x$-) axis.
 We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
@@
 \end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle.}
-
-To assess the assumption that the CSF flow is governed by the Stokes equations, we also compute the Reynolds number
+and then averaging $\overline{u}$ in time over one cardiac cycle. To assess the assumption that the CSF flow is governed by the Stokes equations,
+we also compute the Reynolds number
 \begin{equation*}
@@
 
-The Stokes equations~\eqref{eq:stokes_eqs} are discretized with a finite element method in space, while in time, we employ a first-order implicit Euler discretization.
+The Stokes equations~\eqref{eq:stokes_eqs} are discretized with a finite element method
+in space, while in time, we employ a first-order implicit Euler discretization.
 We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
 For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
-The BDM elements have degrees of freedom associated with integral moments of the velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems}, thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
-We impose the boundary conditions for both the tangential traction $\bsigpar$ and the normal pressure $\Tilde{p}(t)$ weakly.
+The BDM elements have degrees of freedom associated with integral moments of the
+velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems},
+thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
+We impose the boundary conditions for both the tangential traction $\bsigpar$ and
+the normal pressure $\Tilde{p}(t)$ weakly.
 For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
 The resulting total number of degrees of freedom at each time step is 943 820.
-\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming but stable discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-The discretization includes a penalty parameter $\gamma$ which needs to be chosen large enough to ensure stability of the finite element method. We set $\gamma=10$.}
-Since the divergence of the velocity is a subspace of the pressure space for this scheme, the divergence-free condition of the velocity is satisfied exactly on each element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
+\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
+discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
+To ensure stability of the scheme, continuity in tangential velocities on interior facets
+is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.}
+Since the divergence of the velocity is a subspace of the pressure space for this scheme,
+the divergence-free condition of the velocity is satisfied exactly on each
+element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
 
 \subsection*{Numerical approximation of the advection-diffusion equation}
-The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized with a first-order implicit Euler method in time, and a first-order,
-symmetric interior penalty discontinuous Galerkin (DG) method in space~\cite{Arnold1982AnElements}.
-To accurately approximate the solute concentrations even in the presence of strong advection (high Péclet numbers), we use an upwind scheme for the velocity when calculating the advective flux~\cite{Patankar2018NumericalFlow}.
-As for the flow equations, we use a timestep size of $\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles, with a final time of simulation $T = 856$ s.
+The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized
+with a first-order implicit Euler method in time, and a first-order,
+symmetric interior penalty discontinuous Galerkin (DG)
+method in space~\cite{Arnold1982AnElements}.
+To accurately approximate the solute concentrations even
+in the presence of strong advection (high Péclet numbers),
+we use an upwind scheme for the velocity when calculating the
+advective flux~\cite{Patankar2018NumericalFlow}.
+As for the flow equations, we use a timestep size of
+$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
+with a final time of simulation $T = 856$ s.
 A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
@@
 \subsection*{Solution strategy and software implementation}
-Because of the one-way coupling between the velocity field $\uu$ and the concentration $c$, the governing equations for the CSF flow and the concentration can be solved sequentially when modeling solute transport.
-\fixme{For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state.} In this case, we first solve the \fixme{steady-state} Stokes equations~\eqref{eq:stokes_eqs} for $\uu$ and $p$,
-and then use the velocity field $\uu$ as input when solving the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
-For the other flow scenarios, the Stokes equations are solved for one period of the pulsatile cardiac motion.
-The solution of this one period is then used periodically as input for the advection-diffusion equation.
-
-The numerical solution schemes for the Stokes equations and the advection-diffusion equation were implemented and solved numerically with DOLFINx,
-the Python interface of the finite element software FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
-A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the linear systems resulting from the discretized Stokes equations.
-For the discretized advection-diffusion equation, we used an iterative linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen}.
-Numerical experiments verified the accuracy of the model implementation (\Cref{sec:appB_verification}). The simulation code is openly available~\cite{zenodo-link-to-all-code}.
+Owing to the one-way coupling between the velocity field $\uu$
+and the concentration $c$, the governing equations for the
+CSF flow and the concentration can be solved sequentially when modeling solute transport.
+\fixme{For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state.}
+In this case, we first solve the \fixme{steady-state} Stokes equations~\eqref{eq:stokes_eqs}
+for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
+the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
+For the other flow scenarios, the Stokes equations are solved for one
+period of the pulsatile cardiac motion. The solution of this one period
+is then used periodically as input for the advection-diffusion equation.
+
+The numerical solution schemes for the Stokes equations and the
+advection-diffusion equation were implemented and solved numerically with DOLFINx,
+the Python interface of the finite element software
+FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with
+petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
+A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
+linear systems resulting from the discretized Stokes equations.
+For the discretized advection-diffusion equation, we used an iterative
+linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
+preconditioning~\cite{Jacobi1845UeberGleichungen}.
+Numerical experiments verified the accuracy of the model implementation
+(\Cref{sec:appB_verification}). The simulation code is openly
+available~\cite{zenodo-link-to-all-code}.
 
@@
 \subsection*{Zebrafish maintenance and strains in photoconversion experiments}
-The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the Norwegian Food Safety Authority (NFSA, Mattilsynet).
-The zebrafish were maintained in accordance with the guidelines set by the NFSA and the European Communities Council Directive.
-
-The larval and adult zebrafish were raised under standard husbandry conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
-The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a 14/10 hr light/dark cycle.
-From fertilization to 3 dpf, larvae were maintained in egg water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
-and subsequently transferred to artificial fish water (AFW) (1.2 g marine salt in 20 L RO water).
-The zebrafish lines used in the experiments were \emph{ccdc103(dnaaf19)\textsuperscript{tn222a}} (\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
-and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures}, \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
-Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
-
-Wholemount~\emph{in vivo} live imaging and photoconversion experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
-\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2}) adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
-Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+}) or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
+The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
+Norwegian Food Safety Authority (NFSA, Mattilsynet).
+The zebrafish were maintained in accordance with the guidelines set by the
+NFSA and the European Communities Council Directive.
+
+The larval and adult zebrafish were raised under standard husbandry
+conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
+The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a
+14/10 hr light/dark cycle.
+From fertilization to 3 dpf, larvae were maintained in egg
+water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
+and subsequently transferred to artificial fish water (AFW)
+(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
+\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
+(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
+and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
+\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
+Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
+(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
+
+Wholemount~\emph{in vivo} live imaging and photoconversion
+experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
+\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
+adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
+or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
 The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
@@
 \subsection*{Genotyping of adult zebrafish}
-Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA, tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
-To stop the lysis reaction, the samples were heated to 95°C for 10 minutes and then centrifuged at 13000 rpm for 2 minutes.
+Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
+fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
+tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
+To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
+and then centrifuged at 13000 rpm for 2 minutes.
 The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14 $\mu$L of assay mix; 1.86 $\mu$L of RO water.
+The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was
+used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
+For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14
+$\mu$L of assay mix; 1.86 $\mu$L of RO water.
 
@@
 \lyng{Needs a more understandable title.}
-The open reading frame (ORF) of the neuropeptide y (npy) signal peptide (\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal of zebrafish codon optimized Dendra2 DNA sequence.
-The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and 3’ ends (GenScript Biotech),
-and inserted into the pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish} through restriction enzyme cloning (GenScript Biotech).
+The open reading frame (ORF) of the neuropeptide y (npy) signal peptide
+(\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal
+of zebrafish codon optimized Dendra2 DNA sequence.
+The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
+3’ ends (GenScript Biotech), and inserted into the
+pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
+through restriction enzyme cloning (GenScript Biotech).
 
 To generate the transgenic line, the 5xuas:Signal-Dendra2 plasmid DNA was used.
-A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg) was microinjected into one-cell stage embryos,
-as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected embryos were raised to adulthood (F0).
-Germline-transmitted founder zebrafish were identified by breeding with multiple Gal4 transgenic lines.
-Stable F1 embryos expressing the Gal4-driven Dendra2 signals were screened and raised to adult zebrafish.
+A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
+was microinjected into one-cell stage embryos,
+as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
+embryos were raised to adulthood (F0).
+Germline-transmitted founder zebrafish were identified by breeding with
+multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
+Dendra2 signals were screened and raised to adult zebrafish.
 
 \subsection*{Wholemount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
-Two dpf larval zebrafish were anesthetized in 0.013\% MS222 (Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
-to obtain a lateral view of the brain ventricles. After the fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
-After solidification, AFW containing 0.013\% MS222 was added, and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
-and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat) at room temperature.
-
-The time-lapse images were acquired in a single plane, covering the telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
-with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
-The first 10 images were scanned without photoconversion to obtain a baseline value of fluorescence intensity, and the next 290 images were scanned while performing photoconversion.
-
-For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software were used. A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel)
-of the dorsoposterior diencephalic ventricle with 100\% laser power. The laser was illuminated in the area repeatedly between each scanning.
+Two dpf larval zebrafish were anesthetized in 0.013\% MS222
+(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
+mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
+to obtain a lateral view of the brain ventricles. After the
+fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
+After solidification, AFW containing 0.013\% MS222 was added,
+and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
+and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
+at room temperature.
+
+The time-lapse images were acquired in a single plane, covering the
+telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
+with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
+of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
+The first 10 images were scanned without photoconversion to obtain a
+baseline value of fluorescence intensity, and the next 290 images were
+scanned while performing photoconversion.
+
+For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software
+were used. A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel)
+of the dorsoposterior diencephalic ventricle with 100\% laser power.
+The laser was illuminated in the area repeatedly between each scanning.
 After imaging, the fish health was checked and only data from healthy fish were analyzed.
-Data were collected and analyzed from three separate experiments, with a total of 8 controls and 6 mutants.
+Data were collected and analyzed from three separate experiments,
+with a total of 8 controls and 6 mutants.
 
 \subsection*{Photoconversion data analysis}
-All data analysis was performed in MATLAB and the codes are available in the repository of this article: \url{repo-link}.
-
-Following import of the image data, the photoconverted channel was aligned to correct for drift
-in $x,y$ directions using previously developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}. Only stable recordings were further analyzed. 
-To increase the signal to noise ratio, the images were downsampled by a block average using a resampling factor of 6 (using the MATLAB function blockproc).
-The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as $\Delta F$$)$ was calculated for each pixel at each time point of the data.
-Here, the value $F_0$ is the average fluorescence intensity for the baseline (the first 10 time-lapse images) acquired before photoconversion.
-
-To identify the time needed to pass a certain threshold value, $\Delta F$ values were first smoothened.
-The first timepoint when values surpassed the threshold was reported per pixel (in the downsampled images).
-A mask for the image was generated using the green (not photoconverted) channel and calculated on the block-averaged data based on the intensity being higher than 1.5x median intensity of all the frames.
-
-To obtain $\Delta F$ values for a region of interest (ROI), ROIs were first drawn on the aligned and block-averaged time series.
-Six ROIs were drawn manually: ROI 1 around the location of photoconversion, and ROIs 2--6 in different regions of the ventricular system.
-The pixel values of the fluorescence intensity within one ROI were averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
-To normalize the data with respect to photoconversion efficiency, the $\Delta F$ curves for all ROIs were divided by the $\Delta F$ values obtained for ROI 1 at the end of the experiment,
-so that $\Delta F$ values for the photoconverted site ROI 1 ranged from zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
+All data analysis was performed in MATLAB and the codes are available in
+the repository of this article: \url{repo-link}.
+
+Following import of the image data, the photoconverted channel
+was aligned to correct for drift in $x,y$ directions using previously
+developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
+Only stable recordings were further analyzed. 
+To increase the signal to noise ratio, the images were downsampled by
+a block average using a resampling factor of 6 (using the MATLAB function blockproc).
+The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
+$\Delta F$$)$ was calculated for each pixel at each time point of the data.
+Here, the value $F_0$ is the average fluorescence intensity for the
+baseline (the first 10 time-lapse images) acquired before photoconversion.
+
+To identify the time needed to pass a certain threshold value,
+$\Delta F$ values were first smoothened.
+The first timepoint when values surpassed the threshold was reported
+per pixel (in the downsampled images).
+A mask for the image was generated using the green (not photoconverted)
+channel and calculated on the block-averaged data based on the intensity
+being higher than 1.5x median intensity of all the frames.
+
+To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
+first drawn on the aligned and block-averaged time series.
+Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
+and ROIs 2--6 in different regions of the ventricular system.
+The pixel values of the fluorescence intensity within one ROI were
+averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
+To normalize the data with respect to photoconversion efficiency, the
+$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
+obtained for ROI 1 at the end of the experiment,
+so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
+zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
 We report these mean values together with a one-standard deviation error band.
@@
 \subsection*{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Cref{fig:figure1}b, c, we carried out particle tracking in a larval zebrafish injected with fluorescent beads.
-As described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment}, anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
-(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
-dissolved in artificial CSF. Artificial CSF composition was as follows: 124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
-1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3}, 2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
-The needles used for the injections were pulled with a Sutter Instrument Co. Model P-2000 from thin-walled glass capillaries (1.00 mm; VWR) and cut open with a forceps.
-A volume of 1 nl of the solution was injected with a pressure injector (Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
+To recover the flow fields shown in~\Cref{fig:figure1}b, c, we carried out
+particle tracking in a larval zebrafish injected with fluorescent beads.
+As described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment},
+anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
+(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
+in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
+dissolved in artificial CSF. Artificial CSF composition was as follows:
+124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
+1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
+2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
+The needles used for the injections were pulled with a
+Sutter Instrument Co. Model P-2000 from thin-walled glass
+capillaries (1.00 mm; VWR) and cut open with a forceps.
+A volume of 1 nl of the solution was injected with a pressure injector
+(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
 The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
 
-Following injection, the zebrafish was directly placed under the confocal microscope and 1200 images were acquired at a frequency of 13.1 Hz.
-A single optical section was obtained. Particle tracking was done using TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
-and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}. The parameters for TrackMate were as follows.
-The DoG detector was used with the settings: threshold: 2.0, with median filtering; radius: 2.0, with subpixel localization.
-Next, the Simple LAP tracker was used with settings: max frame gap: 2; alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
-splitting max distance: 15.0; allow gap closing: true; allow track splitting: false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
-Only the particle tracks with at least 30 data points, while simultaneously covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:figure1}b, c.
+Following injection, the zebrafish was directly placed under the confocal
+microscope and 1200 images were acquired at a frequency of 13.1 Hz.
+A single optical section was obtained. Particle tracking was done using
+TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
+and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
+The parameters for TrackMate were as follows.
+The DoG detector was used with the settings: threshold: 2.0, with
+median filtering; radius: 2.0, with subpixel localization.
+Next, the Simple LAP tracker was used with settings: max frame gap: 2;
+alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
+splitting max distance: 15.0; allow gap closing: true; allow track splitting:
+false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
+Only the particle tracks with at least 30 data points, while simultaneously
+covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:figure1}b, c.
 
 %%--------------RESULTS--------------%%
-\section*{Results}\label{sec:results}
+\section*{Results}
 
@@
 
-\mer{One sentence on why? - what do we not know - what do we try to
-  find out?} \mer{@Halvor: If you want, try to revamp this paragraph
-  as suggested by Nathalie. First cilia. Then pulsatile. Then
-  combined.} To characterize CSF flow patterns predicted by
+We seek to model the compartimentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:figure1}b--c).
+To characterize CSF flow patterns predicted by
 computational fluid dynamics within the brain ventricles, we begin by
-considering the simulated CSF velocity and pressure when driven by
-both cilia motion and cardiac pressure pulsations. These forces induce
-\fixme{persistent} flow features, with vortex-structures in the
-anterior and middle ventricles and \fixme{unidirectional} flow in the
-posterior ventricle (\Cref{fig:figure1}e,
+considering the simulated CSF velocity and pressure when only considering
+cilia motion, disregarding cardiac pressure pulsations. The
+bidirectional traction induced by the motile cilia
+inherently leads to a partial compartmentalization of the ventricular
+system, with large-scale vortex structures in the anterior and middle
+ventricles~(\Cref{fig:figure1}e). The highest velocities ($26.5$ \textmu m/s)
+occur in the vicinity of the dorsal cilia in the middle ventricle.
+
+To examine the effect of cardiac pressure pulsations,
+we next consider a no-cilia model variation. In this scenario, the simulated CSF
+flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:figure1}g),
+with a peak velocity magnitude of $4.8$ \textmu m/s. At each time instant, the flow
+is unidirectional, with CSF initially flowing rostrocaudally (positive $x-$axis) before changing
+direction to caudorostral in the middle of the cardiac cycle.
+
+We now consider the baseline model, simulating flow driven by both cilia
+and cardiac pulsations. We observe \fixme{persistent} flow features,
+with vortex-structures in the anterior and middle ventricles
+and directional flow in the posterior ventricle (\Cref{fig:figure1}e,
 \fixme{Supplementary video 1}). These characteristic patterns suggest
@@
 result of both the traction induced by the cilia and the pulsatile
-pressure-driven flow being aligned with the rostrocaudal ($x-$)
-axis. Using this maximum velocity magnitude and choosing the height of
+pressure-driven flow being aligned with the rostrocaudal 
+axis. Using the observed maximum velocity magnitude and choosing the height of
 the middle ventricle ($110$ \textmu m) as a characteristic length
 scale, yields a Reynolds number $\mathrm{Re} \approx 0.004$,
-justifying the assumption of Stokes flow. To further examine the
-effect of the cilia, we next consider a no-cilia model variation. In
-this scenario, the simulated CSF flow is pulsatile and
-\fixme{unidirectional} (\Cref{fig:figure1}g), with a peak velocity
-magnitude of \fixme{$4.8$ \textmu m/s}. On the other hand, the
-vortices (re)appear when considering a variation with cilia but no
-cardiac contribution (\Cref{fig:figure1}h), in which case the highest
-velocities ($26.5$ \textmu m/s) also occur in the vicinity of the
-cilia. Thus, the bidirectional traction induced by motile cilia
-inherently leads to a partial compartmentalization of the ventricular
-system.
-
-%% %\subsection*{Vortex structures vanish in the absence of cilia}
-%% The pulsatile motion is absent when disregarding cardiac motion~(model I, \cref{fig:figure1}, panel~\textbf{f}).
-For model I, the boundary conditions are not time-dependent, rendering the solution to the Stokes equations~\eqref{eq:stokes_eqs} a steady-state flow field.
-Streamlines demonstrate the compartmentalization of the cerebrospinal fluid flow driven by cilia, and we observe highest vorticity in the vicinity of cilia.
-
-%% Excluding the cilia tangential traction from the model (model II), vortex-structured compartmentalization of the ventricular flow does not occur, and the flow is directional and pulsatile as a result of the pressure boundary conditions imposed~(\cref{fig:figure1}, panel \textbf{g}).
-
-%% The cardiac pressure forces induce a pulsatile motion of the
-%% cerebrospinal fluid synchronized with the cardiac cycle, with velocity
-%% magnitudes of the pulsatile motion being approximately an order of
-%% magnitude smaller than the velocities related to the cilia-driven
-%% motion.
+justifying the assumption of Stokes flow. In summary, the computational
+CSF flow model reproduces the flow features observed \emph{in vivo}.
 
@@
     \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
-    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time in each region of interest (ROI)
+    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time
+    in each region of interest (ROI)
     observed during experiments of photoconversion of Dendra2 proteins in ROI 1.
-    \textbf{b.} Mean concentration $\cbar$ as function of time in each ROI in a simulation of Dendra2 protein transport with
+    \textbf{b.} Mean concentration $\cbar$ as function of time in each ROI in a
+    simulation of Dendra2 protein transport with
     the diffusion coefficient $D_3$.
-    \textbf{c.} Time to $\Delta F$ reaches a threshold value of 0.25 in one representative zebrafish larva.
-    Time to $\cbar$ reaches a threshold value of 0.25 for a transport simulation with diffusion coefficient $D_3$.
+    \textbf{c.} Time to $\Delta F$ reaches a threshold value of 0.25 in
+    one representative zebrafish larva.
+    Time to $\cbar$ reaches a threshold value of 0.25 for
+    a transport simulation with diffusion coefficient $D_3$.
     We have excluded the posterior-most regions of the geometries,
-    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold value of 0.25 in these regions.}
+    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
+    value of 0.25 in these regions.}
     \label{fig:figure3_compare_exp_and_sim_control}
@@
 \subsection*{Absence of ciliary motion affects local protein distribution}
-To assess the impact of cilia motion on solute distribution, we measured the movement of photoconverted Dendra2 signal
+To assess the impact of cilia motion on solute distribution,
+we measured the movement of photoconverted Dendra2 signal
 in control and motile-cilia mutant zebrafish (\emph{schmalhans} (\emph{smh})).
-By plotting the means of $\Delta F$ (\Cref{fig:figure4_compare_control_mutant}a) and the time to threshold
-across the control and mutant cohorts (\Cref{fig:figure4_compare_control_mutant}b), we identified a significant
+By plotting the means of $\Delta F$ (\Cref{fig:figure4_compare_control_mutant}a)
+and the time to threshold
+across the control and mutant cohorts (\Cref{fig:figure4_compare_control_mutant}b),
+we identified a significant
 difference in Dendra2 distribution in ROIs 2 and 4, but not in ROIs 3, 5, and 6. In ROIs 2 and 4,
@@
 we observed a slower increase of fluorescence intensity,
-resulting in a $\sim 45\%$ higher mean time-to-threshold in the \emph{smh}
-mutant compared to controls (\Cref{fig:figure4_compare_control_mutant}b).
+resulting in $\sim X\%$ (ROI 2) and $\sim 45\%$ (ROI 4)
+higher mean times-to-threshold in the \emph{smh}
+mutants compared to controls (\Cref{fig:figure4_compare_control_mutant}b).
 
@@
 we simulated protein transport by using the only-cardiac/no-cilia flow model 
-and compared it with the baseline model (both cilia and cardiac motion) (\Cref{fig:figure4_compare_control_mutant}c).
+and compared it with the baseline model
+(both cilia and cardiac motion) (\Cref{fig:figure4_compare_control_mutant}c).
 Similar to our experiments, we observed slower dynamics in simulations for ROIs 2 and 4.
@@
 with the time-to-threshold in ROI 2 being 90\% higher in absence of cilia-mediated flow.
-Moreover, ROI 5 exhibits very different $\cbar$ profiles for the two configurations in our computational model,
+Moreover, ROI 5 exhibits very different $\cbar$ profiles for the two
+configurations in our computational model,
 but not in our experimental data.
-Altogether, our findings identify that diffusion plays an important role for solute movement to regions upstream in the cilia flow fields or to distant ventricles.
+Altogether, our findings identify that diffusion plays an important
+role for solute movement to regions upstream in the cilia flow fields or to distant ventricles.
 \begin{figure}[H]
@@
     \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
-    \caption{\textbf{a.} Relative change in fluorescence intensity $F$ over time in each region of interest (ROI) for control (black lines) and \emph{smh} mutant (red lines) fish. 
-    \textbf{b.} Times when $\Delta F$ first exceeds a threshold value, equal to 0.25 (ROIs 2-4) or 0.10 (ROIs 5, 6), for control (gray dots) and \emph{smh} mutant (red dots) fish.
-    The thick black lines denote mean values of the datasets, and $p$-values were calculated using a Mann-Whitney U test with a confidence level of 95\%.
-    \textbf{c.} Mean concentration $\cbar$ as function of time in each ROI, simulated using the baseline model (black lines) and the cardiac-only/no-cilia model (red lines).
-    The horizontal gray lines mark the threshold value $\hat{c}$, and the time $\hat{t}$ when the threshold is first exceeded is reported in the plot legends.
-    Note that in both panels \textbf{a} and \textbf{c}, the vertical axes have different limits in each plot.}
+    \caption{\textbf{a.} Relative change in fluorescence intensity $F$ over
+    time in each region of interest (ROI) for control (black lines) and \emph{smh} mutant (red lines) fish. 
+    \textbf{b.} Times when $\Delta F$ first exceeds a threshold value,
+    equal to 0.25 (ROIs 2--4) or 0.10 (ROIs 5, 6), for control (gray dots) and
+    \emph{smh} mutant (red dots) fish.
+    The thick black lines denote mean values of the datasets, and $p$-values
+    were calculated using a Mann-Whitney U test with a confidence level of 95\%.
+    \textbf{c.} Mean concentration $\cbar$ as function of time in each ROI,
+    simulated using the baseline model (black lines) and the cardiac-only/no-cilia model (red lines).
+    The horizontal gray lines mark the threshold value $\hat{c}$, and the time
+    $\hat{t}$ when the threshold is first exceeded is reported in the plot legends.
+    Note that in both panels \textbf{a} and \textbf{c}, the vertical axes have
+    different limits in each plot.}
     \label{fig:figure4_compare_control_mutant}
@@
 To identify the role of these lineages on CSF transport, we modified flow boundary conditions
-in the three different ciliated regions (\Cref{fig:figure5_compare_cilia_modifications}a) and simulated
-CSF flow using the Stokes equations. We identified that the velocities were most strongly
+in the three different ciliated regions
+(\Cref{fig:figure5_compare_cilia_modifications}a, magenta markers)
+and simulated CSF flow using the Stokes equations.
+We identified that the velocities were most strongly
 affected when removing cilia in the dorsal diencephalic cilia,
@@
 less solute has spread towards the posterior ventricle (ROI 6).
-
 \begin{figure}[H]
@@
     \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
-    \caption{Caption}
+    \caption{\textbf{a.} The three separate ciliated regions where loss of cilia motility is simulated
+    by imposing a zero tangential traction boundary condition in the respective region.
+    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest in the three 
+    loss-of-cilia-motility scenarios considered. The region named in the legend is the region
+    where we modify the cilia tangential traction boundary condition to a free-slip condition
+    in the CSF flow model.}
     \label{fig:figure5_compare_cilia_modifications}

### 2025-02-04 paper/main.tex
Results 2, remove 'Computational flow modelling scenarios'

@@
 
-\subsection*{Computational flow modelling scenarios}
-
-\mer{MER: @Halvor I suggest you move these two paragraphs into their respective
-Results sections (Results 2 and 5).}
-When simulating transport of solute in the ventricles,
-we consider the same six different regions of interest that were
-considered in the photoconversion experiments.
-In region number one (the photoconversion region),
-we use the function~\eqref{eq:photoconversion_curve} to enforce
-the concentration such that it represents the experimental data
-of photoconversion of proteins. We consider the three different diffusion
-coefficients introduced in previous sections to simulate and compare results
-for transport of molecules of varying sizes.
-
-To simulate transport in the pathological case of region-specific cilia absence,
-we consider three scenarios where we modify the boundary conditions of the CSF flow model.
-The cilia tangential stress boundary condition for the boundary where we
-remove cilia is changed to a free-slip boundary condition,
-prescribing zero tangential forces to represent absence of cilia motion
-in the region where we consider cilia removal.
-We consider removal of cilia in the three separate cilia-covered regions
-of the telencephalic (anterior) ventricle, the dorsal part of the diencephalic (middle) ventricle,
-and the ventral part of the diencephalic ventricle~(\Cref{fig:figure1}d).
-For the three scenarios, we simulate CSF flow modeled by the Stokes
-equations~\eqref{eq:stokes_eqs} with the modified boundary conditions,
-and use the resulting velocity field in transport simulations.
-
 \subsection*{Quantities of interest}
@@
 \subsection*{Ventricular solute transport is advection-dominated for larger molecules}
-We next ask what is the impact of these CSF flow patterns and
+We next ask: what is the impact of these CSF flow patterns and
 magnitudes on solute transport generally within the brain ventricles?
@@
 rapidly with increasing diffusion coefficient. Interestingly, the
-distribution patterns differ between the different-characteristics
+distribution patterns differ between the \fixme{different-characteristics}
 solutes. For the smallest diffusion coefficient, representing
@@
 obfuscated, and the solute spreads more uniformly throughout the
-ventricular geometry (\Cref{fig:fig2}\fixme{x-y}). Interestingly, the
+ventricular geometry (\Cref{fig:fig2}\fixme{x-y}). Notably, the
 smaller solutes with higher diffusion coefficients spread more quickly
@@
     \includegraphics[width=0.95\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}
-    \caption{Simulated distribution and evolution after photoconversion of Dendra ($D_1$), STM+GFP ($D_2$) and Exosomes ($D_3$).
-    \mer{MER: I think you should show on the same color scale here in a) (the range of values lets you and then it is possible to compare). Split a into a, b, c. Show e) first (so that e) becomes a)}.
-    \textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm, the center of the geometry) showing the concentration field simulated with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s.
+    \caption{Simulated distribution and evolution after photoconversion of
+    Dendra ($D_1$), STM+GFP ($D_2$) and Exosomes ($D_3$).
+    \mer{MER: I think you should show on the same color scale here in a)
+    (the range of values lets you and then it is possible to compare).
+    Split a into a, b, c. Show e) first (so that e) becomes a)}.
+    \textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm,
+    the center of the geometry) showing the concentration field simulated
+    with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three
+    time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s.
     Note that the colorbars indicating the magnitude of $c$ have different limits for each column.
-    \textbf{b--d.} Mean concentration $\cbar$ in each region of interest (ROI) as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively.
+    \textbf{b--d.} Mean concentration $\cbar$ in each region of interest (ROI)
+    as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively.
     \textbf{e.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
-    \textbf{f.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.
+    \textbf{f.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a
+    threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.
     Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}
@@
 
-\mer{MER: Stopped here with the editing (except commenting out), assuming that Nathalie had something to say about the next paragraph.}
-
-Transport of solute is quantified by the profile of the mean concentrations $\cbar_i(t)$ in the regions of interest (ROIs) $\Omega_i$ as functions of time~(\Cref{fig:fig2}b--d).
-An illustration of the ROIs is provided in \Cref{fig:fig2}e. The dynamics of ROI 1 follow from imposing~\Cref{eq:photoconversion_curve}.
-For ROIs 2--6, we observe more rapid concentration increases when the diffusion coefficient increases. 
-For all three diffusion coefficients, the dynamics of ROI 6 is the slowest.
-Region 5 exhibits a more rapid increase in mean concentration, and an even faster increase is observed for ROIs 2--4.
-The profiles of the latter three regions are similar, displaying only small differences in all of the three plots.
-\lyng{HH: Add some quantification in terms of percentages, e.g. final values of $\cbar_i$ for the different $D_i$?}
-In region 6, the threshold is never exceeded for $D_1$, with the mean concentration close to zero at the end of the simulation. 
-To quantify the balance of advection versus diffusion as transport mehcanisms on a global scale,
-we calculate the Péclet numbers $\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
-Since $\mathrm{Pe}>1$, this indicates that advection is the dominant transport mechanism for the molecules considered.
+To quantify the transport of solute, we plot the profile of the mean
+concentrations $\cbar_i(t)$ as functions of time
+(\cref{fig:figure2_compare_diffusion_coefficients}\fixme{b--d}) and
+the times $\hat{t}$ when the mean concentrations $\cbar_i$ first exceed
+a threshold value $\hat{c}$ (\cref{fig:figure2_compare_diffusion_coefficients}\fixme{f})
+in 6 regions of interest (ROIs) (\cref{fig:figure2_compare_diffusion_coefficients}\fixme{e}).
+The dynamics at the site of photoconversion (ROI 1)
+is logarithmic and follows from imposing \eqref{eq:photoconversion_curve}.
+For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
+(\Cref{fig:figure2_compare_diffusion_coefficients}\fixme{b--d}),
+which results in smaller time to threshold
+(\Cref{fig:figure2_compare_diffusion_coefficients}\fixme{f}).
+For all three diffusion coefficients, the dynamics of ROI 5
+is significantly delayed compared to ROI 2--4,
+and ROI 6 is the slowest. Notably, for $D_1$ the mean concentration
+in ROI 6 is close to zero at the end of simulation.
+To quantify the balance of advection versus diffusion as transport mehcanisms,
+we calculate the Péclet numbers $\mathrm{Pe}_1=519$,
+$\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
+Since $\mathrm{Pe}>1$, this indicates that advection is the
+dominant transport mechanism on a \fixme{global} scale.
 
 \subsection*{Validation of the simulations with experimental data}
-To validate our computational model, we performed photoconversion experiments in transgenic zebrafish larvae expressing a secreted Dendra2 in their brain ventricles.
-Our photoconversion protocol consisted of the acquisition of a baseline, before localized exposure to a UV laser (at the ROI 1 location)
+To validate our computational model, we performed photoconversion experiments
+in transgenic zebrafish larvae expressing a secreted Dendra2 in their brain ventricles.
+Our photoconversion protocol consisted of the acquisition of a baseline,
+before localized exposure to a UV laser (at the ROI 1 location)
 that converts Dendra2 from a green to a red emitting fluorescent protein. 
-To quantify the transport of photoconverted proteins, we measured and calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
-over time (\Cref{fig:figure3_compare_exp_and_sim_control}a, $F_0$ being the average fluorescence at baseline).
+To quantify the transport of photoconverted proteins, we measured and
+calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
+over time (\Cref{fig:figure3_compare_exp_and_sim_control}a,
+$F_0$ being the average fluorescence at baseline).
 
@@
 Importantly, since the initial condition of the simulation is a mean concentration of zero,
-the mean concentration $\cbar$ can be interpreted as the change in mean concentration and is thus a similar metric to $\Delta F$.
+the mean concentration $\cbar$ can be interpreted as the change in mean concentration and
+is thus a similar metric to $\Delta F$.
 The final values of $\cbar$ were 0.76, 0.72, 0.82, 0.56 and 0.35 respectively,
@@
 For instance, transport dynamics in ROIs 2--6 were faster in the simulation and reached higher final values.
-Moreover, the $\cbar$ profiles of ROIs 3--4 were opposite order in the simulations as compared to the experiments.
+Moreover, the $\cbar$ profiles of ROIs 3--4 were opposite order in
+the simulations as compared to the experiments.
 Despite observing small differences, the \emph{in vivo} experiments and
@@
 \subsection*{Absence of ciliary motion affects local protein distribution}
-To assess the impact of cilia motion on solute distribution,
+Since CSF flow is highly disturbed in the absence of motile cilia, we
+want to assess the impact of cilia motion on solute distribution. To this end,
 we measured the movement of photoconverted Dendra2 signal

### 2025-02-04 paper/main.tex
Results 5 and 6

@@
 symmetric interior penalty discontinuous Galerkin (DG)
-method in space~\cite{Arnold1982AnElements}.
+method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
+conservation properties.
 To accurately approximate the solute concentrations even
@@
 zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain}.
-To identify the role of these lineages on CSF transport, we modified flow boundary conditions
-in the three different ciliated regions
-(\Cref{fig:figure5_compare_cilia_modifications}a, magenta markers)
-and simulated CSF flow using the Stokes equations.
+To identify the role of these lineages on CSF transport, we simulate transport
+upon region-specific cilia paralysis by modifying the boundary conditions
+of the CSF flow model. Three separate cilia-covered regions were considered separately:
+the telencephalic (anterior) ventricle, the dorsal part and the ventral part
+of the diencephalic (middle) ventricle (\Cref{fig:figure5_compare_cilia_modifications}a).
+The cilia tangential traction boundary condition is for each case
+changed to a free-slip boundary condition in paralyzed region,
+prescribing zero tangential forces to
+represent absence of cilia motion.
+We simulate CSF flow modeled by the Stokes equations with the
+modified boundary conditions, and use the resulting
+velocity fields in transport simulations.
+
 We identified that the velocities were most strongly
@@
 as the maximum velocity dropped from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
+\emph{In vivo}, these cilia generate the strongest flow at
+this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
 In contrast, removing telencephalic and ventral diencephalic had minimal
 impact and resulted in maximum velocities of 27.7 $\mu$m/s or 27.2 $\mu$m/s, respectively.
-
-With the resulting velocity fields, we simulated transport of Dendra2.
-Changes in the transport dynamics were most prominent when removing the dorsal cilia
-in the diencephalic ventricle, which produces the strongest flow at this developmental stage.
-All ROIs (except ROI 1, where we locally released solutes) exhibit significant changes
-in the dynamics of $\cbar$ (\Cref{fig:figure5_compare_cilia_modifications}b).
+Changes in the transport dynamics of Dendra2 were most prominent when removing the dorsal cilia
+in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
+exhibit significant changes in the dynamics of $\cbar$
+(\Cref{fig:figure5_compare_cilia_modifications}b).
 Compared to the baseline model results, we observed a slower increase and lower final concentration
 in the middle and anterior ventricles (ROIs 2--5),
-and a faster transport to the posterior ventricle (ROI 6).
+and more rapid transport to the posterior ventricle (ROI 6).
 In contrast, removal of telencephalic cilia did not alter the evolution of the
@@
 \subsection*{Modification of ventricles geometry impacts protein distribution}
+Variations in ventricular morphology impacts the CSF flow patterns.
 To assess the impact of ventricular morphologies on solute distribution,
@@
 We simulate CSF flow in the modified geometries with the baseline flow model
-and use the resulting velocity field to simulate transport of Dendra2 (\Cref{fig:figure6_sim_results_compare_geometries}b).
+and use the resulting velocity field to simulate transport of Dendra2
+(\Cref{fig:figure6_sim_results_compare_geometries}b).
 

### 2025-02-04 paper/main.tex
Department of
add geometry percentage changes

@@
 \author[2,+, *]{Nathalie Jurisch-Yaksi}
-\affil[1]{Department for Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
+\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
 \affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway}
@@
 individuals, and under physiological and pathological conditions. 
-Motivated by an interest in how geometry impacts solute distribution,
-we also consider four variations in the ventricular geometry: by shrinking the fore-mid brain connection, 
-the middle ventricle, the mid-hind brain connection, and all three simultaneously. 
+Motivated by an interest in how ventricular geometry impacts solute distribution,
+we also consider four variations in the geometry \fixme{(percentage reduction in cross-sectional areas):
+by shrinking the fore-mid brain connection (66 \%), 
+the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
 We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
-\mer{MER: More specifics (i.e.~1 sentence and/or inserted info) here on how much these were shrunk and how.}
 

### 2025-02-04 paper/main.tex
clean Appendix

@@
 injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:figure1}d).
+From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}d).
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
@@
 Parts of the ventricular surfaces were marked to be lined with
-motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:figure1}d, magenta markers).
+motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}d, magenta markers).
 \begin{figure}%[hbt!]
@@
     \includegraphics[width=\linewidth]{graphics/figure1.png}
-    \caption{\lyng{Experimenting with velocity colorbars, thoughts on the
-    two options? Or have two separate as it is now?}}
-    \label{fig:figure1}
+    \caption{\fixme{Reorder panels.} 
+    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
+    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
+    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
+    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
+    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
+    anterior/posterior facets (blue).
+    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
+    cilia-only/no-cardiac flow model.
+    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
+    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
+    \textbf{g.} Streamlines simulated with the baseline flow model at
+    a time 50\% into the cardiac cycle. %t=0.225225 s
+    \textbf{h.} Streamlines simulated with the baseline flow model at
+    a time 70\% into the cardiac cycle. %t=0.315315 s
+    }
+    \label{fig:fig1}
 \end{figure}
@@
 structures~\cite{Olstad2019CiliaryDevelopment}
-within the brain ventricles (\Cref{fig:figure1}a--c).
+within the brain ventricles (\Cref{fig:fig1}a--c).
 In addition, cardiac pulsations induces pulsatile CSF flow.
@@
     In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
-    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0
+    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
 
@@
     Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
-    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I
+    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
 
@@
     $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
-    anterior/posterior boundary $\Gp$.  % Model II
+    anterior/posterior boundary $\Gp$.  % Model II/Model B
 \end{itemize}
@@
 \subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:figure1}d, magenta markers),
+On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:fig1}d, magenta markers),
 we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
@@
 $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
-boundary $\Gp$~(\Cref{fig:figure1}d, blue markers).
+boundary $\Gp$~(\Cref{fig:fig1}d, blue markers).
 Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
@@
 \subsection*{Generation of \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}} line}
-\lyng{Needs a more understandable title.}
+\fixme{@Nathalie: This needs a more understandable title for us non-experts, could we change to
+e.g. "Generation of transgenic line"?.}
 The open reading frame (ORF) of the neuropeptide y (npy) signal peptide
@@
 \subsection*{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Cref{fig:figure1}b, c, we carried out
+To recover the flow fields shown in~\Cref{fig:fig1}b, c, we carried out
 particle tracking in a larval zebrafish injected with fluorescent beads.
@@
 Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:figure1}b, c.
+covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:fig1}b, c.
 
@@
 
-We seek to model the compartimentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:figure1}b--c).
+We seek to model the compartimentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}b--c).
 To characterize CSF flow patterns predicted by
@@
 system, with large-scale vortex structures in the anterior and middle
-ventricles~(\Cref{fig:figure1}e). The highest velocities ($26.5$ \textmu m/s)
+ventricles~(\Cref{fig:fig1}e). The highest velocities ($26.5$ \textmu m/s)
 occur in the vicinity of the dorsal cilia in the middle ventricle.
@@
 we next consider a no-cilia model variation. In this scenario, the simulated CSF
-flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:figure1}g),
+flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:fig1}g),
 with a peak velocity magnitude of $4.8$ \textmu m/s. At each time instant, the flow
@@
 We now consider the baseline model, simulating flow driven by both cilia
-and cardiac pulsations. We observe \fixme{persistent} flow features,
+and cardiac pulsations. We observe persistent flow features,
 with vortex-structures in the anterior and middle ventricles
-and directional flow in the posterior ventricle (\Cref{fig:figure1}e,
+and directional flow in the posterior ventricle (\Cref{fig:fig1}e,
 \fixme{Supplementary video 1}). These characteristic patterns suggest
@@
 concentrations $\cbar_i(t)$ as functions of time
-(\cref{fig:figure2_compare_diffusion_coefficients}\fixme{b--d}) and
+(\Cref{fig:fig2}\fixme{b--d}) and
 the times $\hat{t}$ when the mean concentrations $\cbar_i$ first exceed
-a threshold value $\hat{c}$ (\cref{fig:figure2_compare_diffusion_coefficients}\fixme{f})
-in 6 regions of interest (ROIs) (\cref{fig:figure2_compare_diffusion_coefficients}\fixme{e}).
+a threshold value $\hat{c}$ (\Cref{fig:fig2}\fixme{f})
+in 6 regions of interest (ROIs) (\Cref{fig:fig2}\fixme{e}).
 The dynamics at the site of photoconversion (ROI 1)
@@
 For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
-(\Cref{fig:figure2_compare_diffusion_coefficients}\fixme{b--d}),
+(\Cref{fig:fig2}\fixme{b--d}),
 which results in smaller time to threshold
-(\Cref{fig:figure2_compare_diffusion_coefficients}\fixme{f}).
+(\Cref{fig:fig2}\fixme{f}).
 For all three diffusion coefficients, the dynamics of ROI 5
@@
 flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
-It has been observed, both previously and in this work, that the fluid velocity increases towards the wall~(\Cref{fig:figure1}c).
+It has been observed, both previously and in this work, that the fluid velocity increases towards the wall~(\Cref{fig:fig1}c).
 Using slip boundary conditions allows for this behavior.
@@
 used a force expression that increased linearly from the wall to a maximum force density of
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 $\mu$m away from the wall,
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m away from the wall,
 which represented cilium length. If we assumed a cilia array of the same thickness
-$l = 15$ $\mu$m in our model, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$
+$l = 15$ \textmu m in our model, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$
 would correspond to a maximum force density of 
@@
 which smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 $\mu m$ is the a typical length of cilia in human brain ventricles
-(in general the length is between 10--15 $\mu$m~\cite{Afzelius2004Cilia-relatedDiseases}),
-while in zebrafish they are closer to 5 $\mu$m~\cite{Salman2022ComputationalEmbryo}.
-With $l=5$ $\mu$m, our traction parameter corresponds to a maximum force density of
+The length 15 \textmu m is the a typical length of cilia in human brain ventricles
+(in general the length is between 10--15 \textmu m~\cite{Afzelius2004Cilia-relatedDiseases}),
+while in zebrafish they are closer to 5 \textmu m~\cite{Salman2022ComputationalEmbryo}.
+With $l=5$ \textmu m, our traction parameter corresponds to a maximum force density of
 $f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$
@@
 4000 N/$\mathrm{m^2}$. The resulting numerical velocity fields matched well with
-\emph{in vivo} measurements, where the maximum velocity magnitude was around 5 $\mu$m/s
-(recall that our model exhibits a maximum of 27.7 $\mu$m/s).
+\emph{in vivo} measurements, where the maximum velocity magnitude was around 5 \textmu m/s
+(recall that our model exhibits a maximum of 27.7 \textmu m/s).
 The geometry they studied resembles a pipe, probably offering more flow resistance
@@
 errors are expected to decay with order $k$, see for example Cockburn~\emph{et al.}~\cite{Cockburn2005AEquations}.
-For the sake of simplicity,~\Cref{tab:cylinder_error_rates} reports the velocity errors in the standard $H^1$ norm.
-Using polynomial degree
+For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
+reports the velocity errors in the standard $H^1$ norm. Using polynomial degree  
 $k=1$, we observe linear convergence in both the velocity and the pressure.   
-\mk{MK: I see 1.5 in the table for $\uu$ in $L^2$?} \lyng{HH: Yes, while the $H^1$ error decays linearly, isn't this in line with expectations? Could be more specific: "Using polynomial degree 
+\mk{MK: I see 1.5 in the table for $\uu$ in $L^2$?}
+\lyng{HH: Yes, while the $H^1$ error decays linearly, isn't this in line with expectations?
+Could be more specific: "Using polynomial degree 
 $k=1$, we observe linear convergence in both the velocity $H^1$ error and the pressure $L^2$ error."}
-
-\lyng{HH: Add a paragraph discussing the advection-diffusion equation discretization with DG elements?}
 
@@
 \begin{equation}
-    \intO{\rho\pdifft{\uu}\cdot\vv} - \intG{\bsig\nn\cdot\vv} + \intO{2\mu\beps(\uu) : \beps(\vv)} - \intO{p\nabla\cdot\vv} = \mathbf{0}, \label{eq:modelA_weak_form1}
+    \intO{\rho\pdifft{\uu}\cdot\vv}
+    - \intG{\bsig\nn\cdot\vv}
+    + \intO{2\mu\beps(\uu) : \beps(\vv)}
+    - \intO{p\nabla\cdot\vv} = \mathbf{0}, \label{eq:modelA_weak_form1}
 \end{equation}
@@
 
-We choose $\mathbf{r} = \rr^+ = (1, 0, 1)$ or $\mathbf{r} = \rr^- = -(1, 0, 1)$ to impose forces perpendicular to the $y$-axis.
-The reason for this is that all of the experimental images we compare with are taken in the $xz$-plane,
+We choose $\mathbf{r} = \rr^+ = (1, 0, 1)$ or $\mathbf{r} = \rr^- = -(1, 0, 1)$
+to impose forces perpendicular to the $y$-axis.
+The reason for this is that all of the experimental images we compare
+with are taken in the $xz$-plane,
 rendering flow features in the $y$-direction unobservable.
@@
         \uu\cdot\nn &= 0 \quad &&\mathrm{on} \ \Gamma=\Gc\cup\Gs, \label{eq:modelA_slip_BC_impermeability} \\
-        %\hat{\sigma} - (\hat{\sigma}\cdot\nn)\nn &= \tau P_{\nn}(\rr) \quad &&\mathrm{on} \ \Gamma_s,
         \bsigpar &= \btau \quad &&\mathrm{on} \ \Gc,
@@
 \end{subequations}%
-on the boundary $\Gamma=\Gamma_c\cup\Gamma_s$.
-The boundary $\Gamma_s$ is a free-slip boundary, where we impose the free-slip condition~\eqref{eq:modelA_full_slip_BC}.
-The first condition~\eqref{eq:modelA_slip_BC_impermeability} is the impermeability condition, enforcing no flow normal to the boundary, whereas~\eqref{eq:modelA_slip_BC_shear} imposes a stress tangential to the boundary.
-These tangential stresses are applied to represent the forces that the collective cilia motion exerts on the cerebrospinal fluid.
+on the boundary $\Gamma=\Gamma_c\cup\Gamma_s$. The boundary $\Gamma_s$ is a free-slip boundary,
+where we impose the free-slip condition~\eqref{eq:modelA_full_slip_BC}.
+The first condition~\eqref{eq:modelA_slip_BC_impermeability} is the
+impermeability condition, enforcing no flow normal to the boundary,
+whereas~\eqref{eq:modelA_slip_BC_shear} imposes a stress tangential to
+the boundary. These tangential stresses are applied to represent
+the forces that the collective cilia motion exerts on the cerebrospinal fluid.
 
@@
 \end{equation}
-in the weak form~\eqref{eq:modelA_weak_form1} of the Stokes equations. We decompose the traction vector $\hat{\bsig}$ into a normal and tangential component:
+in the weak form~\eqref{eq:modelA_weak_form1} of the Stokes equations.
+We decompose the traction vector $\hat{\bsig}$ into a normal and tangential component:
 \begin{equation*}
@@
 \end{equation*}
-Inserting the above into~\eqref{eq:boundary_integral_BC1}, combined with application of the tangential traction condition~\eqref{eq:modelA_slip_BC_shear} and the free-slip condition~\eqref{eq:modelA_full_slip_BC}, yields
+Inserting the above into~\eqref{eq:boundary_integral_BC1},
+combined with application of the tangential traction
+condition~\eqref{eq:modelA_slip_BC_shear} and the
+free-slip condition~\eqref{eq:modelA_full_slip_BC}, yields
 \begin{equation}
     \intG{\hat{\bsig}\cdot\vv} = \int_{\Gc\cup\Gs}{(\bsigperp + \bsigpar)\cdot\vv}\, ds = 
-    \int_{\Gc\cup\Gs}{\bsigperp\cdot\vv}\, ds + \intGc{\btau\cdot\vv} = \intG{\bsigperp\cdot\vv} + \intGc{\btau\cdot\vv}.
+    \int_{\Gc\cup\Gs}{\bsigperp\cdot\vv}\, ds
+    + \intGc{\btau\cdot\vv} = \intG{\bsigperp\cdot\vv} + \intGc{\btau\cdot\vv}.
     \label{eq:boundary_integral_BC2}
 \end{equation}
-The second term on the right-hand side of~\eqref{eq:boundary_integral_BC2} is moved to the right-hand side of the weak form, since $\btau$ is known.
-Using $\hat{\bsig}_{\perp} = (\hat{\bsig}\cdot\nn)\nn$, we can write the first term on the right-hand side of~\eqref{eq:boundary_integral_BC2} as
+The second term on the right-hand side of~\eqref{eq:boundary_integral_BC2}
+is moved to the right-hand side of the weak form, since $\btau$ is known
+ Using $\hat{\bsig}_{\perp} = (\hat{\bsig}\cdot\nn)\nn$,
+ we can write the first term on the right-hand side of~\eqref{eq:boundary_integral_BC2} as
 \begin{equation}
@@
 \end{equation}
-In a later section, we will discretize the weak formulation of the Stokes equations with Brezzi-Douglas-Marini finite elements~\cite{Brezzi1985TwoProblems}.
-These elements are defined through integral moments of the normal component of a variable on the facets of an element, we can strongly enforce the value of $\uu\cdot\nn$ and thus the boundary condition~\eqref{eq:modelA_slip_BC_impermeability}.
-Consequently, the test function counterpart $\vv\cdot\nn$ vanishes on the boundary, and the term~\eqref{eq:boundary_integral_BC_normal} is therefore dropped from the weak form.
-As a result, for model verison I, the weak form of the momentum equation takes the following form:
-\begin{equation*}
-    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} - \intO{p\nabla\cdot\vv} = \intGc{\btau\cdot\vv}, \quad\forall\vv\in\VV.
-\end{equation*}
-Next, multiplying the continuity equation~\eqref{eq:BDM_stokes_div} with a test function $q\in Q$, we require that
+In a later section, we will discretize the weak formulation
+of the Stokes equations with Brezzi-Douglas-Marini
+finite elements~\cite{Brezzi1985TwoProblems}. These elements are
+defined through integral moments of the normal component of a
+variable on the facets of an element, we can strongly enforce
+the value of $\uu\cdot\nn$ and thus the boundary
+condition~\eqref{eq:modelA_slip_BC_impermeability}.
+Consequently, the test function counterpart $\vv\cdot\nn$ vanishes
+on the boundary, and the term~\eqref{eq:boundary_integral_BC_normal}
+is therefore dropped from the weak form. As a result, for the cilia-only/no-cardiac model,
+the weak form of the momentum equation takes the following form:
+\begin{equation*}
+    \intO{\rho\pdifft{\uu}\cdot\vv}
+    + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)}
+    - \intO{p\nabla\cdot\vv} = \intGc{\btau\cdot\vv}, \quad\forall\vv\in\VV.
+\end{equation*}
+Next, multiplying the continuity equation~\eqref{eq:BDM_stokes_div}
+with a test function $q\in Q$, we require that
 \begin{equation}
@@
 \end{equation}
-The full weak form of the Stokes equations for model version I is then: find $(\uu, \, p) \in \VV\times Q$, such that
+The full weak form of the Stokes equations for this flow model is then:
+find $(\uu, \, p) \in \VV\times Q$, such that
 \begin{subequations}
     \begin{alignat}{5}
-        &\intO{\rho\pdifft{\uu}\cdot\vv} + &\intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} - &\intO{p\nabla\cdot\vv} &&= \intGc{\btau\cdot\vv}, &&\quad\forall\vv\in\VV, \label{eq:stokes_weak_mom_modelA}\\
+        &\intO{\rho\pdifft{\uu}\cdot\vv}
+        + &\intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)}
+        - &\intO{p\nabla\cdot\vv}
+        &&= \intGc{\btau\cdot\vv}, &&\quad\forall\vv\in\VV, \label{eq:stokes_weak_mom_modelA}\\ 
         &{} &{}  -&\intO{q\nabla\cdot\uu} &&= 0, &&\quad\forall q\in Q. \label{eq:stokes_weak_cont_modelA}
@@
 \end{subequations}%
-where the boundary $\Gamma = \Gs\cup\Gp$ consists of a free-slip boundary $\Gs$, and a part $\Gp$ where a normal traction type of boundary condition is imposed.
-Note, however, that the transpose velocity gradient term must be included inside the parentheses on the left-hand side of~\eqref{eq:modelB_pressure_BC} for it to be the traction $\bsig$.
-Since this is not the case, we rather refer to this boundary condition as a normal pressure boundary condition.
-The boundary $\Gs$ is handled as discussed in the previous section, such that the stress boundary integral~\eqref{eq:boundary_integral_BC1} vanishes over $\Gs$.
-Therefore, we now have
+where the boundary $\Gamma = \Gs\cup\Gp$ consists of a free-slip boundary $\Gs$,
+and a part $\Gp$ where a normal traction type of boundary condition is imposed.
+Note, however, that the transpose velocity gradient term must be
+included inside the parentheses on the left-hand side of~\eqref{eq:modelB_pressure_BC}
+for it to be the traction $\bsig$. Since this is not the case,
+we rather refer to this boundary condition as a normal pressure boundary condition.
+The boundary $\Gs$ is handled as discussed in the previous section,
+such that the stress boundary integral~\eqref{eq:boundary_integral_BC1}
+vanishes over $\Gs$. Therefore, we now have
 \begin{align}
@@
 \end{align}
-We leave the first term on the left-hand side of~\eqref{eq:modelB_boundary_integral1} in the weak form of the momentum equation.
-The second term is determined by the boundary condition~\eqref{eq:modelB_pressure_BC}, and is therefore moved to the right-hand side of the weak form.
-The weak form of the momentum equation for model version IIa is then
+We leave the first term on the left-hand side
+of~\eqref{eq:modelB_boundary_integral1} in the weak form of
+the momentum equation. The second term is determined by
+the boundary condition~\eqref{eq:modelB_pressure_BC},
+and is therefore moved to the right-hand side of the weak form.
+The weak form of the momentum equation is then
 \begin{equation}
@@
 \end{equation}
-Also considering the weak form of the continuity equation, the weak formulation for model version II then reads: find $(\uu,\, p)\in\VV\times Q$ such that~\eqref{eq:weak_form_mom_eq_modelB} and~\eqref{eq:pressure_weak_form} hold for all $(\vv, \, q)\in\VV\times Q$.
-To simulate the back-and-forth motion induced by the cardiac cycle observed in previous work~\cite{Olstad2019CiliaryDevelopment}, we apply sinusoidal forcing.
-The boundary $\Gamma_p$ has two separate regions: one located on the anterior ventricle and one on the posterior ventricle~(\cref{fig:figure1}, panel \textbf{b}).
+Also considering the weak form of the continuity equation,
+the weak formulation for the cardiac-only/no-cilia model version
+then reads: find $(\uu,\, p)\in\VV\times Q$
+such that~\eqref{eq:weak_form_mom_eq_modelB} and~\eqref{eq:pressure_weak_form}
+hold for all $(\vv, \, q)\in\VV\times Q$.
+To simulate the back-and-forth motion induced by the cardiac cycle observed in
+previous work~\cite{Olstad2019CiliaryDevelopment}, we apply sinusoidal forcing.
+The boundary $\Gamma_p$ has two separate regions: one located on the
+anterior ventricle and one on the posterior ventricle~(\Cref{fig:fig1}\fixme{d}, blue markers).
 For the normal pressure boundary condition, we set $\Tilde{p}(t) = 0$ on the anterior part and
-$\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The value of the amplitude $A$ was based on heuristics and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.
-
-\textbf{Baseline model.} This model version, regarded as the baseline model, considers both cilia and cardiac beating as driving mechanisms of fluid flow. We therefore consider the boundary conditions
+$\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The value of the amplitude
+$A$ was based on heuristics and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.
+
+\textbf{Baseline model.} The baseline flow model
+considers both cilia and cardiac beating as driving mechanisms of fluid flow.
+We therefore consider the boundary conditions
 \begin{subequations}
     \begin{alignat}{2}
-      \uu\cdot\nn = 0, \ \bsigpar &= \btau  \quad &&\mathrm{on} \ \Gc, \label{eq:slip_BC_modelC} \\
-      \uu\cdot\nn = 0, \ \bsigpar &= \mathbf{0}  \quad &&\mathrm{on} \ \Gs, \label{eq:freeslip_BC_modelC} \\
-      (\mu\nabla\uu - p\mathbf{I})\nn &= \Tilde{p}(t)\nn \quad &&\mathrm{on} \ \Gp, \label{eq:pressure_BC_modelC}
+      \uu\cdot\nn = 0, \ \bsigpar
+      &= \btau  \quad &&\mathrm{on} \ \Gc, \label{eq:slip_BC_modelC} \\
+      \uu\cdot\nn = 0, \ \bsigpar
+      &= \mathbf{0}  \quad &&\mathrm{on} \ \Gs, \label{eq:freeslip_BC_modelC} \\
+      (\mu\nabla\uu - p\mathbf{I})\nn
+      &= \Tilde{p}(t)\nn \quad &&\mathrm{on} \ \Gp, \label{eq:pressure_BC_modelC}
     \end{alignat}
@@
 where $\Gamma = \Gc\cup\Gs\cup\Gp$ is the boundary of $\Omega$.
-The quantities $\btau$ and $\Tilde{p}(t)$ are as introduced in the sections on model versions I and IIa.
-We handle the boundary conditions~\eqref{eq:slip_BC_modelC} and~\eqref{eq:freeslip_BC_modelC} as introduced for model version I, and the boundary condition~\eqref{eq:pressure_BC_modelC} is applied as discussed in the section on model IIa.
-The abstract weak formulation for model version 0 is then: find $(\uu,\, p)\in\VV\times Q$ such that
+The quantities $\btau$ and $\Tilde{p}(t)$ are as introduced in
+the sections of the other flow model versions. We handle the boundary
+conditions~\eqref{eq:slip_BC_modelC} and~\eqref{eq:freeslip_BC_modelC}
+as introduced for the cilia-only/no-cardiac model, and the boundary
+condition~\eqref{eq:pressure_BC_modelC} is applied as discussed in the section
+on the cardiac-only/no-cilia model. The abstract weak formulation for 
+the baseline model is then: find $(\uu,\, p)\in\VV\times Q$ such that
 \begin{subequations}
@@
 \begin{align}
-    \mathcal{A}(\uu, \vv) &= \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} -\intGp{\mu(\nabla\uu)^T\nn\cdot\vv}, \label{eq:stokes_bilinear_form}\\
+    \mathcal{A}(\uu, \vv) &= \intO{\rho\pdifft{\uu}\cdot\vv}
+                          + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)}
+                          -\intGp{\mu(\nabla\uu)^T\nn\cdot\vv}, \label{eq:stokes_bilinear_form}\\
     \mathcal{B}(\uu, q) &= -\intO{q\nabla\cdot\uu}, \label{eq:stokes_skew_form}\\
@@
 \subsection{Discretization of the Stokes equations}
-We will outline the discretization of the weak formulation~\cref{eq:abstract_weak_form_modelC,eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form} of the Stokes equations for model version 0.
-A similar approach can be used to discretize the weak formulation for the other model versions.
+We will outline the discretization of the weak
+formulation~\cref{eq:abstract_weak_form_modelC,
+eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
+of the Stokes equations for the baseline model. A similar approach can
+be used to discretize the weak formulation for the other model versions.
 First, we consider the spatial discretization of the weak formulation.
-We rewrite the weak form in terms of the discretized variables, denoted with the subscript $h$:
+We rewrite the weak form in terms of the discretized variables,
+denoted with the subscript $h$:
 \begin{subequations}
     \begin{alignat}{2}
-        \mathcal{A}(\uu_h, \vv_h) + \mathcal{B}(\vv_h, p_h) &= \mathcal{L}(\vv_h), &&\quad\forall\vv_h\in\VV_h, \\
+        \mathcal{A}(\uu_h, \vv_h) + \mathcal{B}(\vv_h, p_h)
+        &= \mathcal{L}(\vv_h), &&\quad\forall\vv_h\in\VV_h, \\
         \mathcal{B}(\uu_h, q_h) &= 0, &&\quad\forall q_h\in Q_h.
@@
 \end{subequations}%
-Our choice for the discrete spaces $\VV_h$ and $Q_h$ are finite elements of the Brezzi-Douglas-Marini family~\cite{Brezzi1985TwoProblems} and discontinuous Galerkin elements, respectively.
-Application of this scheme requires a stabilization of the bilinear form $\mathcal{A}(\uu_h, \vv_h)$.
+Our choice for the discrete spaces $\VV_h$ and $Q_h$ are finite elements
+of the Brezzi-Douglas-Marini family~\cite{Brezzi1985TwoProblems} and
+discontinuous Galerkin elements, respectively. Application of this scheme
+requires a stabilization of the bilinear form $\mathcal{A}(\uu_h, \vv_h)$.
 We apply the stabilization outlined in Hong~\emph{et al.}~\cite{Hong2016AEquations}.
@@
 \begin{equation*}
-    \avg{\uu} = \frac{\uu^+\cdot\nn^+ - \uu^-\cdot\nn^-}{2} \qquad\mathrm{and}\qquad \jump{\uu} = \uu^+ - \uu^-,
-\end{equation*}
-where $\nn$ is the normal vector on a facet separating two cells, where the plus and minus signs denote variables in each of the two cells.
-The normal vector is chosen such that it points towards the exterior of its corresponding cell.
-On the boundary, the operators are defined as $\avg{\uu} = \uu\cdot\nn$ and $\jump{\uu} = \uu$,
-with $\nn$ pointing to the exterior of the domain. We now define and add the bilinear form
+    \avg{\uu} = \frac{\uu^+\cdot\nn^+ - \uu^-\cdot\nn^-}{2}
+    \qquad\mathrm{and}\qquad \jump{\uu} = \uu^+ - \uu^-,
+\end{equation*}
+where $\nn$ is the normal vector on a facet separating two cells,
+where the plus and minus signs denote variables in each of the two cells.
+The normal vector is chosen such that it points towards the exterior of
+its corresponding cell. On the boundary, the operators are defined as
+$\avg{\uu} = \uu\cdot\nn$ and $\jump{\uu} = \uu$,
+with $\nn$ pointing to the exterior of the domain. We now define
+and add the bilinear form
 \begin{align*}
-    \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) &= \sum_{k\in K}\intF{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}\cdot \jump{P_{\nn}(\vv_h)}}\\
-    &-\sum_{k\in K}\intF{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}-\sum_{k\in K}\intF{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}
+    \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) &=
+    \sum_{k\in K}\intF{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}\cdot \jump{P_{\nn}(\vv_h)}}\\
+    &-\sum_{k\in K}\intF{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}
+    -\sum_{k\in K}\intF{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}
 \end{align*}
-to the discrete weak  formulation~\eqref{eq:no_stabilization_abstract_discrete_weak_form_modelC}, where $\mathcal{F} = \{\mathcal{F}_k : k\in K\}$ is the set of all interior facets $\mathcal{F}_k$ of the computational mesh.
-The parameter $\gamma>0$ is introduced to penalize jumps in the tangential components of the velocity across facets, wheras $h$ is the cell diameter of a mesh cell, defined as the maximal distance between two points in a cell.
-The semi-discrete weak formulation of the Stokes equations reads: find ($\uu_h, p_h$)$\in$($\VV_h, Q_h$) such that
+to the discrete weak  formulation~\eqref{eq:no_stabilization_abstract_discrete_weak_form_modelC},
+where $\mathcal{F} = \{\mathcal{F}_k : k\in K\}$ is the set of all interior facets
+$\mathcal{F}_k$ of the computational mesh. The parameter $\gamma>0$ is
+introduced to penalize jumps in the tangential components of the velocity
+across facets, wheras $h$ is the cell diameter of a mesh cell,
+defined as the maximal distance between two points in a cell.
+The semi-discrete weak formulation of the Stokes equations reads:
+find ($\uu_h, p_h$)$\in$($\VV_h, Q_h$) such that
 \begin{subequations}
     \begin{alignat}{2}
-        \mathcal{A}(\uu_h, \vv_h) + \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) + \mathcal{B}(\vv_h, p_h) &= \mathcal{L}(\vv_h), &&\quad\forall\vv_h\in\VV_h, \\
+        \mathcal{A}(\uu_h, \vv_h)
+        + \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h)
+        + \mathcal{B}(\vv_h, p_h)
+        &= \mathcal{L}(\vv_h), &&\quad\forall\vv_h\in\VV_h, \\
         \mathcal{B}(\uu_h, q_h) &= 0, &&\quad\forall q_h\in Q_h.
@@
 \end{subequations}%
-We solved~\eqref{eq:abstract_semi_discrete_weak_form_modelC} numerically with the penalty parameter $\gamma=10$.
-
-In time, we discretize the weak formulation~\eqref{eq:abstract_semi_discrete_weak_form_modelC} with the implicit Euler method.
+We solved~\eqref{eq:abstract_semi_discrete_weak_form_modelC}
+numerically with the penalty parameter $\gamma=10$.
+
+In time, we discretize the weak formulation~\eqref{eq:abstract_semi_discrete_weak_form_modelC}
+with the implicit Euler method.
 
@@
 \begin{equation}
-    \intO{\pdifft{c}\phi} + \intG{(\JJ\cdot\nn)\phi} - \intO{\JJ\cdot\nabla\phi} = 0.\label{eq:adv_diff_weak_formA1}
+    \intO{\pdifft{c}\phi} + \intG{(\JJ\cdot\nn)\phi}
+    - \intO{\JJ\cdot\nabla\phi} = 0.\label{eq:adv_diff_weak_formA1}
 \end{equation}
-The boundary integral of the total flux is handled differently for the three different model versions, depending on the boundary conditions considered.
-
-\textbf{Only-cilia/no-cardiac model.} We consider $\Omega$ to be closed and with impermeable walls, setting $\JJ\cdot\nn=0$ on $\Gamma$. The weak form is then reduced to
+The boundary integral of the total flux is handled differently for
+the three different model versions, depending on the boundary conditions considered.
+
+\textbf{Only-cilia/no-cardiac model.} We consider $\Omega$ to be
+a closed domain with impermeable walls, setting $\JJ\cdot\nn=0$ on $\Gamma$.
+The weak form is then reduced to
 \begin{equation*}
@@
 \end{equation*}
-we have the following abstract weak formulation for model version I: find $c\in W$ such that
+we get the following abstract weak formulation: find $c\in W$ such that
 \begin{equation*}
@@
 
-\textbf{Only-cardiac/no-cilia model.} When using the normal pressure boundary condition~\eqref{eq:modelB_pressure_BC} to model pulsatile flow,
-we have in- and outflow of cerebrospinal fluid and thus advection of $c$ on the pressure boundary $\Gp$.
+\textbf{Only-cardiac/no-cilia model.} When using the normal pressure
+boundary condition~\eqref{eq:modelB_pressure_BC} to model pulsatile flow,
+we have in- and outflow of cerebrospinal fluid and thus advection of
+$c$ on the pressure boundary $\Gp$.
 Let $\Gp=\Gin\cup\Gout$ and $\Gamma = \Gnf\cup\Gin\cup\Gout$, with 
@@
 Using the introduced approaches of handling the in- and outflow boundaries,
-the resulting abstract weak formulation for model version II is: find $c\in W$ such that
+the resulting abstract weak formulation for the cardiac-only/no-cilia model is:
+find $c\in W$ such that
 \begin{equation}
@@
 
-\textbf{Baseline model.} Since both free-slip and cilia tangential traction boundaries have the same no-flux boundary condition in the advection-diffusion equation, the weak formulation of the advection-diffusion equation for model version 0 is identical to that of model version II, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
+\textbf{Baseline model.} Since both free-slip and cilia tangential
+traction boundaries have the same no-flux boundary condition
+in the advection-diffusion equation, the weak formulation of
+the advection-diffusion equation for the baseline model is
+identical to that of the cardiac-only/no-cilia model,
+defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
 
 \subsection{Discretization of the advection-diffusion equation}
-We outline the discretization of the advection-diffusion weak formulation for model version 0, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
+We outline the discretization of the advection-diffusion weak formulation
+for the baseline model, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
 The weak formulation is discretized with a symmetric interior-penalty method using discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}.
@@
     \centering
-    \caption{Error norms of the velocity $\uu_h$ in the $\mathbf{L}^2$ and $\mathbf{H}^1$ norms, the pressure $p_h$ in the $L^2$ norm, and the error in the maximum velocity magnitude $\uu_{h, {\mathrm{mag}}}$ for mesh refinement on a cylinder mesh with model version I.
+    \caption{Error norms of the velocity $\uu_h$ in the
+    $\mathbf{L}^2$ and $\mathbf{H}^1$ norms,
+    the pressure $p_h$ in the $L^2$ norm,
+    and the error in the maximum velocity magnitude $\uu_{h, {\mathrm{mag}}}$
+    for mesh refinement on a cylinder mesh with the only-cilia/no-cardiac flow model.
     Additionally, we report the $L^2$ norm of the divergence of the velocity.
-For all error norms, convergence rates calculated with~\eqref{eq:convergence_order_estimate} are given in parentheses.}\label{tab:cylinder_error_rates}
+    For all error norms, convergence rates calculated
+    with~\eqref{eq:convergence_order_estimate} are given
+    in parentheses.}\label{tab:cylinder_error_rates}
     \begin{tabular}{cc|ccccc}
         \toprule
-        $h/h_0$ & \# dofs & $\normltwovec{\uu_h - \uu_{\mathrm{ex}}}$ & $\Hnorm{\uu_h - \uu_{\mathrm{ex}}}$ & $\normltwo{p_h - p_{\mathrm{ex}}}$ & $\normlinf{u_h} -\normlinf{u_{\mathrm{ex}}}$ & $\normltwo{\nabla\cdot\uu_h}$\\
+        $h/h_0$ & \# dofs &
+        $\normltwovec{\uu_h - \uu_{\mathrm{ex}}}$
+        & $\Hnorm{\uu_h - \uu_{\mathrm{ex}}}$
+        & $\normltwo{p_h - p_{\mathrm{ex}}}$
+        & $\normlinf{u_h} -\normlinf{u_{\mathrm{ex}}}$
+        & $\normltwo{\nabla\cdot\uu_h}$\\ 
         \midrule 
-        1    & 8652 & \num{2.3e-02} (---) & \num{4.3e-01} (---) & \num{5.4e-01} (---) & \num{2.4e-02} (---) & \num{1.4e-07} \\  
-        1/2  & 41190 & \num{9.3e-03} (1.30) & \num{2.8e-01} (0.61) & \num{3.7e-01} (0.53) & \num{5.0e-03} (2.25) & \num{2.8e-08} \\  
-        1/4  & 255016 & \num{3.5e-03} (1.42)    & \num{1.4e-01} (1.00) & \num{2.1e-01} (0.79) & \num{1.4e-03} (1.83) & \num{7.3e-11} \\         
-        1/8  & 1855337 & \num{1.3e-03} (1.46) & \num{6.9e-02}  (1.03) & \num{1.1e-01} (0.94)  & \num{6.7e-04} (1.08) & \num{1.4e-10} \\   
+        1    & 8652    & \num{2.3e-02}  (--)  & \num{4.3e-01}   (--)  & \num{5.4e-01}  (--) 
+        & \num{2.4e-02} (---) & \num{1.4e-07} \\
+
+        1/2  & 41190   & \num{9.3e-03} (1.30) & \num{2.8e-01}  (0.61) & \num{3.7e-01} (0.53)
+        & \num{5.0e-03} (2.25) & \num{2.8e-08} \\
+
+        1/4  & 255016  & \num{3.5e-03} (1.42) & \num{1.4e-01}  (1.00) & \num{2.1e-01} (0.79)
+        & \num{1.4e-03} (1.83) & \num{7.3e-11} \\
+
+        1/8  & 1855337 & \num{1.3e-03} (1.46) & \num{6.9e-02}  (1.03) & \num{1.1e-01} (0.94)
+        & \num{6.7e-04} (1.08) & \num{1.4e-10} \\   
         \bottomrule
@@
 To verify the model implementation with the zebrafish brain ventricles mesh,
-we compared velocity norms for varying degrees of refinement of the brain ventricles mesh~(\Cref{tab:ventricles_norms_BDM}).
+we compared velocity norms for varying degrees of refinement of the brain ventricles
+mesh~(\Cref{tab:ventricles_norms_BDM}).
 For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$.
@@
     \centering
-    \caption{Velocity norms under mesh refinement on the brain ventricles mesh using model version I with $\btau = \tau P_{\nn}(\rr)$, using $\tau = 6.5\times 10^{-4}$ Pa, $\rr = (1, 0, 1)$ in the ventral middle ventricle and, $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle.}\label{tab:ventricles_norms_BDM}
+    \caption{Velocity norms under mesh refinement
+    on the brain ventricles mesh using the only-cilia/no-cardiac flow model
+     with $\btau = \tau P_{\nn}(\rr)$, using
+     $\tau = 6.5\times 10^{-4}$ Pa,
+     $\rr = (1, 0, 1)$ in the ventral middle ventricle and,
+     $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and
+     the anterior ventricle.}\label{tab:ventricles_norms_BDM}
     \begin{tabular}{cc|cccc}
         \toprule
-        \# cells & \# dofs & $\normlinf{u_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$ & $\frac{1}{|\Gc|}\normlinf{u_h}$ $\left[\frac{1}{\mathrm{mm\cdot s}}\right]$ & $\frac{1}{\vert\Omega\vert}\normltwovec{\uu_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$ & $\normltwo{\nabla\cdot\uu_h}$ $\left[\frac{\mathrm{mm^3}}{\mathrm{s^2}}\right]$\\
+        \# cells & \# dofs &
+        $\normlinf{u_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$
+        & $\frac{1}{|\Gc|}\normlinf{u_h}$ $\left[\frac{1}{\mathrm{mm\cdot s}}\right]$
+        & $\frac{1}{\vert\Omega\vert}\normltwovec{\uu_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$
+        & $\normltwo{\nabla\cdot\uu_h}$ $\left[\frac{\mathrm{mm^3}}{\mathrm{s^2}}\right]$\\
         \midrule 
@@
 
-\section{Quantification of particle transport}\label{sec:appC_particle_transport}
+\section{Quantification of velocities in particle tracking}\label{sec:appC_particle_transport}
 Particle tracking data~\cite{Olstad2019CiliaryDevelopment} was analyzed.
@@
 in absolute values were 10.2 $\mu$m/s and 2.4 $\mu$m/s for $\overline{u}_x$ and $\overline{u}_y$,
-respectively. We used flow model II (only cardiac forces) to tune the pressure boundary condition
+respectively. We used the only-cardiac/no-cilia flow model to tune the pressure boundary condition
 amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude

### 2025-02-04 paper/main.tex
clean, draft conclusion, prepare comments

@@
 \usepackage{graphicx}
-\usepackage{tkz-euclide} % draw tikz pictures
 \usepackage{subcaption}
@@
 \author[1]{Miroslav Kuchta} 
-\author[X]{Inyoung Jeong} % OK?
+\author[\fixme{X}]{Inyoung Jeong} % OK?
 \author[1,3,+]{Marie E.~Rognes} % OK order?
 \author[2,+, *]{Nathalie Jurisch-Yaksi}
-\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
-\affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway}
+\affil[1]{Department of Numerical Analysis and Scientific Computing,
+Simula Research Laboratory, Oslo, Norway}
+\affil[2]{\fixme{@Nathalie is this correct?: Department of Clinical and Molecular Medicine,
+Norwegian University of Science and Technology, Trondheim, Norway \\
+Same affiliation for Inyoung?}}
 \affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
-\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no} \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
+\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}
+\href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
 \affil[+]{these authors contributed equally to this work}
@@
 injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}d).
+From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}\fixme{d}).
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
@@
 Parts of the ventricular surfaces were marked to be lined with
-motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}d, magenta markers).
+motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}\fixme{d}, magenta markers).
 \begin{figure}%[hbt!]
@@
 structures~\cite{Olstad2019CiliaryDevelopment}
-within the brain ventricles (\Cref{fig:fig1}a--c).
+within the brain ventricles (\Cref{fig:fig1}\fixme{a--c}).
 In addition, cardiac pulsations induces pulsatile CSF flow.
@@
 \subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:fig1}d, magenta markers),
+On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:fig1}\fixme{d}, magenta markers),
 we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
@@
 $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
-boundary $\Gp$~(\Cref{fig:fig1}d, blue markers).
+boundary $\Gp$~(\Cref{fig:fig1}\fixme{d}, blue markers).
 Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
@@
 \subsection*{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Cref{fig:fig1}b, c, we carried out
+To recover the flow fields shown in~\Cref{fig:fig1}\fixme{b, c}, we carried out
 particle tracking in a larval zebrafish injected with fluorescent beads.
@@
 Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:fig1}b, c.
+covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:fig1}\fixme{b, c}.
 
@@
 
-We seek to model the compartimentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}b--c).
+We seek to model the compartimentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}\fixme{b--c}).
 To characterize CSF flow patterns predicted by
@@
 system, with large-scale vortex structures in the anterior and middle
-ventricles~(\Cref{fig:fig1}e). The highest velocities ($26.5$ \textmu m/s)
+ventricles~(\Cref{fig:fig1}\fixme{e}). The highest velocities ($26.5$ \textmu m/s)
 occur in the vicinity of the dorsal cilia in the middle ventricle.
@@
 To examine the effect of cardiac pressure pulsations,
-we next consider a no-cilia model variation. In this scenario, the simulated CSF
-flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:fig1}g),
+we next consider a no-cilia model variation. In this scenario, the vortex structures
+generated by the ciliary motion vanish. The simulated CSF
+flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:fig1}\fixme{g}),
 with a peak velocity magnitude of $4.8$ \textmu m/s. At each time instant, the flow
@@
 
-We now consider the baseline model, simulating flow driven by both cilia
+Next we consider the baseline model, simulating flow driven by both cilia
 and cardiac pulsations. We observe persistent flow features,
 with vortex-structures in the anterior and middle ventricles
-and directional flow in the posterior ventricle (\Cref{fig:fig1}e,
+and directional flow in the posterior ventricle (\Cref{fig:fig1}\fixme{e},
 \fixme{Supplementary video 1}). These characteristic patterns suggest
@@
 we observed a slower increase of fluorescence intensity,
-resulting in $\sim X\%$ (ROI 2) and $\sim 45\%$ (ROI 4)
+resulting in $\sim 45\%$ (ROI 2) and \fixme{$\sim X\%$ (ROI 4)}
 higher mean times-to-threshold in the \emph{smh}
@@
 and more rapid transport to the posterior ventricle (ROI 6).
-In contrast, removal of telencephalic cilia did not alter the evolution of the
+On the other hand, removal of telencephalic cilia did not alter the evolution of the
 mean concentration $\cbar$ with time (\Cref{fig:figure5_compare_cilia_modifications}b).
@@
 
-In contrast, we identified that transport of larger molecules
+Meanwhile, we identified that transport of larger molecules
 (thus with smaller diffusion coefficients),
@@
 
-\subsection*{Impact of cilia properties and ventricular geometry}
-To gain further insights into how CSF distribution depends on cilia properties and geometries,
+\subsection*{Impact of cilia \fixme{properties} and ventricular geometry}
+To gain further insights into how CSF distribution depends on cilia \fixme{properties (@Nathalie: do we really
+investigate properties? Rather location or population?)} and geometries,
 we manipulated certain parameters in our models. First, we removed cilia in specific regions of
@@
 We previously identified large inter-individual variation in ventricular size and
-CSF velocities between larva at given developmental stages and throughout development~\fixme{@Nathalie: Add some citation here? Olstad/D'Gama}.
+CSF velocities between larva at given developmental stages and throughout
+development~\fixme{@Nathalie: Add some citation here? Olstad 2019/D'Gama 2025?}.
 Our results suggest that these two parameters may well co-vary and explain the variation.
@@
 Altogether, our model is flexible and thereby allows \emph{in silico} testing of
-further hypotheses on the contribution of ciliated lineages and geometries.
-We trust that it will be useful as a basis for future analysis of CSF dynamics in more complex geometries.
+further hypotheses on the effects of ciliated lineages and ventricular morphology on
+CSF flow and intraventricular transport.
+We trust that it will be useful as a basis for future analysis of
+CSF dynamics in more complex geometries \fixme{and other animal species}.
 
@@
 refer to this~\cite{Siyahhan2014FlowVentricles} and this~\cite{Yoshida2022EffectVentricles}
-paper that studied this in human brain ventricles. Include a discussion of what happened when these papers removed cilia.}
+paper that studied this in human brain ventricles.
+Include a discussion of what happened when these papers removed cilia.}
 
@@
 flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
-It has been observed, both previously and in this work, that the fluid velocity increases towards the wall~(\Cref{fig:fig1}c).
+It has been observed, both previously and in this work, that the fluid velocity increases
+towards the wall~(\Cref{fig:fig1}\fixme{c}).
 Using slip boundary conditions allows for this behavior.
-A couple of previous continuum model simulation studies of cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
+A couple of previous continuum model simulation studies of
+cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
 have modeled cilia as body forces. We chose to model the cilia as a force exerted tangentially on the boundary.
@@
 \begin{equation*}
-    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{l} = \frac{\num{2.5e-3} \ \mathrm{Pa}}{15 \ \mu\mathrm{m}} = 169 \ \mathrm{N/m^3},
+    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{l}
+        = \frac{\num{2.5e-3} \ \mathrm{Pa}}{15 \ \mu\mathrm{m}}
+        = 169 \ \mathrm{N/m^3},
 \end{equation*}
@@
 since these boundary conditions appear naturally in the weak form of the
-Stokes equations~(\cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
+Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
 elements were to be used, the impermeability boundary condition must
@@
 derived in a mesh-dependent broken $H^1$-norm for $\uu$ and the $L^2$-norm for the pressure. The respective 
-errors are expected to decay with order $k$, see for example Cockburn~\emph{et al.}~\cite{Cockburn2005AEquations}.
+errors are expected to decay with order $k$,
+see for example Cockburn~\emph{et al.}~\cite{Cockburn2005AEquations}.
 For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
@@
 
-\subsection*{The role of motile cilia in intraventricular flow and transport}
+\subsection*{The role of motile cilia in intraventricular flow and transport
+\fixme{Might be merged with further work.}}
 Our work has studied CSF flow and solute distribution
@@
     \item improved advection-diffusion equation BCs
-    \item Modeling deformation of the ventricles and investigating how the arising flow compares with pulsatile flow observed in experiments
+    \item Modeling deformation of the ventricles
+    and investigating how the arising flow compares with pulsatile flow observed in experiments
 \end{itemize}
 
+\fixme{Based on our conclusion that advection drives transport of larger proteins, could
+we make some bold claims about advective transport of exosomes/extracellular vesicles in the
+ventricles, and the importance of this?}
+
 \section*{Conclusion}
-We have presented experimental data from imaging photoconversion of a fluorescent protein in zebrafish brain ventricles, both for healthy animals and mutant animals with ciliary dysfunction.
-Experimental results indicate that cilia only affect the local distribution of proteins, while most of the transport is by diffusion.
-We also presented a numerical model of flow and transport in zebrafish brain ventricles based on finite element methods.
-A realistic brain ventricles geometry from medical imaging was used to perform a computational study with the presented model.
-The flow model reproduces qualitatively the experimentally observed flow features of cilia-mediated cerebrospinal fluid flow in zebrafish brain ventricles.
-Coupling the flow to the transport model, we estimated how slowly or rapidly molecules of varying size are transported in the ventricles.
-Simulations indicate that cilia-driven advection is important for transport of larger molecules.
+We have presented a numerical model
+of cerebrospinal fluid flow and solute transport in
+zebrafish brain ventricles based on finite element methods.
+A realistic brain ventricles geometry from medical imaging was used to perform a
+computational study with the presented model. The flow model reproduces
+the experimentally observed flow features of cilia-mediated cerebrospinal fluid
+flow in zebrafish brain ventricles. Coupling the flow to the transport model,
+we estimated how slowly or rapidly molecules of varying size are transported in
+the ventricles. Simulations indicate that cilia-driven advection is important
+for transport of larger molecules. 
+The numerical model was validated with experiments, measuring the movement of
+a photoconverted fluorescent protein in zebrafish brain ventricles,
+both for healthy animals and mutant animals with ciliary dysfunction.
+We observed good alignment between computational and experimental results.
+Experimental results indicate that cilia only affect the local distribution of small proteins,
+while most of the transport is governed by diffusion.
 
@@
 We will outline the discretization of the weak
-formulation~\cref{eq:abstract_weak_form_modelC,
+formulation~\Cref{eq:abstract_weak_form_modelC,
 eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
@@
 and $\mathbf{H}^1$ error norms for $\uu_h$, and the $L^2$ error norm for
-$p_h$~(\cref{tab:cylinder_error_rates}). Based on the error norm calculations,
+$p_h$~(\Cref{tab:cylinder_error_rates}). Based on the error norm calculations,
 we also calculated the experimental order of convergence~(\Cref{subsec:norms_and_eoc}).

### 2025-02-04 paper/main.tex
clean plot scripts, add seaborn dependency

@@
 \author[1]{Miroslav Kuchta} 
-\author[\fixme{X}]{Inyoung Jeong} % OK?
+\author[FIX ME]{Inyoung Jeong} % OK?
 \author[1,3,+]{Marie E.~Rognes} % OK order?
@@
 \affil[2]{\fixme{@Nathalie is this correct?: Department of Clinical and Molecular Medicine,
-Norwegian University of Science and Technology, Trondheim, Norway \\
+Norwegian University of Science and Technology, Trondheim, Norway\\
 Same affiliation for Inyoung?}}
@@
 Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz,
-while other fluid dynamic processes in the brain are slower and span larger three-dimensional volumes.
+while other fluid dynamic processes in the brain are slower and span larger volumes.
 Most studies until now have analyzed one process at a time, especially in mammals.
@@
 The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
-maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). 
+maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
@@
 conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
-The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a
+The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
 14/10 hr light/dark cycle.
@@
 Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
-fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
+fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
 tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
@@
 The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was
+The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
 used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14
-$\mu$L of assay mix; 1.86 $\mu$L of RO water.
+For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
+\textmu L of assay mix; 1.86 \textmu L of RO water.
 
@@
 For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software
-were used. A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel)
+were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
 of the dorsoposterior diencephalic ventricle with 100\% laser power.
@@
 Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:fig1}\fixme{b, c}.
+covering a distance of at least 8.8 \textmu m, were plotted in~\Cref{fig:fig1}\fixme{b, c}.
 
@@
 we observed a slower increase of fluorescence intensity,
-resulting in $\sim 45\%$ (ROI 2) and \fixme{$\sim X\%$ (ROI 4)}
+resulting in $\sim 45\%$ (ROI 2) and $\sim 25\%$ (ROI 4)
 higher mean times-to-threshold in the \emph{smh}
@@
 affected when removing cilia in the dorsal diencephalic cilia,
-as the maximum velocity dropped from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
+as the maximum velocity dropped from 27.7 \textmu m/s to 8.0 \textmu m/s.
 \emph{In vivo}, these cilia generate the strongest flow at
@@
 In contrast, removing telencephalic and ventral diencephalic had minimal
-impact and resulted in maximum velocities of 27.7 $\mu$m/s or 27.2 $\mu$m/s, respectively.
+impact and resulted in maximum velocities of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
 Changes in the transport dynamics of Dendra2 were most prominent when removing the dorsal cilia
@@
 For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance
-$L=200$ $\mu$m from the middle to the posterior ventricle is approximately 24500 s.
+$L=200$ \textmu m from the middle to the posterior ventricle is approximately 24500 s.
 Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen
@@
 refinement near the ciliated boundaries in the case that a
-body force were to be applied in a $\sim$ 5 $\mu$m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.
+body force were to be applied in a $\sim$ 5 \textmu m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.
 
@@
 Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
-0.26 $\mu$m/s and the mean of $\overline{u}_y$ was 0.08 $\mu$m/s. The maximum mean velocities
-in absolute values were 10.2 $\mu$m/s and 2.4 $\mu$m/s for $\overline{u}_x$ and $\overline{u}_y$,
+0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s. The maximum mean velocities
+in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for $\overline{u}_x$ and $\overline{u}_y$,
 respectively. We used the only-cardiac/no-cilia flow model to tune the pressure boundary condition
 amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude
-of 4.8 $\mu$m/s, which is close to the maximum observed in the particle tracking data when
-rejecting the outlier at around 10 $\mu$m/s; (ii) it yields a time-averaged mean velocity
-of 0.89 $\mu$m/s, which is close to the mean observed in the particle tracking data.
+of 4.8 \textmu m/s, which is close to the maximum observed in the particle tracking data when
+rejecting the outlier at around 10 \textmu m/s; (ii) it yields a time-averaged mean velocity
+of 0.89 \textmu m/s, which is close to the mean observed in the particle tracking data.
 \begin{figure}[H]

### 2025-02-04 src/plot_ROI_time_to_threshold.py

@@ -8,7 +8,7 @@ import matplotlib.pyplot as plt
 
 from mpi4py       import MPI
 from basix.ufl    import element
-from imports.mesh import create_ventricle_volumes_meshtags
+from utilities.mesh import create_ventricle_volumes_meshtags
 
 # Set latex text properties
 plt.rcParams.update({
@@ -20,7 +20,7 @@ gm   = dfx.mesh.GhostMode.shared_facet
 k = 1 # element degree
 model_version = 'C'
 molecule = 'D3'
-mesh_input_filename = "output/flow/checkpoints/pressure+original/model_C/velocity_data_dt=0.02252"
+mesh_input_filename = "../output/flow/checkpoints/pressure+original/model_C/velocity_data_dt=0.02252"
 mesh = a4d.read_mesh(comm=comm, filename=mesh_input_filename, engine="BP4", ghost_mode=gm)
 
 # Get mesh properties
@@ -52,9 +52,9 @@ volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=M
 # Load data c_hat, the total concenctration in each ROI
 # with open(f'output/transport/model_B_{molecule}_DG1_pressureBC/injection_site_middle_dorsal_posterior/npy_data/c_hats.npy', 'rb') as file:
 #     c_hats_B = np.load(file)
-with open("./output/transport/original+mod_ROI/log_model_C_D3_DG1_pressureBC/injection_site_middle_dorsal_posterior/npy_data/c_hats.npy", "rb") as file:
+with open("../output/transport/original+mod_ROI/log_model_C_D3_DG1_pressureBC/injection_site_middle_dorsal_posterior/npy_data/c_hats.npy", "rb") as file:
     c_hats_B = np.load(file)
-with open(f"./output/transport/original/log_model_C_D3_DG1_pressureBC/injection_site_middle_dorsal_posterior/npy_data/c_hats.npy", "rb") as file:
+with open(f"../output/transport/original/log_model_C_D3_DG1_pressureBC/injection_site_middle_dorsal_posterior/npy_data/c_hats.npy", "rb") as file:
     c_hats_C = np.load(file)
 
 # Scale the total concentrations in the ROIs by the volume of the respective ROI
@@ -106,12 +106,13 @@ for idx, tag in enumerate(ROI_tags):
[…]

### 2025-02-04 src/plot_compare_experiments_control_mutant.py

@@ -16,7 +16,7 @@ plt.rcParams.update({
 plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
 
 # Set data directory and load .mat files
-data_dir = "./data_photoconversion/aggregated_data/"
+data_dir = "../data/data_photoconversion/aggregated_data/"
 metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
 colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
 control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data
@@ -94,6 +94,8 @@ for idx, tag in enumerate(ROI_tags):
     # Plot horizontal line at means
     control_mean = df['control'].mean()
     mutant_mean = df['mutant'].mean()
+    print("Control mean: ", control_mean)
+    print("Mutant mean: ", mutant_mean)
     ca_ttt.axhline(y=control_mean, xmin=0.1, xmax=0.4, color='k', linewidth=3)
     ca_ttt.axhline(y=mutant_mean, xmin=0.6, xmax=0.9, color='k', linewidth=3)
 
@@ -115,8 +117,8 @@ for idx, tag in enumerate(ROI_tags):
 
 # Set tight layout and show (and optionally save)
 fig_dff.tight_layout(); fig_ttt.tight_layout()
-save_figs = 1
+save_figs = 0
 if save_figs:
-    fig_dff.savefig(f"output/illustrations/experiments_dff_compare_control_mutant.png")
-    fig_ttt.savefig(f"output/illustrations/experiments_ttt_compare_control_mutant.png")
+    fig_dff.savefig(f"../output/illustrations/experiments_dff_compare_control_mutant.png")
+    fig_ttt.savefig(f"../output/illustrations/experiments_ttt_compare_control_mutant.png")
 plt.show()

### 2025-02-04 src/plot_compare_simulations_cilia_regions.py

@@ -7,7 +7,7 @@ import adios4dolfinx     as a4d
 import matplotlib.pyplot as plt
 
 from mpi4py       import MPI
-from imports.mesh import create_ventricle_volumes_meshtags
+from utilities.mesh import create_ventricle_volumes_meshtags
 
 # Set matplotlib properties
 plt.rcParams.update({
@@ -22,7 +22,7 @@ comm = MPI.COMM_WORLD # MPI Communicator
 gm   = dfx.mesh.GhostMode.shared_facet
 k = 1 # element degree
 model_version = 'C'
-original_mesh_input_filename = f"output/flow/checkpoints/variable_tau/pressure+original/model_{model_version}/velocity_data_dt=0.02252"
+original_mesh_input_filename = f"../output/flow/checkpoints/variable_tau/pressure+original/model_{model_version}/velocity_data_dt=0.02252"
 mesh = a4d.read_mesh(comm=comm, filename=original_mesh_input_filename, engine="BP4", ghost_mode=gm)
 ct, ROI_tags = create_ventricle_volumes_meshtags(mesh)
 dx = ufl.Measure('dx', domain=mesh, subdomain_data=ct)
@@ -30,10 +30,10 @@ volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=M
 volumes[3] += volumes[2]+volumes[1]+volumes[0]
 
 # Load data c_hat, the total concenctration in each ROI
-with open(f"output/transport/results/variable_tau/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_original    = np.load(file)
-with open(f"output/transport/results/variable_tau+rm_dorsal/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_dorsal  = np.load(file)
-with open(f"output/transport/results/variable_tau+rm_ventral/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_ventral = np.load(file)
-with open(f"output/transport/results/variable_tau+rm_telencephalic/original/log_model_{model_version}_D3_DG1_pressureBC/data/c_hats.npy", 'rb') as file: c_bar_telenc = np.load(file)
[…]

### 2025-02-04 src/plot_compare_simulations_models.py

@@ -6,7 +6,7 @@ import adios4dolfinx     as a4d
 import matplotlib.pyplot as plt
 
 from mpi4py       import MPI
-from imports.mesh import create_ventricle_volumes_meshtags
+from utilities.mesh import create_ventricle_volumes_meshtags
 
 # Set matplotlib properties
 plt.rcParams.update({
@@ -24,7 +24,7 @@ molecule = 'D3'
 tau_version  = 'original_tau'
 tau_version  = 'variable_tau'
 mesh_version = 'original'
-mesh_input_filename = f"output/flow/checkpoints/{tau_version}/pressure+{mesh_version}/model_C/velocity_data_dt=0.02252"
+mesh_input_filename = f"../output/flow/checkpoints/{tau_version}/pressure+{mesh_version}/model_C/velocity_data_dt=0.02252"
 mesh = a4d.read_mesh(comm=comm, filename=mesh_input_filename, engine="BP4", ghost_mode=gm)
 
 # Create meshtags and calculate ROI volumes
@@ -34,9 +34,9 @@ volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=M
 volumes[3] += volumes[2]+volumes[1]+volumes[0] # Add ROI 1, 2, 3 volumes to ROI 4 volume
 
 # Load data c_bar, the total concenctration in each ROI
-with open(f"./output/transport/results/original_tau/{mesh_version}/log_model_B_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
+with open(f"../output/transport/results/original_tau/{mesh_version}/log_model_B_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
     c_bar_B = np.load(file)
-with open(f"./output/transport/results/{tau_version}/{mesh_version}/log_model_C_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
+with open(f"../output/transport/results/{tau_version}/{mesh_version}/log_model_C_{molecule}_DG1_pressureBC/data/c_hats.npy", "rb") as file:
     c_bar_C = np.load(file)
 
 # Scale the total concentrations in the ROIs by the volume of the respective ROI
@@ -141,6 +141,6 @@ for idx, tag in enumerate(ROI_tags):
 fig_c.tight_layout(); fig_t.tight_layout()
 save_figs = 1
 if save_figs:
[…]

### 2025-02-04 src/plot_fluorescence_intensities.py

@@ -13,7 +13,7 @@ plt.rcParams.update({
 plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
 
 # Set data directory and load .mat files
-data_dir = "./data_photoconversion/aggregated_data/"
+data_dir = "../data/data_photoconversion/aggregated_data/"
 metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
 colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
 control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data
@@ -54,10 +54,12 @@ ax2.set_xlabel("Time [s]", fontsize=60, labelpad=25)
 ax2.set_ylabel(r"Fluoresc. intensity change $\Delta F$ [-]", fontsize=60, labelpad=25)
 ax2.legend(loc='upper left', fontsize=50, frameon=True, fancybox=False, edgecolor='k')
 ax2.tick_params(labelsize=60)
+
 fig1.tight_layout()
 fig2.tight_layout()
-save_figs = 1
+
+save_figs = 0
 if save_figs:
-    fig1.savefig(f"output/illustrations/experimental_time_evolution_control.png")
-    fig2.savefig(f"output/illustrations/experimental_time_evolution_mutant.png")
+    fig1.savefig(f"../output/illustrations/experimental_time_evolution_control.png")
+    fig2.savefig(f"../output/illustrations/experimental_time_evolution_mutant.png")
 plt.show()

### 2025-02-04 src/plot_mean_concentrations.py

@@ -21,19 +21,19 @@ plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-seri
 
 comm = MPI.COMM_WORLD # MPI Communicator
 gm   = dfx.mesh.GhostMode.shared_facet
-colors = loadmat("./data_photoconversion/aggregated_data/colors")['color'] # The colors used for plotting
+colors = loadmat("../data/data_photoconversion/aggregated_data/colors")['color'] # The colors used for plotting
 fig_num = 1 # Figure number index
 
 # Directories
-flow_dir = './output/flow/checkpoints/'
-transport_dir = './output/transport/results/'
+flow_dir = '../output/flow/checkpoints/'
+transport_dir = '../output/transport/results/'
 
 # Problem version
 model_version = 'C'
 molecules = ['D1', 'D2', 'D3']
 tau_version  = 'variable_tau'
 mesh_version = 'original'
-output_dir = f'output/illustrations/{mesh_version}/{tau_version}/'
+output_dir = f'../output/illustrations/{mesh_version}/{tau_version}/'
 
 # Read mesh
 mesh_input_filename = flow_dir+f"{tau_version}/pressure+{mesh_version}/model_{model_version}/velocity_data_dt=0.02252"
@@ -70,7 +70,7 @@ for idx, molecule in enumerate(molecules):
 
     # Scale the total concentrations in the ROIs by the volume of the respective ROI
     for i in ROI_tags: c_bars[:, i-1] /= volumes[i-1]
-    print("end_C: ", c_bars[-1, :])
+    print("c_bar at final time: ", c_bars[-1, :])
 
     # Write final concentration values to file
     with open(file=output_dir+f"final_c_bar_values.txt", mode="w+" if idx==0 else "a+") as file:

### 2025-02-04 src/plot_slice_time_to_threshold.py

@@ -72,8 +72,8 @@ plotter.camera.focal_point = (x_mid, y_max, z_mid)
 plotter.camera.zoom(0.275)
 
 # Display the plot and save to file
-save_plot = 1
-if save_plot:
+save_fig = 1
+if save_fig:
     output_filename = f'../output/illustrations/original/{tau_version}/slice_time_to_threshold_model{model_version}_{molecule}'
     plotter.show(screenshot=output_filename+'.png')
 else:

### 2025-02-04 src/plot_slices_concentration.py

@@ -8,6 +8,7 @@ import matplotlib.pyplot as plt
 
 from mpi4py    import MPI
 from basix.ufl import element
+from utilities.create_colormap import register_colormaps
 
 """ Visualize concentration slices in a 3x3 figure. """
 
@@ -82,7 +83,6 @@ plot_shape = (3, 3)
 plotter = pv.Plotter(shape=plot_shape, window_size=[1600, 900], border=False)
 
 # Set colormap
-from create_colormap import register_colormaps
 register_colormaps()
 cmap = "wgk"
 
@@ -120,8 +120,8 @@ for i in range(plot_shape[0]):
         m += 1
         
 # Display the plot and save to file
-save_plot = 0
-if save_plot:
+save_fig = 0
+if save_fig:
     output_filename = f'../output/illustrations/original/{tau_version}/concentration_slices_DG{k}_varying_D'
     plotter.show(screenshot=output_filename+'.png')
 else:

### 2025-02-05 paper/main.tex
caption figure 2

@@
     Dendra ($D_1$), STM+GFP ($D_2$) and Exosomes ($D_3$).
-    \mer{MER: I think you should show on the same color scale here in a)
-    (the range of values lets you and then it is possible to compare).
-    Split a into a, b, c. Show e) first (so that e) becomes a)}.
-    \textbf{a.} Slices in the $xz$-plane ($y=0.140$ mm,
-    the center of the geometry) showing the concentration field simulated
-    with diffusion coefficients $D_1$, $D_2$ and $D_3$ for three
-    time instants $t=45.0$ s, $t=112.6$ s, $t=450.5$ s.
-    Note that the colorbars indicating the magnitude of $c$ have different limits for each column.
-    \textbf{b--d.} Mean concentration $\cbar$ in each region of interest (ROI)
+    \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
+    \textbf{b--d.} Slice of the concentration field simulated
+    with diffusion coefficients $D_1$, $D_2$ and $D_3$ for eight time instants covering the
+    time range from 45 seconds to 790 seconds, corresponding to 100 to 1750 cardiac cycles.
+    Slices are taken in the $xz$-plane ($y=0.140$ mm, the center of the geometry).
+    The colorbar is scaled so the maximum is the maximum concentration of the Dendra2 
+    condentration field slice at the last time instant.
+    \textbf{e--g.} Mean concentration $\cbar$ in each region of interest (ROI)
     as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively. 
-    \textbf{e.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
-    \textbf{f.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a
+    \textbf{h.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a
     threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.

### 2025-02-05 paper/main.tex
fix figure and panel references

@@
 interest in the dorsal region of the middle ventricle (ROI 1)
-(\Cref{fig:fig2}\fixme{e/x}). In particular, we consider the spread of
+(\Cref{fig:fig2}a). In particular, we consider the spread of
 a solute concentration with a given molecular diffusion coefficient,
@@
 Exosomes, the advection induced by the CSF flow dominates diffusion
-(\Cref{fig:fig2}a). The vortex structures of the velocity field
+(\Cref{fig:fig2}b). The vortex structures of the velocity field
 carry over into the concentration field, indicating that transport
@@
 obfuscated, and the solute spreads more uniformly throughout the
-ventricular geometry (\Cref{fig:fig2}\fixme{x-y}). Notably, the
+ventricular geometry (\Cref{fig:fig2}c, d). Notably, the
 smaller solutes with higher diffusion coefficients spread more quickly
-to regions distal to the photoconversion site (\Cref{fig:fig2}\fixme{z}).
+to regions distal to the photoconversion site.
 \begin{figure}%[H]
@@
 concentrations $\cbar_i(t)$ as functions of time
-(\Cref{fig:fig2}\fixme{b--d}) and
+(\Cref{fig:fig2}e--g) and
 the times $\hat{t}$ when the mean concentrations $\cbar_i$ first exceed
-a threshold value $\hat{c}$ (\Cref{fig:fig2}\fixme{f})
-in 6 regions of interest (ROIs) (\Cref{fig:fig2}\fixme{e}).
+a threshold value $\hat{c}$ (\Cref{fig:fig2}h)
+in 6 regions of interest (ROIs) (\Cref{fig:fig2}a).
 The dynamics at the site of photoconversion (ROI 1)
@@
 For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
-(\Cref{fig:fig2}\fixme{b--d}),
-which results in smaller time to threshold
-(\Cref{fig:fig2}\fixme{f}).
+(\Cref{fig:fig2}e--g),
+which results in smaller times-to-threshold
+(\Cref{fig:fig2}h).
 For all three diffusion coefficients, the dynamics of ROI 5
@@
 calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
-over time (\Cref{fig:figure3_compare_exp_and_sim_control}a,
+over time (\Cref{fig:fig3}a,
 $F_0$ being the average fluorescence at baseline).
 
-We obtained very similar kinetics curves (\Cref{fig:figure3_compare_exp_and_sim_control}a, b)
-and time-to-threshold values (\Cref{fig:figure3_compare_exp_and_sim_control}c, d) when comparing our
-experiments (\Cref{fig:figure3_compare_exp_and_sim_control}a, c) with
-simulation (\Cref{fig:figure3_compare_exp_and_sim_control}b, d).
+We obtained very similar kinetics curves (\Cref{fig:fig3}a, b)
+and time-to-threshold values (\Cref{fig:fig3}c, d) when comparing our
+experiments (\Cref{fig:fig3}a, c) with
+simulation (\Cref{fig:fig3}b, d).
 Importantly, since the initial condition of the simulation is a mean concentration of zero,
@@
     value of 0.25 in these regions.}
-    \label{fig:figure3_compare_exp_and_sim_control}
+    \label{fig:fig3}
 \end{figure}
@@
 in control and motile-cilia mutant zebrafish (\emph{schmalhans} (\emph{smh})).
-By plotting the means of $\Delta F$ (\Cref{fig:figure4_compare_control_mutant}a)
+By plotting the means of $\Delta F$ (\Cref{fig:fig4}a)
 and the time to threshold
-across the control and mutant cohorts (\Cref{fig:figure4_compare_control_mutant}b),
+across the control and mutant cohorts (\Cref{fig:fig4}b),
 we identified a significant
@@
 higher mean times-to-threshold in the \emph{smh}
-mutants compared to controls (\Cref{fig:figure4_compare_control_mutant}b).
+mutants compared to controls (\Cref{fig:fig4}b).
 
@@
 and compared it with the baseline model
-(both cilia and cardiac motion) (\Cref{fig:figure4_compare_control_mutant}c).
+(both cilia and cardiac motion) (\Cref{fig:fig4}c).
 Similar to our experiments, we observed slower dynamics in simulations for ROIs 2 and 4.
@@
     different limits in each plot.}
-    \label{fig:figure4_compare_control_mutant}
+    \label{fig:fig4}
 \end{figure}
@@
 the telencephalic (anterior) ventricle, the dorsal part and the ventral part
-of the diencephalic (middle) ventricle (\Cref{fig:figure5_compare_cilia_modifications}a).
+of the diencephalic (middle) ventricle (\Cref{fig:fig5}a).
 The cilia tangential traction boundary condition is for each case
@@
 exhibit significant changes in the dynamics of $\cbar$
-(\Cref{fig:figure5_compare_cilia_modifications}b).
+(\Cref{fig:fig5}b).
 Compared to the baseline model results, we observed a slower increase and lower final concentration
@@
 On the other hand, removal of telencephalic cilia did not alter the evolution of the
-mean concentration $\cbar$ with time (\Cref{fig:figure5_compare_cilia_modifications}b).
+mean concentration $\cbar$ with time (\Cref{fig:fig5}b).
 Finally, without ventral cilia in the diencephalic ventricle,
@@
     in the CSF flow model.}
-    \label{fig:figure5_compare_cilia_modifications}
+    \label{fig:fig5}
 \end{figure}
@@
 one where the middle ventricle is shrunk in the lateral direction;
-and the combination of the above three modifications (\Cref{fig:figure6_sim_results_compare_geometries}a).
+and the combination of the above three modifications (\Cref{fig:fig6}a).
 We simulate CSF flow in the modified geometries with the baseline flow model
 and use the resulting velocity field to simulate transport of Dendra2
-(\Cref{fig:figure6_sim_results_compare_geometries}b).
+(\Cref{fig:fig6}b).
 
@@
 in the cilia-deficient model than in the experimental data in
-\Cref{fig:figure4_compare_control_mutant}, which have different duct diameters.
+\Cref{fig:fig4}, which have different duct diameters.
 
@@
     areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
-    \label{fig:figure6_sim_results_compare_geometries}
+    \label{fig:fig6}
 \end{figure}
@@
 we manipulated certain parameters in our models. First, we removed cilia in specific regions of
-our model (\Cref{fig:figure5_compare_cilia_modifications}). We identified that the cilia in the
+our model (\Cref{fig:fig5}). We identified that the cilia in the
 dorsal middle ventricle contribute the most to solute distribution, which aligns well with the fact

### 2025-02-10 paper/main.tex
minor updates
add shrunk cross-sectional areas information
edits after Nathalie's revision

@@
 \author[1]{Miroslav Kuchta} 
-\author[FIX ME]{Inyoung Jeong} % OK?
+\author[2]{Inyoung Jeong} % OK?
 \author[1,3,+]{Marie E.~Rognes} % OK order?
-\author[2,+, *]{Nathalie Jurisch-Yaksi}
+\author[2,+,*]{Nathalie Jurisch-Yaksi}
 \affil[1]{Department of Numerical Analysis and Scientific Computing,
 Simula Research Laboratory, Oslo, Norway}
-\affil[2]{\fixme{@Nathalie is this correct?: Department of Clinical and Molecular Medicine,
-Norwegian University of Science and Technology, Trondheim, Norway\\
-Same affiliation for Inyoung?}}
+\affil[2]{Department of Clinical and Molecular Medicine,
+Norwegian University of Science and Technology, Trondheim, Norway}
 \affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
@@
 Brain development and function depend on numerous regulatory processes,
-including interactions with cerebrospinal fluid (CSF).
-CSF is a clear liquid produced by the choroid plexus, which is a secretory
-epithelium located within the brain ventricles.
-Following production, CSF flows through the ventricular system and
-subarachnoid space, where it regulates brain development and
-homeostasis by transporting growth factors, nutrients, neurotransmitters,
-waste products and other molecules and metabolites.
-
-To achieve its function, CSF needs to circulate throughout the brain.
-In fact, CSF disturbances can univocally lead to brain disorders,
-such as hydrocephalus where accumulation of CSF requires emergency surgical treatment.
-CSF movement occurs through multiple physiological processes, including the action of
-motile cilia on the ventricular wall,
-CSF secretion by the choroid plexus and pressure gradients generated by the
-cardiac cycle, respiration, and bodily movement.
-Motile cilia are microscopic hair-like structures that beat in a metachronal
-wave pattern to generate flow pattern. Due to their microscopic size, ranging from 6 to 15 microns,
-they contribute to fluid flow primarily at the surface of the brain ventricles.
-In contrast, pressure gradients generate fluid flow further from the ventricular
-walls and along the perivascular space surrounding the major blood vessels.
-
-To date, it remains poorly understood how cilia contribute to the overall fluid
-flow and solute transport in the brain.
-These questions have been especially challenging to tackle due to technical limitations.
-Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz,
-while other fluid dynamic processes in the brain are slower and span larger volumes.
-Most studies until now have analyzed one process at a time, especially in mammals.
-For instance, multiple studies have convincingly shown that cilia generate complex
-flow patterns at the surface of the brain ventricles.
-However, since all these studies have been performed on brain explants, they failed
-to identify the role of pressure gradients associated with respiration and heart pulsations in CSF transport.
-Similarly, while MRI technology can measure CSF movement in humans, it cannot detect
-the fast movements of cilia or understand their impact in the large human brain.
-Consequently, we lack a comprehensive understanding of how cilia contribute to CSF
-movement and solute transport, and whether cilia dysfunction will alter CSF distribution
-and lead to brain disorders.
-This is particularly important since ventricular enlargement or hydrocephalus is
-commonly observed in animal models with motile cilia deficiency, potentially affecting
-brain activity and behavior.
+including interactions with cerebrospinal fluid
+(CSF). CSF is a clear liquid produced by the choroid plexus
+that flows through the ventricular system and subarachnoid space.
+By delivering growth factors, nutrients, neurotransmitters and metabolites
+and removing waste products, CSF regulates brain development and homeostasis.
+Disturbances of CSF circulation can lead to brain disorders, such as
+hydrocephalus where accumulation of CSF often requires emergency surgical treatment.
+
+CSF movement occurs through multiple physiological processes,
+including the action of motile cilia on the ventricular walls,
+CSF secretion by the choroid plexus, and pressure gradients generated
+by the cardiac cycle, respiration, and bodily movement. Motile cilia
+are microscopic hair-like structures that beat in a metachronal wave
+pattern to mediate fluid flow. Due to their microscopic size, ranging
+from 6 to 15 microns, they contribute to flow primarily at the surface
+of the brain ventricles. In contrast, pressure gradients induce fluid
+flow \fixme{further from the ventricular walls (bulk flow)} and along the
+perivascular space surrounding the major blood vessels.
+
+To date, it remains poorly understood how cilia contribute to the
+overall fluid flow and solute transport in the brain.
+These questions have been challenging to tackle due to technical
+limitations. Notably, cilia are microscopic and beat at high
+frequencies ranging from 10 to 30 Hz, while other fluid dynamic
+processes in the brain are slower and span larger volumes, making
+cilia dynamics challenging to monitor. Until now, most studies have
+analyzed one physical mechanism at a time, especially in mammals.
+For instance, studies using brain explants have convincingly shown
+that cilia generate complex flow patterns at the surface of the brain
+ventricles; however, they failed to identify the role of pressure
+gradients associated with respiration and heart pulsations in CSF
+transport. Similarly, while MRI technology can measure CSF movement
+in humans, it cannot detect the microscopic movements of cilia to
+understand their impact in the large human brain. Consequently, we
+lack a comprehensive understanding of how cilia contribute to CSF
+movement and solute transport, and whether cilia dysfunction will
+alter CSF composition and lead to brain disorders. This is particularly
+important since ventricular enlargement, known as hydrocephalus,
+is observed in animal models and humans with motile cilia deficiency,
+\fixme{potentially affecting brain activity and behavior.}
 
 The technical limitations of studying cilia-mediated flow and transport opens the
-possibility of mathematical modeling and computational investigations. Cilia have been studied previously,
-with numerous studies on the interaction between single or several cilia and surrounding
+possibility of mathematical modeling and computational investigations. Numerous previous studies
+focused on modeling the interaction between single or several cilia and surrounding
 fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids,
@@
 Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
-These studies have provided valuable insights, showing that cilia lend themselves to simulation studies.
+These simulation studies have provided valuable insights on how cilia \fixme{pump fluids}
+and may contribute to tissue physiology.
 
@@
 Next, we validated our computation model with experimental data by monitoring
-the dynamics of a photoconvertible fluorescent protein expressed within the brain ventricles.
+the dynamics of a photoconvertible fluorescent protein Dendra2 expressed within the brain ventricles.
 Our results show that diffusion plays a major role in the transport of small solutes,
@@
 We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+% Cross-sectional areas of ducts normal to flow direction
+% Modified region       Original mesh        Deformed mesh
+% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
+% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
+% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
 
@@
 within the brain ventricles (\Cref{fig:fig1}\fixme{a--c}).
-In addition, cardiac pulsations induces pulsatile CSF flow.
+In addition, cardiac pulsations induce pulsatile CSF flow.
 We model this flow of CSF in the brain ventricles by the time-dependent,
@@
 used in this study, the Starmaker+Green Fluorescent Protein (STM+GFP) reported in
-Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and Exosomes.
-To estimate the diffusion coefficients of these, when and if not
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
+To estimate the diffusion coefficients of these, when not
 available in the literature, we use the Stokes--Einstein relation:
@@
 The resulting diffusion coefficients used in the simulations
-are $D_1$ (Exosomes), $D_2$ (STM+GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
+are $D_1$ (exosomes), $D_2$ (STM+GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
 
@@
 %%------PHYSICAL EXPERIMENTS------%%
-\subsection*{Zebrafish maintenance and strains in photoconversion experiments}
+\subsection*{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
 The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
@@
 
-\subsection*{Genotyping of adult zebrafish}
-Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
+For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
 fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
@@
 
-\subsection*{Generation of \emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}} line}
-\fixme{@Nathalie: This needs a more understandable title for us non-experts, could we change to
-e.g. "Generation of transgenic line"?.}
-The open reading frame (ORF) of the neuropeptide y (npy) signal peptide
-(\emph{npy}: ENSDARG00000036222, Q1LW93) was fused with the N-terminal
-of zebrafish codon optimized Dendra2 DNA sequence.
+\subsection*{Generation of transgenic line to study CSF \fixme{and transport} dynamics} %\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}
+To generate a transgenic line expressing the photoconvertible protein Dendra2 in
+the brain ventricles, we fused the open reading frame (ORF)
+of the neuropeptide y (npy) signal peptide
+(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
+zebrafish codon optimized Dendra2 DNA sequence.
 The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
-3’ ends (GenScript Biotech), and inserted into the
+3’ ends (GenScript Biotech) and inserted into the
 pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
-through restriction enzyme cloning (GenScript Biotech).
-
-To generate the transgenic line, the 5xuas:Signal-Dendra2 plasmid DNA was used.
+through restriction enzyme cloning (GenScript Biotech)
+to generate the 5xuas:Signal-Dendra2 plasmid DNA..
+
 A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
-was microinjected into one-cell stage embryos,
+was microinjected into one-cell stage embryos to generate the transgenic line,
 as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
@@
 
-We seek to model the compartimentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}\fixme{b--c}).
+We model the compartmentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}\fixme{b--c})
+by the Stokes equations, and solve the equations numerically using a finite element method.
 To characterize CSF flow patterns predicted by
-computational fluid dynamics within the brain ventricles, we begin by
-considering the simulated CSF velocity and pressure when only considering
+computational fluid dynamics within the brain ventricles, we first
+consider the simulated CSF velocity and pressure when only modeling
 cilia motion, disregarding cardiac pressure pulsations. The
@@
 \fixme{Supplementary video 1}). These characteristic patterns suggest
-that the flow in the anterior and middle ventricles are dominated by
-the cilia contribution, while the cardiac pressure pulsations dominate
-within the posterior ventricle. Over one cardiac cycle, the CSF flow
+that the flow in the anterior and middle ventricles is majorly driven
+by cilia, while the cardiac pressure pulsations dominate
+within the posterior ventricle and in the ducts connecting the ventricular
+compartments. Over one cardiac cycle, the CSF flow
 speed reaches up to 27.7 \textmu m/s, dorsally in the posterior part
 of the middle ventricle. This peak is attained at the time instant
-coinciding with the time of peak caudal cardiac pulsatile flow, as a
-result of both the traction induced by the cilia and the pulsatile
-pressure-driven flow being aligned with the rostrocaudal 
+coinciding with the time of peak caudal cardiac pulsatile flow, since 
+both the tangential traction induced by the cilia and the pulsatile
+pressure-driven flow are aligned with the rostrocaudal 
 axis. Using the observed maximum velocity magnitude and choosing the height of
 the middle ventricle ($110$ \textmu m) as a characteristic length
-scale, yields a Reynolds number $\mathrm{Re} \approx 0.004$,
+scale yields a Reynolds number $\mathrm{Re} \approx 0.004$,
 justifying the assumption of Stokes flow. In summary, the computational
-CSF flow model reproduces the flow features observed \emph{in vivo}.
+CSF flow model reproduces the flow features observed \emph{in vivo}~\cite{Olstad2019CiliaryDevelopment}.
 
 \subsection*{Ventricular solute transport is advection-dominated for larger molecules}
-We next ask: what is the impact of these CSF flow patterns and
-magnitudes on solute transport generally within the brain ventricles?
-To address this question, we simulate the distribution and evolution
-of different solutes subject to photoconversion within a region of
+We next explore the impact of these CSF flow patterns and magnitudes
+on solute transport within the brain ventricles.
+To this end, we simulate the distribution and evolution
+of different solutes subjected to photoconversion within a region of
 interest in the dorsal region of the middle ventricle (ROI 1)
-(\Cref{fig:fig2}a). In particular, we consider the spread of
+(\Cref{fig:fig2}a). We consider the spread of
 a solute concentration with a given molecular diffusion coefficient,
-corresponding to Exosomes ($D_1 = 1.63 \times 10^{-12}$ m$^2$/s),
-STM+GFP ($D_2 = 5.75 \times 10^{-11}$ m$^2$/s), and Dendra2 ($D_3 =
-1.15 \times 10^{-10}$ m$^2$/s). As expected, transport occurs more
+corresponding to exosomes ($D_1 = 1.63 \times 10^{-12}$ m$^2$/s),
+a circa 90 kDa protein STM-GFP ($D_2 = 5.75 \times 10^{-11}$ m$^2$/s),
+and the 26 kDa photoconvertible protein  Dendra2 ($D_3 = 1.15 \times 10^{-10}$ m$^2$/s).
+As expected, transport occurs more
 rapidly with increasing diffusion coefficient. Interestingly, the
-distribution patterns differ between the \fixme{different-characteristics}
-solutes. For the smallest diffusion coefficient, representing
-Exosomes, the advection induced by the CSF flow dominates diffusion
+distribution patterns differ between the solutes.
+For the smallest diffusion coefficient, representing
+exosomes, the advective transport by the CSF flow dominates diffusion
 (\Cref{fig:fig2}b). The vortex structures of the velocity field
@@
 streamlines. The balance between diffusion and advection shifts with
-increasing diffusion coefficients, the CSF flow structures become more
+increasing diffusion coefficients: the CSF flow structures become more
 obfuscated, and the solute spreads more uniformly throughout the
@@
     \caption{Simulated distribution and evolution after photoconversion of
-    Dendra ($D_1$), STM+GFP ($D_2$) and Exosomes ($D_3$).
+    exosomes ($D_1$), STM+GFP ($D_2$) and Dendra2 ($D_3$).
     \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
@@
     The colorbar is scaled so the maximum is the maximum concentration of the Dendra2 
-    condentration field slice at the last time instant.
+    concentration field slice at the last time instant.
     \textbf{e--g.} Mean concentration $\cbar$ in each region of interest (ROI)
@@
 a threshold value $\hat{c}$ (\Cref{fig:fig2}h)
-in 6 regions of interest (ROIs) (\Cref{fig:fig2}a).
+in 6 ROIs (\Cref{fig:fig2}a).
 The dynamics at the site of photoconversion (ROI 1)
@@
 in ROI 6 is close to zero at the end of simulation.
-To quantify the balance of advection versus diffusion as transport mehcanisms,
+To quantify the balance of advection versus diffusion as transport mechanisms,
 we calculate the Péclet numbers $\mathrm{Pe}_1=519$,
@@
 To validate our computational model, we performed photoconversion experiments
-in transgenic zebrafish larvae expressing a secreted Dendra2 in their brain ventricles.
+in transgenic zebrafish larvae expressing the secreted Dendra2 in their brain ventricles.
 Our photoconversion protocol consisted of the acquisition of a baseline,
@@
 is thus a similar metric to $\Delta F$.
-The final values of $\cbar$ were 0.76, 0.72, 0.82, 0.56 and 0.35 respectively,
-compared to 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
+The final values of $\cbar$ in our simulations 0.76, 0.72, 0.82, 0.56 and 0.35 (ROIs 2--6, respectively)
+were generally higher than the experimental values 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
 Notwithstanding similarities, we observed small differences between the experiments and simulation.
@@
     \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
-    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time
+    \caption{\fixme{Create common legend.}
+    \textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time
     in each region of interest (ROI)
@@
 we measured the movement of photoconverted Dendra2 signal
-in control and motile-cilia mutant zebrafish (\emph{schmalhans} (\emph{smh})).
+in control and motile-cilia mutant zebrafish (\emph{smh}).
 By plotting the means of $\Delta F$ (\Cref{fig:fig4}a)
@@
 (both cilia and cardiac motion) (\Cref{fig:fig4}c).
-Similar to our experiments, we observed slower dynamics in simulations for ROIs 2 and 4.
+Similar to our experiments, we observed slower dynamics in simulations for ROIs 2 and 4,
+but small changes for ROIs 3 and 6.
 Interestingly, the difference was even greater for the simulations,
@@
 We simulate CSF flow modeled by the Stokes equations with the
-modified boundary conditions, and use the resulting
+modified boundary conditions and use the resulting
 velocity fields in transport simulations.
@@
 We identified that the velocities were most strongly
-affected when removing cilia in the dorsal diencephalic cilia,
+affected when removing cilia in the dorsal diencephalic ventricle,
 as the maximum velocity dropped from 27.7 \textmu m/s to 8.0 \textmu m/s.
@@
 in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
-exhibit significant changes in the dynamics of $\cbar$
-(\Cref{fig:fig5}b).
+exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}b).
 Compared to the baseline model results, we observed a slower increase and lower final concentration
@@
     by imposing a zero tangential traction boundary condition in the respective region.
-    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest in the three 
+    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
     loss-of-cilia-motility scenarios considered. The region named in the legend is the region
@@
 \subsection*{Modification of ventricles geometry impacts protein distribution}
-Variations in ventricular morphology impacts the CSF flow patterns.
-To assess the impact of ventricular morphologies on solute distribution,
+Variations in ventricular morphology impact CSF flow patterns.
+To assess how ventricular morphologies influence solute distribution,
 we used four alternative brain ventricles meshes:
@@
 \emph{in vivo} experiments, the dynamics of the simulations were generally
-more rapid and resulted in higher total amounts.
+more rapid and resulted in higher total amounts of solute.
 Differences between experiments and simulations may relate to
@@
 solute distribution and the geometry used for the model was larger than in experiments.
-Alternatively, it may relate to the way we defined the photoconversion site (region of interest 1)
+Alternatively, it may relate to the way we defined the photoconversion site (ROI 1)
 in the simulations, since the volume of the photoconversion region determines
@@
 is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
-Since Dendra2 is around 26 kDa in size~\cite{Gurskaya2006EngineeringLight},
-and thus under this reported limit, one could assume that if Dendra2
-leaks out of the brain ventricles, the dynamics become slower.
-
-In general, the mean concentration dynamics of the simulations was 
-more rapid than the fluorescence intensity dynamics of the photoconversion experiments.
-This is strongly related to our definition of the photoconversion site
-(ROI 1) in the simulations, and whether this corresponds well to the
-region used in experiments, because the volume of the photoconversion
-region used in the simulations determines the total amount of solute,
-and thus impacts the rate of transport. The alignment of the computational
-and experimental region of interest definition is hard to quantify.
-Additionally, a source of discrepancy in the results is the fact that the
-brain ventricles might be permeable, such that some Dendra2 diffuses out
-of the brain ventricles in the experiments. An assay has shown that the neuroepithelium
-lining the walls of brain ventricles in embryonic zebrafish 24 hours post-fertilization
-is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
-Dendra2 are almost 26 kDa in size~\cite{Gurskaya2006EngineeringLight},
-and are thus under this reported limit. If such permeability also is the case for 2 days
-post-fertilization zebrafish embryo ventricles, this would lead to Dendra2 leaking
-out of the brain ventricles in the experiments, making the dynamics appear slower.
+Since Dendra2 is around 26 kDa in size~\cite{Gurskaya2006EngineeringLight} and
+thus under this reported limit, one could assume that Dendra2 may
+leak out of the brain ventricles and render the dynamics slower.
 
@@
 Indeed, we identified that the diffusion coefficient had a greater impact on transport to
-regions located upstream in the CSF flow field (ROI 4 \fixme{@Nathalie: should this have been 3 instead of 4?}) or in different ventricles (ROIs 5--6),
+regions located upstream in the CSF flow field (ROI 3) or in different ventricles (ROIs 5--6),
 than the regions located downstream of cilia-mediated flow (ROI 2).
@@
 investigate properties? Rather location or population?)} and geometries,
-we manipulated certain parameters in our models. First, we removed cilia in specific regions of
+we manipulated certain parameters in our models. First, we paralyzed cilia in specific regions of
 our model (\Cref{fig:fig5}). We identified that the cilia in the
 dorsal middle ventricle contribute the most to solute distribution, which aligns well with the fact
-that these cilia generate the strongest flow field \emph{in vivo} and in our model.
+that these cilia generate the strongest flow field \emph{in vivo}~\cite{Olstad2019CiliaryDevelopment} and in our model.
 In contrast, removing the ventral cilia in the middle ventricle did not greatly impact flow dynamics.
@@
 CSF velocities between larva at given developmental stages and throughout
-development~\fixme{@Nathalie: Add some citation here? Olstad 2019/D'Gama 2025?}.
+development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
 Our results suggest that these two parameters may well co-vary and explain the variation.
@@
 We trust that it will be useful as a basis for future analysis of
-CSF dynamics in more complex geometries \fixme{and other animal species}.
+CSF dynamics in more complex geometries \fixme{and other animal species and humans}.
 

### 2025-02-10 src/simulate_transport.py

@@ -152,7 +152,7 @@ class TransportSolver:
         a2  = self.D('+') * alpha('+') / avg(self.hf) * dot(jump(w, self.n), jump(c, self.n)) * dS
         a2 -= self.D('+') * dot(avg(grad(w)), jump(c, self.n)) * dS
         a2 -= self.D('+') * dot(jump(w, self.n), avg(grad(c))) * dS
-
+        
         # Advective term
         a3  = dot(jump(w), self.un('+') * c('+') - self.un('-') * c('-')) * dS
 

### 2025-02-12 paper/main.tex
update figures 1, 3 and figure references

@@
 \affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
-\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}
+\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no},
 \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
@@
 injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}\fixme{d}).
+From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}d).
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
@@
 Parts of the ventricular surfaces were marked to be lined with
-motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}\fixme{d}, magenta markers).
+motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}d, magenta markers).
 \begin{figure}%[hbt!]
@@
     \includegraphics[width=\linewidth]{graphics/figure1.png}
-    \caption{\fixme{Reorder panels.} 
+    \caption{
     \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
@@
     \textbf{g.} Streamlines simulated with the baseline flow model at
+    a time 25\% into the cardiac cycle. %t=0.112613 s
+    \textbf{h.} Streamlines simulated with the baseline flow model at
     a time 50\% into the cardiac cycle. %t=0.225225 s
-    \textbf{h.} Streamlines simulated with the baseline flow model at
-    a time 70\% into the cardiac cycle. %t=0.315315 s
+    \textbf{i.} Streamlines simulated with the baseline flow model at
+    a time 75\% into the cardiac cycle. %t=0.315315 s
+    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
+    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
     }
@@
 structures~\cite{Olstad2019CiliaryDevelopment}
-within the brain ventricles (\Cref{fig:fig1}\fixme{a--c}).
+within the brain ventricles (\Cref{fig:fig1}a--c).
 In addition, cardiac pulsations induce pulsatile CSF flow.
@@
 \subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:fig1}\fixme{d}, magenta markers),
+On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:fig1}d, magenta markers),
 we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
@@
 $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
-boundary $\Gp$~(\Cref{fig:fig1}\fixme{d}, blue markers).
+boundary $\Gp$~(\Cref{fig:fig1}d, blue markers).
 Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
@@
 
-For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software
+For photoconversion, ``Bleaching" and ``Region" in the ZEN software
 were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
@@
 \subsection*{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Cref{fig:fig1}\fixme{b, c}, we carried out
+To recover the flow fields shown in~\Cref{fig:fig1}b, c, we carried out
 particle tracking in a larval zebrafish injected with fluorescent beads.
@@
 Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 \textmu m, were plotted in~\Cref{fig:fig1}\fixme{b, c}.
+covering a distance of at least 8.8 \textmu m, were plotted in~\Cref{fig:fig1}b, c.
 
@@
 
-We model the compartmentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}\fixme{b--c})
+We model the compartmentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}b, c)
 by the Stokes equations, and solve the equations numerically using a finite element method.
@@
 system, with large-scale vortex structures in the anterior and middle
-ventricles~(\Cref{fig:fig1}\fixme{e}). The highest velocities ($26.5$ \textmu m/s)
+ventricles~(\Cref{fig:fig1}e). The highest velocities ($26.5$ \textmu m/s)
 occur in the vicinity of the dorsal cilia in the middle ventricle.
@@
 generated by the ciliary motion vanish. The simulated CSF
-flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:fig1}\fixme{g}),
+flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:fig1}f, g),
 with a peak velocity magnitude of $4.8$ \textmu m/s. At each time instant, the flow
@@
 with vortex-structures in the anterior and middle ventricles
-and directional flow in the posterior ventricle (\Cref{fig:fig1}\fixme{e},
+and directional flow in the posterior ventricle (\Cref{fig:fig1}h--j,
 \fixme{Supplementary video 1}). These characteristic patterns suggest
@@
     \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
-    \caption{\fixme{Create common legend.}
+    \caption{
     \textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time

### 2025-02-13 paper/main.tex
update figure captions, clean mesh msh-to-xdmf code

@@
 Motivated by an interest in how ventricular geometry impacts solute distribution,
-we also consider four variations in the geometry \fixme{(percentage reduction in cross-sectional areas):
+we also consider four variations in the geometry \fixme{(cross-sectional area
+reduction in parentheses):
 by shrinking the fore-mid brain connection (66 \%), 
@@
 CSF flow and the concentration can be solved sequentially when modeling solute transport.
-\fixme{For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state.}
-In this case, we first solve the \fixme{steady-state} Stokes equations~\eqref{eq:stokes_eqs}
+For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
+the viscous forces dominate the inertial forces.
+In this case, we first solve the steady-state Stokes equations~\eqref{eq:stokes_eqs}
 for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
@@
 (\Cref{sec:appB_verification}). The simulation code is openly
-available~\cite{zenodo-link-to-all-code}.
+available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
 
@@
 All data analysis was performed in MATLAB and the codes are available in
-the repository of this article: \url{repo-link}.
+the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
 
@@
 
-Next we consider the baseline model, simulating flow driven by both cilia
+Finally, we consider the baseline model, simulating flow driven by both cilia
 and cardiac pulsations. We observe persistent flow features,
@@
 justifying the assumption of Stokes flow. In summary, the computational
-CSF flow model reproduces the flow features observed \emph{in vivo}~\cite{Olstad2019CiliaryDevelopment}.
+CSF flow model reproduces the flow features observed
+\emph{in vivo}~\cite{Olstad2019CiliaryDevelopment}.
 
@@
     \caption{Simulated distribution and evolution after photoconversion of
-    exosomes ($D_1$), STM+GFP ($D_2$) and Dendra2 ($D_3$).
+    exosomes ($D_1$), STM+GFP ($D_2$) and Dendra2 ($D_3$). \\
     \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
@@
 Since $\mathrm{Pe}>1$, this indicates that advection is the
-dominant transport mechanism on a \fixme{global} scale.
+dominant transport mechanism on a global scale.
 
@@
 is thus a similar metric to $\Delta F$.
-The final values of $\cbar$ in our simulations 0.76, 0.72, 0.82, 0.56 and 0.35 (ROIs 2--6, respectively)
-were generally higher than the experimental values 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
-Notwithstanding similarities, we observed small differences between the experiments and simulation.
-For instance, transport dynamics in ROIs 2--6 were faster in the simulation and reached higher final values.
-Moreover, the $\cbar$ profiles of ROIs 3--4 were opposite order in
+The final values of $\cbar$ in our simulations 0.76, 0.72, 0.82, 0.56 and 0.35
+(ROIs 2--6, respectively)
+are generally higher than the mean experimental values 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
+Notwithstanding similar dynamics, we observe small differences between the experiments and simulation.
+For instance, transport in ROIs 2--6 is faster in the simulation and reaches higher final values.
+Moreover, the $\cbar$ profiles of ROIs 3--4 are opposite order in
 the simulations as compared to the experiments.
 Despite observing small differences, the \emph{in vivo} experiments and
-simulations were similar enough to convincingly validate the model.
+simulations are similar enough to convincingly validate the model.
 \begin{figure}[H]
@@
     \caption{
-    \textbf{a.} Relative change in fluorescence intensity $\Delta F$ over time
+    \textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$ 
     in each region of interest (ROI)
     observed during experiments of photoconversion of Dendra2 proteins in ROI 1.
-    \textbf{b.} Mean concentration $\cbar$ as function of time in each ROI in a
+    \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
     simulation of Dendra2 protein transport with
     the diffusion coefficient $D_3$.
-    \textbf{c.} Time to $\Delta F$ reaches a threshold value of 0.25 in
+    \textbf{c.} Time to $\Delta F(t)$ reaches a threshold value of 0.25 in
     one representative zebrafish larva.
-    Time to $\cbar$ reaches a threshold value of 0.25 for
+    Time to $\cbar(t)$ reaches a threshold value of 0.25 for
     a transport simulation with diffusion coefficient $D_3$.
@@
 we measured the movement of photoconverted Dendra2 signal
-in control and motile-cilia mutant zebrafish (\emph{smh}).
+in control and motile-cilia mutant (\emph{smh}) zebrafish .
 By plotting the means of $\Delta F$ (\Cref{fig:fig4}a)
@@
 we observed a slower increase of fluorescence intensity,
-resulting in $\sim 45\%$ (ROI 2) and $\sim 25\%$ (ROI 4)
+resulting in $45\%$ (ROI 2) and $25\%$ (ROI 4)
 higher mean times-to-threshold in the \emph{smh}
@@
 Next, to identify whether our model would recapitulate these findings,
-we simulated protein transport by using the only-cardiac/no-cilia flow model 
-and compared it with the baseline model
+we simulate protein transport by using the only-cardiac/no-cilia flow model 
+and compare it with the baseline model
 (both cilia and cardiac motion) (\Cref{fig:fig4}c).
-Similar to our experiments, we observed slower dynamics in simulations for ROIs 2 and 4,
+Similar to our experiments, we observe slower dynamics in simulations for ROIs 2 and 4,
 but small changes for ROIs 3 and 6.
 Interestingly, the difference was even greater for the simulations,
-with the time-to-threshold in ROI 2 being 90\% higher in absence of cilia-mediated flow.
+with the times-to-threshold in ROI 2 and 4 being 90\% and 34\% higher
+in the absence of cilia-mediated flow.
 Moreover, ROI 5 exhibits very different $\cbar$ profiles for the two
@@
     \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
-    \caption{\textbf{a.} Relative change in fluorescence intensity $F$ over
-    time in each region of interest (ROI) for control (black lines) and \emph{smh} mutant (red lines) fish. 
-    \textbf{b.} Times when $\Delta F$ first exceeds a threshold value,
+    \caption{\textbf{a.} Relative change in fluorescence intensity $F(t)$
+    in each region of interest (ROI) for control (black lines)
+    and \emph{smh} mutant (red lines) fish. 
+    \textbf{b.} Times when $\Delta F(t)$ first exceeds a threshold value,
     equal to 0.25 (ROIs 2--4) or 0.10 (ROIs 5, 6), for control (gray dots) and
     \emph{smh} mutant (red dots) fish.
-    The thick black lines denote mean values of the datasets, and $p$-values
-    were calculated using a Mann-Whitney U test with a confidence level of 95\%.
-    \textbf{c.} Mean concentration $\cbar$ as function of time in each ROI,
+    The thick black lines denote mean values of the datasets. The $p$-values
+    were calculated using a Mann-Whitney U test with a confidence level of 95\%, with 
+    the null hypothesis that the two distributions of control and mutant data are 
+    from the same population.
+    \textbf{c.} Mean concentration $\cbar(t)$ in each ROI,
     simulated using the baseline model (black lines) and the cardiac-only/no-cilia model (red lines).
@@
 upon region-specific cilia paralysis by modifying the boundary conditions
-of the CSF flow model. Three separate cilia-covered regions were considered separately:
-the telencephalic (anterior) ventricle, the dorsal part and the ventral part
+of the CSF flow model. Three cilia-covered regions were considered separately:
+the telencephalic (anterior) ventricle, and the dorsal and ventral parts
 of the diencephalic (middle) ventricle (\Cref{fig:fig5}a).
 The cilia tangential traction boundary condition is for each case
-changed to a free-slip boundary condition in paralyzed region,
+changed to a free-slip boundary condition in the paralyzed region,
 prescribing zero tangential forces to
@@
 
-We identified that the velocities were most strongly
+The CSF velocities are most strongly
 affected when removing cilia in the dorsal diencephalic ventricle,
-as the maximum velocity dropped from 27.7 \textmu m/s to 8.0 \textmu m/s.
+as the maximum velocity magnitude drops from 27.7 \textmu m/s to 8.0 \textmu m/s.
 \emph{In vivo}, these cilia generate the strongest flow at
 this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
-In contrast, removing telencephalic and ventral diencephalic had minimal
-impact and resulted in maximum velocities of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
-Changes in the transport dynamics of Dendra2 were most prominent when removing the dorsal cilia
+In contrast, removing telencephalic and ventral diencephalic cilia has minimal
+impact and results in maximum speeds of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
+Changes in the transport dynamics of Dendra2 are most prominent when removing the dorsal cilia
 in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
 exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}b).
-Compared to the baseline model results, we observed a slower increase and lower final concentration
+Compared to the baseline model results, we observe a slower increase and lower final concentration
 in the middle and anterior ventricles (ROIs 2--5),
 and more rapid transport to the posterior ventricle (ROI 6).
-On the other hand, removal of telencephalic cilia did not alter the evolution of the
+In contrast, removal of telencephalic cilia does not alter the evolution of the
 mean concentration $\cbar$ with time (\Cref{fig:fig5}b).
 Finally, without ventral cilia in the diencephalic ventricle,
-more solute has spread towards the anterior ventricle (ROI 5) and
-less solute has spread towards the posterior ventricle (ROI 6).
+more solute spreads towards the anterior ventricle (ROI 5) and
+less solute spreads towards the posterior ventricle (ROI 6).
 \begin{figure}[H]
@@
 To assess how ventricular morphologies influence solute distribution,
-we used four alternative brain ventricles meshes:
-one where the connection between the anterior and middle ventricles is constricted;
-one where the connection between the middle and posterior ventricles is constricted;
-one where the middle ventricle is shrunk in the lateral direction;
+we consider four alternative brain ventricles meshes:
+one where the duct connecting the anterior and middle ventricles is constricted
+(66 \% reduction in cross-sectional area);
+one where the duct connecting the middle and posterior ventricles is constricted
+(33 \% reduction);
+one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
 and the combination of the above three modifications (\Cref{fig:fig6}a).
@@
 and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
-On the other hand, constricting the connection between the middle and the posterior ventricle
+On the other hand, constricting the duct connecting the middle and the posterior ventricle
 leads to less transport into the posterior ventricle (ROI 6),
@@
 posterior ventricle (ROI 6) is also the case for the geometry with a shrunk middle ventricle.
-Additionally, for this configuration the transport upstream the flow fields towards the
+Additionally, for the latter configuration, the transport upstream of CSF flow towards the
 ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
@@
 we observe higher retention of solute in the middle ventricle (ROIs 2--4),
-while both the anterior and the posterior ventricles (ROIs 5 and 6) have lower concentration.
-Altogether our results identify that the geometry and width of the ventricular ducts matter
-for solute transport and may explain why we observed larger differences
-in the cilia-deficient model than in the experimental data in
-\Cref{fig:fig4}, which have different duct diameters.
+while both the anterior and the posterior ventricles (ROIs 5 and 6) have lower mean concentrations.
+Altogether, our results show that the geometry and width of the ventricular ducts matter
+for solute transport. This may explain why we observed larger differences
+in the cilia-deficient computational model compared to the experimental data in
+\Cref{fig:fig4}, as the model and the fish have different duct diameters.
 
@@
     \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
-    \caption{Caption. \mk{MK: How do the different geoemtries compare in terms of volume,
+    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
+    \textbf{b.} The four modified versions of the computational geometry. Compared
+    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
+    and 9.4\%.
+    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
+    in the 6 ROIs. 
+    \mk{MK: How do the different geoemtries compare in terms of volume,
     areas where cilia are active?} \lyng{HH: Good question, will add this information.}}

### 2025-02-13 src/mesh_ventricles.py

@@ -1,12 +1,0 @@
-import dolfinx as dfx
-
-from utilities.mesh import read_msh_parallel
-from mpi4py import MPI
-
-# for i in range(9):
-i=10
-filename = './geometries/ventricles_' + str(i) + '.msh'
-mesh = read_msh_parallel(filename=filename, comm=MPI.COMM_WORLD)
-
-with dfx.io.XDMFFile(MPI.COMM_WORLD, filename.removesuffix('.msh') + '.xdmf', 'w') as xdmf:
-    xdmf.write_mesh(mesh=mesh)

### 2025-02-13 src/utilities/mesh.py

@@ -1,12 +1,9 @@
-import ufl
-import meshio
 import numpy.typing
 
 import numpy     as np
 import dolfinx   as dfx
 
 from mpi4py   import MPI
-from pathlib  import Path
 
 # Mesh tags
 NOSLIP    = 1
@@ -18,7 +15,6 @@ UPPER     = 6
 ANTERIOR  = 7
 ANTERIOR2 = 8
 SLIP      = 9
-
 
 # Mesh tags for flow
 ANTERIOR_PRESSURE    = 2
@@ -38,83 +34,6 @@ MIDDLE_DORSAL_ANTERIOR  = 14
 POSTERIOR_VENTRAL       = 15
 ANTERIOR_VENTRAL        = 16
 MIDDLE_VENTRAL          = 17
-
-def old_create_ventricle_volumes_meshtags(mesh: dfx.mesh.Mesh) -> tuple((dfx.mesh.MeshTags, list[int])):
-    """ Create cell meshtags for the different regions of interest (ROI)
-        used in the analysis and comparison with experimental data.
-
-    Parameters
-    ----------
-    mesh : dfx.mesh.Mesh
-        The brain ventricles mesh.
-
-    Returns
-    -------
-    tuple(dfx.mesh.MeshTags, list[int])
-        The celltags and a list of the integer tag values for each ROI.
-    """
-    
-    # Define the planes that separate the anterior, middle and posterior ventricles
-    z_min = mesh.comm.allreduce(mesh.geometry.x[:, 2].min(), op=MPI.MIN)
-    z_max = mesh.comm.allreduce(mesh.geometry.x[:, 2].max(), op=MPI.MAX)
-    z_mid = (z_min + z_max) / 2
-    a1 = [0.165, 0.0, z_mid]
-    b1 = [0.125, 0.0, z_max*0.78]
-
-    a2 = [0.33, 0.0, z_mid*0.8]
-    b2 = [0.345, 0.0, z_max*0.75]
-
-    line1 = lambda t: a1[2] + (b1[2] - a1[2])/(b1[0] - a1[0])*(t - a1[0])
-    line2 = lambda t: a2[2] + (b2[2] - a2[2])/(b2[0] - a2[0])*(t - a2[0])
-
-    # Define locator functions for each region of interest (ROI)
-    def ROI_1(x):
-        """ The dorsal posterior region of the middle ventricle. """
-        x_range = np.logical_and(x[0] > 0.295, x[0] < 0.325)
[…]

### 2025-02-13 src/utilities/mesh_ventricles_msh_to_xdmf.py

@@ -1,0 +1,66 @@
+from mpi4py    import MPI
+from pathlib   import Path
+
+import ufl
+import basix
+import meshio
+import numpy   as np
+import dolfinx as dfx
+
+def read_msh_parallel(filename: str | Path, comm: MPI.Comm, rank: int=0, num_refinements: int=0) -> dfx.mesh.Mesh:
+    """ Read mesh file of type .msh and return a dolfinx.mesh.Mesh mesh.
+        
+        Possibly in parallel and possibly with refinements.
+
+    Parameters
+    ----------
+    filename : str | Path
+        Filename of .msh mesh as string or path.
+    comm : MPI.Comm
+        MPI communicator.
+    rank : int, optional
+        Rank owning mesh, by default 0
+    num_refinements : int, optional
+        Number of mesh refinements to perform, by default 0
+
+    Returns
+    -------
+    mesh : dolfinx.mesh.Mesh
+
+    """
+
+    if comm.rank==rank:
+        msh = meshio.read(filename)
+        # Extract cells and points from the .msh mesh
+        cells  = msh.get_cells_type("tetra")
+        points = msh.points
+        points /= 1000  # Divide geometry by thousand to get millimeters
+    else:
+        cells  = np.empty((0, 4), dtype=np.int64)
+        points = np.empty((0, 3), dtype=np.float64)
+
+    element = basix.ufl.element("Lagrange", basix.CellType.tetrahedron, 1, shape=(3,))
+    domain = ufl.Mesh(element)
+    partitioner = dfx.cpp.mesh.create_cell_partitioner(dfx.mesh.GhostMode.shared_facet)
+    mesh = dfx.mesh.create_mesh(comm, cells, points, domain, partitioner=partitioner)
+    if comm.rank==rank:
+        print("Total # cells in mesh: {0}.\n".format(mesh.topology.index_map(3).size_global))
+
+    if num_refinements!=0:
+        print(f"Refining the mesh {num_refinements} times.")
+        for _ in range(num_refinements):
+            mesh.topology.create_entities(1)
+            mesh = dfx.mesh.refine(mesh)
+    
+        if comm.rank==rank:
+            print("Total # cells in refined mesh: {0}.\n".format(mesh.topology.index_map(3).size_global))
+    
+    return mesh
+
+if __name__=='__main__':
+    i=5
[…]

### 2025-02-14 paper/main.tex
polish discussion

@@
 Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
-These simulation studies have provided valuable insights on how cilia \fixme{pump fluids}
-and may contribute to tissue physiology.
+These simulation studies have provided valuable insights on how cilia mediate complex
+biological flows, and how cilia may contribute to tissue physiology.
 
@@
 Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
-and $\mu=6.97\times 10^{-4} \ \mathrm{Pa\cdot s}$ is the dynamic viscosity
+and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
 of the CSF~\cite{Bloomfield1998EffectsFluid}.
@@
 cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=6.5\times 10^{-4}$ Pa were chosen by 
+Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
 model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
@@
 the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
-The amplitude $A=1.5\times 10^{-3}$ Pa determines the magnitude of the pulsatile flow,
+The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
 and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
@@
 we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
-used in this study, the Starmaker+Green Fluorescent Protein (STM+GFP) reported in
+used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
 Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
@@
 since the smaller exosomes would have diffusion coefficients similar to the other molecules.
-For STM+GFP, we estimated the diffusion coefficient by extrapolating
+For STM-GFP, we estimated the diffusion coefficient by extrapolating
 the experimentally observed diffusion coefficient of
@@
 The resulting diffusion coefficients used in the simulations
-are $D_1$ (exosomes), $D_2$ (STM+GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
+are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
 
@@
         & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM+GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
+        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
         & $\num{5.75e-11}$ & * \\
@@
     \caption{Simulated distribution and evolution after photoconversion of
-    exosomes ($D_1$), STM+GFP ($D_2$) and Dendra2 ($D_3$). \\
+    exosomes ($D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). \\
     \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
@@
 other systems in the future when their flow parameters are comprehensively resolved.  
-By imposing tangential traction and normal pressure on the CSF flow, we achieved to reproduce
+By imposing tangential traction and normal pressure on the CSF flow, we were able to reproduce
 flow fields with similar features as observed experimentally, consisting of vortex-structured flow,
@@
 These results compared well with experimental data performed \emph{in vivo} in zebrafish.
-Next, by using both a model and zebrafish mutants with paralyzed cilia,
+Then, by using both a computational model and zebrafish mutants with paralyzed cilia,
 we identified that even though advection by cilia is dominant,
-diffusion plays a significant role  in protein transport. Finally, we report how local
-flow patterns and ventricular geometries affect solute distribution.
-Altogether our results provide not only new findings on the role of
-diffusion and advection but also offer a new framework to study CSF transport in complex geometries.
+diffusion plays a significant role in protein transport.
+Finally, we reported how local cilia paralysis and ventricular geometries
+affect solute distribution. Altogether, we present not only new findings on the role of
+diffusion and advection, but also provide a novel framework to
+study CSF flow and transport in complex geometries.
 

### 2025-02-15 paper/main.tex
add dolfinx citation

@@
 The numerical solution schemes for the Stokes equations and the
-advection-diffusion equation were implemented and solved numerically with DOLFINx,
+advection-diffusion equation were implemented and solved numerically with DOLFINx~\cite{dolfinx2023preprint},
 the Python interface of the finite element software
-FEniCSx~\cite{TheFEniCSProject2024FEniCSxDocumentation}, with
+FEniCSx, with
 petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.

### 2025-02-15 src/simulate_transport.py

@@ -111,7 +111,6 @@ class TransportSolver:
 
         # Penalty parameters
         self.alpha_val = 25.0  # DG interior penalty parameter
-        self.beta_val  = 500.0 # Nitsche penalty parameter, for weak imposition of Dirichlet BC
 
         # Create meshtags for the different ventricle ROIs
         self.ROI_ct, self.ROI_tags = create_ventricle_volumes_meshtags(mesh=self.mesh)      

### 2025-02-17 paper/main.tex
add r/lambda table to appendix

@@
     \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
-    \caption{\textbf{a.} The three separate ciliated regions where loss of cilia motility is simulated
+    \caption{\textbf{a.} The three separate ciliated regions cilia paralysis is simulated
     by imposing a zero tangential traction boundary condition in the respective region.
     \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
-    loss-of-cilia-motility scenarios considered. The region named in the legend is the region
+    paralysis scenarios considered. The region named in the legend is the region
     where we modify the cilia tangential traction boundary condition to a free-slip condition
@@
 The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia
-motion differ for the cilia regions. We heuristically determined $\tau$ and $\lambda(\xx)$.
-As noted previously, $\tau=\num{6.5e-4}$ Pa. We set $\rr = \rr^+$ and $\rr = \rr^-$ in
-the ventral and dorsal regions of the diencephalic ventricle, respectively. In the ventral region,
-we set the linear profile $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$,
-where $[x_{0, v}, x_{e, v}]$ is the $x$-range of the cilia region, so the stresses decrease
-linearly towards the posterior part of the geometry. We impose a linearly increasing profile
-over the $x$-range $[x_{0, d}, x_{e, d}]$ in the dorsal region:
-$\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$.
-\lyng{Put all of this information on $\lambda$ choice in a table.}
-
-In the telencephalic ventricle, we set $\rr=\rr^-$ and $\lambda=\frac{2}{5}$
-in the anterior most part of the cilia region,
-and $\rr=\rr^+$ and $\lambda(\xx)=1$ in the posterior part.
+motion differ for the cilia regions. We heuristically determined the constant $\tau= 0.65$ mPa
+and the spatially varying function $\lambda(\xx)$. The definitions of $\rr$ and $\lambda(\xx)$
+for the different cilia populations are summarized in~\Cref{tab:r_vector_and_lambda_function}.
+\begingroup
+\setlength{\tabcolsep}{20pt}
+\renewcommand{\arraystretch}{1.5}
+\begin{table}[H]
+    \centering
+    \caption{Definitions of $\rr$ and $\lambda(\xx)$ used in for the cilia tangential 
+    traction boundary condition $\btau = \tau\lambda(\xx)P_{\nn}(\rr)$,
+    where $\tau=0.65$ mPa. The $x-$coordinates $x_{0, i}$ and $x_{e, i}$ define 
+    the cilia domain in the dorsal ($i=d$) and ventral ($i=v$) regions of 
+    the middle ventricle.}\label{tab:r_vector_and_lambda_function}
+    \begin{tabular}{lcc}
+        \toprule
+        Cilia population & $\rr$ & $\lambda(\xx)$ \\
+        \midrule 
+        Anterior region, anterior ventricle  & $-(1, 0, 1)$ & $\frac{2}{5}$ \\
+        Posterior region, anterior ventricle & $\ \ \ (1, 0, 1)$ & 1 \\
+        Dorsal region, middle ventricle      & $-(1, 0, 1)$ & $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
+        Ventral region, middle ventricle     & $\ \ \ (1, 0, 1)$ & $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+\endgroup
 
@@
 with the velocity and pressure expressions defined in~\Cref{subsec:mms}
-for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{H}(\mathrm{div};\Omega)$
+for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{L}^2$
 and $\mathbf{H}^1$ error norms for $\uu_h$, and the $L^2$ error norm for

### 2025-02-17 paper/main.tex
Fig5: add tangential force contribution bar plot

@@
 impact and results in maximum speeds of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
+Of the total tangential force exerted by the cilia, ventral cilia in the middle ventricle
+contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
+force~(\Cref{fig:fig5}b). The magnitude of the force contributions are thus
+more similar than the difference in their impact on the maximum velocity magnitudes.
+
 Changes in the transport dynamics of Dendra2 are most prominent when removing the dorsal cilia
 in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
-exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}b).
+exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}c).
 Compared to the baseline model results, we observe a slower increase and lower final concentration
@@
 In contrast, removal of telencephalic cilia does not alter the evolution of the
-mean concentration $\cbar$ with time (\Cref{fig:fig5}b).
+mean concentration $\cbar$ with time (\Cref{fig:fig5}c).
 Finally, without ventral cilia in the diencephalic ventricle,
@@
     by imposing a zero tangential traction boundary condition in the respective region.
-    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
+    \textbf{b.} The total tangential force applied through the tangential traction
+    boundary condition in the three separate ciliated regions.
+    \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
     paralysis scenarios considered. The region named in the legend is the region

### 2025-02-17 src/plot_cilia_force_bars.py

@@ -1,0 +1,39 @@
+import numpy  as np
+import matplotlib.pyplot as plt
+
+plt.style.use('petroff10')
+
+# Set matplotlib properties
+plt.rcParams.update({
+    "font.family" : "Arial",
+    "axes.spines.top" : False,
+    "axes.spines.right" : False
+})
+
+save_fig = 1
+
+import colormaps as cm
+green = cm.dark2_3.colors[0]
+orange = cm.dark2_3.colors[1]
+purple = cm.puor_4.colors[3]
+colors = [green, orange, purple, 'k']
+
+fig, ax = plt.subplots(figsize=[11.35, 10])
+idx = [1, 2, 3, 4]
+
+# Forces applied [dorsal, ventral, anterior, total]
+forces = np.array([3.64E-06, 2.41E-06, 9.78E-07, 7.03E-06])*1e6 # Forces in micro Newton
+
+hatches = ['/', '\\', 'x', '']
+bars = ax.bar(x=idx, height=forces, width=0.5, color=colors, hatch=hatches)
+
+ax.set_title('Cilia population contribution', fontsize=50, pad=30)
+ax.set_ylabel(r'Tangential force $\mathrm{[\mu N]}$', fontsize=45, labelpad=25)
+ax.set_yticks(range(1, 8))
+ax.set_xticks(idx)
+ax.set_xticklabels(['Dorsal', 'Ventral', 'Anterior', 'Total'], fontsize=45)
+ax.tick_params(axis='both', labelsize=45, pad=25)
+fig.tight_layout()
+
+if save_fig: fig.savefig('../output/illustrations/compare_cilia/cilia_forces_bar_plot.png')
+plt.show()

### 2025-02-17 src/plot_compare_simulations_cilia_regions.py

@@ -12,12 +12,10 @@ from utilities.mesh import create_ventricle_volumes_meshtags
 
 # Set matplotlib properties
 plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
+    "font.family" : "Arial",
     "axes.spines.top" : False,
     "axes.spines.right" : False
 })
-plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
 
 comm = MPI.COMM_WORLD # MPI Communicator
 gm   = dfx.mesh.GhostMode.shared_facet
@@ -97,9 +95,9 @@ for row_idx in range(ax_c.shape[0]):
         ca_c = ax_c[row_idx, col_idx]
         
         ca_c.plot(times, c_bar_original[:, idx], color=colors[0], label='Original', linewidth=lw)
-        ca_c.plot(times, c_bar_dorsal[:, idx]  , color=colors[1], linestyle='--', marker='o', markevery=2000, label=r'Dorsal cilia\textsuperscript{-/-}', linewidth=lw, markersize=msize)
-        ca_c.plot(times, c_bar_ventral[:, idx] , color=colors[2], linestyle='--', marker='^', markevery=2000, label=r'Ventral cilia\textsuperscript{-/-}', linewidth=lw, markersize=msize)
-        ca_c.plot(times, c_bar_telenc[:, idx] , color=colors[3], linestyle='--', marker='s', markevery=2000, label=r'Telencephalic cilia\textsuperscript{-/-}', linewidth=lw, markersize=msize)
+        ca_c.plot(times, c_bar_dorsal[:, idx]  , color=colors[1], linestyle='--', marker='o', markevery=2000, label=r'Dorsal paralyzed', linewidth=lw, markersize=msize)
+        ca_c.plot(times, c_bar_ventral[:, idx] , color=colors[2], linestyle='--', marker='^', markevery=2000, label=r'Ventral paralyzed', linewidth=lw, markersize=msize)
+        ca_c.plot(times, c_bar_telenc[:, idx] , color=colors[3], linestyle='--', marker='s', markevery=2000, label=r'Telencephalic paralyzed', linewidth=lw, markersize=msize)
 
         ca_c.set_title(f'ROI {tag}', fontsize=30, pad=2.0)
         ca_c.set_xticks([0, 250, 500, 750])
[…]

### 2025-02-18 paper/main.tex
last version before template change
Wiley template

@@
-\documentclass[fleqn]{wlscirep}
-\usepackage[utf8]{inputenc}
-\usepackage{lipsum}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{siunitx}
-\usepackage{physics}
-\usepackage{stmaryrd} % double brackets for jump operator
-\usepackage{nameref}
-\usepackage{booktabs}
-\usepackage{bm}
-\usepackage{amsopn}
-\usepackage[skip=10pt]{caption}
-\usepackage{color}
-\usepackage{xcolor,colortbl}
-\usepackage[nameinlink, capitalise]{cleveref}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{tablefootnote} % for table footnotes
-\usepackage{float} % figure placement
-
-% Bibliography tools
-\usepackage{csquotes}
-
-% Set some cref options
-\newcommand{\crefrangeconjunction}{--} % Change crefrange from "to" to dashed
-
-%% Some new commands
-% Math
-\newcommand{\cbar}{\overline{c}}
-
-% Partial derivatives
-\newcommand{\pdifft}[1]{\frac{\partial  #1}{\partial t}}
-\newcommand{\pdiffx}[1]{\frac{\partial #1}{\partial x}}
-\newcommand{\pdiffy}[1]{\frac{\partial #1}{\partial y}}
-\newcommand{\pdiffxi}[1]{\frac{\partial #1}{\partial x_i}}
-\newcommand{\pdiffxj}[1]{\frac{\partial #1}{\partial x_j}}
-\newcommand{\secpdiffx}[1]{\frac{\partial^2 #1}{\partial x^2}}
-\newcommand{\secpdiffxi}[1]{\frac{\partial^2 #1}{\partial x_i \partial x_i}}
-\newcommand{\secpdiffxj}[1]{\frac{\partial^2 #1}{\partial x_j \partial x_j}}
-
-% Norms
-\newcommand{\normltwo}[1]{{ \vert\vert#1\vert\vert}_{L^2}}
-\newcommand{\normltwovec}[1]{{ \vert\vert#1\vert\vert}_{\mathbf{L}^2}}
-\newcommand{\normlinf}[1]{{\vert\vert#1\vert\vert}_{L^{\infty}}}
-\newcommand{\Hnorm}[1]{\norm{#1}_{\mathbf{H}^1}}
-\newcommand{\Hdivnorm}[1]{\norm{#1}_{\mathbf{H}(\mathrm{div};\Omega)}}
-
-% Integrals
-\newcommand{\dx}{\, \mathrm d\bm{x}}
-\newcommand{\intO}[1]{\int_{\Omega}#1 \, \mathrm d\bm{x}}
-\newcommand{\intG}[1]{\int_{\Gamma}#1 \, \mathrm ds}
-\newcommand{\intF}[1]{\int_{\mathcal{F}_k}#1 \, \mathrm dS}
-\newcommand{\intGnf}[1]{\int_{\Gamma_{\mathrm{nf}}}#1 \, \mathrm ds}
-\newcommand{\intGinj}[1]{\int_{\Gamma_{\mathrm{inj}}}#1 \, \mathrm ds}
-\newcommand{\intGin}[1]{\int_{\Gamma_{\mathrm{in}}}#1 \, \mathrm ds}
-\newcommand{\intGout}[1]{\int_{\Gamma_{\mathrm{out}}}#1 \, \mathrm ds}
-\newcommand{\intGinjout}[1]{\int_{\Gamma_{\mathrm{inj}}\cup\Gamma_{\mathrm{out}}}#1 \, \mathrm ds}
-\newcommand{\intGs}[1]{\int_{\Gamma_s}#1 \, \mathrm ds}
-\newcommand{\intGc}[1]{\int_{\Gamma_c}#1 \, \mathrm ds}
-\newcommand{\intGp}[1]{\int_{\Gamma_p}#1 \, \mathrm ds}
-
-% Domain and boundaries
-\newcommand{\Gs}{\Gamma_{s}}
-\newcommand{\Gc}{\Gamma_{c}}
-\newcommand{\Gp}{\Gamma_{p}}
-\newcommand{\Ginj}{\Gamma_{\mathrm{inj}}}
-\newcommand{\Gnf}{\Gamma_{\mathrm{nf}}}
-\newcommand{\Gin}{\Gamma_{\mathrm{in}}}
-\newcommand{\Gout}{\Gamma_{\mathrm{out}}}
-
-% Discontinuity operators
-\newcommand{\avg}[1]{\{#1\}}
-\newcommand{\jump}[1]{\llbracket#1\rrbracket}
-
-% Bold faced math characters
-\newcommand{\ff}{\mathbf{f}}
-\newcommand{\nn}{\mathbf{n}}
-\newcommand{\rr}{\mathbf{r}}
-\newcommand{\uu}{\mathbf{u}}
-\newcommand{\vv}{\mathbf{v}}
-\newcommand{\ww}{\mathbf{w}}
-\newcommand{\xx}{\bm{x}}
-\newcommand{\JJ}{\mathbf{J}}
-\newcommand{\VV}{\mathbf{V}}
-\newcommand{\bsig}{\bm{\sigma}}
-\newcommand{\bsigpar}{\hat{\bsig}_{\parallel}}
-\newcommand{\bsigperp}{\hat{\bsig}_{\perp}}
-\newcommand{\beps}{\bm{\varepsilon}}
-\newcommand{\btau}{\bm{\tau}}
-
-% Comments
-\newcommand{\lyng}[1]{\textcolor{blue}{#1}}
-\newcommand{\mer}[1]{\textcolor{magenta}{#1}}
-\newcommand{\mk}[1]{\textcolor{olive}{MK: #1}}
-
-\newcommand{\fixme}[1]{\textcolor{red}{#1}}
-
-% Title
-\title{The role of advection versus diffusion in intraventricular transport}
-\author[1,*]{Halvor Herlyng}
-\author[1]{Ada J.~Ellingsrud}
-\author[1]{Miroslav Kuchta} 
-\author[2]{Inyoung Jeong} % OK?
-\author[1,3,+]{Marie E.~Rognes} % OK order?
-\author[2,+,*]{Nathalie Jurisch-Yaksi}
-\affil[1]{Department of Numerical Analysis and Scientific Computing,
-Simula Research Laboratory, Oslo, Norway}
-\affil[2]{Department of Clinical and Molecular Medicine,
-Norwegian University of Science and Technology, Trondheim, Norway}
-\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
-\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no},
-\href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
-\affil[+]{these authors contributed equally to this work}
-% Optional PDF information
-\ifpdf
-\hypersetup{
-  pdftitle={zebrafish-cilia-csf},
-  pdfauthor={H.~Herlyng~\emph{et al.}}
-}
-\fi
-
+\documentclass{WileyMSP-template}
+
+\begin{document}
+
+\pagestyle{fancy}
+\rhead{\includegraphics[width=2.5cm]{vch-logo.png}}
+
+\title{Advection Versus Diffusion in Intraventricular Transport}
+
+\maketitle
+
+% Author: Please give full first and last names for authors and include * after the name of all corresponding authors
+
+\author{Halvor Herlyng*}
+\author{Ada J.~Ellingsrud}
+\author{Miroslav Kuchta}
+\author{Inyoung Jeong}
+\author{Marie E.~Rognes} \\
+\author{Nathalie Jurisch-Yaksi*}
+
+% Affiliations: Please provide adacemic titles (Prof. or Dr.) for all authors where applicable, and include an institutional email address for all corresponding authors
+\begin{affiliations}
+H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
+Department of Numerical Analysis and Scientific Computing,
+Simula Research Laboratory, Kristian Augusts gate 23, 0164 Oslo, Norway\\
+Email Address: hherlyng@simula.no
+
+Dr.~M.~E.~Rognes \\
+K.~G.~Jebsen Center for Brain Fluid Research, Oslo, Norway
+\\
+Dr.~I.~Jeong, Dr.~N.~Jurisch-Yaksi\\
+Department of Clinical and Molecular Medicine,
+Norwegian University of Science and Technology, Erling Skjalgsons gate 1, 7491 Trondheim, Norway \\
+Email Address: nathalie.jurisch-yaksi@ntnu.no
+
+\end{affiliations}
+
+% Keywords: Please provide a minimum of three and a maximum of seven keywords, separated by commas
+
+\keywords{cerebrospinal fluid, brain ventricles, fluid flow, transport}
+
+% Abstract should be written in the present tense and impersonal style (i.e., avoid we), and be at most 200 words long
 \begin{abstract}
-    This paper presents ...
-    %Flow of cerebrospinal fluid in zebrafish brain ventricles is studied in this work.
-Motivated by experimental observations, we consider motile cilia and cardiac beating as the driving flow mechanisms.
-    %A mathematical model of the flow is developed and coupled with a transport model to study the transport of molecules inside the brain ventricles. 
-    %The Stokes equations are used to model the flow, with the motile cilia acting as a force on the fluid through a stress boundary condition that allows slip at the wall. 
-    %Transport is modeled with an advection-diffusion equation coupled to the velocity field obtained from solving the Stokes equations.
-    %The flow and transport models are discretized with finite element methods.
-For the Stokes equations we employ a non-conforming discretization based on elements of the Brezzi-Douglas-Marini family.
-    %The advection-diffusion equation is discretized with discontinuous Galerkin elements. 
-    %We implement and solve the discretized equations numerically to simulate flow and transport in a zebrafish brain ventricles geometry obtained with medical imaging.
+
+Please insert your abstract here
+
 \end{abstract}
-\begin{document}
-\maketitle
-% Introduction:
-% 1. What are cilia and why are they important?
-% 2. Previous studies of cilia flow
-% 3. What problem do we want to solve
-% 4. The model and work done in this paper
-\section*{Introduction}
+
+% Text: Please use section headings and subheadings as specified below. For communications, all section headings apart from Experimental Section should be removed
+% Please make the first reference to a display item bold: \textbf{Figure 1}
+% Do not abbreviate Figure, Equation, etc.; display items are always singular, i.e., Figure 1 and 2.
+% Equations are always singular, i.e., Equation 1 and 2, and should be inserted using the {equation} environment, not as graphics
+% Please do not use footnotes in the text, additional information can be added to the Reference list.
+
+%\section{First Section}
+
+%\subsection{First Subsection}
+
+%\subsubsection{First Sub Subsection}
+
+%\threesubsection{First lowest-level subsection}
+
+\section{Introduction}
 Brain development and function depend on numerous regulatory processes,
@@
 
-\section*{Methods}
-\subsection*{Image-based computational geometries of zebrafish brain ventricles}
-To model flow and transport in zebrafish larval brain ventricles, we generated a
-3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
-injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}d).
-The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
-The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
-maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
-At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
-the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
-Parts of the ventricular surfaces were marked to be lined with
-motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}d, magenta markers).
-\begin{figure}%[hbt!]
-    \centering
-    \includegraphics[width=\linewidth]{graphics/figure1.png}
-    \caption{
-    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
-    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
-    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
-    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
-    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
-    anterior/posterior facets (blue).
-    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
-    cilia-only/no-cardiac flow model.
-    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
-    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
-    \textbf{g.} Streamlines simulated with the baseline flow model at
-    a time 25\% into the cardiac cycle. %t=0.112613 s
-    \textbf{h.} Streamlines simulated with the baseline flow model at
-    a time 50\% into the cardiac cycle. %t=0.225225 s
-    \textbf{i.} Streamlines simulated with the baseline flow model at
-    a time 75\% into the cardiac cycle. %t=0.315315 s
-    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
-    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
-    }
-    \label{fig:fig1}
-\end{figure}
-
-The morphology and geometry of the brain ventricles vary across zebrafish
-individuals, and under physiological and pathological conditions. 
-Motivated by an interest in how ventricular geometry impacts solute distribution,
-we also consider four variations in the geometry \fixme{(cross-sectional area
-reduction in parentheses):
-by shrinking the fore-mid brain connection (66 \%), 
-the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
-% Cross-sectional areas of ducts normal to flow direction
-% Modified region       Original mesh        Deformed mesh
-% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
-% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
-% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
-
-\subsection*{Computational CSF dynamics}
-The beating motion of the cilia generates CSF flow with steady rotational
-structures~\cite{Olstad2019CiliaryDevelopment}
-within the brain ventricles (\Cref{fig:fig1}a--c).
-In addition, cardiac pulsations induce pulsatile CSF flow.
-We model this flow of CSF in the brain ventricles by the time-dependent,
-incompressible Stokes equations which read as follows.
-Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
-and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
-\begin{subequations}
-    \begin{align}
-      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
-      \quad \text{in } \Omega,\\
-      \nabla \cdot \uu &= 0
-      \quad  \text{in } \Omega,
-  \end{align}
-  \label{eq:stokes_eqs}% 
-\end{subequations}%
-where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
-and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
-Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
-Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
-and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
-of the CSF~\cite{Bloomfield1998EffectsFluid}.
-We introduce the tangential traction $\bsigpar$ as the
-tangential component of the traction $\hat{\bsig}=\bsig\nn$:
-\begin{equation*}
-    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
-\end{equation*}
-where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
-and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
-We consider three types of boundary conditions:
-(i) \emph{tangential traction} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
-(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
-the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
-and (iii) \emph{free slip} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the
-boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
-
-To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
-we consider the following computational flow scenarios,
-each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
-\begin{itemize}
-    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
-    contributions both from the cilia forces and the cardiac pulsations.
-    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
-    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
-
-    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
-    cilia forces but no cardiac pulsations.
-    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
-    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
-
-    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
-    cardiac pulsations but no cilia forces.
-    Here, we set the tangential traction to zero on the cilia boundary
-    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
-    anterior/posterior boundary $\Gp$.  % Model II/Model B
-\end{itemize}
-
-\subsection*{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Cref{fig:fig1}d, magenta markers),
-we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
-of the cilia acting on the CSF.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
-and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
-cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
-model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
-The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
-$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
-In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
-We calibrated $\tau$ heuristically by comparing these experimental velocity values
-with the simulated, maximum velocity magnitude.
-
-\subsection*{Flow induced by cardiac pulsations}\label{subsec:pressure_bcs}
-To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
-$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
-boundary $\Gp$~(\Cref{fig:fig1}d, blue markers).
-Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
-the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
-The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
-and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
-Particle tracking data of pulsatile motion was used to determine the contributions of the
-cardiac pulsations to the velocity magnitude,
-as compared to the effect of cilia motion on the flow (see~\Cref{sec:appC_particle_transport}).
-
-\subsection*{Computational model of solute transport after photoconversion}
-We simulate transport of photoconverted proteins within the brain ventricles by
-modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
-time $t > 0$ by the advection-diffusion equation
-\begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
-    \label{eq:adv_diff_strong}
-\end{equation}
-where the total concentration flux $\mathbf{J}$ is assumed to consist of an advective and a diffusive flux:
-\begin{equation*}
-    \JJ = c\uu - D\nabla c .
-\end{equation*}
-Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\eqref{eq:stokes_eqs},
-and $D$ is the molecular diffusion coefficient of the solute.
-Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
-The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
-except at the anterior/posterior boundary $\Gamma_p$.
-At the anterior/posterior boundary, we permit the solute concentration to be advected into
-and out of the domain in a manner that ensures conservation of mass
-(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
-
-To computationally represent protein photoconversion in a region
-$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
-we prescribe a given time-dependent value to the solute concentration in this region. 
-Mimicking the experimental protocol, we consider the dorsal part of the
-diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
-\begin{equation}
-  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
-  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
-\label{eq:photoconversion_curve}
-\end{equation}
-The value $a=65$ was chosen to fit the fluorescence intensity curve
-observed in the physical photoconversion experiments.
-
-\subsection*{Estimation of diffusion coefficients via the Stokes-Einstein relation}
-Motivated by an interest in molecules that are significant in neural development,
-we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
-used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
-Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
-To estimate the diffusion coefficients of these, when not
-available in the literature, we use the Stokes--Einstein relation:
-\begin{equation}
-    D = \frac{k_B T}{6\pi \mu R},
-    \label{eq:D_stokes_einstein}
-\end{equation}
-which is an expression for the diffusion coefficient of a spherical
-molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
-In~\eqref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
-$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
-solvent (in this case the CSF), and $R$ is the radius of the molecule.
-For the exosomes, we calculate $D$ using~\eqref{eq:D_stokes_einstein}
-with $R=200$ nm. This radius covers the slowest diffusing exosomes,
-since the smaller exosomes would have diffusion coefficients similar to the other molecules.
-For STM-GFP, we estimated the diffusion coefficient by extrapolating
-the experimentally observed diffusion coefficient of
-GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-assuming that if $D$ scales with $1/R$ according to~\eqref{eq:D_stokes_einstein},
-$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations
-are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
-
-%Implicit in this approach is the assumption that the proteins all have the same density.
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{l|ccc}
-        \toprule
-        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
-        \midrule 
-        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
-        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
-        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{5.75e-11}$ & * \\
-        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
-        \bottomrule
-    \end{tabular}
-    \caption{Molecular mass and diffusion coefficients of simulated solutes.
-    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-    (*) The value was extrapolated based on the value of $D$ for
-    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-    assuming that $D$ scales with the cube root of the molecule mass.
-    (\textdagger) The value was estimated using the Stokes-Einstein relation~\eqref{eq:D_stokes_einstein}.}
-    \label{tab:diff_coeff_table}
-\end{table}
-
-\subsection*{Quantities of interest}
-We calculate the mean solute concentrations
-\begin{equation}
-    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
-    \label{eq:c_mean_i}
-\end{equation}
-in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
-as functions of time, where $|\Omega_i|$ is the volume of
-the domain $\Omega_i$. The dynamics of ROI 1 follows directly
-from~\eqref{eq:photoconversion_curve}. In addition,
-we report time-to-threshold: the time $\hat{t}_i$ when
-the mean concentration $\cbar_i$ first exceed a threshold
-value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
-$\hat{c}_i=0.10$ for ROI 5--6.
-
-To evaluate the relative importance of advection and
-diffusion as transport mechanisms, we consider the Péclet number
-\begin{equation*}
-    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
-    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
-\end{equation*}
-Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
-and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
-Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
-respectively, and $D$ is the solute diffusion coefficient.
-In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
-ventricles geometry along the rostrocaudal ($x$-) axis.
-We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
-The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
-\begin{equation*}
-    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
-\end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle. To assess the assumption that the CSF flow is governed by the Stokes equations,
-we also compute the Reynolds number
-\begin{equation*}
-    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
-\end{equation*}
-with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
-
-%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
-\subsection*{Numerical approximation of the Stokes equations}
-
-The Stokes equations~\eqref{eq:stokes_eqs} are discretized with a finite element method
-in space, while in time, we employ a first-order implicit Euler discretization.
-We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
-For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
-The BDM elements have degrees of freedom associated with integral moments of the
-velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems},
-thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
-We impose the boundary conditions for both the tangential traction $\bsigpar$ and
-the normal pressure $\Tilde{p}(t)$ weakly.
-For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
-The resulting total number of degrees of freedom at each time step is 943 820.
-\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
-discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-To ensure stability of the scheme, continuity in tangential velocities on interior facets
-is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.}
-Since the divergence of the velocity is a subspace of the pressure space for this scheme,
-the divergence-free condition of the velocity is satisfied exactly on each
-element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
-
-\subsection*{Numerical approximation of the advection-diffusion equation}
-The advection-diffusion equation~\eqref{eq:adv_diff_strong} is discretized
-with a first-order implicit Euler method in time, and a first-order,
-symmetric interior penalty discontinuous Galerkin (DG)
-method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
-conservation properties.
-To accurately approximate the solute concentrations even
-in the presence of strong advection (high Péclet numbers),
-we use an upwind scheme for the velocity when calculating the
-advective flux~\cite{Patankar2018NumericalFlow}.
-As for the flow equations, we use a timestep size of
-$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
-with a final time of simulation $T = 856$ s.
-A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
-
-\subsection*{Solution strategy and software implementation}
-Owing to the one-way coupling between the velocity field $\uu$
-and the concentration $c$, the governing equations for the
-CSF flow and the concentration can be solved sequentially when modeling solute transport.
-For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
-the viscous forces dominate the inertial forces.
-In this case, we first solve the steady-state Stokes equations~\eqref{eq:stokes_eqs}
-for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
-the advection-diffusion equation~\eqref{eq:adv_diff_strong}.
-For the other flow scenarios, the Stokes equations are solved for one
-period of the pulsatile cardiac motion. The solution of this one period
-is then used periodically as input for the advection-diffusion equation.
-
-The numerical solution schemes for the Stokes equations and the
-advection-diffusion equation were implemented and solved numerically with DOLFINx~\cite{dolfinx2023preprint},
-the Python interface of the finite element software
-FEniCSx, with
-petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
-A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
-linear systems resulting from the discretized Stokes equations.
-For the discretized advection-diffusion equation, we used an iterative
-linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
-preconditioning~\cite{Jacobi1845UeberGleichungen}.
-Numerical experiments verified the accuracy of the model implementation
-(\Cref{sec:appB_verification}). The simulation code is openly
-available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-%%------PHYSICAL EXPERIMENTS------%%
-\subsection*{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
-The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
-Norwegian Food Safety Authority (NFSA, Mattilsynet).
-The zebrafish were maintained in accordance with the guidelines set by the
-NFSA and the European Communities Council Directive.
-
-The larval and adult zebrafish were raised under standard husbandry
-conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
-The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
-14/10 hr light/dark cycle.
-From fertilization to 3 dpf, larvae were maintained in egg
-water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
-and subsequently transferred to artificial fish water (AFW)
-(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
-\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
-(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
-and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
-\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
-Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
-(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
-
-Wholemount~\emph{in vivo} live imaging and photoconversion
-experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
-\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
-adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
-Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
-or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
-The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
-
-For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
-fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
-tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
-To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
-and then centrifuged at 13000 rpm for 2 minutes.
-The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
-used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
-\textmu L of assay mix; 1.86 \textmu L of RO water.
-
-\subsection*{Generation of transgenic line to study CSF \fixme{and transport} dynamics} %\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}
-To generate a transgenic line expressing the photoconvertible protein Dendra2 in
-the brain ventricles, we fused the open reading frame (ORF)
-of the neuropeptide y (npy) signal peptide
-(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
-zebrafish codon optimized Dendra2 DNA sequence.
-The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
-3’ ends (GenScript Biotech) and inserted into the
-pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
-through restriction enzyme cloning (GenScript Biotech)
-to generate the 5xuas:Signal-Dendra2 plasmid DNA..
-
-A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
-was microinjected into one-cell stage embryos to generate the transgenic line,
-as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
-embryos were raised to adulthood (F0).
-Germline-transmitted founder zebrafish were identified by breeding with
-multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
-Dendra2 signals were screened and raised to adult zebrafish.
-
-\subsection*{Wholemount zebrafish \emph{in vivo} live time-lapse imaging and photoconversion of Dendra2}
-Two dpf larval zebrafish were anesthetized in 0.013\% MS222
-(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
-mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
-to obtain a lateral view of the brain ventricles. After the
-fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
-After solidification, AFW containing 0.013\% MS222 was added,
-and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
-and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
-at room temperature.
-
-The time-lapse images were acquired in a single plane, covering the
-telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
-with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
-of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
-The first 10 images were scanned without photoconversion to obtain a
-baseline value of fluorescence intensity, and the next 290 images were
-scanned while performing photoconversion.
-
-For photoconversion, ``Bleaching" and ``Region" in the ZEN software
-were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
-of the dorsoposterior diencephalic ventricle with 100\% laser power.
-The laser was illuminated in the area repeatedly between each scanning.
-After imaging, the fish health was checked and only data from healthy fish were analyzed.
-Data were collected and analyzed from three separate experiments,
-with a total of 8 controls and 6 mutants.
-
-\subsection*{Photoconversion data analysis}
-All data analysis was performed in MATLAB and the codes are available in
-the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-Following import of the image data, the photoconverted channel
-was aligned to correct for drift in $x,y$ directions using previously
-developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
-Only stable recordings were further analyzed. 
-To increase the signal to noise ratio, the images were downsampled by
-a block average using a resampling factor of 6 (using the MATLAB function blockproc).
-The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
-$\Delta F$$)$ was calculated for each pixel at each time point of the data.
-Here, the value $F_0$ is the average fluorescence intensity for the
-baseline (the first 10 time-lapse images) acquired before photoconversion.
-
-To identify the time needed to pass a certain threshold value,
-$\Delta F$ values were first smoothened.
-The first timepoint when values surpassed the threshold was reported
-per pixel (in the downsampled images).
-A mask for the image was generated using the green (not photoconverted)
-channel and calculated on the block-averaged data based on the intensity
-being higher than 1.5x median intensity of all the frames.
-
-To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
-first drawn on the aligned and block-averaged time series.
-Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
-and ROIs 2--6 in different regions of the ventricular system.
-The pixel values of the fluorescence intensity within one ROI were
-averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
-To normalize the data with respect to photoconversion efficiency, the
-$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
-obtained for ROI 1 at the end of the experiment,
-so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
-zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
-We report these mean values together with a one-standard deviation error band.
-
-\subsection*{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Cref{fig:fig1}b, c, we carried out
-particle tracking in a larval zebrafish injected with fluorescent beads.
-As described in Olstad~\emph{et al.}~\cite{Olstad2019CiliaryDevelopment},
-anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
-(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
-in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
-dissolved in artificial CSF. Artificial CSF composition was as follows:
-124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
-1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
-2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
-The needles used for the injections were pulled with a
-Sutter Instrument Co. Model P-2000 from thin-walled glass
-capillaries (1.00 mm; VWR) and cut open with a forceps.
-A volume of 1 nl of the solution was injected with a pressure injector
-(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
-The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
-
-Following injection, the zebrafish was directly placed under the confocal
-microscope and 1200 images were acquired at a frequency of 13.1 Hz.
-A single optical section was obtained. Particle tracking was done using
-TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
-and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
-The parameters for TrackMate were as follows.
-The DoG detector was used with the settings: threshold: 2.0, with
-median filtering; radius: 2.0, with subpixel localization.
-Next, the Simple LAP tracker was used with settings: max frame gap: 2;
-alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
-splitting max distance: 15.0; allow gap closing: true; allow track splitting:
-false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
-Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 \textmu m, were plotted in~\Cref{fig:fig1}b, c.
-
 %%--------------RESULTS--------------%%
-\section*{Results}
-
-\subsection*{Motile cilia induce flow compartmentalization within the brain ventricles}
-
-We model the compartmentalized and pulsatile CSF flow observed \emph{in vivo}~(\Cref{fig:fig1}b, c)
+\section{Results}
+\subsection{Motile cilia induce flow compartmentalization within the brain ventricles}
+
+We model the compartmentalized and pulsatile CSF flow observed in vivo~(\Crefpanels{fig:fig1}{b, c})
 by the Stokes equations, and solve the equations numerically using a finite element method.
@@
 system, with large-scale vortex structures in the anterior and middle
-ventricles~(\Cref{fig:fig1}e). The highest velocities ($26.5$ \textmu m/s)
+ventricles~(~\Crefpanels{fig:fig1}{e}). The highest velocities ($26.5$ \textmu m/s)
 occur in the vicinity of the dorsal cilia in the middle ventricle.
@@
 generated by the ciliary motion vanish. The simulated CSF
-flow is pulsatile as a result of the sinusoidal pressure gradient (\Cref{fig:fig1}f, g),
+flow is pulsatile as a result of the sinusoidal pressure gradient (~\Crefpanels{fig:fig1}{f, g}),
 with a peak velocity magnitude of $4.8$ \textmu m/s. At each time instant, the flow
@@
 with vortex-structures in the anterior and middle ventricles
-and directional flow in the posterior ventricle (\Cref{fig:fig1}h--j,
+and directional flow in the posterior ventricle (~\Crefpanels{fig:fig1}{h--j},
 \fixme{Supplementary video 1}). These characteristic patterns suggest
@@
 CSF flow model reproduces the flow features observed
-\emph{in vivo}~\cite{Olstad2019CiliaryDevelopment}.
-
-\subsection*{Ventricular solute transport is advection-dominated for larger molecules}
+in vivo~\cite{Olstad2019CiliaryDevelopment}.
+
+\subsection{Ventricular solute transport is advection-dominated for larger molecules}
 We next explore the impact of these CSF flow patterns and magnitudes
@@
 interest in the dorsal region of the middle ventricle (ROI 1)
-(\Cref{fig:fig2}a). We consider the spread of
+(~\Crefpanels{fig:fig2}{a}). We consider the spread of
 a solute concentration with a given molecular diffusion coefficient,
@@
 exosomes, the advective transport by the CSF flow dominates diffusion
-(\Cref{fig:fig2}b). The vortex structures of the velocity field
+(\Crefpanels{fig:fig2}{b}). The vortex structures of the velocity field
 carry over into the concentration field, indicating that transport
@@
 obfuscated, and the solute spreads more uniformly throughout the
-ventricular geometry (\Cref{fig:fig2}c, d). Notably, the
+ventricular geometry (\Crefpanels{fig:fig2}{c, d}). Notably, the
 smaller solutes with higher diffusion coefficients spread more quickly
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}
-    \caption{Simulated distribution and evolution after photoconversion of
-    exosomes ($D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). \\
+    \includegraphics[width=\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}\caption{Simulated distribution and evolution after photoconversion of
+    exosomes ($D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). 
     \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
@@
     threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.
-    Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}
-    \label{fig:fig2}
+    Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}\label{fig:fig2}
 \end{figure}
@@
 concentrations $\cbar_i(t)$ as functions of time
-(\Cref{fig:fig2}e--g) and
+(\Crefpanels{fig:fig2}{e--g}) and
 the times $\hat{t}$ when the mean concentrations $\cbar_i$ first exceed
-a threshold value $\hat{c}$ (\Cref{fig:fig2}h)
-in 6 ROIs (\Cref{fig:fig2}a).
+a threshold value $\hat{c}$ (\Crefpanels{fig:fig2}{h})
+in 6 ROIs (\Crefpanels{fig:fig2}{a}).
 The dynamics at the site of photoconversion (ROI 1)
@@
 For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
-(\Cref{fig:fig2}e--g),
+(\Crefpanels{fig:fig2}{e--g}),
 which results in smaller times-to-threshold
-(\Cref{fig:fig2}h).
+(\Crefpanels{fig:fig2}{h}).
 For all three diffusion coefficients, the dynamics of ROI 5
@@
 
-\subsection*{Validation of the simulations with experimental data}
+\subsection{Validation of the simulations with experimental data}
 To validate our computational model, we performed photoconversion experiments
@@
 calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
-over time (\Cref{fig:fig3}a,
+over time (\Crefpanels{fig:fig3}{a},
 $F_0$ being the average fluorescence at baseline).
 
-We obtained very similar kinetics curves (\Cref{fig:fig3}a, b)
-and time-to-threshold values (\Cref{fig:fig3}c, d) when comparing our
-experiments (\Cref{fig:fig3}a, c) with
-simulation (\Cref{fig:fig3}b, d).
+We obtained very similar kinetics curves (\Crefpanels{fig:fig3}{a, b})
+and time-to-threshold values (\Crefpanels{fig:fig3}{c, d}) when comparing our
+experiments (\Crefpanels{fig:fig3}{a, c}) with
+simulation (\Crefpanels{fig:fig3}{b, d}).
 Importantly, since the initial condition of the simulation is a mean concentration of zero,
@@
 the simulations as compared to the experiments.
-Despite observing small differences, the \emph{in vivo} experiments and
+Despite observing small differences, the in vivo experiments and
 simulations are similar enough to convincingly validate the model.
@@
 
-\subsection*{Absence of ciliary motion affects local protein distribution}
+\subsection{Absence of ciliary motion affects local protein distribution}
 Since CSF flow is highly disturbed in the absence of motile cilia, we
@@
 in control and motile-cilia mutant (\emph{smh}) zebrafish .
-By plotting the means of $\Delta F$ (\Cref{fig:fig4}a)
+By plotting the means of $\Delta F$ (\Crefpanels{fig:fig4}{a})
 and the time to threshold
-across the control and mutant cohorts (\Cref{fig:fig4}b),
+across the control and mutant cohorts (\Crefpanels{fig:fig4}{b}),
 we identified a significant
@@
 higher mean times-to-threshold in the \emph{smh}
-mutants compared to controls (\Cref{fig:fig4}b).
+mutants compared to controls (\Crefpanels{fig:fig4}{b}).
 
@@
 and compare it with the baseline model
-(both cilia and cardiac motion) (\Cref{fig:fig4}c).
+(both cilia and cardiac motion) (\Crefpanels{fig:fig4}{c}).
 Similar to our experiments, we observe slower dynamics in simulations for ROIs 2 and 4,
@@
 
-\subsection*{Loss of cilia motility in specific subpopulation slows down transport}
+\subsection{Loss of cilia motility in specific subpopulation slows down transport}
 We previously identified three distinct ciliated cell lineages in the
@@
 the telencephalic (anterior) ventricle, and the dorsal and ventral parts
-of the diencephalic (middle) ventricle (\Cref{fig:fig5}a).
+of the diencephalic (middle) ventricle (\Crefpanels{fig:fig5}{a}).
 The cilia tangential traction boundary condition is for each case
@@
 as the maximum velocity magnitude drops from 27.7 \textmu m/s to 8.0 \textmu m/s.
-\emph{In vivo}, these cilia generate the strongest flow at
+In vivo, these cilia generate the strongest flow at
 this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
@@
 contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
-force~(\Cref{fig:fig5}b). The magnitude of the force contributions are thus
+force~(\Crefpanels{fig:fig5}{b}). The magnitude of the force contributions are thus
 more similar than the difference in their impact on the maximum velocity magnitudes.
@@
 in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
-exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}c).
+exhibit changes in the dynamics of $\cbar$ (\Crefpanels{fig:fig5}{c}).
 Compared to the baseline model results, we observe a slower increase and lower final concentration
@@
 In contrast, removal of telencephalic cilia does not alter the evolution of the
-mean concentration $\cbar$ with time (\Cref{fig:fig5}c).
+mean concentration $\cbar$ with time (\Crefpanels{fig:fig5}{c}).
 Finally, without ventral cilia in the diencephalic ventricle,
@@
 
-\subsection*{Modification of ventricles geometry impacts protein distribution}
+\subsection{Modification of ventricles geometry impacts protein distribution}
 Variations in ventricular morphology impact CSF flow patterns.
@@
 one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
-and the combination of the above three modifications (\Cref{fig:fig6}a).
+and the combination of the above three modifications (\Crefpanels{fig:fig6}{a}).
 We simulate CSF flow in the modified geometries with the baseline flow model
 and use the resulting velocity field to simulate transport of Dendra2
-(\Cref{fig:fig6}b).
+(\Crefpanels{fig:fig6}{b}).
 
@@
 
-%%--------------------------------------%%
-%%--------------------------------------%%
-%%--------------DISCUSSION--------------%%
-%%--------------------------------------%%
-%%--------------------------------------%%
-
-\section*{Discussion}
+\section{Discussion}
 We have presented a computational model of CSF flow and solute transport within the brain ventricles.
@@
 Using the simulated CSF flow, we modeled solute transport by an advection-diffusion equation.
-These results compared well with experimental data performed \emph{in vivo} in zebrafish.
+These results compared well with experimental data performed in vivo in zebrafish.
 Then, by using both a computational model and zebrafish mutants with paralyzed cilia,
@@
 
-\subsection*{The roles of advection and diffusion in intraventricular solute transport}
+\subsection{The roles of advection and diffusion in intraventricular solute transport}
 To investigate the roles of advection and diffusion in solute transport, we quantified transport
@@
 Even though we identified very similar dynamics in simulations and
-\emph{in vivo} experiments, the dynamics of the simulations were generally
+in vivo experiments, the dynamics of the simulations were generally
 more rapid and resulted in higher total amounts of solute.
@@
 
-\subsection*{Impact of cilia \fixme{properties} and ventricular geometry}
+\subsection{Impact of cilia \fixme{properties} and ventricular geometry}
 To gain further insights into how CSF distribution depends on cilia \fixme{properties (@Nathalie: do we really
@@
 dorsal middle ventricle contribute the most to solute distribution, which aligns well with the fact
-that these cilia generate the strongest flow field \emph{in vivo}~\cite{Olstad2019CiliaryDevelopment} and in our model.
+that these cilia generate the strongest flow field in vivo~\cite{Olstad2019CiliaryDevelopment} and in our model.
 In contrast, removing the ventral cilia in the middle ventricle did not greatly impact flow dynamics.
@@
 
-Altogether, our model is flexible and thereby allows \emph{in silico} testing of
+Altogether, our model is flexible and thereby allows in silico testing of
 further hypotheses on the effects of ciliated lineages and ventricular morphology on
@@
 
-\subsection*{Computational model assumptions and boundary conditions}
+\subsection{Computational model assumptions and boundary conditions}
 To model CSF, we employed slip boundary conditions at the ventricular walls,
@@
 It has been observed, both previously and in this work, that the fluid velocity increases
-towards the wall~(\Cref{fig:fig1}\fixme{c}).
+towards the wall~(\Crefpanels{fig:fig1}c).
 Using slip boundary conditions allows for this behavior.
@@
 
-\subsection*{Estimation of computational model parameters}
+\subsection{Estimation of computational model parameters}
 The diffusion coefficients used in this study were partially based on values
@@
 Potma2001ReducedCells, Mahmood2023ExosomeTemperature} using the Stokes-Einstein
-relation~\cite{Einstein1905UberTeilchen}~(\Cref{eq:D_stokes_einstein}).
+relation~(\Cref{eq:D_stokes_einstein})~\cite{Einstein1905UberTeilchen}.
 This extrapolation assumes the diffusing substance is of spherical shape, which proteins are not,
@@
 the CSF in which photoconverted Dendra2 are transport in our experiments may be more viscous
-than what we consider. This would reduce the diffusion coefficient~(cf.~\Cref{eq:D_stokes_einstein}),
+than what we consider. This would reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
 but based on reports of protein concentration having a limited impact on the viscosity of
@@
 
-We heuristically determined the parameter $\tau = \num{6.5e-4}$ Pa, which determines
+We heuristically determined the parameter $\tau = 0.65$ mPa, which determines
 the magnitude of the cilia tangential traction boundary conditions. The maximum force applied
 was in the dorsal region of the middle ventricle, where the posterior region had a tangential
-traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = \num{2.5e-3}$ Pa applied to the
+traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = 2.5$ mPa applied to the
 boundary. A couple of previous simulation studies of cilia-mediated flow in brain ventricles have
@@
 4000 N/$\mathrm{m^2}$. The resulting numerical velocity fields matched well with
-\emph{in vivo} measurements, where the maximum velocity magnitude was around 5 \textmu m/s
+in vivo measurements, where the maximum velocity magnitude was around 5 \textmu m/s
 (recall that our model exhibits a maximum of 27.7 \textmu m/s).
@@
 
-\subsection*{Numerical approximation and convergence rates}
+\subsection{Numerical approximation and convergence rates}
 The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme
@@
 
-\emph{A priori} error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
+A priori error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
 derived in a mesh-dependent broken $H^1$-norm for $\uu$ and the $L^2$-norm for the pressure. The respective 
@@
 
-\subsection*{The role of motile cilia in intraventricular flow and transport
-\fixme{Might be merged with further work.}}
+\subsection{The role of motile cilia in intraventricular flow and transport}
 Our work has studied CSF flow and solute distribution
@@
 
-\section*{Conclusion}
+\section{Conclusion}
 We have presented a numerical model
@@
 
-%%--------------ACKNOWLEDGMENTS--------------%%
-\section*{Acknowledgments}
+% Experimental section
+
+\section{Computational and Experimental Methods}
+\subsection{Image-based computational geometries of zebrafish brain ventricles}
+To model flow and transport in zebrafish larval brain ventricles, we generated a
+3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
+injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
+From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
+The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
+The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
+maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
+At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
+the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
+Parts of the ventricular surfaces were marked to be lined with
+motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
+\begin{figure}%[hbt!]
+    \centering
+    \includegraphics[width=\linewidth]{graphics/figure1.png}
+    \caption{
+    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
+    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
+    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
+    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
+    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
+    anterior/posterior facets (blue).
+    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
+    cilia-only/no-cardiac flow model.
+    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
+    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
+    \textbf{g.} Streamlines simulated with the baseline flow model at
+    a time 25\% into the cardiac cycle. %t=0.112613 s
+    \textbf{h.} Streamlines simulated with the baseline flow model at
+    a time 50\% into the cardiac cycle. %t=0.225225 s
+    \textbf{i.} Streamlines simulated with the baseline flow model at
+    a time 75\% into the cardiac cycle. %t=0.315315 s
+    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
+    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
+    }
+    \label{fig:fig1}
+\end{figure}
+
+The morphology and geometry of the brain ventricles vary across zebrafish
+individuals, and under physiological and pathological conditions. 
+Motivated by an interest in how ventricular geometry impacts solute distribution,
+we also consider four variations in the geometry \fixme{(cross-sectional area
+reduction in parentheses):
+by shrinking the fore-mid brain connection (66 \%), 
+the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+% Cross-sectional areas of ducts normal to flow direction
+% Modified region       Original mesh        Deformed mesh
+% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
+% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
+% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
+
+\subsection{Computational CSF dynamics}
+The beating motion of the cilia generates CSF flow with steady rotational
+structures~\cite{Olstad2019CiliaryDevelopment}
+within the brain ventricles (\Crefpanels{fig:fig1}{a--c}).
+In addition, cardiac pulsations induce pulsatile CSF flow.
+We model this flow of CSF in the brain ventricles by the time-dependent,
+incompressible Stokes equations which read as follows.
+Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
+and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
+\begin{subequations}
+    \begin{align}
+      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
+      \quad \text{in } \Omega,\\
+      \nabla \cdot \uu &= 0
+      \quad  \text{in } \Omega,
+  \end{align}
+  \label{eq:stokes_eqs}% 
+\end{subequations}%
+where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
+and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
+Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
+Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
+and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
+of the CSF~\cite{Bloomfield1998EffectsFluid}.
+We introduce the tangential traction $\bsigpar$ as the
+tangential component of the traction $\hat{\bsig}=\bsig\nn$:
+\begin{equation*}
+    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
+\end{equation*}
+where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
+and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
+We consider three types of boundary conditions:
+(i) \emph{tangential traction} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
+the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
+and (iii) \emph{free slip} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
+Unless noted otherwise, the free-slip condition is applied on the
+boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
+
+To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
+we consider the following computational flow scenarios,
+each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
+\begin{itemize}
+    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
+    contributions both from the cilia forces and the cardiac pulsations.
+    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
+    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
+
+    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
+    cilia forces but no cardiac pulsations.
+    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
+    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
+
+    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
+    cardiac pulsations but no cilia forces.
+    Here, we set the tangential traction to zero on the cilia boundary
+    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
+    anterior/posterior boundary $\Gp$.  % Model II/Model B
+\end{itemize}
+
+\subsection{Cilia-driven flow}
+On the ciliated regions of the ventricle walls $\Gc$ (\Crefpanels{fig:fig1}{d}, magenta markers),
+we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
+of the cilia acting on the CSF.
+We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
+and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
+cilia region (see~\Cref{subsec:appendixA1}).
+Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
+model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
+The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
+$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
+In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
+We calibrated $\tau$ heuristically by comparing these experimental velocity values
+with the simulated, maximum velocity magnitude.
+
+\subsection{Flow induced by cardiac pulsations}
+To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
+$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
+boundary $\Gp$~(\Crefpanels{fig:fig1}{d}, blue markers).
+Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
+the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
+The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
+and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
+Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
+Particle tracking data of pulsatile motion was used to determine the contributions of the
+cardiac pulsations to the velocity magnitude,
+as compared to the effect of cilia motion on the flow (see~\Cref{sec:appC_particle_transport}).
+
+\subsection{Computational model of solute transport after photoconversion}
+We simulate transport of photoconverted proteins within the brain ventricles by
+modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
+time $t > 0$ by the advection-diffusion equation
+\begin{equation}
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
+    \label{eq:adv_diff_strong}
+\end{equation}
+where the total concentration flux $\mathbf{J}$ is assumed to consist of an advective and a diffusive flux:
+\begin{equation*}
+    \JJ = c\uu - D\nabla c .
+\end{equation*}
+Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\Cref{eq:stokes_eqs},
+and $D$ is the molecular diffusion coefficient of the solute.
+Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
+The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
+except at the anterior/posterior boundary $\Gamma_p$.
+At the anterior/posterior boundary, we permit the solute concentration to be advected into
+and out of the domain in a manner that ensures conservation of mass
+(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
+
+To computationally represent protein photoconversion in a region
+$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
+we prescribe a given time-dependent value to the solute concentration in this region. 
+Mimicking the experimental protocol, we consider the dorsal part of the
+diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
+\begin{equation}
+  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
+  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
+\label{eq:photoconversion_curve}
+\end{equation}
+The value $a=65$ was chosen to fit the fluorescence intensity curve
+observed in the physical photoconversion experiments.
+
+\subsection{Estimation of diffusion coefficients via the Stokes-Einstein relation}
+Motivated by an interest in molecules that are significant in neural development,
+we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
+used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
+To estimate the diffusion coefficients of these, when not
+available in the literature, we use the Stokes--Einstein relation:
+\begin{equation}
+    D = \frac{k_B T}{6\pi \mu R},
+    \label{eq:D_stokes_einstein}
+\end{equation}
+which is an expression for the diffusion coefficient of a spherical
+molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
+In~\Cref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
+$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
+solvent (in this case the CSF), and $R$ is the radius of the molecule.
+For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
+with $R=200$ nm. This radius covers the slowest diffusing exosomes,
+since the smaller exosomes would have diffusion coefficients similar to the other molecules.
+For STM-GFP, we estimated the diffusion coefficient by extrapolating
+the experimentally observed diffusion coefficient of
+GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+assuming that if $D$ scales with $1/R$ according to~\Cref{eq:D_stokes_einstein},
+$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
+The resulting diffusion coefficients used in the simulations
+are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
+
+%Implicit in this approach is the assumption that the proteins all have the same density.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{l|ccc}
+        \toprule
+        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
+        \midrule 
+        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
+        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
+        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
+        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{5.75e-11}$ & * \\
+        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
+        \bottomrule
+    \end{tabular}
+    \caption{Molecular mass and diffusion coefficients of simulated solutes.
+    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+    (*) The value was extrapolated based on the value of $D$ for
+    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+    assuming that $D$ scales with the cube root of the molecule mass.
+    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
+    \label{tab:diff_coeff_table}
+\end{table}
+
+\subsection{Quantities of interest}
+We calculate the mean solute concentrations
+\begin{equation}
+    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
+    \label{eq:c_mean_i}
+\end{equation}
+in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
+as functions of time, where $|\Omega_i|$ is the volume of
+the domain $\Omega_i$. The dynamics of ROI 1 follows directly
+from~\Cref{eq:photoconversion_curve}. In addition,
+we report time-to-threshold: the time $\hat{t}_i$ when
+the mean concentration $\cbar_i$ first exceed a threshold
+value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
+$\hat{c}_i=0.10$ for ROI 5--6.
+
+To evaluate the relative importance of advection and
+diffusion as transport mechanisms, we consider the Péclet number
+\begin{equation*}
+    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
+    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
+\end{equation*}
+Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
+and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
+Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
+respectively, and $D$ is the solute diffusion coefficient.
+In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
+ventricles geometry along the rostrocaudal ($x$-) axis.
+We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
+The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
+\begin{equation*}
+    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
+\end{equation*}
+and then averaging $\overline{u}$ in time over one cardiac cycle. To assess the assumption that the CSF flow is governed by the Stokes equations,
+we also compute the Reynolds number
+\begin{equation*}
+    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
+\end{equation*}
+with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
+
+%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
+\subsection{Numerical approximation of the Stokes equations}
+
+The Stokes equations~\Cref{eq:stokes_eqs} are discretized with a finite element method
+in space, while in time, we employ a first-order implicit Euler discretization.
+We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
+For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
+The BDM elements have degrees of freedom associated with integral moments of the
+velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems},
+thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
+We impose the boundary conditions for both the tangential traction $\bsigpar$ and
+the normal pressure $\Tilde{p}(t)$ weakly.
+For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
+The resulting total number of degrees of freedom at each time step is 943 820.
+\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
+discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
+To ensure stability of the scheme, continuity in tangential velocities on interior facets
+is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.}
+Since the divergence of the velocity is a subspace of the pressure space for this scheme,
+the divergence-free condition of the velocity is satisfied exactly on each
+element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
+
+\subsection{Numerical approximation of the advection-diffusion equation}
+The advection-diffusion equation~\Cref{eq:adv_diff_strong} is discretized
+with a first-order implicit Euler method in time, and a first-order,
+symmetric interior penalty discontinuous Galerkin (DG)
+method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
+conservation properties.
+To accurately approximate the solute concentrations even
+in the presence of strong advection (high Péclet numbers),
+we use an upwind scheme for the velocity when calculating the
+advective flux~\cite{Patankar2018NumericalFlow}.
+As for the flow equations, we use a timestep size of
+$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
+with a final time of simulation $T = 856$ s.
+A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
+
+\subsection{Solution strategy and software implementation}
+Owing to the one-way coupling between the velocity field $\uu$
+and the concentration $c$, the governing equations for the
+CSF flow and the concentration can be solved sequentially when modeling solute transport.
+For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
+the viscous forces dominate the inertial forces.
+In this case, we first solve the steady-state Stokes equations~\Cref{eq:stokes_eqs}
+for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
+the advection-diffusion equation~\Cref{eq:adv_diff_strong}.
+For the other flow scenarios, the Stokes equations are solved for one
+period of the pulsatile cardiac motion. The solution of this one period
+is then used periodically as input for the advection-diffusion equation.
+
+The numerical solution schemes for the Stokes equations and the
+advection-diffusion equation were implemented and solved numerically with DOLFINx~\cite{dolfinx2023preprint},
+the Python interface of the finite element software
+FEniCSx, with
+petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
+A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
+linear systems resulting from the discretized Stokes equations.
+For the discretized advection-diffusion equation, we used an iterative
+linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
+preconditioning~\cite{Jacobi1845UeberGleichungen}.
+Numerical experiments verified the accuracy of the model implementation
+(\Cref{sec:appB_verification}). The simulation code is openly
+available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+
+%%------PHYSICAL EXPERIMENTS------%%
+\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
+The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
+Norwegian Food Safety Authority (NFSA, Mattilsynet).
+The zebrafish were maintained in accordance with the guidelines set by the
+NFSA and the European Communities Council Directive.
+
+The larval and adult zebrafish were raised under standard husbandry
+conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
+The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
+14/10 hr light/dark cycle.
+From fertilization to 3 dpf, larvae were maintained in egg
+water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
+and subsequently transferred to artificial fish water (AFW)
+(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
+\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
+(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
+and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
+\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
+Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
+(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
+
+Wholemount in vivo live imaging and photoconversion
+experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
+\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
+adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
+or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
+The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
+
+For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
+fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
+tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
+To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
+and then centrifuged at 13000 rpm for 2 minutes.
+The supernatant containing gDNA was utilized for KASP assays-based analysis.
+The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
+used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
+For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
+\textmu L of assay mix; 1.86 \textmu L of RO water.
+
+\subsection{Generation of transgenic line to study CSF \fixme{and transport} dynamics} %\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}
+To generate a transgenic line expressing the photoconvertible protein Dendra2 in
+the brain ventricles, we fused the open reading frame (ORF)
+of the neuropeptide y (npy) signal peptide
+(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
+zebrafish codon optimized Dendra2 DNA sequence.
+The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
+3’ ends (GenScript Biotech) and inserted into the
+pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
+through restriction enzyme cloning (GenScript Biotech)
+to generate the 5xuas:Signal-Dendra2 plasmid DNA..
+
+A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
+was microinjected into one-cell stage embryos to generate the transgenic line,
+as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
+embryos were raised to adulthood (F0).
+Germline-transmitted founder zebrafish were identified by breeding with
+multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
+Dendra2 signals were screened and raised to adult zebrafish.
+
+\subsection{Wholemount zebrafish in vivo live time-lapse imaging and photoconversion of Dendra2}
+Two dpf larval zebrafish were anesthetized in 0.013\% MS222
+(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
+mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
+to obtain a lateral view of the brain ventricles. After the
+fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
+After solidification, AFW containing 0.013\% MS222 was added,
+and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
+and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
+at room temperature.
+
+The time-lapse images were acquired in a single plane, covering the
+telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
+with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
+of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
+The first 10 images were scanned without photoconversion to obtain a
+baseline value of fluorescence intensity, and the next 290 images were
+scanned while performing photoconversion.
+
+For photoconversion, ``Bleaching" and ``Region" in the ZEN software
+were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
+of the dorsoposterior diencephalic ventricle with 100\% laser power.
+The laser was illuminated in the area repeatedly between each scanning.
+After imaging, the fish health was checked and only data from healthy fish were analyzed.
+Data were collected and analyzed from three separate experiments,
+with a total of 8 controls and 6 mutants.
+
+\subsection{Photoconversion data analysis}
+All data analysis was performed in MATLAB and the codes are available in
+the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+
+Following import of the image data, the photoconverted channel
+was aligned to correct for drift in $x,y$ directions using previously
+developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
+Only stable recordings were further analyzed. 
+To increase the signal to noise ratio, the images were downsampled by
+a block average using a resampling factor of 6 (using the MATLAB function blockproc).
+The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
+$\Delta F$$)$ was calculated for each pixel at each time point of the data.
+Here, the value $F_0$ is the average fluorescence intensity for the
+baseline (the first 10 time-lapse images) acquired before photoconversion.
+
+To identify the time needed to pass a certain threshold value,
+$\Delta F$ values were first smoothened.
+The first timepoint when values surpassed the threshold was reported
+per pixel (in the downsampled images).
+A mask for the image was generated using the green (not photoconverted)
+channel and calculated on the block-averaged data based on the intensity
+being higher than 1.5x median intensity of all the frames.
+
+To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
+first drawn on the aligned and block-averaged time series.
+Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
+and ROIs 2--6 in different regions of the ventricular system.
+The pixel values of the fluorescence intensity within one ROI were
+averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
+To normalize the data with respect to photoconversion efficiency, the
+$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
+obtained for ROI 1 at the end of the experiment,
+so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
+zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
+We report these mean values together with a one-standard deviation error band.
+
+\subsection{Intraventricular injection of microbeads and particle tracking}
+To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c}, we carried out
+particle tracking in a larval zebrafish injected with fluorescent beads with a procedure described in detail in previous work~\cite{Olstad2019CiliaryDevelopment}.
+Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
+(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
+in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
+dissolved in artificial CSF. Artificial CSF composition was as follows:
+124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
+1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
+2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
+The needles used for the injections were pulled with a
+Sutter Instrument Co. Model P-2000 from thin-walled glass
+capillaries (1.00 mm; VWR) and cut open with a forceps.
+A volume of 1 nl of the solution was injected with a pressure injector
+(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
+The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
+
+Following injection, the zebrafish was directly placed under the confocal
+microscope and 1200 images were acquired at a frequency of 13.1 Hz.
+A single optical section was obtained. Particle tracking was done using
+TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
+and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
+The parameters for TrackMate were as follows.
+The DoG detector was used with the settings: threshold: 2.0, with
+median filtering; radius: 2.0, with subpixel localization.
+Next, the Simple LAP tracker was used with settings: max frame gap: 2;
+alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
+splitting max distance: 15.0; allow gap closing: true; allow track splitting:
+false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
+Only the particle tracks with at least 30 data points, while simultaneously
+covering a distance of at least 8.8 \textmu m, were plotted in~\Crefpanels{fig:fig1}{b, c}.
+
+\medskip
+\textbf{Supporting Information} \par %Please delete the Suppporting Information statement if it is not applicable.
+Please supply Supporting Information in another file.
+Supporting information should not be provided in .tex format
+Supporting Information is available from the Wiley Online Library or from the author.
+
+% Acknowledgements
+\medskip
+\textbf{Acknowledgements} \par 
 Halvor Herlyng acknowledges support from the national infrastructure for computational
@@
 This work was funded by the Research Council of Norway (NJY FRIPRO grants 314189 and 353348).
-\newpage
 
@@
 You should be careful here. The H(div) functions do not have a
-well defined gradient (and in turn $\varepsilon$). However, for the derivations of
+well defined gradient (and in turn $\beps$). However, for the derivations of
 the continuous problem you don't need H(div). I would derive all the weak forms
@@
 \begin{equation}
-    \intG{\bsigperp\cdot\vv} = \intG{(\hat{\bsig}\cdot\nn)\nn\cdot\vv} = \intG{(\hat{\bsig}\cdot\nn)(\vv\cdot\nn)}.
+    \intG{\bsigperp\cdot\vv} = \intG{((\hat{\bsig}\cdot\nn)\nn)\cdot\vv} = \intG{(\hat{\bsig}\cdot\nn)(\vv\cdot\nn)}.
     \label{eq:boundary_integral_BC_normal}
@@
     \intO{\rho\pdifft{\uu}\cdot\vv}
-    + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)}
+    + \intO{2\mu\beps(\uu) : \beps(\vv)}
     - \intO{p\nabla\cdot\vv} = \intGc{\btau\cdot\vv}, \quad\forall\vv\in\VV.
@@
         &\intO{\rho\pdifft{\uu}\cdot\vv}
-        + &\intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)}
+        + &\intO{2\mu\beps(\uu) : \beps(\vv)}
         - &\intO{p\nabla\cdot\vv}
@@
     \begin{aligned}
-    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)} - \intO{p\nabla\cdot\vv} &-\intGp{\mu(\nabla\uu)^T\nn\cdot\vv} \\ &=\intGp{\Tilde{p}(t)(\vv\cdot\nn)}, \quad\forall\vv\in\VV.
+    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\beps(\uu) : \beps(\vv)} - \intO{p\nabla\cdot\vv} &-\intGp{\mu(\nabla\uu)^T\nn\cdot\vv} \\ &=\intGp{\Tilde{p}(t)(\vv\cdot\nn)}, \quad\forall\vv\in\VV.
     \end{aligned}
@@
     \mathcal{A}(\uu, \vv) &= \intO{\rho\pdifft{\uu}\cdot\vv}
-                          + \intO{2\mu\varepsilon(\uu) : \varepsilon(\vv)}
-                          -\intGp{\mu(\nabla\uu)^T\nn\cdot\vv}, \label{eq:stokes_bilinear_form}\\
+                          + \intO{2\mu\beps(\uu) : \beps(\vv)}
+                          -\intGp{\mu(\nabla\uu)^T\nn\cdot\vv},\label{eq:stokes_bilinear_form}\\
     \mathcal{B}(\uu, q) &= -\intO{q\nabla\cdot\uu}, \label{eq:stokes_skew_form}\\
@@
 We will outline the discretization of the weak
-formulation~\Cref{eq:abstract_weak_form_modelC,
-eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
+formulation~\Cref{eq:abstract_weak_form_modelC,eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
 of the Stokes equations for the baseline model. A similar approach can
@@
 in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the frequency of acquisition.
-Mean velocities $\overline{u}_x$~(\Cref{fig:meanx}) and $\overline{u}_y$~(\Cref{fig:meany}),
+Mean velocities $\overline{u}_x$~(\Crefpanels{fig:particle_tracking_data}{a}) and $\overline{u}_y$~(\Crefpanels{fig:particle_tracking_data}{b}),
 which serve as a quantification of particle drift, were calculated
@@
         \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
-        \subcaption{Mean velocities in the $x$ direction of the particles tracked.}\label{fig:meanx}
     \end{minipage}
@@
         \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
-        \subcaption{Mean velocities in the $y$ direction of the particles tracked.}\label{fig:meany}
     \end{minipage} 
-    \caption{Particle tracking data. The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
+    \caption{Particle tracking data. Mean velocities in the $x$ and $y$ directions of the particles tracked. The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
 \end{figure}
-\clearpage
-\bibliography{ref}{}
+
+% References
+\medskip
+
+% Use the following code if you wish to generate your bibliography with BibTeX;
+% replace the string "MSP-template" below with the name(s) of
+% the BibTeX data base(s) you want to use.
+% The resulting bibliography-output (the content of the .bbl file)
+% must be pasted back into this file before submission.
+% Please also include your BibTeX data base file(s) in your submission
+% so that we can re-run BibTeX if necessary.
+%
+\bibliographystyle{MSP}
+\bibliography{ref}
+
+\textbf{References}\\
+1	((Journal articles)) a) A. B. Author 1, C. D. Author 2, Adv. Mater. 2006, 18, 1; b) A. Author 1, B. Author 2, Adv. Funct. Mater. 2006, 16, 1.\\
+2	((Work accepted)) A. B. Author 1, C. D. Author 2, Macromol. Rapid Commun., DOI: 10.1002/marc.DOI.\\
+3	((Books)) H. R. Allcock, Introduction to Materials Chemistry, Wiley, Hoboken, NJ, USA 2008.\\
+4	((Edited books or proceedings volumes)) J. W. Grate, G. C. Frye, in Sensors Update, Vol. 2 (Eds: H. Baltes, W. Göpel, J. Hesse), Wiley-VCH, Weinheim, Germany 1996, Ch. 2.\\
+5	((Presentation at a conference, proceeding not published)) Author, presented at Abbrev. Conf. Title, Location of Conference, Date of Conference ((Month, Year)).\\
+6	((Thesis)) Author, Degree Thesis, University (location if not obvious), Month, Year.\\
+7	((Patents)) a) A. B. Author 1, C. D. Author 2 (Company), Country Patent Number, Year; b) W. Lehmann, H. Rinke (Bayer AG) Ger. 838217, 1952.\\
+8	((Website)) Author, Short description or title, URL, accessed: Month, Year.\\
+9	…((Please include all authors, and do not use “et al.”))\\
+
+% Table of contents entry should be 50 - 60 words long
+% Image should be 55 mm broad and 50 mm high or 110 mm broad and 20 mm high
+
+\begin{figure}
+\textbf{Table of Contents}\\
+\medskip
+  \includegraphics{toc-image.png}
+  \medskip
+  \caption*{ToC Entry}
+\end{figure}
+
 \end{document}

### 2025-02-18 paper/main.tex
reorder: methods appear after intro

@@
 particles within the brain ventricles.
+
+% Experimental section
+\section{Computational Methods}
+\subsection{Image-based computational geometries of zebrafish brain ventricles}
+To model flow and transport in zebrafish larval brain ventricles, we generated a
+3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
+injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
+From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
+The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
+The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
+maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
+At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
+the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
+Parts of the ventricular surfaces were marked to be lined with
+motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
+\begin{figure}%[hbt!]
+    \centering
+    \includegraphics[width=\linewidth]{graphics/figure1.png}
+    \caption{
+    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
+    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
+    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
+    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
+    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
+    anterior/posterior facets (blue).
+    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
+    cilia-only/no-cardiac flow model.
+    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
+    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
+    \textbf{g.} Streamlines simulated with the baseline flow model at
+    a time 25\% into the cardiac cycle. %t=0.112613 s
+    \textbf{h.} Streamlines simulated with the baseline flow model at
+    a time 50\% into the cardiac cycle. %t=0.225225 s
+    \textbf{i.} Streamlines simulated with the baseline flow model at
+    a time 75\% into the cardiac cycle. %t=0.315315 s
+    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
+    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
+    }
+    \label{fig:fig1}
+\end{figure}
+
+The morphology and geometry of the brain ventricles vary across zebrafish
+individuals, and under physiological and pathological conditions. 
+Motivated by an interest in how ventricular geometry impacts solute distribution,
+we also consider four variations in the geometry \fixme{(cross-sectional area
+reduction in parentheses):
+by shrinking the fore-mid brain connection (66 \%), 
+the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+% Cross-sectional areas of ducts normal to flow direction
+% Modified region       Original mesh        Deformed mesh
+% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
+% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
+% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
+
+\subsection{Computational CSF dynamics}
+The beating motion of the cilia generates CSF flow with steady rotational
+structures~\cite{Olstad2019CiliaryDevelopment}
+within the brain ventricles (\Crefpanels{fig:fig1}{a--c}).
+In addition, cardiac pulsations induce pulsatile CSF flow.
+We model this flow of CSF in the brain ventricles by the time-dependent,
+incompressible Stokes equations which read as follows.
+Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
+and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
+\begin{subequations}
+    \begin{align}
+      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
+      \quad \text{in } \Omega,\\
+      \nabla \cdot \uu &= 0
+      \quad  \text{in } \Omega,
+  \end{align}
+  \label{eq:stokes_eqs}% 
+\end{subequations}%
+where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
+and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
+Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
+Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
+and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
+of the CSF~\cite{Bloomfield1998EffectsFluid}.
+We introduce the tangential traction $\bsigpar$ as the
+tangential component of the traction $\hat{\bsig}=\bsig\nn$:
+\begin{equation*}
+    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
+\end{equation*}
+where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
+and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
+We consider three types of boundary conditions:
+(i) \emph{tangential traction} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
+the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
+and (iii) \emph{free slip} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
+Unless noted otherwise, the free-slip condition is applied on the
+boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
+
+To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
+we consider the following computational flow scenarios,
+each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
+\begin{itemize}
+    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
+    contributions both from the cilia forces and the cardiac pulsations.
+    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
+    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
+
+    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
+    cilia forces but no cardiac pulsations.
+    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
+    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
+
+    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
+    cardiac pulsations but no cilia forces.
+    Here, we set the tangential traction to zero on the cilia boundary
+    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
+    anterior/posterior boundary $\Gp$.  % Model II/Model B
+\end{itemize}
+
+\subsubsection{Cilia-driven flow}
+On the ciliated regions of the ventricle walls $\Gc$ (\Crefpanels{fig:fig1}{d}, magenta markers),
+we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
+of the cilia acting on the CSF.
+We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
+and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
+cilia region (see~\Cref{subsec:appendixA1}).
+Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
+model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
+The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
+$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
+In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
+We calibrated $\tau$ heuristically by comparing these experimental velocity values
+with the simulated, maximum velocity magnitude.
+
+\subsubsection{Flow induced by cardiac pulsations}
+To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
+$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
+boundary $\Gp$~(\Crefpanels{fig:fig1}{d}, blue markers).
+Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
+the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
+The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
+and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
+Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
+Particle tracking data of pulsatile motion was used to determine the contributions of the
+cardiac pulsations to the velocity magnitude,
+as compared to the effect of cilia motion on the flow (see~\Cref{sec:appC_particle_transport}).
+
+\subsection{Computational model of solute transport after photoconversion}
+We simulate transport of photoconverted proteins within the brain ventricles by
+modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
+time $t > 0$ by the advection-diffusion equation
+\begin{equation}
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
+    \label{eq:adv_diff_strong}
+\end{equation}
+where the total concentration flux $\mathbf{J}$ is assumed to consist of an advective and a diffusive flux:
+\begin{equation*}
+    \JJ = c\uu - D\nabla c .
+\end{equation*}
+Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\Cref{eq:stokes_eqs},
+and $D$ is the molecular diffusion coefficient of the solute.
+Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
+The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
+except at the anterior/posterior boundary $\Gamma_p$.
+At the anterior/posterior boundary, we permit the solute concentration to be advected into
+and out of the domain in a manner that ensures conservation of mass
+(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
+
+To computationally represent protein photoconversion in a region
+$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
+we prescribe a given time-dependent value to the solute concentration in this region. 
+Mimicking the experimental protocol, we consider the dorsal part of the
+diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
+\begin{equation}
+  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
+  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
+\label{eq:photoconversion_curve}
+\end{equation}
+The value $a=65$ was chosen to fit the fluorescence intensity curve
+observed in the physical photoconversion experiments.
+
+\subsection{Estimation of diffusion coefficients via the Stokes-Einstein relation}
+Motivated by an interest in molecules that are significant in neural development,
+we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
+used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
+To estimate the diffusion coefficients of these, when not
+available in the literature, we use the Stokes--Einstein relation:
+\begin{equation}
+    D = \frac{k_B T}{6\pi \mu R},
+    \label{eq:D_stokes_einstein}
+\end{equation}
+which is an expression for the diffusion coefficient of a spherical
+molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
+In~\Cref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
+$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
+solvent (in this case the CSF), and $R$ is the radius of the molecule.
+For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
+with $R=200$ nm. This radius covers the slowest diffusing exosomes,
+since the smaller exosomes would have diffusion coefficients similar to the other molecules.
+For STM-GFP, we estimated the diffusion coefficient by extrapolating
+the experimentally observed diffusion coefficient of
+GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+assuming that if $D$ scales with $1/R$ according to~\Cref{eq:D_stokes_einstein},
+$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
+The resulting diffusion coefficients used in the simulations
+are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
+
+%Implicit in this approach is the assumption that the proteins all have the same density.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{l|ccc}
+        \toprule
+        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
+        \midrule 
+        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
+        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
+        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
+        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{5.75e-11}$ & * \\
+        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
+        \bottomrule
+    \end{tabular}
+    \caption{Molecular mass and diffusion coefficients of simulated solutes.
+    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+    (*) The value was extrapolated based on the value of $D$ for
+    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+    assuming that $D$ scales with the cube root of the molecule mass.
+    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
+    \label{tab:diff_coeff_table}
+\end{table}
+
+\subsection{Quantities of interest}
+We calculate the mean solute concentrations
+\begin{equation}
+    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
+    \label{eq:c_mean_i}
+\end{equation}
+in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
+as functions of time, where $|\Omega_i|$ is the volume of
+the domain $\Omega_i$. The dynamics of ROI 1 follows directly
+from~\Cref{eq:photoconversion_curve}. In addition,
+we report time-to-threshold: the time $\hat{t}_i$ when
+the mean concentration $\cbar_i$ first exceed a threshold
+value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
+$\hat{c}_i=0.10$ for ROI 5--6.
+
+To evaluate the relative importance of advection and
+diffusion as transport mechanisms, we consider the Péclet number
+\begin{equation*}
+    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
+    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
+\end{equation*}
+Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
+and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
+Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
+respectively, and $D$ is the solute diffusion coefficient.
+In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
+ventricles geometry along the rostrocaudal ($x$-) axis.
+We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
+The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
+\begin{equation*}
+    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
+\end{equation*}
+and then averaging $\overline{u}$ in time over one cardiac cycle. To assess the assumption that the CSF flow is governed by the Stokes equations,
+we also compute the Reynolds number
+\begin{equation*}
+    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
+\end{equation*}
+with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
+
+%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
+\subsection{Numerical approximation of the Stokes equations}
+The Stokes equations~\Cref{eq:stokes_eqs} are discretized with a finite element method
+in space, while in time, we employ a first-order implicit Euler discretization.
+We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
+For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
+The BDM elements have degrees of freedom associated with integral moments of the
+velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems},
+thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
+We impose the boundary conditions for both the tangential traction $\bsigpar$ and
+the normal pressure $\Tilde{p}(t)$ weakly.
+For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
+The resulting total number of degrees of freedom at each time step is 943 820.
+\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
+discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
+To ensure stability of the scheme, continuity in tangential velocities on interior facets
+is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.}
+Since the divergence of the velocity is a subspace of the pressure space for this scheme,
+the divergence-free condition of the velocity is satisfied exactly on each
+element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
+
+\subsection{Numerical approximation of the advection-diffusion equation}
+The advection-diffusion equation~\Cref{eq:adv_diff_strong} is discretized
+with a first-order implicit Euler method in time, and a first-order,
+symmetric interior penalty discontinuous Galerkin (DG)
+method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
+conservation properties.
+To accurately approximate the solute concentrations even
+in the presence of strong advection (high Péclet numbers),
+we use an upwind scheme for the velocity when calculating the
+advective flux~\cite{Patankar2018NumericalFlow}.
+As for the flow equations, we use a timestep size of
+$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
+with a final time of simulation $T = 856$ s.
+A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
+
+\subsection{Solution strategy and software implementation}
+Owing to the one-way coupling between the velocity field $\uu$
+and the concentration $c$, the governing equations for the
+CSF flow and the concentration can be solved sequentially when modeling solute transport.
+For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
+the viscous forces dominate the inertial forces.
+In this case, we first solve the steady-state Stokes equations~\Cref{eq:stokes_eqs}
+for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
+the advection-diffusion equation~\Cref{eq:adv_diff_strong}.
+For the other flow scenarios, the Stokes equations are solved for one
+period of the pulsatile cardiac motion. The solution of this one period
+is then used periodically as input for the advection-diffusion equation.
+
+The numerical solution schemes for the Stokes equations and the
+advection-diffusion equation were implemented and solved numerically with
+DOLFINx~\cite{dolfinx2023preprint} with petsc4py~\cite{Dalcin2011ParallelPython}
+as linear algebra backend.
+A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
+linear systems resulting from the discretized Stokes equations.
+For the discretized advection-diffusion equation, we used an iterative
+linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
+preconditioning~\cite{Jacobi1845UeberGleichungen}. We discretize the time-dependent 
+diffusion equation (without advection) and use the assembled linear system matrix
+as the preconditioner matrix for the advection-diffusion problem.
+Numerical experiments verified the accuracy of the model implementation
+(\Cref{sec:appB_verification}). The simulation code is openly
+available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+
+%%------PHYSICAL EXPERIMENTS------%%
+\section{Experimental Methods}
+\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
+The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
+Norwegian Food Safety Authority (NFSA, Mattilsynet).
+The zebrafish were maintained in accordance with the guidelines set by the
+NFSA and the European Communities Council Directive.
+
+The larval and adult zebrafish were raised under standard husbandry
+conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
+The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
+14/10 hr light/dark cycle.
+From fertilization to 3 dpf, larvae were maintained in egg
+water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
+and subsequently transferred to artificial fish water (AFW)
+(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
+\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
+(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
+and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
+\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
+Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
+(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
+
+Wholemount in vivo live imaging and photoconversion
+experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
+\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
+adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
+or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
+The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
+
+For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
+fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
+tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
+To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
+and then centrifuged at 13000 rpm for 2 minutes.
+The supernatant containing gDNA was utilized for KASP assays-based analysis.
+The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
+used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
+For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
+\textmu L of assay mix; 1.86 \textmu L of RO water.
+
+\subsection{Generation of transgenic line to study CSF \fixme{and transport} dynamics} %\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}
+To generate a transgenic line expressing the photoconvertible protein Dendra2 in
+the brain ventricles, we fused the open reading frame (ORF)
+of the neuropeptide y (npy) signal peptide
+(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
+zebrafish codon optimized Dendra2 DNA sequence.
+The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
+3’ ends (GenScript Biotech) and inserted into the
+pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
+through restriction enzyme cloning (GenScript Biotech)
+to generate the 5xuas:Signal-Dendra2 plasmid DNA.
+
+A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
+was microinjected into one-cell stage embryos to generate the transgenic line,
+as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
+embryos were raised to adulthood (F0).
+Germline-transmitted founder zebrafish were identified by breeding with
+multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
+Dendra2 signals were screened and raised to adult zebrafish.
+
+\subsection{Wholemount zebrafish in vivo live time-lapse imaging and photoconversion of Dendra2}
+Two dpf larval zebrafish were anesthetized in 0.013\% MS222
+(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
+mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
+to obtain a lateral view of the brain ventricles. After the
+fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
+After solidification, AFW containing 0.013\% MS222 was added,
+and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
+and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
+at room temperature.
+
+The time-lapse images were acquired in a single plane, covering the
+telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
+with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
+of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
+The first 10 images were scanned without photoconversion to obtain a
+baseline value of fluorescence intensity, and the next 290 images were
+scanned while performing photoconversion.
+
+For photoconversion, ``Bleaching" and ``Region" in the ZEN software
+were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
+of the dorsoposterior diencephalic ventricle with 100\% laser power.
+The laser was illuminated in the area repeatedly between each scanning.
+After imaging, the fish health was checked and only data from healthy fish were analyzed.
+Data were collected and analyzed from three separate experiments,
+with a total of 8 controls and 6 mutants.
+
+\subsection{Photoconversion data analysis}
+All data analysis was performed in MATLAB and the codes are available in
+the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+
+Following import of the image data, the photoconverted channel
+was aligned to correct for drift in $x,y$ directions using previously
+developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
+Only stable recordings were further analyzed. 
+To increase the signal to noise ratio, the images were downsampled by
+a block average using a resampling factor of 6 (using the MATLAB function blockproc).
+The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
+$\Delta F$$)$ was calculated for each pixel at each time point of the data.
+Here, the value $F_0$ is the average fluorescence intensity for the
+baseline (the first 10 time-lapse images) acquired before photoconversion.
+
+To identify the time needed to pass a certain threshold value,
+$\Delta F$ values were first smoothened.
+The first timepoint when values surpassed the threshold was reported
+per pixel (in the downsampled images).
+A mask for the image was generated using the green (not photoconverted)
+channel and calculated on the block-averaged data based on the intensity
+being higher than 1.5x median intensity of all the frames.
+
+To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
+first drawn on the aligned and block-averaged time series.
+Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
+and ROIs 2--6 in different regions of the ventricular system.
+The pixel values of the fluorescence intensity within one ROI were
+averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
+To normalize the data with respect to photoconversion efficiency, the
+$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
+obtained for ROI 1 at the end of the experiment,
+so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
+zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
+We report these mean values together with a one-standard deviation error band.
+
+\subsection{Intraventricular injection of microbeads and particle tracking}
+To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c}, we carried out
+particle tracking in a larval zebrafish injected with fluorescent beads with a procedure described in detail in previous work~\cite{Olstad2019CiliaryDevelopment}.
+Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
+(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
+in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
+dissolved in artificial CSF. Artificial CSF composition was as follows:
+124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
+1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
+2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
+The needles used for the injections were pulled with a
+Sutter Instrument Co. Model P-2000 from thin-walled glass
+capillaries (1.00 mm; VWR) and cut open with a forceps.
+A volume of 1 nl of the solution was injected with a pressure injector
+(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
+The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
+
+Following injection, the zebrafish was directly placed under the confocal
+microscope and 1200 images were acquired at a frequency of 13.1 Hz.
+A single optical section was obtained. Particle tracking was done using
+TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
+and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
+The parameters for TrackMate were as follows.
+The DoG detector was used with the settings: threshold: 2.0, with
+median filtering; radius: 2.0, with subpixel localization.
+Next, the Simple LAP tracker was used with settings: max frame gap: 2;
+alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
+splitting max distance: 15.0; allow gap closing: true; allow track splitting:
+false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
+Only the particle tracks with at least 30 data points, while simultaneously
+covering a distance of at least 8.8 \textmu m, were plotted in~\Crefpanels{fig:fig1}{b, c}.
 
@@
 while most of the transport is governed by diffusion.
-
-% Experimental section
-
-\section{Computational and Experimental Methods}
-\subsection{Image-based computational geometries of zebrafish brain ventricles}
-To model flow and transport in zebrafish larval brain ventricles, we generated a
-3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
-injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
-The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
-The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
-maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
-At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
-the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
-Parts of the ventricular surfaces were marked to be lined with
-motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
-\begin{figure}%[hbt!]
-    \centering
-    \includegraphics[width=\linewidth]{graphics/figure1.png}
-    \caption{
-    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
-    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
-    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
-    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
-    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
-    anterior/posterior facets (blue).
-    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
-    cilia-only/no-cardiac flow model.
-    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
-    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
-    \textbf{g.} Streamlines simulated with the baseline flow model at
-    a time 25\% into the cardiac cycle. %t=0.112613 s
-    \textbf{h.} Streamlines simulated with the baseline flow model at
-    a time 50\% into the cardiac cycle. %t=0.225225 s
-    \textbf{i.} Streamlines simulated with the baseline flow model at
-    a time 75\% into the cardiac cycle. %t=0.315315 s
-    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
-    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
-    }
-    \label{fig:fig1}
-\end{figure}
-
-The morphology and geometry of the brain ventricles vary across zebrafish
-individuals, and under physiological and pathological conditions. 
-Motivated by an interest in how ventricular geometry impacts solute distribution,
-we also consider four variations in the geometry \fixme{(cross-sectional area
-reduction in parentheses):
-by shrinking the fore-mid brain connection (66 \%), 
-the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
-% Cross-sectional areas of ducts normal to flow direction
-% Modified region       Original mesh        Deformed mesh
-% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
-% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
-% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
-
-\subsection{Computational CSF dynamics}
-The beating motion of the cilia generates CSF flow with steady rotational
-structures~\cite{Olstad2019CiliaryDevelopment}
-within the brain ventricles (\Crefpanels{fig:fig1}{a--c}).
-In addition, cardiac pulsations induce pulsatile CSF flow.
-We model this flow of CSF in the brain ventricles by the time-dependent,
-incompressible Stokes equations which read as follows.
-Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
-and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
-\begin{subequations}
-    \begin{align}
-      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
-      \quad \text{in } \Omega,\\
-      \nabla \cdot \uu &= 0
-      \quad  \text{in } \Omega,
-  \end{align}
-  \label{eq:stokes_eqs}% 
-\end{subequations}%
-where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
-and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
-Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
-Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
-and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
-of the CSF~\cite{Bloomfield1998EffectsFluid}.
-We introduce the tangential traction $\bsigpar$ as the
-tangential component of the traction $\hat{\bsig}=\bsig\nn$:
-\begin{equation*}
-    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
-\end{equation*}
-where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
-and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
-We consider three types of boundary conditions:
-(i) \emph{tangential traction} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
-(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
-the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
-and (iii) \emph{free slip} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the
-boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
-
-To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
-we consider the following computational flow scenarios,
-each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
-\begin{itemize}
-    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
-    contributions both from the cilia forces and the cardiac pulsations.
-    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
-    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
-
-    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
-    cilia forces but no cardiac pulsations.
-    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
-    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
-
-    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
-    cardiac pulsations but no cilia forces.
-    Here, we set the tangential traction to zero on the cilia boundary
-    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
-    anterior/posterior boundary $\Gp$.  % Model II/Model B
-\end{itemize}
-
-\subsection{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Crefpanels{fig:fig1}{d}, magenta markers),
-we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
-of the cilia acting on the CSF.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
-and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
-cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
-model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
-The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
-$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
-In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
-We calibrated $\tau$ heuristically by comparing these experimental velocity values
-with the simulated, maximum velocity magnitude.
-
-\subsection{Flow induced by cardiac pulsations}
-To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
-$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
-boundary $\Gp$~(\Crefpanels{fig:fig1}{d}, blue markers).
-Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
-the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
-The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
-and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
-Particle tracking data of pulsatile motion was used to determine the contributions of the
-cardiac pulsations to the velocity magnitude,
-as compared to the effect of cilia motion on the flow (see~\Cref{sec:appC_particle_transport}).
-
-\subsection{Computational model of solute transport after photoconversion}
-We simulate transport of photoconverted proteins within the brain ventricles by
-modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
-time $t > 0$ by the advection-diffusion equation
-\begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
-    \label{eq:adv_diff_strong}
-\end{equation}
-where the total concentration flux $\mathbf{J}$ is assumed to consist of an advective and a diffusive flux:
-\begin{equation*}
-    \JJ = c\uu - D\nabla c .
-\end{equation*}
-Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\Cref{eq:stokes_eqs},
-and $D$ is the molecular diffusion coefficient of the solute.
-Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
-The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
-except at the anterior/posterior boundary $\Gamma_p$.
-At the anterior/posterior boundary, we permit the solute concentration to be advected into
-and out of the domain in a manner that ensures conservation of mass
-(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
-
-To computationally represent protein photoconversion in a region
-$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
-we prescribe a given time-dependent value to the solute concentration in this region. 
-Mimicking the experimental protocol, we consider the dorsal part of the
-diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
-\begin{equation}
-  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
-  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
-\label{eq:photoconversion_curve}
-\end{equation}
-The value $a=65$ was chosen to fit the fluorescence intensity curve
-observed in the physical photoconversion experiments.
-
-\subsection{Estimation of diffusion coefficients via the Stokes-Einstein relation}
-Motivated by an interest in molecules that are significant in neural development,
-we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
-used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
-Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
-To estimate the diffusion coefficients of these, when not
-available in the literature, we use the Stokes--Einstein relation:
-\begin{equation}
-    D = \frac{k_B T}{6\pi \mu R},
-    \label{eq:D_stokes_einstein}
-\end{equation}
-which is an expression for the diffusion coefficient of a spherical
-molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
-In~\Cref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
-$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
-solvent (in this case the CSF), and $R$ is the radius of the molecule.
-For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
-with $R=200$ nm. This radius covers the slowest diffusing exosomes,
-since the smaller exosomes would have diffusion coefficients similar to the other molecules.
-For STM-GFP, we estimated the diffusion coefficient by extrapolating
-the experimentally observed diffusion coefficient of
-GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-assuming that if $D$ scales with $1/R$ according to~\Cref{eq:D_stokes_einstein},
-$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations
-are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
-
-%Implicit in this approach is the assumption that the proteins all have the same density.
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{l|ccc}
-        \toprule
-        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
-        \midrule 
-        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
-        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
-        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{5.75e-11}$ & * \\
-        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
-        \bottomrule
-    \end{tabular}
-    \caption{Molecular mass and diffusion coefficients of simulated solutes.
-    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-    (*) The value was extrapolated based on the value of $D$ for
-    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-    assuming that $D$ scales with the cube root of the molecule mass.
-    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
-    \label{tab:diff_coeff_table}
-\end{table}
-
-\subsection{Quantities of interest}
-We calculate the mean solute concentrations
-\begin{equation}
-    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
-    \label{eq:c_mean_i}
-\end{equation}
-in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
-as functions of time, where $|\Omega_i|$ is the volume of
-the domain $\Omega_i$. The dynamics of ROI 1 follows directly
-from~\Cref{eq:photoconversion_curve}. In addition,
-we report time-to-threshold: the time $\hat{t}_i$ when
-the mean concentration $\cbar_i$ first exceed a threshold
-value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
-$\hat{c}_i=0.10$ for ROI 5--6.
-
-To evaluate the relative importance of advection and
-diffusion as transport mechanisms, we consider the Péclet number
-\begin{equation*}
-    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
-    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
-\end{equation*}
-Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
-and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
-Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
-respectively, and $D$ is the solute diffusion coefficient.
-In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
-ventricles geometry along the rostrocaudal ($x$-) axis.
-We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
-The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
-\begin{equation*}
-    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
-\end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle. To assess the assumption that the CSF flow is governed by the Stokes equations,
-we also compute the Reynolds number
-\begin{equation*}
-    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
-\end{equation*}
-with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
-
-%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
-\subsection{Numerical approximation of the Stokes equations}
-
-The Stokes equations~\Cref{eq:stokes_eqs} are discretized with a finite element method
-in space, while in time, we employ a first-order implicit Euler discretization.
-We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
-For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
-The BDM elements have degrees of freedom associated with integral moments of the
-velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems},
-thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
-We impose the boundary conditions for both the tangential traction $\bsigpar$ and
-the normal pressure $\Tilde{p}(t)$ weakly.
-For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
-The resulting total number of degrees of freedom at each time step is 943 820.
-\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
-discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-To ensure stability of the scheme, continuity in tangential velocities on interior facets
-is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.}
-Since the divergence of the velocity is a subspace of the pressure space for this scheme,
-the divergence-free condition of the velocity is satisfied exactly on each
-element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
-
-\subsection{Numerical approximation of the advection-diffusion equation}
-The advection-diffusion equation~\Cref{eq:adv_diff_strong} is discretized
-with a first-order implicit Euler method in time, and a first-order,
-symmetric interior penalty discontinuous Galerkin (DG)
-method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
-conservation properties.
-To accurately approximate the solute concentrations even
-in the presence of strong advection (high Péclet numbers),
-we use an upwind scheme for the velocity when calculating the
-advective flux~\cite{Patankar2018NumericalFlow}.
-As for the flow equations, we use a timestep size of
-$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
-with a final time of simulation $T = 856$ s.
-A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
-
-\subsection{Solution strategy and software implementation}
-Owing to the one-way coupling between the velocity field $\uu$
-and the concentration $c$, the governing equations for the
-CSF flow and the concentration can be solved sequentially when modeling solute transport.
-For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
-the viscous forces dominate the inertial forces.
-In this case, we first solve the steady-state Stokes equations~\Cref{eq:stokes_eqs}
-for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
-the advection-diffusion equation~\Cref{eq:adv_diff_strong}.
-For the other flow scenarios, the Stokes equations are solved for one
-period of the pulsatile cardiac motion. The solution of this one period
-is then used periodically as input for the advection-diffusion equation.
-
-The numerical solution schemes for the Stokes equations and the
-advection-diffusion equation were implemented and solved numerically with DOLFINx~\cite{dolfinx2023preprint},
-the Python interface of the finite element software
-FEniCSx, with
-petsc4py~\cite{Dalcin2011ParallelPython} as linear algebra backend.
-A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
-linear systems resulting from the discretized Stokes equations.
-For the discretized advection-diffusion equation, we used an iterative
-linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
-preconditioning~\cite{Jacobi1845UeberGleichungen}.
-Numerical experiments verified the accuracy of the model implementation
-(\Cref{sec:appB_verification}). The simulation code is openly
-available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-%%------PHYSICAL EXPERIMENTS------%%
-\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
-The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
-Norwegian Food Safety Authority (NFSA, Mattilsynet).
-The zebrafish were maintained in accordance with the guidelines set by the
-NFSA and the European Communities Council Directive.
-
-The larval and adult zebrafish were raised under standard husbandry
-conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
-The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
-14/10 hr light/dark cycle.
-From fertilization to 3 dpf, larvae were maintained in egg
-water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
-and subsequently transferred to artificial fish water (AFW)
-(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
-\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
-(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
-and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
-\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
-Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
-(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
-
-Wholemount in vivo live imaging and photoconversion
-experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
-\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
-adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
-Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
-or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
-The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
-
-For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
-fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
-tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
-To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
-and then centrifuged at 13000 rpm for 2 minutes.
-The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
-used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
-\textmu L of assay mix; 1.86 \textmu L of RO water.
-
-\subsection{Generation of transgenic line to study CSF \fixme{and transport} dynamics} %\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}
-To generate a transgenic line expressing the photoconvertible protein Dendra2 in
-the brain ventricles, we fused the open reading frame (ORF)
-of the neuropeptide y (npy) signal peptide
-(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
-zebrafish codon optimized Dendra2 DNA sequence.
-The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
-3’ ends (GenScript Biotech) and inserted into the
-pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
-through restriction enzyme cloning (GenScript Biotech)
-to generate the 5xuas:Signal-Dendra2 plasmid DNA..
-
-A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
-was microinjected into one-cell stage embryos to generate the transgenic line,
-as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
-embryos were raised to adulthood (F0).
-Germline-transmitted founder zebrafish were identified by breeding with
-multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
-Dendra2 signals were screened and raised to adult zebrafish.
-
-\subsection{Wholemount zebrafish in vivo live time-lapse imaging and photoconversion of Dendra2}
-Two dpf larval zebrafish were anesthetized in 0.013\% MS222
-(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
-mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
-to obtain a lateral view of the brain ventricles. After the
-fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
-After solidification, AFW containing 0.013\% MS222 was added,
-and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
-and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
-at room temperature.
-
-The time-lapse images were acquired in a single plane, covering the
-telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
-with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
-of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
-The first 10 images were scanned without photoconversion to obtain a
-baseline value of fluorescence intensity, and the next 290 images were
-scanned while performing photoconversion.
-
-For photoconversion, ``Bleaching" and ``Region" in the ZEN software
-were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
-of the dorsoposterior diencephalic ventricle with 100\% laser power.
-The laser was illuminated in the area repeatedly between each scanning.
-After imaging, the fish health was checked and only data from healthy fish were analyzed.
-Data were collected and analyzed from three separate experiments,
-with a total of 8 controls and 6 mutants.
-
-\subsection{Photoconversion data analysis}
-All data analysis was performed in MATLAB and the codes are available in
-the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-Following import of the image data, the photoconverted channel
-was aligned to correct for drift in $x,y$ directions using previously
-developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
-Only stable recordings were further analyzed. 
-To increase the signal to noise ratio, the images were downsampled by
-a block average using a resampling factor of 6 (using the MATLAB function blockproc).
-The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
-$\Delta F$$)$ was calculated for each pixel at each time point of the data.
-Here, the value $F_0$ is the average fluorescence intensity for the
-baseline (the first 10 time-lapse images) acquired before photoconversion.
-
-To identify the time needed to pass a certain threshold value,
-$\Delta F$ values were first smoothened.
-The first timepoint when values surpassed the threshold was reported
-per pixel (in the downsampled images).
-A mask for the image was generated using the green (not photoconverted)
-channel and calculated on the block-averaged data based on the intensity
-being higher than 1.5x median intensity of all the frames.
-
-To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
-first drawn on the aligned and block-averaged time series.
-Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
-and ROIs 2--6 in different regions of the ventricular system.
-The pixel values of the fluorescence intensity within one ROI were
-averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
-To normalize the data with respect to photoconversion efficiency, the
-$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
-obtained for ROI 1 at the end of the experiment,
-so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
-zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
-We report these mean values together with a one-standard deviation error band.
-
-\subsection{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c}, we carried out
-particle tracking in a larval zebrafish injected with fluorescent beads with a procedure described in detail in previous work~\cite{Olstad2019CiliaryDevelopment}.
-Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
-(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
-in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
-dissolved in artificial CSF. Artificial CSF composition was as follows:
-124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
-1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
-2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
-The needles used for the injections were pulled with a
-Sutter Instrument Co. Model P-2000 from thin-walled glass
-capillaries (1.00 mm; VWR) and cut open with a forceps.
-A volume of 1 nl of the solution was injected with a pressure injector
-(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
-The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
-
-Following injection, the zebrafish was directly placed under the confocal
-microscope and 1200 images were acquired at a frequency of 13.1 Hz.
-A single optical section was obtained. Particle tracking was done using
-TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
-and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
-The parameters for TrackMate were as follows.
-The DoG detector was used with the settings: threshold: 2.0, with
-median filtering; radius: 2.0, with subpixel localization.
-Next, the Simple LAP tracker was used with settings: max frame gap: 2;
-alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
-splitting max distance: 15.0; allow gap closing: true; allow track splitting:
-false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
-Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 \textmu m, were plotted in~\Crefpanels{fig:fig1}{b, c}.
 

### 2025-02-22 paper/main.tex
updates discussion

@@
 
-\title{Advection Versus Diffusion in Intraventricular Transport}
+\title{The Role of Advection Versus Diffusion in Intraventricular Transport}
 
@@
 
-% Author: Please give full first and last names for authors and include * after the name of all corresponding authors
+% Author: Please give full first and last names for authors and
+% include * after the name of all corresponding authors
 
@@
 
-% Affiliations: Please provide adacemic titles (Prof. or Dr.) for all authors where applicable, and include an institutional email address for all corresponding authors
+% Affiliations: Please provide adacemic titles (Prof. or Dr.) for all authors where applicable,
+% and include an institutional email address for all corresponding authors
 \begin{affiliations}
@@
 Email Address: hherlyng@simula.no
-
-Dr.~M.~E.~Rognes \\
+\\
+Dr.~M.~E.~Rognes\\
 K.~G.~Jebsen Center for Brain Fluid Research, Oslo, Norway
@@
 
-\keywords{cerebrospinal fluid, brain ventricles, fluid flow, transport}
+\keywords{cerebrospinal fluid, brain ventricles, transport, finite element method}
 
@@
 The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
-The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
+The standard mesh consisted of 132 134 tetrahedral cells and had a
 maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
 At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
-the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
+the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
+which are connected by interventricular ducts. 
 Parts of the ventricular surfaces were marked to be lined with
@@
 The morphology and geometry of the brain ventricles vary across zebrafish
-individuals, and under physiological and pathological conditions. 
+individuals, and under physiological and pathological conditions~\cite{Olstad2019CiliaryDevelopment}. 
 Motivated by an interest in how ventricular geometry impacts solute distribution,
-we also consider four variations in the geometry \fixme{(cross-sectional area
+we also consider four variations in the geometry (cross-sectional area
 reduction in parentheses):
 by shrinking the fore-mid brain connection (66 \%), 
-the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.} 
+the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.
 We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
@@
 (i) \emph{tangential traction} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ with a force $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+$\uu \cdot \nn = 0$ with a stress $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
 (ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
@@
 and (iii) \emph{free slip} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ and no tangential forces $\bsigpar = {\bf 0}$).
+$\uu \cdot \nn = 0$ and no tangential traction $\bsigpar = {\bf 0}$).
 Unless noted otherwise, the free-slip condition is applied on the
@@
 \end{equation}
-where the total concentration flux $\mathbf{J}$ is assumed to consist of an advective and a diffusive flux:
+where the total concentration flux $\JJ$ is assumed to consist of an advective and a diffusive flux:
 \begin{equation*}
@@
 To estimate the diffusion coefficients of these, when not
-available in the literature, we use the Stokes--Einstein relation:
+available in the literature, we use the Stokes--Einstein relation
 \begin{equation}
@@
 with $R=200$ nm. This radius covers the slowest diffusing exosomes,
-since the smaller exosomes would have diffusion coefficients similar to the other molecules.
+a choice made because smaller exosomes would have diffusion coefficients
+similar to the other molecules.
 For STM-GFP, we estimated the diffusion coefficient by extrapolating
@@
     \centering
+    \caption{Molecular mass and diffusion coefficients of simulated solutes.
+    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+    (*) The value was extrapolated based on the value of $D$ for
+    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+    assuming that $D$ scales with the cube root of the molecule mass.
+    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
+    \label{tab:diff_coeff_table}
     \begin{tabular}{l|ccc}
@@
     \end{tabular}
-    \caption{Molecular mass and diffusion coefficients of simulated solutes.
-    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-    (*) The value was extrapolated based on the value of $D$ for
-    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-    assuming that $D$ scales with the cube root of the molecule mass.
-    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
-    \label{tab:diff_coeff_table}
 \end{table}
@@
 \end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle. To assess the assumption that the CSF flow is governed by the Stokes equations,
+and then averaging $\overline{u}$ in time over one cardiac cycle.
+To assess the assumption that the CSF flow is governed by the Stokes equations,
 we also compute the Reynolds number
@@
 The resulting total number of degrees of freedom at each time step is 943 820.
-\fixme{The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
+The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
 discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
 To ensure stability of the scheme, continuity in tangential velocities on interior facets
-is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.}
+is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.
 Since the divergence of the velocity is a subspace of the pressure space for this scheme,
 the divergence-free condition of the velocity is satisfied exactly on each
-element~\cite{Boffi2008FiniteProblem}, ensuring mass conservation.
+element, ensuring mass conservation.~\cite{Boffi2008FiniteProblem}
 
@@
 
-\subsection{Generation of transgenic line to study CSF \fixme{and transport} dynamics} %\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}
+\subsection{Generation of transgenic line to study CSF and transport dynamics} 
 To generate a transgenic line expressing the photoconvertible protein Dendra2 in
@@
 \section{Discussion}
-We have presented a computational model of CSF flow and solute transport within the brain ventricles.
-In this study, we used the larval zebrafish brain ventricles since its geometry,
+In this study, we have presented a computational model of CSF flow and solute transport within the brain ventricles.
+We used the larval zebrafish brain ventricles since its geometry,
 flow components and kinetics are well described, thereby allowing us to validate
-our simulation experimentally. Nevertheless, our simulations can be implemented in
-other systems in the future when their flow parameters are comprehensively resolved.  
-By imposing tangential traction and normal pressure on the CSF flow, we were able to reproduce
-flow fields with similar features as observed experimentally, consisting of vortex-structured flow,
+our simulation experimentally. Nevertheless, our computational framework can be adapted to and implemented in
+other ventricular systems in the future, given that the flow parameters of such systems
+are comprehensively resolved. By imposing tangential traction and normal pressure
+on the CSF flow, we were able to reproduce flow fields with similar features
+as observed experimentally. The prominent flow features were vortex-structured flow,
 mediated by cilia, and pulsatile flow, mediated by the cardiac cycle.
@@
 Using the simulated CSF flow, we modeled solute transport by an advection-diffusion equation.
-These results compared well with experimental data performed in vivo in zebrafish.
-Then, by using both a computational model and zebrafish mutants with paralyzed cilia,
+The transport results compared well with experimental data performed in vivo in zebrafish.
+Then, by using a computational model as well as zebrafish mutants with paralyzed cilia,
 we identified that even though advection by cilia is dominant,
@@
 affect solute distribution. Altogether, we present not only new findings on the role of
-diffusion and advection, but also provide a novel framework to
+diffusion and advection in intraventriuclar transport, but also provide a novel framework to
 study CSF flow and transport in complex geometries.
@@
 Differences between experiments and simulations may relate to
-ventricular size, as we showed that modifying the duct volumes impacts
-solute distribution and the geometry used for the model was larger than in experiments.
-Alternatively, it may relate to the way we defined the photoconversion site (ROI 1)
-in the simulations, since the volume of the photoconversion region determines
-the total amount of solute, and thereby the rate of transport. Another source
+ventricular size, as we showed that modifying the geometry of the interventricular ducts
+impacts solute distribution, and the geometry used for the computational model was larger
+than geometries used in experiments. Alternatively, dissimilarities in results may relate
+to the way we defined the photoconversion site (ROI 1) in the simulations,
+since the volume of the photoconversion region determines
+the total amount of solute and thereby the rate of transport. Another source
 of discrepancy may relate to the permeability of the ventricular wall,
 which we have ignored in our simulation. Reports have shown that the
-neuroepithelium lining the walls of brain ventricles in 24h old zebrafish
+neuroepithelium lining the walls of brain ventricles in 24 hour old zebrafish
 is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
@@
 thus under this reported limit, one could assume that Dendra2 may
-leak out of the brain ventricles and render the dynamics slower.
-
-Nevertheless, our results convincingly show that intraventricular transport of proteins
-depends on a balance of advection and diffusion. While advection is the strongest transport
-mechanism on a global scale for Dendra2 (global Péclet number 7.4), diffusion is balancing out
+leak out of the brain ventricles over the time spans we consider
+and render the dynamics slower.
+
+Nevertheless, our results convincingly show that
+intraventricular transport of proteins depends on a balance of advection and diffusion.
+While advection is the strongest transport mechanism on a global scale for
+Dendra2 (global Péclet number 7.4), diffusion is balancing out
 advection especially for shorter distances and for regions devoid of motile cilia activity.
@@
 Indeed, there was essentially zero solute in the posterior ventricle at the
-final simulation time (around 850 s), where transport is largely driven by diffusion.
+final simulation time (around 850 s), a ventricle where transport is largely driven
+by diffusion due to the absence of motile cilia.
 For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance
 $L=200$ \textmu m from the middle to the posterior ventricle is approximately 24500 s.
-Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen
-on a timescale of the order of $t_a=L/\overline{U}=141$ s. Comparing this with the minuscule values of
-$\cbar_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection
+Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same
+distance would happen on a timescale of the order of $t_a=L/\overline{U}=141$ s.
+Comparing this with the minuscule values of $\cbar_6$ after simulating transport
+with $D_1$ for 850 s, one can conclude that if advection
 played a role in transporting solute from the photoconversion site in the middle ventricle
@@
 
-\subsection{Impact of cilia \fixme{properties} and ventricular geometry}
-To gain further insights into how CSF distribution depends on cilia \fixme{properties (@Nathalie: do we really
-investigate properties? Rather location or population?)} and geometries,
-we manipulated certain parameters in our models. First, we paralyzed cilia in specific regions of
-our model (\Cref{fig:fig5}). We identified that the cilia in the
-dorsal middle ventricle contribute the most to solute distribution, which aligns well with the fact
-that these cilia generate the strongest flow field in vivo~\cite{Olstad2019CiliaryDevelopment} and in our model.
-In contrast, removing the ventral cilia in the middle ventricle did not greatly impact flow dynamics.
-However, it lead to reduced transport towards the posterior ventricle,
-and increased transport towards the anterior ventricle, as the ventral cilia help induce
-flow towards the posterior ventricles. Removing the cilia in the anterior ventricle did not affect the transport.
-
-Next, we modified the ventricular geometry and identified varying impact on transport.
-Notably, shrinking ducts reduced movement between the ventricles, while shrinking the middle ventricle
-reduced diffusive transport upstream of the flow field (ROI 4).
+\subsection{Impact of cilia motility and ventricular morphology}
+To gain further insights into how CSF flow and intraventricular transport depend on cilia
+motility and ventricular morphology, we manipulated certain
+parameters in our models. First, we paralyzed cilia in specific regions of
+our model. We identified that the cilia in the dorsal middle ventricle contribute
+the most to solute distribution, which aligns well with the fact
+that these cilia generate the strongest flow field in vivo~\cite{Olstad2019CiliaryDevelopment}
+and in our model. In contrast, removing the ventral cilia in the middle ventricle
+did not greatly impact flow dynamics, despite these cilia contributing a third of
+the total force exerted by the cilia. However, removing ventral cilia in the middle ventricle
+lead to reduced transport towards the posterior ventricle,
+meanwhile increasing transport towards the anterior ventricle,
+as the ventral cilia help induce flow towards the posterior ventricle.
+Removing the cilia in the anterior ventricle did not affect the transport.
+
+Next, we modified the ventricular geometry and identified the impact on transport.
+Notably, shrinking ducts reduced interventricular solute movement, while shrinking
+the middle ventricle reduced diffusive transport upstream of the flow field.
 We previously identified large inter-individual variation in ventricular size and
@@
 development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
-Our results suggest that these two parameters may well co-vary and explain the variation.
-
-Altogether, our model is flexible and thereby allows in silico testing of
-further hypotheses on the effects of ciliated lineages and ventricular morphology on
-CSF flow and intraventricular transport.
-We trust that it will be useful as a basis for future analysis of
-CSF dynamics in more complex geometries \fixme{and other animal species and humans}.
+Our results suggest that these two parameters, CSF velocities and ventricular size,
+may well co-vary and explain the variation in the two.
+
+These simulation studies demonstrate that our model is flexible and allows in silico
+testing of further hypotheses on the effects of ciliated
+lineages and ventricular morphology on CSF flow and intraventricular transport.
+We envision that our framework will be useful as a basis for future analyses of
+CSF dynamics in more complex geometries and also other animal species and humans.
 
@@
 refinement near the ciliated boundaries in the case that a
-body force were to be applied in a $\sim$ 5 \textmu m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.
+body force were to be applied in a cilia layer of depth around
+5 \textmu m~\cite{Salman2022ComputationalEmbryo}.
 
@@
 is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an
-experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the values $D_2$ and
-$D_1$ were extrapolated based on experimental data~\cite{Swaminathan1997PhotobleachingDiffusion,
-Potma2001ReducedCells, Mahmood2023ExosomeTemperature} using the Stokes-Einstein
-relation~(\Cref{eq:D_stokes_einstein})~\cite{Einstein1905UberTeilchen}.
-This extrapolation assumes the diffusing substance is of spherical shape, which proteins are not,
-and the relation does not necessarily hold in CSF. Consequently, there is uncertainty in the values used.
+experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the Stokes-Einstein
+relation~(\Cref{eq:D_stokes_einstein})~\cite{Einstein1905UberTeilchen} was used to extrapolate
+the value of $D_2$ and estimate the value of $D_1$, based on experimental
+data~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells,
+Mahmood2023ExosomeTemperature}. The Stokes-Einstein relation assumes the diffusing
+substance is of spherical shape, which proteins are not, and the relation does not
+necessarily hold in CSF. Moreover, the extrapolation implies the assumption that
+the two substances (the one for which we determine $D$ and the one we extrapolate from)
+have equal densities. Consequently, there is uncertainty in the diffusion coefficient values used.
 We note that Sadovsky~\emph{et al.}~\cite{GuraSadovsky2017MeasurementExpansion} reported that
-Dendra2 satisfies the Stokes-Einstein in the solution they used, a solution which had similar viscosity
-to water. We used CSF density and viscosity values measured in humans~\cite{Bloomfield1998EffectsFluid},
+Dendra2 satisfies the Stokes-Einstein in the solution they used,
+a solution which had similar viscosity
+to water. We used CSF density and viscosity values measured in
+humans~\cite{Bloomfield1998EffectsFluid},
 and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances,
@@
 coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
-Considering the diffusion coefficients $D_1$ and $D_2$ both smaller than $D_3$ in our transport analysis
-provides information about how the simulation results of Dendra2 transport would be altered if the
-diffusion coefficient $D_3$ is overestimated. In the case that $D_3$ is underestimated, we assume the
-results would follow the same trend as the differences between results for $D_2$ and $D_3$: diffusion becomes
-more important, and is almost balancing advective transport for $D_3$. Thus for a higher diffusion coefficient,
-we would see transport that is mostly explained by diffusive behavior.
+Considering the diffusion coefficients $D_1$ and $D_2$ (both smaller
+than $D_3$) in our transport analysis provides information about how the simulation
+results of Dendra2 transport would be altered if the
+diffusion coefficient $D_3$ is overestimated. In the case that $D_3$ is
+underestimated, we assume the
+results would follow the same trend as the differences between results for
+$D_2$ and $D_3$: diffusion becomes
+more important, and is almost balancing advective transport for $D_3$. 
+Thus for a higher diffusion coefficient, we would see transport that is
+mostly explained by diffusive behavior.
 
@@
 paramount to attain a stable discretization of the advection-diffusion equation
-in advection-dominated regions. Preliminary attempts using Taylor-Hood elements
-proved hard to achieve stable transport results with a reasonable computational mesh size.
-Stability either required excessive mesh refinement and/or problem-specific tuning of
+in advection-dominated regions. Using conventional Taylor-Hood elements for the Stokes equations,
+stability of the advection-diffusion discretization either
+required excessive mesh refinement and/or problem-specific tuning of
 hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization
-method~\cite{Franca1992StabilizedModel}. Probing numerical values of the divergence of
-the velocity when using Taylor-Hood elements revealed that, on the standard computational
-mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was in the order of $10^{-6}$, while the
+method~\cite{Franca1992StabilizedModel} instead of the current DG method.
+Probing numerical values of the divergence of
+the velocity when using Taylor-Hood elements for the fluid equations revealed that,
+on the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was
+in the order of $10^{-6}$, while the
 maximum value of the divergence of the velocity was of order unity. This is a result
-of the fact that incompressibility is only achieved in a distributional sense when
+of the fact that incompressibility is only achieved in a (global) weak sense when
 employing Taylor-Hood elements. On a refined mesh with roughly six times as many
@@
 $\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still
-of the same orders as reported for the standard mesh. This may lead to the
+of order unity. This may lead to the
 hyperbolic advective term in the advection-diffusion equation accumulating errors
@@
 Our work has studied CSF flow and solute distribution
-in a relatively small and simple model, which is devoid of
+in a relatively small and simple brain model, which is devoid of
 active CSF secretion and CSF absorption. Even though there is
 a clear conservation of the ventricular system across vertebrates,
-there are also important considerations to take, which include
-ventricular size and geometries, properties of ciliated cells,
+there are also important considerations to take. These include (but are not limitied to)
+ventricular size and morphology, properties of ciliated cells,
 animal posture, and magnitude of velocities. For instance, a large
@@
 if based solely on diffusion. Besides, the presence of multiple cilia
-instead of a single cilium per cell, as described in mammalian ependymal cells,
-will generate much stronger velocities. Hence advection may be more
-dominant in those situations. However, in large brains, cilia beating will
-only contribute to a restricted flow at the very close proximity of the ventricular walls,
+instead of a single cilium per cell -- the former can be found in
+mammalian ependymal cells -- will generate much stronger velocities.
+Hence advection may be more dominant in those situations.
+However, in large brains such as the human brain, cilia beating will
+only contribute to flow in localized regions of very high proximity to the ventricular walls,
 while blood vessel pulsations, respiration and CSF secretion will generate a
@@
 generated by ciliary motion is of the scale of the geometry, and thus not
-only contributes to near-wall flow dynamics, but the whole ventricular system.
-As of now, motile cilia deficiency has been associated with altered brain function
+only contributes to near-wall flow dynamics, but flow in the entire ventricular system.
+To date, motile-cilia deficiency has been associated with altered brain function
 in the zebrafish and ventricular enlargement in zebrafish, rodents and humans.
@@
 We are also confident that our model can be adjusted and implemented to fit
-microscopic and macroscopic parameters once acquired for larger brains.
+microscopic and macroscopic parameters for larger brains, once these parameters are acquired.
 
@@
     and investigating how the arising flow compares with pulsatile flow observed in experiments
+    \item FSI: CSF flow coupled to 1D/2D/3D cilia structures.
 \end{itemize}
@@
 \medskip
-\textbf{Supporting Information} \par %Please delete the Suppporting Information statement if it is not applicable.
-Please supply Supporting Information in another file.
-Supporting information should not be provided in .tex format
+\textbf{Data Availability Statement} \par
+\fixme{TO DO}.
+
+\medskip
+\textbf{Declaration of No Competing Interest} \par
+\fixme{TO DO}.
+
+\medskip
+\textbf{Supporting Information} \par %Please delete the Suppporting Information statement
+%if it is not applicable. Please supply Supporting Information in another file.
+%Supporting information should not be provided in .tex format
 Supporting Information is available from the Wiley Online Library or from the author.
@@
 Halvor Herlyng acknowledges support from the national infrastructure for computational
-science in Norway, Sigma2, via grant \#NN8049K. Thanks are extended to J\o rgen Dokken
-for valuable model implementation discussions.
+science in Norway, Sigma2, via grant \#NN8049K.
 This work was funded by the Research Council of Norway (NJY FRIPRO grants 314189 and 353348).
+Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
 

### 2025-02-23 paper/main.tex
edit introduction and discussion

@@
 
-\keywords{cerebrospinal fluid, brain ventricles, transport, finite element method}
+\keywords{cerebrospinal fluid, brain ventricles, transport, finite element methods}
 
@@
 Brain development and function depend on numerous regulatory processes,
-including interactions with cerebrospinal fluid
+including the flow of cerebrospinal fluid
 (CSF). CSF is a clear liquid produced by the choroid plexus
-that flows through the ventricular system and subarachnoid space.
-By delivering growth factors, nutrients, neurotransmitters and metabolites
+and the fluid flows through the ventricular system and subarachnoid space.
+By transporting growth factors, nutrients, neurotransmitters and metabolites
 and removing waste products, CSF regulates brain development and homeostasis.
-Disturbances of CSF circulation can lead to brain disorders, such as
+Disturbance of the CSF circulation can lead to brain disorders, such as
 hydrocephalus where accumulation of CSF often requires emergency surgical treatment.
 
-CSF movement occurs through multiple physiological processes,
-including the action of motile cilia on the ventricular walls,
+Motion of CSF occurs through multiple physiological processes,
+including the beating motion of motile cilia lining the ventricular walls,
 CSF secretion by the choroid plexus, and pressure gradients generated
@@
 pattern to mediate fluid flow. Due to their microscopic size, ranging
-from 6 to 15 microns, they contribute to flow primarily at the surface
-of the brain ventricles. In contrast, pressure gradients induce fluid
-flow \fixme{further from the ventricular walls (bulk flow)} and along the
-perivascular space surrounding the major blood vessels.
+from 6 to 15 microns, the cilia contribute to flow primarily at the surface
+of the brain ventricles. In contrast, fluid flow induced by the 
+cardiac and respiratory cycles account for the bulk flow in the brain
+ventricles~\cite{Vinje2019RespiratoryMeasurements},
+as well as the CSF flow in the perivascular spaces.
 
 To date, it remains poorly understood how cilia contribute to the
-overall fluid flow and solute transport in the brain.
+overall fluid flow and solute transport within the brain.
 These questions have been challenging to tackle due to technical
@@
 processes in the brain are slower and span larger volumes, making
-cilia dynamics challenging to monitor. Until now, most studies have
+cilia dynamics challenging to monitor in vivo. Until now, most studies have
 analyzed one physical mechanism at a time, especially in mammals.
@@
 ventricles; however, they failed to identify the role of pressure
-gradients associated with respiration and heart pulsations in CSF
-transport. Similarly, while MRI technology can measure CSF movement
+gradients associated with respiration and cardiac pulsations in CSF flow
+and the accompanying transport. Similarly, while MRI technology can measure CSF movement
 in humans, it cannot detect the microscopic movements of cilia to
@@
 lack a comprehensive understanding of how cilia contribute to CSF
-movement and solute transport, and whether cilia dysfunction will
+motion and solute transport, and whether cilia dysfunction will
 alter CSF composition and lead to brain disorders. This is particularly
@@
 is observed in animal models and humans with motile cilia deficiency,
-\fixme{potentially affecting brain activity and behavior.}
+indiciating that the cilia play a crucial role for healthy brain functioning.
 
@@
 possibility of mathematical modeling and computational investigations. Numerous previous studies
-focused on modeling the interaction between single or several cilia and surrounding
+have focused on modeling the interaction between single or several cilia and surrounding
 fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids,
 Cui2019NumericalMethod, Cui2022AFlow}.
-Others considered applications such as ciliary transport of mucous in
+Others considered applications such as ciliary transport of mucous and particles in
 airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
@@
 Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella},
-coral reefs~\cite{Pacherres2022CiliaryProduction}, and the brain~\cite{Siyahhan2014FlowVentricles,
+oxygen regulation in coral reefs~\cite{Pacherres2022CiliaryProduction},
+and cilia-mediated flow in the brain~\cite{Siyahhan2014FlowVentricles,
 Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
@@
 In this study, we combined computational and experimental approaches to investigate
-the role of motile cilia in CSF flow and solute transport.
-First, we computed flow patterns and intraventricular transport \emph{in silico}. To
+the role of motile cilia in intraventricular CSF flow and transport.
+First, we computed flow patterns and simulated solute transport with a computational model. To
 this end, we used the geometry of the zebrafish larval brain ventricles,
-for which we have detailed knowledge of cilia properties and CSF movement velocities
+for which we have detailed knowledge of cilia properties and CSF motion velocities
 and frequencies. Notably, this early developmental stage allows us to simplify our model
-by omitting CSF secretion, which starts at later stages, while still being well-conserved with mammals.
-Next, we validated our computation model with experimental data by monitoring
-the dynamics of a photoconvertible fluorescent protein Dendra2 expressed within the brain ventricles.
+by omitting CSF secretion, which starts at later stages,
+while still being well-conserved with mammals. 
+Next, we validated our computation model with experimental data by monitoring in vivo
+the dynamics of a photoconvertible fluorescent protein Dendra2
+expressed within the brain ventricles.
 Our results show that diffusion plays a major role in the transport of small solutes,
@@
 impact solute distribution. Altogether, our work presents a computational
-framework together with new concepts of how cilia
-collaborate with other factors to distribute molecules and
+framework together with new concepts of how cilia contribute to distribution of molecules and
 particles within the brain ventricles.
@@
 \subsubsection{Flow induced by cardiac pulsations}
-To drive a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
+To generate a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
 $\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
@@
 cardiac pulsations to the velocity magnitude,
-as compared to the effect of cilia motion on the flow (see~\Cref{sec:appC_particle_transport}).
+as compared to the effect of cilia motion on the flow (cf.~\Cref{sec:appC_particle_transport}).
 
@@
 For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
-with $R=200$ nm. This radius covers the slowest diffusing exosomes,
+with $R=150$ nm, which represents exosomes at the larger end of the
+scale~\cite{Moghassemi2024ExtracellularDecade}.
+Hence this radius covers the slowest diffusing exosomes,
 a choice made because smaller exosomes would have diffusion coefficients
-similar to the other molecules.
+similar to the other molecules we consider.
 For STM-GFP, we estimated the diffusion coefficient by extrapolating
@@
         & $\num{5.75e-11}$ & * \\
-        Exosomes (radius of 200 nm) & -- & $\num{1.63e-12}$ & \textdagger \\
+        Exosomes (radius of 150 nm) & -- & $\num{2.17e-12}$ & \textdagger \\
         \bottomrule
@@
 and then averaging $\overline{u}$ in time over one cardiac cycle.
-To assess the assumption that the CSF flow is governed by the Stokes equations,
+To assess the assumption that inertial forces are negligible compared to
+viscous forces in the CSF flow, such that the flow is governed by the Stokes equations,
 we also compute the Reynolds number
@@
 The dynamics at the site of photoconversion (ROI 1)
-is logarithmic and follows from imposing \eqref{eq:photoconversion_curve}.
+is logarithmic and follows from imposing \Cref{eq:photoconversion_curve}.
 For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
@@
 (thus with smaller diffusion coefficients),
-such as 200 nm exosomes, are almost entirely dependent on advection.
+such as 150 nm exosomes, are almost entirely dependent on advection.
 Indeed, there was essentially zero solute in the posterior ventricle at the
@@
 
-\subsection{Impact of cilia motility and ventricular morphology}
+\subsection{Effects of cilia motility and ventricular morphology}
 To gain further insights into how CSF flow and intraventricular transport depend on cilia
 motility and ventricular morphology, we manipulated certain
-parameters in our models. First, we paralyzed cilia in specific regions of
+parameters in our models. First, we investigated how complete loss of cilia motility
+impacted the transport dynamics. Simulations with a cardiac-only/no-cilia lead to
+slower transport when compared to the baseline model that included cilia. Especially
+the middle-ventricular region downstream of CSF flow (ROI 2) and the anterior ventricle (ROI 5)
+experienced substantially increased times-to-threshold. We also observed
+slower dynamics in the rest of the middle ventricle (ROIs 3 and 4), whereas the
+posterior ventricle (ROI 6) was unaffected by the loss
+of cilia motility, indicating that transport from the middle to the posterior ventricle is
+purely driven by diffusion. We also performed photoconversion experiments on cilia mutant
+zebrafish larva (\emph{smh}), observing statistically signifcant slower transport in 
+ROIs 2 and 4. The results provide not only confidence in that our computational model
+well represents the physics, but also valuable quantification of the impact of cilia motility
+on intraventricular transport. Interestingly, a previous simulation study of reduced cilia motility
+also observed a drastic reduction in CSF mixing in specific regions of the brain
+ventricles~\cite{Yoshida2022EffectVentricles}, similar to our results. Since impaired brain 
+clearance of tracers has been demonstrated in idiopathic normal pressure hydrocephalus
+patients~\cite{Eide2020MagneticHydrocephalus}, cilia-enhanced mixing in the brain might be
+fundamental to physiological transport within the brain.
+
+Next, we paralyzed cilia in specific regions of
 our model. We identified that the cilia in the dorsal middle ventricle contribute
@@
 
-Next, we modified the ventricular geometry and identified the impact on transport.
+With an interest in assessing the impact of ventricular morphology on solute transprot,
+we simulated transport on modified ventricular geometries.
 Notably, shrinking ducts reduced interventricular solute movement, while shrinking
@@
 CSF dynamics in more complex geometries and also other animal species and humans.
-
-\lyng{HH: Compare numerical results with transport results in Figure 7 in \cite{Olstad2019CiliaryDevelopment}.}
-
-\lyng{HH: Discuss cilia serving as an "enhanced mixing factor" on small scales,
-refer to this~\cite{Siyahhan2014FlowVentricles} and this~\cite{Yoshida2022EffectVentricles}
-paper that studied this in human brain ventricles.
-Include a discussion of what happened when these papers removed cilia.}
 
@@
 A priori error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
-derived in a mesh-dependent broken $H^1$-norm for $\uu$ and the $L^2$-norm for the pressure. The respective 
-errors are expected to decay with order $k$,
-see for example Cockburn~\emph{et al.}~\cite{Cockburn2005AEquations}.
+derived in a mesh-dependent broken $H^k$-norm for $\uu$ and the $L^2$-norm for the pressure.
+The respective error norms are expected to decay with order $k$~\cite{Cockburn2005AEquations}.
 For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
-reports the velocity errors in the standard $H^1$ norm. Using polynomial degree  
+reports the velocity errors in the standard $H^k$ norm. Using polynomial degree  
 $k=1$, we observe linear convergence in both the velocity and the pressure.   
 \mk{MK: I see 1.5 in the table for $\uu$ in $L^2$?}
-\lyng{HH: Yes, while the $H^1$ error decays linearly, isn't this in line with expectations?
-Could be more specific: "Using polynomial degree 
-$k=1$, we observe linear convergence in both the velocity $H^1$ error and the pressure $L^2$ error."}
+\lyng{HH: Yes, we should expect 2 there? Maybe be more specific in the comment:
+"Using polynomial degree $k=1$, we observe linear convergence in both the velocity $H^1$ error
+and the pressure $L^2$ error. For the $L^2$ error of the velocity, we observe a suboptimal
+convergence order of 1.5"}
 
@@
 \textbf{Data Availability Statement} \par
-\fixme{TO DO}.
+The data and implementations presented in this paper are licensed under \fixme{LICENSE}
+and openly avalaible at \fixme{REPO-LINK}.
 
 \medskip
-\textbf{Declaration of No Competing Interest} \par
-\fixme{TO DO}.
+\textbf{Conflict of Interest Disclosure} \par
+The authors declare no conflicts of interest.
 
@@
 \textbf{Acknowledgements} \par 
+Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
 Halvor Herlyng acknowledges support from the national infrastructure for computational
@@
 This work was funded by the Research Council of Norway (NJY FRIPRO grants 314189 and 353348).
-Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
 
@@
 \begin{alignat}{2}
-   \rho\pdifft{\uu} - \nabla \cdot \bsig(\uu, p) &= \mathbf{0} \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_mom}\\
+   \rho\pdifft{\uu} - \nabla \cdot \bsig(\uu, p)
+   &= \mathbf{0} \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_mom}\\
   \nabla \cdot \uu &= 0 \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_div} 
@@
     L^2(\Omega) &= \bigg\{p \ : \ \intO{p^2} < \infty\bigg\} \\
-    \mathbf{H}^1(\mathrm{div}; \Omega) &= \bigg\{\uu \ : \ \uu\in\mathbf{L}^2(\Omega), \nabla\cdot\uu\in L^2(\Omega)\bigg\}.
+    \mathbf{H}^1(\mathrm{div}; \Omega)
+    &= \bigg\{\uu \ : \ \uu\in\mathbf{L}^2(\Omega), \nabla\cdot\uu\in L^2(\Omega)\bigg\}.
 \end{align*}
@@
 \begin{equation*}
-    \VV =  \bigg\{\vv \ : \ \vv\in\mathbf{H}^1(\mathrm{div}; \Omega), \vv\cdot\nn=0 \ \mathrm{on} \ \Gamma\setminus\Gamma_{\mathrm{io}}\bigg\}.
+    \VV =  \bigg\{\vv \ : \ \vv\in\mathbf{H}^1(\mathrm{div}; \Omega),
+    \vv\cdot\nn=0 \ \mathrm{on} \ \Gamma\setminus\Gamma_{\mathrm{io}}\bigg\}.
 \end{equation*}
@@
 }
-To derive a weak formulation of the Stokes equations~\eqref{eq:appendix_stokes_eqs},
-we begin by multiplying~\eqref{eq:BDM_stokes_mom} with a
+To derive a weak formulation of the Stokes equations~\Cref{eq:appendix_stokes_eqs},
+we begin by multiplying~\Cref{eq:BDM_stokes_mom} with a
 test function $\vv\in\VV$ and integrating over the domain:
@@
 as the only mechanism driving flow. We consider the
-Stokes equations~\eqref{eq:appendix_stokes_eqs} with the slip boundary conditions
+Stokes equations~\Cref{eq:appendix_stokes_eqs} with the slip boundary conditions
 \begin{subequations}
     \begin{alignat}{2}
-        \uu\cdot\nn &= 0 \quad &&\mathrm{on} \ \Gamma=\Gc\cup\Gs, \label{eq:modelA_slip_BC_impermeability} \\
+        \uu\cdot\nn &= 0 \quad &&\mathrm{on} \ \Gamma=\Gc\cup\Gs,
+        \label{eq:modelA_slip_BC_impermeability} \\
         \bsigpar &= \btau \quad &&\mathrm{on} \ \Gc,
@@
 on the boundary $\Gamma=\Gamma_c\cup\Gamma_s$. The boundary $\Gamma_s$ is a free-slip boundary,
-where we impose the free-slip condition~\eqref{eq:modelA_full_slip_BC}.
-The first condition~\eqref{eq:modelA_slip_BC_impermeability} is the
+where we impose the free-slip condition~\Cref{eq:modelA_full_slip_BC}.
+The first condition~\Cref{eq:modelA_slip_BC_impermeability} is the
 impermeability condition, enforcing no flow normal to the boundary,
-whereas~\eqref{eq:modelA_slip_BC_shear} imposes a stress tangential to
+whereas~\Cref{eq:modelA_slip_BC_shear} imposes a stress tangential to
 the boundary. These tangential stresses are applied to represent
@@
 
-The boundary conditions~\eqref{eq:modelA_slip_BC} are set weakly through the stress boundary integral 
+The boundary conditions~\Cref{eq:modelA_slip_BC} are set weakly through the stress
+boundary integral 
 \begin{equation}
@@
 \end{equation}
-in the weak form~\eqref{eq:modelA_weak_form1} of the Stokes equations.
+in the weak form~\Cref{eq:modelA_weak_form1} of the Stokes equations.
 We decompose the traction vector $\hat{\bsig}$ into a normal and tangential component:
@@
 \end{equation*}
-Inserting the above into~\eqref{eq:boundary_integral_BC1},
+Inserting the above into~\Cref{eq:boundary_integral_BC1},
 combined with application of the tangential traction
-condition~\eqref{eq:modelA_slip_BC_shear} and the
-free-slip condition~\eqref{eq:modelA_full_slip_BC}, yields
+condition~\Cref{eq:modelA_slip_BC_shear} and the
+free-slip condition~\Cref{eq:modelA_full_slip_BC}, yields
 \begin{equation}
@@
 \end{equation}
-The second term on the right-hand side of~\eqref{eq:boundary_integral_BC2}
+The second term on the right-hand side of~\Cref{eq:boundary_integral_BC2}
 is moved to the right-hand side of the weak form, since $\btau$ is known
  Using $\hat{\bsig}_{\perp} = (\hat{\bsig}\cdot\nn)\nn$,
- we can write the first term on the right-hand side of~\eqref{eq:boundary_integral_BC2} as
+ we can write the first term on the right-hand side of~\Cref{eq:boundary_integral_BC2} as
 \begin{equation}
-    \intG{\bsigperp\cdot\vv} = \intG{((\hat{\bsig}\cdot\nn)\nn)\cdot\vv} = \intG{(\hat{\bsig}\cdot\nn)(\vv\cdot\nn)}.
+    \intG{\bsigperp\cdot\vv} = \intG{((\hat{\bsig}\cdot\nn)\nn)\cdot\vv} =
+    \intG{(\hat{\bsig}\cdot\nn)(\vv\cdot\nn)}.
     \label{eq:boundary_integral_BC_normal}
@@
 the value of $\uu\cdot\nn$ and thus the boundary
-condition~\eqref{eq:modelA_slip_BC_impermeability}.
+condition~\Cref{eq:modelA_slip_BC_impermeability}.
 Consequently, the test function counterpart $\vv\cdot\nn$ vanishes
-on the boundary, and the term~\eqref{eq:boundary_integral_BC_normal}
+on the boundary, and the term~\Cref{eq:boundary_integral_BC_normal}
 is therefore dropped from the weak form. As a result, for the cilia-only/no-cardiac model,
@@
 \end{equation*}
-Next, multiplying the continuity equation~\eqref{eq:BDM_stokes_div}
+Next, multiplying the continuity equation~\Cref{eq:BDM_stokes_div}
 with a test function $q\in Q$, we require that
@@
         &&= \intGc{\btau\cdot\vv}, &&\quad\forall\vv\in\VV, \label{eq:stokes_weak_mom_modelA}\\ 
-        &{} &{}  -&\intO{q\nabla\cdot\uu} &&= 0, &&\quad\forall q\in Q. \label{eq:stokes_weak_cont_modelA}
+        &{} &{}  -&\intO{q\nabla\cdot\uu} &&= 0, &&\quad\forall q\in Q.
+        \label{eq:stokes_weak_cont_modelA}
     \end{alignat}%
@@
 \end{subequations}%
-We observe that, in this case with slip boundary conditions on the entirety of the boundary $\Gamma$, the
-vector $(\uu, p)=(\mathbf{0}, C)$ for any real constant $C$ satisfies the equations.
-The system~\eqref{eq:stokes_weak_modelA} is thus singular with a one-dimensional nullspace of constant pressures.
-Consequently, assembly of our discretization of the  equations~\eqref{eq:stokes_weak_modelA} into a
-linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
+We observe that, in this case with slip boundary conditions on the entirety of
+the boundary $\Gamma$, the vector $(\uu, p)=(\mathbf{0}, C)$ for any real
+constant $C$ satisfies the equations.
+The system~\Cref{eq:stokes_weak_modelA} is thus singular with a one-dimensional nullspace
+of constant pressures.
+Consequently, assembly of our discretization of the  equations~\Cref{eq:stokes_weak_modelA}
+into a linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
 To ensure existence of solutions, we orthogonalize the right-hand side vector $\mathbf{b}$ with
-respect to the pressure nullspace basis (the set of all constants), before solving the linear system.
-To obtain a unique solution, which together with existence renders the problem well-posed,
-information of the pressure nullspace is passed to the linear solver. Let us remark that
-the singularity is a consequence of the fact that the impermeability condition is assumed
-to hold on the \emph{entire} domain boundary for this model version, which leaves the
-pressure under-determined as a result of no boundary condition specifying the pressure.
+respect to the pressure nullspace basis (the set of all constants), before solving the linear
+system. To obtain a unique solution, which together with existence renders the
+problem well-posed, information of the pressure nullspace is passed to the linear solver.
+Let us remark that the singularity is a consequence of the fact that the
+impermeability condition is assumed to hold on the \emph{entire} domain boundary
+for this model version, which leaves the pressure under-determined as a result of no
+boundary condition specifying the pressure.
 
@@
         \midrule 
-        Anterior region, anterior ventricle  & $-(1, 0, 1)$ & $\frac{2}{5}$ \\
-        Posterior region, anterior ventricle & $\ \ \ (1, 0, 1)$ & 1 \\
-        Dorsal region, middle ventricle      & $-(1, 0, 1)$ & $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
-        Ventral region, middle ventricle     & $\ \ \ (1, 0, 1)$ & $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
+        Anterior region, anterior ventricle 
+        & $-(1, 0, 1)$ & $\frac{2}{5}$ \\
+        Posterior region, anterior ventricle
+        & $\ \ \ (1, 0, 1)$ & 1 \\
+        Dorsal region, middle ventricle     
+        & $-(1, 0, 1)$
+        & $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
+        Ventral region, middle ventricle    
+        & $\ \ \ (1, 0, 1)$
+        & $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
         \bottomrule
@@
     \begin{alignat}{2}
-      \uu\cdot\nn = 0, \ \hat{\bsig}_{\parallel} &= \mathbf{0} \quad &&\mathrm{on} \ \Gs, \label{eq:modelB_slip_BC} \\
-      (\mu\nabla\uu - p\mathbf{I})\nn &= \Tilde{p}(t)\nn \quad &&\mathrm{on} \ \Gp, \label{eq:modelB_pressure_BC}
+      \uu\cdot\nn = 0, \ \hat{\bsig}_{\parallel} &= \mathbf{0} \quad &&\mathrm{on} \ \Gs,
+      \label{eq:modelB_slip_BC} \\
+      (\mu\nabla\uu - p\mathbf{I})\nn &= \Tilde{p}(t)\nn \quad &&\mathrm{on} \ \Gp,
+      \label{eq:modelB_pressure_BC}
     \end{alignat}%
@@
 Note, however, that the transpose velocity gradient term must be
-included inside the parentheses on the left-hand side of~\eqref{eq:modelB_pressure_BC}
+included inside the parentheses on the left-hand side of~\Cref{eq:modelB_pressure_BC}
 for it to be the traction $\bsig$. Since this is not the case,
@@
 The boundary $\Gs$ is handled as discussed in the previous section,
-such that the stress boundary integral~\eqref{eq:boundary_integral_BC1}
+such that the stress boundary integral~\Cref{eq:boundary_integral_BC1}
 vanishes over $\Gs$. Therefore, we now have
 \begin{align}
-    \intG{\hat{\bsig}\cdot\vv} = \intGp{\hat{\bsig}\cdot\vv} &= \intGp{(\mu(\nabla\uu + (\nabla\uu)^T) - p\mathbf{I})\nn\cdot\vv}\notag \\
-    &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{(\mu\nabla\uu - p\mathbf{I})\nn\cdot\vv}\notag\\
+    \intG{\hat{\bsig}\cdot\vv} = \intGp{\hat{\bsig}\cdot\vv}
+    &= \intGp{(\mu(\nabla\uu + (\nabla\uu)^T) - p\mathbf{I})\nn\cdot\vv}\notag \\
+    &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{(\mu\nabla\uu
+    - p\mathbf{I})\nn\cdot\vv}\notag\\
     &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}
@@
 We leave the first term on the left-hand side
-of~\eqref{eq:modelB_boundary_integral1} in the weak form of
+of~\Cref{eq:modelB_boundary_integral1} in the weak form of
 the momentum equation. The second term is determined by
-the boundary condition~\eqref{eq:modelB_pressure_BC},
+the boundary condition~\Cref{eq:modelB_pressure_BC},
 and is therefore moved to the right-hand side of the weak form.
@@
     \begin{aligned}
-    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\beps(\uu) : \beps(\vv)} - \intO{p\nabla\cdot\vv} &-\intGp{\mu(\nabla\uu)^T\nn\cdot\vv} \\ &=\intGp{\Tilde{p}(t)(\vv\cdot\nn)}, \quad\forall\vv\in\VV.
+    \intO{\rho\pdifft{\uu}\cdot\vv} + \intO{2\mu\beps(\uu) : \beps(\vv)} -
+    \intO{p\nabla\cdot\vv} &-\intGp{\mu(\nabla\uu)^T\nn\cdot\vv} \\
+    &=\intGp{\Tilde{p}(t)(\vv\cdot\nn)}, \quad\forall\vv\in\VV.
     \end{aligned}
@@
 then reads: find $(\uu,\, p)\in\VV\times Q$
-such that~\eqref{eq:weak_form_mom_eq_modelB} and~\eqref{eq:pressure_weak_form}
+such that~\Cref{eq:weak_form_mom_eq_modelB} and~\Cref{eq:pressure_weak_form}
 hold for all $(\vv, \, q)\in\VV\times Q$.
@@
 $\Tilde{p}(t) = p_c(t) = -A\sin{\omega t}$ on the posterior part. The value of the amplitude
-$A$ was based on heuristics and $\omega = 2\pi f$, where $f=2.22$ Hz is the cardiac cycle frequency.
+$A$ was based on heuristics and $\omega = 2\pi f$, where $f=2.22$ Hz
+is the cardiac cycle frequency.
 
@@
 the sections of the other flow model versions. We handle the boundary
-conditions~\eqref{eq:slip_BC_modelC} and~\eqref{eq:freeslip_BC_modelC}
+conditions~\Cref{eq:slip_BC_modelC} and~\Cref{eq:freeslip_BC_modelC}
 as introduced for the cilia-only/no-cardiac model, and the boundary
-condition~\eqref{eq:pressure_BC_modelC} is applied as discussed in the section
+condition~\Cref{eq:pressure_BC_modelC} is applied as discussed in the section
 on the cardiac-only/no-cilia model. The abstract weak formulation for 
@@
     \begin{alignat}{2}
-        \mathcal{A}(\uu, \vv) + \mathcal{B}(\vv, p) &= \mathcal{L}(\vv), &&\quad\forall\vv\in\VV, \\
+        \mathcal{A}(\uu, \vv) + \mathcal{B}(\vv, p) &= \mathcal{L}(\vv),
+        &&\quad\forall\vv\in\VV, \\
         \mathcal{B}(\uu, q) &= 0, &&\quad\forall q\in Q,
@@
     \mathcal{B}(\uu, q) &= -\intO{q\nabla\cdot\uu}, \label{eq:stokes_skew_form}\\
-    \mathcal{L}(\vv) &= \intGc{\btau\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}. \label{eq:stokes_linear_form}
+    \mathcal{L}(\vv) &= \intGc{\btau\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}.
+    \label{eq:stokes_linear_form}
 \end{align}
@@
     \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) &=
-    \sum_{k\in K}\intF{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}\cdot \jump{P_{\nn}(\vv_h)}}\\
+    \sum_{k\in K}\intF{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}
+    \cdot\jump{P_{\nn}(\vv_h)}}\\
     &-\sum_{k\in K}\intF{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}
@@
 \end{align*}
-to the discrete weak  formulation~\eqref{eq:no_stabilization_abstract_discrete_weak_form_modelC},
+to the discrete weak  formulation~\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC},
 where $\mathcal{F} = \{\mathcal{F}_k : k\in K\}$ is the set of all interior facets
@@
 \end{subequations}%
-We solved~\eqref{eq:abstract_semi_discrete_weak_form_modelC}
+We solved~\Cref{eq:abstract_semi_discrete_weak_form_modelC}
 numerically with the penalty parameter $\gamma=10$.
 
-In time, we discretize the weak formulation~\eqref{eq:abstract_semi_discrete_weak_form_modelC}
+In time, we discretize the weak formulation~\Cref{eq:abstract_semi_discrete_weak_form_modelC}
 with the implicit Euler method.
 
-\subsection{Weak formulation of the advection-diffusion equation}\label{subsec:adv_diff_eq_weak_form}
+\subsection{Weak formulation of the advection-diffusion equation}
+\label{subsec:adv_diff_eq_weak_form}
 Recall the strong form of the advection-diffusion equation:
@@
 The concentration $c\in W$ and the cerebrospinal fluid velocity $\uu\in\VV$.
-The weak form of~\eqref{eq:adv_diff_strong_DG} is derived by
+The weak form of~\Cref{eq:adv_diff_strong_DG} is derived by
 multiplying the equation with a test function $\phi \in W$ and integrating over the domain: 
@@
 \textbf{Only-cardiac/no-cilia model.} When using the normal pressure
-boundary condition~\eqref{eq:modelB_pressure_BC} to model pulsatile flow,
+boundary condition~\Cref{eq:modelB_pressure_BC} to model pulsatile flow,
 we have in- and outflow of cerebrospinal fluid and thus advection of
@@
 \end{equation*}
-For the outflow boundary integral over $\Gout$, we impose zero diffusive flux $D\nabla c\cdot\nn=0$,
+For the outflow boundary integral over $\Gout$, we impose zero
+diffusive flux $D\nabla c\cdot\nn=0$,
 with the advection term $c(\uu\cdot\nn)$ simply left in the variational form as an unknown.
-For the continuous problem this is problematic, since we are lacking a boundary condition to close the problem. 
+For the continuous problem this is problematic, since we are lacking a boundary
+condition to close the problem. 
 In the discrete setting, however, this method of leaving the boundary term has been shown
@@
 setting the advective flux to being the one consistent with the weak form,
-for which there is a unique $c$ satisfying the equations, with $\uu$ determined by the Stokes equations.
+for which there is a unique $c$ satisfying the equations, with $\uu$ determined by
+the Stokes equations.
 
@@
 when solving the linear system for the concentration $c^{n+1}$ at the next timestep $n+1$,
-we set the inflow flux $h_{\mathrm{in}}^{n+1} = h_{\mathrm{out}}^{n}$, where the latter is the outflow flux
+we set the inflow flux $h_{\mathrm{in}}^{n+1} = h_{\mathrm{out}}^{n}$, where the
+latter is the outflow flux
 \begin{equation*}
@@
 \begin{align}
-    a(c, \phi) &= \intO{\pdifft{c}\phi} - \intO{\JJ\cdot\nabla\phi}, \label{eq:adv_diff_bilinear_form}\\
+    a(c, \phi) &= \intO{\pdifft{c}\phi} - \intO{\JJ\cdot\nabla\phi},
+    \label{eq:adv_diff_bilinear_form}\\
     b(c, \phi) &= \intGout{c(\uu\cdot\nn)\phi}, \label{eq:adv_diff_skew_form} \\
@@
 identical to that of the cardiac-only/no-cilia model,
-defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
+defined by~\Cref{eq:adv_diff_weak_formB,eq:adv_diff_skew_form,eq:adv_diff_linear_form}.
 
@@
 We outline the discretization of the advection-diffusion weak formulation
-for the baseline model, defined by~\eqref{eq:adv_diff_weak_formB}--\eqref{eq:adv_diff_linear_form}.
-The weak formulation is discretized with a symmetric interior-penalty method using discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}.
-Let the subscript $h$ denote discrete variables.
-Exchanging the variables in~\eqref{eq:adv_diff_weak_formB} with their discrete counterparts yields the discrete weak form: find $c_h\in W_h$ such that
+for the baseline model, defined
+by~\Cref{eq:adv_diff_weak_formB,eq:adv_diff_skew_form,eq:adv_diff_linear_form}.
+The weak formulation is discretized with a symmetric interior-penalty method using
+discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}.
+Let the subscript $h$ denote discrete variables. Exchanging the
+variables in~\Cref{eq:adv_diff_weak_formB} with their discrete
+counterparts yields the discrete weak form: find $c_h\in W_h$ such that
 \begin{equation*}
@@
 \end{equation*}
-The space $W_h$ is constructed with  finite elements with discontinuous linear Lagrange polynomial basis functions, allowing for discontinuities in the discrete solution across element edges.
+The space $W_h$ is constructed with  finite elements with
+discontinuous linear Lagrange polynomial basis functions,
+allowing for discontinuities in the discrete solution across element edges.
 To achieve a stable discretization with these elements, we add the stabilization
@@
     \begin{aligned}
-        a_{\mathrm{stab}}(c_h, \phi_h) = &\sum_{k\in K}\intF{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}} +\sum_{k\in K}\intF{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
-         -&\sum_{k\in K}\intF{D\avg{\nabla\phi_h}\cdot\jump{c_h}} -\sum_{k\in K}\intF{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
+        a_{\mathrm{stab}}(c_h, \phi_h)
+        = &\sum_{k\in K}\intF{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
+        +\sum_{k\in K}\intF{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
+         -&\sum_{k\in K}\intF{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
+         -\sum_{k\in K}\intF{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
     \end{aligned}\label{eq:SIP_stabilization}
@@
 \end{equation*}
-is used to upwind the velocity $\uu_h$, with the velocity upwinded with respect to a facet $\mathcal{F}_k$.
-The stabilization parameter $\alpha>0$ must be chosen large enough to achieve stability.
-The average and jump operators used in~\eqref{eq:SIP_stabilization} are defined, respectively, as
+is used to upwind the velocity $\uu_h$, with the velocity upwinded with respect to a
+facet $\mathcal{F}_k$. The stabilization parameter $\alpha>0$ must be chosen
+large enough to achieve stability. The average and jump operators used
+in~\Cref{eq:SIP_stabilization} are defined, respectively, as
 \begin{equation*}
@@
 \end{equation*}
-The final discrete weak formulation of the advection-diffusion equation is: find $c_h\in W_h$, such that
+The final discrete weak formulation of the advection-diffusion equation is:
+find $c_h\in W_h$, such that
 \begin{equation}
-    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h), \quad\forall\phi_h\in W_h.
+    a(c_h, \phi_h) + a_{\mathrm{stab}}(c_h, \phi_h) + b(c_h, \phi_h) = L(\phi_h),
+    \quad\forall\phi_h\in W_h.
     \label{eq:discrete_weak_form_adv_diff}
 \end{equation}
-In this work, we solved~\eqref{eq:discrete_weak_form_adv_diff} numerically with the penalty parameter value $\alpha=25$.
-
-In time, we discretized~\eqref{eq:discrete_weak_form_adv_diff} with the implicit Euler method.
+In this work, we solved~\Cref{eq:discrete_weak_form_adv_diff} numerically
+with the penalty parameter value $\alpha=25$.
+
+In time, we discretized~\Cref{eq:discrete_weak_form_adv_diff} with the implicit Euler method.
 
@@
 be the spatial coordinates scaled by the length $L$, which is the length of
-the computational domain $\Omega$ in the $x$-direction. Letting $\bm{\phi}$ be the vector-valued function
-\begin{equation*}
-    \bm{\phi} = \left(\sin{(\pi(\hat{x} - \hat{y}))}, \sin{(\pi(\hat{y} + \hat{z}))}, \sin{(\pi(\hat{x} - \hat{z}))}\right)
+the computational domain $\Omega$ in the $x$-direction. Letting $\bm{\phi}$ be
+the vector-valued function
+\begin{equation*}
+    \bm{\phi} = \left(\sin{(\pi(\hat{x} - \hat{y}))},
+    \sin{(\pi(\hat{y} + \hat{z}))},
+    \sin{(\pi(\hat{x} - \hat{z}))}\right)
 \end{equation*}
@@
 Using the Method of Manufactured Solutions~\cite{Roache2001CodeSolutions},
-we construct a problem with the Stokes equations where~\eqref{eq:velocity_mms}
-and~\eqref{eq:pressure_mms} are the solutions.
+we construct a problem with the Stokes equations where~\Cref{eq:velocity_mms}
+and~\Cref{eq:pressure_mms} are the solutions.
 To this end, we consider the general form of the steady Stokes equations
@@
 where $\Gamma=\partial\Omega$ is the boundary of the domain.
-Since the velocity field~\eqref{eq:velocity_mms} is divergence free by construction,
+Since the velocity field~\Cref{eq:velocity_mms} is divergence free by construction,
 $g = 0$. Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$
-using~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms},
-the solutions $\uu$ and $p$ to~\eqref{eq:stokes_mms} will be the ones
-defined by~\eqref{eq:velocity_mms} and~\eqref{eq:pressure_mms},
+using~\Cref{eq:velocity_mms} and~\Cref{eq:pressure_mms},
+the solutions $\uu$ and $p$ to~\Cref{eq:stokes_mms} will be the ones
+defined by~\Cref{eq:velocity_mms} and~\Cref{eq:pressure_mms},
 as long as we enforce equality in the mean pressures, i.e. $\intO{(p_h - p_{\mathrm{mms}})}=0$.
 Convergence rates are then readily calculated by comparing the numerical approximations of
-$\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$ on meshes of varying grid resolution.
+$\uu$ and $p$ with $\uu_{\mathrm{mms}}$ and $p_{\mathrm{mms}}$
+on meshes of varying grid resolution.
 
@@
 were measured in the $\mathbf{H}^1$ and $L^2$ error norms, respectively.
-With the exact velocity field $\uu_{\mathrm{ex}}$, the $\mathbf{H}^1$ error norm was calculated as
-\begin{equation*}
-    \Hnorm{\uu_h - \uu_{\mathrm{ex}}}^2 = \intO{\nabla(\uu_h - \uu_{\mathrm{ex}}) : \nabla(\uu_h - \uu_{\mathrm{ex}})}.
+With the exact velocity field $\uu_{\mathrm{ex}}$, the $\mathbf{H}^1$
+error norm was calculated as
+\begin{equation*}
+    \Hnorm{\uu_h - \uu_{\mathrm{ex}}}^2
+    = \intO{\nabla(\uu_h - \uu_{\mathrm{ex}}) : \nabla(\uu_h - \uu_{\mathrm{ex}})}.
 \end{equation*}
@@
 errors, respectively. Numerical integration was performed with a Gauss quadrature rule,
-with the quadrature rule degree equal to the polynomial degree of the integrated finite element functions.
+with the quadrature rule degree equal to the polynomial degree of the integrated
+finite element functions.
 
@@
 \end{equation*}
-with basis functions $\psi_i$, where $i$ are the degrees of freedom and Einstein summation is employed.
+with basis functions $\psi_i$, where $i$ are the degrees of freedom and Einstein
+summation is employed.
 The infinity norm of $\phi$ was approximated from the vector
@@
     For all error norms, convergence rates calculated
-    with~\eqref{eq:convergence_order_estimate} are given
+    with~\Cref{eq:convergence_order_estimate} are given
     in parentheses.}\label{tab:cylinder_error_rates}
@@
 owing to the unstructured organization of the mesh cells. This change in the surface
-area over which the tangential traction was applied directly affected the maximum velocity magnitude,
+area over which the tangential traction was applied directly affected
+the maximum velocity magnitude,
 since the maximum velocity magnitude is a result of the total amount of force
@@
         & $\frac{1}{|\Gc|}\normlinf{u_h}$ $\left[\frac{1}{\mathrm{mm\cdot s}}\right]$
-        & $\frac{1}{\vert\Omega\vert}\normltwovec{\uu_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$
+        & $\frac{1}{\vert\Omega\vert}\normltwovec{\uu_h}$
+        $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$
         & $\normltwo{\nabla\cdot\uu_h}$ $\left[\frac{\mathrm{mm^3}}{\mathrm{s^2}}\right]$\\
@@
 calculating the change in positions $\Delta x$ and $\Delta y$ relative to the change
-in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the frequency of acquisition.
-Mean velocities $\overline{u}_x$~(\Crefpanels{fig:particle_tracking_data}{a}) and $\overline{u}_y$~(\Crefpanels{fig:particle_tracking_data}{b}),
+in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the
+frequency of acquisition.
+Mean velocities $\overline{u}_x$~(\Crefpanels{fig:particle_tracking_data}{a}) and
+$\overline{u}_y$~(\Crefpanels{fig:particle_tracking_data}{b}),
 which serve as a quantification of particle drift, were calculated
@@
 Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
-0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s. The maximum mean velocities
-in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for $\overline{u}_x$ and $\overline{u}_y$,
-respectively. We used the only-cardiac/no-cilia flow model to tune the pressure boundary condition
-amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude
-of 4.8 \textmu m/s, which is close to the maximum observed in the particle tracking data when
+0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s.
+The maximum mean velocities
+in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for
+$\overline{u}_x$ and $\overline{u}_y$,
+respectively. We used the only-cardiac/no-cilia flow model to tune the
+pressure boundary condition
+amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a
+maximum velocity magnitude
+of 4.8 \textmu m/s, which is close to the maximum observed in the
+particle tracking data when
 rejecting the outlier at around 10 \textmu m/s; (ii) it yields a time-averaged mean velocity
@@
     \end{minipage} 
-    \caption{Particle tracking data. Mean velocities in the $x$ and $y$ directions of the particles tracked. The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
+    \caption{Particle tracking data. Mean velocities in
+    the $x$ (\textbf{a.}) and $y$ (\textbf{b.}) directions of the particles tracked.
+    The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
 \end{figure}

### 2025-02-23 paper/main.tex
minor update

@@
         & $-(1, 0, 1)$
-        & $\lambda(\xx)=\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
+        & \frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
         Ventral region, middle ventricle    
         & $\ \ \ (1, 0, 1)$
-        & $\lambda(\xx) = \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
+        & \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
         \bottomrule

### 2025-02-23 paper/main.tex
fix

@@
         & $-(1, 0, 1)$
-        & \frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
+        & $\frac{11}{4}\left(\frac{x-x_{0, d}}{x_{e, d} - x_{0, d}}\right)$\\
         Ventral region, middle ventricle    
         & $\ \ \ (1, 0, 1)$
-        & \frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
+        & $\frac{1}{2}\left(1 - \frac{x-x_{0, v}}{x_{e, v} - x_{0, v}}\right)$ \\
         \bottomrule

### 2025-02-24 paper/main.tex
discussion and appendix edits, update bib

@@
 The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
-except at the anterior/posterior boundary $\Gamma_p$.
+except at the anterior/posterior boundary $\Gp$.
 At the anterior/posterior boundary, we permit the solute concentration to be advected into
@@
 We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
-For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM) elements for the velocity.
+For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM)
+elements for the velocity.~\cite{Brezzi1985TwoProblems, Nedelec1986AIR3}
 The BDM elements have degrees of freedom associated with integral moments of the
-velocity component normal to the facets of elements~\cite{Brezzi1985TwoProblems},
+velocity component normal to the facets of elements,
 thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
@@
 is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.
-Since the divergence of the velocity is a subspace of the pressure space for this scheme,
+Since the divergence of the velocity space is a subspace of the pressure space for this scheme,
 the divergence-free condition of the velocity is satisfied exactly on each
@@
 \Cref{fig:fig4}, as the model and the fish have different duct diameters.
-
-\lyng{HH: Quantify differences in terms of percentage changes in the
-final mean concentration values, maybe with a bar plot?}
 \begin{figure}[H]
@@
 The use of slip boundary conditions is motivated by experimental observations of the
-flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
-It has been observed, both previously and in this work, that the fluid velocity increases
-towards the wall~(\Crefpanels{fig:fig1}c).
-Using slip boundary conditions allows for this behavior.
-A couple of previous continuum model simulation studies of
-cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
-have modeled cilia as body forces. We chose to model the cilia as a force exerted tangentially on the boundary.
-First, we deem this a good representation of the real nature of cilia,
-since they are in reality microscale structures confined to the ventricular walls that
-generate flow through collective motion. Second, it avoids the need of excessive mesh
+flow field in zebrafish embryo brain ventricles, both previously and in this work, in which
+the fluid velocity increases towards the
+wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. Slip boundary
+conditions allow for this behavior, in contrast to a noslip condition where the velocity
+has to go to zero at the wall.
+
+As opposed to a couple of previous continuum model simulation studies of
+cilia-mediated flow where cilia were represented by body
+forces,~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
+we chose to model the cilia as a force
+exerted tangentially on the boundary.
+We deem this a good representation of the real nature of cilia,
+since they are microscale structures confined to the ventricular walls that
+generate flow through collective motion. Furthermore, it avoids the need of mesh
 refinement near the ciliated boundaries in the case that a
@@
 
-In our CSF flow model, the ciliated boundaries are homogeneous,
+The ciliated boundaries in our CSF flow model are regionally homogeneous,
 whereas in reality, cilia populate the ventricle walls in a
-heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneous spatial
-arrangement of cilia, both in location and beating direction,
+heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneous
+arrangement of cilia, both in location, beating direction and beating frequency,
 has been shown to enhance particle clearance in airway cilia arrays
-in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}. Incorporating spatial arrangement heterogeneity
-in our model could possibly result in different transport timescales,
+in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
+Incorporating spatial arrangement heterogeneity in our model could possibly
+result in different transport timescales,
 but we would not expect notable changes to the general trends of the macroscopic
@@
 On the other hand, introducing more heterogeneous beating directionality could
-alter the transport timescales as well as the directionality. In our model, all of the applied cilia
+alter the transport timescales as well as the directionality.
+In our model, all of the applied cilia
 tangential traction is aligned with the rostrocaudal axis, and more heterogeneity
@@
 left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry,
-Sawamoto2006NewBrain}. Although these studies were mostly on spatial scales resolving individual cilia,
+Sawamoto2006NewBrain}.
+Although these studies were mostly on spatial scales resolving individual cilia,
 we could envision the same effects in our continuum model,
@@
 
-We used an advection-diffusion equation to simulate protein transport in the brain ventricles.
-Except for where we imposed a normal pressure boundary condition on the CSF flow,
+To simulate protein transport in the brain ventricles, we numerically solved
+an advection-diffusion equation. Except for where we imposed a normal pressure
+boundary condition on the CSF flow,
 we imposed a no-flux condition on the concentration. Imposing a pressure-driven
@@
 and the advective transport then requires handling of in- and outflux boundary conditions.
-Reflecting our assumption that the ventricular system is closed, we set boundary conditions such
-that the total mass is conserved in the limit that the timestep size is zero.
-We handle the outflux by leaving the advective flux term as an unknown in the weak formulation
-of the advection-diffusion equation. This has been referred to with different names in previous works,
-names such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition},
+We set boundary conditions such that the total mass is conserved in the
+limit that the timestep size is zero, reflecting our assumption that the
+ventricular system is closed.
+We handled the outflux by leaving the advective flux term as an unknown in the weak formulation
+of the advection-diffusion equation. This has been referred to with different names
+in previous works, names such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition},
 the ``no boundary condition"~\cite{Griffiths1997TheCondition}, and the 
@@
 In leaving the advective flux term in the weak form we are lacking a boundary condition,
-so the approach seems problematic in the continuous sense of the problem.
+which is problematic in the continuous sense of the problem.
 However, the discrete problem is well-posed, because the approach represents
@@
 
-On the inflow boundary, we applied an approximate periodic boundary condition by setting
+Our approach can be interpreted as an approximate periodic boundary condition, where we set
 the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous
 timestep $n-1$. This is expected to be of low-order accuracy, and for high Péclet numbers,
-the boundary condition affects the concentration field in the vicinity of the in- and outflow boundaries
-due to large advective fluxes. For the simulation scenarios we considered, both in terms of model parameters
-and time span, the photoconversion region where solute originates is far enough away from the in- and outflow
+the boundary condition affects the concentration field in the vicinity of the
+in- and outflow boundaries
+due to large advective fluxes. For the simulation scenarios we considered,
+both in terms of model parameters
+and time span, the photoconversion region where solute originates
+is far enough away from the in- and outflow
 boundaries for the flux boundary condition to not significantly impact the results. Nevertheless,
@@
 A possible improvement to the in- and outflow boundary conditions we employed would be
-to consider a 3D-0D coupling of the in- and outflow boundaries using ordinary differential equations,
-similar to what has been done in cardiac modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
+to consider a 3D-0D coupling of the in- and outflow boundaries using
+ordinary differential equations,
+similar to what has been done in cardiac
+modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
 However, if the ventricular system in reality is a closed system,
@@
 traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = 2.5$ mPa applied to the
-boundary. A couple of previous simulation studies of cilia-mediated flow in brain ventricles have
-used a volumetric force density to represent the cilia. Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}
+boundary. Previous simulation studies of cilia-mediated flow in brain ventricles have
+used a volumetric force density to represent the cilia.
+Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}
 used a force expression that increased linearly from the wall to a maximum force density of
@@
 \end{equation*}
-which smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
+which is smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
 The length 15 \textmu m is the a typical length of cilia in human brain ventricles
@@
 With $l=5$ \textmu m, our traction parameter corresponds to a maximum force density of
-$f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with $f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$
+$f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$
 used by Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}.
-We note that they based $f_{\mathrm{max}}$ on reconstructions of flow velocities in murine brain ventricles.
+We note that they based $f_{\mathrm{max}}$ on reconstructions of
+flow velocities in murine brain ventricles.
 
@@
 e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
-($\mathbb{P}_2-\mathbb{P}_1$ elements) or lower-order enriched elements~\cite{Brezzi2011MixedMethods},
-such as the mini-element ($\mathbb{P}_1-\mathbb{P}_1$ with a velocity stabilization).
-Here, $\mathbb{P}_k$ is the set of continuous Lagrange polynomials of order $k$.
+($P_2-P_1$ elements) or lower-order enriched
+elements~\cite{Brezzi2011MixedMethods},
+such as the mini-element ($P_1-P_1$ with a velocity stabilization).
+Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
+than or equal to $k$.
 We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
 since numerical experiments proved that a divergence-free velocity field was
-paramount to attain a stable discretization of the advection-diffusion equation
-in advection-dominated regions. Using conventional Taylor-Hood elements for the Stokes equations,
+fundamental to attain a stable discretization of the advection-diffusion equation
+in advection-dominated regions. Using conventional
+Taylor-Hood elements for the Stokes equations
 stability of the advection-diffusion discretization either
@@
 hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization
-method~\cite{Franca1992StabilizedModel} instead of the current DG method.
+method~\cite{Franca1992StabilizedModel}, which is why we also opted for a DG method
+for the advection-diffusion equation.
 Probing numerical values of the divergence of
@@
 be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
-or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers, Bertoluzza2017BoundaryHemodynamics}.
+or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
+Bertoluzza2017BoundaryHemodynamics}.
 
@@
 
-We will consider the function spaces $\VV$ and $Q$ based on the
-Sobolev spaces $\mathbf{H}^1(\mathrm{div}; \Omega)$ and $L^2(\Omega)$,
-respectively, defined as 
+To derive weak formulations of the continuous problem defined by the Stokes
+equations~\Cref{eq:appendix_stokes_eqs}, we consider the function space
 \begin{align*}
-    L^2(\Omega) &= \bigg\{p \ : \ \intO{p^2} < \infty\bigg\} \\
-    \mathbf{H}^1(\mathrm{div}; \Omega)
-    &= \bigg\{\uu \ : \ \uu\in\mathbf{L}^2(\Omega), \nabla\cdot\uu\in L^2(\Omega)\bigg\}.
+    \VV &= \bigg\{\vv \ : \ \vv\in\mathbf{H}^1(\Omega),
+    \vv\cdot\nn=0 \ \mathrm{on} \ \Gamma\setminus\Gp\bigg\},
 \end{align*}
-Bold-faced characters for a space denotes a $d$--dimensional vector space,
+for the velocity and $Q=L^2(\Omega)$ for the pressure.
+Here $\Gp$ is the anterior/posterior boundary where we impose a normal pressure
+boundary condition for the model versions that consider fluid motion induced by
+cardiac pulsations. Bold-faced characters for a space denotes a $d$--dimensional vector space,
 where $d$ is the spatial dimension of $\Omega$. For example,
 $\mathbf{H}^1(\Omega) = [H^1(\Omega)]^3$ if $\Omega$ is three-dimensional.
-We will consider $p\in Q=L^2_0(\Omega)$, with subscript 0 meaning
-that $\intO{p} = 0$, and $\uu\in\VV$ with
-\begin{equation*}
-    \VV =  \bigg\{\vv \ : \ \vv\in\mathbf{H}^1(\mathrm{div}; \Omega),
-    \vv\cdot\nn=0 \ \mathrm{on} \ \Gamma\setminus\Gamma_{\mathrm{io}}\bigg\}.
-\end{equation*}
-Here $\Gamma_{\mathrm{io}}$ denotes an in- or outflow boundary.
-
-\mk{
-You should be careful here. The H(div) functions do not have a
-well defined gradient (and in turn $\beps$). However, for the derivations of
-the continuous problem you don't need H(div). I would derive all the weak forms
-in $V = \left\{ v\in H^1, v\cdot n = \text{on} \Gamma\right\}$. Then in A.2 you say we
-chose spaces $V_h$ which are are not conforming, i.e. it does not hold that $V_h\subset V$.
-Instead you have $V_h\subset H(div)$. Reasons is better mass csrv and as a
-bonus the bcs can be enforced strongly. Note that H(div) functions can have
-jumps in tangential components on surfaces in $\Omega$. Then introduce the discrete weak form.  
-}
+
 To derive a weak formulation of the Stokes equations~\Cref{eq:appendix_stokes_eqs},
@@
 Further steps depend on the boundary conditions applied,
-which is different for the three model versions we consider.
-Before going through the different model versions, let us introduce
-some notation used in defining slip boundary conditions. We make use of a decomposition
+which is different for the three model versions we consider in this paper.
+Before proceeding, let us introduce some notation used in defining the
+slip boundary conditions. We make use of a decomposition
 of any vector $\vv$ on the boundary $\Gamma$ into its normal and tangential components,
@@
 rendering flow features in the $y$-direction unobservable.
-Next, we consider the way of handling the stress boundary integral for each model version.
+In the following, we consider the way of handling the stress
+boundary integral for each model version successively.
 
@@
 \end{subequations}%
-on the boundary $\Gamma=\Gamma_c\cup\Gamma_s$. The boundary $\Gamma_s$ is a free-slip boundary,
+on the boundary $\Gamma=\Gc\cup\Gs$. The boundary $\Gs$ is a free-slip boundary,
 where we impose the free-slip condition~\Cref{eq:modelA_full_slip_BC}.
@@
 \end{equation}
-In a later section, we will discretize the weak formulation
-of the Stokes equations with Brezzi-Douglas-Marini
-finite elements~\cite{Brezzi1985TwoProblems}. These elements are
-defined through integral moments of the normal component of a
-variable on the facets of an element, we can strongly enforce
-the value of $\uu\cdot\nn$ and thus the boundary
-condition~\Cref{eq:modelA_slip_BC_impermeability}.
-Consequently, the test function counterpart $\vv\cdot\nn$ vanishes
-on the boundary, and the term~\Cref{eq:boundary_integral_BC_normal}
-is therefore dropped from the weak form. As a result, for the cilia-only/no-cardiac model,
+Since $\Gp=\emptyset$ in this model version, and the term~\Cref{eq:boundary_integral_BC_normal}
+vanishes owing to the construction $\VV$. As a result, for the cilia-only/no-cardiac model,
 the weak form of the momentum equation takes the following form:
@@
 Consequently, assembly of our discretization of the  equations~\Cref{eq:stokes_weak_modelA}
-into a linear equation system $\mathbf{A}\xx=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
+into a linear equation system $\mathbf{A}\mathbf{x}=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
 To ensure existence of solutions, we orthogonalize the right-hand side vector $\mathbf{b}$ with
@@
 
-The tangential stresses $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represent the cilia
+The tangential traction $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represents the cilia
 motion differ for the cilia regions. We heuristically determined the constant $\tau= 0.65$ mPa
@@
 previous work~\cite{Olstad2019CiliaryDevelopment}, we apply sinusoidal forcing.
-The boundary $\Gamma_p$ has two separate regions: one located on the
-anterior ventricle and one on the posterior ventricle~(\Cref{fig:fig1}\fixme{d}, blue markers).
+The boundary $\Gp$ has two separate regions: one located on the
+anterior ventricle and one on the posterior ventricle~(\Crefpanels{fig:fig1}{d}, blue markers).
 For the normal pressure boundary condition, we set $\Tilde{p}(t) = 0$ on the anterior part and
@@
 where $\Gamma = \Gc\cup\Gs\cup\Gp$ is the boundary of $\Omega$.
-The quantities $\btau$ and $\Tilde{p}(t)$ are as introduced in
-the sections of the other flow model versions. We handle the boundary
+The quantities $\btau$ and $\Tilde{p}(t)$ have been introduced in
+the previous sections covering the other flow model versions. We handle the boundary
 conditions~\Cref{eq:slip_BC_modelC} and~\Cref{eq:freeslip_BC_modelC}
 as introduced for the cilia-only/no-cardiac model, and the boundary
-condition~\Cref{eq:pressure_BC_modelC} is applied as discussed in the section
-on the cardiac-only/no-cilia model. The abstract weak formulation for 
+condition~\Cref{eq:pressure_BC_modelC} as introduced for the cardiac-only/no-cilia model.
+The abstract weak formulation for 
 the baseline model is then: find $(\uu,\, p)\in\VV\times Q$ such that
@@
 We will outline the discretization of the weak
-formulation~\Cref{eq:abstract_weak_form_modelC,eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
+formulation~\Cref{eq:abstract_weak_form_modelC,
+eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
 of the Stokes equations for the baseline model. A similar approach can
@@
 We rewrite the weak form in terms of the discretized variables,
-denoted with the subscript $h$:
+denoted with the subscript $h$, on the discrete domain $\Omega_h$:
 \begin{subequations}
@@
 \end{subequations}%
-Our choice for the discrete spaces $\VV_h$ and $Q_h$ are finite elements
-of the Brezzi-Douglas-Marini family~\cite{Brezzi1985TwoProblems} and
-discontinuous Galerkin elements, respectively. Application of this scheme
+Our choice of discretization are finite elements
+of the Brezzi-Douglas-Marini (BDM) family~\cite{Brezzi1985TwoProblems, Nedelec1986AIR3}
+for the velocity
+space and discontinuous Lagrange polynomial elements for the pressure. We refer to the latter
+as discontinuous Galerkin (DG) elements. We define
+\begin{align*}
+    {\VV}_h &= \Big\{\vv_h : \vv_h\in\mathbf{H}(\mathrm{div});
+    \vv_h\vert_K\in\big[P_k\big]^d;
+    \forall K\in\Omega_h;
+    \vv_h\cdot\nn=0 \ \text{on } \Gamma\setminus\Gp\Big\},\\
+    Q_h &= \Big\{q_h : q_h\in L^2;  q_h\vert_K\in P_{k-1}; \forall K\in\Omega_h\Big\},
+\end{align*}
+where $P_k$ is the space of polynomials of degree less than or equal to $k$.
+The BDM family of elements have degrees of freedom
+associated with integral moments of vector components normal to facets of the mesh,
+and is therefore non-conforming. However, the BDM-DG is $\mathbf{H}(\mathrm{div})$
+conforming and thus exactly mass-conserving, because the continuity equation can be satisfied
+in every computational mesh cell due to the fact that $\nabla\cdot\VV_h\subset Q_h$.
+Moreover, control of normal components of $\uu_h$ conveniently 
+lets us enforce the impermeability condition $\uu_h\cdot\nn=0$ strongly.
 requires a stabilization of the bilinear form $\mathcal{A}(\uu_h, \vv_h)$.
+
+Because the elements of $\VV_h$ define the normal components of $\uu_h$,
+continuity in tangential components of $\uu_h$ on interior facets of
+the mesh is ensured through stabilization
+of the discrete weak form~\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}.
 We apply the stabilization outlined in Hong~\emph{et al.}~\cite{Hong2016AEquations}.
@@
     \mathcal{A}_{\mathrm{stab}}(\uu_h, \vv_h) &=
-    \sum_{k\in K}\intF{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}
+    \sum_{f\in \mathcal{F}}\int_f{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}
     \cdot\jump{P_{\nn}(\vv_h)}}\\
-    &-\sum_{k\in K}\intF{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}
-    -\sum_{k\in K}\intF{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}
+    &-\sum_{f\in \mathcal{F}}\int_f{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}
+    -\sum_{f\in \mathcal{F}}\int_f{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}
 \end{align*}
 to the discrete weak formulation~\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC},
-where $\mathcal{F} = \{\mathcal{F}_k : k\in K\}$ is the set of all interior facets
-$\mathcal{F}_k$ of the computational mesh. The parameter $\gamma>0$ is
-introduced to penalize jumps in the tangential components of the velocity
-across facets, wheras $h$ is the cell diameter of a mesh cell,
+where $\mathcal{F}$ is the set of all interior facets of the computational mesh.
+The parameter $\gamma>0$ penalizes jumps in the tangential components of the velocity
+across facets, whereas $h$ is the cell diameter of a mesh cell,
 defined as the maximal distance between two points in a cell.
@@
 \begin{align*}
-    \Gin  &= \bigg\{\xx\in\Gamma : \uu(\xx, t)\cdot\nn(\xx) < 0 \bigg\}, \\
-    \Gout &= \bigg\{\xx\in\Gamma : \uu(\xx, t)\cdot\nn(\xx) > 0 \bigg\},
+    \Gin  &= \Big\{\xx\in\Gamma : \uu(\xx, t)\cdot\nn(\xx) < 0 \Big\}, \\
+    \Gout &= \Big\{\xx\in\Gamma : \uu(\xx, t)\cdot\nn(\xx) > 0 \Big\},
 \end{align*}
@@
 The space $W_h$ is constructed with finite elements with
-discontinuous linear Lagrange polynomial basis functions,
-allowing for discontinuities in the discrete solution across element edges.
-To achieve a stable discretization with these elements, we add the stabilization
+discontinuous Lagrange polynomial basis functions:
+\begin{equation}
+    W_h = \Big\{w_h : w_h\in L^2;  w_h\vert_K\in P_k; \forall K\in\Omega_h\Big\}.
+\end{equation}
+These elements allow for discontinuities in the discrete solution across element edges.
+To ensure a stable discretization with these elements, we add the stabilization
 \begin{equation}
@@
         a_{\mathrm{stab}}(c_h, \phi_h)
-        = &\sum_{k\in K}\intF{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
-        +\sum_{k\in K}\intF{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
-         -&\sum_{k\in K}\intF{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
-         -\sum_{k\in K}\intF{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
+        = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
+        +\sum_{f\in \mathcal{F}}\int_f{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
+         -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
+         -\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
     \end{aligned}\label{eq:SIP_stabilization}
 \end{equation}
-\mk{
-Above and also in weak form of BDM Stokes there should not be the sum over elements.
-The sum is over facets. The way it is written you would include each interior facet twice.
-}
 to the discrete weak formulation, where
@@
 we have by construction that the velocity is divergence-free,
-owing to the identity $\nabla\cdot(\nabla\times\mathbf{F}) = 0$ for
-an arbitrary vector field $\mathbf{F}$. The pressure was defined as
+owing to the identity $\nabla\cdot(\nabla\times\bm{F}) = 0$ for
+an arbitrary vector field $\bm{F}$. The pressure was defined as
 \begin{equation}

### 2025-02-24 paper/main.tex
minor fix

@@
 \end{equation*}
-is used to upwind the velocity $\uu_h$, with the velocity upwinded with respect to a
-facet $\mathcal{F}_k$. The stabilization parameter $\alpha>0$ must be chosen
+is used to upwind the velocity $\uu_h$ with respect to a
+facet. The stabilization parameter $\alpha>0$ must be chosen
 large enough to achieve stability. The average and jump operators used
@@
 pressure boundary condition
-amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a
+amplitude $A$. The choice of $A=1.5$ mPa was used since: (i) it yields a
 maximum velocity magnitude

### 2025-02-24 paper/main.tex
discussiond and conclusion

@@
 instead of a single cilium per cell -- the former can be found in
-mammalian ependymal cells -- will generate much stronger velocities.
+mammalian ependymal cells -- will generate stronger velocities.
 Hence advection may be more dominant in those situations.
-However, in large brains such as the human brain, cilia beating will
-only contribute to flow in localized regions of very high proximity to the ventricular walls,
-while blood vessel pulsations, respiration and CSF secretion will generate a
-pulsatile bulk flow in the central regions of the ventricles~\cite{Siyahhan2014FlowVentricles}.
-Based on this, cilia probably play an important role in regulating the
-amount of substances close to the ventricular walls, similar to coral
+
+In large brains such as the human brain, we presume ciliary beating mostly 
+contributes to flow in localized regions proximal to the ventricular walls due to
+the microscopic length of the cilia.
+Although the precise mechanisms of intraventricular flow are still debated,
+much evidence indicate that blood vessel pulsations, respiration, CSF secretion
+and brain motion induce the pulsatile bulk flow in the central
+regions of the ventricles~\cite{Vinje2019RespiratoryMeasurements,
+Siyahhan2014FlowVentricles, Linninger2005PulsatileBrain, Enzmann1992BrainImaging,
+Kurtcuoglu2007ComputationalSylvius}.
+In human brains, cilia therefore probably play an important role in regulating the
+amount of substances like exosomes close to the ventricular walls, similar to coral
 reefs, where it has been observed that cilia are primary regulators of
 oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}.
-But for zebrafish embryos, the ventricles are so small that the flow
+Flow mediated by cilia indeed serves such a purpose in nodal flow at early
+developmental stages of the brain~\cite{Hirokawa2006NodalAsymmetry}, and the discovery
+of a cilia-driven flow network in rodent brains suggest such selective
+transport~\cite{Faubel2016Cilia-basedVentricles}.
+
+On the other hand, for the zebrafish embryos we studied,
+the ventricles are so small that the flow
 generated by ciliary motion is of the scale of the geometry, and thus not
-only contributes to near-wall flow dynamics, but flow in the entire ventricular system.
+only contributes to near-wall flow dynamics, but flow in the entire ventricular
+system~\cite{Olstad2019CiliaryDevelopment}.
 To date, motile-cilia deficiency has been associated with altered brain function
-in the zebrafish and ventricular enlargement in zebrafish, rodents and humans.
+in the zebrafish, dysfunctional establishment of left-right symmetry,
+and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004Cilia-relatedDiseases,
+Youn2018PrimaryDiseases, Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}
 Yet the molecular mechanisms leading to these alterations are poorly understood.
@@
 
-\lyng{HH: Refer to Eichele et al. article discussion about role of cilia.}
-
-\subsection*{Limitations and further work}
+\subsection{Limitations and further work}
 The model presented has certain limitations. Future work could consider:
@@
     \item time-varying cilia?
-    \item improved advection-diffusion equation BCs
-    \item Modeling deformation of the ventricles
+    \item improved advection-diffusion equation influx/outflux BCs, or instead
+    modeling deformation of a closed ventricular system. 
     and investigating how the arising flow compares with pulsatile flow observed in experiments
@@
 \end{itemize}
-
-\fixme{Based on our conclusion that advection drives transport of larger proteins, could
-we make some bold claims about advective transport of exosomes/extracellular vesicles in the
-ventricles, and the importance of this?}
 
@@
 zebrafish brain ventricles based on finite element methods.
-A realistic brain ventricles geometry from medical imaging was used to perform a
-computational study with the presented model. The flow model reproduces
+A realistic ventricular geometry from medical imaging was used to perform a
+computational study. The flow model reproduces
 the experimentally observed flow features of cilia-mediated cerebrospinal fluid
@@
 we estimated how slowly or rapidly molecules of varying size are transported in
-the ventricles. Simulations indicate that cilia-driven advection is important
-for transport of larger molecules. 
-The numerical model was validated with experiments, measuring the movement of
+the ventricles. 
+The numerical model was validated with in vivo experiments, measuring the movement of
 a photoconverted fluorescent protein in zebrafish brain ventricles,
@@
 We observed good alignment between computational and experimental results.
-Experimental results indicate that cilia only affect the local distribution of small proteins,
-while most of the transport is governed by diffusion.
+Simulations indicate that cilia-driven advection is important
+for transport of larger molecules, whereas diffusion accounts for most of
+the transport of smaller molecules. 
+Experimental results support the conclusion that cilia only affect the
+local distribution of small proteins,
+while most of their transport is governed by diffusion.
 
@@
 $\bsigpar = \btau(\xx, \rr) = \tau\lambda(\xx) P_{\nn}(\rr)$,
-where the parameter $\tau=\num{6.5e-4}$ Pa was used to control the magnitude
+where the parameter $\tau=0.65$ mPa was used to control the magnitude
 of the tangential stresses, and chosen by calibrating simulated velocity
@@
 
-We choose $\mathbf{r} = \rr^+ = (1, 0, 1)$ or $\mathbf{r} = \rr^- = -(1, 0, 1)$
+We choose $\rr = \rr^+ = (1, 0, 1)$ or $\rr = \rr^- = -(1, 0, 1)$
 to impose forces perpendicular to the $y$-axis.
@@
 We observe that, in this case with slip boundary conditions on the entirety of
-the boundary $\Gamma$, the vector $(\uu, p)=(\mathbf{0}, C)$ for any real
-constant $C$ satisfies the equations.
-The system~\Cref{eq:stokes_weak_modelA} is thus singular with a one-dimensional nullspace
+the boundary $\Gamma$, for any real constant $C$ the vector
+$(\uu, p)=(\mathbf{0}, C)$ satisfies the equations.
+Hence the system~\Cref{eq:stokes_weak_modelA} is singular with a one-dimensional nullspace
 of constant pressures.
@@
 space and discontinuous Lagrange polynomial elements for the pressure. We refer to the latter
-as discontinuous Galerkin (DG) elements. We define
+as discontinuous Galerkin (DG) elements. For all cells $K$ of the computational mesh $\Omega_h$,
+we define
 \begin{align*}
@@
 where $\mathcal{F}$ is the set of all interior facets of the computational mesh.
-The parameter $\gamma>0$ penalizes jumps in the tangential components of the velocity
-across facets, whereas $h$ is the cell diameter of a mesh cell,
-defined as the maximal distance between two points in a cell.
-The semi-discrete weak formulation of the Stokes equations reads:
+The first term of $\mathcal{A}_{\mathrm{stab}}$ penalizes jumps
+in the tangential components of the velocity
+across interior facets, where the penalty parameter $\gamma>0$ must be chosen large enough
+to achieve stability. For convergence the penalization term
+scales with the cell diameter of a mesh cell $h$,
+defined as the maximal distance between two points in a cell. The other two terms
+of $\mathcal{A}_{\mathrm{stab}}$ are added to ensure coercivity and symmetry of
+the bilinear form, such that the problem is well-defined.
+
+Including the stabilization outlined above, the semi-discrete weak formulation of
+the Stokes equations reads:
 find ($\uu_h, p_h$)$\in$($\VV_h, Q_h$) such that
@@
         = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
-        +\sum_{f\in \mathcal{F}}\int_f{\jump{\phi_h}\cdot\jump{c_h \hat{u}_h}}  \\
+        +\sum_{f\in \mathcal{F}}\int_f{\jump{c_h \hat{u}_h}\cdot\jump{\phi_h}}  \\
          -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
@@
 is used to upwind the velocity $\uu_h$ with respect to a
-facet. The stabilization parameter $\alpha>0$ must be chosen
-large enough to achieve stability. The average and jump operators used
+facet. Similar to the stabilization employed for the Stokes equations, the first two terms
+of \Cref{eq:SIP_stabilization} penalize jumps in the concentration flux across interior facets.
+The stabilization parameter $\alpha>0$ must be chosen
+large enough to achieve stability. The two last terms in $a_{\mathrm{stab}}$ are
+added to preserve coercivity and symmetry of the bilinear form. The average and jump operators used
 in~\Cref{eq:SIP_stabilization} are defined, respectively, as

### 2025-02-25 paper/main.tex
update figures 5 and 6 and plot code

@@
     in the 6 ROIs.
-    \mk{MK: How do the different geoemtries compare in terms of volume,
-    areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
+    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
+    and the total force applied. In each region, the force $F_{\mathrm{original}}$ 
+    applied on the original mesh is the baseline of 100\%,
+    to which the force $F_i$ of the other mesh versions are compared, where $i$ denotes
+    the case. The bars for the four shrunk scenarios thus
+    display $F_i/F_{\mathrm{original}}\cdot 100\%$.}
     \label{fig:fig6}

### 2025-02-25 src/plot_cilia_force_bars.py

@@ -1,7 +1,7 @@
-import numpy  as np
+import numpy     as np
+import pandas    as pd
+import colormaps as cm
 import matplotlib.pyplot as plt
-
-plt.style.use('petroff10')
 
 # Set matplotlib properties
 plt.rcParams.update({
@@ -10,13 +10,18 @@ plt.rcParams.update({
     "axes.spines.right" : False
 })
 
-save_fig = 1
+save_figs = 1
+regions = ['Dorsal', 'Ventral', 'Anterior', 'Total']
+versions = ['Original', 'Shrunk fore-mid', 'Shrunk middle', 'Shrunk mid-hind', 'Fore+middle+hind']
 
-import colormaps as cm
+
+##########################
+##  FIGURE 5 BAR PLOT   ##
+##########################
 green = cm.dark2_3.colors[0]
 orange = cm.dark2_3.colors[1]
 purple = cm.puor_4.colors[3]
-colors = [green, orange, purple, 'k']
+colors = [green, purple, orange, 'k']
 
 fig, ax = plt.subplots(figsize=[11.35, 10])
 idx = [1, 2, 3, 4]
@@ -27,13 +32,59 @@ forces = np.array([3.64E-06, 2.41E-06, 9.78E-07, 7.03E-06])*1e6 # Forces in micr
 hatches = ['/', '\\', 'x', '']
 bars = ax.bar(x=idx, height=forces, width=0.5, color=colors, hatch=hatches)
 
-ax.set_title('Cilia population contribution', fontsize=50, pad=30)
-ax.set_ylabel(r'Tangential force $\mathrm{[\mu N]}$', fontsize=45, labelpad=25)
+ax.set_title('Regional cilia contribution', fontsize=52, pad=20)
+ax.set_ylabel(r'Tangential force $\mathrm{[\mu N]}$', fontsize=48, labelpad=25)
 ax.set_yticks(range(1, 8))
 ax.set_xticks(idx)
-ax.set_xticklabels(['Dorsal', 'Ventral', 'Anterior', 'Total'], fontsize=45)
-ax.tick_params(axis='both', labelsize=45, pad=25)
+ax.set_xticklabels(regions, fontsize=48)
+ax.tick_params(axis='both', labelsize=48, pad=25)
 fig.tight_layout()
 
-if save_fig: fig.savefig('../output/illustrations/compare_cilia/cilia_forces_bar_plot.png')
[…]

### 2025-02-25 src/plot_compare_simulations_cilia_regions.py

@@ -85,7 +85,7 @@ import colormaps as cm
 green = cm.dark2_3.colors[0]
 orange = cm.dark2_3.colors[1]
 purple = cm.puor_4.colors[3]
-colors = ['k', green, orange, purple]
+colors = ['k', green, purple, orange]
 
 # Plot concentrations
 idx = 0
@@ -114,30 +114,5 @@ plt.tight_layout()
 plt.subplots_adjust(hspace=0.30)
 save_figs = 1
 if save_figs: fig_c.savefig(f"../output/illustrations/compare_cilia/concentrations_model{model_version}.png")
-
-
-cols = range(4)
-final_c = pd.DataFrame(index=ROI_tags, columns=cols)
-for i, c_bar in enumerate([c_bar_original, c_bar_dorsal, c_bar_ventral, c_bar_telenc]):
-    final_c[i] = c_bar[-1, :]
-
-fig_bars, ax_bars = plt.subplots(num=4, figsize=[18, 8])
-final_c.reset_index(inplace=True)
-bars = final_c.plot.bar(x='index', y=cols,
-                         color=colors,
-                         ax=ax_bars, rot=True, width=0.75)
-hatches = ['', '\\', 'x', '/', '^']
-for bar_container, hatch in zip(bars.containers, hatches):
-    for bar in bar_container:
-        bar.set_hatch(hatch)
-
-ax_bars.set_xlabel("ROI number", fontsize=35, labelpad=25)
-ax_bars.set_ylabel(r"Final mean concentration $\bar{c}(T)$ [-]", fontsize=35, labelpad=50)
-ax_bars.tick_params(labelsize=35)
-ax_bars.get_legend().remove()
-# ax_bars.legend(labels=['Original', 'Fore', 'Middle', 'Hind', 'Fore+middle+hind'], loc='right', fontsize=32, frameon=True, fancybox=False, edgecolor='k')
-fig_bars.tight_layout()
-
-if save_figs: fig_bars.savefig(f"../output/illustrations/compare_cilia/final_concentrations_model{model_version}.png")
 
 plt.show()

### 2025-02-25 src/plot_compare_simulations_geometry.py

@@ -31,8 +31,7 @@ Author: Halvor Herlyng, 2024.
 
 # Set matplotlib properties
 plt.rcParams.update({
-    "text.usetex" : True,
-    "font.family" : "sans-serif",
+    "font.family" : "Arial",
     "axes.spines.top" : False,
     "axes.spines.right" : False
 })
@@ -123,7 +122,7 @@ green = cm.dark2_3.colors[0]
 orange = cm.dark2_3.colors[1]
 purple = cm.puor_4.colors[3]
 yellow = cm.puor_4.colors[1]
-colors = ['k', green, orange, purple, yellow]
+colors = ['k', green, purple, orange, yellow]
 print([colors[i]*255 for i in range(1, len(colors))])
 
 # Plot concentrations
@@ -134,9 +133,9 @@ for row_idx in range(ax_c.shape[0]):
         ca_c = ax_c[row_idx, col_idx]
     
         ca_c.plot(times, c_bar1[:, idx], color=colors[0], label='Original', linewidth=lw)
-        ca_c.plot(times, c_bar2[:, idx], color=colors[1], linestyle='--', marker='o', markevery=2000, label='Fore', linewidth=lw, markersize=msize)
-        ca_c.plot(times, c_bar3[:, idx], color=colors[2], linestyle='--', marker='^', markevery=2000, label='Middle', linewidth=lw, markersize=msize)
-        ca_c.plot(times, c_bar4[:, idx], color=colors[3], linestyle='--', marker='s', markevery=2000, label='Hind', linewidth=lw, markersize=msize)
+        ca_c.plot(times, c_bar2[:, idx], color=colors[1], linestyle='--', marker='o', markevery=2000, label='Shrunk fore-mid', linewidth=lw, markersize=msize)
+        ca_c.plot(times, c_bar3[:, idx], color=colors[2], linestyle='--', marker='^', markevery=2000, label='Shrunk middle', linewidth=lw, markersize=msize)
+        ca_c.plot(times, c_bar4[:, idx], color=colors[3], linestyle='--', marker='s', markevery=2000, label='Shrunk mid-hind', linewidth=lw, markersize=msize)
         ca_c.plot(times, c_bar5[:, idx], color=colors[4], linestyle='--', marker='p', markevery=2000, label='Fore+middle+hind', linewidth=lw, markersize=msize)
 
[…]

### 2025-02-25 src/plot_mean_concentration.py

@@ -51,12 +51,13 @@ f = 2.22
 dt = 1/f/20
 
 # Plot parameters
-save_fig = 1 # Save figures if set to 1, don't save if set to 0
+save_fig = 0 # Save figures if set to 1, don't save if set to 0
 lw = 6 # linewidth
 
 # Loop over molecules
-transport_data_filename = transport_dir + \
-    f"{tau_version}/{mesh_version}/log_model_{model_version}_{molecule}_DG1_pressureBC/data/c_hats.npy"
+transport_data_filename = '../output/transport/results/variable_tau+weak_PC/original/model_C_molecule_D2/data/c_hats.npy'
+# transport_dir + \
+# f"{tau_version}/{mesh_version}/log_model_{model_version}_{molecule}_DG1_pressureBC/data/c_hats.npy"
 
 # Load transport data: c_bars = the total concentration in each ROI
 with open(transport_data_filename, "rb") as file: c_bars = np.load(file) 

### 2025-02-25 src/plot_mean_concentration_and_time_to_threshold.py

@@ -52,7 +52,7 @@ f = 2.22
 dt = 1/f/20
 
 # Plot parameters
-save_figs = 1 # Save figures if set to 1, don't save if set to 0
+save_figs = 0 # Save figures if set to 1, don't save if set to 0
 lw = 8 # linewidth
 msize = 4 # marker size
 

### 2025-02-25 paper/main.tex
update figures, add force calculation

--- 2025-02-24 paper/main.tex
@@
 with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
+
+When studying how cilia paralysis and ventricular morphology affect intraventricular
+flow and transport, we calculate the magnitude of a tangential force $F$ 
+exerted by the cilia on a part $\mathcal{S}\subset\Gc$ of the ventricular surface as:
+\begin{equation}
+    F = \int_{\mathcal{S}}\sqrt{\btau\cdot\btau}\,\mathrm ds.
+    \label{eq:tangential_force_calculation}
+\end{equation}
 
@@
 impact and results in maximum speeds of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
-Of the total tangential force exerted by the cilia, ventral cilia in the middle ventricle
+Of the total tangential forces exerted by the cilia, ventral cilia in the middle ventricle
 contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
@@
     by imposing a zero tangential traction boundary condition in the respective region.
-    \textbf{b.} The total tangential force applied through the tangential traction
-    boundary condition in the three separate ciliated regions.
+    \textbf{b.} The total tangential force applied with the tangential traction
+    boundary condition in the three separate ciliated regions, as well as the total
+    (the sum of the three regions), calculated with \Cref{eq:tangential_force_calculation}. 
     \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
@@
 one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
-and the combination of the above three modifications (\Crefpanels{fig:fig6}{a}).
+and the combination of the above three modifications (\Crefpanels{fig:fig6}{a}). In these
+four modified geometries the volume is reduced by 3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively,
+comapred to the original geometry.
 We simulate CSF flow in the modified geometries with the baseline flow model
@@
 slower transport to the anterior ventricle (ROI 5),
-and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry.
+and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry
+(\Crefpanels{fig:fig6}{c}, shrunk fore-mid scenario). This is notwithstanding a
+9.5\% reduction in ventral cilia force magnitude
+(\Crefpanels{fig:fig6}{d}), which are the cilia that propel CSF and solute towards ROI 6.
 On the other hand, constricting the duct connecting the middle and the posterior ventricle
 leads to less transport into the posterior ventricle (ROI 6),
-and slightly more transport towards the anterior ventricle (ROI 5).
+and slightly more transport towards the anterior ventricle (ROI 5)
+(\Crefpanels{fig:fig6}{c}, shrunk mid-hind scenario).
 Faster transport to the anterior ventricle (ROI 5) and slower transport to the
-posterior ventricle (ROI 6) is also the case for the geometry with a shrunk middle ventricle.
-Additionally, for the latter configuration, the transport upstream of CSF flow towards the
+posterior ventricle (ROI 6) is also the case for the geometry with a
+shrunk middle ventricle.
+Here also the change in transport to ROI 6 is counter to expectation when comparing with
+ventral cilia forces, with transport reducing in spite of a 6.6\% increase in the
+ventral cilia forces.
+Additionally, for the shrunk middle configuration, the transport upstream of CSF flow towards the
 ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
@@
 Altogether, our results show that the geometry and width of the ventricular ducts matter
-for solute transport. This may explain why we observed larger differences
+for solute transport, with notable differences in transport from relatively small
+geometry modifications. This may explain why we observed larger differences
 in the cilia-deficient computational model compared to the experimental data in
@@
     in the 6 ROIs.
-    \mk{MK: How do the different geoemtries compare in terms of volume,
-    areas where cilia are active?} \lyng{HH: Good question, will add this information.}}
+    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
+    and the total force applied, calculated with \Cref{eq:tangential_force_calculation}.
+    In each region, the force $F_{\mathrm{original}}$ 
+    applied on the original mesh is the baseline of 100\%,
+    to which the forces $F_i$ of the other mesh versions are compared, where $i$ denotes
+    the cases fore-shrunk, middle shrunk, mid-hind shrunk, and the combination of the three.
+    The bars for the four shrunk scenarios thus
+    display $F_i/F_{\mathrm{original}}\cdot 100\%$.}
     \label{fig:fig6}
@@
 \subsection{Limitations and further work}
-The model presented has certain limitations. Future work could consider:
+The model presented has certain limitations. Future work could consider improving:
 \begin{itemize}
+    \item quantify cilia force parameter to avoid tuning
     \item spatial heterogeneity of the cilia, how this affects flow and transport
@@
     \item FSI: CSF flow coupled to 1D/2D/3D cilia structures.
+    \item any comments on experiments?
 \end{itemize}
@@
 
-\medskip
-\textbf{Data Availability Statement} \par
-The data and implementations presented in this paper are licensed under \fixme{LICENSE}
-and openly avalaible at \fixme{REPO-LINK}.
-
-\medskip
-\textbf{Conflict of Interest Disclosure} \par
-The authors declare no conflicts of interest.
-
-\medskip
-\textbf{Supporting Information} \par %Please delete the Suppporting Information statement
-%if it is not applicable. Please supply Supporting Information in another file.
-%Supporting information should not be provided in .tex format
-Supporting Information is available from the Wiley Online Library or from the author.
-
 % Acknowledgements
@@
 This work was funded by the Research Council of Norway (NJY FRIPRO grants 314189 and 353348).
+
+\medskip
+\textbf{Data Availability Statement} \par
+The data and implementations presented in this paper are licensed under \fixme{LICENSE}
+and openly avalaible at \fixme{REPO-LINK}.
+
+\medskip
+\textbf{Conflict of Interest Disclosure} \par
+The authors declare no conflicts of interest.
+
+\medskip
+\textbf{Supporting Information} \par %Please delete the Suppporting Information statement
+%if it is not applicable. Please supply Supporting Information in another file.
+%Supporting information should not be provided in .tex format
+Supporting Information is available from the Wiley Online Library or from the author.
 

### 2025-03-03 paper/main.tex
Formatting tweaks. This template still hurts my eyes.

@@
 
-\pagestyle{fancy}
-\rhead{\includegraphics[width=2.5cm]{vch-logo.png}}
-
-\title{The Role of Advection Versus Diffusion in Intraventricular Transport}
-
+%\pagestyle{fancy}
+%\rhead{}%\includegraphics[width=2.5cm]{vch-logo.png}}
+\pagestyle{plain} % MER
+
+\title{The role of advection versus diffusion in intraventricular transport}
+%
 \maketitle
-
+%
 % Author: Please give full first and last names for authors and
 % include * after the name of all corresponding authors
-
-\author{Halvor Herlyng*}
-\author{Ada J.~Ellingsrud}
-\author{Miroslav Kuchta}
-\author{Inyoung Jeong}
-\author{Marie E.~Rognes} \\
+%
+\author{Halvor Herlyng*},
+\author{Ada J.~Ellingsrud},
+\author{Miroslav Kuchta},
+\author{Inyoung Jeong},
+\author{Marie E.~Rognes}, 
 \author{Nathalie Jurisch-Yaksi*}
@@
 \begin{affiliations}
-H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
+\noindent H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
 Department of Numerical Analysis and Scientific Computing,
 Simula Research Laboratory, Kristian Augusts gate 23, 0164 Oslo, Norway\\
-Email Address: hherlyng@simula.no
-\\
-Dr.~M.~E.~Rognes\\
-K.~G.~Jebsen Center for Brain Fluid Research, Oslo, Norway
-\\
+Email Address: hherlyng@simula.no \\ 
+Dr.~M.~E.~Rognes \\
+K.~G.~Jebsen Centre for Brain Fluid Research, Oslo, Norway \\
 Dr.~I.~Jeong, Dr.~N.~Jurisch-Yaksi\\
@@
 \section{Introduction}
-Brain development and function depend on numerous regulatory processes,
-including the flow of cerebrospinal fluid
-(CSF). CSF is a clear liquid produced by the choroid plexus
-and the fluid flows through the ventricular system and subarachnoid space.
-By transporting growth factors, nutrients, neurotransmitters and metabolites
-and removing waste products, CSF regulates brain development and homeostasis.
-Disturbance of the CSF circulation can lead to brain disorders, such as
-hydrocephalus where accumulation of CSF often requires emergency surgical treatment.
+Brain development and function depend on numerous regulatory
+processes, including the flow of cerebrospinal fluid (CSF). CSF is a
+clear liquid produced by the choroid plexus and the fluid flows
+through the ventricular system and subarachnoid space.  By
+transporting growth factors, nutrients, neurotransmitters and
+metabolites and removing waste products, CSF regulates brain
+development and homeostasis.  Disturbance of the CSF circulation can
+lead to brain disorders, such as hydrocephalus where accumulation of
+CSF often requires emergency surgical treatment.
 

### 2025-03-03 paper/main.tex
Spell-check, move references up, and comment out boilerplate stuff.

@@
 is observed in animal models and humans with motile cilia deficiency,
-indiciating that the cilia play a crucial role for healthy brain functioning.
+indicating that the cilia play a crucial role for healthy brain functioning.
 
@@
 four modified geometries the volume is reduced by 3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively,
-comapred to the original geometry.
+compared to the original geometry.
 We simulate CSF flow in the modified geometries with the baseline flow model
@@
 affect solute distribution. Altogether, we present not only new findings on the role of
-diffusion and advection in intraventriuclar transport, but also provide a novel framework to
+diffusion and advection in intraventricular transport, but also provide a novel framework to
 study CSF flow and transport in complex geometries.
@@
 purely driven by diffusion. We also performed photoconversion experiments on cilia mutant
-zebrafish larva (\emph{smh}), observing statistically signifcant slower transport in 
+zebrafish larva (\emph{smh}), observing statistically significant slower transport in 
 ROIs 2 and 4. The results provide not only confidence in that our computational model
@@
 
-With an interest in assessing the impact of ventricular morphology on solute transprot,
+With an interest in assessing the impact of ventricular morphology on solute transport,
 we simulated transport on modified ventricular geometries.
@@
 a clear conservation of the ventricular system across vertebrates,
-there are also important considerations to take. These include (but are not limitied to)
+there are also important considerations to take. These include (but are not limited to)
 ventricular size and morphology, properties of ciliated cells,
@@
 \medskip
-\textbf{Acknowledgements} \par 
+\textbf{Acknowledgments} \par 
 Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
@@
 The data and implementations presented in this paper are licensed under \fixme{LICENSE}
-and openly avalaible at \fixme{REPO-LINK}.
+and openly available at \fixme{REPO-LINK}.
 
@@
 
+% References
+\medskip
+
+% Use the following code if you wish to generate your bibliography with BibTeX;
+% replace the string "MSP-template" below with the name(s) of
+% the BibTeX data base(s) you want to use.
+% The resulting bibliography-output (the content of the .bbl file)
+% must be pasted back into this file before submission.
+% Please also include your BibTeX data base file(s) in your submission
+% so that we can re-run BibTeX if necessary.
+%
+\bibliographystyle{MSP}
+\bibliography{ref}
+
+\newpage 
 %%--------------APPENDIX--------------%%
@@
 
-% References
-\medskip
-
-% Use the following code if you wish to generate your bibliography with BibTeX;
-% replace the string "MSP-template" below with the name(s) of
-% the BibTeX data base(s) you want to use.
-% The resulting bibliography-output (the content of the .bbl file)
-% must be pasted back into this file before submission.
-% Please also include your BibTeX data base file(s) in your submission
-% so that we can re-run BibTeX if necessary.
-%
-\bibliographystyle{MSP}
-\bibliography{ref}
-
-\textbf{References}\\
-1	((Journal articles)) a) A. B. Author 1, C. D. Author 2, Adv. Mater. 2006, 18, 1; b) A. Author 1, B. Author 2, Adv. Funct. Mater. 2006, 16, 1.\\
-2	((Work accepted)) A. B. Author 1, C. D. Author 2, Macromol. Rapid Commun., DOI: 10.1002/marc.DOI.\\
-3	((Books)) H. R. Allcock, Introduction to Materials Chemistry, Wiley, Hoboken, NJ, USA 2008.\\
-4	((Edited books or proceedings volumes)) J. W. Grate, G. C. Frye, in Sensors Update, Vol. 2 (Eds: H. Baltes, W. Göpel, J. Hesse), Wiley-VCH, Weinheim, Germany 1996, Ch. 2.\\
-5	((Presentation at a conference, proceeding not published)) Author, presented at Abbrev. Conf. Title, Location of Conference, Date of Conference ((Month, Year)).\\
-6	((Thesis)) Author, Degree Thesis, University (location if not obvious), Month, Year.\\
-7	((Patents)) a) A. B. Author 1, C. D. Author 2 (Company), Country Patent Number, Year; b) W. Lehmann, H. Rinke (Bayer AG) Ger. 838217, 1952.\\
-8	((Website)) Author, Short description or title, URL, accessed: Month, Year.\\
-9	…((Please include all authors, and do not use “et al.”))\\
+%% \textbf{References}\\
+%% 1	((Journal articles)) a) A. B. Author 1, C. D. Author 2, Adv. Mater. 2006, 18, 1; b) A. Author 1, B. Author 2, Adv. Funct. Mater. 2006, 16, 1.\\
+%% 2	((Work accepted)) A. B. Author 1, C. D. Author 2, Macromol. Rapid Commun., DOI: 10.1002/marc.DOI.\\
+%% 3	((Books)) H. R. Allcock, Introduction to Materials Chemistry, Wiley, Hoboken, NJ, USA 2008.\\
+%% 4	((Edited books or proceedings volumes)) J. W. Grate, G. C. Frye, in Sensors Update, Vol. 2 (Eds: H. Baltes, W. Göpel, J. Hesse), Wiley-VCH, Weinheim, Germany 1996, Ch. 2.\\
+%% 5	((Presentation at a conference, proceeding not published)) Author, presented at Abbrev. Conf. Title, Location of Conference, Date of Conference ((Month, Year)).\\
+%% 6	((Thesis)) Author, Degree Thesis, University (location if not obvious), Month, Year.\\
+%% 7	((Patents)) a) A. B. Author 1, C. D. Author 2 (Company), Country Patent Number, Year; b) W. Lehmann, H. Rinke (Bayer AG) Ger. 838217, 1952.\\
+%% 8	((Website)) Author, Short description or title, URL, accessed: Month, Year.\\
+%% 9	…((Please include all authors, and do not use “et al.”))\\
 
@@
 
-\begin{figure}
-\textbf{Table of Contents}\\
-\medskip
-  \includegraphics{toc-image.png}
-  \medskip
-  \caption*{ToC Entry}
-\end{figure}
+%% \begin{figure}
+%% \textbf{Table of Contents}\\
+%% \medskip
+%%   \includegraphics{toc-image.png}
+%%   \medskip
+%%   \caption*{ToC Entry}
+%% \end{figure}
 

### 2025-03-03 paper/main.tex
Request citations in Introduction.

@@
 \section{Introduction}
+
+% I1: What is the problem - from big picture to focus
 Brain development and function depend on numerous regulatory
-processes, including the flow of cerebrospinal fluid (CSF). CSF is a
-clear liquid produced by the choroid plexus and the fluid flows
-through the ventricular system and subarachnoid space.  By
-transporting growth factors, nutrients, neurotransmitters and
-metabolites and removing waste products, CSF regulates brain
-development and homeostasis.  Disturbance of the CSF circulation can
-lead to brain disorders, such as hydrocephalus where accumulation of
-CSF often requires emergency surgical treatment.
-
-Motion of CSF occurs through multiple physiological processes,
-including the beating motion of motile cilia lining the ventricular walls,
-CSF secretion by the choroid plexus, and pressure gradients generated
-by the cardiac cycle, respiration, and bodily movement. Motile cilia
-are microscopic hair-like structures that beat in a metachronal wave
-pattern to mediate fluid flow. Due to their microscopic size, ranging
-from 6 to 15 microns, the cilia contribute to flow primarily at the surface
-of the brain ventricles. In contrast, fluid flow induced by the 
-cardiac and respiratory cycles account for the bulk flow in the brain
-ventricles~\cite{Vinje2019RespiratoryMeasurements},
-as well as the CSF flow in the perivascular spaces.
-
-To date, it remains poorly understood how cilia contribute to the
-overall fluid flow and solute transport within the brain.
-These questions have been challenging to tackle due to technical
-limitations. Notably, cilia are microscopic and beat at high
-frequencies ranging from 10 to 30 Hz, while other fluid dynamic
-processes in the brain are slower and span larger volumes, making
-cilia dynamics challenging to monitor in vivo. Until now, most studies have
-analyzed one physical mechanism at a time, especially in mammals.
+processes, including the flow of cerebrospinal fluid
+(CSF)~\cite{CITATTION}. CSF is a clear liquid produced by the choroid
+plexus that flows through the ventricular system and subarachnoid
+space. By transporting growth factors, nutrients, neurotransmitters
+and metabolites as well as removing waste products, CSF regulates
+brain development and homeostasis~\cite{CITATTION}. Disturbance of the
+CSF circulation can lead to brain disorders, such as hydrocephalus
+where accumulation of CSF often requires emergency surgical
+treatment~\cite{CITATTION}.
+
+% MER: Add this to the paragraph above.
+%
+% This is particularly important since ventricular enlargement, known
+% as hydrocephalus, is observed in animal models and humans with
+% motile cilia deficiency, indicating that the cilia play a crucial
+% role for healthy brain functioning.
+
+% I2: What do we know about the problem?
+The flow of CSF in the ventricular system is driven by multiple
+physiological processes, including via the beating motion of motile
+cilia lining the ventricular walls, CSF secretion by the choroid
+plexus, and pulsatile pressure gradients generated by the cardiac
+cycle, respiration, neural activity, and bodily
+movement~\cite{CITATION}. Motile cilia are microscopic hair-like
+structures that beat in a metachronal wave pattern at frequencies of
+10--30 Hz~\cite{CITATION}. Given their microscopic size, ranging from
+6 to 15 microns, the cilia clearly contributes to flow near the
+ventricular surface~\cite{CITATION}. On the other hand, cardiac,
+respiratory and delta waves at lower frequencies induce pulsatile flow
+at scale in the brain ventricular system, subarachnoid space, and
+subarachnoid perivascular
+spaces~\cite{Vinje2019RespiratoryMeasurements, eide2024functional,
+  causemann2025insilico, fultz2019coupled}.
+
+%How the cilia contribute to overall CSF flow and solute transport
+%remains poorly understood however.
+
+%These questions have been challenging to tackle due to technical
+%limitations.
+
+% I3: What do we not know about the problem and what do we want to
+% know?
+
+%As a result, cilia dynamics are technically challenging to monitor
+%in-vivo.
+%
+%Until now, most studies have analyzed one physical mechanism at a
+%time, especially in mammals.
+%
+\mer{MER: Let's look at this next paragraph together.
+It should clearly lay out what we do not know about the problem (and what we want to find out).
+Be precise.
+Refer to specific studies and what specifically we (do not) know.
+What we know belongs nicely in the paragraph above.}
 For instance, studies using brain explants have convincingly shown
@@
 ventricles; however, they failed to identify the role of pressure
-gradients associated with respiration and cardiac pulsations in CSF flow
-and the accompanying transport. Similarly, while MRI technology can measure CSF movement
-in humans, it cannot detect the microscopic movements of cilia to
-understand their impact in the large human brain. Consequently, we
-lack a comprehensive understanding of how cilia contribute to CSF
-motion and solute transport, and whether cilia dysfunction will
-alter CSF composition and lead to brain disorders. This is particularly
-important since ventricular enlargement, known as hydrocephalus,
-is observed in animal models and humans with motile cilia deficiency,
-indicating that the cilia play a crucial role for healthy brain functioning.
-
-The technical limitations of studying cilia-mediated flow and transport opens the
+gradients associated with respiration and cardiac pulsations in CSF
+flow and the accompanying transport. Similarly, while MRI technology
+can measure CSF movement in humans, it cannot detect the microscopic
+movements of cilia to understand their impact in the large human
+brain. Consequently, we lack a comprehensive understanding of how
+cilia contribute to CSF motion and solute transport, and whether cilia
+dysfunction will alter CSF composition and lead to brain
+disorders. The technical limitations of studying cilia-mediated flow and transport opens the
 possibility of mathematical modeling and computational investigations. Numerous previous studies
@@
 
+% I4: How do we address the problem and what do we find out?
 In this study, we combined computational and experimental approaches to investigate

### 2025-03-06 paper/main.tex
Shuffle structure.
And move Discussion

@@
 % include * after the name of all corresponding authors
-%
+
 \author{Halvor Herlyng*},
@@
 
-% Experimental section
-\section{Computational Methods}
-\subsection{Image-based computational geometries of zebrafish brain ventricles}
-To model flow and transport in zebrafish larval brain ventricles, we generated a
-3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
-injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
-The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
-The standard mesh consisted of 132 134 tetrahedral cells and had a
-maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
-At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
-the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
-which are connected by interventricular ducts. 
-Parts of the ventricular surfaces were marked to be lined with
-motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
 \begin{figure}%[hbt!]
@@
 \end{figure}
-
-The morphology and geometry of the brain ventricles vary across zebrafish
-individuals, and under physiological and pathological conditions~\cite{Olstad2019CiliaryDevelopment}. 
-Motivated by an interest in how ventricular geometry impacts solute distribution,
-we also consider four variations in the geometry (cross-sectional area
-reduction in parentheses):
-by shrinking the fore-mid brain connection (66 \%), 
-the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
-% Cross-sectional areas of ducts normal to flow direction
-% Modified region       Original mesh        Deformed mesh
-% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
-% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
-% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
-
-\subsection{Computational CSF dynamics}
-The beating motion of the cilia generates CSF flow with steady rotational
-structures~\cite{Olstad2019CiliaryDevelopment}
-within the brain ventricles (\Crefpanels{fig:fig1}{a--c}).
-In addition, cardiac pulsations induce pulsatile CSF flow.
-We model this flow of CSF in the brain ventricles by the time-dependent,
-incompressible Stokes equations which read as follows.
-Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
-and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
-\begin{subequations}
-    \begin{align}
-      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
-      \quad \text{in } \Omega,\\
-      \nabla \cdot \uu &= 0
-      \quad  \text{in } \Omega,
-  \end{align}
-  \label{eq:stokes_eqs}% 
-\end{subequations}%
-where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
-and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
-Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
-Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
-and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
-of the CSF~\cite{Bloomfield1998EffectsFluid}.
-We introduce the tangential traction $\bsigpar$ as the
-tangential component of the traction $\hat{\bsig}=\bsig\nn$:
-\begin{equation*}
-    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
-\end{equation*}
-where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
-and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
-We consider three types of boundary conditions:
-(i) \emph{tangential traction} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ with a stress $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
-(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
-the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
-and (iii) \emph{free slip} (no flow normal to the boundary
-$\uu \cdot \nn = 0$ and no tangential traction $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the
-boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
-
-To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
-we consider the following computational flow scenarios,
-each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
-\begin{itemize}
-    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
-    contributions both from the cilia forces and the cardiac pulsations.
-    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
-    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
-
-    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
-    cilia forces but no cardiac pulsations.
-    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
-    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
-
-    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
-    cardiac pulsations but no cilia forces.
-    Here, we set the tangential traction to zero on the cilia boundary
-    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
-    anterior/posterior boundary $\Gp$.  % Model II/Model B
-\end{itemize}
-
-\subsubsection{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Crefpanels{fig:fig1}{d}, magenta markers),
-we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
-of the cilia acting on the CSF.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
-and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
-cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
-model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
-The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
-$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
-In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
-We calibrated $\tau$ heuristically by comparing these experimental velocity values
-with the simulated, maximum velocity magnitude.
-
-\subsubsection{Flow induced by cardiac pulsations}
-To generate a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
-$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
-boundary $\Gp$~(\Crefpanels{fig:fig1}{d}, blue markers).
-Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
-the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
-The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
-and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
-Particle tracking data of pulsatile motion was used to determine the contributions of the
-cardiac pulsations to the velocity magnitude,
-as compared to the effect of cilia motion on the flow (cf.~\Cref{sec:appC_particle_transport}).
-
-\subsection{Computational model of solute transport after photoconversion}
-We simulate transport of photoconverted proteins within the brain ventricles by
-modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
-time $t > 0$ by the advection-diffusion equation
-\begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
-    \label{eq:adv_diff_strong}
-\end{equation}
-where the total concentration flux $\JJ$ is assumed to consist of an advective and a diffusive flux:
-\begin{equation*}
-    \JJ = c\uu - D\nabla c .
-\end{equation*}
-Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\Cref{eq:stokes_eqs},
-and $D$ is the molecular diffusion coefficient of the solute.
-Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
-The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
-except at the anterior/posterior boundary $\Gp$.
-At the anterior/posterior boundary, we permit the solute concentration to be advected into
-and out of the domain in a manner that ensures conservation of mass
-(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
-
-To computationally represent protein photoconversion in a region
-$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
-we prescribe a given time-dependent value to the solute concentration in this region. 
-Mimicking the experimental protocol, we consider the dorsal part of the
-diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
-\begin{equation}
-  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
-  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
-\label{eq:photoconversion_curve}
-\end{equation}
-The value $a=65$ was chosen to fit the fluorescence intensity curve
-observed in the physical photoconversion experiments.
-
-\subsection{Estimation of diffusion coefficients via the Stokes-Einstein relation}
-Motivated by an interest in molecules that are significant in neural development,
-we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
-used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
-Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
-To estimate the diffusion coefficients of these, when not
-available in the literature, we use the Stokes--Einstein relation
-\begin{equation}
-    D = \frac{k_B T}{6\pi \mu R},
-    \label{eq:D_stokes_einstein}
-\end{equation}
-which is an expression for the diffusion coefficient of a spherical
-molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
-In~\Cref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
-$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
-solvent (in this case the CSF), and $R$ is the radius of the molecule.
-For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
-with $R=150$ nm, which represents exosomes at the larger end of the
-scale~\cite{Moghassemi2024ExtracellularDecade}.
-Hence this radius covers the slowest diffusing exosomes,
-a choice made because smaller exosomes would have diffusion coefficients
-similar to the other molecules we consider.
-For STM-GFP, we estimated the diffusion coefficient by extrapolating
-the experimentally observed diffusion coefficient of
-GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-assuming that if $D$ scales with $1/R$ according to~\Cref{eq:D_stokes_einstein},
-$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations
-are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
-
-%Implicit in this approach is the assumption that the proteins all have the same density.
-
-\begin{table}[h!]
-    \centering
-    \caption{Molecular mass and diffusion coefficients of simulated solutes.
-    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
-    (*) The value was extrapolated based on the value of $D$ for
-    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
-    assuming that $D$ scales with the cube root of the molecule mass.
-    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
-    \label{tab:diff_coeff_table}
-    \begin{tabular}{l|ccc}
-        \toprule
-        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
-        \midrule 
-        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
-        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
-        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{5.75e-11}$ & * \\
-        Exosomes (radius of 150 nm) & -- & $\num{2.17e-12}$ & \textdagger \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\subsection{Quantities of interest}
-We calculate the mean solute concentrations
-\begin{equation}
-    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
-    \label{eq:c_mean_i}
-\end{equation}
-in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
-as functions of time, where $|\Omega_i|$ is the volume of
-the domain $\Omega_i$. The dynamics of ROI 1 follows directly
-from~\Cref{eq:photoconversion_curve}. In addition,
-we report time-to-threshold: the time $\hat{t}_i$ when
-the mean concentration $\cbar_i$ first exceed a threshold
-value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
-$\hat{c}_i=0.10$ for ROI 5--6.
-
-To evaluate the relative importance of advection and
-diffusion as transport mechanisms, we consider the Péclet number
-\begin{equation*}
-    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
-    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
-\end{equation*}
-Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
-and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
-Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
-respectively, and $D$ is the solute diffusion coefficient.
-In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
-ventricles geometry along the rostrocaudal ($x$-) axis.
-We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
-The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
-\begin{equation*}
-    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
-\end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle.
-To assess the assumption that inertial forces are negligible compared to
-viscous forces in the CSF flow, such that the flow is governed by the Stokes equations,
-we also compute the Reynolds number
-\begin{equation*}
-    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
-\end{equation*}
-with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
-
-When studying how cilia paralysis and ventricular morphology affect intraventricular
-flow and transport, we calculate the magnitude of a tangential force $F$ 
-exerted by the cilia on a part $\mathcal{S}\subset\Gc$ of the ventricular surface as:
-\begin{equation}
-    F = \int_{\mathcal{S}}\sqrt{\btau\cdot\btau}\,\mathrm ds.
-    \label{eq:tangential_force_calculation}
-\end{equation}
-
-%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
-\subsection{Numerical approximation of the Stokes equations}
-The Stokes equations~\Cref{eq:stokes_eqs} are discretized with a finite element method
-in space, while in time, we employ a first-order implicit Euler discretization.
-We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
-For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM)
-elements for the velocity.~\cite{Brezzi1985TwoProblems, Nedelec1986AIR3}
-The BDM elements have degrees of freedom associated with integral moments of the
-velocity component normal to the facets of elements,
-thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
-We impose the boundary conditions for both the tangential traction $\bsigpar$ and
-the normal pressure $\Tilde{p}(t)$ weakly.
-For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
-The resulting total number of degrees of freedom at each time step is 943 820.
-The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
-discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-To ensure stability of the scheme, continuity in tangential velocities on interior facets
-is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.
-Since the divergence of the velocity space is a subspace of the pressure space for this scheme,
-the divergence-free condition of the velocity is satisfied exactly on each
-element, ensuring mass conservation.~\cite{Boffi2008FiniteProblem}
-
-\subsection{Numerical approximation of the advection-diffusion equation}
-The advection-diffusion equation~\Cref{eq:adv_diff_strong} is discretized
-with a first-order implicit Euler method in time, and a first-order,
-symmetric interior penalty discontinuous Galerkin (DG)
-method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
-conservation properties.
-To accurately approximate the solute concentrations even
-in the presence of strong advection (high Péclet numbers),
-we use an upwind scheme for the velocity when calculating the
-advective flux~\cite{Patankar2018NumericalFlow}.
-As for the flow equations, we use a timestep size of
-$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
-with a final time of simulation $T = 856$ s.
-A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
-
-\subsection{Solution strategy and software implementation}
-Owing to the one-way coupling between the velocity field $\uu$
-and the concentration $c$, the governing equations for the
-CSF flow and the concentration can be solved sequentially when modeling solute transport.
-For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
-the viscous forces dominate the inertial forces.
-In this case, we first solve the steady-state Stokes equations~\Cref{eq:stokes_eqs}
-for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
-the advection-diffusion equation~\Cref{eq:adv_diff_strong}.
-For the other flow scenarios, the Stokes equations are solved for one
-period of the pulsatile cardiac motion. The solution of this one period
-is then used periodically as input for the advection-diffusion equation.
-
-The numerical solution schemes for the Stokes equations and the
-advection-diffusion equation were implemented and solved numerically with
-DOLFINx~\cite{dolfinx2023preprint} with petsc4py~\cite{Dalcin2011ParallelPython}
-as linear algebra backend.
-A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
-linear systems resulting from the discretized Stokes equations.
-For the discretized advection-diffusion equation, we used an iterative
-linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
-preconditioning~\cite{Jacobi1845UeberGleichungen}. We discretize the time-dependent 
-diffusion equation (without advection) and use the assembled linear system matrix
-as the preconditioner matrix for the advection-diffusion problem.
-Numerical experiments verified the accuracy of the model implementation
-(\Cref{sec:appB_verification}). The simulation code is openly
-available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-%%------PHYSICAL EXPERIMENTS------%%
-\section{Experimental Methods}
-\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
-The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
-Norwegian Food Safety Authority (NFSA, Mattilsynet).
-The zebrafish were maintained in accordance with the guidelines set by the
-NFSA and the European Communities Council Directive.
-
-The larval and adult zebrafish were raised under standard husbandry
-conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
-The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
-14/10 hr light/dark cycle.
-From fertilization to 3 dpf, larvae were maintained in egg
-water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
-and subsequently transferred to artificial fish water (AFW)
-(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
-\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
-(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
-and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
-\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
-Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
-(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
-
-Wholemount in vivo live imaging and photoconversion
-experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
-\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
-adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
-Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
-or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
-The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
-
-For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
-fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
-tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
-To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
-and then centrifuged at 13000 rpm for 2 minutes.
-The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
-used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
-\textmu L of assay mix; 1.86 \textmu L of RO water.
-
-\subsection{Generation of transgenic line to study CSF and transport dynamics} 
-To generate a transgenic line expressing the photoconvertible protein Dendra2 in
-the brain ventricles, we fused the open reading frame (ORF)
-of the neuropeptide y (npy) signal peptide
-(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
-zebrafish codon optimized Dendra2 DNA sequence.
-The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
-3’ ends (GenScript Biotech) and inserted into the
-pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
-through restriction enzyme cloning (GenScript Biotech)
-to generate the 5xuas:Signal-Dendra2 plasmid DNA.
-
-A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
-was microinjected into one-cell stage embryos to generate the transgenic line,
-as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
-embryos were raised to adulthood (F0).
-Germline-transmitted founder zebrafish were identified by breeding with
-multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
-Dendra2 signals were screened and raised to adult zebrafish.
-
-\subsection{Wholemount zebrafish in vivo live time-lapse imaging and photoconversion of Dendra2}
-Two dpf larval zebrafish were anesthetized in 0.013\% MS222
-(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
-mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
-to obtain a lateral view of the brain ventricles. After the
-fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
-After solidification, AFW containing 0.013\% MS222 was added,
-and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
-and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
-at room temperature.
-
-The time-lapse images were acquired in a single plane, covering the
-telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
-with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
-of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
-The first 10 images were scanned without photoconversion to obtain a
-baseline value of fluorescence intensity, and the next 290 images were
-scanned while performing photoconversion.
-
-For photoconversion, ``Bleaching" and ``Region" in the ZEN software
-were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
-of the dorsoposterior diencephalic ventricle with 100\% laser power.
-The laser was illuminated in the area repeatedly between each scanning.
-After imaging, the fish health was checked and only data from healthy fish were analyzed.
-Data were collected and analyzed from three separate experiments,
-with a total of 8 controls and 6 mutants.
-
-\subsection{Photoconversion data analysis}
-All data analysis was performed in MATLAB and the codes are available in
-the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-Following import of the image data, the photoconverted channel
-was aligned to correct for drift in $x,y$ directions using previously
-developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
-Only stable recordings were further analyzed. 
-To increase the signal to noise ratio, the images were downsampled by
-a block average using a resampling factor of 6 (using the MATLAB function blockproc).
-The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
-$\Delta F$$)$ was calculated for each pixel at each time point of the data.
-Here, the value $F_0$ is the average fluorescence intensity for the
-baseline (the first 10 time-lapse images) acquired before photoconversion.
-
-To identify the time needed to pass a certain threshold value,
-$\Delta F$ values were first smoothened.
-The first timepoint when values surpassed the threshold was reported
-per pixel (in the downsampled images).
-A mask for the image was generated using the green (not photoconverted)
-channel and calculated on the block-averaged data based on the intensity
-being higher than 1.5x median intensity of all the frames.
-
-To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
-first drawn on the aligned and block-averaged time series.
-Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
-and ROIs 2--6 in different regions of the ventricular system.
-The pixel values of the fluorescence intensity within one ROI were
-averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
-To normalize the data with respect to photoconversion efficiency, the
-$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
-obtained for ROI 1 at the end of the experiment,
-so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
-zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
-We report these mean values together with a one-standard deviation error band.
-
-\subsection{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c}, we carried out
-particle tracking in a larval zebrafish injected with fluorescent beads with a procedure described in detail in previous work~\cite{Olstad2019CiliaryDevelopment}.
-Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
-(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
-in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
-dissolved in artificial CSF. Artificial CSF composition was as follows:
-124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
-1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
-2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
-The needles used for the injections were pulled with a
-Sutter Instrument Co. Model P-2000 from thin-walled glass
-capillaries (1.00 mm; VWR) and cut open with a forceps.
-A volume of 1 nl of the solution was injected with a pressure injector
-(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
-The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
-
-Following injection, the zebrafish was directly placed under the confocal
-microscope and 1200 images were acquired at a frequency of 13.1 Hz.
-A single optical section was obtained. Particle tracking was done using
-TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
-and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
-The parameters for TrackMate were as follows.
-The DoG detector was used with the settings: threshold: 2.0, with
-median filtering; radius: 2.0, with subpixel localization.
-Next, the Simple LAP tracker was used with settings: max frame gap: 2;
-alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
-splitting max distance: 15.0; allow gap closing: true; allow track splitting:
-false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
-Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 \textmu m, were plotted in~\Crefpanels{fig:fig1}{b, c}.
 
@@
 
-\section{Conclusion}
-We have presented a numerical model
+%\section{Conclusion}
+In conclusion, we have presented a numerical model
 of cerebrospinal fluid flow and solute transport in
@@
 while most of their transport is governed by diffusion.
+
+\section{Methods}
+
+\subsection{Zebrafish maintenance, genotyping and strains in photoconversion experiments}
+The animal facilities for zebrafish~(\emph{danio rerio}) are approved by the
+Norwegian Food Safety Authority (NFSA, Mattilsynet).
+The zebrafish were maintained in accordance with the guidelines set by the
+NFSA and the European Communities Council Directive.
+
+The larval and adult zebrafish were raised under standard husbandry
+conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
+The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
+14/10 hr light/dark cycle.
+From fertilization to 3 dpf, larvae were maintained in egg
+water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
+and subsequently transferred to artificial fish water (AFW)
+(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
+\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
+(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
+and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
+\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
+Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
+(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.
+
+Wholemount in vivo live imaging and photoconversion
+experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
+\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
+adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
+or \emph{smh}\textsuperscript{+/-} heterozygous zebrafish from the same breeding.
+The mutants were identified based on their curved body~\cite{Jau-NianChen1997Left-rightZebrafish}.
+
+For genotyping, genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
+fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
+tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
+To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
+and then centrifuged at 13000 rpm for 2 minutes.
+The supernatant containing gDNA was utilized for KASP assays-based analysis.
+The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
+used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
+For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
+\textmu L of assay mix; 1.86 \textmu L of RO water.
+
+\subsection{Generation of transgenic line to study CSF and transport dynamics} 
+To generate a transgenic line expressing the photoconvertible protein Dendra2 in
+the brain ventricles, we fused the open reading frame (ORF)
+of the neuropeptide y (npy) signal peptide
+(\emph{npy}: ENSDARG00000036222, Q1LW93) to the N-terminal of
+zebrafish codon optimized Dendra2 DNA sequence.
+The DNA sequence was synthesized with EcoR1 enzyme sites at the 5’ and
+3’ ends (GenScript Biotech) and inserted into the
+pT2MUASMCS vector~\cite{Asakawa2008GeneticZebrafish}
+through restriction enzyme cloning (GenScript Biotech)
+to generate the 5xuas:Signal-Dendra2 plasmid DNA.
+
+A volume of 2 nl of a mixture of the plasmid DNA (60 pg) and tol2 mRNA (10 pg)
+was microinjected into one-cell stage embryos to generate the transgenic line,
+as described in Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}. The injected
+embryos were raised to adulthood (F0).
+Germline-transmitted founder zebrafish were identified by breeding with
+multiple Gal4 transgenic lines. Stable F1 embryos expressing the Gal4-driven
+Dendra2 signals were screened and raised to adult zebrafish.
+
+\subsection{Wholemount zebrafish in vivo live time-lapse imaging and photoconversion of Dendra2}
+Two dpf larval zebrafish were anesthetized in 0.013\% MS222
+(Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
+mounted laterally in 1.5\% low melting agarose in a Flurodish (VWR, FD35PDL-100),
+to obtain a lateral view of the brain ventricles. After the
+fish were positioned in the agarose, the dish stood for 5 min to allow the agarose to solidify.
+After solidification, AFW containing 0.013\% MS222 was added,
+and then the fish were transferred to the confocal microscope (LSM880 Examiner, Zeiss)
+and imaged using a 20x water-immersion objective (Zeiss, NA 1.0, Plan-Apochromat)
+at room temperature.
+
+The time-lapse images were acquired in a single plane, covering the
+telencephalic, diencephalic and rhombencephalic ventricles simultaneously,
+with a frequency of 0.37--0.38 Hz (2.60--2.68 sec / frame). The size
+of the images was $1024\times400$ pixels. In total, 300 images were acquired per fish.
+The first 10 images were scanned without photoconversion to obtain a
+baseline value of fluorescence intensity, and the next 290 images were
+scanned while performing photoconversion.
+
+For photoconversion, ``Bleaching" and ``Region" in the ZEN software
+were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
+of the dorsoposterior diencephalic ventricle with 100\% laser power.
+The laser was illuminated in the area repeatedly between each scanning.
+After imaging, the fish health was checked and only data from healthy fish were analyzed.
+Data were collected and analyzed from three separate experiments,
+with a total of 8 controls and 6 mutants.
+
+\subsection{Photoconversion data analysis}
+All data analysis was performed in MATLAB and the codes are available in
+the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+
+Following import of the image data, the photoconverted channel
+was aligned to correct for drift in $x,y$ directions using previously
+developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
+Only stable recordings were further analyzed. 
+To increase the signal to noise ratio, the images were downsampled by
+a block average using a resampling factor of 6 (using the MATLAB function blockproc).
+The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
+$\Delta F$$)$ was calculated for each pixel at each time point of the data.
+Here, the value $F_0$ is the average fluorescence intensity for the
+baseline (the first 10 time-lapse images) acquired before photoconversion.
+
+To identify the time needed to pass a certain threshold value,
+$\Delta F$ values were first smoothened.
+The first timepoint when values surpassed the threshold was reported
+per pixel (in the downsampled images).
+A mask for the image was generated using the green (not photoconverted)
+channel and calculated on the block-averaged data based on the intensity
+being higher than 1.5x median intensity of all the frames.
+
+To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
+first drawn on the aligned and block-averaged time series.
+Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
+and ROIs 2--6 in different regions of the ventricular system.
+The pixel values of the fluorescence intensity within one ROI were
+averaged for each time point, and the relative change $\Delta F$ calculated with this averaged value.
+To normalize the data with respect to photoconversion efficiency, the
+$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
+obtained for ROI 1 at the end of the experiment,
+so that $\Delta F$ values for the photoconverted site ROI 1 ranged from
+zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
+We report these mean values together with a one-standard deviation error band.
+
+\subsection{Intraventricular injection of microbeads and particle tracking}
+To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c}, we carried out
+particle tracking in a larval zebrafish injected with fluorescent beads with a procedure described in detail in previous work~\cite{Olstad2019CiliaryDevelopment}.
+Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
+(SPHERO Fluorescent Yellow Particles 1\% w/v, F = 0.16 mm) diluted
+in 7.5 mg/ml 70 kDa rhodamine B isothiocyanate-dextran (RITCdextran; Sigma-Aldrich, R9379)
+dissolved in artificial CSF. Artificial CSF composition was as follows:
+124 mM NaCl, 22 mM D-(+)-Glucose, 2.0 mM KCl, 1.6 mM MgSO\textsubscript{4} $\cdot$ 7 H\textsubscript{2}O,
+1.3 mM KH\textsubscript{2}PO\textsubscript{4}, 24 mM NaHCO\textsubscript{3},
+2.0 mM CaCl\textsubscript{2} $\cdot$ 2 H\textsubscript{2}O.
+The needles used for the injections were pulled with a
+Sutter Instrument Co. Model P-2000 from thin-walled glass
+capillaries (1.00 mm; VWR) and cut open with a forceps.
+A volume of 1 nl of the solution was injected with a pressure injector
+(Eppendorf Femtojet 4i) in the rostral rhombencephalic ventricle.
+The pressure and time were calibrated for each needle using a 0.01 mm calibration slide.
+
+Following injection, the zebrafish was directly placed under the confocal
+microscope and 1200 images were acquired at a frequency of 13.1 Hz.
+A single optical section was obtained. Particle tracking was done using
+TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
+and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
+The parameters for TrackMate were as follows.
+The DoG detector was used with the settings: threshold: 2.0, with
+median filtering; radius: 2.0, with subpixel localization.
+Next, the Simple LAP tracker was used with settings: max frame gap: 2;
+alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
+splitting max distance: 15.0; allow gap closing: true; allow track splitting:
+false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
+Only the particle tracks with at least 30 data points, while simultaneously
+covering a distance of at least 8.8 \textmu m, were plotted in~\Crefpanels{fig:fig1}{b, c}.
+
+\subsection{Image-based computational geometries of zebrafish brain ventricles}
+To model flow and transport in zebrafish larval brain ventricles, we generated a
+3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
+injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
+From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
+The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
+The standard mesh consisted of 132 134 tetrahedral cells and had a
+maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
+At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
+the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
+which are connected by interventricular ducts. 
+Parts of the ventricular surfaces were marked to be lined with
+motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
+
+The morphology and geometry of the brain ventricles vary across zebrafish
+individuals, and under physiological and pathological conditions~\cite{Olstad2019CiliaryDevelopment}. 
+Motivated by an interest in how ventricular geometry impacts solute distribution,
+we also consider four variations in the geometry (cross-sectional area
+reduction in parentheses):
+by shrinking the fore-mid brain connection (66 \%), 
+the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.
+We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+% Cross-sectional areas of ducts normal to flow direction
+% Modified region       Original mesh        Deformed mesh
+% Fore                  3.36e-3 mm^2         1.15e-3 mm^2
+% Mid                   6.11e-3 mm^2         4.08e-3 mm^2
+% Hind                  2.91e-3 mm^2         1.67e-3 mm^2
+
+\subsection{Computational CSF dynamics}
+The beating motion of the cilia generates CSF flow with steady rotational
+structures~\cite{Olstad2019CiliaryDevelopment}
+within the brain ventricles (\Crefpanels{fig:fig1}{a--c}).
+In addition, cardiac pulsations induce pulsatile CSF flow.
+We model this flow of CSF in the brain ventricles by the time-dependent,
+incompressible Stokes equations which read as follows.
+Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
+and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
+\begin{subequations}
+    \begin{align}
+      \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
+      \quad \text{in } \Omega,\\
+      \nabla \cdot \uu &= 0
+      \quad  \text{in } \Omega,
+  \end{align}
+  \label{eq:stokes_eqs}% 
+\end{subequations}%
+where the stress tensor is defined as $\bsig(\uu, p) = 2\mu\beps(\uu) - p\mathbf{I}$
+and $\beps(\uu) = \frac{1}{2}\left(\nabla \uu + (\nabla\uu)^T\right)$ is the strain-rate tensor. 
+Bold-face characters denote vectors or tensors, and $\mathbf{I}$ is the identity tensor in three dimensions.
+Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
+and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
+of the CSF~\cite{Bloomfield1998EffectsFluid}.
+We introduce the tangential traction $\bsigpar$ as the
+tangential component of the traction $\hat{\bsig}=\bsig\nn$:
+\begin{equation*}
+    \bsigpar = P_{\nn}(\hat{\bsig}) = (\mathbf{I} - \nn\otimes\nn)\hat{\bsig},
+\end{equation*}
+where $\nn$ is the outer unit normal of the boundary surface $\Gamma = \partial\Omega$,
+and $P_{\nn}(\rr)$ is the tangential projection of a vector $\rr$ onto $\Gamma$.
+We consider three types of boundary conditions:
+(i) \emph{tangential traction} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ with a stress $\btau$ applied tangentially on the boundary $\bsigpar = \btau$),
+(ii) \emph{normal pressure} (a pressure $\Tilde{p}$ applied in
+the normal direction: $(\mu\nabla\uu - p\mathbf{I})\nn = \Tilde{p}(t)\nn$),
+and (iii) \emph{free slip} (no flow normal to the boundary
+$\uu \cdot \nn = 0$ and no tangential traction $\bsigpar = {\bf 0}$).
+Unless noted otherwise, the free-slip condition is applied on the
+boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
+
+To study the impact of the motile cilia and the cardiac pulsations on the CSF flow,
+we consider the following computational flow scenarios,
+each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
+\begin{itemize}
+    \item A \emph{baseline} flow model representing a wild-type zebrafish including 
+    contributions both from the cilia forces and the cardiac pulsations.
+    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
+    $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
+
+    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
+    cilia forces but no cardiac pulsations.
+    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
+    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
+
+    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
+    cardiac pulsations but no cilia forces.
+    Here, we set the tangential traction to zero on the cilia boundary
+    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
+    anterior/posterior boundary $\Gp$.  % Model II/Model B
+\end{itemize}
+
+\subsubsection{Cilia-driven flow}
+On the ciliated regions of the ventricle walls $\Gc$ (\Crefpanels{fig:fig1}{d}, magenta markers),
+we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
+of the cilia acting on the CSF.
+We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
+and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
+cilia region (see~\Cref{subsec:appendixA1}).
+Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
+model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
+The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
+$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
+In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
+We calibrated $\tau$ heuristically by comparing these experimental velocity values
+with the simulated, maximum velocity magnitude.
+
+\subsubsection{Flow induced by cardiac pulsations}
+To generate a cardiac-induced pulsatile flow inside the brain ventricles, we set $\Tilde{p}(t)=0$ and
+$\Tilde{p}(t)=-A\sin{\omega t}$ on anterior and posterior parts, respectively, of the
+boundary $\Gp$~(\Crefpanels{fig:fig1}{d}, blue markers).
+Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
+the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
+The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
+and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
+Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
+Particle tracking data of pulsatile motion was used to determine the contributions of the
+cardiac pulsations to the velocity magnitude,
+as compared to the effect of cilia motion on the flow (cf.~\Cref{sec:appC_particle_transport}).
+
+\subsection{Computational model of solute transport after photoconversion}
+We simulate transport of photoconverted proteins within the brain ventricles by
+modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
+time $t > 0$ by the advection-diffusion equation
+\begin{equation}
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
+    \label{eq:adv_diff_strong}
+\end{equation}
+where the total concentration flux $\JJ$ is assumed to consist of an advective and a diffusive flux:
+\begin{equation*}
+    \JJ = c\uu - D\nabla c .
+\end{equation*}
+Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\Cref{eq:stokes_eqs},
+and $D$ is the molecular diffusion coefficient of the solute.
+Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
+The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
+except at the anterior/posterior boundary $\Gp$.
+At the anterior/posterior boundary, we permit the solute concentration to be advected into
+and out of the domain in a manner that ensures conservation of mass
+(see~\Cref{subsec:adv_diff_eq_weak_form} for details).
+
+To computationally represent protein photoconversion in a region
+$\Omega_{\mathrm{pc}} \subset \Omega$ (corresponding to ROI 1),
+we prescribe a given time-dependent value to the solute concentration in this region. 
+Mimicking the experimental protocol, we consider the dorsal part of the
+diencephalic ventricle as the subdomain $\Omega_{\mathrm{pc}}$, and set
+\begin{equation}
+  c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
+  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
+\label{eq:photoconversion_curve}
+\end{equation}
+The value $a=65$ was chosen to fit the fluorescence intensity curve
+observed in the physical photoconversion experiments.
+
+\subsection{Estimation of diffusion coefficients via the Stokes-Einstein relation}
+Motivated by an interest in molecules that are significant in neural development,
+we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
+used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
+To estimate the diffusion coefficients of these, when not
+available in the literature, we use the Stokes--Einstein relation
+\begin{equation}
+    D = \frac{k_B T}{6\pi \mu R},
+    \label{eq:D_stokes_einstein}
+\end{equation}
+which is an expression for the diffusion coefficient of a spherical
+molecule suspended in a viscous fluid~\cite{Einstein1905UberTeilchen}.
+In~\Cref{eq:D_stokes_einstein}, $k_B = \num{1.38e-23}$ J/K is the Boltzmann constant,
+$T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
+solvent (in this case the CSF), and $R$ is the radius of the molecule.
+For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
+with $R=150$ nm, which represents exosomes at the larger end of the
+scale~\cite{Moghassemi2024ExtracellularDecade}.
+Hence this radius covers the slowest diffusing exosomes,
+a choice made because smaller exosomes would have diffusion coefficients
+similar to the other molecules we consider.
+For STM-GFP, we estimated the diffusion coefficient by extrapolating
+the experimentally observed diffusion coefficient of
+GFP~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+assuming that if $D$ scales with $1/R$ according to~\Cref{eq:D_stokes_einstein},
+$D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
+The resulting diffusion coefficients used in the simulations
+are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
+
+%Implicit in this approach is the assumption that the proteins all have the same density.
+
+\begin{table}[h!]
+    \centering
+    \caption{Molecular mass and diffusion coefficients of simulated solutes.
+    STM and GFP denote Starmaker Protein and Green Fluorescent Protein, respectively.
+    (*) The value was extrapolated based on the value of $D$ for
+    GFP reported in the literature~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells},
+    assuming that $D$ scales with the cube root of the molecule mass.
+    (\textdagger) The value was estimated using the Stokes-Einstein relation~\Cref{eq:D_stokes_einstein}.}
+    \label{tab:diff_coeff_table}
+    \begin{tabular}{l|ccc}
+        \toprule
+        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
+        \midrule 
+        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
+        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
+        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
+        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
+        & $\num{5.75e-11}$ & * \\
+        Exosomes (radius of 150 nm) & -- & $\num{2.17e-12}$ & \textdagger \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\subsection{Quantities of interest}
+We calculate the mean solute concentrations
+\begin{equation}
+    \cbar_i(t) = \frac{1}{|\Omega_i|}\int_{\Omega_i} c(\xx, t)\,\dx,
+    \label{eq:c_mean_i}
+\end{equation}
+in the six regions of interest (ROIs) $\Omega_i$ ($i = 1, \dots, 6$)
+as functions of time, where $|\Omega_i|$ is the volume of
+the domain $\Omega_i$. The dynamics of ROI 1 follows directly
+from~\Cref{eq:photoconversion_curve}. In addition,
+we report time-to-threshold: the time $\hat{t}_i$ when
+the mean concentration $\cbar_i$ first exceed a threshold
+value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
+$\hat{c}_i=0.10$ for ROI 5--6.
+
+To evaluate the relative importance of advection and
+diffusion as transport mechanisms, we consider the Péclet number
+\begin{equation*}
+    \mathrm{Pe} = \frac{\mathrm{diffusion \ timescale}}{\mathrm{advection \ timescale}}
+    = \frac{t_d}{t_a} = \frac{L_p^2/D}{L_p/U_p} = \frac{L_p U_p}{D}.
+\end{equation*}
+Thus, if $\mathrm{Pe} > 1$, transport is dominated by advection,
+and if $\mathrm{Pe} < 1$ transport is dominated by diffusion.
+Here, $L_p$ and $U_p$ are characteristic length and velocity scales,
+respectively, and $D$ is the solute diffusion coefficient.
+In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
+ventricles geometry along the rostrocaudal ($x$-) axis.
+We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
+The mean velocity $\overline{U}$ is calculated by first averaging the velocity in space:
+\begin{equation*}
+    \overline{u}^2 = \frac{1}{|\Omega|}\int_{\Omega}\uu\cdot\uu\dx,
+\end{equation*}
+and then averaging $\overline{u}$ in time over one cardiac cycle.
+To assess the assumption that inertial forces are negligible compared to
+viscous forces in the CSF flow, such that the flow is governed by the Stokes equations,
+we also compute the Reynolds number
+\begin{equation*}
+    \mathrm{Re} = \frac{\mathrm{inertial \ forces}}{\mathrm{viscous \ forces}} = \frac{\rho U_r L_r}{\mu},
+\end{equation*}
+with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
+
+When studying how cilia paralysis and ventricular morphology affect intraventricular
+flow and transport, we calculate the magnitude of a tangential force $F$ 
+exerted by the cilia on a part $\mathcal{S}\subset\Gc$ of the ventricular surface as:
+\begin{equation}
+    F = \int_{\mathcal{S}}\sqrt{\btau\cdot\btau}\,\mathrm ds.
+    \label{eq:tangential_force_calculation}
+\end{equation}
+
+%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
+\subsection{Numerical approximation of the Stokes equations}
+The Stokes equations~\Cref{eq:stokes_eqs} are discretized with a finite element method
+in space, while in time, we employ a first-order implicit Euler discretization.
+We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
+For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM)
+elements for the velocity.~\cite{Brezzi1985TwoProblems, Nedelec1986AIR3}
+The BDM elements have degrees of freedom associated with integral moments of the
+velocity component normal to the facets of elements,
+thus we enforce the impermeability condition $\uu\cdot\nn=0$ strongly.
+We impose the boundary conditions for both the tangential traction $\bsigpar$ and
+the normal pressure $\Tilde{p}(t)$ weakly.
+For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
+The resulting total number of degrees of freedom at each time step is 943 820.
+The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
+discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
+To ensure stability of the scheme, continuity in tangential velocities on interior facets
+is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.
+Since the divergence of the velocity space is a subspace of the pressure space for this scheme,
+the divergence-free condition of the velocity is satisfied exactly on each
+element, ensuring mass conservation.~\cite{Boffi2008FiniteProblem}
+
+\subsection{Numerical approximation of the advection-diffusion equation}
+The advection-diffusion equation~\Cref{eq:adv_diff_strong} is discretized
+with a first-order implicit Euler method in time, and a first-order,
+symmetric interior penalty discontinuous Galerkin (DG)
+method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
+conservation properties.
+To accurately approximate the solute concentrations even
+in the presence of strong advection (high Péclet numbers),
+we use an upwind scheme for the velocity when calculating the
+advective flux~\cite{Patankar2018NumericalFlow}.
+As for the flow equations, we use a timestep size of
+$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
+with a final time of simulation $T = 856$ s.
+A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
+
+\subsection{Solution strategy and software implementation}
+Owing to the one-way coupling between the velocity field $\uu$
+and the concentration $c$, the governing equations for the
+CSF flow and the concentration can be solved sequentially when modeling solute transport.
+For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
+the viscous forces dominate the inertial forces.
+In this case, we first solve the steady-state Stokes equations~\Cref{eq:stokes_eqs}
+for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
+the advection-diffusion equation~\Cref{eq:adv_diff_strong}.
+For the other flow scenarios, the Stokes equations are solved for one
+period of the pulsatile cardiac motion. The solution of this one period
+is then used periodically as input for the advection-diffusion equation.
+
+The numerical solution schemes for the Stokes equations and the
+advection-diffusion equation were implemented and solved numerically with
+DOLFINx~\cite{dolfinx2023preprint} with petsc4py~\cite{Dalcin2011ParallelPython}
+as linear algebra backend.
+A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
+linear systems resulting from the discretized Stokes equations.
+For the discretized advection-diffusion equation, we used an iterative
+linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
+preconditioning~\cite{Jacobi1845UeberGleichungen}. We discretize the time-dependent 
+diffusion equation (without advection) and use the assembled linear system matrix
+as the preconditioner matrix for the advection-diffusion problem.
+Numerical experiments verified the accuracy of the model implementation
+(\Cref{sec:appB_verification}). The simulation code is openly
+available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+
+%%------PHYSICAL EXPERIMENTS------%%
+%\section{Experimental Methods}
 

### 2025-03-06 paper/main.tex
Minor updates in experimental methods

@@
 14/10 hr light/dark cycle.
-From fertilization to 3 dpf, larvae were maintained in egg
+From fertilization to 3 days post-fertilization (dpf), larvae were maintained in egg
 water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
@@
 Wholemount in vivo live imaging and photoconversion
-experiments were performed with zebrafish larvae at 2 days post-fertilization (dpf) stage obtained from inbreeding of heterozygous
+experiments were performed with zebrafish larvae at the 2 dpf stage obtained from inbreeding of heterozygous
 \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
-adult animals, as described in D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+adult animals, as described by D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
 Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
@@
 used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
+For each sample well, the \fixme{master} mix contained: 5 \textmu L of master mix; 0.14
 \textmu L of assay mix; 1.86 \textmu L of RO water.
@@
 
-\subsection{Wholemount zebrafish in vivo live time-lapse imaging and photoconversion of Dendra2}
+\subsection{Wholemount zebrafish in vivo time-lapse imaging and photoconversion of Dendra2}
 Two dpf larval zebrafish were anesthetized in 0.013\% MS222
@@
 \subsection{Photoconversion data analysis}
-All data analysis was performed in MATLAB and the codes are available in
-the repository of this article~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
-
-Following import of the image data, the photoconverted channel
-was aligned to correct for drift in $x,y$ directions using previously
-developed codes~\cite{Reiten2017Motile-Cilia-MediatedComputations, Ringers2023NovelEpithelia}.
-Only stable recordings were further analyzed. 
-To increase the signal to noise ratio, the images were downsampled by
-a block average using a resampling factor of 6 (using the MATLAB function blockproc).
-The change of fluorescence $($$(F-F_0)/F_0$, hereafter referred to as
-$\Delta F$$)$ was calculated for each pixel at each time point of the data.
-Here, the value $F_0$ is the average fluorescence intensity for the
-baseline (the first 10 time-lapse images) acquired before photoconversion.
+The image data analysis was performed in MATLAB and the codes are
+openly available~\fixme{\cite{zenodo-link-to-all-code}}.  The
+photoconverted channel was aligned to correct for drift in $x,y$
+directions using previously developed
+codes~\cite{Reiten2017Motile-Cilia-MediatedComputations,
+  Ringers2023NovelEpithelia}.  Only stable recordings were further
+analyzed.  To increase the signal-to-noise ratio, the images were
+downsampled by a block average using a resampling factor of 6. % (using the MATLAB function blockproc).
+The change in fluorescence intensity
+$\Delta F = (F-F_0)/F_0$ was
+calculated for each pixel and each time point.  Here, the
+value $F_0$ is the average fluorescence intensity for the baseline
+(the first 10 time-lapse images) acquired before photoconversion.
 
@@
 
-To obtain $\Delta F$ values for a region of interest (ROI), ROIs were
-first drawn on the aligned and block-averaged time series.
+To obtain $\Delta F$ values for each region of interest (ROI), ROIs were
+first drawn on the aligned and block-averaged time series (\Cref{fig:fig2}).
 Six ROIs were drawn manually: ROI 1 around the location of photoconversion,
@@
 zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
-We report these mean values together with a one-standard deviation error band.
+%We report these mean values together with a one-standard deviation error band.
 
 \subsection{Intraventricular injection of microbeads and particle tracking}
-To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c}, we carried out
-particle tracking in a larval zebrafish injected with fluorescent beads with a procedure described in detail in previous work~\cite{Olstad2019CiliaryDevelopment}.
+%To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c},
+
+We also carried out
+particle tracking in a larval zebrafish injected with fluorescent beads, as described in previous work~\cite{Olstad2019CiliaryDevelopment}.
 Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
@@
 microscope and 1200 images were acquired at a frequency of 13.1 Hz.
-A single optical section was obtained. Particle tracking was done using
+A single optical section was obtained. Particle tracking was performed using
 TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
-and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
+and plotted using MATLAB, as described by Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
 The parameters for TrackMate were as follows.
@@
 Only the particle tracks with at least 30 data points, while simultaneously
-covering a distance of at least 8.8 \textmu m, were plotted in~\Crefpanels{fig:fig1}{b, c}.
+covering a distance of at least 8.8 \textmu m, are shown (\Crefpanels{fig:fig1}{b, c}).
 

### 2025-03-06 paper/main.tex
Updates in Comp methods  1

@@
 \subsection{Image-based computational geometries of zebrafish brain ventricles}
-To model flow and transport in zebrafish larval brain ventricles, we generated a
-3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
-injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
-From the imaging data, we constructed a computational mesh of the ventricles (\Crefpanels{fig:fig1}{d}).
-The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
-The standard mesh consisted of 132 134 tetrahedral cells and had a
-maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
-At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
-the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles,
-which are connected by interventricular ducts. 
-Parts of the ventricular surfaces were marked to be lined with
-motile cilia (\Crefpanels{fig:fig1}{d}, magenta markers)~\cite{Olstad2019CiliaryDevelopment}.
+To model CSF flow and transport in the zebrafish brain ventricles, we
+generated a 3D surface representation of the ventricular walls using
+confocal imaging data of a zebrafish embryo injected
+intraventricularly with a 70 kDa dye at 2
+dpf~\cite{Olstad2019CiliaryDevelopment}. At 2 dpf, the ventricular
+system consists mainly of 3 cavities: the telencephalic (anterior),
+the di-/mesencephalic (middle) and the rhombencephalic (posterior)
+ventricles, which are connected by interventricular ducts. From the
+surface geometry, we constructed a volumetric mesh of the ventricles
+using fTetWild~\cite{Hu2020FastWild}, consisting of 132 134
+tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu
+m (4.68 \textmu m) (\Crefpanels{fig:fig1}{d}). Parts of the
+ventricular surfaces were marked to be lined with motile cilia
+(\Crefpanels{fig:fig1}{d}, magenta
+markers)~\cite{Olstad2019CiliaryDevelopment}.
 
@@
 the middle ventricle (33 \%), the mid-hind brain connection (43 \%), and all three simultaneously.
-We used Blender~\cite{Community2018BlenderPackage} to modify the brain ventricles geometry.
+We used Blender~\cite{Community2018BlenderPackage} to modify the geometries (\Crefpanels{fig:fig6}{a, b}).
 % Cross-sectional areas of ducts normal to flow direction

### 2025-03-06 paper/main.tex
More updates in Methods

@@
 
-\subsection{Computational CSF dynamics}
-The beating motion of the cilia generates CSF flow with steady rotational
+\subsection{Computational CSF dynamics in the brain ventricles}
+The beating motion of the cilia generates CSF flow with persistent rotational
 structures~\cite{Olstad2019CiliaryDevelopment}
@@
 In addition, cardiac pulsations induce pulsatile CSF flow.
-We model this flow of CSF in the brain ventricles by the time-dependent,
+We model this flow of CSF by the time-dependent,
 incompressible Stokes equations which read as follows.
@@
 we consider the following computational flow scenarios,
-each predicting a CSF flow velocity $\uu$ and CSF pressure $p$.
+each predicting a CSF flow velocity $\uu$ and pressure $p$.
 \begin{itemize}
@@
 
-    \item A \emph{cilia-only/no-cardiac} flow model including contributions from the
+    \item A \emph{cilia-driven/no-cardiac} flow model including contributions from the
     cilia forces but no cardiac pulsations.
-    Here, we apply the tangential traction $\btau$ on the cilia boundary $\Gc$.
+    Here, we apply a tangential traction $\btau$ on the cilia boundary $\Gc$.
     In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
 
-    \item A \emph{cardiac-only/no-cilia} flow model including contributions from the
+    \item A \emph{cardiac-induced/no-cilia} flow model including contributions from the
     cardiac pulsations but no cilia forces.
@@
 \end{itemize}
+The tangential traction and normal pressure are described further below.
 
 \subsubsection{Cilia-driven flow}
-On the ciliated regions of the ventricle walls $\Gc$ (\Crefpanels{fig:fig1}{d}, magenta markers),
-we impose a constant-in-time tangential traction $\bsigpar=\btau$ to represent the net forces
-of the cilia acting on the CSF.
-We set $\btau(\xx, \rr) = \tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$
-and the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
-cilia region (see~\Cref{subsec:appendixA1}).
-Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
-model calibration using experimental data~\cite{Olstad2019CiliaryDevelopment}.
-The data indicate speeds proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
-$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the middle ventricle, respectively.
-In the anterior ventricle, the speeds were estimated at $4.7 \pm 1.3$ \textmu m/s.
-We calibrated $\tau$ heuristically by comparing these experimental velocity values
-with the simulated, maximum velocity magnitude.
+On the ciliated regions of the ventricle walls $\Gc$
+(\Crefpanels{fig:fig1}{d}, magenta markers), we impose a
+constant-in-time tangential traction $\bsigpar=\btau$ to represent the
+net forces of the cilia acting on the CSF.  We set $\btau(\xx, \rr) =
+\tau \lambda(\xx) P_{\nn}(\rr)$, where the function $\lambda(\xx)$ and
+the sign of the vector $\rr=\pm(1, 0, 1)$ varies depending on the
+cilia region (see~\Cref{subsec:appendixA1}). Previous
+experiments~\cite{Olstad2019CiliaryDevelopment} indicate flow speeds
+proximate to the ventricular walls of $27.4 \pm 5.4$ \textmu m/s and
+$2.6 \pm 0.6$ \textmu m/s in the dorsal and ventral regions of the
+middle ventricle, respectively.  In the anterior ventricle, the speeds
+were estimated at $4.7 \pm 1.3$ \textmu m/s. We calibrated $\rr$ and
+$\tau=0.65$ mPa by comparison of the simulated maximum velocity
+magnitude with these flow speeds.
+
+%% comparing these experimental velocity values
+%% with the simulated, maximum velocity magnitude.
+
+%% Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
+%% calibration against experimentally measured flow speeds~\cite{Olstad2019CiliaryDevelopment}.
 
@@
 Based on a measured cardiac frequency of $f=2.22$ Hz~\cite{Olstad2019CiliaryDevelopment},
-the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s.
-The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow,
-and was calibrated based on experimental data~\cite{Olstad2019CiliaryDevelopment}.
-Similar to $\tau$, the amplitude $A$ was chosen by comparing experimental and simulated velocities.
-Particle tracking data of pulsatile motion was used to determine the contributions of the
+we set the angular cardiac frequency $\omega=2\pi f=6.97$ rad/s. The amplitude $A=1.5$ mPa determines the magnitude of the pulsatile flow
+and was calibrated based on previous experiments~\cite{Olstad2019CiliaryDevelopment}.
+Particle tracking data were used to determine the contributions of the
 cardiac pulsations to the velocity magnitude,

### 2025-03-06 paper/main.tex
Edits up to 4.9

@@
 \end{equation*}
-Here, $\uu$ is the CSF velocity field, governed by the Stokes equations~\Cref{eq:stokes_eqs},
+Here, $\uu$ is the CSF velocity field, governed by the Stokes equations (\Cref{eq:stokes_eqs}),
 and $D$ is the molecular diffusion coefficient of the solute.
@@
 Motivated by an interest in molecules that are significant in neural development,
-we study the transport of molecules resembling the Dendra2 Fluorescent Protein (Dendra2)
-used in this study, the Starmaker+Green Fluorescent Protein (STM-GFP) reported in
-Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and exosomes.
+we study the transport of molecules resembling (i) the Dendra2 Fluorescent Protein (Dendra2)
+used in the photoconversion, (ii) the Starmaker+Green Fluorescent Protein (STM-GFP) reported by
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and (iii) exosomes.
 To estimate the diffusion coefficients of these, when not
@@
 $T = 310$ K is the absolute temperature, $\mu$ is the dynamic viscosity of the
-solvent (in this case the CSF), and $R$ is the radius of the molecule.
+CSF, and $R$ is the radius of the molecule.
 For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
-with $R=150$ nm, which represents exosomes at the larger end of the
-scale~\cite{Moghassemi2024ExtracellularDecade}.
-Hence this radius covers the slowest diffusing exosomes,
-a choice made because smaller exosomes would have diffusion coefficients
-similar to the other molecules we consider.
-For STM-GFP, we estimated the diffusion coefficient by extrapolating
+with the relatively large $R=150$ nm~\cite{Moghassemi2024ExtracellularDecade}.
+%Hence this radius covers the slowest diffusing exosomes,
+%a choice made because smaller exosomes would have diffusion coefficients
+%similar to the other molecules we consider.
+For STM-GFP, we estimate the diffusion coefficient by extrapolating
 the experimentally observed diffusion coefficient of
@@
 $D$ would scale with the cube root of the molecule mass~\cite{Goodhill1997DiffusionGuidance}.
-The resulting diffusion coefficients used in the simulations
-are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2)~(\Cref{tab:diff_coeff_table}).
+The resulting diffusion coefficients
+are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2) as given by \Cref{tab:diff_coeff_table}.
 
@@
     \label{tab:diff_coeff_table}
-    \begin{tabular}{l|ccc}
+    \begin{tabular}{lc|ccc}
         \toprule
-        Molecule & Mass [kDa] & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
+        Molecule & Label & Mass [kDa]  & $D \ [\mathrm{m^2/s}]$ & Reference \\ 
         \midrule 
-        Dendra2 Fluorescent Protein & 25.6~\cite{Gurskaya2006EngineeringLight}
-        & $\num{1.15e-10}$  & \cite{GuraSadovsky2017MeasurementExpansion}\\
-        GFP (saline aqueous solution) & 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
-        STM-GFP & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB}
-        & $\num{5.75e-11}$ & * \\
-        Exosomes (radius of 150 nm) & -- & $\num{2.17e-12}$ & \textdagger \\
+        Exosomes (radius of 150 nm) & $D_1$ & -- & $\num{2.17e-12}$ & \textdagger \\
+        GFP (saline aqueous solution) & -- & 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\
+        STM-GFP & $D_2$ & 66.2~\cite{UniProt2024StmUniProtKB} + 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{5.75e-11}$ & * \\
+        Dendra2 Fluorescent Protein & $D_3$ & 25.6~\cite{Gurskaya2006EngineeringLight} & $\num{1.15e-10}$ & \cite{GuraSadovsky2017MeasurementExpansion}\\
         \bottomrule

### 2025-03-06 paper/main.tex
Methods and end stuff.

@@
 from~\Cref{eq:photoconversion_curve}. In addition,
-we report time-to-threshold: the time $\hat{t}_i$ when
-the mean concentration $\cbar_i$ first exceed a threshold
+we report the time-to-threshold as the time $\hat{t}_i$ when
+the mean concentration $\cbar_i$ first exceeds a threshold
 value $\hat{c}_i$. We use $\hat{c}_i=0.25$ for ROI 1--4 and
@@
 In calculating a global Péclet number, we use $L_p=600$ \textmu m, the approximate length of the
-ventricles geometry along the rostrocaudal ($x$-) axis.
+ventricular geometry along the rostrocaudal ($x$-) axis.
 We use a mean velocity $\overline{U}$ as the characteristic velocity $U_p$.
@@
 \end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle.
+and then averaging $\overline{u}$ in time over one cardiac cycle to yield $\overline{U} = \fixme{X}$ \fixme{unit}.
 To assess the assumption that inertial forces are negligible compared to
-viscous forces in the CSF flow, such that the flow is governed by the Stokes equations,
-we also compute the Reynolds number
+viscous forces, we also compute the Reynolds number
 \begin{equation*}
@@
 \end{equation*}
-with $L_r$ and $U_r$ as length and velocity scales characteristic of the flow.
-
-When studying how cilia paralysis and ventricular morphology affect intraventricular
+with $L_r = \fixme{X}$ \fixme{unit} and $U_r = \fixme{X}$ \fixme{unit}
+as length and velocity scales characteristic of the flow.
+
+To study how cilia paralysis and ventricular morphology affect intraventricular
 flow and transport, we calculate the magnitude of a tangential force $F$ 
@@
 \subsection{Numerical approximation of the Stokes equations}
-The Stokes equations~\Cref{eq:stokes_eqs} are discretized with a finite element method
+The Stokes equations (\Cref{eq:stokes_eqs}) are discretized with a finite element method
 in space, while in time, we employ a first-order implicit Euler discretization.
-We set the timestep size $\Delta t = 0.02252$ s such that 20 timesteps represent one cardiac cycle.
+We set the timestep size $\Delta t = 0.023$ s such that 20 timesteps represent one cardiac cycle.
 For the spatial discretization, we use piecewise linear Brezzi-Douglas-Marini (BDM)
@@
 discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
-To ensure stability of the scheme, continuity in tangential velocities on interior facets
+Continuity in tangential velocities on interior facets
 is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.
 Since the divergence of the velocity space is a subspace of the pressure space for this scheme,
-the divergence-free condition of the velocity is satisfied exactly on each
-element, ensuring mass conservation.~\cite{Boffi2008FiniteProblem}
+the divergence-free condition of the velocity is satisfied exactly, ensuring mass conservation.~\cite{Boffi2008FiniteProblem}
 
 \subsection{Numerical approximation of the advection-diffusion equation}
-The advection-diffusion equation~\Cref{eq:adv_diff_strong} is discretized
+The advection-diffusion equation (\Cref{eq:adv_diff_strong}) is discretized
 with a first-order implicit Euler method in time, and a first-order,
-symmetric interior penalty discontinuous Galerkin (DG)
+symmetric interior penalty DG
 method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
@@
 As for the flow equations, we use a timestep size of
-$\Delta t = 0.02252$ s. We simulate transport for 1900 cardiac cycles,
+$\Delta t = 0.023$ s. We simulate transport for 1900 cardiac cycles,
 with a final time of simulation $T = 856$ s.
@@
 and the concentration $c$, the governing equations for the
-CSF flow and the concentration can be solved sequentially when modeling solute transport.
-For the cilia-only/no-cardiac flow scenario, the velocity quickly reaches steady-state since
+CSF flow and the concentration can be solved sequentially.
+For the cilia-driven/no-cardiac flow scenario, the velocity quickly reaches steady-state since
 the viscous forces dominate the inertial forces.
-In this case, we first solve the steady-state Stokes equations~\Cref{eq:stokes_eqs}
+In this case, we first solve the steady-state Stokes equations (\Cref{eq:stokes_eqs})
 for $\uu$ and $p$, and then use the velocity field $\uu$ as input when solving
-the advection-diffusion equation~\Cref{eq:adv_diff_strong}.
+the advection-diffusion equation (\Cref{eq:adv_diff_strong}).
 For the other flow scenarios, the Stokes equations are solved for one
@@
 DOLFINx~\cite{dolfinx2023preprint} with petsc4py~\cite{Dalcin2011ParallelPython}
-as linear algebra backend.
+as linear algebra backend. The simulation code is openly
+available\fixme{~\cite{zenodo-link-to-all-code}}.
 A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
@@
 Numerical experiments verified the accuracy of the model implementation
-(\Cref{sec:appB_verification}). The simulation code is openly
-available~\cite{zenodo-link-to-all-code}\fixme{Add repo link.}.
+(\Cref{sec:appB_verification}).
 
@@
 \medskip
-\textbf{Acknowledgments} \par 
-Thanks are extended to J\o rgen Dokken for valuable model implementation discussions.
-Halvor Herlyng acknowledges support from the national infrastructure for computational
-science in Norway, Sigma2, via grant \#NN8049K.
-This work was funded by the Research Council of Norway (NJY FRIPRO grants 314189 and 353348).
+\noindent \textbf{Acknowledgments} \par
+\noindent Thanks are extended to J\o rgen Dokken
+for valuable model implementation discussions.  H.~H.~and
+M.~E.~R. acknowledge support from the national infrastructure for
+computational science in Norway, Sigma2, via grant
+\#NN8049K. M.~E.~R.~acknowledges support from Stiftelsen Kristian
+Gerhard Jebsen via the K.~G.~Jebsen Centre for Brain Fluid Research
+and support from the Research Council of Norway (RCN) via grant
+\#324239 (EMIx). N.~J.~Y.~acknowledges support from the Research
+Council of Norway (grants \#314189 and \#353348).
 
 \medskip
-\textbf{Data Availability Statement} \par
-The data and implementations presented in this paper are licensed under \fixme{LICENSE}
+\noindent \textbf{Data Availability Statement} \par
+\noindent The data and implementations presented in this paper are licensed under \fixme{LICENSE}
 and openly available at \fixme{REPO-LINK}.
@@
 \medskip
-\textbf{Conflict of Interest Disclosure} \par
-The authors declare no conflicts of interest.
-
-\medskip
-\textbf{Supporting Information} \par %Please delete the Suppporting Information statement
+\noindent \textbf{Conflict of Interest Disclosure} \par
+\noindent The authors declare no conflicts of interest.
+
+%\medskip
+%\textbf{Supporting Information} \par %Please delete the Suppporting Information statement
 %if it is not applicable. Please supply Supporting Information in another file.
 %Supporting information should not be provided in .tex format
-Supporting Information is available from the Wiley Online Library or from the author.
+%Supporting Information is available from the Wiley Online Library or from the author.
 
 % References
-\medskip
+%\medskip
 

### 2025-03-06 paper/main.tex
Results 1

@@
 \section{Results}
+
 \subsection{Motile cilia induce flow compartmentalization within the brain ventricles}
 
-We model the compartmentalized and pulsatile CSF flow observed in vivo~(\Crefpanels{fig:fig1}{b, c})
-by the Stokes equations, and solve the equations numerically using a finite element method.
-To characterize CSF flow patterns predicted by
-computational fluid dynamics within the brain ventricles, we first
-consider the simulated CSF velocity and pressure when only modeling
-cilia motion, disregarding cardiac pressure pulsations. The
-bidirectional traction induced by the motile cilia
-inherently leads to a partial compartmentalization of the ventricular
-system, with large-scale vortex structures in the anterior and middle
-ventricles~(~\Crefpanels{fig:fig1}{e}). The highest velocities ($26.5$ \textmu m/s)
-occur in the vicinity of the dorsal cilia in the middle ventricle.
-
-To examine the effect of cardiac pressure pulsations,
-we next consider a no-cilia model variation. In this scenario, the vortex structures
-generated by the ciliary motion vanish. The simulated CSF
-flow is pulsatile as a result of the sinusoidal pressure gradient (~\Crefpanels{fig:fig1}{f, g}),
-with a peak velocity magnitude of $4.8$ \textmu m/s. At each time instant, the flow
-is unidirectional, with CSF initially flowing rostrocaudally (positive $x-$axis) before changing
-direction to caudorostral in the middle of the cardiac cycle.
-
-Finally, we consider the baseline model, simulating flow driven by both cilia
-and cardiac pulsations. We observe persistent flow features,
-with vortex-structures in the anterior and middle ventricles
-and directional flow in the posterior ventricle (~\Crefpanels{fig:fig1}{h--j},
-\fixme{Supplementary video 1}). These characteristic patterns suggest
-that the flow in the anterior and middle ventricles is majorly driven
-by cilia, while the cardiac pressure pulsations dominate
-within the posterior ventricle and in the ducts connecting the ventricular
-compartments. Over one cardiac cycle, the CSF flow
-speed reaches up to 27.7 \textmu m/s, dorsally in the posterior part
-of the middle ventricle. This peak is attained at the time instant
-coinciding with the time of peak caudal cardiac pulsatile flow, since 
-both the tangential traction induced by the cilia and the pulsatile
-pressure-driven flow are aligned with the rostrocaudal 
-axis. Using the observed maximum velocity magnitude and choosing the height of
-the middle ventricle ($110$ \textmu m) as a characteristic length
-scale yields a Reynolds number $\mathrm{Re} \approx 0.004$,
-justifying the assumption of Stokes flow. In summary, the computational
-CSF flow model reproduces the flow features observed
-in vivo~\cite{Olstad2019CiliaryDevelopment}.
+% Why? (Intersting point #1. However, we do not know aspect #2. 
+% How? (We therefore ...)
+% What ...
+
+In-vivo particle tracking reveals characteristic CSF flow patterns in
+zebrafish larval brain ventricles
+(\Crefpanels{fig:fig1}{a--c})~\cite{Olstad2019CiliaryDevelopment}. We
+first ask whether we can accurately represent these flow patterns with
+computational fluid dynamics driven by cardiac pulsations and motile
+cilia lining the brain ventricles.
+
+We model the net forces induced by motile cilia as a steady
+bidirectional traction acting on parts of the ventricular wall
+(\Crefpanels{fig:fig1}{d}). Simulations show that this traction alone
+leads to a partial compartmentalization of the ventricular system,
+with large-scale vortex structures in the anterior, middle and
+posterior ventricles (\Crefpanels{fig:fig1}{e}). The highest flow
+speeds ($26.5$ \textmu m/s) occur in the vicinity of the dorsal cilia
+in the middle ventricle. To model the cardiac pulsations, we impose a
+pulsatile pressure difference between the anterior and posterior
+boundaries (\Crefpanels{fig:fig1}{d, \fixme{g}}). The resulting flow
+is pulsatile and directional (\Crefpanels{fig:fig1}{\fixme{f}}), and
+in the absence of the cilia, the vortex structures vanish. The
+velocity magnitude peaks at $4.8$ \textmu m/s. CSF initially flows
+rostrocaudally before changing direction to caudorostral in the middle
+of the cardiac cycle.
+
+When combining the contributions, we recognize flow features
+persisting throughout the cardiac cycle, now with vortex structures in
+the anterior and middle ventricles and directional flow in the
+posterior ventricle (\Crefpanels{fig:fig1}{h--j}, \fixme{Supplementary
+  video 1}). These characteristic patterns suggest that the flow in
+the anterior and middle ventricles is primarily driven by the motile
+cilia, while the cardiac pressure pulsations dominate within the
+posterior ventricle and in the ducts connecting the ventricular
+compartments. The CSF flow speed peaks at the time of peak caudal
+cardiac pulsatile flow, when both the tangential traction induced by
+the cilia and the pulsatile pressure-driven flow are aligned with the
+rostrocaudal axis, reaching up to 27.7 \textmu m/s dorsally in the
+posterior part of the middle ventricle. The flow Reynolds number is
+$\mathrm{Re} \approx 0.004$, justifying the assumption of Stokes
+flow. In summary, the computational CSF flow model reproduces the flow
+features observed in vivo~\cite{Olstad2019CiliaryDevelopment}.
+
+%% Over one cardiac cycle, the CSF flow speed reaches up to
+%% 27.7 \textmu m/s, dorsally in the posterior part of the middle
+%% ventricle. This peak is attained at the time instant coinciding with
+%% the time of peak caudal cardiac pulsatile flow,
+
+%% Using the observed maximum velocity magnitude and choosing the height
+%% of the middle ventricle ($110$ \textmu m) as a characteristic length
+%% scale yields a Reynolds number $\mathrm{Re} \approx 0.004$, justifying
+%% the assumption of Stokes flow.
+
+%We model the compartmentalized and pulsatile CSF flow observed in vivo~(\Crefpanels{fig:fig1}{b, c}) by the Stokes equations, and solve the equations numerically using a finite element method.
+
+%To characterize CSF flow patterns predicted by
+%computational fluid dynamics within the brain ventricles,
+
+%we first consider the simulated CSF velocity and pressure when only
+%modeling cilia motion, disregarding cardiac pressure pulsations.
 

### 2025-03-06 paper/main.tex
Results 2

@@
 \subsection{Ventricular solute transport is advection-dominated for larger molecules}
-We next explore the impact of these CSF flow patterns and magnitudes
-on solute transport within the brain ventricles.
-To this end, we simulate the distribution and evolution
-of different solutes subjected to photoconversion within a region of
-interest in the dorsal region of the middle ventricle (ROI 1)
-(~\Crefpanels{fig:fig2}{a}). We consider the spread of
-a solute concentration with a given molecular diffusion coefficient,
-corresponding to exosomes ($D_1 = 1.63 \times 10^{-12}$ m$^2$/s),
-a circa 90 kDa protein STM-GFP ($D_2 = 5.75 \times 10^{-11}$ m$^2$/s),
-and the 26 kDa photoconvertible protein  Dendra2 ($D_3 = 1.15 \times 10^{-10}$ m$^2$/s).
-As expected, transport occurs more
-rapidly with increasing diffusion coefficient. Interestingly, the
-distribution patterns differ between the solutes.
-For the smallest diffusion coefficient, representing
-exosomes, the advective transport by the CSF flow dominates diffusion
-(\Crefpanels{fig:fig2}{b}). The vortex structures of the velocity field
-carry over into the concentration field, indicating that transport
-along the streamlines is more rapid than the diffusion across the
-streamlines. The balance between diffusion and advection shifts with
-increasing diffusion coefficients: the CSF flow structures become more
-obfuscated, and the solute spreads more uniformly throughout the
-ventricular geometry (\Crefpanels{fig:fig2}{c, d}). Notably, the
+
+%We next explore the impact of these CSF flow patterns and magnitudes
+%on solute transport within the brain ventricles.
+
+Proteins, neurotransmitters and other molecular substances
+intrinsically diffuse within the brain ventricles, but are also
+advected by the flow of CSF. A natural question is which of these
+mechanisms that dominate for any given type of solute. To address this
+question, we simulate the distribution and evolution of three
+different solutes injected within a region of interest (ROI1) in the
+dorsal region of the middle ventricle (\Crefpanels{fig:fig2}{a}),
+subject to the CSF flow induced by motile cilia and cardiac pressure
+pulsations. In particular, we consider three different molecular
+diffusion coefficients, corresponding to a large exosome ($D_1 = 1.63
+\times 10^{-12}$ m$^2$/s), a 90 kDa protein STM-GFP ($D_2 = 5.75
+\times 10^{-11}$ m$^2$/s), and a 26 kDa photoconvertible protein
+Dendra2 ($D_3 = 1.15 \times 10^{-10}$ m$^2$/s).
+
+%As expected, transport occurs more rapidly with increasing diffusion
+%coefficient.
+
+Interestingly, the distribution patterns differ between the
+solutes. For the smallest diffusion coefficient, representing
+exosomes, the advective transport by the CSF dominates diffusion: the
+CSF flow structures carry over into the concentration field,
+indicating that transport along the streamlines is more rapid than the
+diffusion across the streamlines (\Crefpanels{fig:fig2}{b}). The
+balance between diffusion and advection shifts with increasing
+diffusion coefficient as the solute spreads more uniformly throughout
+the ventricular geometry (\Crefpanels{fig:fig2}{b--d}). Notably, the
 smaller solutes with higher diffusion coefficients spread more quickly
-to regions distal to the photoconversion site.
+to distal regions. Computing Péclet numbers, we find that
+$\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for
+$D_1$, $D_2$ and $D_3$, respectively. With all $\mathrm{Pe} > 1$, this
+indicates that advection is the dominant transport mechanism on a
+global scale.
+
+%% To quantify the balance of advection versus diffusion as transport
+%% mechanisms, we calculate the Péclet numbers $\mathrm{Pe}_1=519$,
+%% $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and
+%% $D_3$, respectively.  Since $\mathrm{Pe}>1$, this indicates that
+%% advection is the dominant transport mechanism on a global scale.
+
 \begin{figure}%[H]
@@
 
-To quantify the transport of solute, we plot the profile of the mean
-concentrations $\cbar_i(t)$ as functions of time
-(\Crefpanels{fig:fig2}{e--g}) and
-the times $\hat{t}$ when the mean concentrations $\cbar_i$ first exceed
-a threshold value $\hat{c}$ (\Crefpanels{fig:fig2}{h})
-in 6 ROIs (\Crefpanels{fig:fig2}{a}).
-The dynamics at the site of photoconversion (ROI 1)
-is logarithmic and follows from imposing \Cref{eq:photoconversion_curve}.
-For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
-(\Crefpanels{fig:fig2}{e--g}),
-which results in smaller times-to-threshold
-(\Crefpanels{fig:fig2}{h}).
-For all three diffusion coefficients, the dynamics of ROI 5
-is significantly delayed compared to ROI 2--4,
-and ROI 6 is the slowest. Notably, for $D_1$ the mean concentration
-in ROI 6 is close to zero at the end of simulation.
-To quantify the balance of advection versus diffusion as transport mechanisms,
-we calculate the Péclet numbers $\mathrm{Pe}_1=519$,
-$\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and $D_3$, respectively.
-Since $\mathrm{Pe}>1$, this indicates that advection is the
-dominant transport mechanism on a global scale.
+To further quantify the solute transport, we examine the mean
+concentrations $\cbar_i(t)$ in the six ROIs over time
+(\Crefpanels{fig:fig2}{e--g}) and, in addition, the times $\hat{t}_i$
+when the mean concentrations first exceed a threshold value
+$\hat{c}_i$ (\Crefpanels{fig:fig2}{h}).  Higher diffusion coefficients
+result in more rapid transport (\Crefpanels{fig:fig2}{e--g}), with
+lower times-to-threshold in ROIs 2--6 (\Crefpanels{fig:fig2}{h}). For
+all three diffusion coefficients, the solute first spreads within the
+middle ventricle, covering ROIs 2--4, before appearing in the anterior
+ventricle (ROI5) and finally reaching the posterior ventricle
+(ROI6). Notably, the exosomes, associated with the smallest diffusion
+coefficient, do not reach the posterior ventricle (ROI6) within the
+simulated time frame.
+
+%% For all three diffusion coefficients, the dynamics of ROI 5
+%% is significantly delayed compared to ROI 2--4,
+%% and ROI 6 is the slowest.
+
+%The dynamics at the site of photoconversion (ROI 1)
+%is logarithmic and follows from imposing \Cref{eq:photoconversion_curve}.
+
+%% For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
+%% (\Crefpanels{fig:fig2}{e--g}),
+%% which results in smaller times-to-threshold
+%% (\Crefpanels{fig:fig2}{h}).
 

### 2025-03-06 paper/main.tex
Results 3

@@
 
-\subsection{Validation of the simulations with experimental data}
-To validate our computational model, we performed photoconversion experiments
-in transgenic zebrafish larvae expressing the secreted Dendra2 in their brain ventricles.
-Our photoconversion protocol consisted of the acquisition of a baseline,
-before localized exposure to a UV laser (at the ROI 1 location)
-that converts Dendra2 from a green to a red emitting fluorescent protein. 
-To quantify the transport of photoconverted proteins, we measured and
-calculated the change in fluorescence intensity $\Delta F = (F(t)-F_0)/F_0$
-over time (\Crefpanels{fig:fig3}{a},
-$F_0$ being the average fluorescence at baseline).
-
-We obtained very similar kinetics curves (\Crefpanels{fig:fig3}{a, b})
-and time-to-threshold values (\Crefpanels{fig:fig3}{c, d}) when comparing our
-experiments (\Crefpanels{fig:fig3}{a, c}) with
-simulation (\Crefpanels{fig:fig3}{b, d}).
-Importantly, since the initial condition of the simulation is a mean concentration of zero,
-the mean concentration $\cbar$ can be interpreted as the change in mean concentration and
-is thus a similar metric to $\Delta F$.
-The final values of $\cbar$ in our simulations 0.76, 0.72, 0.82, 0.56 and 0.35
-(ROIs 2--6, respectively)
-are generally higher than the mean experimental values 0.63, 0.71, 0.67, 0.29 and 0.18 for $\Delta F$.
-Notwithstanding similar dynamics, we observe small differences between the experiments and simulation.
-For instance, transport in ROIs 2--6 is faster in the simulation and reaches higher final values.
-Moreover, the $\cbar$ profiles of ROIs 3--4 are opposite order in
-the simulations as compared to the experiments.
-Despite observing small differences, the in vivo experiments and
-simulations are similar enough to convincingly validate the model.
-\begin{figure}[H]
+\subsection{Model validation by comparison with photoconversion experiments}
+
+To validate the model predictions, we performed photoconversion
+experiments in transgenic zebrafish larvae expressing the secreted
+Dendra2 in their brain ventricles. Our photoconversion protocol
+consisted of the acquisition of a baseline fluorescence intensity
+$F_0$, before localized exposure to a UV laser (at ROI 1) that
+converts Dendra2 from a green- to a red-emitting fluorescent
+protein. To quantify the transport of photoconverted proteins, we
+measured and calculated the change in fluorescence intensity $\Delta F
+= (F(t)-F_0)/F_0$ over time (\Crefpanels{fig:fig3}{a}).
+
+Comparing the intensity changes with the simulated concentration
+profiles in ROIs 1--6 (\Crefpanels{fig:fig3}{a, b}) show that the
+model predictions agree well with the experimental measurements. We
+note minor differences however. The simulated values of $\cbar_i$ at
+the final time (0.72, 0.82, 0.56 and 0.35 in ROIs 2--6, respectively)
+are generally higher than the corresponding experimental $\Delta F$
+values (0.63, 0.71, 0.67, 0.29 and 0.18). Moreover, we observe
+differences in the distribution within the middle ventricle,
+especially with regard to ROIs 2 and 3. Overall, we note that the time
+to reach a 25\% threshold agree well between the model predictions and
+experimental values (\Crefpanels{fig:fig3}{c, d}).
+
+%% the $\cbar$ profiles of ROIs 3--4 are opposite order in the
+%% simulations as compared to the experiments.
+
+%% Notwithstanding similar dynamics, we observe small differences between
+%% the experiments and simulation.
+
+%% For instance, transport in ROIs 2--6 is faster in the simulation and
+%% reaches higher final values.
+
+%% We obtained very similar kinetics curves (\Crefpanels{fig:fig3}{a, b})
+%% and time-to-threshold values (\Crefpanels{fig:fig3}{c, d}) when
+%% comparing our experiments (\Crefpanels{fig:fig3}{a, c}) with
+%% simulation (\Crefpanels{fig:fig3}{b, d}).
+
+%% Importantly, since the initial condition of the simulation is a mean
+%% concentration of zero, the mean concentration $\cbar$ can be
+%% interpreted as the change in mean concentration and is thus a similar
+%% metric to $\Delta F$.
+
+\begin{figure}%[H]
     \centering

### 2025-03-06 paper/main.tex
Updates with MER and HH

@@
 \subsection{Absence of ciliary motion affects local protein distribution}
-Since CSF flow is highly disturbed in the absence of motile cilia, we
-want to assess the impact of cilia motion on solute distribution. To this end,
-we measured the movement of photoconverted Dendra2 signal
-in control and motile-cilia mutant (\emph{smh}) zebrafish .
-By plotting the means of $\Delta F$ (\Crefpanels{fig:fig4}{a})
-and the time to threshold
-across the control and mutant cohorts (\Crefpanels{fig:fig4}{b}),
-we identified a significant
-difference in Dendra2 distribution in ROIs 2 and 4, but not in ROIs 3, 5, and 6. In ROIs 2 and 4,
-which measure Dendra2 distribution downstream of the photoconversion site,
-we observed a slower increase of fluorescence intensity,
-resulting in $45\%$ (ROI 2) and $25\%$ (ROI 4)
-higher mean times-to-threshold in the \emph{smh}
-mutants compared to controls (\Crefpanels{fig:fig4}{b}).
-
-Next, to identify whether our model would recapitulate these findings,
-we simulate protein transport by using the only-cardiac/no-cilia flow model 
-and compare it with the baseline model
-(both cilia and cardiac motion) (\Crefpanels{fig:fig4}{c}).
-Similar to our experiments, we observe slower dynamics in simulations for ROIs 2 and 4,
-but small changes for ROIs 3 and 6.
-Interestingly, the difference was even greater for the simulations,
-with the times-to-threshold in ROI 2 and 4 being 90\% and 34\% higher
-in the absence of cilia-mediated flow.
-Moreover, ROI 5 exhibits very different $\cbar$ profiles for the two
-configurations in our computational model,
-but not in our experimental data.
-Altogether, our findings identify that diffusion plays an important
-role for solute movement to regions upstream in the cilia flow fields or to distant ventricles.
+
+\mer{Sentence on why absence of motile cilia is intersting: Cilia
+  motion is key to development and absence of cilia is associated with
+  pathologies.} As observed both experimentally and computationally,
+the absence of motile cilia alters the CSF flow patterns. We next
+investigate the implications of these changes on intraventricular
+transport.
+
+We first experimentally measured the movement of photoconverted
+Dendra2 signal in control and motile-cilia mutant (\emph{smh})
+zebrafish. In ROIs 2 and 4, which measure Dendra2 distribution
+downstream of the photoconversion site, we observed a slower increase
+of fluorescence intensity (\Crefpanels{fig:fig4}{a}), resulting in
+$45\%$ (ROI 2) and $25\%$ (ROI 4) higher mean times-to-threshold
+(\Crefpanels{fig:fig4}{b}), in the \emph{smh} mutants compared to
+controls. We found no significant differences in the Dendra2
+distribution in ROIs 3, 5, and 6 between \emph{smh} mutants and
+controls.
+
+We next mimic the \emph{smh} mutants in the computational model by
+considering transport of Dendra2 with CSF flow driven by cardiac
+pressure pulsations only, representing the absence of motile
+cilia. Comparing the in-silico mutants with transport predictions in
+the presence of both cardiac pulsations and motile cilia, we observe
+noticeably delayed dynamics in ROIs 2, 4 and 5, but little change for
+ROIs 3 and 6 (\Crefpanels{fig:fig4}{c}).
+
+\mer{MER: MER and HH stopped here.}
+
+Comparing with the experiment, the difference between the control and
+mutant scenarios was even greater for the simulations, with the
+times-to-threshold in ROI 2 and 4 being 90\% and 34\% higher in the
+absence of cilia-mediated flow. Moreover, ROI 5 exhibits very
+different $\cbar$ profiles for the two configurations in our
+computational model, but not in our experimental data.  Altogether,
+our findings identify that diffusion plays an important role for
+solute movement to regions upstream in the cilia flow fields or to
+distant ventricles.
+
+%% Again, the simulated Dendra2 distribution patterns differ from the
+
+%% Next, to identify whether our model would recapitulate these findings,
+%% we simulate CSF flow driven only by cardiac pressure pulsations and
+%% the resulting diffusion and advection of
+
+%% Dendra2 transport
+
+%% by using the only-cardiac/no-cilia flow model 
+%% and compare it with the baseline model
+%% (both cilia and cardiac motion) (\Crefpanels{fig:fig4}{c}).
+
 \begin{figure}[H]

### 2025-03-07 paper/main.tex
update template geometry

@@
 
-%\pagestyle{fancy}
-%\rhead{}%\includegraphics[width=2.5cm]{vch-logo.png}}
-\pagestyle{plain} % MER
+\pagestyle{plain}
+
+\begingroup
+\parindent0pt
 
@@
 \begin{affiliations}
-\noindent H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
+H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
 Department of Numerical Analysis and Scientific Computing,
 Simula Research Laboratory, Kristian Augusts gate 23, 0164 Oslo, Norway\\
-Email Address: hherlyng@simula.no \\ 
+Email Address: hherlyng@simula.no
+
+\medskip
 Dr.~M.~E.~Rognes \\
-K.~G.~Jebsen Centre for Brain Fluid Research, Oslo, Norway \\
+K.~G.~Jebsen Centre for Brain Fluid Research, Oslo, Norway
+
+\medskip
 Dr.~I.~Jeong, Dr.~N.~Jurisch-Yaksi\\
@@
 Email Address: nathalie.jurisch-yaksi@ntnu.no
-
 \end{affiliations}
+
+\medskip
 
@@
 \end{abstract}
+
+\endgroup % End 0parindent group
 
@@
     \sum_{f\in \mathcal{F}}\int_f{2\mu\frac{\gamma}{\avg{h}}\jump{P_{\nn}(\uu_h)}
-    \cdot\jump{P_{\nn}(\vv_h)}}\\
-    &-\sum_{f\in \mathcal{F}}\int_f{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}
-    -\sum_{f\in \mathcal{F}}\int_f{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}
+    \cdot\jump{P_{\nn}(\vv_h)}}\,\mathrm ds\\
+    &-\sum_{f\in \mathcal{F}}\int_f{2\mu\avg{\beps(\uu_h)}\cdot\jump{\vv_h}}\,\mathrm ds
+    -\sum_{f\in \mathcal{F}}\int_f{2\mu\avg{\beps(\vv_h)}\cdot\jump{\uu_h}}\,\mathrm ds
 \end{align*}
@@
         a_{\mathrm{stab}}(c_h, \phi_h)
-        = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}
-        +\sum_{f\in \mathcal{F}}\int_f{\jump{c_h \hat{u}_h}\cdot\jump{\phi_h}}  \\
-         -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}
-         -\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla c_h}\cdot\jump{\phi_h}},
+        = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}\,\mathrm ds
+        +\sum_{f\in \mathcal{F}}\int_f{\jump{c_h \hat{u}_h}\cdot\jump{\phi_h}}\,\mathrm ds  \\
+         -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}\,\mathrm ds
+         -\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla c_h}\cdot\jump{\phi_h}}\,\mathrm ds,
     \end{aligned}\label{eq:SIP_stabilization}

### 2025-03-10 paper/main.tex
Results 5 and 6

@@
     observed during experiments of photoconversion of Dendra2 proteins in ROI 1. 
+    Bold lines are mean values of the cohort and shaded regions cover one standard devation errors
+    in the mean.
     \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
@@
 
-We next mimic the \emph{smh} mutants in the computational model by
+The \emph{smh} mutants are mimicked in the computational model by
 considering transport of Dendra2 with CSF flow driven by cardiac
@@
 
-\mer{MER: MER and HH stopped here.}
-
-Comparing with the experiment, the difference between the control and
+Compared to experimental data, the difference between the control and
 mutant scenarios was even greater for the simulations, with the
 times-to-threshold in ROI 2 and 4 being 90\% and 34\% higher in the
-absence of cilia-mediated flow. Moreover, ROI 5 exhibits very
-different $\cbar$ profiles for the two configurations in our
-computational model, but not in our experimental data.  Altogether,
-our findings identify that diffusion plays an important role for
+absence of cilia-mediated flow. Moreover, the ROI 5 $\cbar$ profiles
+for the two configurations in our computational model deviate,
+which is not the case in the experiments.  Altogether,
+our findings identify that, for smaller proteins such as Dendra2,
+diffusion plays an important role for
 solute movement to regions upstream in the cilia flow fields or to
-distant ventricles.
-
-%% Again, the simulated Dendra2 distribution patterns differ from the
-
-%% Next, to identify whether our model would recapitulate these findings,
-%% we simulate CSF flow driven only by cardiac pressure pulsations and
-%% the resulting diffusion and advection of
-
-%% Dendra2 transport
-
-%% by using the only-cardiac/no-cilia flow model 
-%% and compare it with the baseline model
-%% (both cilia and cardiac motion) (\Crefpanels{fig:fig4}{c}).
+distant ventricles, while cilia affect the downstream mean concentrations.
 
@@
     \caption{\textbf{a.} Relative change in fluorescence intensity $F(t)$
-    in each region of interest (ROI) for control (black lines)
-    and \emph{smh} mutant (red lines) fish. 
+    in each region of interest (ROI) for control (black lines, $n=8$)
+    and \emph{smh} mutant (red lines, $n=6$) fish. 
+    Bold lines are mean values of the cohorts and shaded regions cover one standard devation errors
+    in the means.
     \textbf{b.} Times when $\Delta F(t)$ first exceeds a threshold value,
@@
 \subsection{Loss of cilia motility in specific subpopulation slows down transport}
+
 We previously identified three distinct ciliated cell lineages in the
 zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain}.
-To identify the role of these lineages on CSF transport, we simulate transport
-upon region-specific cilia paralysis by modifying the boundary conditions
-of the CSF flow model. Three cilia-covered regions were considered separately:
+To identify the effects of these lineages on CSF flow and transport, 
+we investigate region-specific cilia paralysis with the computational model.
+Three cilia-covered regions were considered paralyzed separately:
 the telencephalic (anterior) ventricle, and the dorsal and ventral parts
 of the diencephalic (middle) ventricle (\Crefpanels{fig:fig5}{a}).
-The cilia tangential traction boundary condition is for each case
-changed to a free-slip boundary condition in the paralyzed region,
+To simulate cilia paralysis, the cilia tangential traction boundary condition
+is for each case changed to a free-slip boundary condition
+in the paralyzed region,
 prescribing zero tangential forces to
 represent absence of cilia motion.
-We simulate CSF flow modeled by the Stokes equations with the
-modified boundary conditions and use the resulting
-velocity fields in transport simulations.
 
@@
 
-Changes in the transport dynamics of Dendra2 are most prominent when removing the dorsal cilia
-in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
-exhibit changes in the dynamics of $\cbar$ (\Crefpanels{fig:fig5}{c}).
-Compared to the baseline model results, we observe a slower increase and lower final concentration
+Changes in the transport of Dendra2 are most prominent when removing the dorsal cilia
+in the diencephalic ventricle. The mean concentration profiles 
+of all ROIs (except ROI 1, where we impose the photoconversion curve)
+exhibit changes (\Crefpanels{fig:fig5}{c}).
+Compared to the baseline model results, we observe less solute distribution
 in the middle and anterior ventricles (ROIs 2--5),
 and more rapid transport to the posterior ventricle (ROI 6).
-In contrast, removal of telencephalic cilia does not alter the evolution of the
-mean concentration $\cbar$ with time (\Crefpanels{fig:fig5}{c}).
+Meanwhile, removal of telencephalic cilia does not alter the 
+mean concentrations (\Crefpanels{fig:fig5}{c}).
 Finally, without ventral cilia in the diencephalic ventricle,
@@
 Variations in ventricular morphology impact CSF flow patterns.
-To assess how ventricular morphologies influence solute distribution,
+To assess how these variations influence solute distribution,
 we consider four alternative brain ventricles meshes:
@@
 one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
-and the combination of the above three modifications (\Crefpanels{fig:fig6}{a}). In these
+and the combination of the above three modifications (\Crefpanels{fig:fig6}{a, b}). In these
 four modified geometries the volume is reduced by 3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively,
 compared to the original geometry.
-We simulate CSF flow in the modified geometries with the baseline flow model
-and use the resulting velocity field to simulate transport of Dendra2
-(\Crefpanels{fig:fig6}{b}).
 
@@
 (\Crefpanels{fig:fig6}{d}), which are the cilia that propel CSF and solute towards ROI 6.
-On the other hand, constricting the duct connecting the middle and the posterior ventricle
+Constricting the mid-hind brain connection
 leads to less transport into the posterior ventricle (ROI 6),
-and slightly more transport towards the anterior ventricle (ROI 5)
-(\Crefpanels{fig:fig6}{c}, shrunk mid-hind scenario).
+and slightly more transport towards the anterior ventricle (ROI 5).
 Faster transport to the anterior ventricle (ROI 5) and slower transport to the
@@
 shrunk middle ventricle.
-Here also the change in transport to ROI 6 is counter to expectation when comparing with
-ventral cilia forces, with transport reducing in spite of a 6.6\% increase in the
-ventral cilia forces.
+Here the transport to the posterior ventricle (ROI 6) is reduced,
+in spite of a 6.6\% increase in the ventral cilia forces.
 Additionally, for the shrunk middle configuration, the transport upstream of CSF flow towards the
 ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
+
 For the mesh where all three ventricles are modified,
 we observe higher retention of solute in the middle ventricle (ROIs 2--4),
-while both the anterior and the posterior ventricles (ROIs 5 and 6) have lower mean concentrations.
-Altogether, our results show that the geometry and width of the ventricular ducts matter
+while both the anterior and the posterior ventricles (ROIs 5 and 6) have reduced
+mean concentrations. Altogether, our results show that the geometry and
+width of the ventricular ducts matter
 for solute transport, with notable differences in transport from relatively small
@@
 Indeed, there was essentially zero solute in the posterior ventricle at the
-final simulation time (around 850 s), a ventricle where transport is largely driven
+final simulation time (around 860 s), a ventricle where transport is largely driven
 by diffusion due to the absence of motile cilia.
@@
 $L=200$ \textmu m from the middle to the posterior ventricle is approximately 24500 s.
-Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same
-distance would happen on a timescale of the order of $t_a=L/\overline{U}=141$ s.
+Advective transport by the mean velocity $\overline{U}=2.4 \ \mu$m/s over the same
+distance would happen on a timescale of the order of $t_a=L/\overline{U}=83$ s.
 Comparing this with the minuscule values of $\cbar_6$ after simulating transport
@@
 
-\subsection{Computational model assumptions and boundary conditions}
-To model CSF, we employed slip boundary conditions at the ventricular walls,
-contrasting the classical choice of a noslip boundary condition.
-The use of slip boundary conditions is motivated by experimental observations of the
+\subsection{Computational modeling aspects}
+We chose to model the cilia as a force
+exerted tangentially on the boundary, as opposed to a
+couple of previous continuum model simulation studies of
+cilia-mediated flow where cilia were represented by body
+forces,~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}.
+We employed slip boundary conditions at the ventricular walls,
+motivated by experimental observations of the
 flow field in zebrafish embryo brain ventricles, both previously and in this work, in which
 the fluid velocity increases towards the
-wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. Slip boundary
-conditions allow for this behavior, in contrast to a noslip condition where the velocity
-has to go to zero at the wall.
-
-As opposed to a couple of previous continuum model simulation studies of
-cilia-mediated flow where cilia were represented by body
-forces,~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
-we chose to model the cilia as a force
-exerted tangentially on the boundary.
-We deem this a good representation of the real nature of cilia,
-since they are microscale structures confined to the ventricular walls that
-generate flow through collective motion. Furthermore, it avoids the need of mesh
-refinement near the ciliated boundaries in the case that a
-body force were to be applied in a cilia layer of depth around
-5 \textmu m~\cite{Salman2022ComputationalEmbryo}.
+wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. 
+In addition to its favorable mass-conserving property, the 
+Brezzi-Douglas-Marini and discontinuous Galerkin (BDM-DG) discretization scheme 
+we employed for the Stokes equations
+lets us impose the impermeability condition strongly, and the tangential
+traction boundary condition weakly, without any tailored approach,
+since these boundary conditions appear naturally in the weak form of the
+Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
+elements were to be used, the impermeability boundary condition must
+be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
+or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
+Bertoluzza2017BoundaryHemodynamics}.
+
+The BDM-DG scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employed for the Stokes equations
+is computationally more expensive than a more conventional approach based on
+e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
+($P_2-P_1$ elements) or lower-order enriched
+elements~\cite{Brezzi2011MixedMethods},
+such as the mini-element ($P_1-P_1$ with a velocity stabilization).
+Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
+than or equal to $k$.
+We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
+as the elements by definition satisfy the incompressibility constraint for the fluid.
+This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
+an important property for the stability of the advection-diffusion equation\cite{CITATION}.
 
@@
 and the advective transport then requires handling of in- and outflux boundary conditions.
-We set boundary conditions such that the total mass is conserved in the
+We set an approximate periodic boundary condition on the the in- and outflux boundaries,
+such that the total mass is conserved in the
 limit that the timestep size is zero, reflecting our assumption that the
@@
 constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}. 
-
-Our approach can be interpreted as an approximate periodic boundary condition, where we set
-the inflow boundary flux at timestep $n$ equal to the outflow boundary flux at the previous
-timestep $n-1$. This is expected to be of low-order accuracy, and for high Péclet numbers,
-the boundary condition affects the concentration field in the vicinity of the
-in- and outflow boundaries
-due to large advective fluxes. For the simulation scenarios we considered,
-both in terms of model parameters
-and time span, the photoconversion region where solute originates
-is far enough away from the in- and outflow
-boundaries for the flux boundary condition to not significantly impact the results. Nevertheless,
-we deliberately excluded the space proximal to in- and outflow boundaries in
-the anterior and posterior regions of interest (5 and 6) to limit adverse effects.
+We deliberately excluded the space proximal to in- and outflow boundaries in
+the anterior and posterior regions of interest (5 and 6) to limit adverse effects of 
+the advective transport at the in- and outflux boundaries on the mean concentrations.
 
@@
 
-\subsection{Numerical approximation and convergence rates}
-The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme
-($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employ for the Stokes equations
-is computationally more expensive than a more conventional approach based on
-e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
-($P_2-P_1$ elements) or lower-order enriched
-elements~\cite{Brezzi2011MixedMethods},
-such as the mini-element ($P_1-P_1$ with a velocity stabilization).
-Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
-than or equal to $k$.
-We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
-since numerical experiments proved that a divergence-free velocity field was
-fundamental to attain a stable discretization of the advection-diffusion equation
-in advection-dominated regions. Using conventional
-Taylor-Hood elements for the Stokes equations
-stability of the advection-diffusion discretization either
-required excessive mesh refinement and/or problem-specific tuning of
-hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization
-method~\cite{Franca1992StabilizedModel}, which is why we also opted for a DG method
-for the advection-diffusion equation.
-Probing numerical values of the divergence of
-the velocity when using Taylor-Hood elements for the fluid equations revealed that,
-on the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was
-in the order of $10^{-6}$, while the
-maximum value of the divergence of the velocity was of order unity. This is a result
-of the fact that incompressibility is only achieved in a (global) weak sense when
-employing Taylor-Hood elements. On a refined mesh with roughly six times as many
-computational cells as the standard mesh, the numerical values of
-$\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still
-of order unity. This may lead to the
-hyperbolic advective term in the advection-diffusion equation accumulating errors
-that grow unstable over time.
-
-In addition to its favorable mass-conserving property, the BDM-DG scheme
-lets us impose the impermeability condition strongly, and the tangential
-traction boundary condition weakly, without any tailored approach,
-since these boundary conditions appear naturally in the weak form of the
-Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
-elements were to be used, the impermeability boundary condition must
-be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
-or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
-Bertoluzza2017BoundaryHemodynamics}.
-
-A priori error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
-derived in a mesh-dependent broken $H^k$-norm for $\uu$ and the $L^2$-norm for the pressure.
-The respective error norms are expected to decay with order $k$~\cite{Cockburn2005AEquations}.
-For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
-reports the velocity errors in the standard $H^k$ norm. Using polynomial degree  
-$k=1$, we observe linear convergence in both the velocity and the pressure.   
-\mk{MK: I see 1.5 in the table for $\uu$ in $L^2$?}
-\lyng{HH: Yes, we should expect 2 there? Maybe be more specific in the comment:
-"Using polynomial degree $k=1$, we observe linear convergence in both the velocity $H^1$ error
-and the pressure $L^2$ error. For the $L^2$ error of the velocity, we observe a suboptimal
-convergence order of 1.5"}
-
 \subsection{The role of motile cilia in intraventricular flow and transport}
@@
 
-%\section{Conclusion}
 In conclusion, we have presented a numerical model
@@
 \end{equation*}
-and then averaging $\overline{u}$ in time over one cardiac cycle to yield $\overline{U} = \fixme{X}$ \fixme{unit}.
+and then averaging $\overline{u}$ in time over one cardiac cycle to yield $\overline{U} = 2.4$ \textmu m/s.
 To assess the assumption that inertial forces are negligible compared to
@@
 \end{equation*}
-with $L_r = \fixme{X}$ \fixme{unit} and $U_r = \fixme{X}$ \fixme{unit}
+with $L_r = 110$ \textmu m and $U_r = 27.7$ \textmu m/s
 as length and velocity scales characteristic of the flow.
@@
 
+\subsection{Discussion of the numerical approximation and convergence rates}
+The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme
+($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employ for the Stokes equations
+is computationally more expensive than a more conventional approach based on
+e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
+($P_2-P_1$ elements) or lower-order enriched
+elements~\cite{Brezzi2011MixedMethods},
+such as the mini-element ($P_1-P_1$ with a velocity stabilization).
+Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
+than or equal to $k$.
+We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
+since numerical experiments proved that a divergence-free velocity field was
+fundamental to attain a stable discretization of the advection-diffusion equation
+in advection-dominated regions. Using conventional
+Taylor-Hood elements for the Stokes equations
+stability of the advection-diffusion discretization either
+required excessive mesh refinement and/or problem-specific tuning of
+hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization
+method~\cite{Franca1992StabilizedModel}, which is why we also opted for a DG method
+for the advection-diffusion equation.
+Probing numerical values of the divergence of
+the velocity when using Taylor-Hood elements for the fluid equations revealed that,
+on the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was
+in the order of $10^{-6}$, while the
+maximum value of the divergence of the velocity was of order unity. This is a result
+of the fact that incompressibility is only achieved in a (global) weak sense when
+employing Taylor-Hood elements. On a refined mesh with roughly six times as many
+computational cells as the standard mesh, the numerical values of
+$\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still
+of order unity. This may lead to the
+hyperbolic advective term in the advection-diffusion equation accumulating errors
+that grow unstable over time.
+
+In addition to its favorable mass-conserving property, the BDM-DG scheme
+lets us impose the impermeability condition strongly, and the tangential
+traction boundary condition weakly, without any tailored approach,
+since these boundary conditions appear naturally in the weak form of the
+Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
+elements were to be used, the impermeability boundary condition must
+be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
+or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
+Bertoluzza2017BoundaryHemodynamics}.
+
+A priori error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
+derived in a mesh-dependent broken $H^k$-norm for $\uu$ and the $L^2$-norm for the pressure.
+The respective error norms are expected to decay with order $k$~\cite{Cockburn2005AEquations}.
+For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
+reports the velocity errors in the standard $H^k$ norm. Using polynomial degree  
+$k=1$, we observe linear convergence in the velocity in the $\mathbf{H}^1$ error norm
+and the pressure in the $L^2$ error norm.
+
 \section{Quantification of velocities in particle tracking}\label{sec:appC_particle_transport}

### 2025-03-12 paper/main.tex
update IC adv-diff, time-stepping, mesh

@@
 surface geometry, we constructed a volumetric mesh of the ventricles
-using fTetWild~\cite{Hu2020FastWild}, consisting of 132 134
-tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu
-m (4.68 \textmu m) (\Crefpanels{fig:fig1}{d}). Parts of the
+by initially using fTetWild~\cite{Hu2020FastWild} and subsequently
+local refinement functionality in~\cite{dolfinx2023preprint}. The mesh
+consists of 141 512 tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu
+m (3.1 \textmu m) (\Crefpanels{fig:fig1}{d}). Parts of the
 ventricular surfaces were marked to be lined with motile cilia
@@
 and $D$ is the molecular diffusion coefficient of the solute. 
-Initially, we set $c(\xx, 0)=0$ for all $\xx\in\Omega$.
 The ventricular walls are assumed to be impermeable (admitting \emph{no flux}: $\JJ\cdot\nn=0$),
@@
 observed in the physical photoconversion experiments. 
+To impose a smooth initial condition, we initially solve the diffusion equation
+\begin{equation*}
+    \pdifft{c} = \Tilde{D}\nabla^2 c
+\end{equation*}
+with an increased diffusion coefficient $\Tilde{D}=D\times 10^{5}$ for two timesteps.
+The solutions are normalized by their respective maximum values, and subsequently
+multiplied with the value of \Cref{eq:photoconversion_curve} at the times $t=\Delta t$
+and $t=2\Delta t$, respectively.
+The resulting concentration fields are used as initial conditions for $c(\xx, 0)$ and
+$c(\xx, \Delta t)$ for all $\xx\in\Omega$, where $\Delta t$
+is the timestep. The two initial conditions are required because of the
+two-step temporal discretization scheme employed (see~\Cref{subsec:num_approx_adv_diff} for more details.)
 
@@
 
-\subsection{Numerical approximation of the advection-diffusion equation}
+\subsection{Numerical approximation of the advection-diffusion equation}\label{subsec:num_approx_adv_diff}
 The advection-diffusion equation (\Cref{eq:adv_diff_strong}) is discretized
-with a first-order implicit Euler method in time, and a first-order,
-symmetric interior penalty DG
+with with a second-order, symmetric interior penalty DG
 method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
-conservation properties.
+conservation properties. In time, the equation is discretized with the second-order backward
+difference scheme BDF2.~\cite{Volker2016}
 To accurately approximate the solute concentrations even
@@
 with a final time of simulation $T = 856$ s.
-A DG penalty parameter $\alpha = 25$ was chosen to ensure stability of the method.
+A DG penalty parameter $\alpha = 50$ was chosen to ensure stability of the method.
 

### 2025-03-12 paper/main.tex
changes to Introduction

@@
 
-% I1: What is the problem - from big picture to focus
+% I1: What is the problem - from big picture to our precise topic - why is it interesting?
 Brain development and function depend on numerous regulatory
 processes, including the flow of cerebrospinal fluid
-(CSF)~\cite{CITATTION}. CSF is a clear liquid produced by the choroid
+(CSF)~\cite{CITATTION}. CSF is a clear liquid mostly produced by the choroid
 plexus that flows through the ventricular system and subarachnoid
-space. By transporting growth factors, nutrients, neurotransmitters
+space~\cite{Damkier2013}. By transporting growth factors, nutrients, neurotransmitters
 and metabolites as well as removing waste products, CSF regulates
-brain development and homeostasis~\cite{CITATTION}. Disturbance of the
-CSF circulation can lead to brain disorders, such as hydrocephalus
-where accumulation of CSF often requires emergency surgical
-treatment~\cite{CITATTION}.
-
-% MER: Add this to the paragraph above.
-%
-% This is particularly important since ventricular enlargement, known
-% as hydrocephalus, is observed in animal models and humans with
-% motile cilia deficiency, indicating that the cilia play a crucial
-% role for healthy brain functioning.
-
-% I2: What do we know about the problem?
+brain development and homeostasis~\cite{CITATTION}. Disruption of the
+CSF circulation is detrimental to brain health and disturbs cognitive and motor functions~\cite{Johanson2008}.
+Pathological CSF flow may also lead to
+disorders such as hydrocephalus, where accumulation of
+CSF often requires emergency surgical
+treatment, but for which there is 
+little agreement on optimal treatments~\cite{flannery2014pediatric}. 
+Of particular importance is the fact that
+hydrocephalus is observed in animal models and humans with deficient motile
+cilia~\cite{Afzelius2004Cilia, Olstad2019CiliaryDevelopment, Mitchison2017Motile},
+indicating that the cilia play a crucial role for healthy brain functioning.
+
+% I2: What do we know about the problem and the topic?
 The flow of CSF in the ventricular system is driven by multiple
@@
 cycle, respiration, neural activity, and bodily
-movement~\cite{CITATION}. Motile cilia are microscopic hair-like
+movement~\cite{Vinje2019RespiratoryMeasurements,
+Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment}.
+Motile cilia are evolutionarily conserved, microscopic hair-like
 structures that beat in a metachronal wave pattern at frequencies of
-10--30 Hz~\cite{CITATION}. Given their microscopic size, ranging from
-6 to 15 microns, the cilia clearly contributes to flow near the
-ventricular surface~\cite{CITATION}. On the other hand, cardiac,
+10--30 Hz to mediate fluid flow~\cite{mitchell2007evolution, Ringers2020Role}.
+Given their microscopic size, ranging from
+6 to 15 microns, the cilia clearly contributes primarily to flow near the
+ventricular surface in the human brain~\cite{Siyahhan2014FlowVentricles}.
+On the other hand, cardiac,
 respiratory and delta waves at lower frequencies induce pulsatile flow
-at scale in the brain ventricular system, subarachnoid space, and
+at the larger scales in the brain ventricular system, subarachnoid space, and
 subarachnoid perivascular
 spaces~\cite{Vinje2019RespiratoryMeasurements, eide2024functional,
-  causemann2025insilico, fultz2019coupled}.
-
-%How the cilia contribute to overall CSF flow and solute transport
-%remains poorly understood however.
-
-%These questions have been challenging to tackle due to technical
-%limitations.
+Causemann2025, fultz2019coupled}.
 
 % I3: What do we not know about the problem and what do we want to
-% know?
-
-%As a result, cilia dynamics are technically challenging to monitor
-%in-vivo.
+% know? What are the precise research questions we want to address?
+% Refer to specific studies and what specifically we do not know.
+
 %
@@
 %
-\mer{MER: Let's look at this next paragraph together.
-It should clearly lay out what we do not know about the problem (and what we want to find out).
-Be precise.
-Refer to specific studies and what specifically we (do not) know.
-What we know belongs nicely in the paragraph above.}
-For instance, studies using brain explants have convincingly shown
+
+Still an underexplored topic, how the motile cilia contribute to overall CSF flow
+and solute transport remains poorly understood. Experimental endeavors are
+challenging to pursue due to technical limitations: the microscopic size
+and high beating frequencies of the cilia make them difficult to monitor 
+in vivo in humans. Studies on animal models such as mice and
+zebrafish have provided unequivocal evidence that cilia are crucial
+for CSF flow in these animals~\cite{Olstad2019CiliaryDevelopment, Faubel2016Cilia}.
+It is clear that cilia affects advective intraventricular transport 
+to some extent. However a quantification of this effect, as well as of to which
+extent diffusion plays a role in transporting solutes, remains
+yet to be performed.
+
+Studies using brain explants have convincingly shown
 that cilia generate complex flow patterns at the surface of the brain
@@
 
-\begin{figure}%[hbt!]
+%%--------------RESULTS--------------%%
+\section{Results}
+
+\subsection{Motile cilia induce flow compartmentalization within the brain ventricles}
+
+% Why? (Intersting point #1. However, we do not know aspect #2. 
+% How? (We therefore ...)
+% What ...
+
+In-vivo particle tracking reveals characteristic CSF flow patterns in
+zebrafish larval brain ventricles
+(\Crefpanels{fig:fig1}{a--c})~\cite{Olstad2019CiliaryDevelopment}. We
+first ask whether we can accurately represent these flow patterns with
+computational fluid dynamics driven by cardiac pulsations and motile
+cilia lining the brain ventricles.
+
+We model the net forces induced by motile cilia as a steady
+bidirectional traction acting on parts of the ventricular wall
+(\Crefpanels{fig:fig1}{d}). Simulations show that this traction alone
+leads to a partial compartmentalization of the ventricular system,
+with large-scale vortex structures in the anterior, middle and
+posterior ventricles (\Crefpanels{fig:fig1}{e}). The highest flow
+speeds ($26.5$ \textmu m/s) occur in the vicinity of the dorsal cilia
+in the middle ventricle. To model the cardiac pulsations, we impose a
+pulsatile pressure difference between the anterior and posterior
+boundaries (\Crefpanels{fig:fig1}{d, \fixme{g}}). The resulting flow
+is pulsatile and directional (\Crefpanels{fig:fig1}{\fixme{f}}), and
+in the absence of the cilia, the vortex structures vanish. The
+velocity magnitude peaks at $4.8$ \textmu m/s. CSF initially flows
+rostrocaudally before changing direction to caudorostral in the middle
+of the cardiac cycle.
+
+When combining the contributions, we recognize flow features
+persisting throughout the cardiac cycle, now with vortex structures in
+the anterior and middle ventricles and directional flow in the
+posterior ventricle (\Crefpanels{fig:fig1}{h--j}, \fixme{Supplementary
+  video 1}). These characteristic patterns suggest that the flow in
+the anterior and middle ventricles is primarily driven by the motile
+cilia, while the cardiac pressure pulsations dominate within the
+posterior ventricle and in the ducts connecting the ventricular
+compartments. The CSF flow speed peaks at the time of peak caudal
+cardiac pulsatile flow, when both the tangential traction induced by
+the cilia and the pulsatile pressure-driven flow are aligned with the
+rostrocaudal axis, reaching up to 27.7 \textmu m/s dorsally in the
+posterior part of the middle ventricle. The flow Reynolds number is
+$\mathrm{Re} \approx 0.004$, justifying the assumption of Stokes
+flow. In summary, the computational CSF flow model reproduces the flow
+features observed in vivo~\cite{Olstad2019CiliaryDevelopment}.
+
+\begin{figure}
     \centering
@@
 \end{figure}
-
-%%--------------RESULTS--------------%%
-\section{Results}
-
-\subsection{Motile cilia induce flow compartmentalization within the brain ventricles}
-
-% Why? (Intersting point #1. However, we do not know aspect #2. 
-% How? (We therefore ...)
-% What ...
-
-In-vivo particle tracking reveals characteristic CSF flow patterns in
-zebrafish larval brain ventricles
-(\Crefpanels{fig:fig1}{a--c})~\cite{Olstad2019CiliaryDevelopment}. We
-first ask whether we can accurately represent these flow patterns with
-computational fluid dynamics driven by cardiac pulsations and motile
-cilia lining the brain ventricles.
-
-We model the net forces induced by motile cilia as a steady
-bidirectional traction acting on parts of the ventricular wall
-(\Crefpanels{fig:fig1}{d}). Simulations show that this traction alone
-leads to a partial compartmentalization of the ventricular system,
-with large-scale vortex structures in the anterior, middle and
-posterior ventricles (\Crefpanels{fig:fig1}{e}). The highest flow
-speeds ($26.5$ \textmu m/s) occur in the vicinity of the dorsal cilia
-in the middle ventricle. To model the cardiac pulsations, we impose a
-pulsatile pressure difference between the anterior and posterior
-boundaries (\Crefpanels{fig:fig1}{d, \fixme{g}}). The resulting flow
-is pulsatile and directional (\Crefpanels{fig:fig1}{\fixme{f}}), and
-in the absence of the cilia, the vortex structures vanish. The
-velocity magnitude peaks at $4.8$ \textmu m/s. CSF initially flows
-rostrocaudally before changing direction to caudorostral in the middle
-of the cardiac cycle.
-
-When combining the contributions, we recognize flow features
-persisting throughout the cardiac cycle, now with vortex structures in
-the anterior and middle ventricles and directional flow in the
-posterior ventricle (\Crefpanels{fig:fig1}{h--j}, \fixme{Supplementary
-  video 1}). These characteristic patterns suggest that the flow in
-the anterior and middle ventricles is primarily driven by the motile
-cilia, while the cardiac pressure pulsations dominate within the
-posterior ventricle and in the ducts connecting the ventricular
-compartments. The CSF flow speed peaks at the time of peak caudal
-cardiac pulsatile flow, when both the tangential traction induced by
-the cilia and the pulsatile pressure-driven flow are aligned with the
-rostrocaudal axis, reaching up to 27.7 \textmu m/s dorsally in the
-posterior part of the middle ventricle. The flow Reynolds number is
-$\mathrm{Re} \approx 0.004$, justifying the assumption of Stokes
-flow. In summary, the computational CSF flow model reproduces the flow
-features observed in vivo~\cite{Olstad2019CiliaryDevelopment}.
 
@@
 by initially using fTetWild~\cite{Hu2020FastWild} and subsequently
-local refinement functionality in~\cite{dolfinx2023preprint}. The mesh
+local refinement functionality in DOLFINx~\cite{dolfinx2023preprint}. The mesh
 consists of 141 512 tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu
@@
 The value $a=65$ was chosen to fit the fluorescence intensity curve
-observed in the physical photoconversion experiments. 
-To impose a smooth initial condition, we initially solve the diffusion equation
+observed in the physical photoconversion experiments. Because steep gradients
+in the concentration field may arise from imposing $c(\xx, t)$ in $\Omega_{\mathrm{pc}}$,
+the mesh is locally refined around this region.
+
+In order to impose a smooth initial condition, we initially solve the diffusion equation
 \begin{equation*}
@@
 \end{equation*}
-with $L_r = 110$ \textmu m and $U_r = 27.7$ \textmu m/s
+with $L_r = 110$ \textmu m (the height of the middle ventricle) and
+$U_r = 27.7$ \textmu m/s (the maximum velocity magnitude)
 as length and velocity scales characteristic of the flow.

### 2025-03-17 paper/main.tex
Nathalie comments, update fig1

@@
     motile cilia and cardiac pulsations, and their contributions to the flow patterns.
-    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
-    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
+    \textbf{b, c.} Particle tracking data visualizing CSF flow directionality (\textbf{b}) and
+    velocity magnitudes in the middle ventricle.
     \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
@@
     model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
-    \textbf{g.} Streamlines simulated with the baseline flow model at
-    a time 25\% into the cardiac cycle. %t=0.112613 s
-    \textbf{h.} Streamlines simulated with the baseline flow model at
-    a time 50\% into the cardiac cycle. %t=0.225225 s
-    \textbf{i.} Streamlines simulated with the baseline flow model at
-    a time 75\% into the cardiac cycle. %t=0.315315 s
-    \textbf{j.} Illustration of the cardiac-related normal pressure forcing imposed on the
-    anterior/posterior boundaries. Time instants of panels \textbf{f, h--j} are indicated.
+    \textbf{g.} Illustration of the cardiac-related normal pressure forcing imposed on the
+    anterior/posterior boundaries.
+    \textbf{h--j.} Streamlines simulated with the baseline flow model at
+    a time a time 25\% (\textbf{h}), 50\% (\textbf{i}) and 75\% (\texbf{j})
+    into the cardiac cycle. Times indicated in panel \textbf{g}.
+    %t=0.112613 s %t=0.225225 s %t=0.315315 s
+    Scale bars 50 \textmu m.
     }
@@
 pulsations. In particular, we consider three different molecular
-diffusion coefficients, corresponding to a large exosome ($D_1 = 1.63
+diffusion coefficients, corresponding to a large extracellular vesicle ($D_1 = 2.17
 \times 10^{-12}$ m$^2$/s), a 90 kDa protein STM-GFP ($D_2 = 5.75
@@
 solutes. For the smallest diffusion coefficient, representing
-exosomes, the advective transport by the CSF dominates diffusion: the
+extracellular vesicles, the advective transport by the CSF dominates diffusion: the
 CSF flow structures carry over into the concentration field,
@@
     \includegraphics[width=\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}\caption{Simulated distribution and evolution after photoconversion of
-    exosomes ($D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). 
+    extracellular vesicles (EVs) ($D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). 
     \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
@@
 ventricle (ROI5) and finally reaching the posterior ventricle
-(ROI6). Notably, the exosomes, associated with the smallest diffusion
+(ROI6). Notably, the extracellular vesicles, associated with the smallest diffusion
 coefficient, do not reach the posterior ventricle (ROI6) within the
@@
 experiments in transgenic zebrafish larvae expressing the secreted
-Dendra2 in their brain ventricles. Our photoconversion protocol
+Dendra2 in their brain ventricles. The approach is inspired by earlier work
+where a photoconvertible protein was injected into the ventricle~\cite{fame2016directional}.
+By using a transgenic system where the protein is directly secreted into the CSF,
+we avoid detrimental effects of intraventricular injection on CSF properties. 
+Our photoconversion protocol
 consisted of the acquisition of a baseline fluorescence intensity
@@
 
-\subsection{Absence of ciliary motion affects local protein distribution}
+\subsection{Absence of ciliary motion affects local solute distribution}
 
@@
 
-We previously identified three distinct ciliated cell lineages in the
+We previously characterized three distinct ciliated cell lineages in the
 zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain}.
@@
 
-\subsection{Modification of ventricles geometry impacts protein distribution}
+\subsection{Modification of ventricular geometry impacts solute distribution}
 Variations in ventricular morphology impact CSF flow patterns.
@@
 in the cilia-deficient computational model compared to the experimental data in
-\Cref{fig:fig4}, as the model and the fish have different duct diameters.
+\Cref{fig:fig4}, as the model and the fish have slightly different duct diameters.
 \begin{figure}[H]
@@
 our simulation experimentally. Nevertheless, our computational framework can be adapted to and implemented in
-other ventricular systems in the future, given that the flow parameters of such systems
+other ventricular systems in the future, once the flow parameters of such systems
 are comprehensively resolved. By imposing tangential traction and normal pressure
@@
 impacts solute distribution, and the geometry used for the computational model was larger
-than geometries used in experiments. Alternatively, dissimilarities in results may relate
+than some of the geometries used in experiments.
+Notably, there are large variations in ventricular size in the control population at 2 dpf.
+Alternatively, dissimilarities in results may relate
 to the way we defined the photoconversion site (ROI 1) in the simulations,
@@
 (thus with smaller diffusion coefficients),
-such as 150 nm exosomes, are almost entirely dependent on advection.
+such as 150 nm radius extracellular vesicles, are almost entirely dependent on advection.
 Indeed, there was essentially zero solute in the posterior ventricle at the
@@
 of cilia motility, indicating that transport from the middle to the posterior ventricle is
-purely driven by diffusion. We also performed photoconversion experiments on cilia mutant
+purely driven by diffusion at this developmental stage.
+We also performed photoconversion experiments on cilia mutant
 zebrafish larva (\emph{smh}), observing statistically significant slower transport in 
 ROIs 2 and 4. The results provide not only confidence in that our computational model
-well represents the physics, but also valuable quantification of the impact of cilia motility
+represents the physics well, but also valuable quantification of the impact of cilia motility
 on intraventricular transport. Interestingly, a previous simulation study of reduced cilia motility
@@
 We deliberately excluded the space proximal to in- and outflow boundaries in
-the anterior and posterior regions of interest (5 and 6) to limit adverse effects of 
+the anterior and posterior ventricles (ROIs 5 and 6) to limit adverse effects of 
 the advective transport at the in- and outflux boundaries on the mean concentrations.
 
-A possible improvement to the in- and outflow boundary conditions we employed would be
+A possible improvement to the in- and outflow boundary conditions would be
 to consider a 3D-0D coupling of the in- and outflow boundaries using
@@
 In human brains, cilia therefore probably play an important role in regulating the
-amount of substances like exosomes close to the ventricular walls, similar to coral
+amount of substances like extracellular vesicles close to the ventricular walls, similar to coral
 reefs, where it has been observed that cilia are primary regulators of
@@
 and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
-\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
+\emph{Tg(5xUAS:Signal-Dendra2)\textsuperscript{nw21Tg}}.
 Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
@@
 experiments were performed with zebrafish larvae at the 2 dpf stage obtained from inbreeding of heterozygous
-\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xuas:Signal-Dendra2})
+\emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xUAS:Signal-Dendra2})
 adult animals, as described by D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
@@
 used in the photoconversion, (ii) the Starmaker+Green Fluorescent Protein (STM-GFP) reported by
-Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and (iii) exosomes.
+Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and (iii) extracellular vesicles.
 To estimate the diffusion coefficients of these, when not
@@
 CSF, and $R$ is the radius of the molecule.
-For the exosomes, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
+For the extracellular vesicles, we calculate $D$ using~\Cref{eq:D_stokes_einstein}
 with the relatively large $R=150$ nm~\cite{Moghassemi2024ExtracellularDecade}.
@@
 The resulting diffusion coefficients
-are $D_1$ (exosomes), $D_2$ (STM-GFP) and $D_3$ (Dendra2) as given by \Cref{tab:diff_coeff_table}.
+are $D_1$ (extracellular vesicles), $D_2$ (STM-GFP) and $D_3$ (Dendra2) as given by \Cref{tab:diff_coeff_table}.
 
@@
         \midrule 
-        Exosomes (radius of 150 nm) & $D_1$ & -- & $\num{2.17e-12}$ & \textdagger \\
+        Extracellular vesicles (radius of 150 nm) & $D_1$ & -- & $\num{2.17e-12}$ & \textdagger \\
         GFP (saline aqueous solution) & -- & 26.9~\cite{UniProt2024GFPUniProtKB} & $\num{8.70e-11}$ & \cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells} \\

### 2025-03-18 paper/main.tex
add references intro

@@
 and metabolites as well as removing waste products, CSF regulates
-brain development and homeostasis~\cite{CITATTION}. Disruption of the
-CSF circulation is detrimental to brain health and disturbs cognitive and motor functions~\cite{Johanson2008}.
+brain development and homeostasis~\cite{Ringers2020Role, fame2020emergence, del2010ependymal}.
+Disruption of the CSF circulation is detrimental to brain health and disturbs
+cognitive and motor functions~\cite{Johanson2008}.
 Pathological CSF flow may also lead to
@@
 physiological processes, including via the beating motion of motile
-cilia lining the ventricular walls, CSF secretion by the choroid
-plexus, and pulsatile pressure gradients generated by the cardiac
-cycle, respiration, neural activity, and bodily
-movement~\cite{Vinje2019RespiratoryMeasurements,
-Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment}.
+cilia, CSF secretion by the choroid plexus, and pulsatile pressure gradients generated by the
+cardiac cycle, the respiration, neural activity, and bodily
+movement~\cite{del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
+Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment,
+macaulay2022cerebrospinal, mestre2018flow}.
 Motile cilia are evolutionarily conserved, microscopic hair-like
-structures that beat in a metachronal wave pattern at frequencies of
-10--30 Hz to mediate fluid flow~\cite{mitchell2007evolution, Ringers2020Role}.
+structures that beat in a coordinate pattern at frequencies of
+10--40 Hz to mediate fluid flow~\cite{mitchell2007evolution, Ringers2020Role}.
 Given their microscopic size, ranging from
@@
 and frequencies. Notably, this early developmental stage allows us to simplify our model
-by omitting CSF secretion, which starts at later stages,
-while still being well-conserved with mammals. 
+by omitting CSF secretion, which starts at later stages~\cite{Jeong2024TheZebrafish},
+while still being well-conserved with mammals~\cite{DGama2025MotileBrain,
+Olstad2019CiliaryDevelopment, Ringers2020Role, DGama2021Diversity, jurisch2020radial}. 
 Next, we validated our computation model with experimental data by monitoring in vivo
@@
 whereas cilia majorly contribute to the movement of larger particles.
-We also found that the location of cilia, as well as the ventricular geometry, greatly
+We also found that the location of cilia, as well as the ventricular geometry, largely
 impact solute distribution. Altogether, our work presents a computational
-framework together with new concepts of how cilia contribute to distribution of molecules and
+framework together with new concepts of how cilia distribute molecules and
 particles within the brain ventricles.

### 2025-03-18 paper/main.tex
more references and intro work

@@
 
-\keywords{cerebrospinal fluid, brain ventricles, transport, finite element methods}
+\keywords{cerebrospinal fluid, brain ventricles, cilia, transport, finite element methods}
 
@@
 processes, including the flow of cerebrospinal fluid
-(CSF)~\cite{CITATTION}. CSF is a clear liquid mostly produced by the choroid
-plexus that flows through the ventricular system and subarachnoid
-space~\cite{Damkier2013}. By transporting growth factors, nutrients, neurotransmitters
+(CSF)~\cite{CITATTION}. Produced mostly by the choroid
+plexus and partly by brain interstitial fluid,
+CSF is a clear liquid that flows through the ventricular system and subarachnoid
+space~\cite{Damkier2013, Brodal2016}. By transporting growth factors, nutrients, neurotransmitters
 and metabolites as well as removing waste products, CSF regulates
@@
 CSF often requires emergency surgical
-treatment, but for which there is 
-little agreement on optimal treatments~\cite{flannery2014pediatric}. 
+treatment~\cite{duy2022rethinking, kahle2024paediatric, wallmeier2022role},
+but for which there is little agreement on optimal treatments~\cite{flannery2014pediatric}. 
 Of particular importance is the fact that
 hydrocephalus is observed in animal models and humans with deficient motile
-cilia~\cite{Afzelius2004Cilia, Olstad2019CiliaryDevelopment, Mitchison2017Motile},
+cilia~\cite{Afzelius2004Cilia, Olstad2019CiliaryDevelopment, Mitchison2017Motile,
+Ibanez-Tallon2002LossHydrocephalus},
 indicating that the cilia play a crucial role for healthy brain functioning.
@@
 cardiac cycle, the respiration, neural activity, and bodily
-movement~\cite{del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
+movement~\cite{Brodal2016, del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
 Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment,
 macaulay2022cerebrospinal, mestre2018flow}.
-Motile cilia are evolutionarily conserved, microscopic hair-like
-structures that beat in a coordinate pattern at frequencies of
-10--40 Hz to mediate fluid flow~\cite{mitchell2007evolution, Ringers2020Role}.
+Motile cilia are hair-like structures that line the ventricular surface of the brain,
+known as the ependyma~\cite{mitchell2007evolution, Ringers2020Role, spassky2013motile}. 
+The cilia beat in a coordinated pattern at frequencies of
+10--40 Hz to mediate fluid flow~\cite{Ringers2023NovelEpithelia, roth2025structure}. 
 Given their microscopic size, ranging from
-6 to 15 microns, the cilia clearly contributes primarily to flow near the
-ventricular surface in the human brain~\cite{Siyahhan2014FlowVentricles}.
-On the other hand, cardiac,
+5 to 15 microns, cilia contribute primarily to flow near the
+ependyma in the human brain~\cite{Siyahhan2014FlowVentricles, Olstad2019CiliaryDevelopment,
+Ringers2020Role, Faubel2016Cilia}. In contrast, cardiac,
 respiratory and delta waves at lower frequencies induce pulsatile flow
@@
 spaces~\cite{Vinje2019RespiratoryMeasurements, eide2024functional,
-Causemann2025, fultz2019coupled}.
+Causemann2025, fultz2019coupled, mestre2018flow, daversin2020mechanisms}.
 
@@
 %
-
-Still an underexplored topic, how the motile cilia contribute to overall CSF flow
-and solute transport remains poorly understood. Experimental endeavors are
-challenging to pursue due to technical limitations: the microscopic size
-and high beating frequencies of the cilia make them difficult to monitor 
-in vivo in humans. Studies on animal models such as mice and
-zebrafish have provided unequivocal evidence that cilia are crucial
-for CSF flow in these animals~\cite{Olstad2019CiliaryDevelopment, Faubel2016Cilia}.
-It is clear that cilia affects advective intraventricular transport 
-to some extent. However a quantification of this effect, as well as of to which
-extent diffusion plays a role in transporting solutes, remains
-yet to be performed.
-
-Studies using brain explants have convincingly shown
+%  Studies on animal models such as mice and
+% zebrafish have provided unequivocal evidence that cilia are crucial
+% for CSF flow in these animals~\cite{Olstad2019CiliaryDevelopment, Faubel2016Cilia}.
+% It is clear that cilia affects advective intraventricular transport 
+% to some extent. However a quantification of this effect, as well as of to which
+% extent diffusion plays a role in transporting solutes, remains
+% yet to be performed.
+
+To date, it remains poorly understood how motile cilia contribute to 
+the overall fluid flow and solute transport within the brain.
+Experimental endeavors are challenging to pursue due to
+technical limitations: the microscopic size and relatively 
+high beating frequencies of the cilia~\cite{ocallaghan2012analysis, mahuzier2018ependymal,
+Jeong2022MeasurementTelencephalon, Olstad2019CiliaryDevelopment, spassky2013motile, DGama2021Diversity},
+as compared to other fluid dynamic processes in the brain that are slower and span larger
+spatial scales~\cite{Vinje2019RespiratoryMeasurements, eide2024functional, fultz2019coupled, mestre2018flow},
+make cilia difficult to monitor in vivo in humans.
+Until now, most studies have analyzed one physical mechanism at a time, especially in mammals.
+For instance, studies using brain explants have convincingly shown
 that cilia generate complex flow patterns at the surface of the brain
-ventricles; however, they failed to identify the role of pressure
+ventricles~\cite{Faubel2016Cilia, Sawamoto2006NewBrain, ibanez2003beat};
+however, they failed to identify the role of pressure
 gradients associated with respiration and cardiac pulsations in CSF
 flow and the accompanying transport. Similarly, while MRI technology
-can measure CSF movement in humans, it cannot detect the microscopic
+can measure CSF movement in humans~\cite{feinberg1987human, battal2011cerebrospinal,
+yamada2015current}, it cannot detect the microscopic
 movements of cilia to understand their impact in the large human
-brain. Consequently, we lack a comprehensive understanding of how
+brain~\cite{Siyahhan2014FlowVentricles}. Consequently, we lack a comprehensive understanding of how
 cilia contribute to CSF motion and solute transport, and whether cilia
-dysfunction will alter CSF composition and lead to brain
-disorders. The technical limitations of studying cilia-mediated flow and transport opens the
+dysfunction alters CSF composition and thus leads to brain disorders.
+
+The technical limitations of studying cilia-mediated flow and transport opens the
 possibility of mathematical modeling and computational investigations. Numerous previous studies
@@
 Others considered applications such as ciliary transport of mucous and particles in
-airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays},
+airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays, roth2025structure},
 propulsion and locomotion of ciliated organisms~\cite{BLAKE1974MechanicsMotion,
@@
     \textbf{h--j.} Streamlines simulated with the baseline flow model at
-    a time a time 25\% (\textbf{h}), 50\% (\textbf{i}) and 75\% (\texbf{j})
+    a time a time 25\% (\textbf{h}), 50\% (\textbf{i}) and 75\% (\textbf{j})
     into the cardiac cycle. Times indicated in panel \textbf{g}.

### 2025-03-18 paper/main.tex
abstract draft

@@
 
-Please insert your abstract here
+Cerebrospinal fluid (CSF) flow is integral to brain function.
+The underlying mechanisms of cilia-mediated flow and transport
+in the brain ventricles remain to be fully explored.
+In this paper, we analyze and evaluate the role of motile cilia
+in intraventricular CSF flow and transport. We combine computational
+modeling with in vivo experiments that monitor transport of a photoconvertible
+protein secreted in the brain ventricles.
+We use the geometry of the zebrafish larval brain ventricles,
+for which we have detailed knowledge of cilia properties and CSF motion velocities and frequencies,
+to develop a finite element model.
+Our results show that while cilia contribute to advection of large particles,
+diffusion plays a significant role in the transport of small molecules such as proteins.
+We also found that cilia location and the geometry of the ventricular system impact solute distribution.
+Altogether, our work offers both a computational framework that can be applied to other
+ventricular system and new concepts of how molecules are transported within the brain and its ventricles.
 
@@
 space~\cite{Damkier2013, Brodal2016}. By transporting growth factors, nutrients, neurotransmitters
-and metabolites as well as removing waste products, CSF regulates
+and metabolites, as well as removing waste products, CSF regulates
 brain development and homeostasis~\cite{Ringers2020Role, fame2020emergence, del2010ependymal}.
@@
 hydrocephalus is observed in animal models and humans with deficient motile
-cilia~\cite{Afzelius2004Cilia, Olstad2019CiliaryDevelopment, Mitchison2017Motile,
+cilia~\cite{Afzelius2004Cilia-relatedDiseases, Olstad2019CiliaryDevelopment, Mitchison2017Motile,
 Ibanez-Tallon2002LossHydrocephalus},
-indicating that the cilia play a crucial role for healthy brain functioning.
+indicating that the cilia play a crucial role for healthy brain function.
 
@@
 ependyma in the human brain~\cite{Siyahhan2014FlowVentricles, Olstad2019CiliaryDevelopment,
-Ringers2020Role, Faubel2016Cilia}. In contrast, cardiac,
+Ringers2020Role, Faubel2016Cilia-basedVentricles}. In contrast, cardiac,
 respiratory and delta waves at lower frequencies induce pulsatile flow
@@
 that cilia generate complex flow patterns at the surface of the brain
-ventricles~\cite{Faubel2016Cilia, Sawamoto2006NewBrain, ibanez2003beat};
+ventricles~\cite{Faubel2016Cilia-basedVentricles, Sawamoto2006NewBrain, ibanez2003beat};
 however, they failed to identify the role of pressure

### 2025-03-18 paper/main.tex
draft abstract, update intro

@@
 
-Cerebrospinal fluid (CSF) flow is integral to brain function.
-The underlying mechanisms of cilia-mediated flow and transport
-in the brain ventricles remain to be fully explored.
-In this paper, we analyze and evaluate the role of motile cilia
-in intraventricular CSF flow and transport. We combine computational
-modeling with in vivo experiments that monitor transport of a photoconvertible
-protein secreted in the brain ventricles.
-We use the geometry of the zebrafish larval brain ventricles,
-for which we have detailed knowledge of cilia properties and CSF motion velocities and frequencies,
-to develop a finite element model.
+Cerebrospinal fluid (CSF) is integral to brain function, as the fluid
+provides mechanical support of the brain and the flow of CSF helps
+distribute nutrients, neurotransmitters and metabolites throughout
+the central nervous system. CSF flow is partly driven
+by beating of motile cilia, hair-like structures that line the ependymal cell layer
+of the brain ventricles. Despite the physiological importance of CSF flow,
+the underlying mechanisms of cilia-mediated flow and transport
+in the brain ventricles remain yet to be comprehensively resolved.
+In this study, we analyze and evaluate the role of motile cilia
+in intraventricular CSF flow and transport. We use the geometry
+of the zebrafish larval brain ventricles, for which we have detailed knowledge of cilia properties and CSF motion velocities
+and frequencies, to develop finite element methods that model flow and transport.
+The computational model is validated by in vivo experiments that monitor transport
+of a photoconvertible protein secreted in the brain ventricles.
 Our results show that while cilia contribute to advection of large particles,
@@
 We also found that cilia location and the geometry of the ventricular system impact solute distribution.
-Altogether, our work offers both a computational framework that can be applied to other
-ventricular system and new concepts of how molecules are transported within the brain and its ventricles.
+Altogether, our work presents a computational framework that can be applied to other
+ventricular systems, together with new concepts of how molecules are transported within the brain and its ventricles.
 
@@
 processes, including the flow of cerebrospinal fluid
-(CSF)~\cite{CITATTION}. Produced mostly by the choroid
-plexus and partly by brain interstitial fluid,
+(CSF)~\cite{fame2020emergence}. Produced mostly by the choroid
+plexus and partly by brain interstitial fluid~\cite{Brodal2016},
 CSF is a clear liquid that flows through the ventricular system and subarachnoid
-space~\cite{Damkier2013, Brodal2016}. By transporting growth factors, nutrients, neurotransmitters
+space~\cite{Damkier2013}. By transporting growth factors, nutrients, neurotransmitters
 and metabolites, as well as removing waste products, CSF regulates
@@
 but for which there is little agreement on optimal treatments~\cite{flannery2014pediatric}.
-Of particular importance is the fact that
-hydrocephalus is observed in animal models and humans with deficient motile
-cilia~\cite{Afzelius2004Cilia-relatedDiseases, Olstad2019CiliaryDevelopment, Mitchison2017Motile,
-Ibanez-Tallon2002LossHydrocephalus},
-indicating that the cilia play a crucial role for healthy brain function.
 
@@
 % Refer to specific studies and what specifically we do not know.
-
-%
-%Until now, most studies have analyzed one physical mechanism at a
-%time, especially in mammals.
-%
-%  Studies on animal models such as mice and
-% zebrafish have provided unequivocal evidence that cilia are crucial
-% for CSF flow in these animals~\cite{Olstad2019CiliaryDevelopment, Faubel2016Cilia}.
-% It is clear that cilia affects advective intraventricular transport 
-% to some extent. However a quantification of this effect, as well as of to which
-% extent diffusion plays a role in transporting solutes, remains
-% yet to be performed.
-
 To date, it remains poorly understood how motile cilia contribute to 
@@
 ventricles~\cite{Faubel2016Cilia-basedVentricles, Sawamoto2006NewBrain, ibanez2003beat};
-however, they failed to identify the role of pressure
-gradients associated with respiration and cardiac pulsations in CSF
-flow and the accompanying transport. Similarly, while MRI technology
+however, they failed to identify the role of other contributions to CSF
+flow and accompanying transport, such as pressure
+gradients associated with respiration and cardiac pulsations. Moreover, while MRI technology
 can measure CSF movement in humans~\cite{feinberg1987human, battal2011cerebrospinal,
@@
 movements of cilia to understand their impact in the large human
-brain~\cite{Siyahhan2014FlowVentricles}. Consequently, we lack a comprehensive understanding of how
-cilia contribute to CSF motion and solute transport, and whether cilia
-dysfunction alters CSF composition and thus leads to brain disorders.
-
-The technical limitations of studying cilia-mediated flow and transport opens the
-possibility of mathematical modeling and computational investigations. Numerous previous studies
-have focused on modeling the interaction between single or several cilia and surrounding
+brain~\cite{Siyahhan2014FlowVentricles}. 
+These technical limitations of studying cilia-mediated flow and transport make 
+mathematical modeling and computational investigations an attractive alternative to experimental
+studies. Numerous previous simulation studies have focused on modeling the interaction
+between single or several cilia and surrounding
 fluids~\cite{Guo2020SimulatingGeometries, Ruvalcaba2021NumericalTree, Smith2009MathematicalFluids,
@@
 biological flows, and how cilia may contribute to tissue physiology.
+However, we still lack a comprehensive understanding of how
+cilia contribute to CSF motion and solute transport within the brain.
+This is of particular importance since disorders such as hydrocephalus are observed
+in animal models and humans with deficient motile cilia~\cite{Afzelius2004Cilia-relatedDiseases,
+Olstad2019CiliaryDevelopment, Mitchison2017Motile, Ibanez-Tallon2002LossHydrocephalus},
+indicating that the cilia play a crucial role for healthy brain function.
 
@@
 the role of motile cilia in intraventricular CSF flow and transport.
-First, we computed flow patterns and simulated solute transport with a computational model. To
-this end, we used the geometry of the zebrafish larval brain ventricles,
-for which we have detailed knowledge of cilia properties and CSF motion velocities
-and frequencies. Notably, this early developmental stage allows us to simplify our model
+We model the flow and transport by partial differential equations and solve
+them numerically with finite element methods to compute flow patterns and
+solute concentration dynamics. A geometry representing the zebrafish larval brain ventricles
+was used, for which we have detailed knowledge of cilia properties and CSF motion velocities
+and frequencies~\cite{Olstad2019CiliaryDevelopment}. 
+Notably, this early developmental stage allows us to simplify our model
 by omitting CSF secretion, which starts at later stages~\cite{Jeong2024TheZebrafish},
@@
 Olstad2019CiliaryDevelopment, Ringers2020Role, DGama2021Diversity, jurisch2020radial}. 
-Next, we validated our computation model with experimental data by monitoring in vivo
+The computational model is validated with experimental data by monitoring in vivo
 the dynamics of a photoconvertible fluorescent protein Dendra2
@@
 whereas cilia majorly contribute to the movement of larger particles.
-We also found that the location of cilia, as well as the ventricular geometry, largely
-impact solute distribution. Altogether, our work presents a computational
-framework together with new concepts of how cilia distribute molecules and
+We also found that the location of cilia, as well as changes to the ventricular geometry,
+largely impact solute distribution. In summary, our work presents a computational
+framework together that can be applied to other
+ventricular systems in the future, together with new concepts
+of how cilia distribute molecules and
 particles within the brain ventricles.
@@
 
-% Why? (Intersting point #1. However, we do not know aspect #2. 
+% Why? (Interesting point #1. However, we do not know aspect #2. 
 % How? (We therefore ...)
@@
 
-In-vivo particle tracking reveals characteristic CSF flow patterns in
+In vivo particle tracking reveals characteristic CSF flow patterns in
 zebrafish larval brain ventricles
@@
 computational fluid dynamics driven by cardiac pulsations and motile
-cilia lining the brain ventricles.
+cilia lining the surface of the brain ventricles.
 
@@
     \textbf{b, c.} Particle tracking data visualizing CSF flow directionality (\textbf{b}) and
-    velocity magnitudes in the middle ventricle.
+    velocity magnitudes (\textbf{c}) in the middle ventricle.
     \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and

### 2025-03-18 paper/main.tex
update peclet# values, caption fig1

@@
 posterior ventricles (\Crefpanels{fig:fig1}{e}). The highest flow
-speeds ($26.5$ \textmu m/s) occur in the vicinity of the dorsal cilia
+speeds ($\fixme{26.5}$ \textmu m/s) occur in the vicinity of the dorsal cilia
 in the middle ventricle. To model the cardiac pulsations, we impose a
@@
 in the absence of the cilia, the vortex structures vanish. The
-velocity magnitude peaks at $4.8$ \textmu m/s. CSF initially flows
+velocity magnitude peaks at $\fixme{4.8}$ \textmu m/s. CSF initially flows
 rostrocaudally before changing direction to caudorostral in the middle
@@
 the cilia and the pulsatile pressure-driven flow are aligned with the
-rostrocaudal axis, reaching up to 27.7 \textmu m/s dorsally in the
+rostrocaudal axis, reaching up to 28.0 \textmu m/s dorsally in the
 posterior part of the middle ventricle. The flow Reynolds number is
@@
     \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
-    anterior/posterior facets (blue).
+    anterior/posterior facets (blue). Dorsal (D), ventral (V), anterior (A), posterior (P),
+    left (L) and right (R) coordinates indicated.
     \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
@@
 %% Over one cardiac cycle, the CSF flow speed reaches up to
-%% 27.7 \textmu m/s, dorsally in the posterior part of the middle
+%% 28.0 \textmu m/s, dorsally in the posterior part of the middle
 %% ventricle. This peak is attained at the time instant coinciding with
@@
 to distal regions. Computing Péclet numbers, we find that
-$\mathrm{Pe}_1=519$, $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for
+$\mathrm{Pe}_1=664$, $\mathrm{Pe}_2=25$ and $\mathrm{Pe}_3=13$ for
 $D_1$, $D_2$ and $D_3$, respectively. With all $\mathrm{Pe} > 1$, this
@@
 affected when removing cilia in the dorsal diencephalic ventricle,
-as the maximum velocity magnitude drops from 27.7 \textmu m/s to 8.0 \textmu m/s.
+as the maximum velocity magnitude drops from \fixme{27.7} \textmu m/s to \fixme{8.0} \textmu m/s.
 In vivo, these cilia generate the strongest flow at
@@
 In contrast, removing telencephalic and ventral diencephalic cilia has minimal
-impact and results in maximum speeds of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
+impact and results in maximum speeds of \fixme{27.7} \textmu m/s or \fixme{27.2} \textmu m/s, respectively.
 Of the total tangential forces exerted by the cilia, ventral cilia in the middle ventricle
@@
 in vivo measurements, where the maximum velocity magnitude was around 5 \textmu m/s
-(recall that our model exhibits a maximum of 27.7 \textmu m/s).
+(recall that our model exhibits a maximum of 28.0 \textmu m/s).
 The geometry they studied resembles a pipe, probably offering more flow resistance
@@
 with $L_r = 110$ \textmu m (the height of the middle ventricle) and
-$U_r = 27.7$ \textmu m/s (the maximum velocity magnitude)
+$U_r = 28.0$ \textmu m/s (the maximum velocity magnitude)
 as length and velocity scales characteristic of the flow.

### 2025-03-18 paper/main.tex
appendix

@@
 The Stokes equations (\Cref{eq:stokes_eqs}) are discretized with a finite element method
-in space, while in time, we employ a first-order implicit Euler discretization.
+in space, while in time, we employ a first-order implicit Euler discretization~\cite{butcher2016numerical}.
 We set the timestep size $\Delta t = 0.023$ s such that 20 timesteps represent one cardiac cycle.
@@
 First, we define the average and jump operators, respectively, as
-\begin{equation*}
+\begin{equation}
     \avg{\uu} = \frac{\uu^+\cdot\nn^+ - \uu^-\cdot\nn^-}{2}
     \qquad\mathrm{and}\qquad \jump{\uu} = \uu^+ - \uu^-,
-\end{equation*}
-where $\nn$ is the normal vector on a facet separating two cells,
+    \label{eq:operators_BDM}
+\end{equation}
+where $\uu$ is a first-order tensor and 
+$\nn$ is the normal vector on a facet separating two cells,
 where the plus and minus signs denote variables in each of the two cells.
@@
 $\avg{\uu} = \uu\cdot\nn$ and $\jump{\uu} = \uu$,
-with $\nn$ pointing to the exterior of the domain. We now define
-and add the bilinear form
+with $\nn$ pointing to the exterior of the domain. Note that average operator
+defined in~\Cref{eq:operators_BDM} reduces the rank of the tensor $\uu$ by one,
+whereas the jump operator preserves rank. This extends to tensors of higher order.
+We now define and add the bilinear form
 \begin{align*}
@@
 In time, we discretize the weak formulation~\Cref{eq:abstract_semi_discrete_weak_form_modelC}
-with the implicit Euler method.
+with the implicit Euler method, approximating the time derivative as
+\begin{equation*}
+    \pdifft{\uu} \approx \frac{\uu^{n+1} - \uu^n}{\Delta t},
+\end{equation*}
+where $n$ denotes the timestep index. All of the other terms
+in~\Cref{eq:abstract_semi_discrete_weak_form_modelC} are evaluated at timestep $n+1$.
+The method is implicit and of first order in time~\cite{butcher2016numerical}.
 
@@
         = &\sum_{f\in \mathcal{F}}\int_f{D\frac{\alpha}{\avg{h}}\jump{c_h}\cdot\jump{\phi_h}}\,\mathrm ds
-        +\sum_{f\in \mathcal{F}}\int_f{\jump{c_h \hat{u}_h}\cdot\jump{\phi_h}}\,\mathrm ds  \\
+        +\sum_{f\in \mathcal{F}}\int_f{\left({c_h \hat{u}_h}|^+ - {c_h \hat{u}_h}|^-\right)\cdot\jump{\phi_h}}\,\mathrm ds  \\
          -&\sum_{f\in \mathcal{F}}\int_f{D\avg{\nabla\phi_h}\cdot\jump{c_h}}\,\mathrm ds
@@
 
-In time, we discretized~\Cref{eq:discrete_weak_form_adv_diff} with the implicit Euler method.
+In time, we discretized~\Cref{eq:discrete_weak_form_adv_diff} with the
+second-order backward difference scheme BDF2~\cite{Volker2016}. This scheme
+approximates the time derivative as
+\begin{equation*}
+    \pdifft{c} \approx \frac{3c^{n+1} - 4c^n + c^{n-1}}{2\Delta t},
+\end{equation*}
+where $n$ denotes the timestep index. All of the other terms
+in~\Cref{eq:discrete_weak_form_adv_diff} are evaluated at timestep $n+1$.
+The method is implicit and of second order in time.
 

### 2025-03-19 src/simulate_flow.py
update output directory structure

@@ -12,7 +12,7 @@ from petsc4py  import PETSc
 from basix.ufl import element, mixed_element
 from dolfinx.fem.petsc import assemble_matrix, _assemble_vector_vec, set_bc, apply_lifting, create_vector
 
-from utilities.mesh                 import mark_facets, anterior_cilia_volume1, middle_ventral_cilia_volume
+from utilities.mesh                 import mark_facets
 from utilities.forcing_expressions  import OscillatoryPressure
 from utilities.normals_and_tangents import facet_vector_approximation
 
@@ -58,20 +58,36 @@ class ReferenceFrameVelocity:
 class FlowSolver:
 
     #----------CLASS CONSTANTS AND PARAMETERS----------#
-    # Material parameters
+    # Fluid parameters
     nu_val  = 0.697 # Kinematic viscosity [mm^2 / s]
     rho_val = 1e-3  # Fluid density [g / mm^3]
 
     # Model parameters
     tau  = 6.5e-4 # Tangential stress BC parameter [Pa]
     freq = 2.22   # Cardiac frequency [Hz]
-    A_pressure   = 0.0015 # Pressure BC amplitude [Pa]
+    A_pressure = 0.0015 # Pressure BC amplitude [Pa]
 
     # Finite elements
     BDM_penalty_val = 10.0 # BDM interior penalty parameter
 
-    def __init__(self, mesh: dfx.mesh.Mesh, ft: dfx.mesh.MeshTags, direct: bool, model_version: str, mesh_version: int,
-                 T: float, dt: float, cilia_scenario: int, write_output: bool=False, write_checkpoint: bool=False):
+    # Cilia scenario strings for output directory names
+    cilia_strings = {0 : 'all_cilia',
+                     1 : 'rm_anterior',
+                     2 : 'rm_dorsal',
+                     3 : 'rm_ventral'
+    }
+
+    def __init__(self,
+                 mesh: dfx.mesh.Mesh,
+                 ft: dfx.mesh.MeshTags,
+                 direct: bool,
+                 model_version: str,
+                 mesh_version: int,
+                 T: float,
+                 dt: float,
+                 cilia_scenario: int,
+                 write_output: bool=False,
+                 write_checkpoint: bool=False):
         """ Constructor.
 
         Parameters
@@ -124,16 +140,18 @@ class FlowSolver:
         self.cilia_scenario = cilia_scenario
         self.write_output = write_output
[…]

### 2025-03-19 src/simulate_transport.py

@@ -1,5 +1,6 @@
 from utilities.local_imports import *
-from utilities.mesh          import create_ventricle_volumes_meshtags, mark_facets
+from utilities.mesh          import create_ventricle_volumes_meshtags
+from diffusion import diffusion_problem
 
 import os
 import time
@@ -39,13 +40,9 @@ SLIP                 = 9
 
 # Diffusion coefficients
 D_coeffs = {
-    'D1'  : 1.63e-6,
-    'D2'  : 57.5e-6,
-    'D3'  : 115e-6,
-    'NPY' : 150e-6,
-    'DFP' : 115e-6,
-    'STM_GFP' : 57.5-6,
-    'EXO' : 1.63e-6
+    'D1' : 2.17e-6, # Exosomes, 150 nm radius 
+    'D2' : 57.5e-6, # STM-GFP
+    'D3' : 115e-6,  # Dendra2
 }
 
 class TransportSolver:
@@ -53,7 +50,7 @@ class TransportSolver:
     
     comm = MPI.COMM_WORLD # MPI communicator
     ghost_mode = dfx.mesh.GhostMode.shared_facet # Mesh partitioning method for MPI communication
-    record_periods = np.array([10, 50, 100, 250, 500, 750, 1000, 1250, 1500, 1750])
+    record_periods = np.array([200, 400, 600, 800, 1000, 1200, 1400, 1600, 1800])
 
     def __init__(self, data_fname: str,
                        model_version: str,
@@ -63,12 +60,7 @@ class TransportSolver:
                        period: float,
                        molecule: str,
                        element_degree: int,
-                       relative: bool,
-                       tau_version: str,
-                       flux_BC: bool=True,
                        write_data: bool=False,
-                       write_peclet_vtx: bool=False,
-                       write_peclet_checkpoint: bool=False,
                        write_output_vtx: bool=False,
                        write_output_xdmf: bool=False,
                        write_checkpoint: bool=False,
@@ -81,8 +73,6 @@ class TransportSolver:
         self.molecule = molecule
         self.D_value = D_coeffs[molecule]
         self.write_data = write_data
-        self.write_peclet_vtx = write_peclet_vtx
-        self.write_peclet_checkpoint = write_peclet_checkpoint
         self.write_output_vtx = write_output_vtx
         self.write_output_xdmf = write_output_xdmf
         self.write_checkpoint = write_checkpoint
[…]

### 2025-03-19 src/utilities/create_colormap.py

@@ -62,9 +62,9 @@ if __name__=='__main__':
         cmap = 'wgk'
         cb = matplotlib.colorbar.ColorbarBase(ax, cmap=cmap, orientation='horizontal')
         cb.set_ticks([0, 1])
-        cb.set_ticklabels([0, 0.77])
-        ax.tick_params(axis='x', labelsize=46)
-        ax.set_title(r"Concentration $c$ [-]", fontsize=46)
+        cb.set_ticklabels([0, 1.0])
+        ax.tick_params(axis='x', labelsize=36)
+        ax.set_title(r"Concentration $c$ [-]", fontsize=42)
         fig_name = "../../output/illustrations/colorbars/colorbar_D3.png"
     elif bar_type==2:
         fig = plt.figure(figsize=(15, 4))

### 2025-03-19 src/utilities/mesh.py

@@ -15,6 +15,59 @@ ANTERIOR_CILIA1      = 7
 ANTERIOR_CILIA2      = 8
 SLIP                 = 9
 
+def create_refinement_meshtags(mesh: dfx.mesh.Mesh):
+
+    # def ROI_1(x):
+    #     """ The dorsal posterior region of the middle ventricle. """
+    #     x_range = np.logical_and(x[0]>0.290, x[0]<0.320) #295, 325
+    #     y_range = np.logical_and(x[1]>0.145, x[1]<0.155)
+    #     z_range = np.logical_and(x[2]>0.195, x[2]<0.220) #200, 225
+    #     xz_range = np.logical_and(x_range, z_range)
+    #     return np.logical_and(y_range, xz_range)
+
+    def ROI_1_refinement_bot(x):
+        x_range = np.logical_and(x[0]>0.290, x[0]<0.320)
+        y_range = np.logical_and(x[1]>0.130, x[1]<0.150)
+        z_range = np.logical_and(x[2]>0.175, x[2]<0.195)
+        xz_range = np.logical_and(x_range, z_range)
+        return np.logical_and(y_range, xz_range)
+    
+    def ROI_1_refinement_top(x):
+        x_range = np.logical_and(x[0]>0.290, x[0]<0.320)
+        y_range = np.logical_and(x[1]>0.130, x[1]<0.150)
+        z_range = np.logical_and(x[2]>0.220, x[2]<0.250)
+        xz_range = np.logical_and(x_range, z_range)
+        return np.logical_and(y_range, xz_range)
+
+    def ROI_1_refinement_left(x):
+        x_range = np.logical_and(x[0]>0.270, x[0]<0.290)
+        y_range = np.logical_and(x[1]>0.130, x[1]<0.150)
+        z_range = np.logical_and(x[2]>0.195, x[2]<0.220)
+        xz_range = np.logical_and(x_range, z_range)
+        return np.logical_and(y_range, xz_range)
+    
+    def ROI_1_refinement_right(x):
+        x_range = np.logical_and(x[0]>0.320, x[0]<0.340)
+        y_range = np.logical_and(x[1]>0.130, x[1]<0.150)
+        z_range = np.logical_and(x[2]>0.195, x[2]<0.220)
+        xz_range = np.logical_and(x_range, z_range)
+        return np.logical_and(y_range, xz_range)
+    
+    tdim = mesh.topology.dim
+
[…]

### 2025-03-20 paper/main.tex
update output directory structure
results, intro

@@
 however, they failed to identify the role of other contributions to CSF
-flow and accompanying transport, such as pressure
+flow and the accompanying transport, such as pressure
 gradients associated with respiration and cardiac pulsations. Moreover, while MRI technology
-can measure CSF movement in humans~\cite{feinberg1987human, battal2011cerebrospinal,
+can measure CSF motion in humans~\cite{feinberg1987human, battal2011cerebrospinal,
 yamada2015current}, it cannot detect the microscopic
@@
 Cui2019NumericalMethod, Cui2022AFlow}.
-Others considered applications such as ciliary transport of mucous and particles in
+Others considered cilia-mediated flow in the brain~\cite{Siyahhan2014FlowVentricles,
+Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}, but also 
+other applications such as ciliary transport of mucous and particles in
 airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays, roth2025structure},
 propulsion and locomotion of ciliated organisms~\cite{BLAKE1974MechanicsMotion,
-Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella},
-oxygen regulation in coral reefs~\cite{Pacherres2022CiliaryProduction},
-and cilia-mediated flow in the brain~\cite{Siyahhan2014FlowVentricles,
-Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}.
+Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella}, and
+oxygen regulation in coral reefs~\cite{Pacherres2022CiliaryProduction}.
 These simulation studies have provided valuable insights on how cilia mediate complex
@@
 This is of particular importance since disorders such as hydrocephalus are observed
-in animal models and humans with deficient motile cilia~\cite{Afzelius2004Cilia-relatedDiseases,
+in animal models and humans with deficient motile cilia~\cite{Afzelius2004CiliaRelatedDiseases,
 Olstad2019CiliaryDevelopment, Mitchison2017Motile, Ibanez-Tallon2002LossHydrocephalus},
@@
 largely impact solute distribution. In summary, our work presents a computational
-framework together that can be applied to other
+framework that can be applied to other
 ventricular systems in the future, together with new concepts
@@
 posterior ventricles (\Crefpanels{fig:fig1}{e}). The highest flow
-speeds ($\fixme{26.5}$ \textmu m/s) occur in the vicinity of the dorsal cilia
+speeds ($26.7$ \textmu m/s) occur in the vicinity of the dorsal cilia
 in the middle ventricle. To model the cardiac pulsations, we impose a
@@
 in the absence of the cilia, the vortex structures vanish. The
-velocity magnitude peaks at $\fixme{4.8}$ \textmu m/s. CSF initially flows
+velocity magnitude peaks at $4.8$ \textmu m/s. CSF initially flows
 rostrocaudally before changing direction to caudorostral in the middle
@@
 the cilia and the pulsatile pressure-driven flow are aligned with the
-rostrocaudal axis, reaching up to 28.0 \textmu m/s dorsally in the
+rostrocaudal axis, reaching up to 27.9 \textmu m/s dorsally in the
 posterior part of the middle ventricle. The flow Reynolds number is
@@
 question, we simulate the distribution and evolution of three
-different solutes injected within a region of interest (ROI1) in the
+different solutes injected within a region of interest (ROI 1) in the
 dorsal region of the middle ventricle (\Crefpanels{fig:fig2}{a}),
@@
     \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
-    \textbf{b--d.} Slice of the concentration field simulated
-    with diffusion coefficients $D_1$, $D_2$ and $D_3$ for eight time instants covering the
-    time range from 45 seconds to 790 seconds, corresponding to 100 to 1750 cardiac cycles.
+    \textbf{b--d.} Slices of the concentration field simulated
+    with diffusion coefficients $D_1$, $D_2$ and $D_3$ for nine time instants covering the
+    time range from 90 seconds to 811 seconds, corresponding to 200 to 1800 cardiac cycles,
+    for even intervals of 200 cycles.
     Slices are taken in the $xz$-plane ($y=0.140$ mm, the center of the geometry).
@@
     \textbf{e--g.} Mean concentration $\cbar$ in each region of interest (ROI)
-    as function of time for diffusion coefficient $D_1$, $D_2$ and $D_3$, respectively. 
+    as function of time for diffusion coefficients $D_1$, $D_2$ and $D_3$, respectively. 
     \textbf{h.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a
     threshold value of $0.25$ (ROIs 2-4) or $0.10$ (ROIs 5, 6) in each simulation setup.
-    Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}\label{fig:fig2}
+    Note that there is no bar for $D_1$ in ROI 6, because the threshold value was never exceeded.}
+    \label{fig:fig2}
 \end{figure}
@@
 middle ventricle, covering ROIs 2--4, before appearing in the anterior
-ventricle (ROI5) and finally reaching the posterior ventricle
-(ROI6). Notably, the extracellular vesicles, associated with the smallest diffusion
-coefficient, do not reach the posterior ventricle (ROI6) within the
-simulated time frame.
+ventricle (ROI 5) and finally reaching the posterior ventricle
+(ROI 6). Notably, the extracellular vesicles, associated with the smallest diffusion
+coefficient, do not reach the posterior ventricle (ROI 6) within the
+simulated time frame~\Crefpanels{fig:fig2}{b, e}.
 
@@
 note minor differences however. The simulated values of $\cbar_i$ at
-the final time (0.72, 0.82, 0.56 and 0.35 in ROIs 2--6, respectively)
+the final time \fixme{(0.72, 0.82, 0.56, 0.35 and X in ROIs 2--6, respectively)}
 are generally higher than the corresponding experimental $\Delta F$
@@
 experimental values (\Crefpanels{fig:fig3}{c, d}).
-
-%% the $\cbar$ profiles of ROIs 3--4 are opposite order in the
-%% simulations as compared to the experiments.
-
-%% Notwithstanding similar dynamics, we observe small differences between
-%% the experiments and simulation.
-
-%% For instance, transport in ROIs 2--6 is faster in the simulation and
-%% reaches higher final values.
 
@@
 
-\mer{Sentence on why absence of motile cilia is intersting: Cilia
-  motion is key to development and absence of cilia is associated with
-  pathologies.} As observed both experimentally and computationally,
-the absence of motile cilia alters the CSF flow patterns. We next
-investigate the implications of these changes on intraventricular
+Ciliary motion is integral to physiological CSF flow,
+and absence of cilia has been associated with defective
+brain development and various pathologies~\cite{Eichele2020Cilia-drivenVentricle,
+Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles,
+Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
+Sawamoto2006NewBrain, Yoshiba2014RolesSymmetry,
+Hirokawa2006NodalAsymmetry}.
+As observed both experimentally and computationally,
+the absence of motile cilia alters the CSF flow patterns. 
+We next investigate the implications of these changes on intraventricular
 transport.
@@
 downstream of the photoconversion site, we observed a slower increase
-of fluorescence intensity (\Crefpanels{fig:fig4}{a}), resulting in
-$45\%$ (ROI 2) and $25\%$ (ROI 4) higher mean times-to-threshold
-(\Crefpanels{fig:fig4}{b}), in the \emph{smh} mutants compared to
-controls. We found no significant differences in the Dendra2
-distribution in ROIs 3, 5, and 6 between \emph{smh} mutants and
-controls.
+of fluorescence intensity (\Crefpanels{fig:fig4}{a}). The mean times-to-threshold
+in the \emph{smh} mutants were $45\%$ (ROI 2) and $25\%$ (ROI 4) higher
+compared to controls (\Crefpanels{fig:fig4}{b}). We found no significant differences
+in the Dendra2 distribution in ROIs 3, 5, and 6 between
+\emph{smh} mutants and controls.
 
@@
 pressure pulsations only, representing the absence of motile
-cilia. Comparing the in-silico mutants with transport predictions in
+cilia. Comparing the in silico mutants with transport predictions in
 the presence of both cardiac pulsations and motile cilia, we observe
@@
 diffusion plays an important role for
-solute movement to regions upstream in the cilia flow fields or to
+solute movement to regions upstream in the cilia-mediated flow fields or to
 distant ventricles, while cilia affect the downstream mean concentrations.
 
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 Three cilia-covered regions were considered paralyzed separately:
-the telencephalic (anterior) ventricle, and the dorsal and ventral parts
-of the diencephalic (middle) ventricle (\Crefpanels{fig:fig5}{a}).
+the anterior ventricle, and the dorsal and ventral parts
+of the middle ventricle (\Crefpanels{fig:fig5}{a}).
 To simulate cilia paralysis, the cilia tangential traction boundary condition
@@
 The CSF velocities are most strongly
-affected when removing cilia in the dorsal diencephalic ventricle,
-as the maximum velocity magnitude drops from \fixme{27.7} \textmu m/s to \fixme{8.0} \textmu m/s.
+affected when removing cilia in the dorsal part of the middle ventricle,
+as the maximum velocity magnitude drops from 27.9 \textmu m/s to 7.9 \textmu m/s.
 In vivo, these cilia generate the strongest flow at
 this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
-In contrast, removing telencephalic and ventral diencephalic cilia has minimal
-impact and results in maximum speeds of \fixme{27.7} \textmu m/s or \fixme{27.2} \textmu m/s, respectively.
+In contrast, removing cilia in the anterior ventricle or the ventral region of the middle
+ventricle has minimal impact, and results in maximum speeds
+of 27.9 \textmu m/s and 27.4 \textmu m/s, respectively.
 Of the total tangential forces exerted by the cilia, ventral cilia in the middle ventricle
@@
 Changes in the transport of Dendra2 are most prominent when removing the dorsal cilia
-in the diencephalic ventricle. The mean concentration profiles 
-of all ROIs (except ROI 1, where we impose the photoconversion curve)
+in the middle ventricle. All mean concentration profiles 
+(except ROI 1, where we impose the photoconversion curve)
 exhibit changes (\Crefpanels{fig:fig5}{c}).
@@
 and more rapid transport to the posterior ventricle (ROI 6).
-Meanwhile, removal of telencephalic cilia does not alter the 
+On the other hand, removal of anterior cilia does not alter the 
 mean concentrations (\Crefpanels{fig:fig5}{c}).
-Finally, without ventral cilia in the diencephalic ventricle,
+Finally, without ventral cilia in the middle ventricle,
 more solute spreads towards the anterior ventricle (ROI 5) and
 less solute spreads towards the posterior ventricle (ROI 6).
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 \subsection{Modification of ventricular geometry impacts solute distribution}
-Variations in ventricular morphology impact CSF flow patterns.
+Variations in ventricular morphology impact CSF flow patterns~\cite{Olstad2019CiliaryDevelopment}.
 To assess how these variations influence solute distribution,
@@
 
-Constricting the connection between the anterior and middle ventricle leads to
-slower transport to the anterior ventricle (ROI 5),
-and a slightly higher mean concentration in ROIs 2--4 and 6, compared to the original geometry
-(\Crefpanels{fig:fig6}{c}, shrunk fore-mid scenario). This is notwithstanding a
+Constricting the connection between the anterior and middle ventricle reduces
+solute transport to the anterior ventricle (ROI 5),
+and the mean concentration in ROIs 2--4 and 6 slightly increases, compared to the original geometry
+(\Crefpanels{fig:fig6}{c}). This is notwithstanding a
 9.5\% reduction in ventral cilia force magnitude
@@
 while both the anterior and the posterior ventricles (ROIs 5 and 6) have reduced
-mean concentrations. Altogether, our results show that the geometry and
-width of the ventricular ducts matter
-for solute transport, with notable differences in transport from relatively small
-geometry modifications. This may explain why we observed larger differences
-in the cilia-deficient computational model compared to the experimental data in
-\Cref{fig:fig4}, as the model and the fish have slightly different duct diameters.
-\begin{figure}[H]
+mean concentrations. To summarize, our results show that the
+ventricular geometry and the cross-sectional area of the ventricular ducts matter
+for solute transport, with notable differences in transport resulting from
+relatively small geometry modifications. This may explain why
+we observed larger differences in the cilia-deficient computational
+model compared to the experimental data in \Cref{fig:fig4},
+as the model and the fish have slightly different geometries.
+\begin{figure}
     \centering
@@
     The bars for the four shrunk scenarios thus
-    display $F_i/F_{\mathrm{original}}\cdot 100\%$.}
+    display $F_i/F_{\mathrm{original}}\times 100\%$.}
     \label{fig:fig6}
@@
 \section{Discussion}
-In this study, we have presented a computational model of CSF flow and solute transport within the brain ventricles.
-We used the larval zebrafish brain ventricles since its geometry,
-flow components and kinetics are well described, thereby allowing us to validate
-our simulation experimentally. Nevertheless, our computational framework can be adapted to and implemented in
-other ventricular systems in the future, once the flow parameters of such systems
+In this study, we have presented a computational model of CSF flow and
+solute transport within the brain ventricles.
+We used the larval zebrafish brain ventricles since its geometry and
+flow mechanisms are well described, thereby allowing us to validate
+our simulation experimentally. Nevertheless, our computational framework can be adapted to,
+and implemented in, other ventricular systems in the future, once the flow parameters of such systems
 are comprehensively resolved. By imposing tangential traction and normal pressure
@@
 Using the simulated CSF flow, we modeled solute transport by an advection-diffusion equation.
-The transport results compared well with experimental data performed in vivo in zebrafish.
+The transport results compared well with data from in vivo experiments in zebrafish.
 Then, by using a computational model as well as zebrafish mutants with paralyzed cilia,
@@
 diffusion plays a significant role in protein transport.
-Finally, we reported how local cilia paralysis and ventricular geometries
+Finally, we investigated how local cilia paralysis and ventricular geometries
 affect solute distribution. Altogether, we present not only new findings on the role of
@@
 mean concentration $\cbar$ (simulations) as functions of time.
-Even though we identified very similar dynamics in simulations and
+Even though we identified similar dynamics in simulations and
 in vivo experiments, the dynamics of the simulations were generally
@@
 leak out of the brain ventricles over the time spans we consider
-and render the dynamics slower.
+and render the dynamics slower. Finally, an important difference
+between the simulations and experiments is the fact that the
+computational model is 3D, while the experiments only resolve
+two-dimensional features.
 
@@
 While advection is the strongest transport mechanism on a global scale for
-Dendra2 (global Péclet number 7.4), diffusion is balancing out
+Dendra2 (global Péclet number 13), diffusion is balancing out
 advection especially for shorter distances and for regions devoid of motile cilia activity.
 Indeed, we identified that the diffusion coefficient had a greater impact on transport to
-regions located upstream in the CSF flow field (ROI 3) or in different ventricles (ROIs 5--6),
+regions located upstream in the CSF flow field (ROI 3) or in distant ventricles (ROIs 5--6),
 than the regions located downstream of cilia-mediated flow (ROI 2).
@@
 such as 150 nm radius extracellular vesicles, are almost entirely dependent on advection.
-Indeed, there was essentially zero solute in the posterior ventricle at the
-final simulation time (around 860 s), a ventricle where transport is largely driven
+There was essentially zero solute in the posterior ventricle at the
+final simulation time (around 860 s), a ventricle where transport is driven
 by diffusion due to the absence of motile cilia.
@@
 $L=200$ \textmu m from the middle to the posterior ventricle is approximately 24500 s.
-Advective transport by the mean velocity $\overline{U}=2.4 \ \mu$m/s over the same
-distance would happen on a timescale of the order of $t_a=L/\overline{U}=83$ s.
+Advective transport by the mean velocity $\overline{U}=2.4$ \textmu m/s over the same
+distance would happen on a timescale of $t_a=L/\overline{U}=83$ s.
 Comparing this with the minuscule values of $\cbar_6$ after simulating transport
@@
 \subsection{Effects of cilia motility and ventricular morphology}
-To gain further insights into how CSF flow and intraventricular transport depend on cilia
+To gain insights into how CSF flow and intraventricular transport depend on cilia
 motility and ventricular morphology, we manipulated certain
 parameters in our models. First, we investigated how complete loss of cilia motility
-impacted the transport dynamics. Simulations with a cardiac-only/no-cilia lead to
+impacted the transport dynamics. Simulations with a cardiac-induced/no-cilia lead to
 slower transport when compared to the baseline model that included cilia. Especially
@@
 flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
-Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004Cilia-relatedDiseases},
+Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases},
 but also in other phenomena such as maintaining healthy functioning of mucous transport in
@@
 The length 15 \textmu m is the a typical length of cilia in human brain ventricles
-(in general the length is between 10--15 \textmu m~\cite{Afzelius2004Cilia-relatedDiseases}),
+(in general the length is between 10--15 \textmu m~\cite{Afzelius2004CiliaRelatedDiseases}),
 while in zebrafish they are closer to 5 \textmu m~\cite{Salman2022ComputationalEmbryo}.
@@
 in vivo measurements, where the maximum velocity magnitude was around 5 \textmu m/s
-(recall that our model exhibits a maximum of 28.0 \textmu m/s).
+(recall that our model exhibits a maximum of 27.9 \textmu m/s).
 The geometry they studied resembles a pipe, probably offering more flow resistance
@@
 in the zebrafish, dysfunctional establishment of left-right symmetry,
-and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004Cilia-relatedDiseases,
+and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004CiliaRelatedDiseases,
 Youn2018PrimaryDiseases, Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}
@@
 Furthermore, $\rho=1000 \ \mathrm{kg/m^3}$ is the CSF density
-and $\mu=0.70 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
+and $\mu=0.7 \ \mathrm{mPa\cdot s}$ is the dynamic viscosity
 of the CSF~\cite{Bloomfield1998EffectsFluid}.
@@
 with $L_r = 110$ \textmu m (the height of the middle ventricle) and
-$U_r = 28.0$ \textmu m/s (the maximum velocity magnitude)
+$U_r = 27.9$ \textmu m/s (the maximum velocity magnitude)
 as length and velocity scales characteristic of the flow.
@@
 For the pressure, we use piecewise constant (zeroth order discontinuous Galerkin (DG)) elements.
-The resulting total number of degrees of freedom at each time step is 943 820.
+The resulting total number of degrees of freedom at each time step is 1 009 874.
 The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
@@
 method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
-conservation properties. In time, the equation is discretized with the second-order backward
+conservation properties. At each timestep the total number of degrees of freedom 
+is 1 415 120. In time, the equation is discretized with the second-order backward
 difference scheme BDF2.~\cite{Volker2016}

### 2025-03-24 paper/main.tex
reformat titlepage

@@
 
-\begin{document}
-
 \pagestyle{plain}
 
-\begingroup
-\parindent0pt
-
-\title{The role of advection versus diffusion in intraventricular transport}
+\title{\textbf{Advection versus diffusion in intraventricular transport}}
 %
-\maketitle
 %
@@
 
-\author{Halvor Herlyng*},
-\author{Ada J.~Ellingsrud},
-\author{Miroslav Kuchta},
-\author{Inyoung Jeong},
-\author{Marie E.~Rognes}, 
-\author{Nathalie Jurisch-Yaksi*}
-
-% Affiliations: Please provide adacemic titles (Prof. or Dr.) for all authors where applicable,
-% and include an institutional email address for all corresponding authors
-\begin{affiliations}
-H.~Herlyng, Dr.~A.~J.~Ellingsrud, Dr.~M.~Kuchta, Dr.~M.~E.~Rognes\\
-Department of Numerical Analysis and Scientific Computing,
-Simula Research Laboratory, Kristian Augusts gate 23, 0164 Oslo, Norway\\
-Email Address: hherlyng@simula.no
-
-\medskip
-Dr.~M.~E.~Rognes \\
-K.~G.~Jebsen Centre for Brain Fluid Research, Oslo, Norway
-
-\medskip
-Dr.~I.~Jeong, Dr.~N.~Jurisch-Yaksi\\
-Department of Clinical and Molecular Medicine,
-Norwegian University of Science and Technology, Erling Skjalgsons gate 1, 7491 Trondheim, Norway \\
-Email Address: nathalie.jurisch-yaksi@ntnu.no
-\end{affiliations}
-
-\medskip
-
-% Keywords: Please provide a minimum of three and a maximum of seven keywords, separated by commas
-
-\keywords{cerebrospinal fluid, brain ventricles, cilia, transport, finite element methods}
+\author[1,*]{Halvor Herlyng}
+\author[1]{Ada J.~Ellingsrud}
+\author[1]{Miroslav Kuchta} 
+\author[2]{Inyoung Jeong}
+\author[1,3]{Marie E.~Rognes}
+\author[2, *]{Nathalie Jurisch-Yaksi}
+\affil[1]{Department for Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway} % Kristian Augusts gate 23, 0164
+\affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway} % Erling Skjalgsons gate 1, 7491
+\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research, Oslo, Norway}
+\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}, \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
+\date{}
+
+% Text: Please use section headings and subheadings as specified below. For communications, all section headings apart from Experimental Section should be removed
+% Please make the first reference to a display item bold: \textbf{Figure 1}
+% Do not abbreviate Figure, Equation, etc.; display items are always singular, i.e., Figure 1 and 2.
+% Equations are always singular, i.e., Equation 1 and 2, and should be inserted using the {equation} environment, not as graphics
+% Please do not use footnotes in the text, additional information can be added to the Reference list.
+
+%\section{First Section}
+
+%\subsection{First Subsection}
+
+%\subsubsection{First Sub Subsection}
+
+%\threesubsection{First lowest-level subsection}
+
+\begin{document}
+\maketitle
 
@@
 
-\endgroup % End 0parindent group
-
-% Text: Please use section headings and subheadings as specified below. For communications, all section headings apart from Experimental Section should be removed
-% Please make the first reference to a display item bold: \textbf{Figure 1}
-% Do not abbreviate Figure, Equation, etc.; display items are always singular, i.e., Figure 1 and 2.
-% Equations are always singular, i.e., Equation 1 and 2, and should be inserted using the {equation} environment, not as graphics
-% Please do not use footnotes in the text, additional information can be added to the Reference list.
-
-%\section{First Section}
-
-%\subsection{First Subsection}
-
-%\subsubsection{First Sub Subsection}
-
-%\threesubsection{First lowest-level subsection}
+% Keywords: Please provide a minimum of three and a maximum of seven keywords, separated by commas
+\noindent\small\hspace{.8725cm}\textbf{Keywords} cerebrospinal fluid, brain ventricles, cilia, transport, finite elements
 
@@
 macaulay2022cerebrospinal, mestre2018flow}.
-Motile cilia are hair-like structures that line the ventricular surface of the brain,
-known as the ependyma~\cite{mitchell2007evolution, Ringers2020Role, spassky2013motile}. 
-The cilia beat in a coordinated pattern at frequencies of
-10--40 Hz to mediate fluid flow~\cite{Ringers2023NovelEpithelia, roth2025structure}. 
+Cilia are hair-like structures found in a vast diversity of
+biological organisms and in several human organs,
+of which the brain is one of them~\cite{Fulford1986Muco-ciliaryLung,
+Pacherres2022CiliaryProduction, Jahn1972LocomotionProtozoa,
+Brennen1977FluidFlagella, Ringers2020Role, spassky2013motile,
+DGama2025MotileBrain, mitchell2007evolution,
+Tsukita2012CoordinatedFeet, BLAKE1974MechanicsMotion,
+Reiten2017Motile-Cilia-MediatedComputations, Thouvenin2020OriginCanal}. 
+The ventricular surface of the brain, known as the ependyma, is lined by
+motile cilia that beat in a coordinated pattern at frequencies of
+10--40 Hz to mediate fluid flow~\cite{mitchell2007evolution,
+Ringers2020Role, spassky2013motile, Ringers2023NovelEpithelia, roth2025structure}. 
 Given their microscopic size, ranging from
@@
 \subsection{Estimation of computational model parameters}
-The diffusion coefficients used in this study were partially based on values
-from experiments and partially estimated. The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$
+The diffusion coefficients used in this study were based on experimental values. 
+The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$
 is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an
@@
 We note that Sadovsky~\emph{et al.}~\cite{GuraSadovsky2017MeasurementExpansion} reported that
-Dendra2 satisfies the Stokes-Einstein in the solution they used,
-a solution which had similar viscosity
-to water. We used CSF density and viscosity values measured in
+Dendra2 satisfies the Stokes-Einstein in a solution of similar viscosity
+to CSF. We used CSF density and viscosity values measured in
 humans~\cite{Bloomfield1998EffectsFluid},
 and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances,
-the CSF in which photoconverted Dendra2 are transport in our experiments may be more viscous
-than what we consider. This would reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
+the CSF in which the photoconverted Dendra2 are transported in our experiments may be more viscous
+than we assumed. This would reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
 but based on reports of protein concentration having a limited impact on the viscosity of
@@
 results of Dendra2 transport would be altered if the
-diffusion coefficient $D_3$ is overestimated. In the case that $D_3$ is
-underestimated, we assume the
-results would follow the same trend as the differences between results for
-$D_2$ and $D_3$: diffusion becomes
-more important, and is almost balancing advective transport for $D_3$. 
-Thus for a higher diffusion coefficient, we would see transport that is
-mostly explained by diffusive behavior.
-
-We heuristically determined the parameter $\tau = 0.65$ mPa, which determines
-the magnitude of the cilia tangential traction boundary conditions. The maximum force applied
-was in the dorsal region of the middle ventricle, where the posterior region had a tangential
-traction vector magnitude of $\vert\btau\vert_{\mathrm{max}} = 2.5$ mPa applied to the
-boundary. Previous simulation studies of cilia-mediated flow in brain ventricles have
+diffusion coefficient $D_3$ is overestimated. In the case that $D_3$ is underestimated, 
+we expect a trend similar to the difference in the $D_2$ and $D_3$ solute concentrations;
+incerasingly diffusive fields.
+
+We heuristically determined the magnitude of the cilia tangential traction boundary condition
+with the parameter $\tau = 0.65$ mPa. The maximum stress $\vert\btau\vert_{\mathrm{max}} = 2.5$ mPa
+was applied in the dorsal-posterior region of the middle ventricle.
+Previous simulation studies of cilia-mediated flow in brain ventricles have
 used a volumetric force density to represent the cilia.
+Based on reconstruction of CSF flow in murine brain ventricles,
 Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}
-used a force expression that increased linearly from the wall to a maximum force density of
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m away from the wall,
-which represented cilium length. If we assumed a cilia array of the same thickness
-$l = 15$ \textmu m in our model, our maximum traction parameter $\vert\btau\vert_{\mathrm{max}}$
+employed a force that increased linearly from the ventricular wall to a maximum force density of
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m (the cilium length)
+away from the wall. If we assumed a cilia array of the same thickness
+$\delta = 15$ \textmu m in our model, the maximum stress $\vert\btau\vert_{\mathrm{max}}$
 would correspond to a maximum force density of 
 \begin{equation*}
-    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{l}
+    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{\delta}
         = \frac{\num{2.5e-3} \ \mathrm{Pa}}{15 \ \mu\mathrm{m}}
@@
 which is smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 \textmu m is the a typical length of cilia in human brain ventricles
-(in general the length is between 10--15 \textmu m~\cite{Afzelius2004CiliaRelatedDiseases}),
-while in zebrafish they are closer to 5 \textmu m~\cite{Salman2022ComputationalEmbryo}.
-With $l=5$ \textmu m, our traction parameter corresponds to a maximum force density of
-$f_c=507$ N/$\mathrm{m^3}$, which is in good agreement with
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$
-used by Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}.
-We note that they based $f_{\mathrm{max}}$ on reconstructions of
-flow velocities in murine brain ventricles.
-
+The length 15 \textmu m is the a typical length of cilia in human brain basedVentricles
+\cite{Afzelius2004CiliaRelatedDiseases, Siyahhan2014FlowVentricles},
+while in zebrafish they are closer to 5 \textmu m~\cite{Olstad2019CiliaryDevelopment,
+Salman2022ComputationalEmbryo, Ringers2023NovelEpithelia}.
+With $\delta=5$ \textmu m, our cilia traction corresponds to a maximum force density of
+$f_c=507$ N/$\mathrm{m^3}$, which is very similar to
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$~\cite{Siyahhan2014FlowVentricles}.
 Another study that used a force density to model ciliary motion is
@@
 in the central canal of zebrafish embryos was modeled using a cilia force density of
-4000 N/$\mathrm{m^2}$. The resulting numerical velocity fields matched well with
-in vivo measurements, where the maximum velocity magnitude was around 5 \textmu m/s
-(recall that our model exhibits a maximum of 27.9 \textmu m/s).
-The geometry they studied resembles a pipe, probably offering more flow resistance
-than the open geometry considered in our work, which may be why they needed a larger
-force density to accurately represent experimental results. In any case, it is
-interesting to note that our and these two previous studies have estimated
-cilia force densities that only differ by one order of magnitude.
+4000 N/$\mathrm{m^2}$. Averaging this value over the central canal diameter 8.9 \textmu m
+they measured yields 449 N/$\mathrm{m^3}$. It is very interesting to note the similarity 
+in cilia force densities estimated in our and these two previous studies.
+
+% The geometry they studied resembles a pipe,
+% probably offering more flow resistance than the open geometry considered in our work,
+% which may be why they needed a larger force density to accurately represent
+% experimental results. In any case,
 
@@
 by initially using fTetWild~\cite{Hu2020FastWild} and subsequently
-local refinement functionality in DOLFINx~\cite{dolfinx2023preprint}. The mesh
+local refinement functionality in DOLFINx~\cite{dolfinx2023preprint}. The standard mesh
 consists of 141 512 tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu

### 2025-03-24 paper/main.tex
methods and discussion updates

@@
 \affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}, \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
-\date{}
+\date{\vspace{-2em}}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}\caption{Simulated distribution and evolution after photoconversion of
-    extracellular vesicles (EVs) ($D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). 
-    \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the ROIs.
+    \includegraphics[width=\textwidth]{graphics/figure2_simulation_results_different_coeffs.png}
+    \caption{Simulated distribution and evolution after photoconversion of
+    extracellular vesicles (EVs, $D_1$), STM-GFP ($D_2$) and Dendra2 ($D_3$). 
+    \textbf{a.} Geometry-centered clip of the ventricles mesh showing the locations of the 
+    regions of interest (ROIs).
     \textbf{b--d.} Slices of the concentration field simulated
@@
     Slices are taken in the $xz$-plane ($y=0.140$ mm, the center of the geometry).
-    The colorbar is scaled so the maximum is the maximum concentration of the Dendra2 
-    concentration field slice at the last time instant.
-    \textbf{e--g.} Mean concentration $\cbar$ in each region of interest (ROI)
-    as function of time for diffusion coefficients $D_1$, $D_2$ and $D_3$, respectively. 
+    \textbf{e--g.} Mean concentration $\cbar$ in each ROI
+    as function of time for diffusion coefficients $D_1$, $D_2$ and $D_3$. 
     \textbf{h.} The time $\hat{t}$ before the mean concentration $\cbar$ exceeds a
@@
 note minor differences however. The simulated values of $\cbar_i$ at
-the final time \fixme{(0.72, 0.82, 0.56, 0.35 and X in ROIs 2--6, respectively)}
+the final time (0.80, 0.76, 0.86, 0.60 and 0.38 in ROIs 2--6, respectively)
 are generally higher than the corresponding experimental $\Delta F$
@@
 To assess how these variations influence solute distribution,
-we consider four alternative brain ventricles meshes:
+we consider four alternative ventricular geometries:
 one where the duct connecting the anterior and middle ventricles is constricted
@@
 With an interest in assessing the impact of ventricular morphology on solute transport,
-we simulated transport on modified ventricular geometries.
-Notably, shrinking ducts reduced interventricular solute movement, while shrinking
+we simulated transport in modified ventricular geometries.
+Notably, shrinking ducts reduced interventricular solute distribution, while shrinking
 the middle ventricle reduced diffusive transport upstream of the flow field.
-We previously identified large inter-individual variation in ventricular size and
+We previously identified large interindividual variation in ventricular size and
 CSF velocities between larva at given developmental stages and throughout
@@
 \subsection{Computational modeling aspects}
-We chose to model the cilia as a force
-exerted tangentially on the boundary, as opposed to a
-couple of previous continuum model simulation studies of
-cilia-mediated flow where cilia were represented by body
-forces,~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}.
-We employed slip boundary conditions at the ventricular walls,
+We modeled motile cilia as a stress
+exerted tangentially on the CSF at the ventricular walls
+while employing a slip boundary condition,
 motivated by experimental observations of the
@@
 wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. 
+The BDM-DG scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) we used to discretize the
+governing equations of the flow is computationally more expensive
+than more conventional approaches such as a
+Taylor-Hood discretization
+($P_2-P_1$ elements)~\cite{Stenberg1990ErrorProblem}, or lower-order enriched
+elements, such as the mini-element
+($P_1-P_1$ with a velocity stabilization)~\cite{Brezzi2011MixedMethods}.
+Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
+than or equal to $k$.
+We opted for the BDM-DG scheme because of its exactly-mass-conserving property;
+by the definition of the elements, the numerical approximation of
+the CSF velocity satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
+This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
+an important property for the stability of the advection-diffusion equation\cite{CITATION}.
 In addition to its favorable mass-conserving property, the 
@@
 Bertoluzza2017BoundaryHemodynamics}.
-
-The BDM-DG scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employed for the Stokes equations
-is computationally more expensive than a more conventional approach based on
-e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
-($P_2-P_1$ elements) or lower-order enriched
-elements~\cite{Brezzi2011MixedMethods},
-such as the mini-element ($P_1-P_1$ with a velocity stabilization).
-Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
-than or equal to $k$.
-We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
-as the elements by definition satisfy the incompressibility constraint for the fluid.
-This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
-an important property for the stability of the advection-diffusion equation\cite{CITATION}.
 
@@
 by initially using fTetWild~\cite{Hu2020FastWild} and subsequently
-local refinement functionality in DOLFINx~\cite{dolfinx2023preprint}. The standard mesh
-consists of 141 512 tetrahedral cells with a maximal (minimal) edge length of 14.9 \textmu
+local refinement functionality in DOLFINx~\cite{dolfinx2023preprint}. 
+The geometry spans approximately 600 microns along the rostrocaudal axis
+and around 300 microns in the lateral direction. At most around
+100 microns separates the ventral and dorsal ventricular walls.
+The standard mesh consists of 141 512 tetrahedral cells with a
+maximal (minimal) edge length of 14.9 \textmu
 m (3.1 \textmu m) (\Crefpanels{fig:fig1}{d}). Parts of the
@@
       \nabla \cdot \uu &= 0 
-      \quad  \text{in } \Omega,
+      \quad  \text{in } \Omega,\label{eq:stokes_eqs_cont} 
   \end{align}
@@
 $\uu \cdot \nn = 0$ and no tangential traction $\bsigpar = {\bf 0}$).
-Unless noted otherwise, the free-slip condition is applied on the
-boundary. We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
+We assume that the system starts at rest: $\uu(\xx, t=0) = \mathbf{0}$.
 
@@
 each predicting a CSF flow velocity $\uu$ and pressure $p$.
+In all of the scenarios, $\Gs$ denotes a free-slip boundary.
 \begin{itemize}
@@
     contributions both from the cilia forces and the cardiac pulsations.
-    In this scenario, we apply the tangential traction $\btau$ on the cilia boundary
+    In this scenario, we let $\Gamma=\Gs\cup\Gc\cup\Gp$ and apply the tangential traction $\btau$ on the cilia boundary
     $\Gc$ and prescribe the normal pressure $\Tilde{p}$ on the anterior/posterior boundary $\Gp$. % Model 0/Model C
@@
     cilia forces but no cardiac pulsations.
-    Here, we apply a tangential traction $\btau$ on the cilia boundary $\Gc$.
-    In the absence of cardiac flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
+    Here, $\Gamma=\Gs\cup\Gc$, and we apply a tangential traction $\btau$ on the cilia boundary $\Gc$.
+    In the absence of cardiac-induced flow, the anterior/posterior boundary $\Gp=\emptyset$. % Model I/Model A
 
@@
     cardiac pulsations but no cilia forces.
-    Here, we set the tangential traction to zero on the cilia boundary
-    $\Gc$, while prescribing the normal pressure $\Tilde{p}$ on the
+    In this scenario, we disregard the cilia and consider $\Gamma=\Gs\cup\Gp$, prescribing the normal pressure $\Tilde{p}$ on the
     anterior/posterior boundary $\Gp$.  % Model II/Model B
@@
 \begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega\setminus\Omega_{\mathrm{pc}},
     \label{eq:adv_diff_strong}
@@
 available\fixme{~\cite{zenodo-link-to-all-code}}.
-A direct solver using MUMPS~\cite{Amestoy2011Mumps} was used to solve the
+A direct solver using MUMPS~\cite{Amestoy2011Mumps} is used to solve the
 linear systems resulting from the discretized Stokes equations.
-For the discretized advection-diffusion equation, we used an iterative
-linear solver based on GMRES~\cite{Saad1986GMRES:Systems} with block Jacobi
-preconditioning~\cite{Jacobi1845UeberGleichungen}. We discretize the time-dependent 
-diffusion equation (without advection) and use the assembled linear system matrix
+For the discretized advection-diffusion equation, we use a flexible GMRES solver~\cite{fgmres}
+with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen} for the outer solves
+and ILU preconditioning for the inner solves~\cite{chan1997approximate}. 
+We discretize the time-dependent diffusion equation (without advection)
+and use the assembled linear system matrix
 as the preconditioner matrix for the advection-diffusion problem.

### 2025-03-24 paper/main.tex
minor updates
abstract update

@@
 \author[2, *]{Nathalie Jurisch-Yaksi}
-\affil[1]{Department for Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway} % Kristian Augusts gate 23, 0164
+\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway} % Kristian Augusts gate 23, 0164
 \affil[2]{Department of Clinical and Molecular Medicine, Norwegian University of Science and Technology, Trondheim, Norway} % Erling Skjalgsons gate 1, 7491
@@
     Cerebrospinal fluid (CSF) is integral to brain function, as the fluid
-    provides mechanical support of the brain and the flow of CSF helps
+    provides mechanical support for the brain and the flow of CSF helps
     distribute nutrients, neurotransmitters and metabolites throughout
@@
     by beating of motile cilia, hair-like structures that line the ependymal cell layer
-    of the brain ventricles. Despite the physiological importance of CSF flow,
+    of the walls of the brain ventricles. Despite the physiological importance of CSF flow,
     the underlying mechanisms of cilia-mediated flow and transport

### 2025-03-25 paper/main.tex
add A-D eq. stability references

@@
 This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
-an important property for the stability of the advection-diffusion equation\cite{CITATION}.
+an important property for the stability of the advection-diffusion
+equation\cite{cesmelioglu2022compatible, johnson2009numerical}.
 In addition to its favorable mass-conserving property, the 

### 2025-03-25 paper/main.tex
edits after read-through

--- 2025-03-24 paper/main.tex
@@
 \author[1,3]{Marie E.~Rognes}
-\author[2, *]{Nathalie Jurisch-Yaksi}
+\author[2,*]{Nathalie Jurisch-Yaksi}
 \affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway} % Kristian Augusts gate 23, 0164
@@
 
-% Text: Please use section headings and subheadings as specified below. For communications, all section headings apart from Experimental Section should be removed
-% Please make the first reference to a display item bold: \textbf{Figure 1}
-% Do not abbreviate Figure, Equation, etc.; display items are always singular, i.e., Figure 1 and 2.
-% Equations are always singular, i.e., Equation 1 and 2, and should be inserted using the {equation} environment, not as graphics
-% Please do not use footnotes in the text, additional information can be added to the Reference list.
-
-%\section{First Section}
-
-%\subsection{First Subsection}
-
-%\subsubsection{First Sub Subsection}
-
-%\threesubsection{First lowest-level subsection}
-
 \begin{document}
@@
 \begin{abstract}
-
 Cerebrospinal fluid (CSF) is integral to brain function, as the fluid
@@
 cardiac cycle, the respiration, neural activity, and bodily
-movement~\cite{Brodal2016, del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
+movements~\cite{Brodal2016, del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
 Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment,
@@
 Our results show that diffusion plays a major role in the transport of small solutes,
-whereas cilia majorly contribute to the movement of larger particles.
+whereas cilia are paramount for the movement of larger particles.
 We also found that the location of cilia, as well as changes to the ventricular geometry,
-largely impact solute distribution. In summary, our work presents a computational
+largely impact solute distribution.
+In summary, our work presents a computational
 framework that can be applied to other
@@
 zebrafish larval brain ventricles
-(\Crefpanels{fig:fig1}{a--c})~\cite{Olstad2019CiliaryDevelopment}. We
-first ask whether we can accurately represent these flow patterns with
+(\Crefpanels{fig:fig1}{a--c})~\cite{Olstad2019CiliaryDevelopment}.
+We attempt to accurately represent these flow patterns with
 computational fluid dynamics driven by cardiac pulsations and motile
@@
 
-We model the net forces induced by motile cilia as a steady
+We assume that viscous forces are dominating the intraventricular CSF flow,
+and model the flow by the Stokes equations.
+The net forces imparted by motile cilia on the CSF are modeled as a steady
 bidirectional traction acting on parts of the ventricular wall
-(\Crefpanels{fig:fig1}{d}). Simulations show that this traction alone
+(\Crefpanels{fig:fig1}{d}), and we assume free velocity slip at the walls.
+Simulations show that this traction alone
 leads to a partial compartmentalization of the ventricular system,
@@
 
-When combining the contributions, we recognize flow features
+When combining cilia motion and cardiac pulsations, we recognize flow features
 persisting throughout the cardiac cycle, now with vortex structures in
@@
 
-%% Over one cardiac cycle, the CSF flow speed reaches up to
-%% 28.0 \textmu m/s, dorsally in the posterior part of the middle
-%% ventricle. This peak is attained at the time instant coinciding with
-%% the time of peak caudal cardiac pulsatile flow,
-
-%% Using the observed maximum velocity magnitude and choosing the height
-%% of the middle ventricle ($110$ \textmu m) as a characteristic length
-%% scale yields a Reynolds number $\mathrm{Re} \approx 0.004$, justifying
-%% the assumption of Stokes flow.
-
-%We model the compartmentalized and pulsatile CSF flow observed in vivo~(\Crefpanels{fig:fig1}{b, c}) by the Stokes equations, and solve the equations numerically using a finite element method.
-
-%To characterize CSF flow patterns predicted by
-%computational fluid dynamics within the brain ventricles,
-
-%we first consider the simulated CSF velocity and pressure when only
-%modeling cilia motion, disregarding cardiac pressure pulsations.
-
 \subsection{Ventricular solute transport is advection-dominated for larger molecules}
-
-%We next explore the impact of these CSF flow patterns and magnitudes
-%on solute transport within the brain ventricles.
 
@@
 question, we simulate the distribution and evolution of three
-different solutes injected within a region of interest (ROI 1) in the
+different diffusing solutes injected within a region of interest (ROI 1) in the
 dorsal region of the middle ventricle (\Crefpanels{fig:fig2}{a}),
@@
 Dendra2 ($D_3 = 1.15 \times 10^{-10}$ m$^2$/s).
-
-%As expected, transport occurs more rapidly with increasing diffusion
-%coefficient.
 
@@
 
-%% To quantify the balance of advection versus diffusion as transport
-%% mechanisms, we calculate the Péclet numbers $\mathrm{Pe}_1=519$,
-%% $\mathrm{Pe}_2=14.7$ and $\mathrm{Pe}_3=7.4$ for $D_1$, $D_2$ and
-%% $D_3$, respectively.  Since $\mathrm{Pe}>1$, this indicates that
-%% advection is the dominant transport mechanism on a global scale.
+To further quantify the solute transport, we examine the mean
+concentrations $\cbar_i(t)$ in six ROIs over time
+(\Crefpanels{fig:fig2}{e--g}) and, in addition, the times $\hat{t}_i$
+when the mean concentrations first exceed a threshold value
+$\hat{c}_i$ (\Crefpanels{fig:fig2}{h}).  Higher diffusion coefficients
+result in more rapid transport (\Crefpanels{fig:fig2}{e--g}), with
+lower times-to-threshold in ROIs 2--6 (\Crefpanels{fig:fig2}{h}). For
+all three diffusion coefficients, the solute first spreads within the
+middle ventricle, covering ROIs 2--4, before appearing in the anterior
+ventricle (ROI 5) and finally reaching the posterior ventricle
+(ROI 6). Notably, the extracellular vesicles, associated with the smallest diffusion
+coefficient, do not reach the posterior ventricle (ROI 6) within the
+simulated time frame~\Crefpanels{fig:fig2}{b, e}.
 
@@
 
-To further quantify the solute transport, we examine the mean
-concentrations $\cbar_i(t)$ in the six ROIs over time
-(\Crefpanels{fig:fig2}{e--g}) and, in addition, the times $\hat{t}_i$
-when the mean concentrations first exceed a threshold value
-$\hat{c}_i$ (\Crefpanels{fig:fig2}{h}).  Higher diffusion coefficients
-result in more rapid transport (\Crefpanels{fig:fig2}{e--g}), with
-lower times-to-threshold in ROIs 2--6 (\Crefpanels{fig:fig2}{h}). For
-all three diffusion coefficients, the solute first spreads within the
-middle ventricle, covering ROIs 2--4, before appearing in the anterior
-ventricle (ROI 5) and finally reaching the posterior ventricle
-(ROI 6). Notably, the extracellular vesicles, associated with the smallest diffusion
-coefficient, do not reach the posterior ventricle (ROI 6) within the
-simulated time frame~\Crefpanels{fig:fig2}{b, e}.
-
-%% For all three diffusion coefficients, the dynamics of ROI 5
-%% is significantly delayed compared to ROI 2--4,
-%% and ROI 6 is the slowest.
-
-%The dynamics at the site of photoconversion (ROI 1)
-%is logarithmic and follows from imposing \Cref{eq:photoconversion_curve}.
-
-%% For ROIs 2--6, we observe faster kinetics with higher diffusion coefficients
-%% (\Crefpanels{fig:fig2}{e--g}),
-%% which results in smaller times-to-threshold
-%% (\Crefpanels{fig:fig2}{h}).
-
 \subsection{Model validation by comparison with photoconversion experiments}
@@
 
-Comparing the intensity changes with the simulated concentration
-profiles in ROIs 1--6 (\Crefpanels{fig:fig3}{a, b}) show that the
+Comparison of the intensity changes with the simulated concentration
+profiles in ROIs 1--6 (\Crefpanels{fig:fig3}{a, b}) shows that the
 model predictions agree well with the experimental measurements. We
@@
 experimental values (\Crefpanels{fig:fig3}{c, d}).
-
-%% We obtained very similar kinetics curves (\Crefpanels{fig:fig3}{a, b})
-%% and time-to-threshold values (\Crefpanels{fig:fig3}{c, d}) when
-%% comparing our experiments (\Crefpanels{fig:fig3}{a, c}) with
-%% simulation (\Crefpanels{fig:fig3}{b, d}).
-
-%% Importantly, since the initial condition of the simulation is a mean
-%% concentration of zero, the mean concentration $\cbar$ can be
-%% interpreted as the change in mean concentration and is thus a similar
-%% metric to $\Delta F$.
 
@@
 %0.18155055624229066 ROI 6
-% Final mean c values ROIs 2-6: 0.7637806  0.72025859 0.81903216 0.56204164 0.34926411
+% Final mean c values ROIs 2-6: 0.80, 0.76, 0.86, 0.60 and 0.38
 
@@
 As observed both experimentally and computationally,
-the absence of motile cilia alters the CSF flow patterns. 
+the absence of motile cilia alters CSF flow patterns. 
 We next investigate the implications of these changes on intraventricular
@@
 
-We first experimentally measured the movement of photoconverted
-Dendra2 signal in control and motile-cilia mutant (\emph{smh})
-zebrafish. In ROIs 2 and 4, which measure Dendra2 distribution
+We experimentally measured the movement of proteins by monitoring
+photoconverted Dendra2 signal in control zebrafish and 
+motile-cilia mutant \emph{schmalhans} (\emph{smh}) zebrafish.
+In ROIs 2 and 4, which quantify Dendra2 distribution
 downstream of the photoconversion site, we observed a slower increase
@@
 compared to controls (\Crefpanels{fig:fig4}{b}). We found no significant differences
-in the Dendra2 distribution in ROIs 3, 5, and 6 between
-\emph{smh} mutants and controls.
+between \emph{smh} mutants and controls
+in the Dendra2 distribution in ROIs 3, 5, and 6.
 
@@
 as the maximum velocity magnitude drops from 27.9 \textmu m/s to 7.9 \textmu m/s.
-In vivo, these cilia generate the strongest flow at
-this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
+In vivo, these dorsal cilia generate the strongest flow at
+this developmental stage of the fish~(\Crefpanels{fig:fig1}{c})~\cite{Olstad2019CiliaryDevelopment}.
 In contrast, removing cilia in the anterior ventricle or the ventral region of the middle
@@
 contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
-force~(\Crefpanels{fig:fig5}{b}). The magnitude of the force contributions are thus
+force~(\Crefpanels{fig:fig5}{b}). The magnitude of these force contributions are thus
 more similar than the difference in their impact on the maximum velocity magnitudes.
@@
 one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
-and the combination of the above three modifications (\Crefpanels{fig:fig6}{a, b}). In these
-four modified geometries the volume is reduced by 3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively,
+and the combination of the above three modifications (\Crefpanels{fig:fig6}{a, b}).
+In these four modified geometries, the total volume is reduced by
+3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively,
 compared to the original geometry.
@@
 shrunk middle ventricle.
-Here the transport to the posterior ventricle (ROI 6) is reduced,
-in spite of a 6.6\% increase in the ventral cilia forces.
+This reduction in the transport to the posterior ventricle (ROI 6)
+happens in spite of a 6.6\% increase in the ventral cilia forces.
 Additionally, for the shrunk middle configuration, the transport upstream of CSF flow towards the
@@
 for solute transport, with notable differences in transport resulting from
-relatively small geometry modifications. This may explain why
+relatively modest geometry modifications. This may explain why
 we observed larger differences in the cilia-deficient computational
-model compared to the experimental data in \Cref{fig:fig4},
+model results compared to the experimental data in \Cref{fig:fig4},
 as the model and the fish have slightly different geometries.
@@
 flow mechanisms are well described, thereby allowing us to validate
-our simulation experimentally. Nevertheless, our computational framework can be adapted to,
+our simulations experimentally. Nevertheless, our computational framework can be adapted to,
 and implemented in, other ventricular systems in the future, once the flow parameters of such systems
-are comprehensively resolved. By imposing tangential traction and normal pressure
+are comprehensively resolved. We assumed that intraventricular CSF flow was governed
+by the Stokes equations.
+By imposing tangential traction and normal pressure
 on the CSF flow, we were able to reproduce flow fields with similar features
@@
 based on changes in fluorescence intensity $\Delta F$ (experiments) and
-mean concentration $\cbar$ (simulations) as functions of time.
+mean concentration $\cbar$ (simulations) over time.
 Even though we identified similar dynamics in simulations and
@@
 between the simulations and experiments is the fact that the
-computational model is 3D, while the experiments only resolve
-two-dimensional features.
+computational model is three-dimensional, while the
+experiments only resolve two-dimensional features.
 
@@
 motility and ventricular morphology, we manipulated certain
-parameters in our models. First, we investigated how complete loss of cilia motility
+parameters in our model and the computational geometry.
+First, we investigated how complete loss of cilia motility
 impacted the transport dynamics. Simulations with a cardiac-induced/no-cilia lead to
@@
 slower dynamics in the rest of the middle ventricle (ROIs 3 and 4), whereas the
-posterior ventricle (ROI 6) was unaffected by the loss
-of cilia motility, indicating that transport from the middle to the posterior ventricle is
+posterior ventricle (ROI 6) was unaffected by the loss of cilia motility,
+further indicating that transport from the middle to the posterior ventricle is
 purely driven by diffusion at this developmental stage.
@@
 as the ventral cilia help induce flow towards the posterior ventricle.
-Removing the cilia in the anterior ventricle did not affect the transport.
+Removing the cilia in the anterior ventricle affected CSF flow only locally,
+and did not affect the global transport.
 
@@
 Notably, shrinking ducts reduced interventricular solute distribution, while shrinking
-the middle ventricle reduced diffusive transport upstream of the flow field.
+the middle ventricle obstructed diffusive transport upstream of the flow field.
 We previously identified large interindividual variation in ventricular size and
@@
 Our results suggest that these two parameters, CSF velocities and ventricular size,
-may well co-vary and explain the variation in the two.
+may well affect each other, which helps explain the variation in the two.
 
@@
 
-\subsection{Computational modeling aspects}
+\subsection{Numerical approximation and computational model parameters}
 We modeled motile cilia as a stress
@@
 wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. 
-The BDM-DG scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) we used to discretize the
-governing equations of the flow is computationally more expensive
+The Brezzi-Douglas-Marini and discontinuous Galerkin scheme
+$\mathrm{BDM}_1$-$\mathrm{DG}_0$
+we used to discretize the governing equations of the flow
+is computationally more expensive
 than more conventional approaches such as a
 Taylor-Hood discretization
-($P_2-P_1$ elements)~\cite{Stenberg1990ErrorProblem}, or lower-order enriched
+($P_k-P_{k-1}$ elements)~\cite{Stenberg1990ErrorProblem}, or lower-order enriched
 elements, such as the mini-element
@@
 Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
-than or equal to $k$.
+than or equal to the integer $k$.
 We opted for the BDM-DG scheme because of its exactly-mass-conserving property;
 by the definition of the elements, the numerical approximation of
-the CSF velocity satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
-This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
-an important property for the stability of the advection-diffusion equation\cite{CITATION}.
-In addition to its favorable mass-conserving property, the 
-Brezzi-Douglas-Marini and discontinuous Galerkin (BDM-DG) discretization scheme 
+the CSF velocity $\uu_h$ satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
+This yields $\normlinf{\nabla\cdot\uu_h}=0$ to within solver tolerances,
+an important property for the stability of the advection-diffusion
+equation\cite{cesmelioglu2022compatible, johnson2009numerical}.
+In addition to its favorable mass-conserving property,
+the BDM-DG discretization scheme 
 we employed for the Stokes equations
-lets us impose the impermeability condition strongly, and the tangential
-traction boundary condition weakly, without any tailored approach,
-since these boundary conditions appear naturally in the weak form of the
-Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
+lets us impose the impermeability condition $\uu\cdot\nn=0$
+strongly without any tailored approach,
+since the BDM elements control the normal component of the 
+velocity~(\Cref{subsec:appendixA1})~\cite{Brezzi1985TwoProblems}.
+If instead (for example) Taylor-Hood
 elements were to be used, the impermeability boundary condition must
@@
 or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
-Bertoluzza2017BoundaryHemodynamics}.
+Bertoluzza2017BoundaryHemodynamics}, which affects
+convergence properties and increases problem complexity.
 
@@
 ventricular system is closed.
-We handled the outflux by leaving the advective flux term as an unknown in the weak formulation
+We handled the outflux by imposing zero diffusive flux while
+leaving the advective flux term as an unknown in the weak formulation
 of the advection-diffusion equation. This has been referred to with different names
@@
 constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}. 
-We deliberately excluded the space proximal to in- and outflow boundaries in
-the anterior and posterior ventricles (ROIs 5 and 6) to limit adverse effects of 
-the advective transport at the in- and outflux boundaries on the mean concentrations.
+In defining ROIs 5 and 6 in the anterior and posterior ventricles,
+we deliberately excluded the space proximal to
+in- and outflow boundaries to limit adverse effects of 
+the advective flux boundary condition on the mean concentrations.
 
@@
 
-\subsection{Estimation of computational model parameters}
 The diffusion coefficients used in this study were based on experimental values. 
@@
 We heuristically determined the magnitude of the cilia tangential traction boundary condition
-with the parameter $\tau = 0.65$ mPa. The maximum stress $\vert\btau\vert_{\mathrm{max}} = 2.5$ mPa
+with the parameter $\tau = 0.65$ mPa. The maximum stress
+$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$
 was applied in the dorsal-posterior region of the middle ventricle.
@@
     f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{\delta}
-        = \frac{\num{2.5e-3} \ \mathrm{Pa}}{15 \ \mu\mathrm{m}}
+        = \frac{\num{2.5e-3} \ \mathrm{N/m^2}}{\num{15e-6} \ \mathrm{m}}
         = 169 \ \mathrm{N/m^3},
@@
 which is smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 \textmu m is the a typical length of cilia in human brain basedVentricles
+The length 15 \textmu m is the typical length of cilia in the human brain
 \cite{Afzelius2004CiliaRelatedDiseases, Siyahhan2014FlowVentricles},
@@
 Salman2022ComputationalEmbryo, Ringers2023NovelEpithelia}.
-With $\delta=5$ \textmu m, our cilia traction corresponds to a maximum force density of
+With $\delta=5$ \textmu m, our cilia stress corresponds to a maximum force density of
 $f_c=507$ N/$\mathrm{m^3}$, which is very similar to
@@
 in cilia force densities estimated in our and these two previous studies.
-
-% The geometry they studied resembles a pipe,
-% probably offering more flow resistance than the open geometry considered in our work,
-% which may be why they needed a larger force density to accurately represent
-% experimental results. In any case,
 
@@
 To date, motile-cilia deficiency has been associated with altered brain function
-in the zebrafish, dysfunctional establishment of left-right symmetry,
+in zebrafish, dysfunctional establishment of left-right symmetry,
 and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004CiliaRelatedDiseases,
@@
 microscopic and macroscopic parameters for larger brains, once these parameters are acquired.
-
-\subsection{Limitations and further work}
-The model presented has certain limitations. Future work could consider improving:
-\begin{itemize}
-    \item quantify cilia force parameter to avoid tuning
-    \item spatial heterogeneity of the cilia, how this affects flow and transport
-    \item time-varying cilia?
-    \item improved advection-diffusion equation influx/outflux BCs, or instead
-    modeling deformation of a closed ventricular system. 
-    and investigating how the arising flow compares with pulsatile flow observed in experiments
-    \item FSI: CSF flow coupled to 1D/2D/3D cilia structures.
-    \item any comments on experiments?
-\end{itemize}
 
@@
 while most of their transport is governed by diffusion.
+
+\subsection{Limitations and further work}
+The model presented has certain limitations. Future work could consider improving:
+\begin{itemize}
+    \item time-varying cilia?
+    \item FSI: CSF flow coupled to 1D/2D/3D cilia structures.
+    \item any comments on experiments?
+\end{itemize}
 

### 2025-03-25 paper/main.tex
minor fixes

@@
 As observed both experimentally and computationally,
-the absence of motile cilia alters CSF flow patterns. 
+absence of motile cilia alters CSF flow patterns. 
 We next investigate the implications of these changes on intraventricular
@@
 induce CSF flow while simultaneously permitting enforcement of the impermeability condition
-$\uu\cdot\nn=0$ on the ventricular walls. Such wall-motion induced CSF flow has been modeled and
+$\uu\cdot\nn=0$ on the ventricular walls. Such wall motion-induced CSF flow has been modeled and
 simulated successfully in the human brain ventricular system~\cite{Causemann2022HumanFramework,
@@
 
-The diffusion coefficients used in this study were based on experimental values. 
+The diffusion coefficients used in this study are based on experimental values. 
 The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$
@@
 the CSF in which the photoconverted Dendra2 are transported in our experiments may be more viscous
-than we assumed. This would reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
+than we assumed. This could reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
 but based on reports of protein concentration having a limited impact on the viscosity of
@@
 In large brains such as the human brain, we presume ciliary beating mostly 
-contributes to flow in localized regions proximal to the ventricular walls due to
+contributes to flow in localized regions proximal to the ventricular walls, due to
 the microscopic length of the cilia.
@@
 developmental stages of the brain~\cite{Hirokawa2006NodalAsymmetry}, and the discovery
-of a cilia-driven flow network in rodent brains suggest such selective
+of a cilia-driven flow network in rodent brains suggests such selective
 transport~\cite{Faubel2016Cilia-basedVentricles}.

### 2025-03-25 paper/main.tex
fix fig1 references

@@
 pulsatile pressure difference between the anterior and posterior
-boundaries (\Crefpanels{fig:fig1}{d, \fixme{g}}). The resulting flow
-is pulsatile and directional (\Crefpanels{fig:fig1}{\fixme{f}}), and
+boundaries (\Crefpanels{fig:fig1}{d, f}). The resulting flow
+is pulsatile and directional (\Crefpanels{fig:fig1}{g}), and
 in the absence of the cilia, the vortex structures vanish. The

### 2025-03-25 paper/main.tex
reformulate cilia forces

@@
 
-We assume that viscous forces are dominating the intraventricular CSF flow,
-and model the flow by the Stokes equations.
-The net forces imparted by motile cilia on the CSF are modeled as a steady
-bidirectional traction acting on parts of the ventricular wall
+Assuming that viscous forces are dominating the intraventricular CSF flow,
+we model the flow by the Stokes equations.
+The net forces of motile cilia acting on the CSF are modeled as a steady,
+bidirectional tangential traction acting on parts of the ventricular wall
 (\Crefpanels{fig:fig1}{d}), and we assume free velocity slip at the walls.

### 2025-03-26 paper/main.tex
add div(u) -> stability references, edit supplementaries

@@
 an important property for the stability of the advection-diffusion
-equation\cite{cesmelioglu2022compatible, johnson2009numerical}.
+equation\cite{cesmelioglu2022compatible, johnson2009numerical, gresho1998incompressible}.
 In addition to its favorable mass-conserving property,
@@
 
-\textbf{Only-cilia/no-cardiac model.} This model version has cilia forces
+\textbf{Cilia-driven/no-cardiac model.} This model version has cilia forces
 as the only mechanism driving flow. We consider the
@@
 impermeability condition, enforcing no flow normal to the boundary,
-whereas~\Cref{eq:modelA_slip_BC_shear} imposes a stress tangential to
-the boundary. These tangential stresses are applied to represent
+whereas~\Cref{eq:modelA_slip_BC_shear} imposes a traction tangential to
+the boundary. This tangential traction is applied to represent
 the forces that the collective cilia motion exerts on the cerebrospinal fluid.
 
-The boundary conditions~\Cref{eq:modelA_slip_BC} are set weakly through the stress
+The boundary conditions~\Cref{eq:modelA_slip_BC} are set weakly through the
 boundary integral 
@@
 \begin{equation*}
-    \hat{\bsig} = \bsigperp + \bsigpar
+    \hat{\bsig} = \bsigperp + \bsigpar.
 \end{equation*}
@@
 \end{equation}
-The second term on the right-hand side of~\Cref{eq:boundary_integral_BC2}
-is moved to the right-hand side of the weak form, since $\btau$ is known
- Using $\hat{\bsig}_{\perp} = (\hat{\bsig}\cdot\nn)\nn$,
+Since $\btau$ is known, the second term on the right-hand side of~\Cref{eq:boundary_integral_BC2}
+is moved to the right-hand side of the weak form.
+With $\hat{\bsig}_{\perp} = (\hat{\bsig}\cdot\nn)\nn$,
 we can write the first term on the right-hand side of~\Cref{eq:boundary_integral_BC2} as
@@
 \end{equation}
-Since $\Gp=\emptyset$ in this model version, and the term~\Cref{eq:boundary_integral_BC_normal}
-vanishes owing to the construction $\VV$. As a result, for the cilia-only/no-cardiac model,
+This term vanishes owing to the construction $\VV$.
+As a result, for the cilia-driven/no-cardiac model,
 the weak form of the momentum equation takes the following form:
@@
 \begin{equation}
-    -\intO{q\nabla\cdot\uu} = 0,\quad\forall q\in Q
+    -\intO{q\nabla\cdot\uu} = 0,\quad\forall q\in Q.
     \label{eq:pressure_weak_form}
@@
     \centering
-    \caption{Definitions of $\rr$ and $\lambda(\xx)$ used in for the cilia tangential 
+    \caption{Definitions of $\rr$ and $\lambda(\xx)$ used in the cilia tangential 
     traction boundary condition $\btau = \tau\lambda(\xx)P_{\nn}(\rr)$,
@@
 
-\textbf{Only-cardiac/no-cilia model.} For this model version,
+\textbf{Cardiac-induced/no-cilia model.} For this model version,
 the only physical mechanism inducing fluid flow is the cardiac cycle.
+The cardiac cycle generates directional back-and-forth motion of the CSF
+in the zebrafish brain ventricles.
 We model the influence of the cardiac cycle with a normal pressure boundary condition:
@@
     - p\mathbf{I})\nn\cdot\vv}\notag\\
-    &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}
+    &= \intGp{\mu(\nabla\uu)^T\nn\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}.
     \label{eq:modelB_boundary_integral1}
@@
 \begin{align*}
-    {\VV}_h &= \Big\{\vv_h : \vv_h\in\mathbf{H}(\mathrm{div});
-    \vv_h\vert_K\in\big[P_k\big]^d;
+    \VV_h &= \Big\{\vv_h : \vv_h\in\mathbf{H}(\mathrm{div});
+    \vv_h\vert_K\in\big[P_k(K)\big]^d;
     \forall K\in\Omega_h;
     \vv_h\cdot\nn=0 \ \text{on } \Gamma\setminus\Gp\Big\},\\
-    Q_h &= \Big\{q_h : q_h\in L^2;  q_h\vert_K\in P_{k-1}; \forall K\in\Omega_h\Big\},
+    Q_h &= \Big\{q_h : q_h\in L^2;  q_h\vert_K\in P_{k-1}(K); \forall K\in\Omega_h\Big\},
 \end{align*}
@@
 The BDM family of elements have degrees of freedom
-associated with integral moments of vector components normal to facets of the mesh,
-and is therefore non-conforming. However, the BDM-DG is $\mathbf{H}(\mathrm{div})$
-conforming and thus exactly mass-conserving, because the continuity equation can be satisfied
+associated with integral moments of vector components normal to facets of the mesh.
+Because $\VV_h\not\subset\VV$, the elements are non-conforming.
+This BDM-DG scheme for the Stokes equations
+is $\mathbf{H}(\mathrm{div})$ conforming and thus exactly mass-conserving,
+because the continuity equation can be satisfied
 in every computational mesh cell due to the fact that $\nabla\cdot\VV_h\subset Q_h$.
@@
 $\nn$ is the normal vector on a facet separating two cells,
-where the plus and minus signs denote variables in each of the two cells.
+and the plus and minus signs denote variables in each of the two cells.
 The normal vector is chosen such that it points towards the exterior of
@@
 across interior facets, where the penalty parameter $\gamma>0$ must be chosen large enough
-to achieve stability. For convergence the penalization term
-scales with the cell diameter of a mesh cell $h$,
-defined as the maximal distance between two points in a cell. The other two terms
-of $\mathcal{A}_{\mathrm{stab}}$ are added to ensure coercivity and symmetry of
+to achieve stability. The penalization term
+scales with the average of the cell diameter of neighboring mesh cells,
+with $h$ defined as the maximal distance between two points in a cell. The other two terms
+of $\mathcal{A}_{\mathrm{stab}}$ are added to ensure consistency and symmetry of
 the bilinear form, such that the problem is well-defined.
@@
 \begin{equation*}
-    \JJ(c) = c\uu - D\nabla c.
-\end{equation*}
+    \JJ(c) = c\uu - D\nabla c,
+\end{equation*}
+where $c\in H^1$ is the solute concentration and
+$\uu\in\VV$ is the cerebrospinal fluid velocity .
 We consider $\JJ = \JJ(c)$, unless otherwise indicated.
-The concentration $c\in W$ and the cerebrospinal fluid velocity $\uu\in\VV$.
 The weak form of~\Cref{eq:adv_diff_strong_DG} is derived by
@@
 \textbf{Only-cilia/no-cardiac model.} We consider $\Omega$ to be
-a closed domain with impermeable walls, setting $\JJ\cdot\nn=0$ on $\Gamma$.
-The weak form is then reduced to
+a closed domain with impermeable walls, so that the whole boundary
+$\Gamma$ constitutes a no-flux boundary $\Gnf$.
+By imposing $\JJ\cdot\nn=0$ on $\Gamma=\Gnf$, 
+the weak form~\Cref{eq:adv_diff_weak_formA1} is reduced to
 \begin{equation*}
@@
 \begin{equation*}
-    \intGin{(\JJ\cdot\nn)} = \intGout{(\JJ\cdot\nn)},
-\end{equation*}
-which means no mass would be added to the system except for at the injection site,
-which is desired as we endeavor to model the ventricles as a closed system.
+    \intGin{(\JJ\cdot\nn)} = \intGout{(\JJ\cdot\nn)}.
+\end{equation*}
+This implies conservation of solute concentration at each timestep,
+which is the desired behavior
+as we endeavor to model the ventricles as a closed system.
+Note that the total concentration would still increase in time,
+because we impose the concentration profile in the photoconversion
+region $\Omega_{\mathrm{pc}}$ (region of interest 1).
 
@@
 discontinuous Galerkin finite elements~\cite{Arnold1982AnElements}.
-Let the subscript $h$ denote discrete variables. Exchanging the
-variables in~\Cref{eq:adv_diff_weak_formB} with their discrete
+Exchanging the variables in~\Cref{eq:adv_diff_weak_formB} with their discrete
 counterparts yields the discrete weak form: find $c_h\in W_h$ such that
@@
 \begin{equation}
-    W_h = \Big\{w_h : w_h\in L^2;  w_h\vert_K\in P_k; \forall K\in\Omega_h\Big\}.
+    W_h = \Big\{w_h : w_h\in L^2;  w_h\vert_K\in P_k(K); \forall K\in\Omega_h\Big\}.
 \end{equation}
@@
 is used to upwind the velocity $\uu_h$ with respect to a
-facet. Similar to the stabilization employed for the Stokes equations, the first two terms
-of \Cref{eq:SIP_stabilization} penalize jumps in the concentration flux across interior facets.
-The stabilization parameter $\alpha>0$ must be chosen
-large enough to achieve stability. The two last terms in $a_{\mathrm{stab}}$ are
-added to preserve coercivity and symmetry of the bilinear form. The average and jump operators used
+facet. The stabilization parameter $\alpha>0$ must be chosen
+large enough to achieve stability. In~\Cref{eq:SIP_stabilization}, the first two terms
+penalize jumps in the concentration flux across interior facets,
+and are needed to preserve coercivity of the bilinear form.
+The last two terms in $a_{\mathrm{stab}}$ are
+added to preserve symmetry and consistency of the bilinear form, respectively.
+The average and jump operators used
 in~\Cref{eq:SIP_stabilization} are defined, respectively, as
@@
 Errors of the velocity $\uu_h$ and pressure $p_h$ approximated with finite elements
-were measured in the $\mathbf{H}^1$ and $L^2$ error norms, respectively.
+were measured in $\mathbf{H}^1$ and $L^2$ error norms, respectively.
 With the exact velocity field $\uu_{\mathrm{ex}}$, the $\mathbf{H}^1$
-error norm was calculated as
+error semi-norm was calculated as
 \begin{equation*}
@@
 Lagrange polynomials of three polynomial degrees higher than the elements used to approximate
-the functions, meaning that polynomial degrees 5 and 4 were used for the velocity and pressure
+the functions, meaning that polynomial degrees 4 and 3 were used for the velocity and pressure
 errors, respectively. Numerical integration was performed with a Gauss quadrature rule,
@@
 for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{L}^2$
-and $\mathbf{H}^1$ error norms for $\uu_h$, and the $L^2$ error norm for
-$p_h$~(\Cref{tab:cylinder_error_rates}). Based on the error norm calculations,
-we also calculated the experimental order of convergence~(\Cref{subsec:norms_and_eoc}).
+error norms and $\mathbf{H}^1$ error semi-norms for $\uu_h$,
+and $L^2$ error norms for $p_h$~(\Cref{tab:cylinder_error_rates}).
+Based on the error norm calculations,
+we calculated the experimental order of convergence,
+as defined in \Cref{subsec:norms_and_eoc}.
 We observe convergence in all of the reported error norms. Furthermore,
 we report the error in calculation of the maximum velocities, and observe
-convergence in this error as well. Lastly, we calculated the $L^2$ norm of
+convergence in this error as well. Finally, we calculated the $L^2$ norms of
 the divergence $\nabla\cdot\uu_h$ to verify the property of mass conservation.
@@
 mesh~(\Cref{tab:ventricles_norms_BDM}).
-For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$.
-For a velocity vector $\uu=(u_x, u_y, u_z)$, the velocity magnitude is
-$u = \sqrt{u_x^2 + u_y^2 + u_z^2}$. We also report the maximum value
-$\normlinf{u_h}$ scaled by the area $|\Gc|=\intGc{}$ over which tangential traction
-$\btau$ was applied. We chose this measure using $|\Gc|$ as a scale because the regions
-of the mesh marked as cilia-populated changes slightly with every mesh refinement,
-owing to the unstructured organization of the mesh cells. This change in the surface
-area over which the tangential traction was applied directly affected
-the maximum velocity magnitude,
-since the maximum velocity magnitude is a result of the total amount of force
-$\intGc{\btau\cdot P_{\nn}(\rr)}$ applied on the ciliated boundary, where the cilia
-vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ as introduced in~\Cref{subsec:appendixA1}.
-In the numerical experiments, we set a constant $\tau = 6.5\times 10^{-4}$ Pa and
-$\lambda(\xx)=1$. We set $\rr = (1, 0, 1)$ in the ventral middle ventricle cilia region
+We used the original mesh obtained by meshing the surface geometry using
+fTetWild~\cite{fTetWild}; the region around the photoconversion region is not
+refined on the mesh used for the convergence study.
+For the cilia traction vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ introduced in~\Cref{subsec:appendixA1},
+we set a constant $\tau = 6.5\times 10^{-4}$ Pa and
+$\lambda(\xx)=1$ in the numerical experiments.
+We set $\rr = (1, 0, 1)$ in the ventral middle ventricle cilia region
 and $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle cilia
@@
 
-To account for the fact that the volume $|\Omega|=\intO{}$ also changes
+For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$.
+We also report $\normlinf{u_h}$ scaled by the area $|\Gc|=\intGc{}$ of the cilia
+boundary $\Gc$ over which tangential traction
+$\btau$ was applied. We chose this measure using $|\Gc|$ as a scale because the regions
+of the mesh marked as cilia-populated change slightly with every mesh refinement,
+owing to the unstructured organization of the mesh cells.
+These changes in the surface area over which the tangential traction is applied
+result in changes to the maximum velocity magnitude,
+since the maximum velocity magnitude is a result of the total amount of force
+$\intGc{\sqrt{\btau\cdot \btau}}$ applied on the cilia boundary.
+
+To account for the fact that the volume of the domain $|\Omega|=\intO{}$ also changes
 slightly with mesh refinement, we report the $\mathbf{L}^2$ norm of $\uu_h$ scaled by $|\Omega|$.
-Finally, we provide verification of mass conservation by reporting the $\mathbf{L}^2$ norms of
+Finally, we provide verification of mass conservation by reporting the $L^2$ norms of
 the divergence $\nabla\cdot\uu_h$. We remark that the units used in the model
@@
     \caption{Velocity norms under mesh refinement
-    on the brain ventricles mesh using the only-cilia/no-cardiac flow model
-     with $\btau = \tau P_{\nn}(\rr)$, using
+    of the brain ventricles mesh using the cilia-driven/no-cardiac flow model
+    with $\btau = \tau \lambda(\xx)P_{\nn}(\rr)$, using
+    $\lambda(\xx)=1$,
     $\tau = 6.5\times 10^{-4}$ Pa,
@@
 \subsection{Discussion of the numerical approximation and convergence rates}
-The Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme
-($\mathrm{BDM}_1$-$\mathrm{DG}_0$) that we employ for the Stokes equations
+A priori error estimates for the
+Brezzi-Douglas-Marini and discontinuous Galerkin discretization scheme
+$\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ are naturally 
+derived in a mesh-dependent broken $H^k$-norm for $\uu$ and the $L^2$-norm for the pressure.
+The respective error norms are expected to decay with order $k$~\cite{Cockburn2005AEquations}.
+For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
+reports the velocity errors in the standard $H^k$ norm. Using polynomial degree  
+$k=1$, we observe linear convergence in the velocity in the $\mathbf{H}^1$ error norm
+and the pressure in the $L^2$ error norm on the cylinder mesh. For the ventricles meshes,
+we observe consistent values of the reported quantities, verifying the model
+implementation.
+
+The $\mathrm{BDM}_1$-$\mathrm{DG}_0$ scheme that we employ for the Stokes equations
 is computationally more expensive than a more conventional approach based on
@@
 such as the mini-element ($P_1-P_1$ with a velocity stabilization).
-Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
-than or equal to $k$.
 We opted for the BDM-DG scheme because of its exactly-mass-conserving property,
@@
 fundamental to attain a stable discretization of the advection-diffusion equation
-in advection-dominated regions. Using conventional
-Taylor-Hood elements for the Stokes equations
-stability of the advection-diffusion discretization either
-required excessive mesh refinement and/or problem-specific tuning of
-hyperparameters when employing a Streamline-Upwind/Petrov Galerkin stabilization
-method~\cite{Franca1992StabilizedModel}, which is why we also opted for a DG method
-for the advection-diffusion equation.
-Probing numerical values of the divergence of
-the velocity when using Taylor-Hood elements for the fluid equations revealed that,
-on the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was
+in advection-dominated regions. Preliminarily, we attempted
+to discretize the Stokes equations with 
+Taylor-Hood elements, but with the resulting numerical approximation
+of the velocity $\uu_h$, we were unable to achieve
+stability of the advection-diffusion discretization.
+Numerical experiments identified non-zero divergence of $\uu_h$
+as the root cause of these stability issues.
+On the standard computational mesh, the $L^2$ norm of $\nabla\cdot\uu_h$ was
 in the order of $10^{-6}$, while the
-maximum value of the divergence of the velocity was of order unity. This is a result
-of the fact that incompressibility is only achieved in a (global) weak sense when
-employing Taylor-Hood elements. On a refined mesh with roughly six times as many
+maximum value of the divergence of the velocity was of order unity.
+On a refined mesh with roughly six times as many
 computational cells as the standard mesh, the numerical values of
-$\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$ were still
-of order unity. This may lead to the
-hyperbolic advective term in the advection-diffusion equation accumulating errors
-that grow unstable over time.
+$\normltwo{\nabla\cdot\uu_h}$ and $\normlinf{\nabla\cdot\uu_h}$
+remained practically unchanged. This is a result
+of the fact that incompressibility is only achieved in a weak sense when
+employing Taylor-Hood elements. Since the advective flux
+\begin{equation*}
+    \nabla\cdot(c\uu) = c(\nabla\cdot\uu) + \uu\cdot\nabla c,
+\end{equation*}
+where in this case $\nabla\cdot\uu\neq 0$, a source (or sink) term for the concentration
+is introduced. This may introduce errors in the numerical approximation of $c$
+and lead to instabilities and spurious oscillations, especially in the case of
+advection-dominated transport
+\cite{gresho1998incompressible, cesmelioglu2022compatible, johnson2009numerical}.
 
 In addition to its favorable mass-conserving property, the BDM-DG scheme
-lets us impose the impermeability condition strongly, and the tangential
-traction boundary condition weakly, without any tailored approach,
-since these boundary conditions appear naturally in the weak form of the
-Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
+lets us impose the impermeability condition strongly without any tailored approach,
+since this boundary condition appears naturally in the weak form of the
+Stokes equations~(\Cref{subsec:appendixA1}) and the BDM elements control
+the normal component of the velocity. If instead (for example) Taylor-Hood
 elements were to be used, the impermeability boundary condition must
@@
 
-A priori error estimates for the $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ scheme are naturally 
-derived in a mesh-dependent broken $H^k$-norm for $\uu$ and the $L^2$-norm for the pressure.
-The respective error norms are expected to decay with order $k$~\cite{Cockburn2005AEquations}.
-For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
-reports the velocity errors in the standard $H^k$ norm. Using polynomial degree  
-$k=1$, we observe linear convergence in the velocity in the $\mathbf{H}^1$ error norm
-and the pressure in the $L^2$ error norm.
-
 \section{Quantification of velocities in particle tracking}\label{sec:appC_particle_transport}
-Particle tracking data~\cite{Olstad2019CiliaryDevelopment} was analyzed.
+Particle tracking data was analyzed~\cite{Olstad2019CiliaryDevelopment}.
 For four zebrafish, five recordings with a few particles for each fish were carried out.
@@
 The collected data constituted $x$ and $y$ positions of the particles at every time
-instant of image acquisition. The velocities $\uu_x$ and $\uu_y$ were determined by
+instant of image acquisition. The velocities $u_x$ and $u_y$ were determined by
 calculating the change in positions $\Delta x$ and $\Delta y$ relative to the change

### 2025-03-26 src/plot_compare_simulations_cilia_regions.py
update MMS code

@@ -32,9 +32,9 @@ volumes = [comm.allreduce(dfx.fem.assemble_scalar(dfx.fem.form(1*dx(tag))), op=M
 volumes[3] += volumes[2]+volumes[1]+volumes[0] # Add ROI volumes 1, 2, and 3 to get the total of ROI 4
 
 # Load data c_hat, the total concenctration in each ROI
-with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[0]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_original    = np.load(file)
-with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[1]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_dorsal  = np.load(file)
-with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[2]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_ventral = np.load(file)
+with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[0]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_original = np.load(file)
+with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[1]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_dorsal   = np.load(file)
+with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[2]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_ventral  = np.load(file)
 with open(f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenarios[3]}_dt={dt:.4g}/data/c_hats.npy', 'rb') as file: c_bar_anterior = np.load(file)
 
 # Divide the total concentrations in the ROIs by the volume of the respective ROI
@@ -42,7 +42,7 @@ for i in ROI_tags:
[…]

### 2025-03-26 src/plot_mean_concentration.py

@@ -27,7 +27,7 @@ transport_dir = '../output/transport/results/'
 
 # Problem version
 model_version = 'C'
-molecule = 'D2'
+molecule = 'D3'
 cilia_string = 'all_cilia'
 mesh_version = 'original'
 output_dir = f'../output/illustrations/'

### 2025-03-26 src/plot_slice_time_to_threshold.py

@@ -9,14 +9,7 @@ import matplotlib.pyplot as plt
 from mpi4py    import MPI
 from basix.ufl import element
 
-""" Visualize concentration slices in a 3x3 figure. """
-
-
-# Set latex text properties
-plt.rcParams.update({
-    "text.usetex": True,
-    "font.family": "serif"
-})
+""" Visualize time-to-threshold for a slice of the geometry. """
 
 comm = MPI.COMM_WORLD # MPI Communicator
 gm   = dfx.mesh.GhostMode.shared_facet
@@ -44,16 +37,16 @@ z_max = x_geo[:, 2].max()
 z_mid = (z_min + z_max) / 2
 
 # Set up unstructured grids with data
-W = dfx.fem.functionspace(mesh=mesh, element=element('DG', mesh.basix_cell(), k)) # DGk function space
+W = dfx.fem.functionspace(mesh=mesh, element=element('DG', mesh.basix_cell(), k)) # DG_k function space
 cells, types, x = dfx.plot.vtk_mesh(W)
 grid = pv.UnstructuredGrid(cells, types, x)
 
 # Load time to threshold function values
-c_in = dfx.fem.Function(W)
+t_hat = dfx.fem.Function(W)
 input_filename = f'../output/transport/mesh={mesh_version}_model={model_version}_molecule={molecule}_ciliaScenario={cilia_scenario}_dt={dt:.4g}/t_hat/'
-a4d.read_function(u=c_in, filename=input_filename, engine="BP4", time=0)
-grid.point_data["c"] = c_in.x.array.real
-grid.set_active_scalars("c")
+a4d.read_function(u=t_hat, filename=input_filename, engine="BP4", time=0, name='t_hat')
+grid.point_data['t_hat'] = t_hat.x.array.real
+grid.set_active_scalars('t_hat')
 grid = grid.threshold(0.0) # Remove all points with values below zero (points that never reached the threshold)
 grid = grid.threshold(840, invert=True) # Clip off posterior edge providing spurious coloring of cells
 
@@ -66,14 +59,25 @@ cmap = cm.dense_r
 my_colors = {'colors' : cmap.colors}
 
 # Add grid to plotter
-plotter.add_mesh(grid.slice(normal=[0, -1, 0]), cmap=cmap, clim=[0, 800], show_scalar_bar=False)
+plot_point_cloud = False
+if plot_point_cloud:
+    # Convert grid to polydata
[…]

### 2025-03-26 src/simulate_mms_verification.py

@@ -14,10 +14,10 @@ print = PETSc.Sys.Print
 # Operators
 # NOTE: these are the jump operators from Krauss, Zikatonov paper.
 # Jump is just a difference and it preserves the rank 
-Jump = lambda arg: arg('+') - arg('-')
+Jump = lambda arg: arg("+") - arg("-")
 
 # Average uses dot with normal and AGAIN MINUS; it reduces the rank
-Avg = lambda arg, n: .5*(dot(arg('+'), n('+')) - dot(arg('-'), n('-')))
+Avg = lambda arg, n: .5*(dot(arg("+"), n("+")) - dot(arg("-"), n("-")))
 
 # Action of (1 - n x n)
 Tangent = lambda v, n: v - n*dot(v, n)
@@ -31,7 +31,6 @@ def assemble_system(a_cpp: dfx.fem.form, L_cpp: dfx.fem.form, bcs: list[dfx.fem.
 
     b = assemble_vector(L_cpp)
     apply_lifting(b, [a_cpp], bcs=[bcs])
-    # b.zeroEntries()
     b.ghostUpdate(addv=PETSc.InsertMode.ADD_VALUES, mode=PETSc.ScatterMode.REVERSE)
     set_bc(b, bcs=bcs)
     b.ghostUpdate(addv=PETSc.InsertMode.INSERT_VALUES, mode=PETSc.ScatterMode.FORWARD)
@@ -46,11 +45,11 @@ def Stabilization(mesh: dfx.mesh.Mesh,
                 penalty: dfx.fem.Constant,
                 consistent: bool=True):
 
-    '''Displacement/Flux Stabilization from Krauss et al paper'''
+    """Displacement/Flux Stabilization from Krauss et al paper"""
     n, hA = ufl.FacetNormal(mesh), avg(ufl.CellDiameter(mesh))
 
     D  = lambda v: sym(grad(v)) # the symmetric gradient
-    dS = ufl.Measure('dS', domain=mesh)
+    dS = ufl.Measure("dS", domain=mesh)
 
     if consistent:
         return (-inner(Avg(2*mu*D(u), n), Jump(Tangent(v, n)))*dS
@@ -64,8 +63,8 @@ def get_system_mms(msh: dfx.mesh.Mesh, penalty_val: float, mu_val: float, direct
 
     k  = 1
     cell = msh.basix_cell()
-    Velm = element('BDM', cell, k)
-    Qelm = element('DG', cell, k-1)
[…]

### 2025-03-26 src/simulate_transport.py

@@ -1,9 +1,10 @@
+from diffusion import diffusion_problem
 from utilities.local_imports import *
 from utilities.mesh          import create_ventricle_volumes_meshtags
-from diffusion import diffusion_problem
 
 import os
 import time
+import adios2
 import adios4dolfinx as a4d
 
 from ufl       import avg, jump
@@ -41,9 +42,9 @@ SLIP                 = 9
 
 # Diffusion coefficients
 D_coeffs = {
-    'D1' : 2.17e-6, # Extracellular vesicles (150 nm radius)
-    'D2' : 57.5e-6, # STM-GFP 
-    'D3' : 115e-6,  # Dendra2 fluorescent protein
+    "D1" : 2.17e-6, # Extracellular vesicles (150 nm radius)
+    "D2" : 57.5e-6, # STM-GFP 
+    "D3" : 115e-6,  # Dendra2 fluorescent protein
 }
 
 class TransportSolver:
@@ -94,7 +95,7 @@ class TransportSolver:
             Cardiac cycle period in seconds.
         
         molecule : str
-            Which molecule to simulate transport of. Options are 'D1', 'D2' and 'D3'.
+            Which molecule to simulate transport of. Options are "D1", "D2" and "D3".
 
         element_degree : int
             Polynomial degree of finite element basis functions.
@@ -132,8 +133,8 @@ class TransportSolver:
         self.element_degree = element_degree
         
         # Read mesh and meshtags from velocity data file
-        self.mesh = a4d.read_mesh(comm=self.comm, filename=data_fname, engine='BP4', ghost_mode=self.ghost_mode)
-        self.ft   = a4d.read_meshtags(filename=data_fname, mesh=self.mesh, meshtag_name='ft')
+        self.mesh = a4d.read_mesh(comm=self.comm, filename=data_fname, engine="BP4", ghost_mode=self.ghost_mode)
+        self.ft   = a4d.read_meshtags(filename=data_fname, mesh=self.mesh, meshtag_name="ft")
         print(f"Total # of cells in mesh: {self.mesh.topology.index_map(self.mesh.topology.dim).size_global}")
 
         # Temporal parameters
@@ -154,7 +155,7 @@ class TransportSolver:
         self.a = 65
 
         # Output directory
-        self.output_dir = f'../output/transport/mesh={self.mesh_version}_model={self.model_version}_molecule={self.molecule}_ciliaScenario={cilia_string}_dt={dt:.4g}/'
[…]

### 2025-03-26 src/utilities/helpers.py

@@ -60,15 +60,15 @@ def nonmatching_mesh_interpolation(mesh0: dfx.mesh.Mesh,
         
         with dfx.io.VTXWriter(mesh0.comm, f"3D_function{string}.bp", [u], "BP4") as vtx:
             vtx.write(0)
-    
-    # # Check that the interpolation is correct
-    # nz_dofs = np.where(u1.x.array!=0.0)[0] # only check dofs where plane intersection is interior to the mesh
-    # assert np.allclose(
-    #     u.x.array[nz_dofs],
-    #     u1.x.array[nz_dofs],
-    #     rtol=np.sqrt(np.finfo(xtype).eps),
-    #     atol=np.sqrt(np.finfo(xtype).eps),
-    # )
+
+    # Check that the interpolation is correct
+    nz_dofs = np.where(u1.x.array!=0.0)[0] # only check dofs where plane intersection is interior to the mesh
+    assert np.allclose(
+        u.x.array[nz_dofs],
+        u1.x.array[nz_dofs],
+        rtol=np.sqrt(np.finfo(xtype).eps),
+        atol=np.sqrt(np.finfo(xtype).eps),
+    )
 
     return u1
 
@@ -99,16 +99,18 @@ def calc_error_L2(u_approx: dfx.fem.Function, u_exact: dfx.fem.Function, dX: ufl
             The L2 error norm.
         """
         # Create higher-order function space for solution refinement
-        degree = u_approx.function_space.ufl_element().degree()
-        family = u_approx.function_space.ufl_element().family()
+        degree = u_approx.ufl_element().degree
+        family = u_approx.ufl_element().family_name
         mesh   = u_approx.function_space.mesh
         if vector_elements:
             # Create higher-order function space based on vector elements
-            W = dfx.fem.FunctionSpace(mesh, ufl.VectorElement(family = family, 
-                                      degree = (degree + degree_raise), cell = mesh.ufl_cell()))
+            W = dfx.fem.functionspace(mesh, element(family=family, 
+                                                    degree=(degree+degree_raise),
+                                                    cell=mesh.basix_cell(),
+                                                    shape=(mesh.geometry.dim,)))
         else:
             # Create higher-order funciton space based on finite elements
-            W = dfx.fem.FunctionSpace(mesh, (family, degree + degree_raise))
+            W = dfx.fem.functionspace(mesh, (family, degree + degree_raise))
             
         # Interpolate the approximate solution into the refined space
         u_W = dfx.fem.Function(W)
[…]

### 2025-03-26 paper/main.tex
stability discussion

@@
 We used the original mesh obtained by meshing the surface geometry using
-fTetWild~\cite{fTetWild}; the region around the photoconversion region is not
+fTetWild~\cite{Hu2020FastWild}; the region around the photoconversion region is not
 refined on the mesh used for the convergence study.
@@
 of the fact that incompressibility is only achieved in a weak sense when
-employing Taylor-Hood elements. Since the advective flux
-\begin{equation*}
-    \nabla\cdot(c\uu) = c(\nabla\cdot\uu) + \uu\cdot\nabla c,
-\end{equation*}
-where in this case $\nabla\cdot\uu\neq 0$, a source (or sink) term for the concentration
+employing Taylor-Hood elements. The advective part of the total flux
+is
+\begin{equation*}
+    \nabla\cdot(c\uu) = c(\nabla\cdot\uu) + \uu\cdot\nabla c.
+\end{equation*}
+In the case that $\nabla\cdot\uu\neq 0$, a source (or sink) term for the concentration
 is introduced. This may introduce errors in the numerical approximation of $c$
@@
 \cite{gresho1998incompressible, cesmelioglu2022compatible, johnson2009numerical}.
+The $\mathrm{BDM}_1$-$\mathrm{DG}_0$ scheme avoids these issues,
+since $\nabla\cdot\uu_h=0$ is satisfied exactly as a result of the element definitions.
 

### 2025-03-26 paper/main.tex
final figure 3

@@
     because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
-    value of 0.25 in these regions.}
+    value of 0.25 in these regions. Scale bars 50 \textmu m.}
     \label{fig:fig3}

### 2025-03-26 paper/main.tex
place figures nicely

@@
 
-To further quantify the solute transport, we examine the mean
-concentrations $\cbar_i(t)$ in six ROIs over time
-(\Crefpanels{fig:fig2}{e--g}) and, in addition, the times $\hat{t}_i$
-when the mean concentrations first exceed a threshold value
-$\hat{c}_i$ (\Crefpanels{fig:fig2}{h}).  Higher diffusion coefficients
-result in more rapid transport (\Crefpanels{fig:fig2}{e--g}), with
-lower times-to-threshold in ROIs 2--6 (\Crefpanels{fig:fig2}{h}). For
-all three diffusion coefficients, the solute first spreads within the
-middle ventricle, covering ROIs 2--4, before appearing in the anterior
-ventricle (ROI 5) and finally reaching the posterior ventricle
-(ROI 6). Notably, the extracellular vesicles, associated with the smallest diffusion
-coefficient, do not reach the posterior ventricle (ROI 6) within the
-simulated time frame~\Crefpanels{fig:fig2}{b, e}.
-
 \begin{figure}%[H]
@@
 
+To further quantify the solute transport, we examine the mean
+concentrations $\cbar_i(t)$ in six ROIs over time
+(\Crefpanels{fig:fig2}{e--g}) and, in addition, the times $\hat{t}_i$
+when the mean concentrations first exceed a threshold value
+$\hat{c}_i$ (\Crefpanels{fig:fig2}{h}).  Higher diffusion coefficients
+result in more rapid transport (\Crefpanels{fig:fig2}{e--g}), with
+lower times-to-threshold in ROIs 2--6 (\Crefpanels{fig:fig2}{h}). For
+all three diffusion coefficients, the solute first spreads within the
+middle ventricle, covering ROIs 2--4, before appearing in the anterior
+ventricle (ROI 5) and finally reaching the posterior ventricle
+(ROI 6). Notably, the extracellular vesicles, associated with the smallest diffusion
+coefficient, do not reach the posterior ventricle (ROI 6) within the
+simulated time frame~\Crefpanels{fig:fig2}{b, e}.
+
 \subsection{Model validation by comparison with photoconversion experiments}
@@
 
-\begin{figure}%[H]
+\begin{figure}[H]
     \centering
-    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
+    \includegraphics[width=0.975\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
     \caption{
@@
     in each region of interest (ROI)
-    observed during experiments of photoconversion of Dendra2 proteins in ROI 1. 
-    Bold lines are mean values of the cohort and shaded regions cover one standard devation errors
-    in the mean.
+    observed during experiments monitoring
+    the movement of Dendra2 proteins photoconverted by laser targeting ROI 1. 
+    Bold lines are mean values of the cohort ($n=8$) and shaded regions cover
+    one standard devation errors in the mean.
     \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
@@
     one representative zebrafish larva.
-    Time to $\cbar(t)$ reaches a threshold value of 0.25 for
+    \textbf{d.} Time to $\cbar(t)$ reaches a threshold value of 0.25 for
     a transport simulation with diffusion coefficient $D_3$.
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering
     \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
-    \caption{\textbf{a.} Relative change in fluorescence intensity $F(t)$
+    \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$
     in each region of interest (ROI) for control (black lines, $n=8$)
@@
     \textbf{c.} Mean concentration $\cbar(t)$ in each ROI,
-    simulated using the baseline model (black lines) and the cardiac-only/no-cilia model (red lines).
+    simulated using the baseline model (black lines) and the cardiac-induced/no-cilia model (red lines).
     The horizontal gray lines mark the threshold value $\hat{c}$, and the time
@@
 more similar than the difference in their impact on the maximum velocity magnitudes.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
+    \caption{\textbf{a.} The three separate cilia regions for which cilia paralysis is simulated
+    by imposing a zero tangential traction boundary condition in the respective region.
+    \textbf{b.} The total tangential force applied to the boundary with the tangential traction
+    boundary condition in each of the three separate ciliated regions, as well as the total force
+    (the sum of the three regions), calculated with \Cref{eq:tangential_force_calculation}. 
+    \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
+    paralysis scenarios considered. The region named in the legend is the region
+    where we modify the cilia tangential traction boundary condition to a free-slip condition
+    in the CSF flow model.}
+    \label{fig:fig5}
+\end{figure}
 
@@
 less solute spreads towards the posterior ventricle (ROI 6).
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
-    \caption{\textbf{a.} The three separate ciliated regions cilia paralysis is simulated
-    by imposing a zero tangential traction boundary condition in the respective region.
-    \textbf{b.} The total tangential force applied with the tangential traction
-    boundary condition in the three separate ciliated regions, as well as the total
-    (the sum of the three regions), calculated with \Cref{eq:tangential_force_calculation}. 
-    \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
-    paralysis scenarios considered. The region named in the legend is the region
-    where we modify the cilia tangential traction boundary condition to a free-slip condition
-    in the CSF flow model.}
-    \label{fig:fig5}
-\end{figure}
 

### 2025-03-26 paper/main.tex
update refs

@@
 advection-diffusion equation were implemented and solved numerically with
-DOLFINx~\cite{dolfinx2023preprint} with petsc4py~\cite{Dalcin2011ParallelPython}
-as linear algebra backend. The simulation code is openly
+DOLFINx with petsc4py as linear algebra backend
+\cite{dolfinx2023preprint, Dalcin2011ParallelPython}.
+The simulation code is openly
 available\fixme{~\cite{zenodo-link-to-all-code}}.
@@
 linear systems resulting from the discretized Stokes equations.
-For the discretized advection-diffusion equation, we use a flexible GMRES solver~\cite{fgmres}
-with block Jacobi preconditioning~\cite{Jacobi1845UeberGleichungen} for the outer solves
-and ILU preconditioning for the inner solves~\cite{chan1997approximate}. 
+For the discretized advection-diffusion equation, we use a flexible GMRES solver
+with block Jacobi preconditioning for the outer solves
+and ILU preconditioning for the inner solves
+\cite{fgmres, Jacobi1845UeberGleichungen, chan1997approximate}. 
 We discretize the time-dependent diffusion equation (without advection)
@@
 
-%% \textbf{References}\\
-%% 1	((Journal articles)) a) A. B. Author 1, C. D. Author 2, Adv. Mater. 2006, 18, 1; b) A. Author 1, B. Author 2, Adv. Funct. Mater. 2006, 16, 1.\\
-%% 2	((Work accepted)) A. B. Author 1, C. D. Author 2, Macromol. Rapid Commun., DOI: 10.1002/marc.DOI.\\
-%% 3	((Books)) H. R. Allcock, Introduction to Materials Chemistry, Wiley, Hoboken, NJ, USA 2008.\\
-%% 4	((Edited books or proceedings volumes)) J. W. Grate, G. C. Frye, in Sensors Update, Vol. 2 (Eds: H. Baltes, W. Göpel, J. Hesse), Wiley-VCH, Weinheim, Germany 1996, Ch. 2.\\
-%% 5	((Presentation at a conference, proceeding not published)) Author, presented at Abbrev. Conf. Title, Location of Conference, Date of Conference ((Month, Year)).\\
-%% 6	((Thesis)) Author, Degree Thesis, University (location if not obvious), Month, Year.\\
-%% 7	((Patents)) a) A. B. Author 1, C. D. Author 2 (Company), Country Patent Number, Year; b) W. Lehmann, H. Rinke (Bayer AG) Ger. 838217, 1952.\\
-%% 8	((Website)) Author, Short description or title, URL, accessed: Month, Year.\\
-%% 9	…((Please include all authors, and do not use “et al.”))\\
-
-% Table of contents entry should be 50 - 60 words long
-% Image should be 55 mm broad and 50 mm high or 110 mm broad and 20 mm high
-
-%% \begin{figure}
-%% \textbf{Table of Contents}\\
-%% \medskip
-%%   \includegraphics{toc-image.png}
-%%   \medskip
-%%   \caption*{ToC Entry}
-%% \end{figure}
-
 \end{document}

### 2025-03-27 paper/main.tex
final fig6, update plot codes

@@
 
-\title{\textbf{Advection versus diffusion in intraventricular transport}}
+\title{\textbf{Advection versus diffusion in brain intraventricular transport}}
 %
@@
 \affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}, \href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
-\date{\vspace{-2em}}
+\date{\vspace{-2em}} % Remove space between affiliations and abstract
 
@@
 in the brain ventricles remain yet to be comprehensively resolved.
-In this study, we analyze and evaluate the role of motile cilia
-in intraventricular CSF flow and transport. We use the geometry
-of the zebrafish larval brain ventricles, for which we have detailed knowledge of cilia properties and CSF motion velocities
-and frequencies, to develop finite element methods that model flow and transport.
+In this study, the role of motile cilia in brain intraventricular CSF flow and transport
+is analyzed and evaluated. The geometry of the zebrafish larval brain ventricles,
+for which detailed knowledge of cilia properties and CSF motion velocities
+and frequencies exists, was used to develop finite element methods that model flow and transport.
 The computational model is validated by in vivo experiments that monitor transport
 of a photoconvertible protein secreted in the brain ventricles.
-Our results show that while cilia contribute to advection of large particles,
+The results show that while cilia contribute to advection of large particles,
 diffusion plays a significant role in the transport of small molecules such as proteins.
-We also found that cilia location and the geometry of the ventricular system impact solute distribution.
-Altogether, our work presents a computational framework that can be applied to other
+It is also demonstrated that cilia location and the geometry of the ventricular system impact solute distribution.
+Altogether, this work presents a computational framework that can be applied to other
 ventricular systems, together with new concepts of how molecules are transported within the brain and its ventricles.
@@
 biological organisms and in several human organs,
-of which the brain is one of them~\cite{Fulford1986Muco-ciliaryLung,
+of which the brain is one of them~\cite{DGama2025MotileBrain,
+Fulford1986Muco-ciliaryLung,
 Pacherres2022CiliaryProduction, Jahn1972LocomotionProtozoa,
 Brennen1977FluidFlagella, Ringers2020Role, spassky2013motile,
-DGama2025MotileBrain, mitchell2007evolution,
+Pellicciotta2020Cilia, mitchell2007evolution,
 Tsukita2012CoordinatedFeet, BLAKE1974MechanicsMotion,
@@
 protein. To quantify the transport of photoconverted proteins, we
-measured and calculated the change in fluorescence intensity $\Delta F
+measured and calculated the change in fluorescence intensity $\Delta F(t)
 = (F(t)-F_0)/F_0$ over time (\Crefpanels{fig:fig3}{a}).
@@
 flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
-Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases},
+Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
+Pellicciotta2020Cilia},
 but also in other phenomena such as maintaining healthy functioning of mucous transport in
@@
 The supernatant containing gDNA was utilized for KASP assays-based analysis.
-The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
-used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
-For each sample well, the \fixme{master} mix contained: 5 \textmu L of master mix; 0.14
-\textmu L of assay mix; 1.86 \textmu L of RO water.
+The gDNAs were diluted (1:2) with water. 
+The KASP assay was run following the guidelines of the
+manufacturer (LGC Biosearch Technologies™) with 3 \textmu L gDNA,
+5 \textmu L of master mix, 0.14 \textmu L of assay mix
+and 1.86 \textmu L of RO water per well on a 96-well plate.
 

### 2025-03-27 src/plot_compare_experiments_control_mutant.py

@@ -15,7 +15,7 @@ plt.rcParams.update({
 plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
 
 # Set data directory and load .mat files
-data_dir = "../data/data_photoconversion/aggregated_data/"
+data_dir = "../data/photoconversion_data/aggregated_data/"
 metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
 colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
 control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data

### 2025-03-27 src/plot_compare_simulations_geometry.py

@@ -148,5 +148,5 @@ for row_idx in range(ax_c.shape[0]):
 
 plt.tight_layout()
 plt.subplots_adjust(hspace=0.30)
-if save_figs: fig_c.savefig(f"../output/illustrations/compare_geometry/all_ROIs_model{model_version}.png")
+if save_figs: fig_c.savefig(f"../output/illustrations/compare_geometry/mean_concentrations_model={model_version}_molecule={molecule}.png")
 plt.show()

### 2025-03-27 src/plot_fluorescence_intensities.py

@@ -12,7 +12,7 @@ plt.rcParams.update({
 plt.rcParams["text.latex.preamble"] += "\\usepackage{sfmath}" # Enable sans-serif math font
 
 # Set data directory and load .mat files
-data_dir = "../data/data_photoconversion/aggregated_data/"
+data_dir = "../data/photoconversion_data/aggregated_data/"
 metadata = loadmat(data_dir+"metadata") # Metadata, e.g. FPS and pixel size
 colors   = loadmat(data_dir+"colors")['color'] # The colors used for plotting
 control = loadmat(data_dir+"control_data")['control'] # The control fish cohort photoconversion data

### 2025-03-27 src/plot_mean_concentration.py

@@ -50,7 +50,7 @@ c_threshold1 = 0.25 # threshold value used to calculate "time to threshold" in R
 c_threshold2 = 0.10 # threshold value used to calculate "time to threshold" in ROIs 5-6
 
 # Plot parameters
-save_fig = 0 # Save figures if set to 1, don't save if set to 0
+save_fig = 1 # Save figures if set to 1, don't save if set to 0
 lw = 6 # linewidth
 
 # Loop over molecules

### 2025-03-27 src/plot_mean_concentration_and_time_to_threshold.py

@@ -22,7 +22,7 @@ comm = MPI.COMM_WORLD # MPI Communicator
 gm   = dfx.mesh.GhostMode.shared_facet
 f = 2.22
 dt = 1/f/20
-colors = loadmat('../data/data_photoconversion/aggregated_data/colors')['color'] # The colors used for plotting
+colors = loadmat('../data/photoconversion_data/aggregated_data/colors')['color'] # The colors used for plotting
 fig_num = 1 # Figure number index
 
 # Directories
@@ -121,8 +121,8 @@ for bar_container, hatch in zip(bars.containers, hatches):
     for bar in bar_container:
         bar.set_hatch(hatch)
 
-ax2.set_xlabel("ROI number", fontsize=35, labelpad=25)
-ax2.set_ylabel(r"Time to threshold $\hat{t}$ [s]", fontsize=35, labelpad=50)
+ax2.set_xlabel("ROI number", fontsize=32, labelpad=25)
+ax2.set_ylabel(r"Time to threshold $\hat{t}$ [s]", fontsize=32, labelpad=50)
 ax2.tick_params(labelsize=35)
 ax2.legend(labels=[r'$D_1$', r'$D_2$', r'$D_3$'], loc='upper left', fontsize=32, frameon=True, fancybox=False, edgecolor='k')
 ax2.yaxis.tick_right()

### 2025-03-27 src/plot_slice_time_to_threshold.py

@@ -77,7 +77,7 @@ plotter.camera.focal_point = (x_mid, y_max, z_mid)
 plotter.camera.zoom(0.275)
 
 # Display the plot and save to file
-save_fig = 0
+save_fig = 1
 if save_fig:
     output_filename = f'../output/illustrations/slice_time_to_threshold_model={model_version}_molecule={molecule}'
     plotter.show(screenshot=output_filename+'.png')

### 2025-03-27 src/plot_slices_concentration.py

@@ -60,7 +60,7 @@ for j in range(len(record_periods)):
         cells, types, x = dfx.plot.vtk_mesh(W)
         grids.append(pv.UnstructuredGrid(cells, types, x))
         c_in = dfx.fem.Function(W)
-        input_filename = f'../output/transport/mesh={mesh_version}_model={model_version}_molecule=D{i}_ciliaScenario={cilia_scenario}_dt={dt:.4g}/'
+        input_filename = f'../output/transport/mesh={mesh_version}_model={model_version}_molecule=D{i}_ciliaScenario={cilia_scenario}_dt={dt:.4g}/checkpoints/concentration_snapshots/'
         a4d.read_function(u=c_in, filename=input_filename, engine="BP4", time=record_periods[j])
         grids[m].point_data["c"] = c_in.x.array.real
         grids[m].set_active_scalars("c")

### 2025-03-27 src/simulate_transport.py

@@ -606,7 +606,7 @@ if __name__ == "__main__":
     # B = cardiac-induced/no-cilia
     # C = cilia+cardiac (baseline)
 
-    model_version = "C" 
+    model_version = "B" 
     write_data = True # Write ROI mean concentrations as numpy data
     write_output_vtx = False # Write VTX output file
     write_output_xdmf = False # Write XDMF output file

### 2025-03-27 src/utilities/create_colormap.py

@@ -64,7 +64,7 @@ if __name__=='__main__':
         cb.set_ticks([0, 1])
         cb.set_ticklabels([0, 1.0])
         ax.tick_params(axis='x', labelsize=36)
-        ax.set_title(r"Concentration $c$ [-]", fontsize=42)
+        ax.set_title(r"Concentration $c$ [-]", fontsize=36)
         fig_name = "../../output/illustrations/colorbars/colorbar_D3.png"
     elif bar_type==2:
         fig = plt.figure(figsize=(15, 4))

### 2025-03-27 paper/main.tex
minor udpates

@@
     \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
-    cilia-only/no-cardiac flow model.
-    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
+    cilia-driven/no-cardiac flow model.
+    \textbf{f.} Illustration of the cardiac-related normal pressure forcing imposed on the
+    anterior/posterior boundaries. Time instants of streamline plots indicated.
+    \textbf{g.} Streamlines of the CSF flow field simulated with the cardiac-induced/no-cilia flow
     model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
-    \textbf{g.} Illustration of the cardiac-related normal pressure forcing imposed on the
-    anterior/posterior boundaries.
-    \textbf{h--j.} Streamlines simulated with the baseline flow model at
-    a time a time 25\% (\textbf{h}), 50\% (\textbf{i}) and 75\% (\textbf{j})
-    into the cardiac cycle. Times indicated in panel \textbf{g}.
-    %t=0.112613 s %t=0.225225 s %t=0.315315 s
+    \textbf{h--j.} Streamlines simulated with the baseline flow model (cilia+cardiac)
+    at a time 25\% (\textbf{h}), 50\% (\textbf{i}) and 75\% (\textbf{j})
+    into the cardiac cycle. %t=0.112613 s %t=0.225225 s %t=0.315315 s
     Scale bars 50 \textmu m.
@@
 pulsations. In particular, we consider three different molecular
-diffusion coefficients, corresponding to a large extracellular vesicle ($D_1 = 2.17
-\times 10^{-12}$ m$^2$/s), a 90 kDa protein STM-GFP ($D_2 = 5.75
-\times 10^{-11}$ m$^2$/s), and a 26 kDa photoconvertible protein
+diffusion coefficients, corresponding to a large extracellular vesicle (EV, $D_1 = 2.17
+\times 10^{-12}$ m$^2$/s), a 90 kDa Starmaker-Green Fluorescent Protein
+(STM-GFP, $D_2 = 5.75 \times 10^{-11}$ m$^2$/s),
+and a 26 kDa photoconvertible protein
 Dendra2 ($D_3 = 1.15 \times 10^{-10}$ m$^2$/s).
@@
     the cases fore-shrunk, middle shrunk, mid-hind shrunk, and the combination of the three.
-    The bars for the four shrunk scenarios thus
-    display $F_i/F_{\mathrm{original}}\times 100\%$.}
+    The bars for the four shrunk scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
     \label{fig:fig6}
@@
 
-\subsection{Numerical approximation and computational model parameters}
+\subsection{Numerical approximation and computational modeling aspects}
 We modeled motile cilia as a stress
@@
 in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
-Incorporating spatial arrangement heterogeneity in our model could possibly
+Incorporating spatial arrangement heterogeneity in our model could
 result in different transport timescales,
@@
 boundary condition on the CSF flow,
-we imposed a no-flux condition on the concentration. Imposing a pressure-driven
-cardiac-related flow on certain parts of the CSF flow boundary leads to in- and outflow,
-and the advective transport then requires handling of in- and outflux boundary conditions.
-We set an approximate periodic boundary condition on the the in- and outflux boundaries,
-such that the total mass is conserved in the
-limit that the timestep size is zero, reflecting our assumption that the
-ventricular system is closed.
+we imposed a no-flux condition on the concentration. The normal pressure
+boundary condition leads to in- and outflow of CSF,
+and this advective transport requires handling of in- and outflux boundary conditions on
+the concentration. For the influx, we applied an approximate periodic boundary condition
+that conserves the total solute concentration.
 We handled the outflux by imposing zero diffusive flux while
-leaving the advective flux term as an unknown in the weak formulation
-of the advection-diffusion equation. This has been referred to with different names
-in previous works, names such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition},
+leaving the advective flux term as an unknown in the weak form
+of the advection-diffusion equation. This approach has been referred to with different names,
+such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition},
 the ``no boundary condition"~\cite{Griffiths1997TheCondition}, and the 
@@
 A possible improvement to the in- and outflow boundary conditions would be
-to consider a 3D-0D coupling of the in- and outflow boundaries using
+to consider a 3D-0D coupling of in- and outflow using
 ordinary differential equations,
-similar to what has been done in cardiac
+similar to applications in cardiac
 modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
-However, if the ventricular system in reality is a closed system,
+However, if the brain ventricular system in reality is a closed system,
 one should rather seek out a way of modeling the CSF flow without open boundaries to avoid
@@
 Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
+
+We heuristically determined the magnitude of the cilia tangential traction boundary condition
+with the parameter $\tau = 0.65$ mPa. The maximum stress
+$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$
+was applied in the dorsal-posterior region of the middle ventricle.
+Previous simulation studies of cilia-mediated flow in brain ventricles have
+used a volumetric force density to represent the cilia.
+Based on reconstruction of CSF flow in murine brain ventricles,
+a previous study employed a force that increased linearly from
+the ventricular wall to a maximum force density of
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m (the cilium length)
+away from the wall~\cite{Siyahhan2014FlowVentricles}.
+If we assumed a cilia array of the same thickness
+$\delta = 15$ \textmu m in our model, the maximum stress $\vert\btau\vert_{\mathrm{max}}$
+would correspond to a maximum force density of 
+\begin{equation*}
+    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{\delta}
+        = \frac{\num{2.5e-3} \ \mathrm{N/m^2}}{\num{15e-6} \ \mathrm{m}}
+        = 169 \ \mathrm{N/m^3},
+\end{equation*}
+which is smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
+The length 15 \textmu m is the typical length of cilia in the human brain
+\cite{Afzelius2004CiliaRelatedDiseases, Siyahhan2014FlowVentricles},
+while in zebrafish they are closer to 5 \textmu m~\cite{Olstad2019CiliaryDevelopment,
+Salman2022ComputationalEmbryo, Ringers2023NovelEpithelia}.
+With $\delta=5$ \textmu m, our cilia stress corresponds to a maximum force density of
+$f_c=507$ N/$\mathrm{m^3}$, which is very similar to
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$~\cite{Siyahhan2014FlowVentricles}.
+Another study that used a force density to model ciliary motion is
+considered two-dimensional flow in the central canal of zebrafish
+embryos~\cite{Thouvenin2020OriginCanal}.
+Cilia was modeled using a cilia force density of
+4000 N/$\mathrm{m^2}$. Averaging this value over the central canal diameter 8.9 \textmu m
+measured in the study yields a maximum force of 449 N/$\mathrm{m^3}$.
+It is very interesting to note the similarity 
+in cilia force densities estimated in our and these two previous studies.
+\fixme{Previous work concluded that motile cilia align by response to the shear
+stress of flow. Perhaps there is an optimal cilia stress?}
 
@@
 have equal densities. Consequently, there is uncertainty in the diffusion coefficient values used.
-We note that Sadovsky~\emph{et al.}~\cite{GuraSadovsky2017MeasurementExpansion} reported that
+We note that one previous study reported that
 Dendra2 satisfies the Stokes-Einstein in a solution of similar viscosity
-to CSF. We used CSF density and viscosity values measured in
+to CSF\cite{GuraSadovsky2017MeasurementExpansion}.
+We used CSF density and viscosity values measured in
 humans~\cite{Bloomfield1998EffectsFluid},
@@
 incerasingly diffusive fields.
-
-We heuristically determined the magnitude of the cilia tangential traction boundary condition
-with the parameter $\tau = 0.65$ mPa. The maximum stress
-$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$
-was applied in the dorsal-posterior region of the middle ventricle.
-Previous simulation studies of cilia-mediated flow in brain ventricles have
-used a volumetric force density to represent the cilia.
-Based on reconstruction of CSF flow in murine brain ventricles,
-Siyahhan~\emph{et al.}~\cite{Siyahhan2014FlowVentricles}
-employed a force that increased linearly from the ventricular wall to a maximum force density of
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m (the cilium length)
-away from the wall. If we assumed a cilia array of the same thickness
-$\delta = 15$ \textmu m in our model, the maximum stress $\vert\btau\vert_{\mathrm{max}}$
-would correspond to a maximum force density of 
-\begin{equation*}
-    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{\delta}
-        = \frac{\num{2.5e-3} \ \mathrm{N/m^2}}{\num{15e-6} \ \mathrm{m}}
-        = 169 \ \mathrm{N/m^3},
-\end{equation*}
-which is smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 \textmu m is the typical length of cilia in the human brain
-\cite{Afzelius2004CiliaRelatedDiseases, Siyahhan2014FlowVentricles},
-while in zebrafish they are closer to 5 \textmu m~\cite{Olstad2019CiliaryDevelopment,
-Salman2022ComputationalEmbryo, Ringers2023NovelEpithelia}.
-With $\delta=5$ \textmu m, our cilia stress corresponds to a maximum force density of
-$f_c=507$ N/$\mathrm{m^3}$, which is very similar to
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$~\cite{Siyahhan2014FlowVentricles}.
-Another study that used a force density to model ciliary motion is
-Thouvenin~\emph{et al.}~\cite{Thouvenin2020OriginCanal}, where two-dimensional flow
-in the central canal of zebrafish embryos was modeled using a cilia force density of
-4000 N/$\mathrm{m^2}$. Averaging this value over the central canal diameter 8.9 \textmu m
-they measured yields 449 N/$\mathrm{m^3}$. It is very interesting to note the similarity 
-in cilia force densities estimated in our and these two previous studies.
 

### 2025-03-27 paper/main.tex
update appendix

@@
 To derive weak formulations of the continuous problem defined by the Stokes
-equations~\Cref{eq:appendix_stokes_eqs}, we consider the function space
+equations (\Cref{eq:appendix_stokes_eqs}), we consider the function space
 \begin{align*}
@@
 
-To derive a weak formulation of the Stokes equations~\Cref{eq:appendix_stokes_eqs},
+To derive a weak formulation of the Stokes equations (\Cref{eq:appendix_stokes_eqs}),
 we begin by multiplying~\Cref{eq:BDM_stokes_mom} with a
@@
 The reason for this is that all of the experimental images we compare
-with are taken in the $xz$-plane,
-rendering flow features in the $y$-direction unobservable.
+with are taken in the $xz$-plane (rostrocaudal-dorsoventral plane),
+rendering flow features in the $y$-direction (lateral) unobservable.
 In the following, we consider the way of handling the stress
@@
 on the boundary $\Gamma=\Gc\cup\Gs$. The boundary $\Gs$ is a free-slip boundary,
-where we impose the free-slip condition~\Cref{eq:modelA_full_slip_BC}.
-The first condition~\Cref{eq:modelA_slip_BC_impermeability} is the
+where we impose the free-slip condition given by \Cref{eq:modelA_full_slip_BC}.
+The first condition (\Cref{eq:modelA_slip_BC_impermeability}) is the
 impermeability condition, enforcing no flow normal to the boundary,
@@
 
-The boundary conditions~\Cref{eq:modelA_slip_BC} are set weakly through the
-boundary integral 
+The boundary conditions defined by~\Cref{eq:modelA_slip_BC}
+are set weakly through the boundary integral 
 \begin{equation}
@@
 \end{equation}
-in the weak form~\Cref{eq:modelA_weak_form1} of the Stokes equations.
+in the weak form of the Stokes equations (\Cref{eq:modelA_weak_form1}).
 We decompose the traction vector $\hat{\bsig}$ into a normal and tangential component:
@@
 combined with application of the tangential traction
-condition~\Cref{eq:modelA_slip_BC_shear} and the
-free-slip condition~\Cref{eq:modelA_full_slip_BC}, yields
+condition (\Cref{eq:modelA_slip_BC_shear}) and the
+free-slip condition (\Cref{eq:modelA_full_slip_BC}), yields
 \begin{equation}
@@
 \end{equation*}
-Next, multiplying the continuity equation~\Cref{eq:BDM_stokes_div}
+Next, multiplying the continuity equation (\Cref{eq:BDM_stokes_div})
 with a test function $q\in Q$, we require that
@@
 $(\uu, p)=(\mathbf{0}, C)$ satisfies the equations.
-Hence the system~\Cref{eq:stokes_weak_modelA} is singular with a one-dimensional nullspace
-of constant pressures.
-Consequently, assembly of our discretization of the  equations~\Cref{eq:stokes_weak_modelA}
+Hence \Cref{eq:stokes_weak_modelA} is a singular system 
+with a one-dimensional nullspace of constant pressures.
+Consequently, assembly of the discretization of the Stokes equations (\Cref{eq:stokes_weak_modelA})
 into a linear equation system $\mathbf{A}\mathbf{x}=\mathbf{b}$ yields a singular matrix $\mathbf{A}$.
@@
 The boundary $\Gs$ is handled as discussed in the previous section,
-such that the stress boundary integral~\Cref{eq:boundary_integral_BC1}
+such that the stress boundary integral in~\Cref{eq:boundary_integral_BC1}
 vanishes over $\Gs$. Therefore, we now have
@@
 the momentum equation. The second term is determined by
-the boundary condition~\Cref{eq:modelB_pressure_BC},
+the boundary condition defined in~\Cref{eq:modelB_pressure_BC},
 and is therefore moved to the right-hand side of the weak form.
@@
     \mathcal{B}(\uu, q) &= -\intO{q\nabla\cdot\uu}, \label{eq:stokes_skew_form}\\
-    \mathcal{L}(\vv) &= \intGc{\btau\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}.
-    \label{eq:stokes_linear_form}
+    \mathcal{L}(\vv) &= \intGc{\btau\cdot\vv} + \intGp{\Tilde{p}(t)(\vv\cdot\nn)}.\label{eq:stokes_linear_form}
 \end{align}
@@
 \subsection{Discretization of the Stokes equations}
-We will outline the discretization of the weak
-formulation~\Cref{eq:abstract_weak_form_modelC,
-eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}
-of the Stokes equations for the baseline model. A similar approach can
-be used to discretize the weak formulation for the other model versions.
+We outline the discretization of the weak
+formulation of the Stokes equations for the baseline model 
+(both cilia traction and cardiac pressure pulsations present) given by
+\Cref{eq:abstract_weak_form_modelC,eq:stokes_bilinear_form,eq:stokes_skew_form,eq:stokes_linear_form}.
+A similar approach can be used to discretize the weak formulation
+for the other model versions.
 First, we consider the spatial discretization of the weak formulation.
@@
 the mesh is ensured through stabilization
-of the discrete weak form~\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}.
+of the discrete weak form defined by \Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}.
 We apply the stabilization outlined in Hong~\emph{et al.}~\cite{Hong2016AEquations}.
@@
 \end{align*}
-to the discrete weak formulation~\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC},
+to the discrete weak formulation (\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}),
 where $\mathcal{F}$ is the set of all interior facets of the computational mesh.
@@
 across interior facets, where the penalty parameter $\gamma>0$ must be chosen large enough
-to achieve stability. The penalization term
-scales with the average of the cell diameter of neighboring mesh cells,
-with $h$ defined as the maximal distance between two points in a cell. The other two terms
+to achieve stability. For appropriate convergence, the penalization term
+includes a scaling with the average of the cell diameter of neighboring mesh cells,
+with $h$ defined as the maximal distance between two points in a cell~\cite{Nitsche1971UberSind}.
+The other two terms
 of $\mathcal{A}_{\mathrm{stab}}$ are added to ensure consistency and symmetry of
@@
 \end{subequations}%
-We solved~\Cref{eq:abstract_semi_discrete_weak_form_modelC}
-numerically with the penalty parameter $\gamma=10$.
-
-In time, we discretize the weak formulation~\Cref{eq:abstract_semi_discrete_weak_form_modelC}
+
+In time, we discretize the weak formulation (\Cref{eq:abstract_semi_discrete_weak_form_modelC})
 with the implicit Euler method, approximating the time derivative as
@@
 The method is implicit and of first order in time~\cite{butcher2016numerical}. 
+The fully discrete Stokes equations were solved with the penalty parameter $\gamma=10$.
 
@@
 
-\textbf{Only-cilia/no-cardiac model.} We consider $\Omega$ to be
+\textbf{Cilia-driven/no-cardiac model.} We consider $\Omega$ to be
 a closed domain with impermeable walls, so that the whole boundary
@@
 By imposing $\JJ\cdot\nn=0$ on $\Gamma=\Gnf$, 
-the weak form~\Cref{eq:adv_diff_weak_formA1} is reduced to
+the weak form defined by \Cref{eq:adv_diff_weak_formA1} is reduced to
 \begin{equation*}
@@
 
-\textbf{Only-cardiac/no-cilia model.} When using the normal pressure
-boundary condition~\Cref{eq:modelB_pressure_BC} to model pulsatile flow,
+\textbf{Cardiac-induced/no-cilia model.} When using the normal pressure
+boundary condition (\Cref{eq:modelB_pressure_BC}) to model pulsatile flow,
 we have in- and outflow of cerebrospinal fluid and thus advection of
@@
 \end{equation}
-In this work, we solved~\Cref{eq:discrete_weak_form_adv_diff} numerically
-with the penalty parameter value $\alpha=25$.
 
@@
 in~\Cref{eq:discrete_weak_form_adv_diff} are evaluated at timestep $n+1$.
-The method is implicit and of second order in time.
+The method is implicit and of second order in time. We solved the fully
+discrete weak formulation of the advection-diffusion equation
+with the penalty parameter value $\alpha=50$.
 
@@
 where $\Gamma=\partial\Omega$ is the boundary of the domain.
-Since the velocity field~\Cref{eq:velocity_mms} is divergence free by construction,
+Since the velocity field defined by~\Cref{eq:velocity_mms} is divergence free by construction,
 $g = 0$. Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$
@@
 implementation was millimeters, which is why~\Cref{tab:ventricles_norms_BDM}
-reports units in millimeters, instead of micrometers which has been used elsewhere in the paper. 
+reports values in units of millimeters, instead of micrometers which has been used elsewhere in the paper. 
 \begin{table}[!htbp]

### 2025-03-27 paper/main.tex
fix ref

@@
 included inside the parentheses on the left-hand side of~\Cref{eq:modelB_pressure_BC}
-for it to be the traction $\bsig$. Since this is not the case,
-we rather refer to this boundary condition as a normal pressure boundary condition.
+for the expression to be the stress tensor $\bsig$, thus the left-hand side of
+\Cref{eq:modelB_pressure_BC} does not constitute the normal traction $\bsigperp$.
+Because of this, we rather refer to this boundary condition
+as a normal pressure boundary condition.
 The boundary $\Gs$ is handled as discussed in the previous section,

### 2025-03-27 paper/main.tex
clean

@@
 \title{\textbf{Advection versus diffusion in brain intraventricular transport}}
-%
-%
-% Author: Please give full first and last names for authors and
-% include * after the name of all corresponding authors
 
@@
 \begin{document}
+
 \maketitle
 
-% Abstract should be written in the present tense and impersonal style (i.e., avoid we), and be at most 200 words long
 \begin{abstract}
@@
 
-% Keywords: Please provide a minimum of three and a maximum of seven keywords, separated by commas
 \noindent\small\hspace{.8725cm}\textbf{Keywords} cerebrospinal fluid, brain ventricles, cilia, transport, finite elements
@@
 
-%%--------------RESULTS--------------%%
 \section{Results}
@@
 analyzed.  To increase the signal-to-noise ratio, the images were
-downsampled by a block average using a resampling factor of 6. % (using the MATLAB function blockproc).
+downsampled by a block average using a resampling factor of 6. 
 The change in fluorescence intensity
@@
 zero to one. Finally, we averaged the $\Delta F$ data from controls and from mutants.
-%We report these mean values together with a one-standard deviation error band.
 
 \subsection{Intraventricular injection of microbeads and particle tracking}
-%To recover the flow fields shown in~\Crefpanels{fig:fig1}{b, c},
-
-We also carried out
-particle tracking in a larval zebrafish injected with fluorescent beads, as described in previous work~\cite{Olstad2019CiliaryDevelopment}.
+We carried out particle tracking in a larval zebrafish injected with fluorescent beads,
+as described in previous work~\cite{Olstad2019CiliaryDevelopment}.
 Anesthetized 2 dpf zebrafish were injected with 1 nl of a mixture containing 0.1\% w/v fluorescent beads
@@
 
-%% comparing these experimental velocity values
-%% with the simulated, maximum velocity magnitude.
-
-%% Both $\rr$ and the value $\tau=0.65$ mPa were chosen by 
-%% calibration against experimentally measured flow speeds~\cite{Olstad2019CiliaryDevelopment}.
-
 \subsubsection{Flow induced by cardiac pulsations}
@@
 with the relatively large $R=150$ nm~\cite{Moghassemi2024ExtracellularDecade}.
-%Hence this radius covers the slowest diffusing exosomes,
-%a choice made because smaller exosomes would have diffusion coefficients
-%similar to the other molecules we consider.
 For STM-GFP, we estimate the diffusion coefficient by extrapolating
@@
 are $D_1$ (extracellular vesicles), $D_2$ (STM-GFP) and $D_3$ (Dendra2) as given by \Cref{tab:diff_coeff_table}.
-
-%Implicit in this approach is the assumption that the proteins all have the same density.
 
@@
 
-%-----DISCRETIZATION AND MODEL IMPLEMENTATION-----%
 \subsection{Numerical approximation of the Stokes equations}
@@
 
-%%------PHYSICAL EXPERIMENTS------%%
-%\section{Experimental Methods}
-
 % Acknowledgements
@@
 
+% Data Availability Statement
 \medskip
@@
 
+% Conflic of Interest Disclosure
 \medskip
@@
 
-%\medskip
-%\textbf{Supporting Information} \par %Please delete the Suppporting Information statement
-%if it is not applicable. Please supply Supporting Information in another file.
-%Supporting information should not be provided in .tex format
-%Supporting Information is available from the Wiley Online Library or from the author.
-
-% References
-%\medskip
-
-% Use the following code if you wish to generate your bibliography with BibTeX;
-% replace the string "MSP-template" below with the name(s) of
-% the BibTeX data base(s) you want to use.
-% The resulting bibliography-output (the content of the .bbl file)
-% must be pasted back into this file before submission.
-% Please also include your BibTeX data base file(s) in your submission
-% so that we can re-run BibTeX if necessary.
-%
+% Bibliography
 \bibliographystyle{MSP}

### 2025-03-28 paper/main.tex
update fig4 and corresponding numbers

@@
 mutant scenarios was even greater for the simulations, with the
-times-to-threshold in ROI 2 and 4 being 90\% and 34\% higher in the
+times-to-threshold in ROI 2 and 4 being 81\% and 28\% higher in the
 absence of cilia-mediated flow. Moreover, the ROI 5 $\cbar$ profiles
@@
     \begin{align}
-        -\nabla\cdot\bsig &= \ff \qquad\mathrm{in \ }\Omega,\\
+        -\nabla\cdot\bsig &= \bm{f} \qquad\mathrm{in \ }\Omega,\\
         \nabla\cdot\uu &= g \qquad\mathrm{in \ }\Omega,
@@
 Since the velocity field defined by~\Cref{eq:velocity_mms} is divergence free by construction,
-$g = 0$. Setting the external force $\ff=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$
+$g = 0$. Setting the external force $\bm{f}=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$
 using~\Cref{eq:velocity_mms} and~\Cref{eq:pressure_mms},
@@
 with the velocity and pressure expressions defined in~\Cref{subsec:mms}
-for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated $\mathbf{L}^2$
-error norms and $\mathbf{H}^1$ error semi-norms for $\uu_h$,
-and $L^2$ error norms for $p_h$~(\Cref{tab:cylinder_error_rates}).
-Based on the error norm calculations,
+for $\uu_{\mathrm{ex}}$ and $p_{\mathrm{ex}}$, we calculated the error of 
+the velocity approximation $\uu_h$
+in the $\mathbf{L}^2$ norm and $\mathbf{H}^1$ semi-norm,
+and the error of the pressure approximation $p_h$ in the $L^2$ norm (\Cref{tab:cylinder_error_rates}).
+Based on the error calculations,
 we calculated the experimental order of convergence,
@@
 we report the error in calculation of the maximum velocities, and observe
-convergence in this error as well. Finally, we calculated the $L^2$ norms of
+convergence in this error as well. Finally, we calculated the $L^2$ norm of
 the divergence $\nabla\cdot\uu_h$ to verify the property of mass conservation.
@@
     and the error in the maximum velocity magnitude $\uu_{h, {\mathrm{mag}}}$
-    for mesh refinement on a cylinder mesh with the only-cilia/no-cardiac flow model.
+    for mesh refinement on a cylinder mesh with the cilia-driven/no-cardiac flow model.
     Additionally, we report the $L^2$ norm of the divergence of the velocity.
@@
 $\overline{u}_x$ and $\overline{u}_y$,
-respectively. We used the only-cardiac/no-cilia flow model to tune the
+respectively. We used the cardiac-induced/no-cilia flow model to tune the
 pressure boundary condition

### 2025-03-28 src/plot_compare_simulations_models.py
clean template

@@ -105,8 +105,8 @@ for idx, tag in enumerate(ROI_tags):
     ca_c.plot(t_hatsB[idx], c_threshold, marker='s', label='Cardiac', markersize=msize_c_plot, color=colors[1])
 
     # Add textbox with times to threshold
-    textstr = r'${\hat{t}}_0$'+f'= {t_hatsC[idx]:.1f} s\n' + \
-              r'${\hat{t}}_{\rm{II}}$'+f'= {t_hatsB[idx]:.1f} s'  
+    textstr = r'${\hat{t}}_0$'+f'= {t_hatsC[idx]:.0f} s\n' + \
+              r'${\hat{t}}_{\rm{II}}$'+f'= {t_hatsB[idx]:.0f} s' 
     props = dict(boxstyle='square', facecolor='white', alpha=0.5)
     ca_c.text(0.05, 0.90, textstr, transform=ca_c.transAxes, fontsize=27, verticalalignment='top', bbox=props)
     

### 2025-03-28 paper/main.tex
minor update BDM-DG

@@
 associated with integral moments of vector components normal to facets of the mesh.
-Because $\VV_h\not\subset\VV$, the elements are non-conforming.
-This BDM-DG scheme for the Stokes equations
-is $\mathbf{H}(\mathrm{div})$ conforming and thus exactly mass-conserving,
-because the continuity equation can be satisfied
-in every computational mesh cell due to the fact that $\nabla\cdot\VV_h\subset Q_h$.
+Because $\VV_h\not\subset\VV$, this BDM-DG scheme yields a non-conforming
+method for the Stokes equations. The scheme is
+$\mathbf{H}(\mathrm{div})$-conforming and exactly mass-conserving:
+due to the fact that $\nabla\cdot\VV_h\subset Q_h$,
+the continuity equation (\Cref{eq:BDM_stokes_div})
+is satisfied in every computational mesh cell.
 Moreover, control of normal components of $\uu_h$ conveniently 
 lets us enforce the impermeability condition $\uu_h\cdot\nn=0$ strongly.
-requires a stabilization of the bilinear form $\mathcal{A}(\uu_h, \vv_h)$.
-
-Because the elements of $\VV_h$ define the normal components of $\uu_h$,
+
+Because the elements of $\VV_h$ only define the normal components of $\uu_h$,
 continuity in tangential components of $\uu_h$ on interior facets of
 the mesh is ensured through stabilization
-of the discrete weak form defined by \Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}.
+of the discrete weak form (\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}).
 We apply the stabilization outlined in Hong~\emph{et al.}~\cite{Hong2016AEquations}.

### 2025-03-28 src/simulate_flow.py

@@ -57,7 +57,7 @@ class FlowSolver:
     rho_val = 1e-3  # Fluid density [g / mm^3]
 
     # Model parameters
-    tau  = 6.5e-4 # Tangential stress BC parameter [Pa]
+    tau  = 6.5e-4 # Tangential traction force density [Pa]
     freq = 2.22   # Cardiac frequency [Hz]
     A_pressure = 0.0015 # Pressure BC amplitude [Pa]
 

### 2025-03-28 paper/main.tex
minor revisions

@@
 \end{subequations}%
-
 In time, we discretize the weak formulation (\Cref{eq:abstract_semi_discrete_weak_form_modelC})
@@
 \end{equation*}
-The final discrete weak formulation of the advection-diffusion equation is:
+
+By including the stabilization $a_{\mathrm{stab}}(c_h, \phi_h)$,
+the final semi-discrete weak formulation of the advection-diffusion equation is:
 find $c_h\in W_h$, such that
@@
 \end{equation}
-
 In time, we discretized~\Cref{eq:discrete_weak_form_adv_diff} with the

### 2025-03-28 paper/main.tex
update tau definition in mms code, clean ref.bib

@@
 (CSF)~\cite{fame2020emergence}. Produced mostly by the choroid
-plexus and partly by brain interstitial fluid~\cite{Brodal2016},
+plexus and partly by brain interstitial fluid,
 CSF is a clear liquid that flows through the ventricular system and subarachnoid
-space~\cite{Damkier2013}. By transporting growth factors, nutrients, neurotransmitters
+space~\cite{Brodal2016, Damkier2013}. By transporting growth factors, nutrients, neurotransmitters
 and metabolites, as well as removing waste products, CSF regulates
@@
 
-The tangential traction $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represents the cilia
-motion differ for the cilia regions. We heuristically determined the constant $\tau= 0.65$ mPa
+For the tangential traction $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ that represents the cilia
+motion, we heuristically determined the constant $\tau= 0.65$ mPa
 and the spatially varying function $\lambda(\xx)$. The definitions of $\rr$ and $\lambda(\xx)$
@@
     \centering
-    \caption{Error norms of the velocity $\uu_h$ in the
+    \caption{Errors of the velocity approximation $\uu_h$ in the
     $\mathbf{L}^2$ and $\mathbf{H}^1$ norms,
@@
     and the error in the maximum velocity magnitude $\uu_{h, {\mathrm{mag}}}$
-    for mesh refinement on a cylinder mesh with the cilia-driven/no-cardiac flow model.
+    for mesh refinement on a cylinder mesh with the cilia-driven/no-cardiac flow model,
+    with $\mu=1$.
     Additionally, we report the $L^2$ norm of the divergence of the velocity.

### 2025-03-28 src/simulate_flow.py

@@ -296,10 +296,10 @@ class FlowSolver:
         tau_vec_anterior2 = tau_vec # Anterior cilia lambda expression (posterior part)
 
         # Use the tau expressions to define the tangent traction vectors
-        self.tangent_traction_dorsal    = lambda n: Tangent(tau_vec_dorsal, n)
-        self.tangent_traction_ventral   = lambda n: Tangent(tau_vec_ventral, n)
-        self.tangent_traction_anterior1 = lambda n: Tangent(tau_vec_anterior1, n)
-        self.tangent_traction_anterior2 = lambda n: Tangent(tau_vec_anterior2, n)
+        self.tangent_traction_dorsal    = Tangent(tau_vec_dorsal, n)
+        self.tangent_traction_ventral   = Tangent(tau_vec_ventral, n)
+        self.tangent_traction_anterior1 = Tangent(tau_vec_anterior1, n)
+        self.tangent_traction_anterior2 = Tangent(tau_vec_anterior2, n)
 
         #------------BILINEAR FORM------------#
         a  = 0 # Initialize
@@ -322,12 +322,12 @@ class FlowSolver:
         if self.model_version == "A": # Only cilia forces
             # Add tangential traction
             if self.cilia_scenario!=1:
-                L += -inner(Tangent(v, n), self.tangent_traction_anterior1(n)) * ds(ANTERIOR_CILIA1)
-                L +=  inner(Tangent(v, n), self.tangent_traction_anterior2(n)) * ds(ANTERIOR_CILIA2)
+                L += -inner(Tangent(v, n), self.tangent_traction_anterior1) * ds(ANTERIOR_CILIA1)
+                L +=  inner(Tangent(v, n), self.tangent_traction_anterior2) * ds(ANTERIOR_CILIA2)
             if self.cilia_scenario!=2:
-                L += -inner(Tangent(v, n), self.tangent_traction_dorsal(n)) * ds(MIDDLE_DORSAL_CILIA)
+                L += -inner(Tangent(v, n), self.tangent_traction_dorsal) * ds(MIDDLE_DORSAL_CILIA)
             if self.cilia_scenario!=3:
-                L +=  inner(Tangent(v, n), self.tangent_traction_ventral(n)) * ds(MIDDLE_VENTRAL_CILIA)
+                L +=  inner(Tangent(v, n), self.tangent_traction_ventral) * ds(MIDDLE_VENTRAL_CILIA)
         elif self.model_version=="B": # Only pulsatile cardiac motion
             # Add time-derivative term
[…]

### 2025-03-28 src/simulate_mms_verification.py

@@ -7,6 +7,8 @@ from ufl       import div, dot, inner, sym, grad, avg, curl
 from mpi4py    import MPI
 from petsc4py  import PETSc
 from basix.ufl import element, mixed_element
+from utilities.mesh    import mark_facets
+from utilities.helpers import calc_error_H1, calc_error_L2, calc_error_Hdiv
 from dolfinx.fem.petsc import assemble_matrix, assemble_vector, set_bc, apply_lifting
 
 print = PETSc.Sys.Print
@@ -146,18 +148,20 @@ def get_system_mms(msh: dfx.mesh.Mesh, penalty_val: float, mu_val: float, direct
     return A, b, W, B, u_ex, p_ex
 
 # Mesh tags for flow
-ANTERIOR_PRESSURE    = 2
-POSTERIOR_PRESSURE   = 3
-VOLUME               = 4
-MIDDLE_VENTRAL_CILIA = 5
-MIDDLE_DORSAL_CILIA  = 6
-ANTERIOR_CILIA       = 7
-SLIP                 = 8
+ANTERIOR_PRESSURE    = 2 # The pressure BC facets on the anterior ventricle boundary
+POSTERIOR_PRESSURE   = 3 # The pressure BC facets on the posterior ventricle boundary
+MIDDLE_VENTRAL_CILIA = 5 # The cilia BC facets on the ventral wall of the middle ventricle
+MIDDLE_DORSAL_CILIA  = 6 # The cilia BC facets on the dorsal wall of the middle ventricle
+ANTERIOR_CILIA1      = 7 # The cilia BC facets on the dorsal, anterior walls of the anterior ventricle
+ANTERIOR_CILIA2      = 8 # The cilia BC facets on the dorsal, posterior walls of the anterior ventricle
+SLIP                 = 9 # The free-slip facets of the boundary
+
+impermeability_tags = (MIDDLE_DORSAL_CILIA, MIDDLE_VENTRAL_CILIA,
+                       ANTERIOR_CILIA1, ANTERIOR_CILIA2, SLIP)
 
 def get_system(msh: dfx.mesh.Mesh, penalty_val: float, mu_val: float, direct: bool):
 
-    from utilities.mesh import mark_boundaries_flow
-    bdry_facets = mark_boundaries_flow(mesh=msh, inflow_outflow=False)
+    bdry_facets = mark_facets(mesh=msh, inflow_outflow=False)
     k  = 1
     cell = msh.basix_cell()
     Velm = element("BDM", cell, k)
[…]

### 2025-04-01 paper/main.tex
title update
update values verification tables, update title

@@
 
-\title{\textbf{Advection versus diffusion in brain intraventricular transport}}
+\title{\Large\textbf{Advection versus diffusion in brain ventricular transport}}
 
@@
 For the discretized advection-diffusion equation, we use a flexible GMRES solver
-with block Jacobi preconditioning for the outer solves
-and ILU preconditioning for the inner solves
-\cite{fgmres, Jacobi1845UeberGleichungen, chan1997approximate}. 
+with block Jacobi preconditioning \cite{fgmres, Jacobi1845UeberGleichungen}. 
 We discretize the time-dependent diffusion equation (without advection)
@@
 \begin{table}[!htbp]
-    \small
+    \footnotesize
     \centering
-    \caption{Errors of the velocity approximation $\uu_h$ in the
-    $\mathbf{L}^2$ and $\mathbf{H}^1$ norms,
-    the pressure $p_h$ in the $L^2$ norm,
-    and the error in the maximum velocity magnitude $\uu_{h, {\mathrm{mag}}}$
-    for mesh refinement on a cylinder mesh with the cilia-driven/no-cardiac flow model,
-    with $\mu=1$.
-    Additionally, we report the $L^2$ norm of the divergence of the velocity.
+    \caption{Error norms for the convergence study
+    performed with a cylinder mesh with
+    the cilia-driven/no-cardiac flow model using $\mu=1$.
     For all error norms, convergence rates calculated
     with~\Cref{eq:convergence_order_estimate} are given
-    in parentheses.}\label{tab:cylinder_error_rates}
+    in parentheses. The coarsest mesh had a mesh size $h_0$,
+    and for every mesh refinement the mesh size $h$ was halved.}\label{tab:cylinder_error_rates}
     \begin{tabular}{cc|ccccc}
@@
         & $\normltwo{p_h - p_{\mathrm{ex}}}$
-        & $\normlinf{u_h} -\normlinf{u_{\mathrm{ex}}}$
+        & $\vert\normlinf{u_h} - \normlinf{u_{\mathrm{ex}}}\vert$
         & $\normltwo{\nabla\cdot\uu_h}$\\ 
         \midrule 
-        1    & 8652    & \num{2.3e-02}  (--)  & \num{4.3e-01}   (--)  & \num{5.4e-01}  (--) 
-        & \num{2.4e-02} (---) & \num{1.4e-07} \\
-
-        1/2  & 41190   & \num{9.3e-03} (1.30) & \num{2.8e-01}  (0.61) & \num{3.7e-01} (0.53)
-        & \num{5.0e-03} (2.25) & \num{2.8e-08} \\
-
-        1/4  & 255016  & \num{3.5e-03} (1.42) & \num{1.4e-01}  (1.00) & \num{2.1e-01} (0.79)
-        & \num{1.4e-03} (1.83) & \num{7.3e-11} \\
-
-        1/8  & 1855337 & \num{1.3e-03} (1.46) & \num{6.9e-02}  (1.03) & \num{1.1e-01} (0.94)
-        & \num{6.7e-04} (1.08) & \num{1.4e-10} \\   
+        1    & 8652    & \num{2.3e-02}  (--)  & \num{4.3e-01}   (--)  & \num{5.6e-01}  (--)  & \num{2.4e-02}  (--)  & \num{1.4e-07} \\  
+        1/2  & 41190   & \num{9.3e-03} (1.30) & \num{2.8e-01}  (0.61) & \num{3.9e-01} (0.53) & \num{5.0e-03} (2.25) & \num{2.8e-08} \\  
+        1/4  & 255016  & \num{3.5e-03} (1.42) & \num{1.4e-01}  (1.00) & \num{2.1e-01} (0.85) & \num{1.4e-03} (1.83) & \num{7.3e-11} \\     
+        1/8  & 1855337 & \num{1.3e-03} (1.46) & \num{6.9e-02}  (1.03) & \num{1.1e-01} (0.92) & \num{6.7e-04} (1.08) & \num{1.5e-10} \\   
         \bottomrule
@@
 refined on the mesh used for the convergence study.
-For the cilia traction vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$ introduced in~\Cref{subsec:appendixA1},
-we set a constant $\tau = 6.5\times 10^{-4}$ Pa and
-$\lambda(\xx)=1$ in the numerical experiments.
-We set $\rr = (1, 0, 1)$ in the ventral middle ventricle cilia region
-and $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and the anterior ventricle cilia
-regions. We used $\gamma=10$ for the BDM penalty parameter.
+In the numerical experiments, we used the cilia
+traction vector $\btau = \tau\lambda(\xx) P_{\nn}(\rr)$
+defined in~\Cref{tab:r_vector_and_lambda_function}
+and $\gamma=10$ for the BDM penalty parameter.
 
 For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$.
-We also report $\normlinf{u_h}$ scaled by the area $|\Gc|=\intGc{}$ of the cilia
-boundary $\Gc$ over which tangential traction
-$\btau$ was applied. We chose this measure using $|\Gc|$ as a scale because the regions
+We also report $\normlinf{u_h}$ scaled by the total force $F=\intGc{\sqrt{\btau\cdot \btau}}$
+applied on the cilia boundary $\Gc$. We chose this measure using $F$ as a scale because the regions
 of the mesh marked as cilia-populated change slightly with every mesh refinement,
@@
 These changes in the surface area over which the tangential traction is applied
-result in changes to the maximum velocity magnitude,
+result in changes to $\normlinf{u_h}$,
 since the maximum velocity magnitude is a result of the total amount of force
-$\intGc{\sqrt{\btau\cdot \btau}}$ applied on the cilia boundary.
+$F$ applied on the cilia boundary.
 
@@
     \centering
+    \small
     \caption{Velocity norms under mesh refinement
-    of the brain ventricles mesh using the cilia-driven/no-cardiac flow model
-    with $\btau = \tau \lambda(\xx)P_{\nn}(\rr)$, using
-    $\lambda(\xx)=1$,
-    $\tau = 6.5\times 10^{-4}$ Pa,
-    $\rr = (1, 0, 1)$ in the ventral middle ventricle and,
-    $\rr = -(1, 0, 1)$ in the dorsal middle ventricle and
-    the anterior ventricle.}\label{tab:ventricles_norms_BDM}
+    of the brain ventricles mesh using the cilia-driven/no-cardiac flow model.}
+    \label{tab:ventricles_norms_BDM}
     \begin{tabular}{cc|cccc}
@@
         $\normlinf{u_h}$ $\left[\frac{\mathrm{mm}}{\mathrm{s}}\right]$
-        & $\frac{1}{|\Gc|}\normlinf{u_h}$ $\left[\frac{1}{\mathrm{mm\cdot s}}\right]$
+        & $\frac{1}{F}\normlinf{u_h}$ $\left[\frac{1}{\mathrm{Pa\cdot mm\cdot s}}\right]$
         & $\frac{1}{\vert\Omega\vert}\normltwovec{\uu_h}$
@@
         \midrule 
-        132134  & 943820  & 0.0276 & 0.97 & \num{3.6e-03} & \num{6.3e-16}\\
-        180901  & 1289881 & 0.0284 & 0.98 & \num{3.7e-03} & \num{1.5e-13}\\
-        262598  & 1870703 & 0.0292 & 0.98 & \num{3.8e-03} & \num{6.2e-16}\\
-        395339  & 2811668 & 0.0292 & 0.96 & \num{3.8e-03} & \num{1.9e-14}\\
-        627439  & 4448761 & 0.0286 & 0.92 & \num{3.7e-03} & \num{4.6e-14}\\
+        132134  & 943820  & 0.026 & \num{3.8e3} & \num{2.2e-03} & \num{1.9e-16}\\
+        180901  & 1289881 & 0.027 & \num{3.7e3} & \num{2.2e-03} & \num{3.0e-16}\\
+        262598  & 1870703 & 0.027 & \num{3.7e3} & \num{2.3e-03} & \num{6.7e-16}\\
+        395339  & 2811668 & 0.028 & \num{3.6e3} & \num{2.2e-03} & \num{2.0e-14}\\
+        627439  & 4448761 & 0.027 & \num{3.5e3} & \num{2.2e-03} & \num{4.9e-14}\\
         \bottomrule

### 2025-04-02 paper/main.tex
Minor edits in abstract

@@
 provides mechanical support for the brain and the flow of CSF helps
-distribute nutrients, neurotransmitters and metabolites throughout
-the central nervous system. CSF flow is partly driven
-by beating of motile cilia, hair-like structures that line the ependymal cell layer
-of the walls of the brain ventricles. Despite the physiological importance of CSF flow,
-the underlying mechanisms of cilia-mediated flow and transport
-in the brain ventricles remain yet to be comprehensively resolved.
-In this study, the role of motile cilia in brain intraventricular CSF flow and transport
-is analyzed and evaluated. The geometry of the zebrafish larval brain ventricles,
-for which detailed knowledge of cilia properties and CSF motion velocities
-and frequencies exists, was used to develop finite element methods that model flow and transport.
-The computational model is validated by in vivo experiments that monitor transport
-of a photoconvertible protein secreted in the brain ventricles.
-The results show that while cilia contribute to advection of large particles,
-diffusion plays a significant role in the transport of small molecules such as proteins.
-It is also demonstrated that cilia location and the geometry of the ventricular system impact solute distribution.
-Altogether, this work presents a computational framework that can be applied to other
-ventricular systems, together with new concepts of how molecules are transported within the brain and its ventricles.
+distribute nutrients, neurotransmitters and metabolites throughout the
+central nervous system. CSF flow is partly driven by beating of motile
+cilia, hair-like structures that line the ependymal cell layer of the
+walls of the brain ventricles. Despite the physiological importance of
+CSF flow, the underlying mechanisms of cilia-mediated flow and
+transport in the brain ventricles remain yet to be comprehensively
+resolved. This study analyzes and evaluates the role of motile cilia
+in brain intraventricular CSF flow and transport. The geometry of the
+zebrafish larval brain ventricles, for which detailed knowledge of
+cilia properties and CSF motion velocities and frequencies exists, was
+used to develop finite element methods for modelling flow and
+transport. The computational model is validated by in-vivo experiments
+that monitor transport of a photoconvertible protein secreted in the
+brain ventricles. Our results show that while cilia contribute to
+advection of large particles, diffusion plays a significant role in
+the transport of small molecules \mer{such as proteins}. We also
+demonstrate how cilia location and the geometry of the ventricular
+system impact solute distribution. Altogether, this work presents a
+computational framework that can be applied to other ventricular
+systems, together with new concepts of how molecules are transported
+within the brain and its ventricles.
 

### 2025-04-02 paper/main.tex
Updates in intro

@@
 cilia, CSF secretion by the choroid plexus, and pulsatile pressure gradients generated by the
-cardiac cycle, the respiration, neural activity, and bodily
+cardiac cycle, respiration, neural activity, and \mer{bodily}
 movements~\cite{Brodal2016, del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
@@
 biological organisms and in several human organs,
-of which the brain is one of them~\cite{DGama2025MotileBrain,
+including the brain~\cite{DGama2025MotileBrain,
 Fulford1986Muco-ciliaryLung,
@@
 
+% MER: Note, we do not write "endeavors" nor "delve". (GenAI does.)
+
+% MER: Note "Failed to identify" indicates that someone tried but
+% failed. It is a very effective way of pissing said authors (often
+% reviewers or potential future collaborators) off if they just didn't
+% try/that was not their target.
+
 % I3: What do we not know about the problem and what do we want to
@@
 the overall fluid flow and solute transport within the brain.
-Experimental endeavors are challenging to pursue due to
-technical limitations: the microscopic size and relatively 
+Experimental approaches face technical challenges: the microscopic size and relatively 
 high beating frequencies of the cilia~\cite{ocallaghan2012analysis, mahuzier2018ependymal,
@@
 ventricles~\cite{Faubel2016Cilia-basedVentricles, Sawamoto2006NewBrain, ibanez2003beat};
-however, they failed to identify the role of other contributions to CSF
+however, they \mer{did not study} the role of other contributions to CSF
 flow and the accompanying transport, such as pressure
@@
 These technical limitations of studying cilia-mediated flow and transport make 
-mathematical modeling and computational investigations an attractive alternative to experimental
-studies. Numerous previous simulation studies have focused on modeling the interaction
+mathematical modeling and computational investigations an attractive complement to experimental
+studies. Previous simulation studies have focused on modeling the interaction
 between single or several cilia and surrounding
@@
 Olstad2019CiliaryDevelopment, Ringers2020Role, DGama2021Diversity, jurisch2020radial}. 
-The computational model is validated with experimental data by monitoring in vivo
+The computational model is validated against experimental data by monitoring in vivo
 the dynamics of a photoconvertible fluorescent protein Dendra2

### 2025-04-02 paper/main.tex
Update abstract intro w/HH

@@
 advection of large particles, diffusion plays a significant role in
-the transport of small molecules \mer{such as proteins}. We also
-demonstrate how cilia location and the geometry of the ventricular
-system impact solute distribution. Altogether, this work presents a
-computational framework that can be applied to other ventricular
-systems, together with new concepts of how molecules are transported
-within the brain and its ventricles.
+the transport of small solutes. We also demonstrate how cilia location
+and the geometry of the ventricular system impact solute
+distribution. Altogether, this work presents a computational framework
+that can be applied to other ventricular systems, together with new
+concepts of how molecules are transported within the brain and its
+ventricles.
 
@@
 physiological processes, including via the beating motion of motile
-cilia, CSF secretion by the choroid plexus, and pulsatile pressure gradients generated by the
-cardiac cycle, respiration, neural activity, and \mer{bodily}
-movements~\cite{Brodal2016, del2010ependymal, Ringers2020Role, Vinje2019RespiratoryMeasurements,
+cilia, CSF secretion by the choroid plexus, and pulsatile pressure
+gradients generated by the cardiac cycle, respiration, neural
+activity, and body movements~\cite{Brodal2016, del2010ependymal,
+  Ringers2020Role, Vinje2019RespiratoryMeasurements,
   Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment,
-macaulay2022cerebrospinal, mestre2018flow}.
-Cilia are hair-like structures found in a vast diversity of
-biological organisms and in several human organs,
-including the brain~\cite{DGama2025MotileBrain,
-Fulford1986Muco-ciliaryLung,
-Pacherres2022CiliaryProduction, Jahn1972LocomotionProtozoa,
-Brennen1977FluidFlagella, Ringers2020Role, spassky2013motile,
-Pellicciotta2020Cilia, mitchell2007evolution,
-Tsukita2012CoordinatedFeet, BLAKE1974MechanicsMotion,
-Reiten2017Motile-Cilia-MediatedComputations, Thouvenin2020OriginCanal}. 
-The ventricular surface of the brain, known as the ependyma, is lined by
-motile cilia that beat in a coordinated pattern at frequencies of
-10--40 Hz to mediate fluid flow~\cite{mitchell2007evolution,
-Ringers2020Role, spassky2013motile, Ringers2023NovelEpithelia, roth2025structure}. 
-Given their microscopic size, ranging from
-5 to 15 microns, cilia contribute primarily to flow near the
-ependyma in the human brain~\cite{Siyahhan2014FlowVentricles, Olstad2019CiliaryDevelopment,
-Ringers2020Role, Faubel2016Cilia-basedVentricles}. In contrast, cardiac,
-respiratory and delta waves at lower frequencies induce pulsatile flow
-at the larger scales in the brain ventricular system, subarachnoid space, and
-subarachnoid perivascular
+  macaulay2022cerebrospinal, mestre2018flow}.  Cilia are hair-like
+structures found in a vast diversity of biological organisms and in
+several human organs, including the brain~\cite{DGama2025MotileBrain,
+  Fulford1986Muco-ciliaryLung, Pacherres2022CiliaryProduction,
+  Jahn1972LocomotionProtozoa, Brennen1977FluidFlagella,
+  Ringers2020Role, spassky2013motile, Pellicciotta2020Cilia,
+  mitchell2007evolution, Tsukita2012CoordinatedFeet,
+  BLAKE1974MechanicsMotion,
+  Reiten2017Motile-Cilia-MediatedComputations,
+  Thouvenin2020OriginCanal}.  The ventricular surface of the brain,
+known as the ependyma, is lined by motile cilia that beat in a
+coordinated pattern at frequencies of 10--40 Hz to mediate fluid
+flow~\cite{mitchell2007evolution, Ringers2020Role, spassky2013motile,
+  Ringers2023NovelEpithelia, roth2025structure}.  Given their
+microscopic size, ranging from 5 to 15 microns, cilia contribute
+primarily to flow near the ependyma in the human
+brain~\cite{Siyahhan2014FlowVentricles, Olstad2019CiliaryDevelopment,
+  Ringers2020Role, Faubel2016Cilia-basedVentricles}. In contrast,
+cardiac, respiratory and delta waves at lower frequencies induce
+pulsatile flow at the larger scales in the brain ventricular system,
+subarachnoid space, and subarachnoid perivascular
 spaces~\cite{Vinje2019RespiratoryMeasurements, eide2024functional,
-Causemann2025, fultz2019coupled, mestre2018flow, daversin2020mechanisms}.
-
-% MER: Note, we do not write "endeavors" nor "delve". (GenAI does.)
-
-% MER: Note "Failed to identify" indicates that someone tried but
-% failed. It is a very effective way of pissing said authors (often
-% reviewers or potential future collaborators) off if they just didn't
-% try/that was not their target.
+  Causemann2025, fultz2019coupled, mestre2018flow,
+  daversin2020mechanisms}.
 
@@
 ventricles~\cite{Faubel2016Cilia-basedVentricles, Sawamoto2006NewBrain, ibanez2003beat};
-however, they \mer{did not study} the role of other contributions to CSF
+however, they did not study the role of other contributions to CSF
 flow and the accompanying transport, such as pressure

### 2025-04-02 paper/main.tex
Updates in Results 4

@@
 
-Ciliary motion is integral to physiological CSF flow,
-and absence of cilia has been associated with defective
-brain development and various pathologies~\cite{Eichele2020Cilia-drivenVentricle,
+Ciliary motion is integral to physiological CSF flow, and absence of
+cilia has been associated with defective brain development and various
+pathologies~\cite{Eichele2020Cilia-drivenVentricle,
   Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles,
@@
   Sawamoto2006NewBrain, Yoshiba2014RolesSymmetry,
-Hirokawa2006NodalAsymmetry}.
-As observed both experimentally and computationally,
-absence of motile cilia alters CSF flow patterns. 
-We next investigate the implications of these changes on intraventricular
-transport.
-
-We experimentally measured the movement of proteins by monitoring
-photoconverted Dendra2 signal in control zebrafish and 
-motile-cilia mutant \emph{schmalhans} (\emph{smh}) zebrafish.
-In ROIs 2 and 4, which quantify Dendra2 distribution
-downstream of the photoconversion site, we observed a slower increase
-of fluorescence intensity (\Crefpanels{fig:fig4}{a}). The mean times-to-threshold
-in the \emph{smh} mutants were $45\%$ (ROI 2) and $25\%$ (ROI 4) higher
-compared to controls (\Crefpanels{fig:fig4}{b}). We found no significant differences
-between \emph{smh} mutants and controls
-in the Dendra2 distribution in ROIs 3, 5, and 6.
-
-The \emph{smh} mutants are mimicked in the computational model by
+  Hirokawa2006NodalAsymmetry}.  As observed both experimentally and
+computationally, absence of motile cilia alters CSF flow patterns.  We
+next investigate the implications of these changes on intraventricular
+transport. We experimentally measured the movement of proteins by
+monitoring photoconverted Dendra2 signal in control zebrafish and
+motile-cilia mutant \emph{schmalhans} (\emph{smh}) zebrafish.  In ROIs
+2 and 4, which quantify Dendra2 distribution downstream of the
+photoconversion site, we observed a slower increase of fluorescence
+intensity (\Crefpanels{fig:fig4}{a}): the mean times-to-threshold in
+the \emph{smh} mutants were $45\%$ (ROI 2) and $25\%$ (ROI 4) higher
+compared to controls (\Crefpanels{fig:fig4}{b}). We found no
+significant differences between \emph{smh} mutants and controls in the
+Dendra2 distribution in ROIs 3, 5, and 6.
+
+In the computational model, we represent the \emph{smh} mutants by
 considering transport of Dendra2 with CSF flow driven by cardiac
@@
 noticeably delayed dynamics in ROIs 2, 4 and 5, but little change for
-ROIs 3 and 6 (\Crefpanels{fig:fig4}{c}).
-
-Compared to experimental data, the difference between the control and
-mutant scenarios was even greater for the simulations, with the
-times-to-threshold in ROI 2 and 4 being 81\% and 28\% higher in the
-absence of cilia-mediated flow. Moreover, the ROI 5 $\cbar$ profiles
-for the two configurations in our computational model deviate,
-which is not the case in the experiments. Altogether,
-our findings identify that, for smaller proteins such as Dendra2,
-diffusion plays an important role for
-solute movement to regions upstream in the cilia-mediated flow fields or to
-distant ventricles, while cilia affect the downstream mean concentrations.
-
+ROIs 3 and 6 (\Crefpanels{fig:fig4}{c}). Compared to experimental
+data, the control and mutant scenarios differed more for the
+simulations, with the times-to-threshold in ROI 2 and 4 being 81\% and
+28\% higher in the absence of cilia-mediated flow. Moreover, the
+predicted mean concentrations in ROI 5 deviate between the two
+scenarios, which is not the case in the experiments. Altogether, our
+findings identify that, for smaller proteins such as Dendra2,
+diffusion plays an important role for solute movement to regions
+upstream in the cilia-mediated flow fields or to distant ventricles,
+while the cilia affect the downstream mean concentrations.
 \begin{figure}[H]

### 2025-04-02 paper/main.tex
Updates in Results 5

@@
 
-\subsection{Loss of cilia motility in specific subpopulation slows down transport}
-
-We previously characterized three distinct ciliated cell lineages in the
-zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain}.
-To identify the effects of these lineages on CSF flow and transport, 
-we investigate region-specific cilia paralysis with the computational model.
-Three cilia-covered regions were considered paralyzed separately:
-the anterior ventricle, and the dorsal and ventral parts
-of the middle ventricle (\Crefpanels{fig:fig5}{a}).
-To simulate cilia paralysis, the cilia tangential traction boundary condition
-is for each case changed to a free-slip boundary condition
-in the paralyzed region,
-prescribing zero tangential forces to
-represent absence of cilia motion.
-
-The CSF velocities are most strongly
-affected when removing cilia in the dorsal part of the middle ventricle,
-as the maximum velocity magnitude drops from 27.9 \textmu m/s to 7.9 \textmu m/s.
-In vivo, these dorsal cilia generate the strongest flow at
-this developmental stage of the fish~(\Crefpanels{fig:fig1}{c})~\cite{Olstad2019CiliaryDevelopment}.
-In contrast, removing cilia in the anterior ventricle or the ventral region of the middle
-ventricle has minimal impact, and results in maximum speeds
-of 27.9 \textmu m/s and 27.4 \textmu m/s, respectively.
-Of the total tangential forces exerted by the cilia, ventral cilia in the middle ventricle
-contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
-force~(\Crefpanels{fig:fig5}{b}). The magnitude of these force contributions are thus
-more similar than the difference in their impact on the maximum velocity magnitudes.
+\subsection{Regional loss of cilia motility delays transport}
+
+We previously characterized three distinct ciliated cell lineages in
+the zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment,
+  DGama2025MotileBrain}.  To identify the effects of these lineages on
+CSF flow and transport, we investigate region-specific cilia paralysis
+with the computational model.  Three cilia-covered regions were
+paralyzed separately: the anterior ventricle, and the dorsal and
+ventral parts of the middle ventricle (\Crefpanels{fig:fig5}{a}).  To
+simulate regional cilia paralysis, we remove the tangential traction exerted by
+the cilia in the respective region.
+%
+%% the cilia tangential traction boundary condition is for each case
+%% changed to a free-slip boundary condition in the paralyzed region,
+%% prescribing zero tangential forces to represent absence of cilia
+%% motion.
+%
+
+Removing cilia in the dorsal part of the middle ventricle has a strong
+effect on the CSF velocities: the maximum velocity magnitude drops
+from 27.9 \textmu m/s to 7.9 \textmu m/s. In vivo, these dorsal cilia
+generate the strongest flow at this developmental stage of the
+fish~(\Crefpanels{fig:fig1}{c})~\cite{Olstad2019CiliaryDevelopment}.
+In contrast, only removing cilia in the anterior ventricle or the
+ventral region of the middle ventricle has minimal impact, and results
+in maximum speeds of 27.9 \textmu m/s and 27.4 \textmu m/s,
+respectively.  We remark that out of the total tangential forces,
+ventral cilia in the middle ventricle contribute by 34\%, while the
+dorsal cilia exert 52\% of the total tangential
+force~(\Crefpanels{fig:fig5}{b}). \mer{Thus, the CSF velocities are
+  affected not only by the magnitude of the applied forces, but result
+  from a nontrivial interplay between force, directionality and
+  location.}
+%% The magnitude of these force
+%% contributions are thus more similar than the difference in their
+%% impact on the maximum velocity magnitudes.
+
+Turning to transport of Dendra2, we again note that removal of the
+dorsal cilia has the most pronounced effect. All mean concentration
+profiles (except ROI 1, where we impose the photoconversion curve)
+change noticeably (\Crefpanels{fig:fig5}{c}). Compared to the baseline
+model results, we observe less solute distribution in the middle and
+anterior ventricles (ROIs 2--5), and more rapid transport to the
+posterior ventricle (ROI 6). On the other hand, removal of anterior
+cilia does not alter the mean concentrations
+(\Crefpanels{fig:fig5}{c}). Finally, without ventral cilia in the
+middle ventricle, more solute spreads towards the anterior ventricle
+(ROI 5) and less solute spreads towards the posterior ventricle (ROI
+6).
 \begin{figure}[H]
@@
 \end{figure}
-
-Changes in the transport of Dendra2 are most prominent when removing the dorsal cilia
-in the middle ventricle. All mean concentration profiles 
-(except ROI 1, where we impose the photoconversion curve)
-exhibit changes (\Crefpanels{fig:fig5}{c}).
-Compared to the baseline model results, we observe less solute distribution
-in the middle and anterior ventricles (ROIs 2--5),
-and more rapid transport to the posterior ventricle (ROI 6).
-On the other hand, removal of anterior cilia does not alter the 
-mean concentrations (\Crefpanels{fig:fig5}{c}).
-Finally, without ventral cilia in the middle ventricle,
-more solute spreads towards the anterior ventricle (ROI 5) and
-less solute spreads towards the posterior ventricle (ROI 6).
 

### 2025-04-02 paper/main.tex
Updates in Results

@@
 \subsection{Modification of ventricular geometry impacts solute distribution}
-Variations in ventricular morphology impact CSF flow patterns~\cite{Olstad2019CiliaryDevelopment}.
-To assess how these variations influence solute distribution,
-we consider four alternative ventricular geometries:
-one where the duct connecting the anterior and middle ventricles is constricted
-(66 \% reduction in cross-sectional area);
-one where the duct connecting the middle and posterior ventricles is constricted
-(33 \% reduction);
-one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
-and the combination of the above three modifications (\Crefpanels{fig:fig6}{a, b}).
+Variations in ventricular morphology impact CSF flow
+patterns~\cite{Olstad2019CiliaryDevelopment}.  To assess how these
+variations influence solute distribution, we consider four alternative
+ventricular geometries: (i) constriction of the anterior-middle
+ventricular duct (66 \% reduction in cross-sectional area); (ii) constriction of the middle-posterior duct (33 \% reduction); (iii) middle ventricle shrunk in the lateral direction (43 \% reduction); and (iv) all three combined (\Crefpanels{fig:fig6}{a, b}).
+%
+%% one where the duct connecting the anterior and middle ventricles is constricted
+%% (66 \% reduction in cross-sectional area);
+%% one where the duct connecting the middle and posterior ventricles is constricted
+%% (33 \% reduction);
+%% one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
+%% and the combination of these three modifications (\Crefpanels{fig:fig6}{a, b}).
+%
+%
 In these four modified geometries, the total volume is reduced by
-3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively,
-compared to the original geometry.
-
-Constricting the connection between the anterior and middle ventricle reduces
-solute transport to the anterior ventricle (ROI 5),
-and the mean concentration in ROIs 2--4 and 6 slightly increases, compared to the original geometry
-(\Crefpanels{fig:fig6}{c}). This is notwithstanding a
+3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively, compared to the original
+geometry. \mer{MER: HH adds a sentence on changes in tangential
+  traction(\Crefpanels{fig:fig6}{d}). This is notwithstanding a
 9.5\% reduction in ventral cilia force magnitude
-(\Crefpanels{fig:fig6}{d}), which are the cilia that propel CSF and solute towards ROI 6.
-Constricting the mid-hind brain connection
-leads to less transport into the posterior ventricle (ROI 6),
-and slightly more transport towards the anterior ventricle (ROI 5).
-Faster transport to the anterior ventricle (ROI 5) and slower transport to the
-posterior ventricle (ROI 6) is also the case for the geometry with a
-shrunk middle ventricle.
-This reduction in the transport to the posterior ventricle (ROI 6)
-happens in spite of a 6.6\% increase in the ventral cilia forces.
-Additionally, for the shrunk middle configuration, the transport upstream of CSF flow towards the
-ventral-posterior region of the middle ventricle (ROI 3) is slowed down.
-
-For the mesh where all three ventricles are modified,
+(\Crefpanels{fig:fig6}{d}), which are the cilia that propel CSF and solute towards ROI 6.)}
+
+Constricting the connection between the anterior and middle ventricle
+reduces solute transport to the anterior ventricle (ROI 5), and the
+mean concentration in ROIs 2--4 and 6 slightly increases, compared to
+the original geometry (\Crefpanels{fig:fig6}{c}). \mer{We thus note
+  that restricting the ...} Constricting the middle-posterior duct
+mainly delays the transport into the posterior ventricle (ROI 6),
+while \mer{gently} accelerating transport towards the anterior
+ventricle (ROI 5). Faster transport to the anterior ventricle (ROI 5)
+and slower transport to the lower middle and posterior ventricle
+(ROI3, ROI 6) is also the case for the geometry with a shrunk middle
+ventricle. \mer{Interestingly, this reduction in the transport to the
+  posterior ventricle (ROI 6) happens in spite of a 6.6\% increase in
+  the ventral cilia forces.}
+%
+%For the mesh where all three ventricles are modified,
+When combining all three modifications,
 we observe higher retention of solute in the middle ventricle (ROIs 2--4),
-while both the anterior and the posterior ventricles (ROIs 5 and 6) have reduced
-mean concentrations. To summarize, our results show that the
-ventricular geometry and the cross-sectional area of the ventricular ducts matter
-for solute transport, with notable differences in transport resulting from
-relatively modest geometry modifications. This may explain why
-we observed larger differences in the cilia-deficient computational
-model results compared to the experimental data in \Cref{fig:fig4},
-as the model and the fish have slightly different geometries.
+while the mean concentration is reduced in both the anterior and the posterior ventricles (ROIs 5 and 6)s.
+
+To summarize, these results show that the ventricular geometry and the
+cross-sectional area of the ventricular ducts clearly impact solute
+transport, with notable differences in transport resulting from modest
+geometry modifications. These findings may explain the larger
+differences in the cilia-deficient computational model results
+compared to the experimental data in \Cref{fig:fig4}, \mer{as the
+computational geometry is not an exact representation for the
+individual zebrafish ventricles.} 
 \begin{figure}

### 2025-04-02 paper/main.tex
Revamp Discussion

@@
 ventricular geometries: (i) constriction of the anterior-middle
-ventricular duct (66 \% reduction in cross-sectional area); (ii) constriction of the middle-posterior duct (33 \% reduction); (iii) middle ventricle shrunk in the lateral direction (43 \% reduction); and (iv) all three combined (\Crefpanels{fig:fig6}{a, b}).
+ventricular duct (66 \% reduction in cross-sectional area);
+(ii) constriction of the middle-posterior duct (33 \% reduction);
+(iii) middle ventricle shrunk in the lateral direction (43 \% reduction);
+and (iv) all three combined (\Crefpanels{fig:fig6}{a, b}).
 %
@@
 we observe higher retention of solute in the middle ventricle (ROIs 2--4),
-while the mean concentration is reduced in both the anterior and the posterior ventricles (ROIs 5 and 6)s.
+while the mean concentration is reduced in both the anterior
+and the posterior ventricles (ROIs 5 and 6)s.
 
@@
 individual zebrafish ventricles.}
+
+\lyng{We previously identified large interindividual variation in ventricular size and
+CSF velocities between larva at given developmental stages and throughout
+development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
+Our results suggest that these two parameters, CSF velocities and ventricular size,
+affect each other.}
 \begin{figure}
@@
 In this study, we have presented a computational model of CSF flow and
-solute transport within the brain ventricles.
+solute transport within brain ventricles.
 We used the larval zebrafish brain ventricles since its geometry and
 flow mechanisms are well described, thereby allowing us to validate
-our simulations experimentally. Nevertheless, our computational framework can be adapted to,
-and implemented in, other ventricular systems in the future, once the flow parameters of such systems
-are comprehensively resolved. We assumed that intraventricular CSF flow was governed
+our simulations experimentally. Our computational framework can be adapted to
+and implemented in other ventricular systems in the future,
+once the flow parameters of such systems
+are adequately resolved.
+We assumed that intraventricular CSF flow was governed
 by the Stokes equations.
@@
 on the CSF flow, we were able to reproduce flow fields with similar features
-as observed experimentally. The prominent flow features were vortex-structured flow,
-mediated by cilia, and pulsatile flow, mediated by the cardiac cycle.
+as observed experimentally. The prominent flow features were vortex-structured flow
+mediated by cilia, and pulsatile flow mediated by the cardiac cycle.
 
@@
 affect solute distribution. Altogether, we present not only new findings on the role of
-diffusion and advection in intraventricular transport, but also provide a novel framework to
-study CSF flow and transport in complex geometries.
+diffusion and advection in intraventricular transport, but also provide a
+computational framework to study CSF flow and transport in ventricular geometries.
 
@@
 based on changes in fluorescence intensity $\Delta F$ (experiments) and
-mean concentration $\cbar$ (simulations) over time.
+mean concentration $\cbar$ (simulations) over time. Our results convincingly show that
+intraventricular transport of solute depends on a balance of advection and diffusion.
+While advection is the strongest transport mechanism on a global scale for
+Dendra2 proteins (global Péclet number 13), diffusion is balancing out
+advection for shorter distances and for regions without motile cilia activity.
+For instance, for the larger extracellular vesicles, no solute reached the (distant)
+posterior ventricle (a distance of $L = 200$ \textmu m) within the simulation time (around 860 s).
+Advective transport by the mean velocity $\overline{U}=2.4$ \textmu m/s over the same
+distance would happen on a timescale of $t_a=L/\overline{U}=83$ s, indicating that
+transport to the posterior ventricle is solely driven by diffusion at the developmental
+stage 2 dpf. The estimated timescale of diffusion $t_d=L^2/D_1$ over the 
+same distance is $\approx$24500 s. Larger molecules
+transported primarily by advection are thus more easily
+compartmentalized within the ventricles
+as a result of the compartmentalized CSF flow.
+
+Removing motile cilia slowed down transport within
+the middle ventricle and towards the anterior ventricle,
+but the transport towards the posterior ventricle was unaffected.
+Photoconversion experiments on cilia mutant
+zebrafish larva (\emph{smh}) aligned with these observations.
+This further indicates that
+transport from the middle to the posterior ventricle is
+purely driven by diffusion at this developmental stage.
+The experimental results provide not only confidence
+in the predictive ability of the computational model,
+but also quantify the impact of cilia motility
+on intraventricular transport.
+Interestingly, Yoshida~\emph{et al.} observed a drastic reduction
+in CSF mixing in specific regions of the brain
+ventricles when simulating reduced cilia motility~\cite{Yoshida2022EffectVentricles}.
+\lyng{Since impaired brain 
+clearance of tracers has been demonstrated in idiopathic normal pressure hydrocephalus
+patients~\cite{Eide2020MagneticHydrocephalus},
+cilia-enhanced mixing in the brain ventricles might be
+fundamental to physiological transport within the brain.}
+
+\subsection{Model validation and choice of parameters}
 Even though we identified similar dynamics in simulations and
@@
 Differences between experiments and simulations may relate to
-ventricular size, as we showed that modifying the geometry of the interventricular ducts
-impacts solute distribution, and the geometry used for the computational model was larger
-than some of the geometries used in experiments.
-Notably, there are large variations in ventricular size in the control population at 2 dpf.
-Alternatively, dissimilarities in results may relate
-to the way we defined the photoconversion site (ROI 1) in the simulations,
-since the volume of the photoconversion region determines
-the total amount of solute and thereby the rate of transport. Another source
+ventricular size, as we showed that modifying the geometry of the
+ventricular geometry impacts solute distribution,
+and the ventricular size varies substantially 
+in the control population at 2 dpf.
+Additionally, differences may result
+from the definition of the photoconversion site (ROI 1)
+as the volume of this region determines the total amount of solute
+and thereby the rate of transport. Another source
 of discrepancy may relate to the permeability of the ventricular wall,
-which we have ignored in our simulation. Reports have shown that the
-neuroepithelium lining the walls of brain ventricles in 24 hour old zebrafish
+which we have considered as impermeable in our simulations.
+The neuroepithelium lining the walls of brain ventricles in 24 hour old zebrafish
 is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
@@
 thus under this reported limit, one could assume that Dendra2 may
-leak out of the brain ventricles over the time spans we consider
-and render the dynamics slower. Finally, an important difference
-between the simulations and experiments is the fact that the
-computational model is three-dimensional, while the
-experiments only resolve two-dimensional features.
-
-Nevertheless, our results convincingly show that
-intraventricular transport of proteins depends on a balance of advection and diffusion.
-While advection is the strongest transport mechanism on a global scale for
-Dendra2 (global Péclet number 13), diffusion is balancing out
-advection especially for shorter distances and for regions devoid of motile cilia activity.
-Indeed, we identified that the diffusion coefficient had a greater impact on transport to
-regions located upstream in the CSF flow field (ROI 3) or in distant ventricles (ROIs 5--6),
-than the regions located downstream of cilia-mediated flow (ROI 2).
-
-Meanwhile, we identified that transport of larger molecules
-(thus with smaller diffusion coefficients),
-such as 150 nm radius extracellular vesicles, are almost entirely dependent on advection.
-There was essentially zero solute in the posterior ventricle at the
-final simulation time (around 860 s), a ventricle where transport is driven
-by diffusion due to the absence of motile cilia.
-For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance
-$L=200$ \textmu m from the middle to the posterior ventricle is approximately 24500 s.
-Advective transport by the mean velocity $\overline{U}=2.4$ \textmu m/s over the same
-distance would happen on a timescale of $t_a=L/\overline{U}=83$ s.
-Comparing this with the minuscule values of $\cbar_6$ after simulating transport
-with $D_1$ for 850 s, one can conclude that if advection
-played a role in transporting solute from the photoconversion site in the middle ventricle
-to the posterior ventricle, values of $\cbar_6$ would be higher than those observed.
-
-\subsection{Effects of cilia motility and ventricular morphology}
-To gain insights into how CSF flow and intraventricular transport depend on cilia
-motility and ventricular morphology, we manipulated certain
-parameters in our model and the computational geometry.
-First, we investigated how complete loss of cilia motility
-impacted the transport dynamics. Simulations with a cardiac-induced/no-cilia lead to
-slower transport when compared to the baseline model that included cilia. Especially
-the middle-ventricular region downstream of CSF flow (ROI 2) and the anterior ventricle (ROI 5)
-experienced substantially increased times-to-threshold. We also observed
-slower dynamics in the rest of the middle ventricle (ROIs 3 and 4), whereas the
-posterior ventricle (ROI 6) was unaffected by the loss of cilia motility,
-further indicating that transport from the middle to the posterior ventricle is
-purely driven by diffusion at this developmental stage.
-We also performed photoconversion experiments on cilia mutant
-zebrafish larva (\emph{smh}), observing statistically significant slower transport in 
-ROIs 2 and 4. The results provide not only confidence in that our computational model
-represents the physics well, but also valuable quantification of the impact of cilia motility
-on intraventricular transport. Interestingly, a previous simulation study of reduced cilia motility
-also observed a drastic reduction in CSF mixing in specific regions of the brain
-ventricles~\cite{Yoshida2022EffectVentricles}, similar to our results. Since impaired brain 
-clearance of tracers has been demonstrated in idiopathic normal pressure hydrocephalus
-patients~\cite{Eide2020MagneticHydrocephalus}, cilia-enhanced mixing in the brain might be
-fundamental to physiological transport within the brain.
-
-Next, we paralyzed cilia in specific regions of
-our model. We identified that the cilia in the dorsal middle ventricle contribute
-the most to solute distribution, which aligns well with the fact
-that these cilia generate the strongest flow field in vivo~\cite{Olstad2019CiliaryDevelopment}
-and in our model. In contrast, removing the ventral cilia in the middle ventricle
-did not greatly impact flow dynamics, despite these cilia contributing a third of
-the total force exerted by the cilia. However, removing ventral cilia in the middle ventricle
-lead to reduced transport towards the posterior ventricle,
-meanwhile increasing transport towards the anterior ventricle,
-as the ventral cilia help induce flow towards the posterior ventricle.
-Removing the cilia in the anterior ventricle affected CSF flow only locally,
-and did not affect the global transport.
-
-With an interest in assessing the impact of ventricular morphology on solute transport,
-we simulated transport in modified ventricular geometries.
-Notably, shrinking ducts reduced interventricular solute distribution, while shrinking
-the middle ventricle obstructed diffusive transport upstream of the flow field.
-We previously identified large interindividual variation in ventricular size and
-CSF velocities between larva at given developmental stages and throughout
-development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
-Our results suggest that these two parameters, CSF velocities and ventricular size,
-may well affect each other, which helps explain the variation in the two.
-
-These simulation studies demonstrate that our model is flexible and allows in silico
-testing of further hypotheses on the effects of ciliated
-lineages and ventricular morphology on CSF flow and intraventricular transport.
-We envision that our framework will be useful as a basis for future analyses of
-CSF dynamics in more complex geometries and also other animal species and humans.
-
-\subsection{Numerical approximation and computational modeling aspects}
-We modeled motile cilia as a stress
-exerted tangentially on the CSF at the ventricular walls
-while employing a slip boundary condition,
-motivated by experimental observations of the
-flow field in zebrafish embryo brain ventricles, both previously and in this work, in which
+leak out of the brain ventricles over the relevant time spans
+and render the dynamics slower. 
+It may also be the case that our model predicts faster
+transport because the Dendra2 diffusion
+coefficient we used (based on an experimental value
+\cite{GuraSadovsky2017MeasurementExpansion}) is too high.
+This could be because embryonic CSF has higher viscosity
+than the solution considered in the measurements, 
+or the presence of proteins, nutrients and other solutes
+that hinder diffusive transport
+\cite{Bloomfield1998EffectsFluid, Einstein1905UberTeilchen, Cussler2009Diffusion:Systems}.
+Finally, an important difference
+is the three-dimensional nature of the computational model,
+while the experimental images only show 2D slices.
+
+We modeled motile cilia as a tangential
+traction at the ventricular walls
+while allowing the CSF to slip,
+motivated by experimental observations of
+flow fields in zebrafish larval brain ventricles in which
 the fluid velocity increases towards the
 wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. 
+The ciliated boundaries in our model are regionally homogeneous,
+whereas in reality, cilia populate the ventricle walls in a
+heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneity
+in cilia location, beating direction and beating frequency
+has been shown to enhance particle clearance in airway cilia arrays
+in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
+Other studies have demonstrated that changes to beating directionality affects transport,
+and that specific coordination of the ciliary beating is important in the brain ventricles for
+flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
+Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
+Pellicciotta2020Cilia},
+for maintaining healthy functioning of mucous transport in
+airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction,
+Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet},
+and in the nodal flow that establishes
+left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry,
+Sawamoto2006NewBrain}.
+Incorporating spatial heterogeneity in our model would
+therefore presumably affect results, and could be
+interesting to pursue in further work.
+
+The maximum stress
+$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$
+of the cilia boundary condition
+was applied in the dorsal-posterior region of the middle ventricle.
+In a model of CSF flow in human brain ventricles,
+Siyahhan~\emph{et al.} modeled ciliary motion with
+a force that increased linearly from
+the ventricular wall to a maximum force density of
+$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m (the cilium length)
+away~\cite{Siyahhan2014FlowVentricles}.
+In a cilia array of thickness $\delta = 15$ \textmu m,
+the maximum stress $\vert\btau\vert_{\mathrm{max}}$
+in our model would correspond to a maximum force density of 
+\begin{equation*}
+    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{\delta}
+        = \frac{\num{2.5e-3} \ \mathrm{N/m^2}}{\num{15e-6} \ \mathrm{m}}
+        = 169 \ \mathrm{N/m^3}.
+\end{equation*}
+With $\delta=5$ \textmu m (the typical cilium length in zebrafish brain ventricles
+\cite{Olstad2019CiliaryDevelopment,
+Salman2022ComputationalEmbryo, Ringers2023NovelEpithelia}) 
+our cilia stress corresponds to a maximum force density of
+$f_c=507$ N/$\mathrm{m^3}$.
+For further comparison, Thouvenin~\emph{et al.}
+modeled two-dimensional cilia-mediated 
+flow in the central canal of zebrafish
+embryos using a force density of 4000 N/$\mathrm{m^2}$\cite{Thouvenin2020OriginCanal}.
+Averaging this value over the reported central canal diameter 8.9 \textmu m
+yields a maximum force of 449 N/$\mathrm{m^3}$.
+It is very interesting to note the similarity 
+in cilia force densities estimated in our and these two previous studies.
+\fixme{Previous work concluded that motile cilia align by response to the shear
+stress of flow. Perhaps there is an optimal cilia stress?}
+
+To simulate protein transport in the brain ventricles we solved
+an advection-diffusion equation. We handled advective transport
+through the anterior/posterior boundaries
+(where cardiac pressure pulsations are imposed)
+with an approximate periodic boundary condition
+that conserves the total solute concentration.
+A possible improvement to this would be
+to consider a 3D-0D coupling of in- and outflow using
+ordinary differential equations,
+similar to applications in cardiac
+modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
+Alternatively, the beating cardiac motion could be modeled by ventricular wall deformation
+to avoid advective boundary fluxes~\cite{Causemann2022HumanFramework,
+Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
+
+% The Stokes-Einstein relation assumes the diffusing
+% substance is of spherical shape and the relation does not
+% necessarily hold in CSF. Moreover, the extrapolation implies the assumption that
+% the two substances (the one for which we determine $D$ and the one we extrapolate from)
+% have equal densities. We note that one previous study reported that
+% Dendra2 satisfies the Stokes-Einstein in a solution of similar viscosity
+% to CSF\cite{GuraSadovsky2017MeasurementExpansion}.
+% We used CSF density and viscosity values measured in
+% humans~\cite{Bloomfield1998EffectsFluid},
+% and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances,
+% the CSF in which the photoconverted Dendra2 are transported in our experiments may be more viscous
+% than we assumed. This could reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
+% but previous works have reported a limited impact of protein concentration on the viscosity of
+% CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}.
+% Merely the presence of other proteins and nutrients may also reduce the diffusion
+% coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
+
+\subsection{Numerical approximation}
 The Brezzi-Douglas-Marini and discontinuous Galerkin scheme
 $\mathrm{BDM}_1$-$\mathrm{DG}_0$
-we used to discretize the governing equations of the flow
+we used to discretize the Stokes equations
 is computationally more expensive
-than more conventional approaches such as a
+than \fixme{conventional} methods such as a
 Taylor-Hood discretization
-($P_k-P_{k-1}$ elements)~\cite{Stenberg1990ErrorProblem}, or lower-order enriched
-elements, such as the mini-element
-($P_1-P_1$ with a velocity stabilization)~\cite{Brezzi2011MixedMethods}.
+($P_k-P_{k-1}$ elements)~\cite{Stenberg1990ErrorProblem} or lower-order enriched
+elements (such as $P_1-P_1$ with a velocity stabilization)~\cite{Brezzi2011MixedMethods}.
 Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
@@
 the CSF velocity $\uu_h$ satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
-This yields $\normlinf{\nabla\cdot\uu_h}=0$ to within solver tolerances,
+This yields $\normlinf{\nabla\cdot\uu_h}=0$,
 an important property for the stability of the advection-diffusion
-equation\cite{cesmelioglu2022compatible, johnson2009numerical, gresho1998incompressible}.
-In addition to its favorable mass-conserving property,
-the BDM-DG discretization scheme 
-we employed for the Stokes equations
+equation that we used to simulate solute transport,
+especially in advection-dominated cases.
+\cite{cesmelioglu2022compatible, johnson2009numerical, gresho1998incompressible}.
+Additionally, the BDM-DG scheme 
 lets us impose the impermeability condition $\uu\cdot\nn=0$
-strongly without any tailored approach,
-since the BDM elements control the normal component of the 
-velocity~(\Cref{subsec:appendixA1})~\cite{Brezzi1985TwoProblems}.
-If instead (for example) Taylor-Hood
-elements were to be used, the impermeability boundary condition must
+strongly, since the BDM elements control the normal component of the 
+velocity~\cite{Brezzi1985TwoProblems}.
+For elements where this is not the case (such as Taylor-Hood elements),
+the impermeability boundary condition must
 be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
@@
 Bertoluzza2017BoundaryHemodynamics}, which affects
-convergence properties and increases problem complexity.
-
-The ciliated boundaries in our CSF flow model are regionally homogeneous,
-whereas in reality, cilia populate the ventricle walls in a
-heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneous
-arrangement of cilia, both in location, beating direction and beating frequency,
-has been shown to enhance particle clearance in airway cilia arrays
-in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
-Incorporating spatial arrangement heterogeneity in our model could
-result in different transport timescales,
-but we would not expect notable changes to the general trends of the macroscopic
-transport that we study here, since the effects of introducing heterogeneous spacing
-of cilia would alter the magnitude of cilia forces, but not their direction.
-On the other hand, introducing more heterogeneous beating directionality could
-alter the transport timescales as well as the directionality.
-In our model, all of the applied cilia
-tangential traction is aligned with the rostrocaudal axis, and more heterogeneity
-in this alignment to reflect heterogeneity in the beating directionality of
-cilia would presumably affect both magnitude and directionality of advective transport.
-Previous studies have demonstrated that changes to beating directionality affects transport,
-and that specific coordination of the ciliary beating is important in the brain ventricles for
-flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
-Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
-Pellicciotta2020Cilia},
-but also in other phenomena such as maintaining healthy functioning of mucous transport in
-airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction,
-Bustamante-Marin2019LackClearance, Tsukita2012CoordinatedFeet} and in nodal flow which establishes
-left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry,
-Sawamoto2006NewBrain}.
-Although these studies were mostly on spatial scales resolving individual cilia,
-we could envision the same effects in our continuum model,
-similar to the results of previous numerical studies~\cite{Ramirez-SanJuan2020Multi-scaleArrays,
-Thouvenin2020OriginCanal, Yoshida2022EffectVentricles}.
-
-To simulate protein transport in the brain ventricles, we numerically solved
-an advection-diffusion equation. Except for where we imposed a normal pressure
-boundary condition on the CSF flow,
-we imposed a no-flux condition on the concentration. The normal pressure
-boundary condition leads to in- and outflow of CSF,
-and this advective transport requires handling of in- and outflux boundary conditions on
-the concentration. For the influx, we applied an approximate periodic boundary condition
-that conserves the total solute concentration.
-We handled the outflux by imposing zero diffusive flux while
-leaving the advective flux term as an unknown in the weak form
-of the advection-diffusion equation. This approach has been referred to with different names,
-such as the ``free boundary condition"~\cite{Papanastasiou1992ACondition},
-the ``no boundary condition"~\cite{Griffiths1997TheCondition}, and the 
-``consistent flux boundary condition"~\cite{Lynch2020NumericalHemodynamics}. 
-In leaving the advective flux term in the weak form we are lacking a boundary condition,
-which is problematic in the continuous sense of the problem.
-However, the discrete problem is well-posed, because the approach represents
-constraining higher-order derivatives of the concentration~\cite{Griffiths1997TheCondition}. 
-In defining ROIs 5 and 6 in the anterior and posterior ventricles,
-we deliberately excluded the space proximal to
-in- and outflow boundaries to limit adverse effects of 
-the advective flux boundary condition on the mean concentrations.
-
-A possible improvement to the in- and outflow boundary conditions would be
-to consider a 3D-0D coupling of in- and outflow using
-ordinary differential equations,
-similar to applications in cardiac
-modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
-However, if the brain ventricular system in reality is a closed system,
-one should rather seek out a way of modeling the CSF flow without open boundaries to avoid
-handling in- and outflow boundary conditions. A more appropriate way of handling the beating
-cardiac motion could be to impose a ventricular wall deformation, assumed to result from pulsatile
-motion of the heart and/or cardiac vessels surrounding the ventricles. This wall deformation would
-induce CSF flow while simultaneously permitting enforcement of the impermeability condition
-$\uu\cdot\nn=0$ on the ventricular walls. Such wall motion-induced CSF flow has been modeled and
-simulated successfully in the human brain ventricular system~\cite{Causemann2022HumanFramework,
-Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
-
-We heuristically determined the magnitude of the cilia tangential traction boundary condition
-with the parameter $\tau = 0.65$ mPa. The maximum stress
-$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$
-was applied in the dorsal-posterior region of the middle ventricle.
-Previous simulation studies of cilia-mediated flow in brain ventricles have
-used a volumetric force density to represent the cilia.
-Based on reconstruction of CSF flow in murine brain ventricles,
-a previous study employed a force that increased linearly from
-the ventricular wall to a maximum force density of
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m (the cilium length)
-away from the wall~\cite{Siyahhan2014FlowVentricles}.
-If we assumed a cilia array of the same thickness
-$\delta = 15$ \textmu m in our model, the maximum stress $\vert\btau\vert_{\mathrm{max}}$
-would correspond to a maximum force density of 
-\begin{equation*}
-    f_c = \frac{\vert\btau\vert_{\mathrm{max}}}{\delta}
-        = \frac{\num{2.5e-3} \ \mathrm{N/m^2}}{\num{15e-6} \ \mathrm{m}}
-        = 169 \ \mathrm{N/m^3},
-\end{equation*}
-which is smaller than $f_{\mathrm{max}}$, albeit the same order of magnitude.
-The length 15 \textmu m is the typical length of cilia in the human brain
-\cite{Afzelius2004CiliaRelatedDiseases, Siyahhan2014FlowVentricles},
-while in zebrafish they are closer to 5 \textmu m~\cite{Olstad2019CiliaryDevelopment,
-Salman2022ComputationalEmbryo, Ringers2023NovelEpithelia}.
-With $\delta=5$ \textmu m, our cilia stress corresponds to a maximum force density of
-$f_c=507$ N/$\mathrm{m^3}$, which is very similar to
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$~\cite{Siyahhan2014FlowVentricles}.
-Another study that used a force density to model ciliary motion is
-considered two-dimensional flow in the central canal of zebrafish
-embryos~\cite{Thouvenin2020OriginCanal}.
-Cilia was modeled using a cilia force density of
-4000 N/$\mathrm{m^2}$. Averaging this value over the central canal diameter 8.9 \textmu m
-measured in the study yields a maximum force of 449 N/$\mathrm{m^3}$.
-It is very interesting to note the similarity 
-in cilia force densities estimated in our and these two previous studies.
-\fixme{Previous work concluded that motile cilia align by response to the shear
-stress of flow. Perhaps there is an optimal cilia stress?}
-
-The diffusion coefficients used in this study are based on experimental values. 
-The value $D_3=\num{1.15e-10} \ \mathrm{m^2/s}$
-is based on the value $\num{1.15e-10} \pm 0.11 \ \mathrm{m^2/s}$ reported in an
-experiment~\cite{GuraSadovsky2017MeasurementExpansion}, while the Stokes-Einstein
-relation~(\Cref{eq:D_stokes_einstein})~\cite{Einstein1905UberTeilchen} was used to extrapolate
-the value of $D_2$ and estimate the value of $D_1$, based on experimental
-data~\cite{Swaminathan1997PhotobleachingDiffusion, Potma2001ReducedCells,
-Mahmood2023ExosomeTemperature}. The Stokes-Einstein relation assumes the diffusing
-substance is of spherical shape, which proteins are not, and the relation does not
-necessarily hold in CSF. Moreover, the extrapolation implies the assumption that
-the two substances (the one for which we determine $D$ and the one we extrapolate from)
-have equal densities. Consequently, there is uncertainty in the diffusion coefficient values used.
-We note that one previous study reported that
-Dendra2 satisfies the Stokes-Einstein in a solution of similar viscosity
-to CSF\cite{GuraSadovsky2017MeasurementExpansion}.
-We used CSF density and viscosity values measured in
-humans~\cite{Bloomfield1998EffectsFluid},
-and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances,
-the CSF in which the photoconverted Dendra2 are transported in our experiments may be more viscous
-than we assumed. This could reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
-but based on reports of protein concentration having a limited impact on the viscosity of
-CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}, this reduction is presumably
-limited. Merely the presence of other proteins and nutrients may also reduce the diffusion
-coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
-Considering the diffusion coefficients $D_1$ and $D_2$ (both smaller
-than $D_3$) in our transport analysis provides information about how the simulation
-results of Dendra2 transport would be altered if the
-diffusion coefficient $D_3$ is overestimated. In the case that $D_3$ is underestimated, 
-we expect a trend similar to the difference in the $D_2$ and $D_3$ solute concentrations;
-incerasingly diffusive fields.
-
-\subsection{The role of motile cilia in intraventricular flow and transport}
-Our work has studied CSF flow and solute distribution
-in a relatively small and simple brain model, which is devoid of
-active CSF secretion and CSF absorption. Even though there is
-a clear conservation of the ventricular system across vertebrates,
-there are also important considerations to take. These include (but are not limited to)
-ventricular size and morphology, properties of ciliated cells,
-animal posture, and magnitude of velocities. For instance, a large
-volume would require an extensive amount of time for solutes to distribute
-if based solely on diffusion. Besides, the presence of multiple cilia
-instead of a single cilium per cell -- the former can be found in
-mammalian ependymal cells -- will generate stronger velocities.
-Hence advection may be more dominant in those situations.
-
-In large brains such as the human brain, we presume ciliary beating mostly 
-contributes to flow in localized regions proximal to the ventricular walls, due to
-the microscopic length of the cilia.
-Although the precise mechanisms of intraventricular flow are still debated,
-much evidence indicate that blood vessel pulsations, respiration, CSF secretion
-and brain motion induce the pulsatile bulk flow in the central
-regions of the ventricles~\cite{Vinje2019RespiratoryMeasurements,
-Siyahhan2014FlowVentricles, Linninger2005PulsatileBrain, Enzmann1992BrainImaging,
-Kurtcuoglu2007ComputationalSylvius}.
-In human brains, cilia therefore probably play an important role in regulating the
-amount of substances like extracellular vesicles close to the ventricular walls, similar to coral
-reefs, where it has been observed that cilia are primary regulators of
+convergence properties and increases problem complexity
+(see \Cref{subsec:appendixA1} for more details).
+
+\subsection{Outlook}
+We studied the zebrafish larval brain ventricles,
+in which the flow generated by ciliary motion
+is of the scale of the geometry~\cite{Olstad2019CiliaryDevelopment}.
+In large brains such as the human brain, ciliary beating mostly 
+contributes to flow in localized regions proximal to the ventricular walls
+due to the microscopic length of the cilia~\cite{Siyahhan2014FlowVentricles}.
+The cilia may play an important role in regulating the
+amount of substances like extracellular vesicles close to the ventricular walls,
+similar to coral reefs,
+where cilia are primary regulators of
 oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}.
@@
 of a cilia-driven flow network in rodent brains suggests such selective
-transport~\cite{Faubel2016Cilia-basedVentricles}.
-
-On the other hand, for the zebrafish embryos we studied,
-the ventricles are so small that the flow
-generated by ciliary motion is of the scale of the geometry, and thus not
-only contributes to near-wall flow dynamics, but flow in the entire ventricular
-system~\cite{Olstad2019CiliaryDevelopment}.
-To date, motile-cilia deficiency has been associated with altered brain function
-in zebrafish, dysfunctional establishment of left-right symmetry,
-and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004CiliaRelatedDiseases,
-Youn2018PrimaryDiseases, Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}
-Yet the molecular mechanisms leading to these alterations are poorly understood.
-We trust that our model sets the basis for future work addressing these open questions.
-We are also confident that our model can be adjusted and implemented to fit
-microscopic and macroscopic parameters for larger brains, once these parameters are acquired.
-
-In conclusion, we have presented a numerical model
-of cerebrospinal fluid flow and solute transport in
-zebrafish brain ventricles based on finite element methods.
-A realistic ventricular geometry from medical imaging was used to perform a
-computational study. The flow model reproduces
-the experimentally observed flow features of cilia-mediated cerebrospinal fluid
-flow in zebrafish brain ventricles. Coupling the flow to the transport model,
-we estimated how slowly or rapidly molecules of varying size are transported in
-the ventricles. 
-The numerical model was validated with in vivo experiments, measuring the movement of
-a photoconverted fluorescent protein in zebrafish brain ventricles,
-both for healthy animals and mutant animals with ciliary dysfunction.
-We observed good alignment between computational and experimental results.
-Simulations indicate that cilia-driven advection is important
-for transport of larger molecules, whereas diffusion accounts for most of
-the transport of smaller molecules. 
-Experimental results support the conclusion that cilia only affect the
-local distribution of small proteins,
-while most of their transport is governed by diffusion.
-
-\subsection{Limitations and further work}
-The model presented has certain limitations. Future work could consider improving:
-\begin{itemize}
-    \item time-varying cilia?
-    \item FSI: CSF flow coupled to 1D/2D/3D cilia structures.
-    \item any comments on experiments?
-\end{itemize}
+brain ventricular transport~\cite{Faubel2016Cilia-basedVentricles}.
+Our simulation studies demonstrate that our computational model is
+flexible and allows in silico testing of such open questions
+and further hypotheses on the effects of ciliated
+lineages and ventricular morphology on CSF flow and intraventricular transport.
+
+% Small versus large brain: For instance, a large
+% volume would require an extensive amount of time for solutes to distribute
+% if based solely on diffusion. Besides, the presence of multiple cilia
+% instead of a single cilium per cell -- the former can be found in
+% mammalian ependymal cells -- will generate stronger velocities.
+% Hence advection may be more dominant in those situations.
+
+% Much evidence indicate that blood vessel pulsations, respiration, CSF secretion
+% and brain motion induce the pulsatile bulk flow in the central
+% regions of the ventricles~\cite{Vinje2019RespiratoryMeasurements,
+% Siyahhan2014FlowVentricles, Linninger2005PulsatileBrain, Enzmann1992BrainImaging,
+% Kurtcuoglu2007ComputationalSylvius}.
+
+% To date, motile-cilia deficiency has been associated with altered brain function
+% in zebrafish, dysfunctional establishment of left-right symmetry,
+% and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004CiliaRelatedDiseases,
+% Youn2018PrimaryDiseases, Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}
 
@@
 Also considering the weak form of the continuity equation,
-the weak formulation for the cardiac-only/no-cilia model version
+the weak formulation for the cardiac-induced/no-cilia model version
 then reads: find $(\uu,\, p)\in\VV\times Q$
@@
 conditions~\Cref{eq:slip_BC_modelC} and~\Cref{eq:freeslip_BC_modelC}
-as introduced for the cilia-only/no-cardiac model, and the boundary
-condition~\Cref{eq:pressure_BC_modelC} as introduced for the cardiac-only/no-cilia model.
+as introduced for the cilia-driven/no-cardiac model, and the boundary
+condition~\Cref{eq:pressure_BC_modelC} as introduced for the cardiac-induced/no-cilia model.
 The abstract weak formulation for 
@@
 \end{equation*}
-where $c\in H^1$ is the solute concentration and
+where $c\in W=H^1$ is the solute concentration and
 $\uu\in\VV$ is the cerebrospinal fluid velocity .
@@
 Using the introduced approaches of handling the in- and outflow boundaries,
-the resulting abstract weak formulation for the cardiac-only/no-cilia model is:
+the resulting abstract weak formulation for the cardiac-induced/no-cilia model is:
 find $c\in W$ such that
@@
 the advection-diffusion equation for the baseline model is
-identical to that of the cardiac-only/no-cilia model,
+identical to that of the cardiac-induced/no-cilia model,
 defined by~\Cref{eq:adv_diff_weak_formB,eq:adv_diff_skew_form,eq:adv_diff_linear_form}.
@@
         -\nabla\cdot\bsig &= \bm{f} \qquad\mathrm{in \ }\Omega,\\
-        \nabla\cdot\uu &= g \qquad\mathrm{in \ }\Omega,
+        \nabla\cdot\uu &= g \qquad\mathrm{\ in \ }\Omega,
     \end{align}
@@
 where $\Gamma=\partial\Omega$ is the boundary of the domain.
-Since the velocity field defined by~\Cref{eq:velocity_mms} is divergence free by construction,
+Since the velocity field defined by~\Cref{eq:velocity_mms} is divergence-free by construction,
 $g = 0$. Setting the external force $\bm{f}=-\nabla\cdot\bsig(\uu_{\mathrm{mms}}, p_{\mathrm{mms}})$

### 2025-04-04 paper/main.tex
revision edition

@@
 resolved. This study analyzes and evaluates the role of motile cilia
-in brain intraventricular CSF flow and transport. The geometry of the
+in brain ventricular CSF flow and transport. The geometry of the
 zebrafish larval brain ventricles, for which detailed knowledge of
@@
 used to develop finite element methods for modelling flow and
-transport. The computational model is validated by in-vivo experiments
+transport. The computational model is validated by in vivo experiments
 that monitor transport of a photoconvertible protein secreted in the
@@
 
-\noindent\small\hspace{.8725cm}\textbf{Keywords} cerebrospinal fluid, brain ventricles, cilia, transport, finite elements
+\noindent\small\hspace{.975cm}\textbf{Keywords} cerebrospinal fluid, brain ventricles, cilia, transport, finite elements
 
@@
 In this study, we combined computational and experimental approaches to investigate
-the role of motile cilia in intraventricular CSF flow and transport.
+the role of motile cilia in brain ventricular CSF flow and transport.
 We model the flow and transport by partial differential equations and solve
@@
 
-Assuming that viscous forces are dominating the intraventricular CSF flow,
+Assuming that viscous forces are dominating the ventricular CSF flow,
 we model the flow by the Stokes equations.
@@
 bidirectional tangential traction acting on parts of the ventricular wall
-(\Crefpanels{fig:fig1}{d}), and we assume free velocity slip at the walls.
+(\Crefpanels{fig:fig1}{d}), with free velocity slip at the walls.
 Simulations show that this traction alone
@@
 
-Ciliary motion is integral to physiological CSF flow, and absence of
-cilia has been associated with defective brain development and various
-pathologies~\cite{Eichele2020Cilia-drivenVentricle,
+Ciliary motion is integral to physiological CSF flow,
+and motile-cilia deficiency has been
+associated with defective brain development and various
+pathologies in zebrafish, rodents and humans~\cite{Eichele2020Cilia-drivenVentricle,
 Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles,
@@
 Sawamoto2006NewBrain, Yoshiba2014RolesSymmetry,
-  Hirokawa2006NodalAsymmetry}.  As observed both experimentally and
+Hirokawa2006NodalAsymmetry, Youn2018PrimaryDiseases,
+Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}.  As observed both experimentally and
 computationally, absence of motile cilia alters CSF flow patterns.  We
-next investigate the implications of these changes on intraventricular
+next investigate the implications of these changes on brain ventricular
 transport. We experimentally measured the movement of proteins by
@@
     \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$
-    in each region of interest (ROI) for control (black lines, $n=8$)
-    and \emph{smh} mutant (red lines, $n=6$) fish. 
-    Bold lines are mean values of the cohorts and shaded regions cover one standard devation errors
-    in the means.
+    in each region of interest (ROI) for control (black lines)
+    and \emph{smh} mutant (red lines) zebrafish. 
+    Bold lines are mean values of the cohorts and shaded regions cover one standard devation.
     \textbf{b.} Times when $\Delta F(t)$ first exceeds a threshold value,
-    equal to 0.25 (ROIs 2--4) or 0.10 (ROIs 5, 6), for control (gray dots) and
-    \emph{smh} mutant (red dots) fish.
-    The thick black lines denote mean values of the datasets. The $p$-values
-    were calculated using a Mann-Whitney U test with a confidence level of 95\%, with 
-    the null hypothesis that the two distributions of control and mutant data are 
+    equal to 0.25 (ROIs 2--4) or 0.10 (ROIs 5, 6), for controls (gray dots) and
+    \emph{smh} mutants (red dots).
+    The thick black lines denote mean values. The $p$-values
+    were calculated using a Mann-Whitney U test with 95\% confidence level,
+    under the null hypothesis that the two distributions of control and mutant data are 
     from the same population.
@@
     $\hat{t}$ when the threshold is first exceeded is reported in the plot legends.
-    Note that in both panels \textbf{a} and \textbf{c}, the vertical axes have
+    Note that in panels \textbf{a} and \textbf{c} the vertical axes have
     different limits in each plot.}
@@
 the cilia in the respective region.
-%
-%% the cilia tangential traction boundary condition is for each case
-%% changed to a free-slip boundary condition in the paralyzed region,
-%% prescribing zero tangential forces to represent absence of cilia
-%% motion.
-%
 
@@
 dorsal cilia exert 52\% of the total tangential
-force~(\Crefpanels{fig:fig5}{b}). \mer{Thus, the CSF velocities are
-  affected not only by the magnitude of the applied forces, but result
-  from a nontrivial interplay between force, directionality and
-  location.}
-%% The magnitude of these force
-%% contributions are thus more similar than the difference in their
-%% impact on the maximum velocity magnitudes.
-
-Turning to transport of Dendra2, we again note that removal of the
-dorsal cilia has the most pronounced effect. All mean concentration
+force~(\Crefpanels{fig:fig5}{b}).
+Thus, the CSF velocities are affected not only by
+the magnitude of the applied forces, but result
+from a nontrivial interplay between force directionality
+and location, and ventricular morphology.
+
+Turning to transport of Dendra2, removal of the
+dorsal cilia again has the most pronounced effect. All mean concentration
 profiles (except ROI 1, where we impose the photoconversion curve)
@@
 cilia does not alter the mean concentrations
-(\Crefpanels{fig:fig5}{c}). Finally, without ventral cilia in the
-middle ventricle, more solute spreads towards the anterior ventricle
-(ROI 5) and less solute spreads towards the posterior ventricle (ROI
-6).
+(\Crefpanels{fig:fig5}{c}). Finally, when removing ventral cilia in the
+middle ventricle more solute spreads towards the anterior ventricle
+(ROI 5), and less solute spreads towards the posterior ventricle (ROI 6).
 \begin{figure}[H]
@@
 Variations in ventricular morphology impact CSF flow
-patterns~\cite{Olstad2019CiliaryDevelopment}.  To assess how these
+patterns, and we previously identified large
+interindividual variation in ventricular size and
+CSF velocities between larva at given developmental stages and throughout
+development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
+To assess how these
 variations influence solute distribution, we consider four alternative
 ventricular geometries: (i) constriction of the anterior-middle
-ventricular duct (66 \% reduction in cross-sectional area);
+interventricular duct (66 \% reduction in cross-sectional area);
 (ii) constriction of the middle-posterior duct (33 \% reduction);
@@
 and (iv) all three combined (\Crefpanels{fig:fig6}{a, b}).
-%
-%% one where the duct connecting the anterior and middle ventricles is constricted
-%% (66 \% reduction in cross-sectional area);
-%% one where the duct connecting the middle and posterior ventricles is constricted
-%% (33 \% reduction);
-%% one where the middle ventricle is shrunk in the lateral direction (43 \% reduction);
-%% and the combination of these three modifications (\Crefpanels{fig:fig6}{a, b}).
-%
-%
 In these four modified geometries, the total volume is reduced by
 3.9\%, 4.1\%, 1.4\% and 9.4\%, respectively, compared to the original
-geometry. \mer{MER: HH adds a sentence on changes in tangential
-  traction(\Crefpanels{fig:fig6}{d}). This is notwithstanding a
-9.5\% reduction in ventral cilia force magnitude
-(\Crefpanels{fig:fig6}{d}), which are the cilia that propel CSF and solute towards ROI 6.)}
-
-Constricting the connection between the anterior and middle ventricle
+geometry. As a result of the geometry modifications,
+the forces applied with the 
+cilia tangential traction differ across the scenarios
+(\Crefpanels{fig:fig6}{c}).
+
+Constricting the anterior-middle duct
 reduces solute transport to the anterior ventricle (ROI 5), and the
-mean concentration in ROIs 2--4 and 6 slightly increases, compared to
-the original geometry (\Crefpanels{fig:fig6}{c}). \mer{We thus note
-  that restricting the ...} Constricting the middle-posterior duct
+mean concentrations in ROIs 2--4 and 6 slightly increase, compared to
+the original geometry (\Crefpanels{fig:fig6}{d}).
+Constricting the middle-posterior duct
 mainly delays the transport into the posterior ventricle (ROI 6),
-while \mer{gently} accelerating transport towards the anterior
-ventricle (ROI 5). Faster transport to the anterior ventricle (ROI 5)
-and slower transport to the lower middle and posterior ventricle
-(ROI3, ROI 6) is also the case for the geometry with a shrunk middle
-ventricle. \mer{Interestingly, this reduction in the transport to the
+while slightly accelerating transport towards the anterior
+ventricle (ROI 5). 
+Thus for both scenarios, solute transport is restricted through
+the respective constricted interventricular duct.
+For the geometry with a shrunk middle
+ventricle, we observe faster transport
+to the anterior ventricle (ROI 5)
+and slower transport to the lower middle 
+and posterior ventricles (ROI 3, ROI 6). 
+Interestingly, this reduction in the transport to the
 posterior ventricle (ROI 6) happens in spite of a 6.6\% increase in
-  the ventral cilia forces.}
-%
-%For the mesh where all three ventricles are modified,
+the ventral cilia forces, which are the cilia that propel
+CSF towards the posterior ventricle.
+
 When combining all three modifications,
 we observe higher retention of solute in the middle ventricle (ROIs 2--4),
-while the mean concentration is reduced in both the anterior
-and the posterior ventricles (ROIs 5 and 6)s.
-
+while the mean concentrations are reduced in both the anterior
+and the posterior ventricles (ROIs 5 and 6).
 To summarize, these results show that the ventricular geometry and the
@@
 differences in the cilia-deficient computational model results
-compared to the experimental data in \Cref{fig:fig4}, \mer{as the
-computational geometry is not an exact representation for the
-individual zebrafish ventricles.}
-
-\lyng{We previously identified large interindividual variation in ventricular size and
-CSF velocities between larva at given developmental stages and throughout
-development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
-Our results suggest that these two parameters, CSF velocities and ventricular size,
-affect each other.}
+compared to the differences in experimental data in \Cref{fig:fig4},
+as the computational geometry is not an exact representation of the
+individual zebrafish ventricles.
+
 \begin{figure}
@@
     \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
-    in the 6 ROIs.
+    in the six regions of interest (ROIs).
     \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
@@
     to which the forces $F_i$ of the other mesh versions are compared, where $i$ denotes
-    the cases fore-shrunk, middle shrunk, mid-hind shrunk, and the combination of the three.
-    The bars for the four shrunk scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
+    the modification scenario.
+    The bars for the four alternative scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
     \label{fig:fig6}
@@
 Finally, we investigated how local cilia paralysis and ventricular geometries
-affect solute distribution. Altogether, we present not only new findings on the role of
-diffusion and advection in intraventricular transport, but also provide a
+affect solute distribution. Altogether, we present not only new findings on the roles of
+advection and diffusion in brain ventricular transport, but also provide a
 computational framework to study CSF flow and transport in ventricular geometries.
 
-\subsection{The roles of advection and diffusion in intraventricular solute transport}
-To investigate the roles of advection and diffusion in solute transport, we quantified transport
+\subsection{The roles of advection and diffusion in brain ventricular solute transport}
+To investigate brain ventricular solute transport, we quantified transport
 based on changes in fluorescence intensity $\Delta F$ (experiments) and
 mean concentration $\cbar$ (simulations) over time. Our results convincingly show that
-intraventricular transport of solute depends on a balance of advection and diffusion.
+the solute transport depends on a balance of advection and diffusion.
 While advection is the strongest transport mechanism on a global scale for
-Dendra2 proteins (global Péclet number 13), diffusion is balancing out
-advection for shorter distances and for regions without motile cilia activity.
+the three solutes we studied (global Péclet numbers greater than unity),
+diffusion is balancing out advection for shorter distances and in regions without motile cilia activity.
 For instance, for the larger extracellular vesicles, no solute reached the (distant)
@@
 distance would happen on a timescale of $t_a=L/\overline{U}=83$ s, indicating that
-transport to the posterior ventricle is solely driven by diffusion at the developmental
-stage 2 dpf. The estimated timescale of diffusion $t_d=L^2/D_1$ over the 
-same distance is $\approx$24500 s. Larger molecules
-transported primarily by advection are thus more easily
+transport to the posterior ventricle is solely driven by diffusion at this developmental
+stage. The estimated timescale of diffusion $t_d=L^2/D_1$ over the 
+same distance is $\approx$24500 s, compared to 696 s and 348 s for the 
+smaller proteins (STM-GFP and Dendra2).
+This explains why $D_1$ is the only
+case where no solute spreads to the posterior ventricle,
+while STM-GFP and Dendra2 are transported there by diffusion.
+Larger molecules transported primarily by advection
+are thus more easily
 compartmentalized within the ventricles
@@
 
+\subsection{Effects of cilia motility on transport}
 Removing motile cilia slowed down transport within
 the middle ventricle and towards the anterior ventricle,
-but the transport towards the posterior ventricle was unaffected.
-Photoconversion experiments on cilia mutant
+but the transport to the posterior ventricle was unaffected.
+Photoconversion experiments with cilia mutant
 zebrafish larva (\emph{smh}) aligned with these observations.
@@
 transport from the middle to the posterior ventricle is
-purely driven by diffusion at this developmental stage.
-The experimental results provide not only confidence
-in the predictive ability of the computational model,
-but also quantify the impact of cilia motility
-on intraventricular transport.
+purely diffusive at this developmental stage,
+while transport within the middle ventricle
+depends on cilia motility.
 Interestingly, Yoshida~\emph{et al.} observed a drastic reduction
@@
 ventricles when simulating reduced cilia motility~\cite{Yoshida2022EffectVentricles}.
-\lyng{Since impaired brain 
-clearance of tracers has been demonstrated in idiopathic normal pressure hydrocephalus
-patients~\cite{Eide2020MagneticHydrocephalus},
-cilia-enhanced mixing in the brain ventricles might be
-fundamental to physiological transport within the brain.}
-
-\subsection{Model validation and choice of parameters}
+Our experimental results provide not only confidence
+in the predictive ability of our computational model,
+but also quantify the impact of cilia motility
+on brain ventricular transport.
+
+\subsection{Model parameters and sources of discrepancies}
 Even though we identified similar dynamics in simulations and
-in vivo experiments, the dynamics of the simulations were generally
+in vivo experiments, the transport dynamics of the simulations were generally
 more rapid and resulted in higher total amounts of solute.
@@
 Additionally, differences may result
-from the definition of the photoconversion site (ROI 1)
-as the volume of this region determines the total amount of solute
+from the definition of the photoconversion site,
+since the volume of this region determines the total amount of solute
 and thereby the rate of transport. Another source
 of discrepancy may relate to the permeability of the ventricular wall,
-which we have considered as impermeable in our simulations.
+which we considered as impermeable in our simulations.
 The neuroepithelium lining the walls of brain ventricles in 24 hour old zebrafish
 is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
-Since Dendra2 is around 26 kDa in size~\cite{Gurskaya2006EngineeringLight} and
-thus under this reported limit, one could assume that Dendra2 may
-leak out of the brain ventricles over the relevant time spans
+If this is also the case at 2 dpf, Dendra2 
+(which are 26 kDa in size~\cite{Gurskaya2006EngineeringLight})
+would leak out of the brain ventricles over the relevant time spans
 and render the dynamics slower.
@@
 than the solution considered in the measurements, 
-or the presence of proteins, nutrients and other solutes
-that hinder diffusive transport
+or because the presence of proteins, nutrients and other solutes
+obstructs diffusive transport
 \cite{Bloomfield1998EffectsFluid, Einstein1905UberTeilchen, Cussler2009Diffusion:Systems}.
@@
 The ciliated boundaries in our model are regionally homogeneous,
-whereas in reality, cilia populate the ventricle walls in a
-heterogeneous manner~\cite{Olstad2019CiliaryDevelopment}. Heterogeneity
+whereas in reality cilia populate the ventricle walls
+heterogeneously~\cite{Olstad2019CiliaryDevelopment}. Heterogeneity
 in cilia location, beating direction and beating frequency
-has been shown to enhance particle clearance in airway cilia arrays
+enhances particle clearance in airway cilia arrays
 in mice~\cite{Ramirez-SanJuan2020Multi-scaleArrays}.
-Other studies have demonstrated that changes to beating directionality affects transport,
-and that specific coordination of the ciliary beating is important in the brain ventricles for
-flow and signaling processes~\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
+Beating directionality can affect transport,
+and specific coordination of the ciliary beating is important for
+flow and signaling processes in the brain ventricles
+\cite{Eichele2020Cilia-drivenVentricle, Olstad2019CiliaryDevelopment,
 Faubel2016Cilia-basedVentricles, Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
 Pellicciotta2020Cilia},
-for maintaining healthy functioning of mucous transport in
+for physiological mucous transport in
 airways~\cite{Rayner1996CiliarySyndrome, Schneiter2021Multi-scaleFunction,
@@
 and in the nodal flow that establishes
-left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry,
-Sawamoto2006NewBrain}.
+left-right symmetry in mammals~\cite{Yoshiba2014RolesSymmetry, Hirokawa2006NodalAsymmetry, Sawamoto2006NewBrain}.
 Incorporating spatial heterogeneity in our model would
@@
 
-The maximum stress
-$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$
-of the cilia boundary condition
-was applied in the dorsal-posterior region of the middle ventricle.
+The maximum stress of the cilia boundary condition was
+$\vert\btau\vert_{\mathrm{max}} = 2.5 \ \mathrm{mPa} = \num{2.5e-3} \ \mathrm{N/m^2}$.
 In a model of CSF flow in human brain ventricles,
 Siyahhan~\emph{et al.} modeled ciliary motion with
-a force that increased linearly from
+a force increasing linearly from
 the ventricular wall to a maximum force density of
-$f_{\mathrm{max}} = 526$ N/$\mathrm{m^3}$ at a distance 15 \textmu m (the cilium length)
+$f_{\mathrm{max}} = 526 \ \mathrm{N/m^3}$ at
+a distance 15 \textmu m (the cilium length)
 away~\cite{Siyahhan2014FlowVentricles}.
 In a cilia array of thickness $\delta = 15$ \textmu m,
-the maximum stress $\vert\btau\vert_{\mathrm{max}}$
-in our model would correspond to a maximum force density of 
+the maximum stress in our model would correspond to a maximum force density of 
 \begin{equation*}
@@
 our cilia stress corresponds to a maximum force density of
-$f_c=507$ N/$\mathrm{m^3}$.
+$f_c=507 \ \mathrm{N/m^3}$.
 For further comparison, Thouvenin~\emph{et al.}
@@
 flow in the central canal of zebrafish
-embryos using a force density of 4000 N/$\mathrm{m^2}$\cite{Thouvenin2020OriginCanal}.
+embryos using a force density of 4000 $\mathrm{N/m^2}$\cite{Thouvenin2020OriginCanal}.
 Averaging this value over the reported central canal diameter 8.9 \textmu m
-yields a maximum force of 449 N/$\mathrm{m^3}$.
-It is very interesting to note the similarity 
-in cilia force densities estimated in our and these two previous studies.
-\fixme{Previous work concluded that motile cilia align by response to the shear
-stress of flow. Perhaps there is an optimal cilia stress?}
-
-To simulate protein transport in the brain ventricles we solved
-an advection-diffusion equation. We handled advective transport
+yields a maximum force of 449 $\mathrm{N/m^3}$.
+In light of the previous finding that motile cilia
+align by response to shear stress magnitudes
+of flow,~\cite{Pellicciotta2020Cilia}
+it is interesting to note the above similarity 
+in cilia force estimates.
+
+\subsection{Numerical approximation}
+When solving an advection-diffusion equation to
+simulate protein transport, we handled advective transport
 through the anterior/posterior boundaries
@@
 Alternatively, the beating cardiac motion could be modeled by ventricular wall deformation
-to avoid advective boundary fluxes~\cite{Causemann2022HumanFramework,
+to avoid advective boundary fluxes\cite{Causemann2022HumanFramework,
 Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
 
-% The Stokes-Einstein relation assumes the diffusing
-% substance is of spherical shape and the relation does not
-% necessarily hold in CSF. Moreover, the extrapolation implies the assumption that
-% the two substances (the one for which we determine $D$ and the one we extrapolate from)
-% have equal densities. We note that one previous study reported that
-% Dendra2 satisfies the Stokes-Einstein in a solution of similar viscosity
-% to CSF\cite{GuraSadovsky2017MeasurementExpansion}.
-% We used CSF density and viscosity values measured in
-% humans~\cite{Bloomfield1998EffectsFluid},
-% and because embryonic CSF in zebrafish is high in proteins, nutrients and other substances,
-% the CSF in which the photoconverted Dendra2 are transported in our experiments may be more viscous
-% than we assumed. This could reduce the diffusion coefficient (cf.~\Cref{eq:D_stokes_einstein}),
-% but previous works have reported a limited impact of protein concentration on the viscosity of
-% CSF~\cite{Bloomfield1998EffectsFluid, Brydon1995PhysicalViscosity}.
-% Merely the presence of other proteins and nutrients may also reduce the diffusion
-% coefficient by reduction of mean-free path lengths of molecules~\cite{Cussler2009Diffusion:Systems}.
-
-\subsection{Numerical approximation}
 The Brezzi-Douglas-Marini and discontinuous Galerkin scheme
@@
 the CSF velocity $\uu_h$ satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
-This yields $\normlinf{\nabla\cdot\uu_h}=0$,
+Resultingly $\normltwo{\nabla\cdot\uu_h}=0$ to within solver tolerances,
 an important property for the stability of the advection-diffusion
-equation that we used to simulate solute transport,
-especially in advection-dominated cases.
-\cite{cesmelioglu2022compatible, johnson2009numerical, gresho1998incompressible}.
+equation, especially in advection-dominated cases.
+\cite{cesmelioglu2022compatible, johnson2009numerical, gresho1998incompressible}
 Additionally, the BDM-DG scheme 
@@
 \subsection{Outlook}
-We studied the zebrafish larval brain ventricles,
-in which the flow generated by ciliary motion
-is of the scale of the geometry~\cite{Olstad2019CiliaryDevelopment}.
-In large brains such as the human brain, ciliary beating mostly 
-contributes to flow in localized regions proximal to the ventricular walls
-due to the microscopic length of the cilia~\cite{Siyahhan2014FlowVentricles}.
+The flow generated by ciliary motion
+in zebrafish larval brain ventricles
+is of the scale of the geometry~\cite{Olstad2019CiliaryDevelopment},
+while in large brains such as the human brain, ciliary beating 
+contributes to flow proximal to the ventricular walls
+\cite{Siyahhan2014FlowVentricles}.
 The cilia may play an important role in regulating the
 amount of substances like extracellular vesicles close to the ventricular walls,
-similar to coral reefs,
-where cilia are primary regulators of
+similar to coral reefs where cilia are primary regulators of
 oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}.
-Flow mediated by cilia indeed serves such a purpose in nodal flow at early
-developmental stages of the brain~\cite{Hirokawa2006NodalAsymmetry}, and the discovery
-of a cilia-driven flow network in rodent brains suggests such selective
+Cilia indeed regulate nodal flow at early
+developmental stages of the brain~\cite{Hirokawa2006NodalAsymmetry},
+and the discovery of a cilia-driven flow network
+in rodent brains suggests such selective
 brain ventricular transport~\cite{Faubel2016Cilia-basedVentricles}.
-Our simulation studies demonstrate that our computational model is
-flexible and allows in silico testing of such open questions
-and further hypotheses on the effects of ciliated
-lineages and ventricular morphology on CSF flow and intraventricular transport.
-
-% Small versus large brain: For instance, a large
-% volume would require an extensive amount of time for solutes to distribute
-% if based solely on diffusion. Besides, the presence of multiple cilia
-% instead of a single cilium per cell -- the former can be found in
-% mammalian ependymal cells -- will generate stronger velocities.
-% Hence advection may be more dominant in those situations.
-
-% Much evidence indicate that blood vessel pulsations, respiration, CSF secretion
-% and brain motion induce the pulsatile bulk flow in the central
-% regions of the ventricles~\cite{Vinje2019RespiratoryMeasurements,
-% Siyahhan2014FlowVentricles, Linninger2005PulsatileBrain, Enzmann1992BrainImaging,
-% Kurtcuoglu2007ComputationalSylvius}.
-
-% To date, motile-cilia deficiency has been associated with altered brain function
-% in zebrafish, dysfunctional establishment of left-right symmetry,
-% and ventricular enlargement in zebrafish, rodents and humans.~\cite{Afzelius2004CiliaRelatedDiseases,
-% Youn2018PrimaryDiseases, Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}
+As the CSF flows through the central nervous system,
+the system may be affected by the changes in CSF composition
+due to reduced mixing following reduced
+ciliary motion. We demonstrated with
+simulations that solute concentrations,
+and in turn CSF composition, 
+are affected by ventricular
+geometry changes. A 10\% difference in volume
+had a noticeable impact on solute transport,
+showing that pathological ventricular volume changes,
+such as the enlargement observed in hydrocephalus,
+would affect CSF composition.
+Because CSF plays an important role in the regulation of solutes
+within the ventricular system~\cite{yamada2021cerebrospinal},
+understanding more of the interplay between
+transport dynamics and ventricular morphology,
+as well as the impact of
+reduced mixing resulting from cilia-deficiency,
+are important considerations for future work.
+We hope our findings and the computational
+framework we have presented can help address
+such open questions in the future.
 
@@
 \begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega\setminus\Omega_{\mathrm{pc}},
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
     \label{eq:adv_diff_strong}
@@
 
-To study how cilia paralysis and ventricular morphology affect intraventricular
+When studying how cilia paralysis and ventricular morphology affect brain ventricular
 flow and transport, we calculate the magnitude of a tangential force $F$ 
@@
 is weakly enforced with a penalty parameter $\gamma=10$~\cite{Hong2016AEquations}.
-Since the divergence of the velocity space is a subspace of the pressure space for this scheme,
+Since the divergence of the velocity function space is the pressure function space for this scheme,
 the divergence-free condition of the velocity is satisfied exactly, ensuring mass conservation.~\cite{Boffi2008FiniteProblem}
@@
 \noindent \textbf{Data Availability Statement} \par
-\noindent The data and implementations presented in this paper are licensed under \fixme{LICENSE}
-and openly available at \fixme{REPO-LINK}.
+\noindent The data and model implementations presented in this paper are
+openly available at \fixme{REPO-LINK}.
 
@@
     \forall K\in\Omega_h;
-    \vv_h\cdot\nn=0 \ \text{on } \Gamma\setminus\Gp\Big\},\\
+    \vv_h\cdot\nn=0 \ \text{on } \Gamma_h\setminus\Gamma_{h, \mathrm{p}}\Big\},\\
     Q_h &= \Big\{q_h : q_h\in L^2;  q_h\vert_K\in P_{k-1}(K); \forall K\in\Omega_h\Big\},
@@
 $\mathbf{H}(\mathrm{div})$-conforming and exactly mass-conserving:
-due to the fact that $\nabla\cdot\VV_h\subset Q_h$,
+due to the fact that $\nabla\cdot\VV_h= Q_h$,
 the continuity equation (\Cref{eq:BDM_stokes_div})
-is satisfied in every computational mesh cell.
+can be satisfied in every computational mesh cell.
 Moreover, control of normal components of $\uu_h$ conveniently 
@@
 of the discrete weak form (\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}).
-We apply the stabilization outlined in Hong~\emph{et al.}~\cite{Hong2016AEquations}.
+We apply the stabilization outlined by Hong~\emph{et al.}~\cite{Hong2016AEquations}.
 First, we define the average and jump operators, respectively, as
@@
 the three different model versions, depending on the boundary conditions considered.
+For all model versions, we simulate photoconversion for times in 
+$\Omega_{\mathrm{pc}}\subset\Omega$ by strongly enforcing
+\begin{equation}
+    c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
+    \quad \forall \xx \in \Omega_{\mathrm{pc}},
+    \label{eq:photoconversion_curve_appendix}
+\end{equation}
+for all times $t$ until simulation ends at time $T$.
+The parameter $a=65$ determines the growth speed of
+the solute concentration and was chosen such that
+\Cref{eq:photoconversion_curve_appendix} is similar
+to the experimental photoconversion curves.
 
@@
         -\nabla\cdot\bsig &= \bm{f} \qquad\mathrm{in \ }\Omega,\\
-        \nabla\cdot\uu &= g \qquad\mathrm{\ in \ }\Omega,
+        \nabla\cdot\uu &= g \qquad\mathrm{\, in \ }\Omega,
     \end{align}
@@
 resolution $h_k$. Based on the assumption that the error scales as
-$e_k \approx C{h_k}^l$, where $C$ is a constant independent of $h_k$,
-the convergence order $l$ was approximated as
+$e_k \approx C{h_k}^\eta$, where $C$ is a constant independent of $h_k$,
+the convergence order $\eta$ was approximated as
 \begin{equation}
-    l = \frac{\log{(e_k/e_{k+1}})}{\log{(h_k/h_{k+1}})}.
+    \eta = \frac{\log{(e_k/e_{k+1}})}{\log{(h_k/h_{k+1}})}.
     \label{eq:convergence_order_estimate}

### 2025-04-06 paper/main.tex
mk pass

@@
 \date{\vspace{-2em}} % Remove space between affiliations and abstract
+
+\newcommand{\miro}[1]{{\color{cyan}#1}}
 
@@
 bidirectional tangential traction acting on parts of the ventricular wall
-(\Crefpanels{fig:fig1}{d}), with free velocity slip at the walls.
+(\Crefpanels{fig:fig1}{d}), with \miro{no-penetration condition at the walls}.
 Simulations show that this traction alone
@@
 Differences between experiments and simulations may relate to
-ventricular size, as we showed that modifying the geometry of the
-ventricular geometry impacts solute distribution,
+ventricular size, as we showed that modifying the ventricular geometry impacts solute distribution,
 and the ventricular size varies substantially 
@@
 is computationally more expensive
-than \fixme{conventional} methods such as a
-Taylor-Hood discretization
-($P_k-P_{k-1}$ elements)~\cite{Stenberg1990ErrorProblem} or lower-order enriched
-elements (such as $P_1-P_1$ with a velocity stabilization)~\cite{Brezzi2011MixedMethods}.
+than \fixme{conventional methods} \miro{ the more commonly used discretizations} such as a
+Taylor-Hood ($P_2-P_{1}$ elements)~\cite{Stenberg1990ErrorProblem} or lower-order enriched
+elements (e.g. MINI)~\cite{Brezzi2011MixedMethods}.
 Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
@@
 Bertoluzza2017BoundaryHemodynamics}, which affects
-convergence properties and increases problem complexity
+convergence properties \miro{$<<$what do you mean here?} and increases problem complexity
 (see \Cref{subsec:appendixA1} for more details).
@@
 \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xUAS:Signal-Dendra2})
-adult animals, as described by D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}.
+adult animals, as described by D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}. \miro{$<<$ undef ref here}
 Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
@@
 Find the CSF velocity $\uu = \uu(\xx, t) = (u_x(\xx, t), u_y(\xx, t), u_z(\xx, t))$
-and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t>0$, such that
+and the CSF pressure $p = p(\xx, t)$ for $\xx \in \Omega$ and time $t\in(0, T]$, such that
 \begin{subequations}
@@
       \rho \pdifft{\uu} - \nabla \cdot \bsig &= \mathbf{0}
-      \quad \text{in } \Omega,\\
+      \quad \text{in } \Omega\times(0, T],\\
       \nabla \cdot \uu &= 0 
-      \quad  \text{in } \Omega,\label{eq:stokes_eqs_cont} 
+      \quad  \text{in } \Omega\times(0, T],\label{eq:stokes_eqs_cont} 
   \end{align}
@@
 modeling transport of a solute with concentration $c(\xx, t)$ for $\xx\in\Omega$ and
-time $t > 0$ by the advection-diffusion equation
+time $t\in(0, T]$ by the advection-diffusion equation
 \begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega,
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad \text{in } \Omega\times(0, T],
     \label{eq:adv_diff_strong}
@@
 In order to impose a smooth initial condition, we initially solve the diffusion equation
-\begin{equation*}
-    \pdifft{c} = \Tilde{D}\nabla^2 c
-\end{equation*}
+\begin{equation}\label{eq:cinit}
+  \begin{aligned}
+    &\pdifft{c} = \Tilde{D}\nabla^2 c \quad \text{in } \Omega\times(0, 2\Delta t]\\
+      &c(\xx, t=0) = 0\quad\text{ in }\Omega
+  \end{aligned}\
+\end{equation}
 with an increased diffusion coefficient $\Tilde{D}=D\times 10^{5}$ for two timesteps.
@@
 Jeong~\emph{et al.}~\cite{Jeong2024TheZebrafish}, and (iii) extracellular vesicles.
-To estimate the diffusion coefficients of these, when not
+To estimate their diffusion coefficients, when not
 available in the literature, we use the Stokes--Einstein relation
@@
 elements for the velocity.~\cite{Brezzi1985TwoProblems, Nedelec1986AIR3}
-The BDM elements have degrees of freedom associated with integral moments of the
+The BDM elements degrees of freedom are associated with integral moments of the
 velocity component normal to the facets of elements,
@@
 The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
-discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}.
+discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}. \miro{In particular,
+  with BDM only the normal component of the velocity is continuous.}
 Continuity in tangential velocities on interior facets
@@
 \subsection{Numerical approximation of the advection-diffusion equation}\label{subsec:num_approx_adv_diff}
-The advection-diffusion equation (\Cref{eq:adv_diff_strong}) is discretized
-with with a second-order, symmetric interior penalty DG
-method in space~\cite{Arnold1982AnElements}, chosen due to its favorable
-conservation properties. At each timestep the total number of degrees of freedom 
+\miro{The advection-diffusion equation (\Cref{eq:adv_diff_strong}) is discretized in
+space with quadratic DG elements using symmetric interior penalty DG method~\cite{Arnold1982AnElements}.
+The scheme was chosen due to its favorable mass 
+conservation properties}. At each timestep the total number of degrees of freedom 
 is 1 415 120. In time, the equation is discretized with the second-order backward
@@
    \rho\pdifft{\uu} - \nabla \cdot \bsig(\uu, p)
-   &= \mathbf{0} \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_mom}\\
-  \nabla \cdot \uu &= 0 \quad &&\mathrm{in} \ \Omega, \label{eq:BDM_stokes_div} 
+   &= \mathbf{0} \quad &&\mathrm{in} \ \Omega\times(0, T], \label{eq:BDM_stokes_mom}\\
+  \nabla \cdot \uu &= 0 \quad &&\mathrm{in} \ \Omega\times(0, T], \label{eq:BDM_stokes_div} 
 \end{alignat}
@@
 To derive weak formulations of the continuous problem defined by the Stokes
-equations (\Cref{eq:appendix_stokes_eqs}), we consider the function space
+equations (\Cref{eq:appendix_stokes_eqs}), we consider the function space\footnote{
+To simplify the exposition we focus only on spatial regularity. In particular,
+$\vv\in\mathbf{H}^1(\Omega)$ is understood as $\vv(\cdot, t)\in \mathbf{H}^1(\Omega)$ for all
+$t>0$. Similar convention is applied also when discussing advection-diffusion equation in \Cref{subsec:adv_diff_eq_weak_form}.
+}
 \begin{align*}
@@
 impermeability condition is assumed to hold on the \emph{entire} domain boundary
-for this model version, which leaves the pressure under-determined as a result of no
-boundary condition specifying the pressure.
+for this model version, which leaves the pressure under-determined as it is not
+subject to any boundary condition.
 
@@
 due to the fact that $\nabla\cdot\VV_h= Q_h$,
-the continuity equation (\Cref{eq:BDM_stokes_div})
-can be satisfied in every computational mesh cell.
+the continuity equation (\Cref{eq:BDM_stokes_div}) is satisfied point-wise.
 Moreover, control of normal components of $\uu_h$ conveniently 
@@
 
-Because the elements of $\VV_h$ only define the normal components of $\uu_h$,
-continuity in tangential components of $\uu_h$ on interior facets of
-the mesh is ensured through stabilization
-of the discrete weak form (\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}).
-We apply the stabilization outlined by Hong~\emph{et al.}~\cite{Hong2016AEquations}.
+\miro{The elements of $\VV_h$ only ensure by construction the continuity of normal components of $\uu_h$.
+Continuity of the tangential components of $\uu_h$ on interior facets of
+the mesh is enforced weakly by additional stabilization to 
+the discrete weak form (\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}).
+Specifically}, we apply the stabilization outlined by Hong~\emph{et al.}~\cite{Hong2016AEquations}.
 First, we define the average and jump operators, respectively, as
@@
 across interior facets, where the penalty parameter $\gamma>0$ must be chosen large enough
-to achieve stability. For appropriate convergence, the penalization term
-includes a scaling with the average of the cell diameter of neighboring mesh cells,
-with $h$ defined as the maximal distance between two points in a cell~\cite{Nitsche1971UberSind}.
+to achieve stability. \miro{For appropriate convergence, the penalization term
+includes a mesh-dependent scaling. In this work we choose it as the average of the cell diameter of neighboring mesh cells,
+with $h$ defined as the maximal distance between two points in a cell~\cite{Nitsche1971UberSind}.}
 The other two terms
@@
 \begin{equation}
-    \pdifft{c} + \nabla\cdot\JJ = 0 \quad\mathrm{in} \ \Omega,
+    \pdifft{c} + \nabla\cdot\JJ = 0 \quad\mathrm{in} \ \Omega\times(0, T],
     \label{eq:adv_diff_strong_DG}
@@
 \end{equation*}
-where $c\in W=H^1$ is the solute concentration and
+where $c\in W=H^1(\Omega)$ is the solute concentration and
 $\uu\in\VV$ is the cerebrospinal fluid velocity .
@@
 \end{equation}
-Consider a finite element function 
-\begin{equation*}
-    \phi = \phi_i\psi_i(\xx)
-\end{equation*}
-with basis functions $\psi_i$, where $i$ are the degrees of freedom and Einstein
-summation is employed.
-The infinity norm of $\phi$ was approximated from the vector
-of coefficients $\left\{\phi_i\right\}$, which represent point evaluations of $\phi$ as
+\miro{
+We define the approximation of the infinity norm of a finite element function
+$\phi = \phi_i\psi_i(\xx)$
+as 
 \begin{equation*}
@@
 \end{equation*}
+Here $\psi_i$ are the basis functions and $\phi_i$ are the degrees of freedom defined as point envaluations}
 
@@
 
-For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$.
+For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$, \miro{$u_h=\sqrt{\uu_h\cdot\uu_h}$}.
 We also report $\normlinf{u_h}$ scaled by the total force $F=\intGc{\sqrt{\btau\cdot \btau}}$
@@
 $\mathrm{BDM}_k$-$\mathrm{DG}_{k-1}$ are naturally 
-derived in a mesh-dependent broken $H^k$-norm for $\uu$ and the $L^2$-norm for the pressure.
+derived in a mesh-dependent broken $\mathbf{H}^1$-norm for $\uu$ and the $L^2$-norm for the pressure.
 The respective error norms are expected to decay with order $k$~\cite{Cockburn2005AEquations}.
 For the sake of simplicity,~\Cref{tab:cylinder_error_rates}
-reports the velocity errors in the standard $H^k$ norm. Using polynomial degree  
+reports the velocity errors in the standard $\mathbf{H}^1$ (semi)norm. Using polynomial degree  
 $k=1$, we observe linear convergence in the velocity in the $\mathbf{H}^1$ error norm
@@
 elements~\cite{Brezzi2011MixedMethods},
-such as the mini-element ($P_1-P_1$ with a velocity stabilization).
+such as the MINI-element.
 We opted for the BDM-DG scheme because of its exactly-mass-conserving property,

### 2025-04-07 paper/main.tex
Spell-check

@@
     Bold lines are mean values of the cohort ($n=8$) and shaded regions cover
-    one standard devation errors in the mean.
+    one standard deviation errors in the mean.
     \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
@@
     and \emph{smh} mutant (red lines) zebrafish. 
-    Bold lines are mean values of the cohorts and shaded regions cover one standard devation.
+    Bold lines are mean values of the cohorts and shaded regions cover one standard deviation.
     \textbf{b.} Times when $\Delta F(t)$ first exceeds a threshold value,
@@
 transport, with notable differences in transport resulting from modest
-geometry modifications. These findings may explain the larger
+geometry modifications. These findings may also explain the larger
 differences in the cilia-deficient computational model results
@@
 the CSF velocity $\uu_h$ satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
-Resultingly $\normltwo{\nabla\cdot\uu_h}=0$ to within solver tolerances,
+As a result $\normltwo{\nabla\cdot\uu_h}=0$ to within solver tolerances,
 an important property for the stability of the advection-diffusion
@@
 \end{equation*}
-Here $\psi_i$ are the basis functions and $\phi_i$ are the degrees of freedom defined as point envaluations}
+Here $\psi_i$ are the basis functions and $\phi_i$ are the degrees of freedom defined as point evaluations}
 
@@
 fundamental to attain a stable discretization of the advection-diffusion equation
-in advection-dominated regions. Preliminarily, we attempted
+in advection-dominated regions. First, we attempted
 to discretize the Stokes equations with 

### 2025-04-07 paper/main.tex
Updates in Discussion preface.

@@
 In this study, we have presented a computational model of CSF flow and
-solute transport within brain ventricles.
-We used the larval zebrafish brain ventricles since its geometry and
-flow mechanisms are well described, thereby allowing us to validate
-our simulations experimentally. Our computational framework can be adapted to
-and implemented in other ventricular systems in the future,
-once the flow parameters of such systems
-are adequately resolved.
-We assumed that intraventricular CSF flow was governed
-by the Stokes equations.
-By imposing tangential traction and normal pressure
-on the CSF flow, we were able to reproduce flow fields with similar features
-as observed experimentally. The prominent flow features were vortex-structured flow
-mediated by cilia, and pulsatile flow mediated by the cardiac cycle.
-
-Using the simulated CSF flow, we modeled solute transport by an advection-diffusion equation.
-The transport results compared well with data from in vivo experiments in zebrafish.
-Then, by using a computational model as well as zebrafish mutants with paralyzed cilia,
-we identified that even though advection by cilia is dominant,
-diffusion plays a significant role in protein transport.
-Finally, we investigated how local cilia paralysis and ventricular geometries
-affect solute distribution. Altogether, we present not only new findings on the roles of
-advection and diffusion in brain ventricular transport, but also provide a
-computational framework to study CSF flow and transport in ventricular geometries.
+solute transport within brain ventricles.  We used the larval
+zebrafish brain ventricles since their geometry and flow mechanisms are
+well described, thereby allowing for validation of the simulation
+results against experimental measurements. Our computational framework
+can be adapted to other ventricular systems, once the flow parameters
+of such are adequately resolved. Here, we assumed that
+intraventricular CSF flow was governed by the Stokes equations. By
+imposing tangential traction and normal pressure acting on the CSF, we
+were able to reproduce flow features observed experimentally. In
+particular, vortex-structured flow mediated by the cilia and pulsatile
+flow mediated by the cardiac cycle emerged as key flow characteristics.
+
+Using the simulated CSF flow, we modeled solute transport via an
+advection-diffusion equation. The resulting evolution and distribution
+of solutes compared well with data from in vivo experiments in
+zebrafish and is advection-dominated on the global scale for a
+physiologically-relevant range of solutes. By studying the
+distribution patterns in the absence of cilia motion, both via
+zebrafish mutants and computationally, we find that diffusion more
+strongly affects solute spread to distant parts of the ventricular
+system (upstream). Regional loss of cilia delayed solute transport
+with the most pronounced effect stemming from dorsal cilia
+paralysis. Moreover, the ventricular morphology also affects solute
+distribution, with the duct between the anterior and middle ventricles
+as a key passage. Altogether, we present not only new findings on the
+roles of advection and diffusion in brain ventricular transport, but
+also provide a computational framework to study CSF flow and transport
+in ventricular geometries.
 

### 2025-04-07 paper/main.tex
Updates in Discussion 1

@@
 \subsection{The roles of advection and diffusion in brain ventricular solute transport}
-To investigate brain ventricular solute transport, we quantified transport
-based on changes in fluorescence intensity $\Delta F$ (experiments) and
-mean concentration $\cbar$ (simulations) over time. Our results convincingly show that
-the solute transport depends on a balance of advection and diffusion.
-While advection is the strongest transport mechanism on a global scale for
-the three solutes we studied (global Péclet numbers greater than unity),
-diffusion is balancing out advection for shorter distances and in regions without motile cilia activity.
-For instance, for the larger extracellular vesicles, no solute reached the (distant)
-posterior ventricle (a distance of $L = 200$ \textmu m) within the simulation time (around 860 s).
-Advective transport by the mean velocity $\overline{U}=2.4$ \textmu m/s over the same
-distance would happen on a timescale of $t_a=L/\overline{U}=83$ s, indicating that
-transport to the posterior ventricle is solely driven by diffusion at this developmental
-stage. The estimated timescale of diffusion $t_d=L^2/D_1$ over the 
-same distance is $\approx$24500 s, compared to 696 s and 348 s for the 
-smaller proteins (STM-GFP and Dendra2).
-This explains why $D_1$ is the only
-case where no solute spreads to the posterior ventricle,
-while STM-GFP and Dendra2 are transported there by diffusion.
-Larger molecules transported primarily by advection
-are thus more easily
-compartmentalized within the ventricles
-as a result of the compartmentalized CSF flow.
+
+We quantified brain ventricular solute transport based on changes in
+fluorescence intensity $\Delta F$ (experiments) and mean concentration
+$\cbar$ (simulations) over time. Our results show that the solute
+distribution depends on a balance between advection and diffusion.
+While advection is the strongest transport mechanism on a global scale
+for the three solutes we studied (global Péclet numbers $> 1$),
+diffusion is balancing out advection for shorter distances and in
+regions without motile cilia activity.  For instance, for the larger
+extracellular vesicles, no solute reached the distant posterior
+ventricle (a distance of $L = 200$ \textmu m) within the simulation
+time (around 860 s). Advective transport by the mean velocity
+$\overline{U}=2.4$ \textmu m/s over the same distance would occur on a
+timescale of $t_a=L/\overline{U}=83$ s, indicating that transport to
+the posterior ventricle is not driven by advection at this
+developmental stage. The estimated timescale of diffusion for the
+extracellular vesicles ($t_d=L^2/D_1$) over the same distance is 24500
+s, but as low as 696 s and 348 s for the smaller proteins STM-GFP and
+Dendra2, respectively. These estimates support our observations that
+STM-GFP and Dendra2 spread to the posterior ventricle (by diffusion)
+while the extracellular vesicles do not. Larger molecules transported
+primarily by advection are thus more easily compartmentalized within
+the ventricles as a result of the compartmentalized CSF flow.
 

### 2025-04-07 paper/main.tex
Updates in Discussion

@@
 \subsection{Effects of cilia motility on transport}
-Removing motile cilia slowed down transport within
+
+Removing motile cilia delayed transport within
 the middle ventricle and towards the anterior ventricle,
-but the transport to the posterior ventricle was unaffected.
+while the transport to the posterior ventricle was unaffected.
 Photoconversion experiments with cilia mutant
@@
 ventricles when simulating reduced cilia motility~\cite{Yoshida2022EffectVentricles}.
-Our experimental results provide not only confidence
+\fixme{Our experimental results provide not only confidence
 in the predictive ability of our computational model,
 but also quantify the impact of cilia motility
-on brain ventricular transport.
-
-\subsection{Model parameters and sources of discrepancies}
-Even though we identified similar dynamics in simulations and
-in vivo experiments, the transport dynamics of the simulations were generally
-more rapid and resulted in higher total amounts of solute.
-Differences between experiments and simulations may relate to
-ventricular size, as we showed that modifying the ventricular geometry impacts solute distribution,
-and the ventricular size varies substantially 
-in the control population at 2 dpf.
-Additionally, differences may result
-from the definition of the photoconversion site,
-since the volume of this region determines the total amount of solute
-and thereby the rate of transport. Another source
-of discrepancy may relate to the permeability of the ventricular wall,
-which we considered as impermeable in our simulations.
-The neuroepithelium lining the walls of brain ventricles in 24 hour old zebrafish
-is permeable to dyes smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.
-If this is also the case at 2 dpf, Dendra2 
-(which are 26 kDa in size~\cite{Gurskaya2006EngineeringLight})
-would leak out of the brain ventricles over the relevant time spans
-and render the dynamics slower.
-It may also be the case that our model predicts faster
-transport because the Dendra2 diffusion
-coefficient we used (based on an experimental value
-\cite{GuraSadovsky2017MeasurementExpansion}) is too high.
-This could be because embryonic CSF has higher viscosity
-than the solution considered in the measurements, 
-or because the presence of proteins, nutrients and other solutes
-obstructs diffusive transport
-\cite{Bloomfield1998EffectsFluid, Einstein1905UberTeilchen, Cussler2009Diffusion:Systems}.
-Finally, an important difference
-is the three-dimensional nature of the computational model,
-while the experimental images only show 2D slices.
+on brain ventricular transport.}
+
+\subsection{Model validation}
+
+Our computational predictions and in vivo experimental measurements
+agree to a large extent. Examining any discrepancies in more detail
+indicates that the simulated transport dynamics are more rapid and
+results in higher total amounts of solute. Differences between
+experiments and simulations may relate to ventricular size, as we
+showed that modifying the ventricular geometry impacts solute
+distribution, and the ventricular size varies substantially in the
+control population at 2 dpf. In addition, differences may result from
+the definition of the photoconversion site, since the volume of this
+region determines the total amount of solute and thereby the rate of
+transport. Another source of discrepancy may relate to the
+permeability of the ventricular wall, which we considered as
+impermeable in our simulations. The neuroepithelium lining the walls
+of brain ventricles in 24 hour old zebrafish is permeable to dyes
+smaller than 70 kDa~\cite{Chang2012AnNeuroepithelium}.  If this is
+also the case at 2 dpf, Dendra2 (which are 26 kDa in
+size~\cite{Gurskaya2006EngineeringLight}) would leak out of the brain
+ventricles over the relevant time spans and render the dynamics
+slower.  It may also be the case that our model predicts faster
+transport because the Dendra2 diffusion coefficient we used (based on
+an experimental value \cite{GuraSadovsky2017MeasurementExpansion}) is
+too high. This could be because embryonic CSF has higher viscosity
+than the solution considered in the measurements, or because the
+presence of proteins, nutrients and other solutes obstructs diffusive
+transport \cite{Bloomfield1998EffectsFluid, Einstein1905UberTeilchen,
+  Cussler2009Diffusion:Systems}. Finally, an important difference is
+the three-dimensional nature of the computational model, while the
+experimental images only show 2D slices.
 
@@
 
-\subsection{Numerical approximation}
-When solving an advection-diffusion equation to
-simulate protein transport, we handled advective transport
+\subsection{Numerical considerations}
+When simulating solute transport, we handled the advective transport
 through the anterior/posterior boundaries
-(where cardiac pressure pulsations are imposed)
-with an approximate periodic boundary condition
-that conserves the total solute concentration.
-A possible improvement to this would be
-to consider a 3D-0D coupling of in- and outflow using
+(where cardiac pressure pulsations were imposed)
+via an approximate periodic boundary condition
+that conserved the total solute concentration.
+A possible improvement would be
+to consider a 3D-0D coupling of the in- and outflow using
 ordinary differential equations,
@@
 modeling~\cite{Brown2024AMechanics, Augustin2021ACirculation}.
-Alternatively, the beating cardiac motion could be modeled by ventricular wall deformation
-to avoid advective boundary fluxes\cite{Causemann2022HumanFramework,
+Alternatively, the beating cardiac motion could be modeled by ventricular wall deformation to avoid advective boundary fluxes\cite{Causemann2022HumanFramework,
 Kurtcuoglu2005ComputationalSystem, Kurtcuoglu2007ComputationalSylvius, Linninger2005PulsatileBrain}.
-
-The Brezzi-Douglas-Marini and discontinuous Galerkin scheme
+%
+We also remark that the Brezzi-Douglas-Marini and discontinuous Galerkin scheme
 $\mathrm{BDM}_1$-$\mathrm{DG}_0$
-we used to discretize the Stokes equations
+used to discretize the Stokes equations
 is computationally more expensive
-than \fixme{conventional methods} \miro{ the more commonly used discretizations} such as a
+than more commons discretizations such as 
 Taylor-Hood ($P_2-P_{1}$ elements)~\cite{Stenberg1990ErrorProblem} or lower-order enriched
 elements (e.g. MINI)~\cite{Brezzi2011MixedMethods}.
-Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
-than or equal to the integer $k$.
-We opted for the BDM-DG scheme because of its exactly-mass-conserving property;
-by the definition of the elements, the numerical approximation of
-the CSF velocity $\uu_h$ satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
-As a result $\normltwo{\nabla\cdot\uu_h}=0$ to within solver tolerances,
-an important property for the stability of the advection-diffusion
+%Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
+%than or equal to the integer $k$.
+However, we prefer the BDM-DG scheme because of its mass conservation properties: the numerical approximation of
+the CSF velocity $\uu_h$ satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}) point-wise, an important property for the stability of the advection-diffusion
 equation, especially in advection-dominated cases.
@@
 lets us impose the impermeability condition $\uu\cdot\nn=0$
-strongly, since the BDM elements control the normal component of the 
-velocity~\cite{Brezzi1985TwoProblems}.
-For elements where this is not the case (such as Taylor-Hood elements),
-the impermeability boundary condition must
-be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
-or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
-Bertoluzza2017BoundaryHemodynamics}, which affects
-convergence properties \miro{$<<$what do you mean here?} and increases problem complexity
-(see \Cref{subsec:appendixA1} for more details).
+directly~\cite{Brezzi1985TwoProblems} (see \Cref{subsec:appendixA1} for more details).
+%% For elements where this is not the case (such as Taylor-Hood elements),
+%% the impermeability boundary condition must
+%% be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
+%% or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
+%% Bertoluzza2017BoundaryHemodynamics}, which affects
+%% convergence properties \miro{$<<$what do you mean here?} and increases problem complexity
+%% (see \Cref{subsec:appendixA1} for more details).
 
@@
 due to reduced mixing following reduced
-ciliary motion. We demonstrated with
-simulations that solute concentrations,
+ciliary motion. We demonstrate that solute concentrations,
 and in turn CSF composition, 
@@
 such as the enlargement observed in hydrocephalus,
-would affect CSF composition.
+could affect CSF composition.
 Because CSF plays an important role in the regulation of solutes
@@
 are important considerations for future work.
-We hope our findings and the computational
-framework we have presented can help address
-such open questions in the future.
+%We hope our findings and the computational
+%framework we have presented can help address
+%such open questions in the future.
 

### 2025-04-08 paper/main.tex
update fig appendix, merge Miro edits

@@
 \date{\vspace{-2em}} % Remove space between affiliations and abstract
-
-\newcommand{\miro}[1]{{\color{cyan}#1}}
 
@@
 bidirectional tangential traction acting on parts of the ventricular wall
-(\Crefpanels{fig:fig1}{d}), with \miro{no-penetration condition at the walls}.
+(\Crefpanels{fig:fig1}{d}), with an impermeability condition at the walls.
 Simulations show that this traction alone
@@
 zebrafish larva (\emph{smh}) aligned with these observations.
-This further indicates that
+These simulations and experiments further indicate that
 transport from the middle to the posterior ventricle is
@@
 depends on cilia motility.
+Furthermore, our experimental results provide quantification
+of the impact of cilia motility
+on brain ventricular transport.
 Interestingly, Yoshida~\emph{et al.} observed a drastic reduction
-in CSF mixing in specific regions of the brain
-ventricles when simulating reduced cilia motility~\cite{Yoshida2022EffectVentricles}.
-\fixme{Our experimental results provide not only confidence
-in the predictive ability of our computational model,
-but also quantify the impact of cilia motility
-on brain ventricular transport.}
+in CSF mixing in specific regions of the human brain
+ventricles when simulating reduced cilia motility~\cite{Yoshida2022EffectVentricles},
+an observation that compares well with our findings.
 
@@
 away~\cite{Siyahhan2014FlowVentricles}.
+Their simulation results suggest that cilia only contribute to
+near-wall flow dynamics, which contrasts our results in which
+the cilia induce large-scale flow. This is a consequence of the 
+scale of the cilia and the difference in ventricular size
+between humans and zebrafish.
 In a cilia array of thickness $\delta = 15$ \textmu m,
@@
 our cilia stress corresponds to a maximum force density of
-$f_c=507 \ \mathrm{N/m^3}$.
+$f_c=507 \ \mathrm{N/m^3}$, similar to the value
+Siyahhan~\emph{et al.} used~\cite{Siyahhan2014FlowVentricles}.
 For further comparison, Thouvenin~\emph{et al.}
@@
 it is interesting to note the above similarity 
-in cilia force estimates.
+in cilia force estimates, despite the variety in application.
 
@@
 \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xUAS:Signal-Dendra2})
-adult animals, as described by D'Gama~\emph{et al.}~\cite{DGama2024Cilia-mediatedBrain}. \miro{$<<$ undef ref here}
+adult animals, as described by D'Gama~\emph{et al.}~\cite{DGama2025MotileBrain}.
 Controls consisted of either wild-type (\emph{smh}\textsuperscript{+/+})
@@
 The element combination $\mathrm{BDM}_1$--$\mathrm{DG}_{0}$ yields a non-conforming
-discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}. \miro{In particular,
-  with BDM only the normal component of the velocity is continuous.}
+discretization scheme for the Stokes equations~\cite{Stenberg1989SomeEquations}. 
+In particular, with BDM only the normal component of the velocity is continuous.
 Continuity in tangential velocities on interior facets
@@
 \subsection{Numerical approximation of the advection-diffusion equation}\label{subsec:num_approx_adv_diff}
-\miro{The advection-diffusion equation (\Cref{eq:adv_diff_strong}) is discretized in
-space with quadratic DG elements using symmetric interior penalty DG method~\cite{Arnold1982AnElements}.
+The advection-diffusion equation (\Cref{eq:adv_diff_strong}) is discretized in
+space with quadratic DG elements using a symmetric interior penalty DG method~\cite{Arnold1982AnElements}.
 The scheme was chosen due to its favorable mass 
-conservation properties}. At each timestep the total number of degrees of freedom 
+conservation properties. At each timestep the total number of degrees of freedom 
 is 1 415 120. In time, the equation is discretized with the second-order backward
@@
 $\vv\in\mathbf{H}^1(\Omega)$ is understood as $\vv(\cdot, t)\in \mathbf{H}^1(\Omega)$ for all
-$t>0$. Similar convention is applied also when discussing advection-diffusion equation in \Cref{subsec:adv_diff_eq_weak_form}.
+$t>0$. Similar convention is applied also when discussing the advection-diffusion equation in \Cref{subsec:adv_diff_eq_weak_form}.
 }
@@
 
-\miro{The elements of $\VV_h$ only ensure by construction the continuity of normal components of $\uu_h$.
+The elements of $\VV_h$ only ensure by construction the continuity of normal components of $\uu_h$.
 Continuity of the tangential components of $\uu_h$ on interior facets of
@@
 the discrete weak form (\Cref{eq:no_stabilization_abstract_discrete_weak_form_modelC}).
-Specifically}, we apply the stabilization outlined by Hong~\emph{et al.}~\cite{Hong2016AEquations}.
+Specifically, we apply the stabilization outlined by Hong~\emph{et al.}~\cite{Hong2016AEquations}.
 First, we define the average and jump operators, respectively, as
@@
 across interior facets, where the penalty parameter $\gamma>0$ must be chosen large enough
-to achieve stability. \miro{For appropriate convergence, the penalization term
-includes a mesh-dependent scaling. In this work we choose it as the average of the cell diameter of neighboring mesh cells,
-with $h$ defined as the maximal distance between two points in a cell~\cite{Nitsche1971UberSind}.}
+to achieve stability. For appropriate convergence, the penalization term
+includes a mesh-dependent scaling. In this work,
+we choose it as the average of the cell diameter of neighboring mesh cells,
+with $h$ defined as the maximal distance between two points in a cell~\cite{Nitsche1971UberSind}.
 The other two terms
@@
 \end{equation}
-\miro{
+
 We define the approximation of the infinity norm of a finite element function
@@
 \end{equation*}
-Here $\psi_i$ are the basis functions and $\phi_i$ are the degrees of freedom defined as point evaluations}
+Here $\psi_i$ are the basis functions and $\phi_i$ are the degrees of freedom defined as point evaluations.
 
@@
 
-For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$, \miro{$u_h=\sqrt{\uu_h\cdot\uu_h}$}.
+For all meshes, we report the maximum discrete velocity magnitude $\normlinf{u_h}$, with $u_h=\sqrt{\uu_h\cdot\uu_h}$.
 We also report $\normlinf{u_h}$ scaled by the total force $F=\intGc{\sqrt{\btau\cdot \btau}}$
@@
 diencephalic ventricle. Frequency of image acquisition was 20.22 Hz.
-The collected data constituted $x$ and $y$ positions of the particles at every time
-instant of image acquisition. The velocities $u_x$ and $u_y$ were determined by
-calculating the change in positions $\Delta x$ and $\Delta y$ relative to the change
+The collected data constituted $x$ (rostrocaudal axis) and $z$ (dorsoventral axis) positions of the particles at every time
+instant of image acquisition. The velocities $u_x$ and $u_z$ were determined by
+calculating the change in positions $\Delta x$ and $\Delta z$ relative to the change
 in time $\Delta t$ between two subsequent images, $\Delta t$ being equal to the
@@
 Mean velocities $\overline{u}_x$~(\Crefpanels{fig:particle_tracking_data}{a}) and
-$\overline{u}_y$~(\Crefpanels{fig:particle_tracking_data}{b}),
+$\overline{u}_z$~(\Crefpanels{fig:particle_tracking_data}{b}),
 which serve as a quantification of particle drift, were calculated
@@
 Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
-0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s.
+0.26 \textmu m/s and the mean of $\overline{u}_z$ was 0.08 \textmu m/s.
 The maximum mean velocities
 in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for
-$\overline{u}_x$ and $\overline{u}_y$,
+$\overline{u}_x$ and $\overline{u}_z$,
 respectively. We used the cardiac-induced/no-cilia flow model to tune the
@@
 \begin{figure}[H]
-    \begin{minipage}[t]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
-    \end{minipage}
-    \begin{minipage}[t]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
-    \end{minipage} 
+    \centering
+    \includegraphics[width=\textwidth]{graphics/figure7.png}
     \caption{Particle tracking data. Mean velocities in
-    the $x$ (\textbf{a.}) and $y$ (\textbf{b.}) directions of the particles tracked.
-    The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
+    the $x$ (\textbf{a}) and $z$ (\textbf{b})
+    directions of the particles tracked.
+    The dashed horizontal lines designate zero.}\label{fig:particle_tracking_data}
 \end{figure}

### 2025-04-10 paper/main.tex
update cylinder convergence rates using hmin

@@
 bidirectional tangential traction acting on parts of the ventricular wall
-(\Crefpanels{fig:fig1}{d}), with an impermeability condition at the walls.
+(\Crefpanels{fig:fig1}{d}), with an impermeability condition (no normal flow) at the walls.
 Simulations show that this traction alone
@@
     \centering
-    \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
+    \includegraphics[width=0.96\textwidth]{graphics/figure4_compare_control_mutant.png}
     \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
+    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
+    \textbf{b.} The four modified versions of the computational geometry. Compared
+    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
+    and 9.4\%.
+    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
+    in the six regions of interest (ROIs).
+    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
+    and the total force applied, calculated with \Cref{eq:tangential_force_calculation}.
+    In each region, the force $F_{\mathrm{original}}$ 
+    applied on the original mesh is the baseline of 100\%,
+    to which the forces $F_i$ of the other mesh versions are compared, where $i$ denotes
+    the modification scenario.
+    The bars for the four alternative scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
+    \label{fig:fig6}
+\end{figure}
+
 Constricting the anterior-middle duct
@@
 individual zebrafish ventricles.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
-    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
-    \textbf{b.} The four modified versions of the computational geometry. Compared
-    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
-    and 9.4\%.
-    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
-    in the six regions of interest (ROIs).
-    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
-    and the total force applied, calculated with \Cref{eq:tangential_force_calculation}.
-    In each region, the force $F_{\mathrm{original}}$ 
-    applied on the original mesh is the baseline of 100\%,
-    to which the forces $F_i$ of the other mesh versions are compared, where $i$ denotes
-    the modification scenario.
-    The bars for the four alternative scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
-    \label{fig:fig6}
-\end{figure}
 
@@
 To normalize the data with respect to photoconversion efficiency, the
-$\Delta F$ curves for all ROIs were divided by the $\Delta F$ values
+$\Delta F$ values for all ROIs were divided by the $\Delta F$ values
 obtained for ROI 1 at the end of the experiment,
@@
   c(\xx, t)=\frac{\log{(1+t/a)}}{\log{(1+T/a)}},
-  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t > 0.
+  \quad \xx \in \Omega_{\mathrm{pc}}, \quad t\in(0, T].
 \label{eq:photoconversion_curve}
@@
 In order to impose a smooth initial condition, we initially solve the diffusion equation
-\begin{equation}\label{eq:cinit}
-  \begin{aligned}
-    &\pdifft{c} = \Tilde{D}\nabla^2 c \quad \text{in } \Omega\times(0, 2\Delta t]\\
-      &c(\xx, t=0) = 0\quad\text{ in }\Omega
-  \end{aligned}\
-\end{equation}
+\begin{alignat*}{2}
+\pdifft{c} &= \Tilde{D}\nabla^2 c \quad &&\text{in } \Omega\times(0, 2\Delta t]\\
+    c(\xx, t=0) &= 0 \quad&&\text{in }\Omega
+\end{alignat*}
 with an increased diffusion coefficient $\Tilde{D}=D\times 10^{5}$ for two timesteps.
@@
 A cylinder geometry meshed with varying degrees of refinement was used to
-perform convergence analysis of the numerical methods used to solve the Stokes equations.
+perform convergence analysis of the numerical method used to solve the Stokes equations.
 The cylinder had unit length and a diameter of one half length unit.
+For each mesh refinement, the edge lengths were approximately halved.
+Since the refinement was not uniform, we used the ratio of the minimal
+edge lengths $h_{\mathrm{min}, k}/h_{\mathrm{min}, k+1}$ between two 
+successive refinements when calculating the convergence rate using
+\Cref{eq:convergence_order_estimate}.
 For the analysis, we used tangential traction boundary conditions on all
@@
     with~\Cref{eq:convergence_order_estimate} are given
-    in parentheses. The coarsest mesh had a mesh size $h_0$,
-    and for every mesh refinement the mesh size $h$ was halved.}\label{tab:cylinder_error_rates}
+    in parentheses.}\label{tab:cylinder_error_rates}
     \begin{tabular}{cc|ccccc}
         \toprule
-        $h/h_0$ & \# dofs &
+        \# cells & \# dofs &
         $\normltwovec{\uu_h - \uu_{\mathrm{ex}}}$
@@
         \midrule 
-        1    & 8652    & \num{2.3e-02}  (--)  & \num{4.3e-01}   (--)  & \num{5.6e-01}  (--)  & \num{2.4e-02}  (--)  & \num{1.4e-07} \\  
-        1/2  & 41190   & \num{9.3e-03} (1.30) & \num{2.8e-01}  (0.61) & \num{3.9e-01} (0.53) & \num{5.0e-03} (2.25) & \num{2.8e-08} \\  
-        1/4  & 255016  & \num{3.5e-03} (1.42) & \num{1.4e-01}  (1.00) & \num{2.1e-01} (0.85) & \num{1.4e-03} (1.83) & \num{7.3e-11} \\     
-        1/8  & 1855337 & \num{1.3e-03} (1.46) & \num{6.9e-02}  (1.03) & \num{1.1e-01} (0.92) & \num{6.7e-04} (1.08) & \num{1.5e-10} \\   
+        1140    & 8652    & \num{2.3e-02}  (--)  & \num{4.3e-01}   (--)  & \num{5.6e-01}  (--)  & \num{2.4e-02}  (--)  & \num{1.4e-07} \\  
+        5568    & 41190   & \num{9.3e-03} (1.59) & \num{2.8e-01}  (0.75) & \num{3.9e-01} (0.65) & \num{5.0e-03} (2.75) & \num{2.8e-08} \\  
+        35311   & 255016  & \num{3.5e-03} (1.58) & \num{1.4e-01}  (1.11) & \num{2.1e-01} (0.95) & \num{1.4e-03} (2.03) & \num{7.3e-11} \\     
+        260717  & 1855337 & \num{1.3e-03} (1.59) & \num{6.9e-02}  (1.12) & \num{1.1e-01} (1.00) & \num{6.7e-04} (1.18) & \num{1.5e-10} \\   
         \bottomrule
@@
 The $\mathrm{BDM}_1$-$\mathrm{DG}_0$ scheme that we employ for the Stokes equations
-is computationally more expensive than a more conventional approach based on
+is computationally more expensive than more common approaches based on
 e.g. Taylor-Hood discretization~\cite{Stenberg1990ErrorProblem}
 ($P_2-P_1$ elements) or lower-order enriched
-elements~\cite{Brezzi2011MixedMethods},
-such as the MINI-element.
+elements (e.g. MINI)~\cite{Brezzi2011MixedMethods}.
 We opted for the BDM-DG scheme because of its exactly-mass-conserving property,

### 2025-04-10 paper/main.tex
rm video

@@
 the anterior and middle ventricles and directional flow in the
-posterior ventricle (\Crefpanels{fig:fig1}{h--j}, \fixme{Supplementary
-  video 1}). These characteristic patterns suggest that the flow in
+posterior ventricle (\Crefpanels{fig:fig1}{h--j}).
+These characteristic patterns suggest that the flow in
 the anterior and middle ventricles is primarily driven by the motile

### 2025-04-11 paper/main.tex
Results changes and Discussion intro

@@
 
-Proteins, neurotransmitters and other molecular substances
+Proteins, neurotransmitters and other molecules
 intrinsically diffuse within the brain ventricles, but are also
 advected by the flow of CSF. A natural question is which of these
-mechanisms that dominate for any given type of solute. To address this
+mechanisms dominates for any given type of solute. To address this
 question, we simulate the distribution and evolution of three
-different diffusing solutes injected within a region of interest (ROI 1) in the
-dorsal region of the middle ventricle (\Crefpanels{fig:fig2}{a}),
+different solutes injected within a region of interest (ROI 1) in the
+dorsal region of the middle ventricle (\Crefpanels{fig:fig2}{a}) and
 subject to the CSF flow induced by motile cilia and cardiac pressure
@@
 Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}.  As observed both experimentally and
-computationally, absence of motile cilia alters CSF flow patterns.  We
+computationally, absence of motile cilia alters CSF flow patterns
+\Crefpanels{fig:fig1}{g}~\cite{Olstad2019CiliaryDevelopment}. We
 next investigate the implications of these changes on brain ventricular
@@
 predicted mean concentrations in ROI 5 deviate between the two
-scenarios, which is not the case in the experiments. Altogether, our
-findings identify that, for smaller proteins such as Dendra2,
+scenarios, while in the experiments the difference in
+fluorescence intensities is not significant.
+Altogether, our findings identify that,
+for smaller proteins such as Dendra2,
 diffusion plays an important role for solute movement to regions
@@
 results against experimental measurements. Our computational framework
-can be adapted to other ventricular systems, once the flow parameters
-of such are adequately resolved. Here, we assumed that
+can be adapted to other ventricular systems, once their flow parameters
+are adequately resolved. Here, we assumed that
 intraventricular CSF flow was governed by the Stokes equations. By

### 2025-04-11 paper/main.tex
abstract

@@
 \begin{abstract}
-Cerebrospinal fluid (CSF) is integral to brain function, as the fluid
-provides mechanical support for the brain and the flow of CSF helps
+Cerebrospinal fluid (CSF) is integral to brain function. CSF
+provides mechanical support for the brain and helps
 distribute nutrients, neurotransmitters and metabolites throughout the
-central nervous system. CSF flow is partly driven by beating of motile
-cilia, hair-like structures that line the ependymal cell layer of the
+central nervous system. CSF flow is driven by several processes,
+including the beating of motile cilia located on the
 walls of the brain ventricles. Despite the physiological importance of
-CSF flow, the underlying mechanisms of cilia-mediated flow and
-transport in the brain ventricles remain yet to be comprehensively
-resolved. This study analyzes and evaluates the role of motile cilia
-in brain ventricular CSF flow and transport. The geometry of the
-zebrafish larval brain ventricles, for which detailed knowledge of
-cilia properties and CSF motion velocities and frequencies exists, was
-used to develop finite element methods for modelling flow and
-transport. The computational model is validated by in vivo experiments
+CSF, the underlying mechanisms of CSF flow and solute transport
+in the brain ventricles remain to be comprehensively
+resolved. This study analyzes and evaluates specifically
+the role of motile cilia in CSF flow and transport. 
+We developed finite element methods for modeling flow
+and transport using the geometry of the zebrafish larval
+brain ventricles, for which we have detailed knowledge of
+cilia properties and CSF motion.
+The computational model is validated by in vivo experiments
 that monitor transport of a photoconvertible protein secreted in the

### 2025-04-11 paper/main.tex
introduction

@@
 
-% I1: What is the problem - from big picture to our precise topic - why is it interesting?
 Brain development and function depend on numerous regulatory
 processes, including the flow of cerebrospinal fluid
-(CSF)~\cite{fame2020emergence}. Produced mostly by the choroid
-plexus and partly by brain interstitial fluid,
-CSF is a clear liquid that flows through the ventricular system and subarachnoid
-space~\cite{Brodal2016, Damkier2013}. By transporting growth factors, nutrients, neurotransmitters
+(CSF)~\cite{fame2020emergence}. Produced predominantly by the choroid
+plexus, CSF is a clear liquid that flows through the ventricular system and subarachnoid
+space~\cite{Brodal2016, Damkier2013, Wichmann2022Overview}.
+By transporting growth factors, nutrients, neurotransmitters
 and metabolites, as well as removing waste products, CSF regulates
 brain development and homeostasis~\cite{Ringers2020Role, fame2020emergence, del2010ependymal}.
-Disruption of the CSF circulation is detrimental to brain health and disturbs
-cognitive and motor functions~\cite{Johanson2008}.
-Pathological CSF flow may also lead to
-disorders such as hydrocephalus, where accumulation of
-CSF often requires emergency surgical
-treatment~\cite{duy2022rethinking, kahle2024paediatric, wallmeier2022role},
-but for which there is little agreement on optimal treatments~\cite{flannery2014pediatric}.
-
-% I2: What do we know about the problem and the topic?
+Disruption of CSF circulation is detrimental to brain health and disturbs
+cognitive and motor functions~\cite{Johanson2008},
+and accumulation of CSF leads to hydrocephalus,
+a disorder often requiring emergency surgical treatment.
+\cite{duy2022rethinking, kahle2024paediatric, wallmeier2022role,
+flannery2014pediatric}
+
 The flow of CSF in the ventricular system is driven by multiple
-physiological processes, including via the beating motion of motile
+physiological processes, including the beating motion of motile
 cilia, CSF secretion by the choroid plexus, and pulsatile pressure
@@
 Kurtcuoglu2005ComputationalSystem, Olstad2019CiliaryDevelopment,
-  macaulay2022cerebrospinal, mestre2018flow}.  Cilia are hair-like
-structures found in a vast diversity of biological organisms and in
+macaulay2022cerebrospinal, mestre2018flow, Williams2023NeuralActivity}. 
+Cilia are hair-like structures found in a vast diversity of
+biological organisms and in
 several human organs, including the brain~\cite{DGama2025MotileBrain,
@@
 Reiten2017Motile-Cilia-MediatedComputations,
-  Thouvenin2020OriginCanal}.  The ventricular surface of the brain,
-known as the ependyma, is lined by motile cilia that beat in a
+Thouvenin2020OriginCanal}. Notably, motile cilia
+are found on the ventricular surface of the brain,
+known as the ependyma, and beat in a
 coordinated pattern at frequencies of 10--40 Hz to mediate fluid
@@
 microscopic size, ranging from 5 to 15 microns, cilia contribute
-primarily to flow near the ependyma in the human
+primarily to flow near the ependyma in the
 brain~\cite{Siyahhan2014FlowVentricles, Olstad2019CiliaryDevelopment,
@@
 cardiac, respiratory and delta waves at lower frequencies induce
-pulsatile flow at the larger scales in the brain ventricular system,
-subarachnoid space, and subarachnoid perivascular
+pulsatile flow at larger scales in the brain ventricular system,
+subarachnoid space, and perivascular
 spaces~\cite{Vinje2019RespiratoryMeasurements, eide2024functional,
@@
 Jeong2022MeasurementTelencephalon, Olstad2019CiliaryDevelopment, spassky2013motile, DGama2021Diversity},
-as compared to other fluid dynamic processes in the brain that are slower and span larger
+as compared to other slower fluid dynamic processes that span larger
 spatial scales~\cite{Vinje2019RespiratoryMeasurements, eide2024functional, fultz2019coupled, mestre2018flow},
-make cilia difficult to monitor in vivo in humans.
+make cilia difficult to monitor in vivo in the rodent and human brain.
 Until now, most studies have analyzed one physical mechanism at a time, especially in mammals.
@@
 Others considered cilia-mediated flow in the brain~\cite{Siyahhan2014FlowVentricles,
-Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal}, but also 
-other applications such as ciliary transport of mucous and particles in
+Yoshida2022EffectVentricles, Salman2022ComputationalEmbryo, Thouvenin2020OriginCanal},
+and other applications such as ciliary transport of mucous and particles in
 airways~\cite{Fulford1986Muco-ciliaryLung, Ramirez-SanJuan2020Multi-scaleArrays, roth2025structure},

### 2025-04-11 paper/main.tex
conclusion and outlook

@@
 is computationally more expensive
-than more commons discretizations such as 
+than more common discretizations such as 
 Taylor-Hood ($P_2-P_{1}$ elements)~\cite{Stenberg1990ErrorProblem} or lower-order enriched
 elements (e.g. MINI)~\cite{Brezzi2011MixedMethods}.
-%Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
-%than or equal to the integer $k$.
 However, we prefer the BDM-DG scheme because of its mass conservation properties: the numerical approximation of
@@
 directly~\cite{Brezzi1985TwoProblems} (see \Cref{subsec:appendixA1} for more details).
-%% For elements where this is not the case (such as Taylor-Hood elements),
-%% the impermeability boundary condition must
-%% be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
-%% or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
-%% Bertoluzza2017BoundaryHemodynamics}, which affects
-%% convergence properties \miro{$<<$what do you mean here?} and increases problem complexity
-%% (see \Cref{subsec:appendixA1} for more details).
-
-\subsection{Outlook}
-The flow generated by ciliary motion
-in zebrafish larval brain ventricles
-is of the scale of the geometry~\cite{Olstad2019CiliaryDevelopment},
-while in large brains such as the human brain, ciliary beating 
-contributes to flow proximal to the ventricular walls
-\cite{Siyahhan2014FlowVentricles}.
-The cilia may play an important role in regulating the
-amount of substances like extracellular vesicles close to the ventricular walls,
+
+\subsection{Conclusion and outlook}
+Altogether, we have shown that the flow
+generated by ciliary motion in the zebrafish larval brain ventricles
+is of the scale of the geometry~\cite{Olstad2019CiliaryDevelopment}.
+In contrast, one can expect that in large brains such as the
+human brain, ciliary beating contributes only to flow proximal
+to the ventricular walls\cite{Siyahhan2014FlowVentricles}.
+Nevertheless, the cilia may still play an important role in regulating the
+amount of substances, especially extracellular vesicles,
+close to the ventricular walls,
 similar to coral reefs where cilia are primary regulators of
 oxygen amounts at the coral surface~\cite{Pacherres2022CiliaryProduction}.
-Cilia indeed regulate nodal flow at early
-developmental stages of the brain~\cite{Hirokawa2006NodalAsymmetry},
-and the discovery of a cilia-driven flow network
-in rodent brains suggests such selective
+Notably, the discovery of a cilia-driven flow network
+in rodent brains strongly supports such selective
 brain ventricular transport~\cite{Faubel2016Cilia-basedVentricles}.
-As the CSF flows through the central nervous system,
-the system may be affected by the changes in CSF composition
-due to reduced mixing following reduced
-ciliary motion. We demonstrate that solute concentrations,
-and in turn CSF composition, 
-are affected by ventricular
-geometry changes. A 10\% difference in volume
+Our results also revealed that solute concentrations are affected
+by ventricular geometry changes.
+In fact, a 9\% difference in volume
 had a noticeable impact on solute transport,
-showing that pathological ventricular volume changes,
+suggesting that pathological ventricular volume changes,
 such as the enlargement observed in hydrocephalus,
-could affect CSF composition.
+could affect CSF distribution and composition.
 Because CSF plays an important role in the regulation of solutes
@@
 are important considerations for future work.
-%We hope our findings and the computational
-%framework we have presented can help address
-%such open questions in the future.
 

### 2025-04-13 paper/main.tex
add zenodo repo link, align figures

@@
     \centering
-    \includegraphics[width=\linewidth]{graphics/figure1.png}
+    \includegraphics[width=\textwidth]{graphics/figure1.png}
     \caption{
@@
 
-\begin{figure}%[H]
+\begin{figure}
     \centering
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.975\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
+    \includegraphics[width=\textwidth]{graphics/figure3_compare_experiments_and_simulations.png}
     \caption{
@@
     Bold lines are mean values of the cohort ($n=8$) and shaded regions cover
-    one standard deviation errors in the mean.
+    one standard deviation.
     \textbf{b.} Mean concentration $\cbar(t)$ in each ROI in a
-    simulation of Dendra2 protein transport with
+    simulation of Dendra2 transport with
     the diffusion coefficient $D_3$.
@@
     a transport simulation with diffusion coefficient $D_3$.
-    We have excluded the posterior-most regions of the geometries,
-    because the values of $\Delta F$ and $\cbar$ never exceeded the threshold
+    The posterior-most regions of the geometries are excluded,
+    because $\Delta F$ and $\cbar$ never exceeded the threshold
     value of 0.25 in these regions. Scale bars 50 \textmu m.}
@@
 while the cilia affect the downstream mean concentrations.
-\begin{figure}[H]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.96\textwidth]{graphics/figure4_compare_control_mutant.png}
+    \includegraphics[width=\textwidth]{graphics/figure4_compare_control_mutant.png}
     \caption{\textbf{a.} Relative change in fluorescence intensity $\Delta F(t)$
@@
 (ROI 5), and less solute spreads towards the posterior ventricle (ROI 6).
-\begin{figure}[H]
+\begin{figure}[!ht]
     \centering
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
-    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
-    \textbf{b.} The four modified versions of the computational geometry. Compared
-    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
-    and 9.4\%.
-    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
-    in the six regions of interest (ROIs).
-    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
-    and the total force applied, calculated with \Cref{eq:tangential_force_calculation}.
-    In each region, the force $F_{\mathrm{original}}$ 
-    applied on the original mesh is the baseline of 100\%,
-    to which the forces $F_i$ of the other mesh versions are compared, where $i$ denotes
-    the modification scenario.
-    The bars for the four alternative scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
-    \label{fig:fig6}
-\end{figure}
-
 Constricting the anterior-middle duct
@@
 individual zebrafish ventricles.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{graphics/figure6_compare_modified_geometries.png}
+    \caption{\textbf{a.} The original computational mesh of the ventricular geometry.
+    \textbf{b.} The four modified versions of the computational geometry. Compared
+    to the original mesh, the volumes of the deformed meshes are reduced by 3.9\%, 4.1\%, 1.4\% 
+    and 9.4\%.
+    \textbf{c.} Mean concentration $\cbar(t)$ simulated with the original and modified geometries
+    in the six regions of interest (ROIs).
+    \textbf{d.} A comparison of the tangential cilia force in the three cilia regions
+    and the total force applied, calculated with \Cref{eq:tangential_force_calculation}.
+    In each region, the force $F_{\mathrm{original}}$ 
+    applied on the original mesh is the baseline of 100\%,
+    to which the forces $F_i$ of the other mesh versions are compared, where $i$ denotes
+    the modification scenario.
+    The bars for the four alternative scenarios display $F_i/F_{\mathrm{original}}\times 100\%$.}
+    \label{fig:fig6}
+\end{figure}
 
@@
 The image data analysis was performed in MATLAB and the codes are
-openly available~\fixme{\cite{zenodo-link-to-all-code}}.  The
+openly available~\cite{Herlyng2025Zenodo}.  The
 photoconverted channel was aligned to correct for drift in $x,y$
@@
 The simulation code is openly
-available\fixme{~\cite{zenodo-link-to-all-code}}.
+available~\cite{Herlyng2025Zenodo}.
 A direct solver using MUMPS~\cite{Amestoy2011Mumps} is used to solve the
@@
 \noindent \textbf{Data Availability Statement} \par
-\noindent The data and model implementations presented in this paper are
-openly available at \fixme{REPO-LINK}.
+\noindent The software and data used and presented in this paper are
+openly available\cite{Herlyng2025Zenodo}.
 
@@
     \caption{Particle tracking data. Mean velocities in
-    the $x$ (\textbf{a}) and $z$ (\textbf{b})
+    along the rostrocaudal axis ($x$ axis, \textbf{a})
+    and along the dorsoventral axis ($z$ axis, \textbf{b})
     directions of the particles tracked.

### 2025-04-14 paper/main.tex
fix sine curve plot annotation

@@
 the anterior and middle ventricles and directional flow in the
-posterior ventricle (\Crefpanels{fig:fig1}{h--j}).
+posterior ventricle (\Crefpanels{fig:fig1}{h--j},
+\href{https://doi.org/10.5281/zenodo.15194757}{Supplementary Video 1}).
 These characteristic patterns suggest that the flow in
@@
 converts Dendra2 from a green- to a red-emitting fluorescent
-protein. To quantify the transport of photoconverted proteins, we
+protein (\href{https://doi.org/10.5281/zenodo.15194757}{Supplementary Video 2}).
+To quantify the transport of photoconverted proteins, we
 measured and calculated the change in fluorescence intensity $\Delta F(t)
@@
 
-\subsection{Conclusion and outlook}
+\subsection{Outlook}
 Altogether, we have shown that the flow
@@
 \medskip
-\noindent \textbf{Data Availability Statement} \par
+\noindent \textbf{Data availability statement} \par
 \noindent The software and data used and presented in this paper are
@@
 \medskip
-\noindent \textbf{Conflict of Interest Disclosure} \par
+\noindent \textbf{Conflict of interest disclosure} \par
 \noindent The authors declare no conflicts of interest.
@@
 % Bibliography
-\bibliographystyle{MSP}
+\bibliographystyle{ieeetr}
 \bibliography{ref}
@@
 \appendix
-\section{Supplementary Theory}
+\section{Supplementary theory and numerical methods}
 \subsection{Weak formulation of the Stokes equations}\label{subsec:appendixA1}

### 2025-04-14 src/plot_sine_curve.py

@@ -45,7 +45,7 @@ ys = [y1, y2, y3]
 bfont = {'family': 'Liberation Serif',
          'size'  : 50,
          'fontweight' : 'bold'}
-ax.text(xs[0], ys[0]*1.125, 'f, h', fontdict=bfont)
+ax.text(xs[0], ys[0]*1.125, 'g, h', fontdict=bfont)
 ax.text(xs[1]*1.025, ys[1], 'i', fontdict=bfont)
 ax.text(xs[2], ys[2]*0.85, 'j', fontdict=bfont)
 

### 2025-04-15 paper/main.tex
final paper version, new .bst

@@
 
-% Why? (Interesting point #1. However, we do not know aspect #2. 
-% How? (We therefore ...)
-% What ...
-
 In vivo particle tracking reveals characteristic CSF flow patterns in
@@
 posterior ventricle (\Crefpanels{fig:fig1}{h--j},
-\href{https://doi.org/10.5281/zenodo.15194757}{Supplementary Video 1}).
+\href{https://doi.org/10.5281/zenodo.15194757}{Supplementary Video S1}).
 These characteristic patterns suggest that the flow in
@@
 extracellular vesicles, the advective transport by the CSF dominates diffusion: the
-CSF flow structures carry over into the concentration field,
+CSF flow structures are evident in the concentration field,
 indicating that transport along the streamlines is more rapid than the
@@
 balance between diffusion and advection shifts with increasing
-diffusion coefficient as the solute spreads more uniformly throughout
+diffusion coefficient as solute spreads more uniformly throughout
 the ventricular geometry (\Crefpanels{fig:fig2}{b--d}). Notably, the
 smaller solutes with higher diffusion coefficients spread more quickly
-to distal regions. Computing Péclet numbers, we find that
+to distal regions. Computing Péclet numbers, we find 
 $\mathrm{Pe}_1=664$, $\mathrm{Pe}_2=25$ and $\mathrm{Pe}_3=13$ for
@@
 converts Dendra2 from a green- to a red-emitting fluorescent
-protein (\href{https://doi.org/10.5281/zenodo.15194757}{Supplementary Video 2}).
+protein (\href{https://doi.org/10.5281/zenodo.15194757}{Supplementary Video S2}).
 To quantify the transport of photoconverted proteins, we
@@
     \caption{\textbf{a.} The three separate cilia regions for which cilia paralysis is simulated
-    by imposing a zero tangential traction boundary condition in the respective region.
-    \textbf{b.} The total tangential force applied to the boundary with the tangential traction
-    boundary condition in each of the three separate ciliated regions, as well as the total force
+    by removing the cilia tangential traction boundary condition in the respective region.
+    \textbf{b.} The total force applied to the boundary with the cilia traction
+    in each of the three separate ciliated regions, and the total force
     (the sum of the three regions), calculated with \Cref{eq:tangential_force_calculation}. 
     \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
-    paralysis scenarios considered. The region named in the legend is the region
-    where we modify the cilia tangential traction boundary condition to a free-slip condition
-    in the CSF flow model.}
+    paralysis scenarios. The legend refers to the region where cilia are removed.}
     \label{fig:fig5}
@@
 
-The numerical solution schemes for the Stokes equations and the
-advection-diffusion equation were implemented and solved numerically with
-DOLFINx with petsc4py as linear algebra backend
-\cite{dolfinx2023preprint, Dalcin2011ParallelPython}.
+The numerical methods for the Stokes equations and the
+advection-diffusion equation were implemented and solved
+with DOLFINx\cite{dolfinx2023preprint}.
 The simulation code is openly
@@
 \noindent \textbf{Data availability statement} \par
-\noindent The software and data used and presented in this paper are
-openly available\cite{Herlyng2025Zenodo}.
+\noindent The software and data used and presented in this paper,
+as well as the supplementary videos, are
+archived on Zenodo and openly available at
+\href{https://doi.org/10.5281/zenodo.15194757}{https://doi.org/10.5281/zenodo.15194757}\cite{Herlyng2025Zenodo}.
 
@@
 % Bibliography
-\bibliographystyle{ieeetr}
+\bibliographystyle{unsrturl}
 \bibliography{ref}

### 2025-04-15 paper/main.tex
add ref

@@
 monitoring photoconverted Dendra2 signal in control zebrafish and
-motile-cilia mutant \emph{schmalhans} (\emph{smh}) zebrafish.  In ROIs
-2 and 4, which quantify Dendra2 distribution downstream of the
+motile-cilia mutant \emph{schmalhans} (\emph{smh}, \emph{ccdc103}) zebrafish\cite{Panizzi2012Mutations}.
+In ROIs 2 and 4, which quantify Dendra2 distribution downstream of the
 photoconversion site, we observed a slower increase of fluorescence

### 2025-06-25 paper/main_v1.tex
diff, original manuscript stored in main_v1

--- 2025-04-15 paper/main.tex
@@
 We developed finite element methods for modeling flow
-and transport using the geometry of the zebrafish larval
+and transport using the geometry of embryonic zebrafish
 brain ventricles, for which we have detailed knowledge of
@@
 them numerically with finite element methods to compute flow patterns and
-solute concentration dynamics. A geometry representing the zebrafish larval brain ventricles
+solute concentration dynamics. A geometry representing the embryonic zebrafish brain ventricles
 was used, for which we have detailed knowledge of cilia properties and CSF motion velocities
@@
 In vivo particle tracking reveals characteristic CSF flow patterns in
-zebrafish larval brain ventricles
+embryonic zebrafish brain ventricles
 (\Crefpanels{fig:fig1}{a--c})~\cite{Olstad2019CiliaryDevelopment}.
@@
 To validate the model predictions, we performed photoconversion
-experiments in transgenic zebrafish larvae expressing the secreted
+experiments in transgenic zebrafish embryos expressing the secreted
 Dendra2 in their brain ventricles. The approach is inspired by earlier work
@@
     \textbf{c.} Time to $\Delta F(t)$ reaches a threshold value of 0.25 in
-    one representative zebrafish larva.
+    one representative zebrafish embryo.
     \textbf{d.} Time to $\cbar(t)$ reaches a threshold value of 0.25 for
@@
 We previously characterized three distinct ciliated cell lineages in
-the zebrafish larval brain~\cite{Olstad2019CiliaryDevelopment,
+the embryonic zebrafish brain~\cite{Olstad2019CiliaryDevelopment,
 DGama2025MotileBrain}.  To identify the effects of these lineages on
@@
 interindividual variation in ventricular size and
-CSF velocities between larva at given developmental stages and throughout
+CSF velocities between embryos at given developmental stages and throughout
 development~\cite{Olstad2019CiliaryDevelopment, DGama2025MotileBrain, Jeong2024TheZebrafish}.
@@
 In this study, we have presented a computational model of CSF flow and
-solute transport within brain ventricles.  We used the larval
+solute transport within brain ventricles.  We used the embryonic
 zebrafish brain ventricles since their geometry and flow mechanisms are
@@
 Photoconversion experiments with cilia mutant
-zebrafish larva (\emph{smh}) aligned with these observations.
+zebrafish embryos (\emph{smh}) aligned with these observations.
 These simulations and experiments further indicate that
@@
 motivated by experimental observations of
-flow fields in zebrafish larval brain ventricles in which
+flow fields in embryonic zebrafish brain ventricles in which
 the fluid velocity increases towards the
@@
 Altogether, we have shown that the flow
-generated by ciliary motion in the zebrafish larval brain ventricles
+generated by ciliary motion in embryonic zebrafish brain ventricles
 is of the scale of the geometry~\cite{Olstad2019CiliaryDevelopment}.
@@
 
-The larval and adult zebrafish were raised under standard husbandry
+The embryonic and adult zebrafish were raised under standard husbandry
 conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
@@
 14/10 hr light/dark cycle.
-From fertilization to 3 days post-fertilization (dpf), larvae were maintained in egg
+From fertilization to 3 days post-fertilization (dpf), embryos were maintained in egg
 water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
@@
 Wholemount in vivo live imaging and photoconversion
-experiments were performed with zebrafish larvae at the 2 dpf stage obtained from inbreeding of heterozygous
+experiments were performed with zebrafish embryos at the 2 dpf stage obtained from inbreeding of heterozygous
 \emph{smh\textsuperscript{+/-};Tg(gfap:Gal4FF);Tg(5xUAS:Signal-Dendra2})
@@
 \subsection{Wholemount zebrafish in vivo time-lapse imaging and photoconversion of Dendra2}
-Two dpf larval zebrafish were anesthetized in 0.013\% MS222
+Two dpf embryonic zebrafish were anesthetized in 0.013\% MS222
 (Ethyl 3-aminobenzoate methanesulfonate, Sigma) in AFW and
@@
 \subsection{Intraventricular injection of microbeads and particle tracking}
-We carried out particle tracking in a larval zebrafish injected with fluorescent beads,
+We carried out particle tracking in an embryonic zebrafish injected with fluorescent beads,
 as described in previous work~\cite{Olstad2019CiliaryDevelopment}.
